\documentclass{book}

\usepackage[T1]{fontenc}
\usepackage{anttor}
\usepackage{url}

\title{Horrors 2: Clever Title Here}
\author{The Something Awful Forums}

\newcommand{\by}[1]{
  \vspace{-20pt}
  \begin{flushleft}
    {\large by #1}
  \end{flushleft}
  \vspace{30pt}
}


\begin{document}
\maketitle

\pagenumbering{roman}

\hbox{}\vfill
\begin{center}
Copyright \copyright 2009, multiple authors

\bigskip

This work is licensed under the Creative Commons
Attribution-Non\-commercial-Share Alike 3.0 United States License. To view
a copy of this license, visit
\url{http://creativecommons.org/licenses/by-nc-sa/3.0/us/} or send a
letter to Creative Commons, 171 Second Street, Suite 300, San Francisco,
California, 94105, USA.

\bigskip

This is a work of fiction.  Any similarity to actual events or persons,
living or dead, is purely coincidental, but totally awesome.  Please let
us know about it!

\bigskip

The {\em Horrors 2} project, including all source for this book and
instructions on how you can print it out and bind your own hardcover
copy, can be found at \url{http://gitorious.org/horrors2/book}.
\end{center}

\newpage

\chapter*{Praise for \em{Horrors 2}}
\noindent {\bf Suddenly, I was sobbing.} --- Luke Bavarius

\bigskip

\noindent {\bf This has been a mindblowing event} --- Ben Biddick

\bigskip

\noindent {\bf } --- Richard ``Lowtax'' Kyanka

\newpage

\hbox{}
\vfill

This is a pre-release copy of {\em Horrors 2}, a freely-redistributable
ebook.  This copy is made available for proofreading; a final copy will
be published for anyone to download, along with instructions on how to
print it and bind it into a real hardcover or paperback book.  For the
latest, check the thread on the Something Awful Forums at
\url{http://forums.somethingawful.com/showthread.php?threadid=3167703}.

\vfill

\noindent
The authors would probably like to dedicate this book to the authors.

\bigskip

\noindent
I am instead dedicating this book to anyone who has ever vomited tears
and/or blood.  Stay strong, pukers.

\indent --- cruft, July 2009

\vfill
\hbox{}

\tableofcontents


\newpage
\pagenumbering{arabic}

\part{Bavarious Reasons}
\include{stories/Batmanuel.The_Strang}
\include{stories/Torgo_.Brian}
\include{stories/Dr__Mulholland.The_Horrid}
%\include{stories/The_Iron_Fury.The_Horrid}
\include{stories/bagrada.The_Earach}
\include{stories/Unununium.The_Scarec}
\include{stories/THE_WORST_DOCTOR.The_Snake_}
\include{stories/Tufty.Dames__the}
\include{stories/leb388.The_Girl}
\include{stories/scarycactusjunior.The_Runawa}
\include{stories/mboger.Luke_From_}
\include{stories/Smokey.Thursday}
\include{stories/Barometer.L_B___V_H_}
\include{stories/Hamelin.The_Painte}
%\include{stories/gigz.What_Went_}
%\include{stories/KryonikMessiah.The_Ninjas}
\include{stories/IShallRiseAgain.The_School}
\include{stories/Paracetamol_Boy.The_Smile}
\include{stories/ack_.The_Dock}
\include{stories/rinski.The_Mansio}
\include{stories/Syphilicious_.What_Lurks}
%\include{stories/Rummanging.Nebulous_C}
\include{stories/antiloquax.The_Unexpe}
\include{stories/benitocereno.The_Beginn}
%\include{stories/A_Child_s_Letter.Yellow_Eye}
\include{stories/Decatur_Fist.The_Last_N}
%\include{stories/Brolita.Mac}
\include{stories/nmg.The_Horrid}
\include{stories/Ghost_Hat.Invisible_}
\include{stories/SummerGlaucoma.Bavarious_}
\include{stories/LesterGroans.Dream_Hyen}
\include{stories/murdered_by_owls.The_One_Ac}
\include{stories/fishguzzler.Untitled}
%\include{stories/TheElectronicOne.In_the_Mir}
\include{stories/WhereTheFishLives.The_Horrid}
\include{stories/on_time_for_once.The_Playgr}
\include{stories/overnightmike.The_Explod}

\part{You're no Hakan}
\include{stories/Part_of_Everything.The_Death_}
\include{stories/Madcosby.Son_Of_Bav}
\include{stories/Dr_Scoofles.The_Long_F}
%\include{stories/Peas_and_Rice.The_King}
\include{stories/reasonable_form.The_Six_Si}
%\include{stories/Smeef.The_Old_Ch}
%\include{stories/jidohanbaiki.The_Ocean}
\include{stories/Knuc_If_U_Buck.The_Horrif}
\include{stories/henpod.The_Last_C}
\include{stories/Mortonic.The_Very_H}
%\include{stories/Oatgan.The_Scream}
\include{stories/Lynxifer.The_Orches}
\include{stories/Cheesus_Christ.The_Horrid}
\include{stories/brylcreem.The_Creatu}
\include{stories/taurapo.The_Child}
\include{stories/Assless_Chaps.The_Mosqui}
\include{stories/Sirocco.The_Monste}
\include{stories/Cota_Froise.The_Horrid}
%\include{stories/Combat_Wombat.The_Librar}
%\include{stories/Phthalogreen.Pearl}
\include{stories/Sleepless_Dreamer.Reunion_Un}
%\include{stories/TheSpiritFox.Untitled}
\include{stories/Lord_Humongus.The_Cellar}
\include{stories/King_Plum_the_Nth.Untitled}
\include{stories/Irish_Joe.The_Boy_Th}
%\include{stories/Dirty_Sanchez.A_Tin_of_P}
%\include{stories/O_Tempora__O_Mores_.The_First_}
%\include{stories/Pro_Swordbro.Nobodys_Sa}
%\include{stories/Detective_Thompson.Words_Will}
%\include{stories/Count_Snapula.Dead_Tired}
\include{stories/Creflo_Chronicle.Black_Rive}
\include{stories/slackerpride.The_Area_t}
%\include{stories/Yaos.The_Killer}
\include{stories/Ghost_Hat.Character_}

\part{The Chronicles Of Biddick}
\include{stories/VelvetEvoker.Station_66}
%\include{stories/Donde_Esta.The_Promis}
\include{stories/BoldFrankensteinMir.Johnny_the}
\include{stories/lemonlime.A_Butter_K}
%\include{stories/Monkey_Trouble.The_Cave}
%\include{stories/Hired_Gun.The_Bodies}
\include{stories/Danger408.The_Torrid}
\include{stories/Safe_Driver.Hell_Cab}
%\include{stories/Livestock.Destiny_Ca}
\include{stories/JohnnyThreeToes.Horrid_Tra}
\include{stories/King_Plum_the_Nth.Flow_My_Te}
\include{stories/Yogi_Byron.Horror_D_o}
\include{stories/Funk_In_Shoe.I_am___bf_}
%\include{stories/Zarimus.Little_Men}
\include{stories/CannedMacabre.For_the_Ch}
\include{stories/Ridgely__Fan.The_Cocoon}
%\include{stories/raptorred.The_Blood_}
\include{stories/Lorentz_Factor.It_s_just_}
%\include{stories/BatsBjorg.The_Horrid}
\include{stories/Twigand_Berries.The_Sack_o}
%\include{stories/Helmet.Kindness_o}
%\include{stories/invision.Creature_O}
\include{stories/Scissorfighter.The_Book}
\include{stories/January.The_Journe}
%\include{stories/katiekawaii.Shiny_Toy_}
\include{stories/rinski.The_Monste}
%\include{stories/BigSkillet.The_Screw_}
\include{stories/HastyDeparture.A_Red_Sky_}
\include{stories/lucifer_chikken.The_Wareho}
%\include{stories/ding_dang_doo.Untitled}
%\include{stories/Dominic_Bones.Again}


\part{I'm out of funny things}
\include{stories/Quovak.A_Cursed_M}
%\include{stories/Anal_Surgery.Satanic_Re}
%\include{stories/Hantu.I__Lucius_}
%\include{stories/Brushingworth.Chamber_Po}
%\include{stories/duck_monster.Luke_Kills}
\include{stories/Orgasmo.Make_My_Da}
%\include{stories/kerimeton.White}
\include{stories/Zahgaegun.The_Pus_St}
%\include{stories/Bonaventure.Horrider_R}
\include{stories/Akbar.Wicked_Wor}
\include{stories/Swanky.Gold_Ribbo}
%\include{stories/Cruo.The_Smoker}
\include{stories/TarDolphinorShark.The_Homele}
\include{stories/Blurry_Gray_Thing.Monstrous}
\include{stories/The_Bananana.Deja_Vu}
%\include{stories/and_Into.The_Truly_}
\include{stories/JuicedSixFo.Untitled}
\include{stories/Baron_von_Eevl.The_Horrid}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Appendices


\appendix
\part{Inflamed Appendices}


\chapter{Colophon}

This book is a collection of stories from the Something Awful Forums,
inspired by the 1991 book {\em Horrors} by Ben Biddick.  Most were written
as a response to a challenge by forums moderator AYBraham:

\begin{quotation}
  Your goal: Write a short story in the theme of {\em Horrors}, the collection
  of short stories written by Mr. Ben Beddick when he was 13 years
  old. Each story is encouraged to feature the tragic protagonist Luke
  Bavarius, and must be more than 500 words each. Each story must show
  that "kids need to be respected and listened to."
\end{quotation}

This book was typeset by the \LaTeX{} document preparation system, using
the {\sf book} class.

It was set in the Antykwa Toru\'nska (``Antiqua of Torun'') typeface,
the most horriffying of all the standard \TeX{}live typefaces.  The face
was designed by Zygfryd Gardzielewski (1914--2001), and first cast in
metal in 1960 in the Grafmasz typefoundry in Warsaw.  The variant used
in this document was digitized by Janusz Marian Nowacki, a tremendously
cool dude from Poland, based off of photocopies of the original design.

\end{document}
