%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{The Stranger. Bavarious.}
\by{Batmanuel}



{\bf FOR MATURE READERS ONLY}



``Whiskey.'' The stranger sat hunched over in the dark
corner of the bar. I would have missed him if it weren't for
my curiosity and his harsh cigarette tinged voice. I sat the glass
down, opened the bottle and poured. ``Leave the
bottle.''



``What's troubling you, Mack?'' I asked as I pulled
my hand away from the bottle. He didn't look up. I tended to
pry, but I got the feeling that this guy wasn't someone to
fuck with.



Minutes passed and I forgot all about this stranger. Smoke hung
aimlessly in the air as someone busted out a trick shot in the
billiards game on the other side of the dark tavern. Maybe a fight
would break out. The regulars hate it when new people come in with
that slick shit. Almost right on cue, Jimmy Dean, a hulk of a man,
grabbed the trick shot artist around the neck and slammed his face
on to the table. This collision proved hard enough to send the
balls rolling in every direction. In practically the same breath,
the guy was thrown out onto the pavement. I let this shit happen.
No cops. Justice prevails and everything returns to a despairing
level of normality.



I turn my attention back to the stranger only to find him gone and
a fifty dollar gold coin on the bar. Under the coin was a business
card with one word on it: Bavarious. How I missed a man dressed in
all black, wearing a knee length black leather trench coat duster,
walk right out the door is beyond me. He had to have crossed right
in front of my field of vision, but I must have been too distracted
by the fight to notice him leave. Whatever.



I couldn't sleep that night. A feeling of uneasiness stuck
with me after my brief encounter with the stranger. He just wanted
a drink, right, lots of people do that, nothing weird about them.
All I could think of was his name. Bavarious. What did it
mean?



The next day, I enter the shit hole and take over for the night. I
expect much of the same. The regulars were already there and most
likely drunk. The stale air welcomed me as I pushed through the
wooden doors of the tavern. I felt a chill rush down my spine as I
looked towards the end of the bar. I didn't even make it
behind the bar before I heard a familiar voice that would remind me
of exactly why I could not sleep.



``Whiskey.'' Fuck. The stranger sat in the exact same
spot. `Same shit, different night' I thought to myself.
As if he didn't remember the minute details from the night
before, his grizzled voice said, ``Leave the
bottle.''



``So, are you drowning your sorrows away?'' I tended to
pry. He didn't look up, so I turned back to cleaning a yellow
beer stained mug. My mind wandered and I began to picture a lost
love. For some reason, I came to the conclusion that he fit the
motif of a heartbroken pathetic being taking everything he did
wrong out on himself. After this, he's probably going to the
nearest bridge and tease ending it all by dangling one foot over
the railing. Pathetic bitches never actually jump since
they're always back the next day drinking the same drink. If
not the bridge, he'll probably stare down the cold steel
barrel of a Beretta. Visions of my ideal womanly being played in my
head and I wanted to join him in downing the fuel of the unwanted.
The poor bastard losing the dark haired, tan skinned, beauty
running through a meadow on a sunny day, must be hell. I snapped
back to reality, shook my head and spun around towards this guy
with another bottle of whiskey. Almost exactly like the night
before, I fail to see him leave and I'm left to wonder why he
leaves the coin. One fucking tip.



``Hey Marv, did you see that cowboy looking son of a bitch
leave?'' Marv, the rat-faced bug-eyed shrew of a motherfucker,
shook his head with a look of confusion. I didn't look too
much into it, as the smoke hovering in the air tends to get to my
head. Unlike the night before, I was able to thwart any thoughts on
the guy. I mean, I was never the obsessive little bitch type. I
tended to pry, but that was part of the job title. I had to talk to
these characters while they drank the night away.



These nights always seem to run together. The same rituals repeat
themselves. The same poor saps gather in this shit hole. The same
rain falls outside. Jimmy and his gang exchange the same stories.
The same game of pool is played. The same fight breaks out. The
same song plays on the jukebox in the corner. The same `out
of service' sign hangs on the bathroom door. The same tourist
loses a wheel on the same pothole and drags his scared wife
who'd much rather stay in the car inside to use our phone.
The same poor fools come and go like fucking clockwork. I
can't complain.



Every night for the past week, the Stranger sat in the same stool
under the same shadow, said the same four words, drank the same
whiskey, left the same goddamn coin and vanished the same way. If
it weren't for the same bad vibes that surrounded him, I
would not have even noticed him.



I still have trouble sleeping at night. It's not that I
don't want to sleep; it's just that I can't. I
stopped trying. Techniques that bobble heads preach up and down to
levels of total effectiveness fail. Pills don't work, lying
in bed passively watching infomercial after infomercial have the
effects of making me wonder what exactly will blend. When I am able
to close my eyes, my mind begins to play a constant slide show of
the worst things imaginable. Decapitations. Bodies buried in
shallow graves. Houses burning. Screams fill my ears and I awake in
a cold sweat. I can't breathe. These problems began the first
night the stranger came into my dive.



I find myself feeling nothing but disdain when I gaze upon my
tattered reflection in the mirror. The unshaven man staring back is
not me. Bloodshot eyes sunken deep into hollow cheeks. I lift my
hand up and it shakes as if my blood created vibrations as it moved
through my protruding veins. The mirror not only shows a vacant
waste of a man, but also serves as a vessel for vengeful shadows
that dance around in the dimness created by the talking heads on
their soapboxes of lies. I look again at my shaking hand to find it
in a tightly clenched fist flying towards the primitive zombie in
the glass imprisonment. The glass shatters into a sea of red.



``Whiskey.'' He's there. Right fucking there. No
one knows where he comes from. No one even bothers to notice this
motherfucker. ``Leave the bottle.''



``You know, you've been coming in here for a while now
and it's the same four fucking words.'' I tended to pry,
but it has gotten to the point where this dude needs a crowbar
upside the head! I wanted answers or just a simple response.
``And man, you don't need to leave a fucking gold coin
lying there. That's too much goddamn money.''



As always, he finished off the bottle and left. As always, a
dirtied gold coin was on the counter. It was right then that I came
up with the worst idea of my life. Worse than moving out to this
fucking desolate place. This dumbass decision is probably my only
regret. Given the circumstances, this was a pretty sound idea and
very simple in execution. I called on Jimmy Dean and his gang to
rough the stranger up a bit. Easy as that. Not to really hurt him,
but to serve as an initiation of sorts.



Jimmy Dean was the type of brute that would fit in prison,
professional wrestling or driving a truck for a repossession
company. The brute, with his shoulder length hair, beard, sharply
clad in leather and denim, carried himself with a high enough level
of untapped fury that assured me that a show was just on the
horizon. His gang lacked the size, and I'd say intelligence,
but Jimmy aint exactly a member of Mensa. It was clear that the
6'6'' tall Jimmy was the leader of the group. These
hours of darkness were going to be something to remember.



``Whiskey.'' Like clockwork. I couldn't help but
crack a smile knowing that this dude was about to get fucked up.
``Leave the bottle.''



The jukebox in the corner began playing ``Here Comes the
Sun.'' Jimmy Dean and his cronies approached the stranger.
Unpromisingly, the green pained lights shuttered as the air became
stale. Marv sat in the stool to the left of the stranger, the other
guy behind him and Jimmy stood to his right. ``Who the fuck
are you?'' Jimmy asked in a slow but forceful tone as he
reached for the bottle. He picked it up, unscrewed the cap and took
a swig. He set the bottle down in a violent enough motion to cause
the liquid to splash on the bar. The stranger didn't flinch.
Hands still clasped around the glass, eyes still looking down.
``This isn't the a film noir. Hey asshole, I'm
talking to you!''



Jimmy reached out for the strangers collar. The temperature in the
room rose, but I felt cold enough to see my breath. My spine felt
severed as I fell back towards the wall behind me. Jimmy now had a
fistful of shirt and was close to unleashing a mallet of a fist on
this guy, when, in the blink of an eye, it was all over. The
stranger threw a swift enough boot to Jimmy's kneecap that
created a sound comparable to a thunderclap. As Jimmy doubled over
in immense pain, the stranger swung his hand around grabbing the
side of Jimmy's head, and, in a fluid motion, flung it down
towards the bar. The hard wood surface of the bar gave way to the
man's fucking head! The wood splintered around the hole that
was now host to a man's head. A second later, the man
standing behind the stranger took flight towards the pool tables,
slammed into the wall and became one with a pool cue. Marv, the
third man, suffered a brutal shot to the throat that sent blood
flying out of his mouth. He collapsed to the floor clutching his
sunken windpipe and gasping for air. I couldn't move.



The stranger turned his gaze to me. His eyes created black holes
amongst the leathery, sandblasted, sun damaged face. His black hair
dangled in strands from under his black hat. He reached up, stroked
the stubble on his chin and sighed. After surveying the
destruction, he nonchalantly picked up his glass, downed it,
reached into his pocket and pulled out a coin. His eyes never moved
from mine, and then a moment of clarity came upon me. The
uneasiness. I froze. I could see flames in the blackness. He stared
a hole directly through my soul. The carnage still existed among an
eerie peacefulness. He flipped the coin in the air, caught it with
his right hand, smiled and placed it on the counter. He then tipped
his hat and left. I remember seeing lights. 

 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Brian}
\by{Torgo!}



Brian hated the new house. Ever since his family moved in he could tell
there was something not right about it. He especially hated his room. It
was an old dusty old room that smelled like death. Their were cobwebs in
his closet and the room smelled like many years gone by.



The first few nights in the house came and went without any events.
On the eighth night though Brian was awoken by a noise eminating
from the closet. It sounded like a big dog was trapped inside. All
Brian could hear was clawing and low grunts and what sounded like a
big dog walking in circles in the closet. Brian cowered under the
sheets afraid to peer out. After ten minutes or so the sounds went
away. Brian lay awake the entire night.



In the morning Brian told his parents about what had happened. They
just told him that it's normal. That old houses have a way of
making sounds like that. Brian didn't believe them though. He knew
what he heard wasn't just a house. It was something else. Something
unnartural.



The next night Brian was awoken to the sounds again. As Brian lay
under his sheets he heard what sounded like sniffing and pawing
coming from the closet. He also heard something else this time.
What sounded like the sharpest fangs tearing apart meat. He also
heard chewing. As Brian peered out from under his sheets he saw a
pool of blood forming under the door. He quickly leaped out of bed
and down the hall to his parent's room. ``You've got to come quick
to my room and look!'' His parents slowly lumbered to his room.
``Their, in my closet!'' His Dad looked in the room but didn't see
anything. He even went to the closet and looked in the door but
didn't see anything.



For the next few weeks nothing happened{\ldots}



Today was Brian's Dad's birthday. Brian and his mom went to the
local mall and picked out some nice presents to give to him. His
mom bought him a toolset that had wrenches and screwdrivers and
Brian got his dad a nice necklace. While Brian's dad was at work
they made him his favorite meal and made a nice cake. Brian's dad
really enjoyed his meal and wore the necklace all the time after
that.



Brian was a lot happier these days because he hadn't heard anything
from the closet for a while.



Another thing that happened is that Brian and his family decided to
start raising rabbits. They had started with 5 five rabbits but now
they had 9.



One day Brian went outside to feed them and was shocked because
there only 3 left. The fence had been broken into and their were
large tracks.



Soon after this Brian started hearing noises from his closet again.
It was the same as before. All Brian could do was cower under the
sheets until the morning light returned.



One dark and wintery night Brian was hiding under the blankets
while he heard the rustling from his closet. As Brian shook and
shivered the noises were growing louder and more violent. Suddenly
he heard the creature burst forth! It shattered through the closet
and crashed into the opposing wall. Brian was now paralyzed with
fear. He dared not look out from his sheets. He could hear the
creature walking towards him, its claws clacking on the floor. He
could hear the beast sniff his sheets. Suddenly he felt the
creature leap onto his bed. Through the weaving of his sheets he
could see glowing red eyes and a large grimacing mouth full of
fangs. But the most shocking thing of all is that he could just
make out the glimmering of something hanging from the creatures
neck in the moonlight. It was the necklace he bought his
father!



``You were always my child'', the creature snarled to him. ``And now I
will give you the Dark Gift!'' ``After all like Father like son!'' The
creature then bit Brian on the face and the transformation began. 

 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{The Horrid Assignment}
\by{Dr.~Mulholland}





Luke Bavarious walked through the front doors of the police
station. He pushed the doors open. Inside was his boss, Johnny
Zepeder.



``Bavarious!''

``What do you want Johnny.'' Bavarious said.

``I have a new assignement for you! I hope you will take this new
assignment!''



Luke Bavarious took the new assignment and opened the manilla
envellope like a kid ripping apart a Christmas present that the kid
had been waiting for. Inside the manilla envellope was a new
assignment: Kill the local mafia boss.



Bavarious looked up from his new assignment at his boss.
``Johnny.''



``What is it, Bavarious?''

``This doesn't sound like-{\ldots}''



Bavarious keeled over and from his mouth cascaded a river of vomit.
His eyes vomited tears too. The tears and vomit he was vomiting
pooled on the floor in a horrible cocktail of tears and
vomit.



``Bavarious!''



Bavarious could say nothing. The cocktail kept pouring out of his
mouth.



``Dear God, I'll get a doc-''



Johnny's neck exploded with blood vomiting out of the veins.
Bavarious screamed. He turned around and screamed again. He raised
his Baretta (all New York detectives have one.).



Bavarious turned around and looked at his boss. ``I'm quite sorry,''
Bavarious said. Johnny said ``you'd b-better b-be'' and belched out
one last spray of blood stained vomit. Bavarious turned and walked
out the doors, pushing the doors aside to get through.



Bavarious looked at his new assignment that he just got. Kill the
mob boss. But why? Bavarious was not a killer. He was a good man, a
good Christian man. But he has a Baretta. Barettas are for killing.
He must kill the boss. He grabbed his Baretta and loaded it and got
in his car and hit the gas.



Bavarious arrived at the mob boss's house. He got out of his car
and shut the door behind him and then locked it. He walked to the
front door and knocked on it three times. Then he realized. The
house had been abandoned since the horrid tragedy that had happened
there 50 years ago. He saw it in his mind{\ldots}



``Hi, Daddy'' said the kid. The kid smiled. Kids are so wonderful and
carefree in this terrible world.

``Hi there kiddo'' said the dad. The dad looked to be about 35 and
had a beer gut.

The dad turned around and walked out of the house, pushing the
door, opening it, and then pulling it, closing it. The kid turned
around and turned on the TV to get out of the horrors of this
wretched life. It was 1959. The kid just got the TV as a birthday
present. His birthday was yesterday.



The kid heard horrid noises from outside. He got up and opened the
door. His dad was lying on the ground with a silhouette on him. He
looked up at the man who was casting the silhouette. He had a can
of beer in his right hand and a Baretta in the other. Suddenly a
semi drove across their front lawn at the speed of fifty five miles
an hour, running the man and his dad over at the same time. Blood
vomited all over the front of the semi and all over the nice clean
green cut grass.





Bavarious woke up. He had fallen asleep. He had dreamed of what
happened in the mob bosses house 50 years ago. Then he realized. He
was the kid of his dreams. Bavarious let out a scream and turned
and ran and went out the front door. He tried to open the door on
his Ford Contour but it wouldn't open. Suddenly, a headless corpse
with a can of Coors walked across the lawn towards him. Getting
closer and closer. Bavarious screamed. He got out his Baretta and
fired. And fired again. The bullets punched bulletholes through his
rotting stinky flesh but they didn't hurt him.



Bavarious screamed and vomited again. The remainders of his lunch
floated around in a blood tinged mess all over his Ford Contour.
The Coors holding headless man kept getting closer. Bavarious could
only do one thing. This was the only option. His father would have
wanted it this way. He stuck the Baretta into his mouth and pulled
the trigger. But he had used all of his bullets. He vomited again,
pouring vomit down the barrel of his gun. He screamed. Finally the
Coors man was two feet away from him{\ldots}



``Luke Bavarious, why did you hate me?''

``Who, who are you?''

``I am an artist. I am the man who killed your father in a
semi.''

He screamed. 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{The Horrid Refraction}
\by{The Iron Fury}


{\em This entry picks up immediately after {\rm The Horrid Reflection}
ends.}


Suddenly, I was sobbing. Once the tears ceased leaping from my
blood-drenched sockets, I took a moment to recollect myself. My
muscles tensed. I looked down at the dark, mangled body next to me.
What the fuck, I thought. I still had glass in my face. My head
throbbed. I rolled the corpse onto its back. And vomited. I vomited
so hard, so long, that a vessel burst in my eye, coloring it red as
Satan's ass. Its body had dissolved into phlegmy puss. The alley
stunk of fear and sweat and blood. And now vomit.

The glow of some unspeakable evil hung heavy, looming over the dark
corridor. It pulsated. I had to get out of there. I had to think
about what just happened.

I got to my lodgings and cleaned up. As I was picking glass out of
my shattered skull, a knock sounded. Heavy- angry almost- on the
thick wooden door. Inching to the corner of the room, I determined
to wait them out. I had darker matters to attend to. What was that
thing I had glimpsed in that dim alley? Why did it wear my badge?
Why was it--

``Bavarious! I know you're there!'' a feminine voice bellowed. I
could sense there would be no introspective pondering for me this
evening. I edged to the door. Skin standing at attention, hairs all
prickle, I passed my hairy appendage over the door knob. Slowly, I
creaked it open. Standing before me was a person I had thought,
hell, hoped I would never see again.

Nora Fury. A halo of fiery red curls cascaded about her, wild and
unrestrained. Just like she was. A single cigarette smouldered in
her claw-like grasp. As soon as she was in the dank room, a slap
encircled my raw face. Blazed like the fury for which she was aptly
named.

``How dare you leave me in Mexico,'' she sneered. I sneered back at
her sneer.

``How dare you shack up with that drug lord,'' I returned with equal
disdain. ``Can't we just move on? You're a tough dame. I knew you
would come out on top. Here, lemme pour you a drink.''

I knew that when Nora was mad, she was a hellcat under the covers.
Maybe a nice distraction would ease my beleaguered mind. I turned
to the crimson cabinet behind my desk and my hands found their way
to two glasses and a bottle of whiskey.

``So what d'ya need from me, Sugar?'' I smarmed, holding out the
stiff libation. It dropped to the floor, shattering at my feet.
There was no one in the room.
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{The Earache}
\by{bagrada}



The night was dark and muggy, the heat weighing down on me like a
heavy winter jacket in the spring. The ringing in my dull aching
ear was the only sound. I stuck in my pinky and wiggled it, then
frowned at the sticky piss-yellow wax left on my finger. Not for
the first time, I thought about seeing a doctor. I shook my head.
My ear has never been right since that day in the pond, so long
ago. Time enough for doctors in the morning. Tonight, I had a girl
to save.



``You have to help our friend, Mr. Bavarious!'' the kids
had said. ``She's been kidnapped by some freaky
cult!'' The cops didn't believe them. Neither did their
parents. But I did. I knew the dangers of not listening to kids. My
sister{\ldots} if I'd listened to her she'd still be
alive today. I'd told her she was just a kid too, that I
didn't have to listen to her, that I could swim where ever I
want. I almost died that day. Instead she died, died much too
young, died saving me. I loaded my beretta and nodded to them.
``Don't worry; I'll bring your sis{\ldots} I mean
your friend back to you.'' The boy shook his head sadly and
looked at me as I left.



As I approached the abandoned warehouse where they said their
friend was taken, I glanced to the stars and felt a shiver run down
my spine as they seemed to blink in the night sky. A coppery rusty
scent floated on the stale breeze. I was close. I walked up to the
old wooden door, with my finger on the trigger, and kicked it open.
LIGHT. Bright searing light. Red rusty light. Purple smoky light.
Spirally yellow light. Grey and black and white colorless light. I
didn't hear the broken door clatter to the ground in front of
me or the vomit that suddenly projected from my throat, just the
constant droning ringing in my ear, louder now.



The lights faded as I tried to blink through the afterimages to
look around the room. All around an old stone altar were the
cultists, theirs eyes bleeding, their robes coated in glistening
puke, their mouths slack in death. On the altar floated the
girl{\ldots} or parts of her. She was split in two; her eyes still
smoking, her hands still raised to the sky in prayer. The left side
of her mouth opened in a bright smile, while a few feet away the
right side gaped wider as if she were screaming. She was pinned in
the air like a butterfly to an insect spreading board. In between
her two halves, something moved, then the world ended around
me.



The air became thick, muddy and gritty, like I was back beneath the
pond again that awful day. The lights returned{\ldots} rusty red,
black and white, vomit green. The horrible spiraling yellow. The
girl melted away, her long blonde hair splashing to the floor, and
I felt the air shift as something floated towards me. The ringing
in my ears was now the tolling of great bells, driving me to my
knees as my gut heaved and tried in vain to find something else,
anything more, to throw up. I felt something bitingly cold and
scalding hot brush my arm as the colors floated past me, and then
my arm wasn't there anymore. It floated off into the lights
which were now many bright balloons, all painted with crying faces
I could almost recognize. I blinked and the balloons popped
revealing a swarm of fireflies, each with a uniquely colored light.
So beautiful and horrible as they flew by me towards the door,
their lights blinking in a pattern my mind fought not to
understand. The tolling of the bells was now a tinkling song that
made me want to float along with it, if only I could recognize the
tune. The fireflies were floating spiders, then darting fish, then
the drowning faces of my dead sister. I staggered to my feet and
turned towards the door as the colors wafted through and became
dark. I took a few stumbling steps after them but stopped when my
foot kicked something metal and heavy{\ldots} the beretta I'd
dropped. Whispers suddenly, in my ear. My little sister.
``Breathe, Luke.''



I gasped for air, realizing I hadn't taken a breath since
kicking the door, and fought my way to the center of the room,
kicking the bodies of the cultists aside, and then gathering the
messy blonde hair and other unrecognizable bits into a clump in the
crook of my remaining arm. ``It's okay.'' I said.
``I've got you.'' With the smell of rusty blood in
my nose, the taste of bile and vomit in my mouth, the ghost of my
left arm screaming that it's still with me, the afterimages
of the wondrous lights seared into the back of my eyes, and the
constant and steady ringing in my ears keeping me company, I
staggered out into the now starless night. ``Don't worry
sis. I'll get you home.'' 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{The Scarecrow}
\by{Unununium}


Luke parked his car at the side of the road. He walked over to the
massive corn field and squinted. Somewhere out there was his big
break. If the legend held true, he knew he'd have it set. Trying to
be silent, Luke pulled apart rows of corn and began to make his way
to the center of the field. Looking out, he knew he had a long way
to go. His revolver sat snuggly in his jean pockets. He wasn't
afraid to use it if he was heard.

Luke's sneakers sunk into the moist soil, as he crept through the
corn field. He knew something was up. The full moon shined brightly
into the center of the corn field. In the center of the field stood
a mounted scarecrow. Its eyes beamed like an illuminating light,
and the straw covering its bare body poked out through seams on its
clothing. Luke was here for a purpose. As an FBI investigator, it
was his job to trot through this corn field to investigate the
claim that underneath the rugged clothing of this lifeless
scarecrow lays a corpse. He barged through a petite opening in the
corn field, and reached the scarecrow. The scarecrow was a morbid
mass of lifeless straw. A knife was tied into the scarecrows hand
with a piece of string. Luke unfastened the rope holding the
scarecrow unto the cross. The scarecrow then toppled over, landing
on Luke. It was heavier then he imagined. Luke rolled over, getting
out from underneath the scarecrow.

Luke looked out into the corn field. It was an infinite abyss of
yellow and green plants. From his viewpoint, he couldn't see out of
the corn field. Luke turned back, and noticed in shock that the
scarecrow was now standing. Luke took a step back, but the
scarecrow moved in closer. With one luxurious swipe, the monument
of hay and straw sliced through Luke's neck with its knife. Luke
vomited wildly through his neck while disturbing and tremendously
rust colored blood came out through the same orifice. A stream of
strawberry-red blood dripped from the scarecrows metallic and
majestic knife, that soon entered into Luke's head. Luke dropped to
his knees. He gurgled like a drowning infant as he struggled to
breathe. Luke vomited blood through the hole in his head as
bubble-gum colored brain matter and blood exited Luke's head with
the scarecrows knife. Luke wasn't quite dead yet, he slowly crawled
away from the deadly straw body, but it was too late. A gust of
wind and magic picked Luke's body up into the air. Like quills, the
scarecrows straw exited his body and pierced into Luke's flesh.
Luke let out one final scream, before he died. Luke's lifeless body
floated magically to the brown wooden cross. As the lifeless
scarecrow soon faded into the ground, Luke's body strapped onto the
cross. The scarecrow was now gone, but a new scarecrow has come to
take its place. 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{The Snake Lady}
\by{THE WORST DOCTOR}


There was a kid who came up to me one evening after I had left my
precinct, sniffling and tugging on the left leg of my pants. He had
snot all over his face and I was pretty disgusted. But my job is to
help people, not to pass judgment, so I decided to give him the
benefit of the doubt. Maybe he had cash on him.

``What's wrong, kid?'' I asked. An ominous breeze
blew from the south. It was going to rain. I didn't ask him
why he was by the bar at such an age. A kid's gotta do what a
kid's gotta do.

``Some lady stole my candy,'' he told me, wiping the snot
from his nose and the tears in his eyes in an upward motion. Both
bodily fluids ended up on his forehead.

``Well,'' I said, popping the collar of my Armani jacket.
``I can handle that. Stay here, sport.''

I gave him a pat on the head, not unlike the pats my father used to
give me when I hadn't completely screwed everything up, and
went into the building.



There was nothing in there that was particularly special, save for
a few local drunks hanging out in the corner. The bartender gave me
a nod, a knowing one; he could tell from my hat and flashy badge
that I meant business. That's what it is to be a private
detective, after all. I sidled up to the bar and took a seat on a
rickety barstool, ordering my usual: an appletini. A girl at the
bar eyed me. She looked like a bitch. I knew I had found my
target.



``Hi,'' she said once I got my drink. The light leaked
from the neon signs that said ``PARADISE''. I chuckled as
I sipped my cocktail gingerly. How ironic.

``What can I do you for,'' I asked. I didn't mean
it the way I made it sound.

``It's not often a man like you comes to town,''
She said, giggling. I noticed she was wearing a rusty
necklace.

``Yes,'' I said simply. I don't like to waste
words. She put her hand on my arm and looked at me with glimmering
eyes. I said nothing.

Suddenly she was grabbing onto my arm and digging her horrid nails
into my flesh. I cried out. My skin was on fire. She drew blood and
laughed like my grandmother used to.

At that moment I knew I hated her.



``You're a thief and a liar!'' I yelled, kicking my
barstool into her lower half. She fell down and brought my
appletini with her as she tried in vain to grab the bar for
support. The people around us piled out of the bar while screaming
and running. I was glad they knew enough to leave at this moment.
It was going to get ugly.

``Bavarioussssss,'' she quipped, her tongue long and thin
like a snake. Her rusty necklace was rusted. Even more rusted than
before. She had no legs now. She was like a snake on the bottom.
Cruel and unforgiving. She was going to squeeze me. I knew
it.



I felt like vomiting. A thin stream spluttered from my mouth. It
got all over my new boots. I was blind with seething rage as I dove
toward her, knocking over bottles of Jack Daniels. I began to punch
and punch and punch. I was screaming though I didn't know
why. She fought back feebly. She tried to kick me but she had no
legs anymore. I laughed. How unfortunate.



She was bleeding a lot. It got all over me. Luckily I had tucked my
tie into my belt. It wouldn't get in my way. She scratched at
me again and called me mean things. There was blood, awful blood,
leaking from her eyes. It was red. Dark red. The color of a heart
after it's been taken out of a body. I was going to take her
heart out of her body. Then I thought against it. Too messy.



Finally I drove the rusty necklace into her. She died of rust
poisoning. She giggled one last time at me before slumping onto the
floor. Then she disappeared in a cloud of smoke.

``Should've gotten your tetanus shot,'' I
commented. I gathered up the kid's candy, colorful wrappers
that may as well have contained pure cane sugar, and went
outside.



The kid was there, snot dried in his hair. He was wringing his
shirt with his grubby little hands when he saw me, fearing the
worst. I dropped the candy on the ground in front of him, and lit a
cigarette for myself.

``Don't let it happen again, champ,'' I said. He
nodded and understood. As he walked away, munching on his dental
problem candy, I was reminded a little bit of myself. Life before I
became a detective. A simple, idle life with no worries. But that
was all behind me now.



I'm Luke Bavarious, detective extraordinaire. 

 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter[Dames, they're all the Same]{Dames, they're all the Same - a
Luke Bavarious detective story inspired by the works of Ben Biddick.}
\by{Tufty}





I'm a private detective. Luke Bavarious is my name. Bavarious by
name, Bavarious by nature. I own this city. The feds think they've
got this place locked up tight, but the criminal scum of the
underworld run rampant through the darkened streets committing
crimes and vandalism. This is where I come in. My name is Luke
Bavarious, and I'm a private detective.



I'm a man with nothing to live for and nothing to lose, and there's
only two things in my life that I wouldn't want to lose, and
they're both Berettas. One is a gun, and I keep it locked and
loaded in my desk drawer, and the other is my sexy secretary, Gina
Beretta. An Italian seductress packing a big chest, tiny waist, and
a loaded gun. There's nothing sexier than a woman with a gun.



The phone on my desk rings, I pick it up. It's Gina. ``There's
someone here to see you.'' says Gina. ``Send them in.'' I reply. Into
my room walks the most gorgeous dame I've ever seen in my life. I'm
talking beautiful - tall, brunette, and an ass like a couple of
melons. Says she has a job for me - the big one, my ticket out of
this hell hole they call a city. She tells me that a couple of big
time crooks are planning a heist on the New York City Bank, and she
wants me to stop them. ``But how do you know this, and why are you
telling me?'' I ask. ``One of those jerks is my ex-boyfriend, and the
idiot left the bank's blueprints and a copy of their plan at my
place before he dumped me.'' ``Hmmm{\ldots} that does sound stupid. I'll
take the job.''



Fast forward to a week later and I'm waiting outside the New York
City Bank. According to the plans, the crooks should be here any
minute. I lean against a street light and light up a smoke, the
wispy trail of smoke rises into the cool night air. I hear a click
like the sound of a cockroach being squashed, and I feel a cold,
hard object poke against my back. ``Don't move, Bavarious'' says a
rough voice filled with pure and utter hatred. The dame set me up!
I knew I never should have trusted her, dames are all the same.
With the lightning-quick speed of a cobra I kick my leg backwards
and send the gun flying out of my assailant's hand. It lands on the
road before skidding down a drain into the sewers. Before my
attacker could even react I've drawn my gun and spun around.
Suddenly, with shock and disbelief I see that the face of my
attacker is actually that of the dame who hired me for this job!
She must have been changing her voice to fool me. She looks
different this time, her eyes are as red as freshly spilt blood and
her skin has a greyish twinge, like a freshly embalmed corpse. ``Why
did you try to set me up?'' I ask her, pressing the gun into her
chest. ``Because{\ldots}'' I press the gun harder into her chest,
impatient for an answer. ``Because, Luke{\ldots} I am your sister.'' My
head reels as my world comes crashing down around me. My sister? I
have a sister? I think back to my childhood and don't remember
having a sister. Thinking of his troubled past and childhood caused
Bavarious to vomit. He did not like to think about his past. As the
vomit pooled on the floor, he could see the reflection of the dame,
his supposed sister, in the slick surface of the pool of vomit. The
sight of her like that brought it all back to me, but in my
distracted state, the dame gives me her best right hook right in my
jaw, and the world turns black{\ldots} 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{The Girl}
\by{leb388}



The night was cool and dark, unusual for summer. But then again, it
was a night for unusual things. Slashes of rain whipped at my face
as I navigated the alley. Fireworks vomited sparks of blue and red
into the sky. The booms sounded more like gunshots from Berettas. I
should know; I have one. I am a private detective.



My name is Bavarious. Luke Bavarious.



I'd been at the bar, kicking back a few martinis, when I got a call
about a noise complaint. I work every night if I have to, even the
Fourth of July. The job sounded easy enough, and after all, the
people need me. I am their protector. I am Luke Bavarious.



But on this night, I wasn't as alone as I thought. As I walked
along, I heard the sound of footsteps. I stopped. ``Who's there?'' I
yelled, raising my Beretta.



No response.



I tensed. ``Come out where I can see you,'' I ordered. ``Now.''



A child stepped out of the shadows and into the trashy street. I
say that because the street was littered with trash. The people
there were usually nice.



Most of the time.



I holstered the Beretta, at ease. The girl looked young. Maybe six,
could even be seven. Who knows, in this town. Probably lost. She
clutched a doll and wore a dark raincoat. Not like that was any
help, in this torrential weather.



``Are you okay?'' I asked her. ``Do you need help?''



``I need to find my mommy,'' she whimpered. She was crying.



A girl that young shouldn't be alone in an alley off 42nd St. in
New York. Especially on a night like tonight. I pulled out my phone
to call to see if anyone reported her missing, but something was
wrong. I looked up at the sky. Fireworks still going at it like
crazy missiles exploding in the air. That's what they were.
Missiles. And that's when I saw it. The creature. The item the girl
was holding wasn't a doll after all--it was a monster. It had
buttons for eyes. There was no mouth, just stitches. The hair was
yarn.



``Get out of here, fiend of hell!'' I screamed.



I grabbed it. If you can call it an it. The hands were soft. At
least until I flung it into the puddle. Then they were wet. I
screamed, shooting at it with my Beretta. I felt a fear no one
should ever have to experience, a fear of the worst possible
things, a fear of death and everything around it. It was taking
hold of me, drowning me, and I kept spinning and spinning in the
abyss of its grip. I felt like vomiting. Maybe that was just from
the martinis. I shot it again and again, and so on. And then I
stopped.



A flash of light made me see its face. Kind. Adorable. Just a doll
after all.



Why do I always investigate noise complaints when I'm drunk?
Suddenly, the girl was sobbing. And I felt like an asshole. 

 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{The Runaway}
\by{scarycactusjunior}






Jimbo hawked a giant ball of phlegm between his dangling feet off
the boat dock and stared into the murky water as he watched his
creation sink to the murky inky depths of the lake. Watching it, he
thought long and hard about his current situation with his Pa. Pa
was starting to frighten him with his publicly known alcoholism.
Every horrible night Pa would sit on the porch of the rustic swamp
cabin in the wicker rocking chair by the front door and drink his
Coors repeatedly for hours. And then, with his eyes horridly
bloodshot he would come stomping back into the cabin and find Jimbo
for the nightly beating. Sometimes the beatings were so bad they
would leave Jimbo in a sobbing heap, his blood and tears mixing
together on his lips. Pa wasn't always like this, Jimbo had
vague memories of happier times; the sunshine days of his early
childhood when his mother was still alive and Pa hadn't drank
so much.

Jimbo heard the front door of the cabin slam, followed by
Pa's heavy, booted footfalls. The wicker rocker began to
creak. Jimbo noticed that the sun was rapidly sinking, the drinking
would begin soon, followed by the almost ritualistic beating.

Jimbo thought to himself. He thought that he didn't have to
return to the cabin. He could make Pa come looking for him in the
swamp, at night, while drunk. Decided, Jimbo arose and proceeded to
make his way deep into the swamp, trying to get as far away from
the cabin before full dark made it impossible to find his way
through the swamp. He tried not to think of how the cypress trees
looked like forlorn entities locked forever in their torment
because of the way the fading daylight lit them, or of the stories
his friend Benny used to tell about the Swamp Creature.

The Swamp Creature was said to be a being of such hideous
countenance that it would drive any who were unfortunate to see its
horrible face completely and totally insane. Privately Jimbo
thought it was the thing that had made the crocodile eat his mother
all those years ago. Jimbo remembered the sight of all that blood
on the water; red blood on black water that boiled and roiled like
a vicious tempest. Jimbo shuddered and tried to push those thoughts
out of his mind.

Distracted as he was, Jimbo slipped on a patch of slimy mud and
slid on his buttocks a little way into the swamp-water. He jumped
up quickly and stared wild-eyed around him, looking out for crocs.
His heart was pounding; he could feel the blood pounding in his
ears. Suddenly, he was very afraid. He fought the sob welling up
within him and went on his way. It was too late to turn back.

He saw something then, a glint of gold in the reeds. Bending down
to get a closer look, he noticed it was a badge of some sort. Jimbo
picked it up and felt a feeling dread wash over him; it was a
slightly tarnished police badge. Jimbo read the name on it
aloud.

``Bavarius{\ldots}''

There was a squelching sound behind him, and Jimbo turned around to
come face-to-face with a creature straight out of nightmares. It
looked like it had been a man once, but now it had no eyes and only
one shriveled ear remained. It looked almost half-melted and
inhuman.

Jimbo vomited great jets of putrid vomit into the swamp. Some of it
landed on the Creature and made it even more horrendous to look at.
Jimbo vomited again until he could vomit no more. Tears sprang into
his eyes and he sobbed loudly, vainly. The Swamp Creature moved its
stumpy arm to catch the paralyzed Jimbo and crush him into the
once-chest. It breathed its foul swampy breath into Jimbo's
face as it spoke.

``I am Luke Bavarius.''

At only thirteen years old, young Jimbo went instantly
insane.



Two days later, there was an article in the newspaper about a
bizarre murder that had happened out at Old Man James's
cabin. Old Man James had been found dead in his wicker rocking
chair, a brass police badge shoved into his jugular. He had not
even dropped the beer he had been holding. On the cabin walls
behind him, written in blood and vomit was a single cryptic word
scrawled over and over: ``Bavarius''. Police searched the
cabin and found James's son rocking on his heels in the back
room, wearing only urine-stained briefs and giggling softly to
himself. He was taken into custody and placed in the State mental
hospital, where he remains to this day singing softly to himself
over and over.

``Bavarius.'' 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Luke From Payroll}
\by{mboger}


I sat down at my desk. The sound had come again. It was my phone
ringing. My hand shook slightly with the heavy receiver in my hand.
The sleek receiver was transmitting and receiving, ready to take
the call. I work in the payroll department. My name is Luke
Bavarious. I hate my fucking job.



People had been complaining about discrepancies in their paychecks
for about a year now, so I finally decided to execute the plan I
had been working on for as long as I can remember. I was assigned
to raise the Demon Lord Gol'Sothog from the fiery pits of
hell.



I spoke into the phone, ``Payroll, this is Bavarious. Luke
Bavarious.''



On the other end of the line, ``Hey, Lou, this is Bill Taylor over
in{\ldots}''



``Luke,'' I interrupted. ``The name is Luke Bavarious.''



``Ok, sorry. Whatever. The reason I'm calling is{\ldots}''



``Say it,'' I interrupted again.



``What?''



I was starting to lose my cool. ``Luke. Bavarious. LUKE! FUCKING!
BAVARIOUS!''



``Jesus, Luke! Sorry! Luke Bavarious, Luke Bavarious, Luke
Bavarious,'' Bill sniveled into the phone. He doesn't deserve to
live and it was then I made up my mind. ``Man, you need to switch to
decaf. Listen, -Luke-. I have a problem on my last paycheck. I had
3 hours of overtime last week that I wasn't paid for and Debbie
over in HR told me to take it up with you.''



Over the last year or so, I, Luke Bavarious, have been slowly
syphoning money out of employee paychecks to fund my Demon Lord
Gol'Sothog sacrificial altar. Twenty bucks here, fifty bucks there.
It adds up.



``Not a problem, Bob,'' intentionally mistaking his name and then
pausing for him to respond. He doesn't. He's so pathetic, he makes
me vomit in my mouth a little bit and then I have to force myself
to swallow it down. He's barely worthy of sacrificing to
Gol'Thogthog, but he'll do. And because he made me swallow my own
vomit, his sacrifice will be slow and painful. ``I see the missing
hours here. Why don't you come up to my office and I'll square you
away.''



``Sounds good. I'll be right up!'' The phone disconnects.



He's fallen for my ruse. Hook. Line. And Sinker. And Luke
Bavarious.



I have about two minutes to prepare, but that's two more minutes
than I need. I'm Luke Bavarious, always prepared. I'm hiding behind
the door with a syringe full of knock-out serum when Bill enters my
office. He doesn't even put up a struggle as I slide the syringe
into his neck, the needle vomiting forth sweet slumber into his
veins.



Bill doesn't wake up until just after midnight. I had waited until
everyone had left the office for the night before loading Bill into
the back of my Dodge SRT-4. A lot of people think the SRT-4 is just
a Dodge Neon with a turbo, but fuck those guys, I love this car. I
drove my totally sweet SRT-4 to the secret location of the Demon
Lord Gol'Sahblah sacrificial altar and waited.



Bill's eyes open and he tries to speak, but he can't. Did I mention
that my knock-out serum was also a paralyzing toxin? Bavarious!
Bill is laying on a solid gold altar, surrounded by dark, fiendish
incense burners. Expensive incense. I had to import it from
Thailand and everything. This is why I was skimming money from
paychecks. Have you ever priced a solid gold sacrificial altar? I
mean, it's not like you can just walk into Bed Bath and Beyond and
pick one out. This shit is expensive.



I raise the jewel encrusted ceremonial sacrificial dagger over
Bill's body. His eyes widen in terror. It's the only movement he's
capable of making, thanks to the knock-out/paralyzing toxic serum,
which also wasn't cheap, by the way. I can't stress enough how much
money this whole thing has set me back.



I began chanting. With each long forgotten word uttered, I can feel
the power in the room increasing. A dark mist begins to swirl and
in that mist I see another dimension. Closer, closer, two worlds
are becoming one. There is only one last thing left to do. I plunge
the dagger into Bill's heart and the ever so slowly twist the
blade. I lean over and whisper into Bill's hear, ``Bavarious.''



I'm then instantly thrown to the ground as an interdimensional rift
opens, unleashing the Demon Lord Gol'Sobeys from his hellish
prison. The Demon Lord smiles at me and I smile back.



``YOU HAVE DONE WELL, LUKE BAVARIOUS. NOW THAT I AM FREE, THERE WILL
BE NO STOPPING ME. I WILL RULE THIS WORLD AND EVERYONE WHO INHABITS
IT.''



``All glory be to Gol'Bladder!,'' I shout.



``YOU HAVE SHOWN YOURSELF TO BE A FAITHFUL SERVANT. AS SUCH, YOU
SHALL BE REWARDED. YOU WILL BE MY RIGHT HAND WHEN I ENSLAVE THIS
PUNY WORLD. YOU WILL HOLD THE HIGHEST RANK IN MY ARMY. THE RANK OF
PAYROLL ADMINISTRATOR.''



I staggered backwards and fell onto a desk that had materialized
behind me. A nameplate sparkled on the side of the desk. Bavarious.
I picked up the phone and heard a horrible ring tone. Suddenly, I
was sobbing.



The moral of the story: Kids should be respected and listened
to.



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Thursday}
\by{Smokey}

\section*{Chapter 1}

Luke Bavarious sat on the sidelines feeling completely helpless as
he watched his team lose yet another game to their cross town
rivals, the Anencephaly High Babies. ``That Dan thinks he's soooo
good at basketball, but one day I'll show him!'' he silently
mouthed to a passerby who made the unfortunate mistake of making
eye contact with him. He decided he had seen enough and couldn't
watch anymore, mainly due to the fact that the game was over.
Suddenly, he had to poop.



Luke made his way to the dumpster behind the gymnasium. As he
pulled his overalls down to relieve himself, he noticed a pair of
girls walking along a path about 25 feet to the right of him . ``I
must have sex to those girls!'' Luke yelled at the birds flying over
head. He quickly finished his business and tossed his diaper into a
nearby tree.



``Oh, you like those girls do you?'' a deep voice boomed from
above.



Luke looked up and saw a large, muscular black man sitting in a
tree branch directly above him. The man hopped down and immediately
began dribbling a basketball with both hands, or ``double dribbling''
as it's referred to in the NBA.



``Sure, I like those girls and I want to lose my virginity by
carefully placing me boner inside of their girl boners, what do you
think about that!'' answered Luke.



''You know what you'd like better than losing your virginity?''
the man coyly asked. ``Never having sex, that's what!''



``Wow I never thought about it like that! Heeeey{\ldots}what's your
name anyhow mister?'' asked Luke.



``My name is AC Green, and i'm a virgin.''



\section*{Chapter 2}

The next morning, AC picked Luke up in his light blue 2003 Dodge
Caravan. They whistled the theme song to ``The Adams
Family'' in perfect unison as they headed to the karate dojo
to learn some much needed self defense.



``You're going to eventually find that women will try
and make you do things you don't want to do Luke, and that
sometimes the word ``NO'' just isn't enough to stop
them from hassling you.'' AC said, his eyes searching for a
parking spot the entire time. ``That's why we're
going to learn some self defense moves today''.



They spent the next 4 hours rolling around the matt and throwing
nasty elbows and flying jump kicks at invisible female assailants,
the rest of the class watching in awe and slight confusion as AC
and Luke kept yelling ``No means no lady!'' and
``That's my penis! You leave him be woman!''



An hour later, as Luke was exiting the police car, he turned and
asked the officer, ``What's gonna happen to him? What
will you do with AC?''



``He's a dangerous man and we've been after him for a long
time. You should thank your lucky stars we caught him before he did
anything to you kid!'' shouted the policeman back at
Luke.



``Well at least he'll stay abstinent in prison!''
Luke said.



Their laughter echoed throughout the otherwise quiet
neighborhood.



Kids need to be respected too!

The End
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter[L.B.; V.H.E.]{L.B.; V.H.E. (the extended directors cut,
with deleted scenes)}
\by{Barometer}


Luke sat in the dimly lighted corner of an underused and
over-bright bar.

``Almost noon'' he thought to himself ``they should be fast asleep by
now.''

Shifting his considerable bulk, he managed to stand on his one good
leg, supporting himself with a hand on the table while his other
hand reached for his cane; an old waking cane bought form a dealer
in Soho many years past.

``God I've really let myself go since the accident'' he whispered to
no-one ``maybe I'll look into that Pilates shit{\ldots}or
something.''

He rolled his one good eye towards the pretty barmaid, a buxom
blonde who was eyeing him suspiciously. His meaty paw fished out a
couple of bills and dropped them unceremoniously onto the wet
tabletop, next to his three empty glasses.

``Hurr'' he spewed ``That'll teach her not to return my
flirtations{\ldots}uppity bitch.'' He gave her a smile that would wither
a rose, showing his rotten teeth that were green and yellow as
vomit.

Lurching forward like some hellish zombie, he headed for the
door.

Once outside, on the street, he shielded his eyes from the bright
sunshine ``Jesus I hate Kansas!'' he shouted, and a couple of elderly
people strolling by averted their gaze. He snarled at them, like
some wild animal that had been too long held in a cage and was only
now getting it's first taste of sweet freedom. ``fuckers'' he
mumbled.

Luke was an old man now, even though he was only forty. He had seen
so much; things that would make your skin crawl right off your
body. Things that could curdle milk by just being discussed. Luke
was a Vampire hunter, in the classical sense. Luke was very, very
good at his job.Checking the swordcane with a swift motion, and
satisfying himself that it was still good and sharp and made of the
finest ebony, he trundled down the street towards the old Biddick
Mansion looking like some undead pimp, rolling towards his best
girl.

``Those goddamn Vampires'll be vomiting blood from their throats,
ere this day is finished'' he vowed to heaven above ``Or my name's
not; Luke Bavarious, Vampire Hunter Extraordinaire!''

A boy of about 12 happened to be standing nearby, and when he heard
this his eyes sparkled with a devilish glee.

``Hey, mister{\ldots}you goin' up to the ol Biddick place?''

``So what if I am, you little shit?'' Luke gnashed his rotten
teeth

``Better not, I hear them folks is crazy{\ldots}and they got some kinda
dawg that wanders the grounds during the daytime. Never see 'em
lessen it's nighttime.''

Bavarious gave the tyke a once-over, and answered ``Izzat
right{\ldots}well, guess it's a good thing I have this Beretta then,
huh?'' as he spoke, Luke eased his brown courdory overcoat aside,
showing off a holstered Beretta 9mm, worn gunslinger style, with
the butt facing forward. ``I imagine THIS will take care of that old
DAWG'' he imitated the boys thick accent. He swooned a bit form the
heat, and sweating copiusly, continued his roll down the street.
Following at a short distance, the boy followed, shoeless and
dressed only in blue coveralls, worn form use and neglect. His bare
feet were covered in sores and wounds garnered from his time
playing in the dirt and rocks surrounding the little no-name town
they were in. His eyes were wide, and full of anticipation. He had
never before seen a man this grossly overweight, and was
intrigued.

After a few minutes, Luke felt as if the eyes of Satan himself were
upon him, so he swung around fiercely, whipping out his sidearm
``WHO DAT?!'' he cried his good eye searching and looking crazily
around until it alighted on the small figure in front of him.

The boy jumped from fright, and for a moment he felt as if his his
heart was going to burst from his chest, spewing crimson blood
across the dusty sidewalk ``IT'S JUST ME MISTER'' he shouted,
thinking the geezer must be hard of hearing if he had not noticed
him following by then ``I WANNA HELP, MISTER!''

``HELP?'' Shouted Luke, unconsciously imitating the boy and shouting
back;``I DON'T--'' he suddenly realised he was shouting, and dropped
his voice seeing that another couple across the street were
watching, intently`` I Don't need your help, kid{\ldots}now, buzz
off{\ldots}get lost{\ldots}scram. Comprende?''

The nameless waif wondered what the hell ``Comprende'' meant, but the
rest of the message was clear enough. ``Fine, you ol' bastard{\ldots}go
on, get yourself killed, see if I care!'' and with that, he ran
off.

It took Luke another ten minutes of lurching to gain the front gate
of the fenced in yard surrounding the mansion. ``Hmmmm, I don't SEE
any big dog'' He continued to roll his single, jaundiced eye back
and forth, looking in vain for any sign of a guard dog. Satisfied
that there was no sign of such a beast, he opened the gate and
hobbled up the front path to the stairs leading onto the porch. He
unintentionally farted. Once in front of the massive oak
double-doors, he swung his eye around for another look. Again,
there was nothing to challenge him, and as he considered knocking,
the doors parted of their own accord, affording him access to the
darkened foyer of the seemingly uninhabited mansion.

``CREEEEEEEEEAK'' went the doors, and when they were fully apart,
L.B. (As his one and only friend called him) took stock of the room
revealed before his eye.

It was a small room, comfortable and sparsly decorated. There were
a couple cameos on the wall, and a small desk, covered in what
looked to be unopened mail. L.B. knew there were Vampires in this
place, he could smell the stink of hell itself in this place and he
figured that like all of their ilk, they would be holed up in the
basement, sleeping their undead sleep in coffins filled with the
dirt of their original resting places.

He shifted his weight ``God-DAMN it I gotta lose some poundage'' he
cursed. After a cursory search of the downstairs, he found what
appeared to be a locked door to the basement, and he put his left
ear up to it and listened.

``Hmmmmm, sounds like a heart beating{\ldots}that's odd'' He tried the
door, but as he had surmised; it was locked!

Suddenly the door came crashing in on him, and the portal vomited
forth a huge, black dog{\ldots}some kind of mutant Great Dane he thought
fleetingly, as it quickly bit into his neck, tearing out his
windpipe and causing Luke to make the most horrid sounds even he,
in his long career of monster slaying, had ever heard.

Somehow, his fat right hand had reacted instinctively and the
Beretta was alive in his hand! Bullets tore through the monstrous
dogs body, knocking it backwards and slamming it against the wall.
As it writhed in its death throes, Luke attempted to staunch his
wound, but he knew it was too late his plump hands could find no
purchase, and the wound was surely a mortal one. His vision was
blurring to the point that he could barely make out the small shape
coming up from the basement.

``You shoulda listened to me, mister'' Said the boy in a quiet tone
``I woulda showed you the cellar door, and then ol Blackwood there
woulda never bit ya!''

``Gurgle..cough, spit'' was all Luke could get out, and as the life
ebbed from him, laying on that dirty linoleum kitchen floor, all he
could think was; ``Shit, why didn't I listen to that kid?'' The boy
crouched down in front of him, and just as his eye glazed over he
caught sight of a family portrait on the wall{\ldots}some cheesy mall
photobooth picture, enlarged, of the boy{\ldots}with the name ``Ben'' in
faux spraypaint letters and some other bling he couldn't quite make
out, before the Angel of Death took him.

``Ma and Pa are gonna be SO PISSED that you killed Blackwood{\ldots}''
said the boy to the corpse, glancing over to the lifeless dog
``Maybe ma will raise ya, so they can punish ya!'' again his eyes
filled with an evil gleam.

With that, he gave a shrill laugh, and ran as fast as he could back
down the stairs, anticipation bubbling forth like boiling coffee. 

 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{The Painter}
\by{Hamelin}





The boy who wanted to be a painter stared at his canvas. His canvas
was blank and it stared back at him. He had many other blank
canvasses and they also stared at him. All the big squares of white
were empty like his mind. He could think of nothing to paint onto
the canvas. It drove him crazy. He would never be popular if he had
nothing but blank canvasses! All of his friends told him that he
would never be a painter. He knew he would show them.



Since there were no ideas in his head the wannabe painter put on
his jacket and went to the art museum. There were a lot of
paintings at the art museum. The difference between these paintings
and his were that these paintings existed and his didn't.

``I wish I could paint paintings like these!'' The boy said out loud
to no one.

``Paintings like these huh?'' A tall shadow suddenly appeared over
the boy's head.

``Would you like to have paintings like these in this museum?'' The
shadow continued.

The boy spun around and standing there blocking light was a tall
gentleman. He was wearing a black overcoat over a black suit. The
gentleman smiled.

``Yes! Yes I would! Can you help?'' The desperate wanna be painter
clapped his hands together with joy.

From the gentleman's overcoat the gentleman grabbed a small wooden
box and handed it over. The box was made of dark wood and was very
smooth.

``Take this box home, what is in it will help you put everything
onto your canvas.''

``Really? Thank you sir!'' The boy jumped up and down
with joy.

The tall gentleman walked away without another word.



Before he knew it the boy was home again. He locked the door and
excitedly opened the box. Inside the box was a paintbrush. The boy
took the paintbrush into his hand and it gave him an idea. He
started to paint. He painted and painted. The sun went down while
he painted, the sun came up and he was still painting. He painted
on every single canvas in his home until he could paint no
more.



Days passed and no one heard anything from the painter. He didn't
show up to school. No one saw him at the park. After a week a group
of his friends broke into his house. They wanted to know if the boy
was ok. What they saw when they broke down the door were hundreds
of canvasses in an empty house. Paintings of furniture, paintings
of household objects, paintings of carpets, paintings of his
parents. Paintings of everything that would be in a house but none
of those things. As they dug through house they found the painter's
last painting sitting on his easel. It was a painting of the
painter himself.



Most of the paintings were put in the art museum. Everyone in the
town was impressed by the paintings. Everyone wanted to meet the
boy who painted all the amazing paintings. They would ask the
museum employees about him. They would only say that no one knew
where he was. They only found his paintings in his house. 

 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{What Went Wrong}
\by{gigz}



There is blood everywhere. My clothes are drenched with it, my
hands slippery. I look down at the dead body of Mrs. Trencher, her
throat still gurgling as she gasps for a final breath. The pencil
in my hand is a dark crimson. Slowly beads of her blood fall to the
already massive pool of blood on the floor. I look up and see that
everyone is staring in horror. It then occurs to me that I am
laughing harder than I ever have in my life.

Flash.

I wake up with a start, scared out of my mind. I am gripping my
pencil so hard I can hear the cheap wood start to splinter. It was
a dream. That's all it was. Hell of a dream though. My name
is Luke Bavarious. I am seventeen years old, and a senior in high
school. I am not shut-in, I am not excluded by my peers, and I am
not ridiculed and mocked. Frankly, people just like me and I get
along with everybody. I think something has happened to me. I just
have no idea what.

Mrs. Trencher is my English Literature professor. I have never
harbored any sort of ill-will towards her. Her tests can be a
bitch, but she is not a disagreeable person. Her classroom habits
don't evoke the anger of any student. She is all-around well
liked and respected. She gives us candy when we study for tests as
a class. She gives us candy when we aren't studying.

There is no reason that dream should have happened. I got plenty of
sleep last night. I wasn't up late, and I fell asleep right
away. I woke up on time, I had a bowl of cereal and a glass of
orange juice, and I made it to school without being rushed.

It's 11:32. Class is continuing as normal, and Mrs. Trencher
didn't notice me sleeping. Then again, she is the type of
professor that continues on with her lesson with, or without, your
participation. If you miss the material, it is your own fault. I
shake my head and continue copying her lecture notes into my
notebook. At this point, I have zoned out and am copying the notes
without paying any attention to what they are. I'll read them
over lunch, so I at least know what she is talking about.

``The elements of gothic fiction are easy to identify. In
almost all of them, a woman is trapped in a circumstance she cannot
escape from. This is usually a house. She has little time before
she suffers `a fate worse than death.' There is
something or someone keeping her in the house, by means of force or
obligation. Somewhere in the text, her savior will enter the house,
learn of the situation and save her from that Hellish
fate.''



Flash.



I look up from my notebook, and see the blonde pony-tail of the
classmate in front of me. With my face torn in a bloodthirsty rage,
I reach forward and grab a hold of it. I yank it back towards me,
her face now staring at the ceiling in pain and confusion. Without
a word, I lunge forward and plunge my pencil deep into her left
eye. She screams. I scream. She is screaming from the pain, I am
screaming because I am delighted. I twist the pencil deeper into
her eye-socket. She convulses, and I hold fast. I stand up, leaving
Jenny to writhe in her chair. I look at my hand. I slowly drag my
tongue across my middle finger, savoring the taste of her
blood.

I laugh harder than I have ever laughed in my life.



Flash.



I wake up on the floor next to my desk, tears stinging my eyes.
Everyone is crowded around me; Mrs. Trencher has sent Jenny off for
the nurse. Her eye is fine. I look up at the concerned faces
hovering over me.

``I'm fine; really{\ldots}I've just been feeling a
little ill. That's all.'' The words have to be choked
out through the tears. I try to stand, only to find a hand on my
shoulder, keeping me at my position on the ground.

``Francis, are you sure you're okay? You shouldn't
try to move. Jenny went to get the nurse, just sit tight.''
Mrs. Trencher's voice is thick with worry. She was one of the
few who cared about her students. For a split second, at the
mention of Jenny's name, I had the image of my pencil twisted
deep into her cornea. I almost throw-up.

``N-no, I'm okay, really{\ldots}''I pull myself to
my feet, using my desk as a crutch. I'm not really okay as I
say I am. I am unsure on my feet, and my vision is blurry.
Everything is swimming, but at least there isn't any blood. I
look around at my classmates; every one of them is staring at me
horrified. I'm not the first person to faint in class.
Melissa did two weeks ago in Biology. We were dissecting frogs, and
she is squeamish. As it turns out, I had screamed in absolute
terror, fallen out of my desk, and laid on the floor convulsing in
tears.

Jenny walks through the classroom door, a very scared looking Ms.
Surough, the school nurse, in tow. I look up at Jenny, tears still
fresh in my eyes. Ms. Surough sets an arm around my shoulders and
leads me out of the room. I numbly follow her direction towards the
nurse's office. Something is wrong with me, and I don't
know what.

Ms. Surough tells me to lie down on the couch in her office. I
happily oblige.

``So, what happened, Francis? Are you okay?'' Her voice
stays level, but you can tell she is concerned. You can see it in
her eyes. The only thing I can think of when I look at her is the
image of my brutally attacking Jenny. What the fuck is
happening?

``I'm fine, really. I just think I'm
overtired{\ldots}I didn't eat this morning. I think
that's it. Just overtired and a little stressed from work.
Really, I'm okay.'' I'm trying to convince myself
more so than Ms. Surough.

That's it, really. I'm just stressed from work. I guess
I did go to bed too late, and didn't eat enough for
breakfast. I'm okay. Really, I'm O.K.

I am O.K. 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{The Ninjas}
\by{KryonikMessiah}





Luke Bavarious was walking through a busy street, the landscape
riddled with urban decay. A building here, windows shattered, foul
smoke emitting from it's fetid chimney. A rusted out car
there, looking as if it had been sitting there for a good decade or
five. And all around was the constant buzz of midday traffic.
Bavarious, however, had other plans on his mind, as he walked into
a building. The building was tall{\ldots}.too tall.



`This building is tall{\ldots}.TOO tall', Bavarious
thought to himself, one hand clutched to a Smith and Wesson .44 in
his pants and the other holding a beer. Suddenly, out of the corner
of his eyes, Bavarious saw a flash! As he turned around to
investigate, a ninja appeared! ``Come on, you commie
scum!'' said Bavarious, as he fired at the ninja. But the
ninja cut the bullet in half! Bavarious jumped back and stared the
ninja straight in the face as they began circling each other in
this old, decrepit factory.



Bavarious narrowed his eyes. These ninjas were a tricky sort. Just
as he narrowed his eyes, a board broke over the back of his head.
Turning around, Luke Bavarious glared at another ninja in anger,
who was shivering with fear, a wet spot covering the crotch of his
costume as he held the piece of a broken board. Bavarious snatched
the pants right off the ninja, and turned around just in time as
the other ninja was leaping at him with a karate kick. Bavarious
wrapped the pants around his face, and he fell to the ground
choking, but then the other ninja made his move!



Bavarious found a knife in his shoulder, which began spraying green
vomit and blood all over the Ninja, and he pulled it out and turned
around, only to duck the broken board. He stabbed the knife into
the ninja's hand, nailing it to the ground, and picked up the
broken piece of board, driving it through the Ninja's head in
one fell swoop, and it exploded into a spray of brains and blood!
Luke Bavarious was on the lookout for more ninjas, when suddenly he
saw two children, a little boy and a little girl, standing maybe
ten feet away from him. A dead ninja was on the ground, and the two
kids were happily tearing his eyeballs out of his skull. Luke
Bavarious grimaced at this, when suddenly, he realized his gun was
missing just as another ninja burst through the wall.



That, however, was fine. The little girl picked up a pistol off the
ground, which went un-noticed by the ninja, who sworded out his
katana at great attack. Taking a chop at the little boy, he was
stopped in his tracks as Luke Bavarious tossed a vomit covered
pillow at him, which struck him in the face, and the little girl
accidentally pulled the trigger, shooting the ninja square between
his legs.



The next day, all ninjas fled the city. Their three brothers in
arms had fallen, and no ninja was mighty enough to stand up to Luke
Bavarious. Children the world over rejoiced.



The End
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{The School}
\by{IShallRiseAgain}


John Jones was your average every-day student at Livingston Middle
School. He was also very late. He hurried into his classroom for
the gifted students of which he was the smartest and coolest. He
hated his teacher, Miss Diabloclous, she was always giving them
homework and pop quizzes. ``Your late, John Jones! You get a
detention!'' shrieked Miss Diabloclous. ``Third one this
week'' thought John as he sat down with a smirk.



When school was over he headed over to Miss Diablocluos's
room. Another student, George Smith, was already there. ``You
boys have been behaving badly, and we can't have that can
we?'' proclaimed Miss Diabloclous. Suddenly her face started
stretching and contorting, and she grew ghastly fangs. George was
screaming and vomiting at the same time. Her jaws stretched, and
she bit off the head of George. His arteries started spewing
copious amounts of blood all over the place. Licking the blood off
her face, Miss Diablocluos shouted ``Your next!'' John
was ready though and pulled out his berretta. ``Pop Quiz time,
what happens when I shoot a bullet through your brain?'', he
exclaimed and then unleashed a hail of bullets into her head.



A police officer rushed in to see what was going on. Upon seeing
the grotesque body of Miss Diablocluos, he turned to John.
Expecting praise for killing the abomination of nature, he was
surprised when the officer unloaded a full clip into him with his
own berretta. Sighing the officer stated, ``Damn public
schools!''. 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{The Smile}
\by{Paracetamol Boy}



{\em Narrated by Luke Bavarius}



I woke to a darkened room. The streetlights outside my window cast
eerie shadows onto the floor. My mouth tasted carpet. My entire
body was immobilised with searing pain. I managed, with great
difficulty, to turn my swollen face toward my left. The living area
was littered with broken furniture.



So it had come to this. My wife had taken the kids and left me for
dead in what was once our family apartment in the central hub of
New York City. Blood seeped out the open wounds of my trunk and
saturated my dark blue clothing with an even darker sheen. There
the knife lay still, blade digging into the carpet in front of my
face. My own knife, that my own wife had turned on me.



I could hear the soft wails of the police sirens from the streets
below. That was the least of my worries. Despite my dizzied state,
my thoughts drifted to my lovely kids, Johnny and Sasha. I wondered
if I would see them again, if they were safe. The steadily
loudening sirens registered faintly in the back of my mind{\ldots}



Suddenly, I had a flash of mental clarity. It was the insight of a
dying man. I could not fight to live. I had lost too much blood,
the evidence of this mixing with the contents of my voided bladder
and slowly pooling around me like a seeping fountain of death. I
was a broken man. There was the chance an arterial bypass would
keep me alive, but even if I lived there was nothing to live for. I
didn't want to let anyone else think otherwise for me.



The knife was only inches from my face. My good arm, my left arm,
could move but only with mind-numbing pain. Slowly, agonizingly, I
brought the arm closer and closer toward the knife. I grasped its
handle and lifted it from the carpet. Each action was excruciating.
But pain is only temporary, for in death there is the ultimate
release. My thoughts drifted again to Johnny and Sasha, as I used
every ounce of my remaining strength to roll onto my back. I
positioned the knife in front of my chest and closed my
eyes{\ldots}



``Daddy.'' I recognised the voice and opened my eyes. In the dark, I
could see two small silhouettes sitting cross-legged beside
me.

``Johnny?''

The silhouette on the left nodded at me and smiled. The smile had
no lips, only teeth. I shook.

``Daddy, what are you doing?'' the shadow on the right enquired
meekly. Sasha?

``Daddy{\ldots}daddy's going away for a while,'' I whispered. The knife
was still in my hand, in front of my chest, frozen in place.

``Look{\ldots}daddy can't be with you guys for very long anymore. I won't
be alive for long{\ldots}I must go.''

``But you can't go, Daddy.'' The silhouette on the left was still
smiling, the white of his teeth glowing eerily in the darkness. ``If
you go{\ldots}I'll eat Sasha.'' The teeth spread to a grin.



``Johnny{\ldots}'' I gasped. As I looked on, Johnny's grin seemed to grow
wider and wider. The rows of teeth separated to form a hole between
them, and the hole widened to a yawning chasm of unfathomable
darkness. A different voice emanated from the hole. ``Daddy,'' it
drawled. ``If you go{\ldots}I'll eat Sasha.''



Still in immense pain, I balked, speechless, at the two shadows in
front of me, one sitting silently, the other leering at me, teeth
as far apart as a basketball, face torn apart by a chasm.

My vision blurred and it became increasingly difficult to breathe.
The knife dropped from my hand. Between ragged breaths, I gasped
weakly. ``Johnny{\ldots}you have your mother's smile.''



Then, as suddenly as they had appeared, the silhouettes were gone,
leaving only the space they had occupied.



I wept bitterly. 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{The Dock}
\by{ack!}



This lake seemed ordinary enough. The drive to this lake seemed
also ordinary enough, though the road was windy and tedious. The
unfortunate youngest child of the Bavarius family, Luke, endured
riding in the very back seat of the Buick station wagon. With each
twist on the windy road to the lake, Luke suppressed his twisting
stomachs urge to purge and vomit due to the car sickness his seat
on this ride caused him. ``I hate this drive and I told them
we shouldn't go this year. I hate being the youngest. I
always have to sit back here and get car sick, but that
doesn't matter to anyone, especially my dad who never listens
to me'', Luke thought while feeling the bile raise to his
throat. ``This ride better end soon'' he wished, but the
ride was really just beginning.



Upon reaching the cabin at the lake they drove to, Luke's
family unpacked for a week's vacation during the summer break
from school. Luke ran to catch up to his older siblings who were
faster than him as they each ran to claim their bunks in the cabin.
The ride left him more nauseas than ever and he had no hope of
getting a bunk in the main room. As usual, his bunk would be the
one in the back room at the back of the house. Once again he found
himself at the back of it all in the most uncomfortable place and
anything he said about it would go unnoticed and uncared about.
Needing fresh air to clear his head and most importantly, his
churning stomach of suppressed oral violence which was nearing
critical mass, Luke ventured outside, alone. He knew this trip
would be bad and the start was proving it.



Behind the cabin was a trail. Dreary and barren, this trail had
seen no visitors all year. Vines grew across its misshapen
cobblestones. He tried to skip as children do, but the uneven
stones reached up to trip him. Even the ground he walked on tried
to make his life miserable. Luke pressed on.



At the end of the trail, which led from the house to the lake, a
dock that rivaled an elderly woman's wrinkled and cracked
skin wound its way above the lake's depths. No one knew the
origins of the dock, but it had endured every frigid winter and
every scorching summer since its birth. Neglected and uncared
without a repairman's hands to repair it, the dock barely
held together with each board twisting and splintering.



Creeping like a silent cat on the hunt for its prey, Luke crept
onto the dock. Engulfed in the mist of the lake which surrounded
him like a funeral curtain, he made his way to the end where he sat
on the end of the dock and put his feet into the water. The
coolness felt good to him and made his stomach settle and no more
churn like a vile popcorn machine ready to spew forth a vomit of
undigested cheese and crackers that was his only meal for the
day.



Peering into the waters, Luke was surprised at the stillness and
the clearness of the lake. As the cruel world spun around him, he
could see through the very depths to the bottom which shimmered. He
could see his reflection coming in and out of shape. As he stared,
it seems time froze and the world stopped turning. His face became
without a shape and disappeared entirely. The faces of his siblings
floated by instead, pushing him out of the way. Then after that,
the faces of his parents, who never listened or cared for their
youngest child mocked him in his place.



Feeling colder than ever before, Luke felt a fiery fury explode in
his blood boiling heart. His mind spun deeper and darker than the
largest tornados in Kansas. His eyes bulged, each vain throbbing
and pumping their purple liquid to increase his vision. The real
picture began to form. This lake was a mirror, a portal, a crystal
ball to show his life, show his future.



The water's blue gave way to rust as each body flowed by
while blood drained from within. ``This is my life'',
Luke realized, ``this is my work. Whoever won't listen,
whoever won't get out of the way, this is where I must put
them, this is where they will pay''.



Snapping awake, Luke glared at his aged reflection in the window
lighted by the moonlight in the night sky. His thoughts settled as
his memory cleared and the pain rose burning and bright like the
devouring flares of the Sun.

``No!! This was not me!!``



''You did this, Horace Manslasher. You took my family that day while
I was at the dock and no one would join me. Now I'm coming
for you.'' 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{The Mansion of Horror}
\by{rinski}





Luke Bavarius stood before the haunted mansion of GhostRaven
Mansion. Black bats circled above, haloing the yellow moon. Luke
reached into his pocket. The cold steel of his Baretta reassured
him.



Legend had it the mansion contained untold riches. Luke liked the
sound of that.



Earlier that day a local kid had tried to stop Luke.

``Don't go to the haunted mansion. It's too
dangerous. It kills people. It never loses.''

``I think I can handle myself, kid.'' Luke said,
smirking.



THUD! Luke kicked the mansion's heavy wooden doors open. He
was in a large living room, 50 feet wide. All the furniture was
covered with ghostly white sheets and a chandelier hung ominously
overhead. There were lit torches on the walls.



Suddenly, all of the furniture exploded. Luke shielded his face
with his arms. Splinters tore at his leather jacket. The splinters
reformed into a giant wood golem. The golem surged to life.
It's eyes glowed with arcane evil.



Luke smirked.



He grabbed a torch from the wall. He threw it. The wooden giant
burst into blue flames. It burned as though it were made of tinder
and lighter fluid. The giant fell to its knees in wooden agony and
then unexploded back into furniture. The haunted white sheets flew
back to again cover the furniture.



``Getting the treasure from this haunted mansion will be a
breeze.'' Luke asserted, smirking.



The next room was a gigantic ball room with chandeliers and a
wooden floor. One wall was covered in old oil paintings. The other
wall was a gigantic window with giant red curtains. He could see
the garden. The hedges looked ominous. ``Probably plant
monsters.'' Luke murmured. He took a step into the room.
Suddenly, zombies were clawing their way out of the wooden floor.
Their empty eye sockets were slick with green rot. It glinted
sickly in the moon light. Luke's nostrils were attacked by
the zombie's horrid stench.



Then Luke was attacked by the zombies themselves.



Luke pulled out his Baretta. He emptied a few bullets into the
mushy heads of the advancing undead army. The bullet wounds oozed
blood and pus but the zombies just kept coming.



``They just keep coming!'' Luke joked, smirking.



He had to act fast. He ran around the zombies and their zombie
holes so he wouldn't trip. Zombies dove at him. Luke dodged
the deft attacks. Zombies dove left and right. Barely, Luke made it
to the other side of the room. As soon as he stepped out of the
room there was a flash. All the zombies disappeared and the floor
grew back. The room looked exactly as it did initially. Luke was
astonished. He stepped back into the room. Zombies poured from the
floor like oozing pus. Luke stepped back. The zombies disappeared.
Luke chuckled. He did this for one minute then moved to the next
room.



The next room was the kitchen. Immediately, all of the knives flew
out of the drawers. The knives hovered lazily in the air. Then the
knives flew at him. They cut through the air. Literally. Blood
droplets condensed out of the air. Luke dodged out of the way of
the knives attack. The knives flew past him into the meat locker,
killing the monster that was hiding inside. The knives made quick
work of the monster, then turned to attack Luke once again. Luke
simply shut the meat locker's door. The knives clattered
against the solid iron door. Luke smirked.



Luke entered the hallway out of the kitchen and was immediately
attacked by a giant spider monster. ``What the!'' Luke
uttered. But before he'd even finished uttering, the spider
lurched forward. It's poison jaws opened. They tried to clamp
closed on Luke's arm. Luke dodged backwards as the jaws
clamped shut. The jaws etched a wound in Luke's arm, but were
unable to deliver their venomous payload. In one fluid motion Luke
drew his Baretta. He shot two bullets into the spider's
bulging bug eyes. Two bullet casings clattered on the floor. The
wound belched forth a thick green blood. The blood hissed as it hit
the floor, dissolving it. The spider recoiled. Its insectoid brain
was riddled with pain and fear and two bullets. But it was too
late. Luke grabbed a sword from the wall. He brought it down on the
spider monster's neck. The head was cleanly sliced off of the
twitching body. The spider collapsed in a heap of bloody legs. The
wounds vomited their acidic syrup and the floor kept
dissolving.



``I'd better get out of here.'' Luke intoned,
smirking.



As Luke was escaping down the hall, he saw a room filled to the
brim with treasure. He stood there, mouth agape. He was going to be
rich. He ran into the room. Suddenly, the room shimmered and
disappeared. Luke fell into a void. He screamed. At the bottom of
the void, as far as the eye could see in every direction, was an
unspeakably horrid beast. It was made of mouths and eyestalks and
tentacles. It covered the entire floor in every direction.



Luke retched a scream. He tumbled towards the gaping maw of the
horrible creature. There was no escape. As Luke fell, a figure
appeared in front of him. It was the boy from before.



``The mansion never loses.'' The boy said, watching Luke
fall.



Luke choked on a sob. It was the last sound he ever made. As Luke
fell into the giant open mouth, the monster started biting him
lightning fast. The bites were so fast that the teeth broke the
sound barrier. Luke was dead before he knew it. He exploded into
bloody slices that fell down into the beast's stomach
acid.



``The mansion never loses.'' The boy repeated. He
smirked. Then he disappeared.


 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter[What Lurks Behind Our Eyes]{What Lurks Behind Our Eyes\\The Horrid Reflection Revisited}
\by{Syphilicious!}





Thursday night, and everything is quiet. Unusual for me, but in my
current settings it should be expected; instead of walking my beat
in the thug-infested alleys of our dear city, I am far out in the
country, at Old Woman McCannshire's place, engaged in a staring
contest with the termites that crawl in and out of the floor of her
porch as I wait for her to answer the door. The middle of nowhere
does not properly describe my location; I'd been driving so long
that I'm probably already halfway out. My name is Luke Bavarius,
and I'm a detective, but tonight I appear to be the guy that drives
around checking under old biddies' beds for monsters.



Even the pranks get men sent out these days. A prank is what I
would have thought this would be, if I didn't know the old woman
calling was too addled to even have a teenager's sense of humor.
McCannshire thinks her house is haunted by spirits, and wants one
of us ``wonderful young men you have working down there'' to come
check it out. I'm almost glad I forgot to bring my spare ammunition
for my Beretta out here; I've used that thing enough today
considering my nerves are just about as shot as those three bank
robbers, and if this goose chase got any more boring I'd probably
put it in my mouth and make brain gumbo.



The unlatching of bolts awakens me from my reverie, and my head
snaps back up into the proper position. ``You win this time,
termites,'' I mutter, wiping a thin string of drool from my chin.
Slowly, the door creaks open, and I am treated to the sight of Mrs.
McCannshire in a wispy white nightgown. Perhaps in the prime of her
youth this might have been something I could have tolerated or even
enjoyed, but the broad has long been in her more tender years of
age, her face has more wrinkles than the wandering Jew's underwear,
and her nightgown is greasy with the mysterious secretions of the
elderly. I try to focus on the mangy grey poodle she cradles in one
arm, a dirty little mutt that she probably pampers like nobody's
business. She really fits the picture of an old bag of bones, and
as soon as she opens her mouth I can tell how far gone she really
she is.



``Are you the detective Officer Dent sent over to help with the
spirits in my house?'' She speaks slowly and clearly, her eyes twin
moons of gawkish innocence. I don't know which kind of dementia
would be worse: the flavor Mrs. McCannshire possesses where one is
magically returned to the age of nine or the other one where you
think the walls are talking to you. Although, considering why I was
here, it's possible she suffered from the latter too.



``Uh{\ldots}yes. Yes, ma'am. Officer Dent is my, uh, superior.'' I stepped
past her and walked inside, trying to ignore the subdued growl the
mutt in her hands had started up upon sight of me. The place was
clean to a point; there were numerous tables and shelves bedecked
with pictures and family heirlooms, all meticulously dusted, but
the carpet was smeared with dirty pawprints and general dust and
filth, it's frayed and ragged material likely not blessed by the
gentle touch of a vaccuum cleaner for years. The carpet and walls
were an ugly matching beige and all the miscellaneous objects,
despite constant care, had lost their luster. The only sign of real
color came from the bathroom behind the door opposite the one I had
come in, wherein an even more hideous bright lime green covered the
small amount of wall I could see around the door.



I turned to face her, reaching into the folds of my trenchcoat and
drawing out a pack of cigarettes and my lighter. ``Now, what seems
to be the problem here?'' A lazy puff of smoke floated serenely past
my raised eyebrow from my now lit cigarette.



``Well,'' she said, setting the dog down onto the carpet where it did
an annoying little dance around our legs, barking and whining,
``I've been noticing things for several days now, but only this
morning did it get really bad. You see, every time I use the
bathroom I feel someone is watching me.''



``How can you tell?''



``Well, at first it was just an uneasy feeling. But then I started
hearing voices that would say things that I couldn't make out. Then
I started seeing faces out of the corner of my eye or in a
reflection. And this is happening quite often, mind you. It's
happened every time I go in there, and these days I tend to{\ldots}oh,
how should I say it{\ldots}do my business more often, mostly because
my--''



``I understand, I understand,'' I said hurriedly. ``Please,
continue.''



``Well, uh, this morning, I saw a face in the mirror behind me. And
I didn't just see it, either; it was directly behind me, an entire
person, and he didn't go away until I turned round.''



My eyebrow, which had just started to head home for the day, turned
right back around and marched up my forehead. This sounded
legitimately interesting. Whatever had actually happened, seeing a
person plain as day was a lot better than imaginary sounds or
tricks of light that even happened to people who weren't sitting
outside Death's doorstep in motorized wheelchairs. There was really
only one thing to do.



``Well, I guess you'll have to show me the bathroom then, Mrs.
McCannshire.''



``Right you are, dear.'' She seems to notice that my gaze had strayed
to the pictures on the small table next to the front door, and as
she hobbles past me towards the bathroom she begins to talk about
her dead husband. Half listening to her talk about the dangers of
late term prostate cancer and wincing at the intimate descriptions
she gives of the times she went with him for his checkups, I search
for an ashtray and find one nestled in between boxes of tissue and
stack of gardening books. I rub the flame out and leave the stub,
resolving not to smoke any more until I leave the house. The old
woman doesn't need all that smoke.



As I join her in the bathroom, I see that her poodle has the same
idea. It flies past me and sits whining at her feet until she
relents and picks it up again. I stand next to her and look around
the room. The mirror is old but clean, and the porcelain throne in
the corner is the same. I look into the sink, and from the short,
curly gray hairs lining the rim I deduce that she washes the dog in
it; either that or she's more up on the trends of women of today
than you'd think of a gal her age.



The horror of the thought further distracts me, and I begin to
develop that thousand yard stare as she tells me about the various
scary encounters she has experienced while voiding her bowels,
unnecessarily clueing me in on the second part in her stories too.
Technically I am looking at the hot water handle, but I am miles
away, back on a real cop's beat or in the arms of a good woman,
whichever one does a better job of distracting me from her current
tale of a mysterious voice whispering in what she thinks is Latin
and the effects of the creamed corn she had with lunch two days
ago. Suddenly I spy in the reflection from the mirror that the dog
has the same idea. The yappy little thing now sits silent and
unmoving in her arms, staring intently into the eyes of its
reflection.



At first I am grateful for the relative silence that its new object
of interest has provided, but after a minute it begins to make my
skin go all goosey. I've never seen a dog sit that still for
anything. I slowly move my hand in front of its face, nodding to
show Mrs. McCannshire I am listening at a pause in her latest story
involving the cupboard swinging open and almost hitting her in the
head and how the fright really helped ``loosen things, down there''.
I pass my hand back in forth in front of the dog's vision to no
effect. In a moment of clarity I drudge up the dog's name out of
its owner's ramblings.



``Jasper! Hey, Jasper!'' At once the dog is a flurry of motion,
leaping out of her hands and latching onto the watch around my
wrist with its teeth. I stumble backwards into the main room and
fall to the floor, frantically batting at the hideous ball of fur
as it growls like a recently castrated bear. Instinct takes over;
my mind recognizes when I am in a fight for my life even when the
opponent is a 15-pound owl pellet. Without thinking I wrap the palm
of the hand it grips around its head and bash it repeatedly against
the edge of a bookshelf next to me, then stagger to my feet and
swing it around the room, screaming to match its rabid cries. All
of a sudden it flies free with a high pitched yelp and collides
with the table on which the ashtray rested and the table and its
contents tumble to the ground.



I approach cautiously, waiting for my opponent to make some sign of
life. At once the small pile of picture frames and knicknacks
erupts as Jasper flies straight towards my face.



I have anticipated it; it passes fruitlessly over my head as I lean
backwards almost parallel to the floor, and I hear its frenzied
growling suddenly muffled. I push my spine back into place with one
hand and spin around only to see Jasper hanging from the ledge of a
desk, his jaw wrapped around it and his teeth grinding into it as
if he imagined it to be my arm. I act quickly, sparing no mercy.
With several steps I come upon the helpless creature and I lift a
booted foot to hover a foot away from the back of its skull.



``Chew on this, pooch.''



There is a loud, wet crack as its skull explodes like a balloon
filled with bones and blood. It's corpse falls silently to the
floor, followed by the lower half of his jaw and head. The top half
rests on top of the desk, firmly embedded into the wood. I curse
silently to myself and wipe my foot off on the carpet, leaving
behind a red smear flecked with hair and bits of bone.



All at once I come to my senses, and I turn to see Mrs. McCannshire
standing at the bathroom door. For a second we both stand staring
wordlessly at each other, then she utters a soft cry and flees back
into the bathroom. I hear a soft click as she locks the door behind
her.



I sigh and walk over, knocking on the door. ``Mrs. McCannshire, I'm
sorry about Jasper, okay? I shouldn't have{\ldots}done that, but he was,
I mean he was attacking me. There was nothing else I could
do.''



I continued to apologize while I listened to her sobs, trying to
look anywhere but back at that head, or that part of it, those
sightless eyes silently judging me. I've killed people before in my
line of work, and I see their faces when I close my eyes, but now
this mutt was getting to me more than any of them ever did. It was
an irritable little thing, but why did it up and attack me like
that? What did it see in that mirror?



I notice that the crying on the other side of the door has stopped,
and for a moment I feel relief. ``Mrs. McCannshire, if you can just
come out here we can talk about this. Again, I'm sorry about your
dog, but--''



I am interrupted by the click of the lock, and as the door slowly
comes ajar I help her open it. She stands there, head down, and she
looks so depressed that I can't help but resume my apologies. ``If
there's anything I can do to pay you back for what I did, you name
it. I really can't tell you how sorry I am, I'll get you a new dog,
whatever you want. I'm sure I{\ldots}could{\ldots}uh{\ldots}''



The look in her eyes when she raises her head is different than
what you'd think a hysterical old woman would have. They're more
intelligent than they were before, those eyes, and they seem to
possess more menace than I assume an old lady like that would be
able to muster.



One bony hand wraps around my throat with otherworldy strength,
choking off the rest of the sentence. She lifts me off my feet,
pulls back, and for a brief moment everything is serene.



Then I hit the wall. I slide down next to the open front door, and
after my eyes uncross and the black in front of my eyes goes away I
use the knob to pull myself up. I check for broken bones and don't
find good news in the ribs area, but other than that I am fine, if
bruised.



``Well, you've got a good arm, I have to give you that.'' I think
over my options, running my tongue over my teeth. I can't hurt her;
she's obviously just possessed by whateve possessed that dog in the
mirror. I have to get the spirit out of her, or incapacitate her,
but I don't know how to perform exorcisms and at her age a gust of
wind could kill her. Although if she's able to throw like that
maybe she's a lot stronger in other ways too. What if I tied her
up?



Something makes my train of thought come to a screeching halt. It
hasn't reached the station, it's gone straight off the tracks.
There were no survivors.



My brain is recieving messages my tongue shouldn't be sending. It's
not finding something that should be there. I grab a polished
silver cup off a table and flash my teeth at my reflection. There's
a black square where there should be a nice little white one.



I've lost a tooth.



This bitch is going to die.



I toss the cup and pull my piece, my finger already on the trigger.
Worse men talk about how their guns sing songs that only ever have
a few notes; that's played out, and anyway my Beretta never saw the
appeal in singing. It yells, and it only ever needs to raise its
voice once to win an argument with someone.



As I aim down the sights at the old girl now barrelling towards me
from accross the room with a horrifying screech, I recall something
about not having ammunition, and I anticipate the empty little
click. Cursing wildly, I hurl the gun at her, and it bounces off
her forehead ineffectively. I reach for the knife strapped to my
leg down at my ankle, but it is too late; she knocks it out of my
hand with one swift strike just as I am bringing it up and it
clatters against the wall. She slams me up against the same patch
of wall that I'd said hello to twenty seconds ago and holds me at
arm's length against the wall, my head more than two feet higher
than hers and my feet off the ground clattering against the wall.
Both hands are wrapped around my neck and I am rapidly losing
oxygen. You need to do something now, I think. Or you're done,
Luke. You're done.



Frantically my hands search for something, anything, to fight her
off with, finding nothing. I'm simply too far off the ground to
reach anything. I turn my head as much as her steel fingers allow,
and through my darkening vision I can barely see an umbrella stand
with one large black umbrella in it. In vain I stretch my left hand
towards the handle, my fingers finding air and then brushing the
handle. I strain as hard as I can as the pain advances and my sight
blackens, and suddenly I have a grip, I grasp it with the very tips
of my fingers, bring it up to my hand. She is laughing now,
piercing and mocking, delighting in her triumph. She doesn't keep
it up for long. I raise the umbrella high above my head then stab
it down into her open mouth and throat, pushing it into her
esophagus as she spits and gurgles, her hands clutching even
tighter at my neck. The handle is just past her teeth, my hand
gripping it firmly even as she bites into my wrist. I use my thumb
to find the release and push it up.



The umbrella is spring operated, the fabric edged with sharp metal.
Her neck evaporates in a cloud of blood and her head shoots up into
the hair, twirling in the air like a basketball and falling to the
ground with I and the rest of her body.



After a while, coughing and wheezing, I push her corpse off of me
and use the blood-soaked umbrella to stand up. As soon as I try to
walk towards the nearest chair, I stumble and trip over her head.
Standing up again, I look back down at the bloody mess on the
carpet and on me. I feel bile rising in my throat, and I turn to
run to the bathroom.



I push past the door and stagger to the sink, where I vomit noisily
and stand for a while, staring into this puddle of my own sick.
After what seems like forever I look up and into my reflection in
the mirror. I am hunched over the sink, my hands still grasping the
sides, my mouth hanging open and a thin trail of vomit hanging from
my lower lip. My eyes are wet with tears from the choking and the
vomiting.



Truly I am a pitiful sight. I give myself a weak smile, as if it
will cheer me up. I can't help but notice that something is off in
my reflection, but I can't think what. Then I tongue the gap where
my tooth used to be. My reflection does not. It still has the full
set.



The reflection straightens its back and wipes the vomit away, dries
its eyes with the sleeve of its shirt, and all I can do is stare in
dumb incomprehension. It is the same short black hair, the same
baby blue eyes, the same trenchcoat, the same man, yet it moves of
its own free will. It is me and yet it is not me.



It has an almost condecending look in its eyes as it reaches down
below the sink, to its ankle. It comes back up, my knife in its
hands, its knife, and I cannot move a muscle.



There is a flash of metal. He cuts through my throat like
cheesecake. The arterial spray gives a good portion of the shitty
green paint job a new coat from the opposite side of the color
wheel. There is a brief sense of motion, and I taste ceramic, my
body thudding to the bathroom floor. I move my mouth wordlessly as
red begins to creep along the grout in between the white tiles. I
hear a shuffle of fabic as my other self steps through the mirror
and lowers himself from the sink to the floor. He steps over my
body, taking care to not step in the advancing pool of blood.



My vision begins to cloud for the last time as he casts the knife
absentmindedly down in front me. It slides to a halt next to my
forehead. He begins to walk towards the front door, then stops,
turns around. He walks cooly back to me, crouches in front of me,
grimacing at the blood that is in danger of soiling the knee of his
pants. He looks me in the eyes, and begins to say something, then
thinks better of it. He does nothing for a second, simply watches
me dying, then reaches over, placing an index and middle finger on
my eyelids, and then he slides them shut.



``Good night, Luke.'' 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Nebulous Cupboard}
\by{Rummanging}





This city is my mistress; it is my wife; it is my secretary. All
that one can feel about a city, I feel it about this one, and more.
My best friend. I watch the public stream past my window, like a
river flowing past rocks, the rocks being my small 1 bedroom
apartment, which was by now dirty and neglected.



When I leave for my patrol, I do not check for my gun. It is as
much a part of me as my toenails are of me. I am forced to bring as
well, my cellular phone. In an ideal world, I could never talk to
anybody, and all would be good, but it is not so I must. As the
rickety door rickets behind me as I leave, I cycle though my
address book.



{\em ABE



CYNTHIA



MOM



PIZZA HUT



DIRECTORIES



INFO HOTLINE}



I ring for ``Abe'', as I am accustomed to doing. A gruff
New York accent shrieks in my ear.



``Bavarious! Thank Christ you rang, something's not
right, need your help immediately! It's coming for me Luke,
it's COMIII --- ``. I interrupt him. ``Abe,
what is this? Where are You?''. I can tell from the tone of
his voice something isn't right. ``Why didn't you
phone ME if something's wrong!'' I said.



``Dammit Bavarious, I ran out of credit, now get your ass over
here!''. I slapped the phone shut like the jaws of an
overprotective crocodile, and sprinted for Abe's hut. It
would be a long run from here, but I can tell he needed me.



His wooden hut was hidden deep in the forest, the outside seemed
normal, well as normal as it could seem, Abe being an
unconventional character to say the least. In one slick
simultaneuous motion, I kicked the door forcefully, sending the
thing flying inwards, and swept my Beretta up from my ankle
holster, a task made significantly more difficult from the kick.
The lights were all not on, leaving the place shrouded in darkness.
I heard a noise from a closet, and rushed to meet the source. The
thin door was locked, so I shot 6 holes in it, allowing me to see
inside. There was nothing inside but my bullets. I carried on with
my sweep.



The lounge: empty. The kitchen: empty. The bathroom: empty, save
for one poo in the bowl. The Stench was fresh, and strong. Whatever
left this vile gift was still here. I turn my head to check my
countenance in the mirror. I am entranced, until I hear a scream
from upstairs, distinctly Abe. I dart out of the room, and it
lumbers after me, slowly and scarily. I find Abe's shrouded
figure huddled in the corner of a blackened room. ``Abe, is
that you, have you been drinking again? You said you'd
quit{\ldots}'' I enquired. He looked me in the eye, and raised his
other hand. The light was so poor, I could not tell what was in it.
Until he flicked the lighter on. The small light illuminated his
tear soaked face, running down his cheeks, carving streams through
the dirt caked on his face. The dirty rag of material hanging from
the bottle neck became visible. ``I'm sorry
Bavarious'' he whimpered, and before I had the time to react,
to light the rag and tossed the bottle high in the air, shattering
on the ceiling above him. Shards of glass and licks of flame fell
down like hell fire onto his crumpled body. The house was wooden,
and the fire spread like wildfire. ``AAAAABBBBEEEEEEE'' I
cried, crying for the loss of a friend. I was forced to vacate the
house as fast as I could, the flames consuming the hut like the
mouth of Lucifer. Just as I was maybe 20 feet from the hut, it
exploded, sending shrapnel every which way. Something rock hard
struck my head, I hit the floor like a rock, out cold.



Some unknown time later, the black mist tentatively receded from my
vision, allowing me to see. It took moments before I recalled where
I was, and I quickly looked back behind me. Nought but a single
cupboard stood. I crawled to it, my legs too burned to work.
Scrambling through the debris, I reached the un-charred doors,
pock-marked by 6 familiar bullet holes. I tried the doors, now
inexplicably unlocked. As the doors swung open, the bloodied corpse
of a small child fell outwards onto me, still clutching his
teddy-bear. I held the child as he held the bear, desperate for
solace in our final moments. I jerked my head back and screamed to
the heavens, and the skies opened. 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{The Unexpected Shocking Surprise}
\by{antiloquax}





Luke Bavarious didn't know why he was called to an abandoned
church. But he had been called. By the man who had killed his
father. And it was the church where his father was murdered.



As he approached the crumbling iron gates of the church, a pale
white boy with black eyes from out of nowhere tugged at his tan
rain jacket.



``Do not go in there, mister,'' said the young boy.



``Nonsense!'' laughed Luke Bavarious haughtily.



``What is in there will destroy you!'' said the young
boy.



Luke Bavarious pulled out his Colt Python and pointed it at the
boys pale white head that was now sweaty with perspiration and
fear. ``I said nonsense,'' said Luke Bavarious.



But fear and bile clung to Luke's throat as he entered the
church. He plunged through the rusty wooden oak doors and reached
for his gun. Then he remembered he was already holding his gun.
Then he crept along the church.



As he tiptoed quietly through the rotting, crumbling church, he saw
that everything was black except for places that were illuminated
by the pale blue light of the moon. It was a full moon. A full moon
just like the night his father died.



At the altar of the church there was a shadow. Luke Bavarious
cocked his pistol and pointed it at the figure. The figure was tall
and intimidating and terrifying. But Luke Bavarious had seen worse
in his time.



``Stop! Show yourself!'' said Luke Bavarious. But the
shadowy figure did not show itself. It was still a shadow.



Blam. That was the sound of Luke Bavarious' gun as he shot
the shadow and killed it. Even in the moonlight, he could see the
glistening red blood shimmer in the moonlight as it spewed upward
and outward and everywhere else and covered the old and rotting
crucifix with gore and rust colored blood.



Luke Bavarious wanted to vomit, but not because of the head that
had exploded and the brains that were on his clothes, but because
he had finally killed the man who had killed his father. The man
who had killed his father had never been caught.



Until that night.



But suddenly the echoing sound of the gunshot was interrupted by
clapping. Clapping hands. Clapping hands of the man who had really
killed Luke Bavarious' father. Luke Bavarius had shot the
wrong man.



``Well done,'' said a voice that belonged to the rough
clapping hands. ``You have passed the test, Luke Bavarious. I
have been waiting for you.''



As Luke Bavarious began to feel the enormity of what he had just
done, the walls begin to spin. Madness and insanity tried to clasp
their hands on Luke's soul and he fell to his knees and
vomited sickly sweet bile and whiskey. His eyes blurred with rage
and tears. And the tears of rage too. And he didn't know what
he could do.



``Luke Bavarious, I killed your father!'' said a mocking
voice.



Blam.



This was not Luke Bavarious' gun. It was the gun of the man
he had just killed.



``What!?'' screamed the voice in the dark.



The man Luke Bavarious thought he had killed was still alive and
had been waiting to shoot the third man who was the man in the
dark.



``No!'' cried the voice in the dark. Luke could see now
and saw that it was the body of his old friend from school who had
grown up with him. Now he was dead. The man who had killed his
father was dead. And so was the other man, who had succumbed to his
injuries.



``Well,'' said Luke Bavarius to no one in particular,
``I should go home.''



As he left, Luke Bavarious again met the pale white boy. But now
the pale white boy was covered in urine and feces because he was
terrified. But what was this? He was also smiling. Smiling the
smiling smile of a child who had lost a battle but won a different
battle.



``Such nonsense you little children believe,'' laughed
Luke Bavarious mockingly.



And Luke left the church forever. But as he left he could feel
someone watching him. It was the eyes of a third man. The man who
had really killed his father. 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{The Beginning}
\by{benitocereno}


Minutes later, to the sound of gunshots, Rogue Davix awoke from his
horrible dream. The lumps, all of the lumps, were nothing more than
a satanic vision. The dreams were always the same. Aliens,
darkness, another world. If he didn't have amnesia maybe he
would have had some clue as to why he was haunted every night. But
it was a dark and dangerous secret, only willing to unlock itself
when he proved himself worthy.



He brushed it off because he was not sleeping well. There were
strange noises outside of his apartment at night. Evil noises.
Noises so black they could snuff out the light of decency in the
strongest of men. He complained several times but no one would take
care of it. That is why he decided to hire Luke Bavarious,
PI.



Rogue jumped out of bed and ran to his window. Luke Bavarious had
unloaded his Beretta into a stumbling ghoul, but the ghoul would
not stop. Luke struggled but was not able to stop the monsters
advances. They were coming towards Rogue's window!



{\em Crash!} The window splintered into a thousand fragments and
flew everywhere. The muscular fighters traded blows. Blood and vile
fluid splattered everywhere. After minutes of fighting it finally
seemed that Luke was the winner- the ghoul fell to the ground and
cocked his head to the side, his bile vomited across the floor.
Luke collapsed to the floor and began to sob, his face disfigured
by the shattered glass and powerful blows delivered by the now
fallen ghoul, the evil merchant of pain. Rogue ran over to help him
up.



``Luke, it's okay, you won.'' Rogue said, trying to
comfort him.

``No, it's just{\ldots} no, I'm one of
them!'' Luke screamed as he looked into a mirrored
fragment.

``No you're not, it's not what you have on the
outside that matters Luke; it's what's on the inside.
And we both know what you are. You're Luke
Bavarious.''

``You{\ldots} you're right. But we can't stay
here.'' He pulled himself together and stood up, triumphantly,
defying the gods trying to keep him down.



Luke was right, outside more sounds began to stir. The ghouls could
smell the evil cocktail of blood and vomit through the broken
window, and they were hungry. Luke handed Rogue his spare
Beretta.



``I hope you know how to use this thing,'' he snarled
through his clenched teeth. Rogue popped the safety off.



The ghouls poured in through the window. Luke kicked open the
apartment door and they both ran to the fire escape.
``We're gonna have to go up!'' Rogue said as he saw
the advancing horde of darkness.



``What's causing this!? Why is this happening?''
Rogue panicked as he fired into the ghouls while climbing the
stairs. His bullets landed in their limbs, barely slowing them
down.



``I don't know, but some people say it's the
Ozone! Without it, people are transforming into these{\ldots}
things! More and more lately! Either that or you just {\em really}
pissed someone off!'' Luke unloaded a clip into the closest
ghoul's skull; brains flew out of the back of its head like a
playdoh press. Images of the horrible dream flashed through
Rogue's head.



They circled the top of the fire escape and stepped onto the
rooftop. Once there Luke turned his trusted Beretta onto the fire
escape itself. {\em Bam, bam, bam,} he shot the retaining bolts
loose. With one swift kick he dislodged the staircase, sending it
and its undead inhabitants to the ground stories below. It was then
that they observed their situation.



The rooftops across the horizon, hundreds of them, were covered in
ghouls. It wouldn't be long until they found a way onto their
roof. The blood red sun rose in the distance, casting the shadows
of the ghouls across the rooftops, giving them an intangible bridge
to their goal. The flesh of Luke Bavarious and Rogue Davix.

Rogue admired his gun with a thousand yard stare.



``Two bullets left{\ldots} I guess we're lucky,'' Rogue
sighed.

``That's two more than we're going to need,''
Luke smirked.

``What do you mean?''

``You saved my life back there when I was ready to throw in
the towel. Now it's time I save yours. You don't remember a thing,
do you?`` Luke paused{\ldots} ''we're getting off of this
planet.'' Luke shot his Beretta into the air, but the bullet
stopped inches from where it left the barrel and resonated with a
metallic thud.



Luke's ship appeared from the naked air, the bullet held in
place by its force field, an impressive blue craft from the
stars.



``Is this{\ldots} the end of Earth?'' Rogue asked.

``No, no son. This is only the beginning.''



Basking in the clarity of the moment, the fog lifted, Rogue grabbed
onto his father's hand as he pulled him into the ship. Luke
hit the burners just as the monsters made their way onto the roof,
turning them into clouds of flying pink mist, their screams silent
against the engines' roar.



They had a lot of zombies to kill, it was time to get to work. 

 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Yellow Eyes}
\by{A Child's Letter}



``I'm not lying, Daddy!'' whimpered Kaitilin Axelplax, a six-year old
girl with an admittedly active imagination. ``I promise
you---{\em promise} you---that I saw it again! Saw
{\em them} again!''



Hubert Axelplax smiled his sick and twisted smile while
nonchalantly wiping the rust-colored tobacco drippings oozing down
his chin. Delicately, he set his Coors on ane Igloo cooler doubling
as an end table.



``Kai, what've I told you 'bout {\em lyin',} you little
{\em bitch!''} Without warning---though she knew it was
coming---Hubert, with speed belying his significantly
overweight frame, backhanded Kaitilin, sending her flying into the
wall. She collapsed in a heap, knocking over a floor lamp in the
process.



She stood, fought to find her balance, then, reeling from the blow,
vomited profusely all over the threadbare couch. Rust-colored blood
seeped wistfully from her gashed eyebrow.



``I {\em swear,} Daddy! I saw the thing with yellow eyes! It was in
the mirror!'' Again, she threw up. Hubert took three long strides
towards his daughter's trembling form and unbuckled his belt in one
fluid motion.



``You're {\em just} like her, you know that? Just like that
{\em whore} of a mother of yours!''



He raised the heavy leather strap above his wickedly grinning head
and---



* * *



Luke Bavarious' radio cackled to life: {\em All units, we've got a
10-34 near Forty-second and somewhere near Dyer. Possible 10-45;
10-52.}



Distractedly, Bavarious holstered his Beretta, taking a moment to
admire its clean lines, its intoxicating heaviness.



Suicide would have to wait.



He took one last, long drag on his cigarette, then tossed the
remainder out the window of his car. Baravious picked up his radio
and responded, ``Dispatch, this is Bavarious. I'm in the vinicity;
10-76. I'll check it out. Over.''



{\em 10-4, Bavarious. Out.}



For the first time in a long time, Bavarious smiled. Nothing like
an old fashioned assault with possibly fatalities to enliven the
night. He had to admit it: he liked this work.



Within minutes, Bavarious arrived at his destination. He parked in
an alley and realized he must be the first officer on the scene.
Everything seemed eerily quiet---especially for New York. Like
liquid, with practiced movement, he unholstered his sidearm and
kicked in the door.



The apartment building's lobby was empty. Bavarious involuntarily
shivered, then made his way up the first flight of stairs. As he
walked gingerly through the halls, when he was just outside of
apartment 209, he thought he heard muffled giggling. He realized it
was the only sound he'd heard since entering the structure.
Adopting a professional demeanor, he knocked.



No one answered.



He knocked again and followed with: ``Police! Open up!''



He thought he could faintly make out the sounds of a children's
program, probably coming from a television. The giggling subsided,
replaced with whispered commands. Something ponderous within the
apartment dragged---or was dragged---across the
floor.



Then, silence.



Bavarious was about to knock again when, suddenly, the door opened,
and a little girl---no more than six or seven, answered.



``Hello, Officer!'' she giggled. Bavarious surveyed her quizzically,
noted the poorly bandaged laceration above her eye, then looked
past her into the depths of the apartment's foyer. He thought he
glimpsed something twist subtly in the shadows. He blinked.



``Uh, good evening, Miss. Are your parents home?''



``I don't h---I mean, no, officer, they're not. My mama died
when I was little, and my daddy, he's{\ldots}um{\ldots}he's---''



She seemed to cock her head, as though hearing an inaudible
voice.



``---he's out buying more beer.'' She suppressed a laugh.



``Is he?'' mused Bavarious. ``Miss, what happened to your
forehead?''



Suddenly, the girl's demeanor changed, plunging from sunny to
downright icy.



``Officer, it's past my bedtime. I need to---you need to
leave.''



``Mi---''



``{\em Right} now.''



Though he couldn't explain it, Bavarious sensed an impossible
authority in her voice. An authority that hadn't been there moments
ago. He glanced at her again and thought for a moment her eyes were
glowing, yellow, bending his will to hers. He shook his head and
looked back into the apartment---anything to get away from that
jaundiced gaze! That's when he noticed what appeared to be a
rust-colored trail leading from an overturned Igloo cooler toward
another room in the apartment.



``I'm afraid I can't do that, Miss,'' he intoned as he brushed past
her, intently avoiding her piercing eyes.



Curiously, she said nothing.



His Beretta held out before him, a talisman against the darkness,
he followed the trail into a bathroom. There, in the tub and amid
the stink of beer and feces, lay the body of what Bavarious assumed
was the little girl's father. The man's belt was still clutched in
his hand.



The man's hand was resting on the countertop, a good seven or eight
feet away from the rest of him.



Unable to control his emotions, Bavarious puked all over the fetid
corpse, displacing several flies. As the chunks rolled slowly down
the disemboweled form, giggling erupted from behind him. He
jumped.



``I told you you needed to leave,'' breathed the little girl, whose
eyes had ceased glowing and now positively {\em surged} with
wicked yellow light. He noticed for the first time that her hands
were the color of rust.



Bewitched, Bavarious could do nothing as her arms shimmered and
became a writhing mass of tentacles. He told his brain to send an
impulse to his trigger finger, but it wouldn't obey him. It had a
new master now.



{\em Good night, Officer Bavarious.} projected the little
gi---



{\em Her name is Kaitilin. How do I know that? How d---}



{\em I---yes, good night, Kaitilin. I'll{\ldots}be{\ldots}going{\ldots}now.
If{\ldots}if that's all right{\ldots}}



* * *



Luke Bavarious awoke outside of an apartment building somewhere
near Forty-second Street and Dyer Avenue, sprawled across the hood
of his car. The sun had just begun to rise above the tangled mass
of skyscrapers all around him. His mouth tasted like vinegar, and
he smelled like a slaughterhouse.



``What am I doing here,'' he wondered aloud.



The sun thrust a glinting beam of radiance through a break in the
buildings; it fell with purpose on a second-story window of the
apartments in front him. Following its path, he thought for a
moment he saw two points of yellow light blink, then vanish.



``Weird,'' he muttered. 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{The Last Night of Luke Bavarious}
\by{Decatur Fist}







Check the machine. No missed calls. No word from Davix.
Nothing.



With a sigh that poured from his mouth with a torrent of non-amused
frustration

Luke Bavarious pulled a small slip of paper from his pocket and
wadded it up and tossed it into the waste receptacle with the
precision of a black man that shoots basketball in a Lakers jersey.
As a fan of black culture Bavarious was known for his hoop skills.
They had even saved his life once and then again on another
separate occasion.



Davix was dead, and that was that. There was no sugar coating any
longer. It must have been brutal. When you're surrounded by a
cacophony of death you think about death a lot. Davix had even said
during a haunting and stormy night that he hoped that he would go
in his sleep.



It didn't happen like that. Luke Bavarious could envision in
his head a vision of Davix dying by the hands of that beast.
Bavarious could see the hand of the beast smashing into
Davix' face terribly powerful. It was a bodacious site. One
to be remembered for an eternity of doomsdays.



You need a drink. Clear your mind. Stay on guard.



Something strange had happened earlier today, it was why Luke
Bavarious now had the small piece of paper that he had just wadded
up and thrown away just moments ago before the ticking sounds of
the clock hauntingly swept its hand across the face of the clock
bringing time forward to this moment.



The boy had told him that Davix would die, and Bavarious too if he
didn't listen. Bavarious had laughed a laugh and chortled a
chuckle at the thought of him and Davix going out on the same day.
However, it looked like the boy was batting half of a perfect
batting average now.



He had shown up on Market Street and followed him all the way down
Pine, up West, and finally had the courage to talk to him once
stopping on Center. He was wearing a grey hoodie and seemed to be
no more than 13. He had dark stormy and haunting eyes, and you
could tell he wanted to be taken seriously.



He had a pension for horror and a knack for stories. He claimed to
be the creator and destructor. His name was Biddick. He was to be
taken seriously by all accounts.



Bavarious had told the boy that he didn't have time for him,
and that he needed to leave, but there was a thirst that needed to
be quenched that longed for the answer of why the boy would show up
after following him and then having the balls that were big enough
to make him say such nonsense to him.



The boy told Bavarious he would be sorry. Bavarious ignored him and
ordered a tuna on wheat.





Alone.



The sounds came slowly at first, but then with a quickening of
rapid speed. Claws clawing razor sharp against banana peel soft
skin. There was a sound of terrible nursing. Like wounds being
cauterized by the flame of a thousand dying invalids.



They were here for Bavarious. He laughed a strange giggling laugh
that sounded like a maniac pumping gas into a Ford Fairlane. He
opened the window and let them vomit into the window and take
him.



They took him with a great brutality. 

 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Mac}
\by{Brolita}



This morning, I woke up to find myself dead.



I don't know how it happened, or why. That's why I'm here. Easy
G's, a dive on the bad side of town. Mac, the guy who runs the
place, is a good friend of mine. Always around to lend an ear.
Tonight, I hope he has two.



My name is Luke. Luke ``Lucky'' Bavarious. I'm a private dick. At
least, I was, before I died. My dad was a cop. A cop that didn't
play by the rules. That's how he died. He broke the rules. Then the
rules broke him.



My dad died when I was 13. He didn't listen to me. I knew the
streets. He thought, because he was old, because he was
experienced, that he knew more about the dark realities of the city
than I did. I tried to warn him. He didn't listen to me.



It was a night just like tonight. Except both of us were still
alive. At least, for now. My dad was called in to investigate a
shooting. Prescott Avenue. The worst street in the worst
neighborhood in the worst city. I remember him drinking when he got
the call. He didn't always drink. Only when he {\em knew}. When he
knew something was going down. When he knew he would be cheating
Death. When he knew that one drink may be his last. He {\em knew}.
And {\em I knew}.



I've blamed myself for my father's death. I've blamed him. I've
blamed the alcohol. I've blamed it all. But the one thing I can't
blame is the person who killed him. I can't do that, because I
don't know who it is. I've spent my life searching for him. I
became a cop, because I thought I could find him. I couldn't. I was
fired for using excessive force on a drunk one day. Served him
right, the swine.



Tonight, maybe, I'll find who I'm looking for.



I breeze into the bar like a shadow. That's pretty much all I am
now. A shadow. A shadow to my father, who is now a shadow himself.
The world is full of shadows, shadows that we don't see until it's
too late. I've been through a lot of crap in my time, seen a lot of
things a sane man would be better off without seeing. Luckily for
me, I'm not a sane man. I guess that's why they call me
Lucky.



Mac's behind the bar. I slam some money down. ``I'll need a strong
one tonight, Mac. Gimme a Screwdriver.'' I wince at the sound of the
word. I killed a man once. Stabbed him through the head with a
screwdriver. Phillips head. Poor Phillip.



Mac pours me a stiff one. ``Rough day?'' He asks. ``I'm just getting
started,'' I say, lighting up a cigarette. Red Apples. Menthol. It
stings like fibreglass, and I almost want to vomit. I take a drink
to cool down my throat. ``Mac,'' I say, my hands shaking, ``I'm
dead.''



Mac looks up at me. To my astonishment, he's not surprised. He
knows.



``I know,'' he says. ``I'm the one that killed you.''



My shaking hands curl into shaking fists. Mac. My friend. My
brother. My killer. I lunge across the bar. ``You ROTTEN MURDERER!''
I scream at him. I can't think. I can't breathe. My cigarette falls
out of my mouth.



I grab his neck. From my holster, I pull my baretta.



I don't even hear him laughing as I pull the trigger. 

 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{The Horrid in the Arcade}
\by{nmg}



Bavarius woke with a startle. He had a hangover from the 3 Coors
beers he drank last night to help him relax and his head was
horrific with vomit and pain. Suddenly he remembered what happened
yesterday. It was his worse case yet ever.



It all started yesterday when he got a telephone call from the
Chief. ``Bavarius I need you to go down to the arcade to investigate
a noise complaint'' he said. ``OK'' said Bavarius.



His head and heart pounding like a drill, Bavarius loaded a clip
into his Barretta and fingered the safety. Nervously he went to his
Chevy Camero and hit the ignition. He punched the gas then realized
his car needed more gas. ``That's fine'' he thought. I have enough
gas to make it to the arcade.



He peeled out of his driveway and sped down the street doing 55
miles per hour. Suddenly he arrived at the arcade. He opened the
door and went inside expecting what he did not find. Instead he
found what he did not expect to find. What he found was a horrific
site.



Blood and vomit and tears streaked the walls and the Space
Invaders. There were kids bodies laying everywhere, torn apart and
still bleeding blood. ``Who could do this.'' thought Bavarius. ``I am
going to catch who did this and find out how he could do this.'' So
he looked around.



Suddenly he heard a movement. It sounded like wet vomit scraping on
sand paper. In a flash he drew his Baratta and loaded a clip. Then
he spun around to face the noise. ``Whoever you are, I have a Bereta
and know how to use it, scum.'' he said.



Suddenly he saw movement. A man or what was once a man or woman
came dashing out from behind Missile Command. ``OUT.. OF..
CREDITS..!!!'' it screeched in a slow southern drawl. ``No monster,
you're out of life'' said Bavarius as he squeezed the trigger
rapidly and deliberately.



One shot to the head, two in each hand, and one in the heart for
good measure. Also he shot the thing in the legs and nose.



The woman howled and fell back then started licking up blood and
vomit. It seemed to give him strength. So Bavarius emptied the rest
of his clip into the thing's head then reloaded. He blew out her
brains so bad that it exploded in a cloud of vomit and regret.
She's not coming back from that, he thought to himself. Frozen with
guilt, the man slowly began to run.



Then he called the Chief and said ``cased closed.'' as he walked out
to his Camarro. He tried to start it but it was out of gas so he
walked to the gas station and bought some gas and put it in a gas
can then walked back and filled up his car with gas. 

 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Invisible Monsters}
\by{Ghost Hat}




Nobody could see! Nobody could see! It was a nightmare. Abby ran
for her life, as hard as she possibly could. What else was there to
do when a monster was chasing you? Her lungs gasped for air already
and her limps burned with exhaustion, but that thing didn't even
breath hard.



It wasn't the monster chasing her that frightened her the most
though. It was the fact that she was the only one who could see
it.



Lurking about the corners. Hiding in the shadows. She thought it
was her imagination. She thought she had been going insane. They
said you showed the first signs of schizophrenia when you became a
teenager. But then, it must have slipped up, for she had seen it
squarely, with both eyes. What's more, it knew.



And then it gave chase.



Down the sidewalks, across the streets despite the busy roads. She
must have been nearly killed five times by squealing cars. She
barely kept herself from tripping several times down the steep
hills. And still it chased her, it seemed to like watching her run.
Enjoying itself perhaps. It loped in plain sight.



But only she saw! Only Abby saw the monster. Everybody else saw a
crazed girl running through the streets, no thought for her own or
others' safety. How did Abby know this? Nobody had believed her
when she said she was seeing things. Nobody screamed and ran
despite the fact a monster ran loose upon the same streets. Maybe
she {\em was} crazy, but she wasn't going to stop long enough to
find out.



How she had wished she had paid better attention! Though even if
she had spotted the creature earlier she would not have known how
to defend herself against it. It had been following her for weeks
though. Weeks in which some shadowy thing had been watching her,
plotting against her{\ldots}



No time! Abby ran.



``You stupid kid!'' some guy screamed as Abby swerved past him. The
streets were full of people, making it hard for Abby to run at full
speed. She had to slow to dive and jump between and around them.
And there were carts everywhere. The beast! The beast was catching
up! Run! Run!



An alleyway. Not a place she would normally go. That's wear drug
addicts and homeless people hung out, but it meant there would be
no people. No people meant no obstacles. Abby ra! She ran down the
alleyway.



It took a moment for Abby to realize her mistakes. People might
have noticed if the monster had jumped her in front of them. Even
if they couldn't see it, they would see that something wrong with
her. With no people around, it could kill her in privacy. That was
her first mistake. The other was that this alley ended with a brick
wall. 10 feet high.



{\em Oh no,} Abby thought, gasping for breath so hard she couldn't
speak. She had enough to scream however. She felt the wind rushing
by as the monster swooped in on wings of black. So close now that
she could see purple in those leathery wings. So close she could
see its gleaming yellow eyes. No pupils. Just shimmering metallic
yellow.



It swooped in and landed with a great gust of wind on the cement
ground. It stood on two legs, like a man. But it was no man. Abby
was suddenly trapped between the brick wall and it. And then it
opened its mouth wide and inside it were hundreds of sharp, silver
teeth. It hissed and Abby screamed as it bent forth to devour
her.



Another rush of air, but from behind the creature. A sudden blur
and then the creature was on the ground, wings spread flat. It
screamed a terrible scream and Abby covered her ears in terror.
Animal instincts took over and she hid behind a dumpster, eyes
squeezed shut, hands clamped over ears. She would never leave this
place. She would stay, stay and hide forever.



She did not see what had overcome the creature. All a blur. She did
not see the man who had saved her until he tapped her on the
shoulder, and then pulled her out much to her horror. It had to be
that creature! That awful creature!



``Agggh!'' she screamed as loudly as she could. Abby writhed and
tried to break free, still blind. Still crazy. Still insane with
fear.



``Stop crying. You've been saved,'' said a voice. Abby
looked up, blinking heavy tears from her eyes, and found a man. An
ordinary man.



Abby was silent, just staring in disbelief. Just a man. And behind
him. Nothing. The creature was suddenly gone. As if it had never
been there in the first place. She panted, sweating, hair a mess,
skin as white as snow. Just a man. And yet. ''You saw it? You saw
it?" she hissed, horrified for what the answer could be.



``Of course I did,'' the man said in a voice as soothing
as butter. ``And it's gone now. It will never bother you
again.''



Abby gave a choke of laughter and could not help but hug the man,
her entire body trembling. The ordinary man reciprocated with one
arm, his other sliding towards his back pocket. He thought, in a
distant sort of way, that the child in his arms was warm. But the
blood from her throat would be warmer. 

 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Bavarious Reasons}
\by{SummerGlaucoma}





I am stuck here, in this place of must and yellowed paper. The
place holds over my face a page, a urine-stained billow. My mouth,
a tool of evil and destruction, vomits bile, blood and
giggles.



{\em Who am I?} I thought, trying to hug the thought as hard as
humanly possible.



{\em Who am I? Who amI? whoami?whoamiwhoam--}





My name is Luke Bavarious. I'm a cop. I like the work.



I have a barrette. I keep it with me in case I've got to put up my
1990s supercop hockey mullet and think real hard.



I'm thinking now. What kind of name is Bavarious? It is the steam,
the steam from the Fatherland's best beer region? And why Luke?
Cool hands, warm heart? Or do I walk in the sky, over to
GRAN-ND-PA's arms, my left leg caught, with my seven-league boots,
in The Barn?



I know we all in this book live in a library basement. Our book is
next to some new kind of backwards comic book from Japan.



When it rains, The Artists' ink runs and lets us visit, and let me
tell you, it's nice to get a furlough -- Okay, fine, that kid who
made us didn't specify breaks. I'm AWOL most of the time. So sue
me! -- in the more -- ahem! -- adult, of those comics. That kid
didn't make any single dames.



Bavarious. Hmf. I don't even know what continent my people live on.
Maybe it's a cover name.



Bavarious.



Bavarious.



Bavarious.



An idea sneaks into my head, slashing its way in through my waxy
ear canal.



I am emitting an evil smirk.



I need to borrow something from Ken-wa over there in Samurai
Land.



{\bf NEXT WEEK, IRAQ, BEN'S P.O.V.}



My name is Ben Biddick. I'm a soldier. Do I like my work? Well,
that depends. I don't like gritty food. I don't like being away
from my parents (they're great -- I'll have to tell you some time
when we get a weekend pass about the time I wrote a book of crappy,
embarrassing stories, and they got it published with this vanity
press! Nope. No shit. None here, anyway). But I am proud of what
I'm doing here, for the Iraqi people, and for the freedoms I
love.



Besides, you guys are the tightest buds I could ever wish for. Shut
up, Johnston! Yeah, well, you too!



Oh, rad! Mail call!



It's a package from that Internet forum that told me about how they
loved my stories. Yeah! I'll show you guys later. It's rad.



Weird. Oh, well. I guess the only copy that Abe dude could find was
this soggy thing. I guess it'll dry out pretty fast here once I
take off the bubble wrap.



Why do I feel so -- uneasy?



What was that flicker -- did Abe put some confetti in with this?
Awesome!



{\em But confetti doesn't wear its hair in a blond, barretted
ponytail.



Good Christ--} (he thought)



No, Johnston! Only {\em your} mom sends nudes. My mom is a
saint.



{\em Yeah? Well, you'd look worried, too. If--}



[a small figure darts towards me, swinging the hundred-times-folded
Kyoto steel with maniacal glee]



Luke Bavarious?



``Why yes{\ldots}! ''



But, Luke: How-- Why do you even {\em own} a katana?



``For Bavarious Reasons!''



Look there! {\em I am pointing to the page. A -- How did a he-she
from Japan get there? A he-she with a Samurai House's
medallion--?!}



Luke says some magic words in some prehistoric Asian language,
pointing the sword at me.



I started to shrink and grow more illustrationlike.



I am drawn to the page, as much as I was when I was a kid. But for
not the same reasons. The child walks towards the page. I am
little. I am dressed in the same faux-b-baller shit I dressed in as
a little kid. I am a G.I. Joe-sized High-Topped Son of a
Bitch.



Bavarious is full size now and god is he ugly as a real human. ``I'm
Luke Bavarious,'' he says to my buddies, ``and I'm a cop. Now, let's
see about this noise disturbance -- Where's this horrid Al Q.
Aida?''



Amid the predictable laughter, I hear the Simoom begin to blow. The
book slams shut.



My name is Ben Biddick. I'm a cop. I like my work.





Suddenly, I was sobbing. 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter[Dream Hyena]{Dream Hyena: A Bavarius Tale}
\by{LesterGroans}





Luke Bavarius checked his watch and rolled his eyes as the radio
vomited some Stones track that the kids listened to these days. He
tapped his foot mindlessly on the gas pedal and honked his horn
again.



``Dammit, woman,'' he mumbled to himself. His ex-wife had promised to
have their kid waiting for them when he got there. It would be the
first time he'd see the little brat in weeks. It was hard being a
cop, even harder having a home life when you were one.



Bavarius grunted like an ape and got out of his Camaro, rounding it
to the suburban sidewalk and up the stone walkway to Carrie
Bavarius's bungalow. He knocked on the door.



``Let's go, champ. Kids who are late don't get ice cream,'' Bavarius
called through the door. Still no answer.



A thick, meaty thumping came from inside, like a pudding-stuffed
side of beef was being smacked against a milk bag. Bavarius
furrowed his expansive brow and rubbed his chin, stubbled and
gritty like the streets he swore to protect.



He kicked the door in, it splintered against the far wall. His
Baretta was out faster than a synapse as he lunged into the
foyer.



There were smears of body ketchup leading down the hall. Bavarius's
eyes narrowed, he started to sweat.



``Carrie?! Lukie Junior?!'' He called out, steadying his firing hand
as he moved down the hall. The walls were streaked with scratch
marks. There were gouges in the wall up to an inch deep -- two
inches in some places. Three inches in others.



As he passed a four inch deep scratch mark he rounded the corner
and there, at the end of the hall, was a thing that could only be
described as a dream hyena. It was on two legs, a scorpion tail
jutting from its distended, mangy belly, wiggling towards Bavarius.
Its jaw hung loose, almost broken, vomiting sickly metal smelling
saliva onto the floor, ruining the hardwood. Its eyes were gone, in
their place were throbbing boils of pus, what looked like a
cockroach had been stuck in the festering eye-wound, its leg
twitching out the side of it.



The sharp scorpion tail had made fast work of Carrie, dicing her
body into so many pieces. Her entrails hung from sconces, the dream
hyena was wearing her hands on the top of its heads like the horns
of Pan.



Bavarius gulped, his adam's apple bobbing. He took a stance and
made sure his voice was steady before calling out, ``You're under
arrest!''



The dream hyena didn't respond. It lurched forward, its legs moving
awkwardly, its clawed hands dicking gouges into the wall, the pads
of its feet squeaking on the glugging, bubbling blood bile that
spewed from Carrie's severed throat. It was already scabbing in
gobs around her neck{\ldots} not the kind of necklace she used to pester
Luke for, that's for sure.



``Where's Lukie?'' Bavarius asked, holding his ground as the thing
lurched again, the umbilical scorpion tail wiggling hypnotically.
Bavarius smirked, ``You don't scare me{\ldots} bringing in punks like you
is my Baretta and butta!''



He opened fire, ripping apart the dream hyena's belly. It hissed as
it vomited disgusting, rotten entrails and a thick gaseous smell
like someone had run over a dead raccoon in a lawnmower.



The dream hyena fell to the floor and darkness flooded over
Bavarius. He blinked, stepping back, dropping his gun. What was
going on?



When he opened his eyes he looked at the floor in front of him.
Little Lukie Bavarius lay holding in his guts as they tried to
snake out of his grasp like loose Swedish sausages.



Bavarius's neck was thick with corded veins, his eyes so wide they
almost blew out of their sockets. He dropped down beside Lukie,
cradling him in his arms, hearing the plopping splash of more guts
tumbling from Lukie's belly.



``Daddy?'' Lukie looked up, his pale face round and innocent. He
looked so wise now. ``I just wanted to see you more, daddy? Y-You
always said you were too busy finding the bad men{\ldots} I-I thought
maybe you'd come if you had one to find here{\ldots}''



Lukie's lower half tore off like wet tissue as Bavarius tried to
pick him up. He held his son's top half like a broken pinata and
sobbed into his son's collar.



This was a helluva thing. 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter[The One Act Remaining]{The One Act Remaining To Me In This World}
\by{murdered by owls}





I'm not sure how it is possible for me to sit here, outwardly
so calm, while a tornado is whipping around inside my brain,
flinging emotions about like bits of debris left over from an
explosion in a sex shop. The definition of surreal: digging dildo
shards out of your ears{\ldots} if only metaphorically.



I glance out the window of the break room of the factory where I
work, and notice that the moon is full, gravid with cold
purple-white light. Why does it seem to be calling me? I want to
understand what it is trying to tell me. I know it's telling
me something, if only I could hear it through the endless,
soundless muttering of a million dying souls. They're everywhere.
Their sighs fill my head like a swarm of crocheted bees.



My coffee is very hot, and tastes of metal, or perhaps the tears of
molested children. I'm not sure why that comes to mind. How
would I know what molested child tears taste like? A trivial
mystery to which I am unlikely ever to find an answer{\ldots}



There is a part of me, deep inside, that is like a tiger with
foot-long blades for claws, and it wants to attack and rip and
destroy this violent feeling of whirligig that raves and rages and
rapes the rest of my brain like a lunatic conquistador. But the
tiger cannot fight an opponent so vague and ephemeral. It's
like trying to grapple with a fart, or wage war against a cloud of
gnats armed only with a Beretta or a bag of tulips.



A solemn fog has grown out of the river just to the north of us,
and it is as though someone has thrown a gray blanket across the
fields surrounding the factory. The moon looks down on all this,
benign, but also wild and terrible, the face of a pagan goddess
with a cold and clear eye. This is somehow comforting.



Two of my fellow night shift machine operators walk in the room,
get their coffee and candy bars, and sit down at the other side of
the room, not speaking a word. We ignore each other testily. The
silence between us is a sacred bond, unrelenting, immutable. It is
more than just mute testimony to our deep and abiding wariness, it
is a black and shapeless ocean, seeming to drown the words we do
not speak.



It is all right; I have grown indifferent.



As I pick up the sports page from the table, I feel a sudden surge
of terror, coming from nowhere and everywhere, as if I had been
shaving in front of the bathroom mirror and seen a reflection of
the tiger streaking towards the back of my neck with deadly, fluid
speed, claws outstretched to rend and destroy.



Outside, I show nothing.



I sip my coffee.



My cock is hard as steel.



Ten minutes later, I am once again at the controls of my machine.
It vomits polyurethane airmail envelopes in an endless stream. The
stink of burning hot melt has settled into my clothing, and can be
sensed faintly anywhere I go, like the ghost of cheap aftershave on
a shirt the day after a date. Here, in the factory, the odor is
strong and almost palpable, with a kind of chewy, yellow
resonance.



My bagger stands at the far end of the monolithic, hissing metal
apparition and collects the envelopes as they are expectorated by
the machine onto a small table. He executes a kind of dance, the
steps repeating every thirty seconds or so. He watches the counter
over the cutter bar, and when it reaches 100, he snatches the pile
out from under the next envelope with greedy, clutching fingers and
slams it into the cardboard flat he has prepared. He folds the top
over, slaps a strip of tape over the seam, and stamps the side with
the date and shift, all in one long, fluid movement. He bends and
twirls, deftly slipping the flat into a bigger box on a pallet.
Then he returns to the table at the end of the machine and prepares
another flat with economical, practiced motions, and places it
before him, ready to enshroud the next stack of the machine's
ejecta. Waiting the next few seconds for the next stack to be
ready, he waits completely motionless, head down, his hands spread
out before him on the table.



I watch him carefully out of the corner of my eye as I run my
machine, and I wonder if he knows he is dancing. Could his
insensate eyes, half-closed and empty, simply be looking within,
seeing himself on some shadowy stage upon which he turns and
leaps?



Actually, I think he's dead, and like a freshly decapitated
chicken, he just hasn't noticed it yet. He's dancing,
all right, but it's the same kind of dance a fresh corpse
executes at the end of a rope after dropping through the trap door.
The ballet of the damned.



When the sun comes up outside, near the end of the shift, it always
seems to me like the whole factory and the buildings and fields
that surround it have been cruising all night through another
dimension, like a spaceship that goes through some kind of time
warp and then reemerges, unharmed and unchanged, at the exact
moment from which it departed. Nothing has changed in the world of
our origin, nothing has changed in our isolated pocket of reality,
but we have gone somewhere and come back nonetheless.



I know that when I leave the factory and drive home in my car, I
will feel like an unknown astronaut quietly and without fanfare
returning home after spending years alone in my ship. I will listen
to the sound of no crowds cheering and watch as no tickertape falls
to celebrate my arrival as I drive through still-slumbering
streets.



I am home, but I am still isolated and alone.



When I walk out the front door, the fog is still there. It writhes
its way down the length of the river, enclosing and concealing it
entirely. I idly speculate that there could be some strange things
going on in there, and nobody would ever know.



Anything could be hiding down there.



There's nothing there, of course. It's just idle
speculation.



I throw a rock down there as I walk past, just to be sure.



Nothing happens. I stand for a moment, listening, and then laugh
nervously and walk on.



I can feel the moon up there, smiling at me, even though it has
disappeared behind the trees. That's one thing about the
moon; you can count on it being there, even if you can't see
it.



If you saw me now, a nondescript man calmly walking to his
nondescript car at the end of another day at his nondescript job,
you would never guess that I'm going insane.



The impending death of my rationality is overtaking me like the
approach of a black hole, and within days, hours{\ldots} minutes,
maybe, I'm going to cross the event horizon and succumb to
the raging storm of gravitation spinning like a top within that
infinite silken darkness.



But before the dissonance of that crazy awakening reaches its
crescendo, I'm going to perform the one act remaining for me
in this world.



I'm going to wear a pair of Jessica Alba's
panties.



Then I can finally die. 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Untitled}
\by{fishguzzler}


Son of a bitch, there's a storm on --- no lightning, so I
do this little dance between the light switch and the bed, partly
because my room is just too dark, no light leaking in through the
levelors, and partly because I can't let my mom see the light
on when she trundles past for another batch of rainbow cookies
--- six neat little rows by five in the box, and four at a time
carefully arranged on a little white saucer-plate, and about a box
and a half gone by the end of the night, which means at least
eleven trips down the hall past my room to the kitchen on a night
when she's watching HBO in bed, pretty much every night
--- but mostly because there's a mad badger in my closet,
an evil monster with beady little eyes glowing faintly green.
Actually, I don't really know what `beady' means.
But I know what a monster is, even if, come to think of it, I
actually don't know what a badger looks like. But I imagine
it looks just like this little bastard in the closet. Maybe not so
mean.

I can hear the television from the next room, though the walls are
ancient and incredibly thick --- I once put my fist into one,
broke through the new plaster, and then through something brittle
and white, until I sliced my whole hand open on a rough mixture of
sand and antique horse-hair that exploded into powder even as it
broke my left pinky and the knuckle of my pointer finger. I can
hear the television because of the heating vent on the wall between
the closet and my bureau, which conducts the voices from the
television with perfect clarity into my room and provides me with
fair warning every time there's a commercial break.
That's when I make my move. I'm fifteen, and I may be a
little pudgy, or maybe a little more than a little, but I'm
extremely light-footed, so I leap down from the bed and tip-toe
sprint to the door as my mother's clomping footsteps
reverberate back and forth in my little acoustic capsule ---
it's not because she's monstrously overweight, though
she must have gained over two-hundred pounds in the last three
years, it's just that she's such a hard stepper. I fly
barefoot across mathematically smooth and cold wood flooring that,
I know, I wouldn't feel if I could really fly. I keep my eyes
trained on the door of the closet and flick off the light,
crouching with my left hand poised on the light switch and my right
hand gripping the doorknob, white-knuckled, the scar where I split
the shit open standing out whitest, crisp even in the
near-blackness as I glare past it into that shadowed crevice with
the mad chittering sounds coming from inside. But it always quiets
as she passes my door, as though it doesn't want to be heard;
I still don't know how she doesn't hear it through the
walls when she's in her room. Stupid old cow.

But tonight she's doing alright, I think, because she's
only made three trips down the hall to the kitchen, three trips
lasting three to five minutes each over the course of three hours,
which is a real record-low for her since things got bad, like maybe
now she's finally getting over it --- or maybe
she's just gotten too fat to walk and decided to start
bringing the box with her from now on. Either way, I've still
had to squat here three times so far in the dark, smelling that
musty yellow odor like rotten tomatoes mixed with, I don't
know, curry or something, listening to that thing cackle and
scratch at the back of the closet door, swinging it open millimeter
by millimeter, because I never dare to leave it closed ---
I'm too scared not to try and hear what he's doing in
there, plus I know perfectly well that he knows we both know that
he can open the fucking door if he wants to. I've seen him do
it, not in minute, scratching increments, but fast.

Tonight the door has stayed put, and I haven't heard a sound
from the little monster. Even his stink, the one everyone else
can't smell, seems to be receding. Normally it hits me at odd
points during the day because it's burned into my fucking
skin, but tonight it seems to be clearing away, the dissipating
pestilential fog.

I hear my mother put down her dish in the kitchen, but the cupboard
does not creak open. The sink splashes on instead, a sound I hear
more through the pipes in the walls than through the air. Is she
washing the dish already, packing it in, with so much less than a
box consumed? Maybe she is getting over it, at least realizing that
a box and a half of delicious rainbow cookies per evening
won't help --- but more likely, she's probably just
got a stomach virus or something. I hear her stomp into the
bathroom, even whistling the tune we all used to sing, ``Your
Face is All over the Place'', which is sung to the tune of
``Your Kiss is what I Miss''. I smile in the dark, no
fear now, thinking it's gone, and maybe this will be the time
it doesn't come back.

There is a muffled thud from the bathroom, and a short, sharp cry
from mom. It brings to mind an image of my mother, beached, prone
in her fuzzy white robe on the bathroom floor, writhing in pain and
as-yet half-realized fear, the muscles in her neck bulging, showing
clearly for the first time in almost two years, as that little
fucker chews through cotton and into her chest. Blood spattering.
Chimp-like, upright badger-monster body, head like a nasty little
dog, Chihuahua or something, only with a cerrated nose like an
alligator, or one of those colorful baboon-things. Snarling bubbles
into the blood welling through the shorn muscle and cracked bone of
her left breast like a child with his chocolate milk{\ldots} Chittering.
Laughing at us. Oh my god her heart.

Instead of flinging the door open and running to the bathroom, I
smack the light on and sprint to the closet door, throw it open and
freeze, staring right into those unforgiving dog-black but
compassionless spheres. So it rears before me, wipes it's
dripping chin with a bony little wrist. Cackles. Now you're
mother is dead too. First him, now her. First him, now her. 

 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{In the Mirror}
\by{TheElectronicOne}


Out of the darkness came Rothard Mavalero. Grunting and thumping,
he was the city undertaker. It was not a job many would like but he
had kept it for fifty years. Some people thought that was unnatural
but they did not know the half of it. And if they knew the whole of
it they would have run in terror. Bodies interested him. He liked
the way they looked. He liked the way they felt. But most of all he
liked the way they tasted.



Today it was Mavalero's favorite kind of body. A floater from the
river. It was still fresh, like a recently caught fish. The coroner
wasn't at work yet. Nobody would know what he was doing. He dragged
the bloated corpse and looked into its eyes. Suddenly, he began to
pry the eyeball from its socket. A sweet ``snap'' sound happened as
the elastic snapped. He licked the slimy eyeball, savoring the
salty taste. Then, as the deceased's other eye seemed to watch him,
he bit into the juicy retina. It tasted chewy and meaty, just like
he had expected.



Mavalero looked down at the body tauntingly. Blood was oozing from
the empty socket. He liked that it was helpless. He stabbed at the
face to make more blood come out, then dipped his finger into the
blood-filled socket and tested the quality of the victim. When he
was done with the little game, he started to pry at the other eye.
This one did not come out so easily. It felt like it was glued into
the socket, and he had to tug and tug. But finally, with the help
of his pocket knife, it came loose. The eye stared Mavalero in the
face. He did not care. Rothard Mavalero was a very bad man. He
downed the second eye with pride, smacking his lips as he smiled in
his conquest.



But as he began to ponder what he would eat next he saw something
in the corner of his eye. He didn't know what it was. His heart
raced like a galloping horse. He turned slowly towards what he had
seen. Then he sighed with relief, because it was just the mirror.
He had seen his own reflection.



{\em {\ldots}or did he?}



He looked at the reflection, but his face looked unfamiliar. He
turned his head, and his mirror self seemed to delay a little bit
before copying him. With a piercing, inhuman scream, Rothard
Mavalero realized what he was seeing. It was not a mirror, but a
window into a room that had been cleverly copied to resemble his
evil laboratory in every respect. The man was not his reflection,
but the young but hardened detective Luke Bavarius in disguise.
Bavarius had seen everything: the body, the eye eating, the
blood.



He felt a nervousness arise in his throat. He struggled to hold his
posture as he waited for his certain death at the hands of the
private eye. Vomitus dribbled out the mouth of Rothard Mavalero.
Then, as he watched, Bavarius reached through the glass and
strangled him alive. 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{The Horrid Lighter}
\by{WhereTheFishLives}





This is a long story about Luke Bavarius when he saw the shadows in
the world when he was younger in 7th grade. Bavarius is me. I saw
the them, the shadows. And it has turned my brain into darkness. I
was walking with my best friend Victor and Praeton when we found
the terrible thing. A sickly sparkle flashed the corner of my eye
and caused me to turn instinctively towards it. It was a silver
lighter, but not any silver lighter you've ever seen. It has a
skull on it with a eye made of ruby pressed into it. ``Cool'' said
Victor as he brushed the dust and soil from the lighter that was
buried centuries ago. It had a certain look that cut to my soul and
made my stomach tighten on its contents.



Victor shifted it open and his expression changed to one of evil.
My teeth clenched as I could feel scaredness take me over. Praeton
began to tremor in delerium as sickly vomit shot from his mouth
like a giant waterfall. Once the vomit was spent, a terrible white
cloud came from the eyes and from his face. The cloud had Praeton's
face. Praeton's face had a certain shocked and unhappy expression.
It would be soon be too late for Praeton. The soul was sucked into
the lighter like an evil waterfall. And the lighter's fire was
switched out for a red indescribable flame as the soul went in into
it.



``Praeton, No!'' I shouted from fear. It was too late, though. I
could tell. He was already changed in a certain way. So I ran away
from the evil duo.



My fearful brain didn't know what else to do. It told my rubbery
legs to run and they did run. The shock of the pounding of my feet
on the ground went up through me. Up through my knees and then my
legs. Then my chest and my soul and then into my brain with a
terrible power. The power shot through me like an jackhammer. My
adreniline squeezed my jaw tighter and yet tighter to fight back my
morning breakfast. Which was prevented from being vomited out by my
teeth. The wind felt strongly against my face. Blinding me. But I
didn't have time to notice. I only had time to run.



All of a sudden I was already at the door of my house when i burst
through it. ``Grand-nd dad? Help!'' I shouted! As I shot slowly like
a bullet from a gun through a sea of adrenaline. But there was no
Grandad, only Praeton who was already there. The silence was
deafening. The only sound was the horrid lighter clicking
deafeningly. I was in an abundance of shock.



``Where's my grandad fiend?!''



``He's in here with us'' Praton made a grand gesture to the lighter
in his hand.



``N-N-No,'' I stammered as I went to the closet and got out the
Baretta. The black gun metal was cool against the palm of my hand.
The blackness of the gun matched my heart's darkness as I aimed at
Praeton.

``I'm gonna take you out!''

``Ha Ha Ha Ha ha'' he laughed. ``Bullets can't hurt me!'' he said
smirkingly. I knew I only had one clip with which to dispatch this
wretched thing. To back to wherever it came from. I fired and a
bullet went directly between his eyes but didn't stop him. Again I
fired, and again, and again I fired a total of 14 times.



``Looks like someone's out of bullets!'' He cackled devilishly. Now
it was my turn to laugh



``Hahahaha! Looks like someone doesn't know anything about the
Beretta M9!'' I triumphantly shouted. With my last bullet I fired.
The 9mm bullet slickly exploded from the barrel and into the
demonic lighter which was still in his hand. While the bullet
struck, metal on metal, the souls were vomited all out of the
it.



``Nooooo!'' cried the thing as he turned to rust. ``It's all over
now.'' While the Beretta fell to the ground in slow motion I was
instantly {\em insane}. 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{The Playground}
\by{on time for once}



When I awoke I was tied up in a dark basement and the little boy
was standing over me. The first time I saw him I had laughed at him
because he was constantly vomiting, the putrid liquid pouring out
of his mouth and nose as if he were a water fountain of vomit. It
didn't seem so funny now.



Now that I was tied up, he seemed much more threatening. He stepped
closer. His warm vomit was now hitting me in the crotch. Where was
it all coming from, anyway? There was so much of it I
couldn't believe it could possibly have all been inside this
small child. Was his face a portal to a parallel dimension? A
parallel dimension of vomit?



As he pistol whipped me with my own Beretta I choked and giggled
and thought about how I, Luke Bavarious, private detective, had
ended up in this situation.



It had started because the children's playground was always
covered in blood and vomit. Every day it would be cleaned, but
every morning it would be covered in blood and vomit again. This
had been going on for several years now and we had finally decided
to see what was going on. I was assigned to stop the blood and
vomit.



I went to the playground one evening and hid under a slide with my
Beretta and my night vision goggles. It wasn't quite dark yet
and there were a few children still playing. One of them was the
vomiting boy, which explained the vomit. Oh, how I laughed.
Hopefully there would be an equally mundane explanation for the
blood. Perhaps the boy had a beautiful blood-vomiting mother. I
would have to talk to her and ask them to clean the playground
themselves after they were finished using it so the city would not
have to pay so many cleaners. I would offer to help her clean the
playground, and maybe we would end up doing sex on a swing. I like
swings.



I was distracted by my fantasy and forgot to watch the playground
for a few minutes. When I looked up again the blood was there and
the children were gone. I got out from under the slide and glanced
around. What had happened? Where was the beautiful woman? Suddenly
something hit me in the back and vomit sprayed over my head. The
boy! The vomiting boy! He must have been on the slide I was hiding
under, and now he had jumped off it onto my back! I tried to get
him off me but he held a urine stained pillow over my face until I
passed out.



And now here I was, in this basement. I could see now that under
the vomit the boy's face and clothes were covered in blood.
And so were his teeth, his sharp horrible teeth. I knew then that
he had eaten the other children. Now he was going to eat me.
Suddenly, I was sobbing.



A man in a lab coat ran in. He was also vomiting.



``Daddy!'' vomited the boy excitedly.



``Son!'' the man vomited, running over to his son,
``Stop! This one is not like the others!''



He injected me with something. Suddenly, I was vomiting. The man
collected some of my vomit in a beaker then poured it into a
machine. Writing in a language I couldn't read appeared on
the machine's screen.



``See, son?'' vomited the man, pointing at the screen,
``This one is not like the others. It will not grow up to be
evil. The strange results you got were not because it will be even
worse than the others but because it is already too old for your
tests to be accurate!''



``You're right, daddy!'' the boy vomited,
``Let's put it back!'' He injected me with
something else and I passed out. As I lost consciousness I heard
him vomit ``We should try another playground, they seem to
have noticed what we are doing here.''



The next morning I woke up under the slide in a puddle of vomit,
with a bad headache and no memory of what had happened. For some
reason, though, I felt certain that this playground would remain
clean from now on. 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{The Exploding Curse}
\by{overnightmike}



A dark night filled with trial and unrestiness was ahead. The bar
tender said unimportant things which I heard. A vague feeling was
consuming me like I was consuming alcoholic beverages. When? When
will the signs come again and would they let me live? Being a
gritty person himself the bartender did not question my long
drinking mainly because I am a very mature person. I could not
shake the vague feeling. It was everywhere.



I felt like vomiting but did not. Instead I was glad I had a
large-caliber handgun.



The door to the tavern burst open, but the bartender never saw who
walked into the door because he had died of fright. I saw his rusty
blood. He was the lucky one of the two of us, who were the only two
people in the bar. Besides the signs, which had arrived. At least I
didn't have to wonder anymore. My legs burst open in a liquid
explosion.



My whole being was pain. Excruciating on the floor of a bad bar in
a skid-row section of town. The signs had left but their work was
completed. For now.



I passed out from the pain of having exploded legs. But I woke up
sometime later and poured some booze on them to make the pain stop,
I could not walk, so I wrapped them in dirty, booze soaked bar
towels, which were plentiful behind the bar. I was left to lay in
the bar with the dead bartender who was putrid with corpse-stink.
That was My Fate. My Punishment. My Own Prison.



Everything was quiet. The dead bartender said, ``What's your name,
cursed one?''



``Burke Dreadnought,'' I said, quivering in fear at the talking
abomination from hell.



``Do you know why you are here at this time, do you know what pain
really is?'' the corpse hissed at me, spraying me and everything
with green putrid goo while the words garbled out.



``My legs exploded so I think I can talk about pain,'' I wiped the
blood off of my gratuitous chin stubble while saying.



``Oh yeah, not yet you can't!'' The corpse began levitating and
suddenly I remembered. Bavarious! The curse all of a sudden made
sense!



Summer 1967. I'm a rookie cop, green and not jaded at all and Luke
Bavarious is showing me the ropes of the hard, rain-slicked streets
of Miami. The Haunted House Murder Case. Fourteen people dead in
the span of one night. Bavarious wasn't assigned to the case but he
was the first one to the scene with me in tow. He growled out
instructions, brazenly brandishing his large-caliber handgun like
he always did. We found a kid. Left at the scene. Not murdered
thankfully.



``The Haunting will follow you unless you put an end to the cure,''
the kid said while shaking because he had vomited so much. ``The
curse must be lifted by giving the bones in the basement a proper
burial. There were ritual murders here back in prohibition times by
an evil bootlegger. Now he haunts the house by killing everyone in
it all the time!''



Bavarious growled, ``You make me want to puke! I'm here to get to
the bottom of this!''



After we left the scene I said meekly to the scowling Bavarious, ``I
think we should give those bones a proper burial bacause kids
should be listened to.''



``Ha! Let's go catch some scumbags!'' Bavarious put on his sunglasses
and went back to his squad car. Six years later I quit the force
and started drinking. That was when the signs came to the bar to
remind me of the curse and the kid I should have listened to.



My legs were spewing gore trails all over and I finally remember
that I always carry a large-caliber handgun. I shot the
curse-zombie bartender right between his red devilish eyes. His
last words were, ``Soon, soon you will know the horrible depths of
hell as I know them, Burke Dreadnought!''



I am in the bar still. I will die here but if I could walk I would
go into a basement in Miami, and dig up the remains of the mad
bootlegger's victims and give them a proper burial. I would dig
them out of the same basement they found Luke Bavarious in last
year, raving about curses to this day in a mental asylum.



The End?



 



