%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\by{VelvetEvoker}


{\bf Station 666}



Tommy and his best friend Bobby were twelve years old. They lived
in a small town that reeked of pestilence and a terrible oldness.
Bobby's parents were very strict with their son and
wouldn't even get him a television, so all they had was an
old antique radio that once belonged to Bobby's
grandpa.



Tommy and Bobby knew there was something wrong with the radio, but
no one would listen. Many times they had asked an adult to come
take a closer look at the radio, because they knew if anyone else
got the same feeling they were getting they'd burn the radio
any bury the remains. Many times Tommy and Bobby tried to throw it
out, but it was too heavy for the children to carry and the adults
would not let them throw it away because it was their old
grandpa's antique.



One night when Tommy was sleeping over at Bobby's house, he
noticed something strange. No matter where it was left the day
before, the dial would start turning and eventually it'd end
up on the frequency of 666. Tommy tried turning it as low as it
would go, and in a few hours it'd be back at 666. It was the
same thing if he tried to turn it higher.



Later that night they turned the radio on while it was at station
666, but it did not seem to be an active station. Nothing but
static spewed forth from the speakers, but in the static was the
sound of dread. Bobby's mom said that it was odd but it must
just be the dial's default setting, so still nothing could be
done about the radio.



The next day at school Tommy agreed to sleep over at Bobby's
house and leave the station on all night to see if anything
happened. However, nothing happened all night and they were tired
so they began to fall asleep. They were awoken again at exactly
midnight by a terrible screeching noise, followed by a voice.



The voice spoke in an unknown language that was possibly even older
than the radio. It was such a terrible voice that it sounded like
nails on a chalkboard and both boys had to cover their ears. Bobby
took his hand off of his ears and they were covered in blood, but
Tommy wasn't bleeding.



Suddenly Bobby leaned over as if he was about to vomit, but instead
of puke a clawed hand came out of his mouth. The hand continued to
emerge, followed by a shoulder, until Bobby's mouth could
take it no more and his head split in two, with his brains slopping
down his back and his jaw trailing down his stomach.



Finally the demon had emerged, covered in Bobby's blood and
stomach fluids. ``I am Xavid Viarabous, and no one has
survived the sound of my voice for a thousand years.''



Suddenly Tommy reached into his sleeping bag and pulled out an old
Beretta he found in the field. On it were the initials
`L.B.'. ``I survived.'' he said. Then he shot
the demon.



The radio was still not thrown out for two days. Tommy turned it to
station 666, and from midnight to 12:01 he could hear Bobby
screaming. 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\by{Donde Esta}


{\bf The Promise}



5 A.M. is a shitty time for burnt coffee.



As I, Luke Bavarious, stared in to my barren mug and gently touched
the still fresh wound on the side of my head, a reflection in the
still slick bottom forced a sob from the trenches of my gut.



It was him.



That night in the alley way, four sleepless and coffee spurn nights
ago, I saw something that can only be described as awful, and I
shot it. I shot it dead.



He came at me and he came at me hard, but Ol' Betsy finally
laid him to rest. As he slumped over my side, covered in warm
oozing liquid, I caught a reflection of something far worse than
the disfigured wretch I had just put down. It was him; the man of
my non-existent nightmares.



I caught his reflection in the broken glass and he was smiling,
smiling an unnatural and hideous grin. I was in no position to
defend myself. While I might be able to load a Beretta faster than
anyone else this side of the Hudson, being in his presence, time
seemed to slow to a halt.



His wild arms flapped about as if the cool alleyway breeze had been
given life. Entirely too tall and entirely too pale to be human,
only one thing came to mind: Slender Man.



Two weeks before that, I had gotten a call from an extremely upset
and distraught mother. She said that her son came home and he
wouldn't stop talking about how the ``Slender Man''
had just played with him and some of the other children at Bryant
Park just off of W 41st St.



Her son went on to tell her how ``Slendy'', as the boy
had nicknamed him, had taken a particular interest in Suzy Carlton.
He said that Slendy took her into the alleyway and she came back
with a strange purple mark on her arm. She thought it was awesome
and all the other children wanted one too, but Slendy said that
they would have to wait and that he, ``Would be back for
everyone!'' Her son was the only one who was scared of
him.



I scoffed at the lady and told her that I had more important things
to do than investigate some street performer handing out stickers
to children in the park. I didn't care if her kid got stiffed
a purple tattoo from some freak. I hung up on her.



I shouldn't have hung up on her.



As I laid in the street, looking at the piece of glass I was
terrified. Sobbing, making all the connections in my mind, I stared
at him. Stared into his devilish eyes, wondering what it was that
he wanted from me.



As he approached me, arms dangling all around, he bent down in a
way that a human should not be able to and stuck his face nearly an
inch from mine.



In that moment, the only thing I wished for was death; quick and
sudden death. Instead, the Slender Man would give me something much
worse: a promise.



He looked me in the eyes and with a smile he whispered in a voice
which came out in chortles, ``Don't
worry{\ldots}Bavarious{\ldots}I'll be back for you
too.'' It was a promise which kept me awake for four nights,
and a promise I expected him to keep.



Now, looking into my cup, I watched as he stood behind me. I did my
best not to show my fear.



I looked at the badge lying out on the table. A gold shield made of
brass and time. It wasn't much, just a symbol, but it gave me
the courage to speak.



``Mr. Slender, why'd you go after those children?''
I asked, trying to sound as calm as possible.



``The children give me{\ldots}'' it sounded now as if it
were trying to speak while a river of maple syrup ran through its
throat, ``{\ldots}they give me lifeeeeeee''.



``So why are you here{\ldots}Slendy?'' I asked
cautiously, doing my best to distract him while positioned my hand
on the holster under my robe.



``Little{\ldots}David Sanders{\ldots}didn't last very
long{\ldots}and his mother{\ldots}was{\ldots}lacking,'' he
said smugly.



``Well Slendy, that night in the alleyway, you should have
taken your chance because now I'm ready for you,'' I
barked, as I spun around and emptied a whole clip into his
chest.



He shrieked and recoiled as black, viscous liquid leaked out onto
my kitchen floor and ate away at it like acid.



With his defenses down I fought through the mess of flailing arms
and pistol whipped him with the still burning hot barrel of my
Berretta.



``You shouldn't have fucked with those kids, Slendy. You
shouldn't have fucked with Luke Bavarious,'' I yelled at
him.



He wasn't done. Despite my damage, he was still functioning,
though severely wounded.



``I'll be{\ldots}back
for{\ldots}you{\ldots}Bavarious,'' he coughed out, between
sputters of demon blood.



He dashed out the door and before I could get to it, the thing was
out of sight.



With a little boy's death that could have been prevented on
my conscience, I now know my purpose in life. If I had only
listened to him.



The Slender Man may have just made me a promise, but I'm
going to beat him to it. Luke Bavarious is now on the case. 

 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\by{henpod}


Fuck man whoever reads all these stories is going to be vomiting
blood like no tomorrow 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\by{BoldFrankensteinMir}


{\bf Johnny the Knifer}



I stopped short at the counter. I sat down. Coffee poured out the
coffee pot and into my cup, like a pot of brown bullets shooting
into my cup and splashing in coffee. The waitress was very pretty.
She said ``would you like some coffee''? My name is Luke Bavarious. I
like coffee. And I am a detective.



It was my favorite restaurant. It was on 756th street in Manhattan.
New York. The waitress was very pretty, and the coffee was just as
good. ``How do you like your coffee Luke Bavarious'' she said. ``Sweet
like you'' I winked. She winked back. There was something about the
way she winked at me and the way she poured my coffee. My heart
beat double the blood suddenly, but I was in control. In control of
my blood.



``How is that kid you have'' I said romantically. The waitress
blushed. ``Johnny is a good kid but I'm afraid he's falling in with
a bad crowd'' she cried. I comforted her, my shoulder soaking up her
sweet sad woman tears that she cried from those pretty eyes.



Suddenly, three men walked into the restaurant. ``Well Well Well
Luke Bavarious'' said the first man. He was horrible and tall and
ugliness all wrapped into a tall horrible suit. ``You better run
Luke Bavarious after you ruined our drug crime this morning!'' he
said. Then he said it again. With his guns. And his bullets.



I jumped behind the counter. The waitress cried ``don't let them
shoot the restaurant I have a kid'' so I jumped in front of the
counter. The mobsters cackled a sick crackling laugh that bled in
waves out of their toothy horror mouths. ``The great Luke Bavarious''
laughed Jimmy the Knifer. ``Hiding behind a woman! Laughable!'' he
said and proved it with more laughs.



``Not so fast!'' I yelled and reached for my sleek silver loaded
Beretta with my name engraved in the gun and on the bullets too. I
realized my gun was gone! I had to think fast.



``Not so fast!'' I yelled and grabbed the pot of coffee. I splashed
it at Jimmy the Knifer and his goons. The goons ran, missing the
terrible shower of deadly boiling coffee. The coffee splashed into
Jimmy the Knifer's hands and face. I recoiled in horrible terror as
he screamed.



``NO'' screamed Jimmy the Knifer. He fell to the ground, the tears of
pain mixing with the steaming sweet coffee as the veins in his
forehead popped open like firecrackers in hot coffee and tears.
Blood and tears and hair and coffee spilled into the coffee puddles
on the floor and he screamed as his skin went into the puddles too.
``NO'' he screamed again. ``NO''.



I turned to have my sandwich that I also ordered and the waitress
had brought to me before the mobsters came in. Tears were on her
face just as surprise was on mine because of hers. ``What's wrong
Suzie'' I said. ``We're in New York the city that never sleeps, of
course there's gonna be a little crime but I'm Luke
Bavarious''.



``NO!'' screamed Suzie. She ran to Jimmy the Knifer! What is
happening?



``I told you he was in with a bad crowd'' she sobbed through tears of
grieving for her dead mobster son. I recoiled in horror from my
sandwich. If I had known! But Jimmy the Knifer was not a
child!



``He looks older because of makeup so adults would take him
seriously!'' she cried at me. I looked now at Jimmy. A kid! The
makeup was melting off in the blood and coffee and boiled skin and
it was a kid! The sandwich dropped from my hands and the coffee pot
shattered all over my shoes also. How could I have known?



Jimmy the Knifer looked at me with blood eyes and tears coughed
from his dying words. ``Who's the big man now{\ldots} Luke{\ldots}
Bavarious{\ldots}'' he said, and in his hand was the baseball card I had
given his mom to give him for his birthday just a week before. That
made it even more incredibly sad.



``NO'' I screamed and they took me away for murder, on two counts of
homicidal killings. Johnny the Knifer{\ldots} and Johnny the Boy. 

 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\by{lemonlime}


A BUTTER KNIFE





Martin Boswell was always required to remain at table until Mr.
Boswell dismissed him. Some nights Martin would sit in his creaky
old wooden chair, picking at a tattered and threadbare corner of
its cushion, until long past midnight. Since eating his supper
never took more than an hour, Martin would be left with a very long
time in which to sit, pick at his lumpy old cushion and watch his
father watching the butter knife. This knife was dull, scratched
stainless steel with a rounded tip and a very slight serration; no
different than any other butter knife that might grace another,
happier supper table.



At first Mr. Boswell would turn it around and around, so that the
lamplight flashed off its blade hypnotically. Then, holding the
handle lightly between his thumb and all four fingers, as one would
hold the bow of a cello, he would run that knife's dainty little
teeth slowly up and down the length of his forearm, occasionally
pausing to turn tight little circles over the network of veins
decorating the inside of his wrist and displaying to all the
precarious restraint in which his very life's blood was held.
Martin had used his father's butter knife once when Mr. Boswell was
at work; from that day forth, seeing his father's shivers never
failed to provoke an answering shiver in himself.



Then Mr. Boswell would turn the butter knife's attentions to his
scarred, scabbed hands, those stained and stinking hands which had
fired the little gun that shot Martin's mother in the back as she
tried to run for the last time. He would drag those hateful smiling
teeth back and forth across the back of his hand as though
buttering an english muffin, hour after hour, until the skin began
to abrade and swell and eventually bleed.



At first the wound was a minor one. But after being kept open by
Mr. Boswell's nightly ritual for the better part of a year it began
to grow wider and deeper. His flesh became purple and black and the
stench of putrefaction was so strong that no one would willingly go
near Mr. Boswell except for Luke Bavarious, a former police
detective turned bodyguard, and Martin.



One night, around 11 o'clock, Martin saw bone. Not even the memory
of the four days of torment his mother suffered in the root cellar
as she died of her gunshot wounds could keep him in his chair then.
In his bedroom, Martin stripped off his soiled clothes and set them
to soak in the bathtub, then opened the window to clear the odor
and began to wonder whether a jump would really kill him. He didn't
feel like adding to the number buried in that grisly root cellar,
yet he knew that if he tried to creep out of any of the doors he'd
be instantly caught by the keen eye of Bavarious.



There was a knock at his bedroom door and then it opened. Luke
Bavarious stood there and he said, ``I'm sorry, Kid, what you're
gotta live with is wrong. Just run back as quick as you can. Get in
your chair and I'll come in a bit later to shake him out of it. I
promise I'll hurry.''



Martin threw on a clean set of clothes and dashed back downstairs.
His father never even looked at him as he took his seat as quietly
as he left it. Mr. Boswell did not shift his attention from the
butter knife until Bavarious walked into the dining room, claiming
to have seen an intruder across the courtyard. Martin was
immediately ordered to his bedroom for the night, and as he left
the table Martin felt a gratitude and devotion for Luke Bavarious
that he could never have imagined just fifteen minutes
before.



That night taught Martin that while Mr. Boswell was watching his
butter knife, he could go anywhere and do anything without his
father seeing him. Only Luke Bavarious could keep him from leaving
during those times. One night, as Mr. Boswell sat mesmerized by the
clean red blood that seeped from his corrupted flesh, Martin went
to the linen closet and pulled out a backpack in which he'd stashed
clothing, food and a little money. Bavarious met him at the
door.



``Let me go, Luke, please,'' Martin begged. ``You know he'll kill me
too, as soon as he sees that I want to leave.''



After looking at Martin for a moment, Luke said, ``I know, kid.
After what he did to your Mom, I knew that I'd only leave this
house when I was dead. Mr. Boswell, he'd kill me in a second if he
knew I was standing here talking to you and not killing you. No way
can I let you stay here. Your father doesn't love or respect you.
But he was a good man once, and I can't bear to live with having
done something to betray his trust in me. No, there's only one way
it's gotta be.''



With that, Luke Bavarious pulled out the Beretta he'd carried since
early childhood, applied the muzzle to his temple and squeezed the
trigger. A scalding wave of blood drenched Martin's face as he
stood frozen there. He turned suddenly and ran away into the
night.



It would be a long time before Martin Boswell stopped running. He
crossed oceans and traversed lands stranger than he'd ever imagined
during the long empty hours sitting at his father's dining room
table. During that time, Martin was a beggar, a slave and a whore.
When he woke up one morning in a place where the air was so thick
it could be used as a sandwich spread and the rain fell as warm as
blood, he knew he was home.



Martin would forget, sometimes, why he'd run. He'd be eating supper
at a cafe and the light shining off one of the diners' butter
knives would make him shiver with some dark lust. But none of that
mattered. Every time he felt the hot rain wash down his face Martin
would feel the blood Luke Bavarious had shed, the sacrifice he'd
make of his own body, so that Martin could be reborn into a new
life. 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\by{King Plum the Nth}


I'm beginning to feel a bit self conscious about the lack of vomit
in my entry.  vomity vomiting vomit which vomits more vomit
from it's oozy vomitous depths. Hmmm{\ldots} 

 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\by{BoldFrankensteinMir}


For some weird reason I just keep imagining Luke Bavarius as
halfway between Luke Cage and Benny Hill's toymaker character from
Chitty Chitty Bang Bang. Am I{\ldots} completely off the mark here, or
what? 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\by{henpod}


I see Bavarious as a Max Payne film noir type detective, but with
loads more vomit and suddenly. 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\by{Monkey Trouble}


{\bf The Cave}



The name's Bavarious. Luke Bavarious, P.I.



My morning began with a mysterious phonecall. An unidentifiable
voice, wracked with sobbing, incoherently pleading for help. The
only words I was able to decipher were ``help'', ``old cave'' ``outside
town''. That could only mean the old, disused coal mine on the
outskirts of town. Whoever the poor shmuck was, I decided to
investigate.



I followed the overgrown dirt track from the edge of town, until I
was staring into the dark, gaping mouth of the cave. As I clicked
on my flashlight, I heard a voice behind me.



``Mister. Hey, Mister.''



There was a small blond-haired boy on a rusted red bicycle behind
me.



``You shouldn't go in there, it's dangerous.'' he said.



``Beat it, kid, you shouldn't be messing around out here.'' I said
gruffly.



A small smile twitched at the corner of his mouth. ``Ok, but don't
say I didn't warn you.''



I watched him turn the bike around and ride off. As I stood at the
cave entrance, I felt a strange itching sensation on my right hand.
Looking down, I saw a wart I hadn't noticed before right next to my
index finger. Dismissing it, I drew my beretta and headed into the
darkness of the cave.





As I shone my flashlight into the murky depths of the cave, I could
see it went on for miles in front of me. The itching sensation had
started to travel all over my body, getting more intense. I was
eager to find whoever was in trouble and get the hell out of
here.



{\em BANG.} A gunshot cut through the air like a knife. I hit the
deck, rolling behind a pile of rocks and scanning my surroundings
for my would-be attacker. It was only then that I realised the shot
had come from my own gun.



I looked down at my gun hand, and recoiled in horror. Where the
wart had been, there was now a fully grown finger{\ldots}{\em and it was
curled around the trigger!}I swiped at it with my other hand and
it responded by trying to turn my own gun on me.



Seeing no other choice, I dropped my flashlight and grabbed my
knife from my pocket and started to saw into the strange digit. I
vomited in pain as the blood flowed from the cut. My flashlight lay
on the floor, casting it's light onto me, and I watched as the
finger continued to grow even as it hit the floor. The flesh
writhed and I realised it was growing into a hand, then an
arm!



The itching sensation suddenly wracked my whole body, and I ripped
open my shirt to reveal several pairs of hands growing from my
chest! I vomited again in disgust, once again going to work with
the knife, vomiting blood and vomit from all over me. Suddenly I
was sobbing.



As the piles of bloody flesh on the floor surrounding me continued
to grow, I felt a hand clamp down on my shoulder, and I was spun
around to face{\ldots}myself. I gazed in horror around me as I realised
all of the parts I had chopped off were growing into other versions
of me!



This{\ldots}is the dawning of the age of Bavarious.



The End{\ldots}? 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\by{Hired Gun}


{\bf The Bodies of Bavarii}



It was a haunting and horrid night in the city. Luke Bavarious sat
at the bar. He knew that nights like these only brought trouble.
All night, he had been feeling like he was being followed. He
sipped his drink and sighed. If only he was back at home with his
family. His wife and son had been killed in a tragic Beretta
incident. Thinking of their deaths made Bavarious want to vomit.
Instead, he had another drink. This was his fourth one
tonight.



After paying for his drinks, Bavarious put on his jacket and walked
out onto the dark street. He knew that every alley and dark corner
could be hiding a horrifying secret. He still felt the presence
following him, but he put it out of his mind. Cautiously yet
fearlessly, Bavarious began the five block walk to his apartment. A
few minutes later, he suddenly heard the unmistakably terrible
sounds of screams. These were no ordinary screams. These were
screams of murder. Bavarious ran into the alley, his Beretta in
hand. It was so dark that he couldn't see anything. He also
suddenly felt that he was no longer being followed.



Suddenly a flash of lightning lit up the sky and illuminated the
scene in the alley. Bavarious could barely stop himself from
vomiting when he realized that there was blood everywhere. And he
was covered in it. Each drop of rain smeared the blood into his
face and his clothes. Another flash of lightning revealed the true
horror of the alley. The blood came from two bodies. The bodies of
his wife and son. Their deaths were no accident after all.
Bavarious stared at his Beretta. He noticed that half the clip was
empty.



As sirens rang in the distance, Bavarious knew he had no other
choice. As blood and vomit flowed down the alley, the sound of one
final gunshot pierced the night. The body of Luke Bavarious fell
next to his son. For a moment, the two pairs of dead eyes met. 

 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\by{Danger408}


{\bf The Torrid Connection}



Cleaning his Beretta for the third time that day, and taking a swig
of cheap whiskey, Luke Bavarious pondered his current case.



``This is going nowhere'' he thought. The case was
different, it wasn't about helping others --- it was
about helping himself. After seeing the face, the one so much like
his own, yet so different; things had changed. He tried to forget,
but all he could remember was the blood, all of the blood, the
blood everywhere. ``Was that really me?'' He didn't
know.



He glanced down at the picture of his son he always had on his
desk. The divorce had been rough, and he hadn't seen him in
while. Taking another swig from his bottle, suddenly he turned as
he heard a knock at the door, followed by two more in quick
succession. He hid the bottle behind his desk, hoping to appear a
bit more professional.



He didn't have to respond however, as the mystery person had
already opened the door.



``Hello,'' A beautiful woman started, ``I need your
help.''



``Have we met?'' He asked.



``I don't believe we have,'' she replied. ''I
got your name from a friend. It's doesn't matter though
- I have a case for you. My husband is missing. I need you to find
him, and I hear you're the best at what you do.''



``I'm not taking any more cases{\ldots} I have a lot of
personal shit to deal with. Besides, you really don't want me
to take the case.'' He paused for a moment. She looked
familiar, a face he knew he had seen, perhaps in another life, but
couldn't put his finger on who it was. She looked good
though.



``I'll do anything.'' She pleaded as she removed
her shirt. Luke had always prided himself as being a man of ethics,
but ethics only went so far. As he removed his shirt, he added,
``I'll take the case!''



They commenced sexuality. It had been a long time for both of them,
too long in fact, as it seemed like it would be over before they
even started.



As he lit up a pair of cigarettes, he once again got the feeling
that he knew her from somewhere. He knew her named started with an
``L'' but he couldn't remember the rest.



``Are you sure we haven't met before?'' He
asked.



``Now that you mention it, I think we have.'' She added
as she began to pull at her face.



She stretched and tugged, as vomit-like ooze poured out of her. She
tore away pieces of herself, discarding them on the floor like a
used condom. It seemed that the only thing left was a bloody mess
--- until she wiped it off, revealing a familiar face{\ldots}
His own.



Scared half to death, and knowing that the other half would soon be
complete, he managed to say, ``Listen to me{\ldots} Whatever
you do{\ldots} Don't touch my son{\ldots}'' He knew he
should have spent more time with the kid.



Finishing him off in more ways the one, the once-woman's
transformation was complete. Dressing in his cloths, and putting on
his badge, she was the new Luke Bavarious. Was it a monster? Or
could the real Luke from the future? Some questions aren't
meant to be answered. 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\by{Safe Driver}


These stories are great!



{\bf Hell Cab}



``Wake up, Bavarius! Wake up! Wake up!'' The
dispatcher's voice screeched through the radio.



Luke Bavarius was asleep behind the wheel again.



``Wasn't sleeping, just resting my eyes.''

The radio buzzed back ``{\ldots}1977 Ruminate Way, pick
up.''



At night the fares usually tip well. Mostly it's vomiting
drunks with wallets that are just as loose as their mouths.
Luke's been pulling a lot of late shifts driving his taxi.
They help keep his mind occupied from the hand life dealt him. His
wife is gone now; it's just Luke. The cancer came out of
nowhere. It cashed in his wife's last chips. It ate her up
from the inside, destroying their lives. All Luke could do was pray
and make empty promises as the doctors ran their constant tests and
hooked up more tubes everyday. It never went back to being right,
she never got better.



With all of his time being devoted to his dying wife, Luke
ostracized everyone else around him. Even their only child, Bryson
Bavarius was ostracized {\ldots} ostracized with extreme prejudice
that it would make you vomit. Luke's neglecting of the rest
of his family lead to more trouble for them. Bryson Bavarius needed
daily injections to keep his type X diabetes under control. The
injections never came. Bryson accidentally ate an entire bowl of
sugar. The moment the sugar touched his lips, Bryson's face
exploded like a pus filled vomit balloon. He died. When Luke found
his body weeks later, the room reeked of rotting vomit and glucose.
Luke told his wife that the boy could not make it to the hospital,
he was just too sad. His wife got worse with each passing
day.



Luke would never forget his wife's final words; it has
haunted him since that day. ``You lied.'' In her final
twitches a pressurized pocket of vomit burst from her mouth. Then
it was over and it was just Luke and his night shift.



The address dispatch sent Luke to was an empty lot; nothing there
but silence. Luke began circling around the lot. It was probably a
crank call. Out of nowhere the read door is yanked open and a
passenger jumps in.

``Christ, I didn't even see you! Gave me a scare there,
well where to?''

Luke looked into the rear view mirror. The passenger's
familiar eyes were empty and cold. The passenger smiled and
Luke's heart skipped a beat. The smile turned into a
grimace.



``Drive Luke, you're just going to drive.'' The
voice was hollow.



Luke's taxi pulled into gear. None of the streets were
familiar anymore. They turned into endless circles of blurred
buildings and drab scenery. Luke had never been so scared in his
entire life, and he did not know why. He vomited on his lap. The
taste was like the final taste he had of his dying wife.
Bile.



The same horrible voice broke Luke's confusion,

``Keep on driving Luke, we're almost there.''



They made it. Luke Bavarius didn't wake up. 

 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\by{  Livestock}


Obviously I'm exempt from winning (and not likely to anyway), but I
thought I'd give it a try.



{\bf Destiny Calls

A Luke Bavarius Mystery}



Luke Bavarius was on edge. For months he'd been receiving
terrifying phone calls from a mad man. The telephone would ring,
Bavarius would pick up, and that horrible voice would speak.



``You're dead, Luke Bavarius. {\em Deeaaaadddd{\ldots}}''



``Who is this?'' Luke would respond. ``I'll get you! I'm a cop, you
idiot!''



``It doesn't matter, Luke. The law cannot stop me.''



Luke wondered what the calls meant. They happened every night at
midnight. Luke knew that midnight held special significance to
satanic cults and the criminal element. In his work as a gritty New
York City detective he had made many enemies. He could scarcely
keep track of all the men he put behind bars, let alone which ones
still harbored a grudge.



Luke could barely sleep. In his dreams he was chased by shadows.
Glimpses of dark alleyways and shattered mirrors haunted his
slumber. Luke was near his breaking point. What did it all
mean?



{\em Ring!} The telephone rang. It was midnight again. Heavy beads
of sweat started oozing from Luke's forehead like anchors dropping
from ships at port.



``Who is it?'' Luke answered angrily.



``Now, now, Luke. Don't be so angry. It's just your old
friend.''



``You're no friend.''



``And you're dead, Luke Bavarius. {\em Deeaaaadddd{\ldots}}''



Luke slammed the phone down. His heart was racing like Big Brown in
the Kentucky Derby: fast and determined. Luke took a swig from his
flask. He knew he had to do something. How long could this go on?
Not much longer, Luke thought.



It was time to involve his friends at the station. Luke called in a
favor from Jim Centauri, an expert at tracing phone calls. Jim
hooked his equipment up to Luke's phones, and the two waited until
midnight. Nothing happened.



``Damnit!'' Luke yelled. ``He calls every night. {\em Every
night!}



''It's probably just a prankster, Luke. Don't let it get you down.
Anyway, maybe he got tired of calling you.``



Jim packed up his equipment and headed home. Luke thanked him, but
felt disappointed he had no answers. Then it happened. The thing
Luke was least prepared for.



{\em Ring!}



''Not again!`` Luke yelled, staring at the ringing telephone. He
debated answering, or letting it sing its horrible, shrill song.
Finally, Luke could wait no more. He reached his left hand out and
clutched the phone, squeezing so tight it would die if it were
alive.



''Nice try, Luke. But you'll have to figure out who I am on your
own.``



''Who are you?`` Luke demanded, his voice surging with anger.



''Don't you know, Luke. Don't you know who I am?``



''It's only a matter of time before I find out.``



''Sooner than that, Luke. Don't you recognize my voice?``



Suddenly a horrible realization came over Luke. ''No. No! No!!!`` he
cried out. He looked to his right, and he was holding a second
telephone.



''All this time, Luke. It was you. It was me. It was
{\em us}!"



Luke heard a click. He looked to his left. The telephone in his
left hand was gone. Now it was a cocked Beretta pointed at his
skull. Suddenly he gulped. {\em Click.} 

 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\by{JohnnyThreeToes}


{\em Horrid Transformation}



A man lives in that abandoned house at the end of the street. He is
old and secret, nobody knows that he is in there. Those that do
know don't suspect it is a man, but maybe a dog or a cat living in
the house. There is strange foggy weather over that house. Tonight
thunder rumbles all around the house in the air.



The man sits at his counter and does not say a word. There is no
one to say it to. He is alone. Pain is in his staring eyes. Pain
from loneliness. Depressed pain. A bowl of eaten cereal is in front
of him. He is frowning, not satisfied. Some open bags of dog food
surround him, too.



Horrid thunder surrounds his house and then there is a flash of
lightning. The man has had enough! Enough of this civilization
where people shun him for his talent. They could never understand.
The man grins and puts on a collar. There is another flash of
lightning and by the end of the flash the man has changed into a
dog. He will do what he always does tonight like every night. He
will wander around until somebody takes pity on him and pets him
and feed him. As a homeless human society hates him, but as a dog
he is the greatest thing ever to them. Life is funny that way, he
silently thinks, walking out the door into the lightning. 

 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\by{King Plum the Nth}


This is just too much fun to let go. If it's not kosher to enter
more than once, I apologize and will be happy to remove one of
these. Ben Biddick, you magnificent bastard, thank you for
providing such a rich literary vein to mine. E: correcting an
annoying number of typos.

* * *



{\bf Flow My Tears, the PI Said.}



The kids from the neighborhood pooled their money to hire me. All
the kids on that street in the Bronx, in New York. One slow day I
was getting ready to leave the office a bit early when a kid pushed
open the door with my name, Luke Bavarious, and my job, private
detective, painted in neat black letters on the gray pebbled
glass.



``Mr. Bavarious?'' he said.

``That's what it says on the door, kid.'' He looked
like he was about 12.

``My friends and I need to hire a private detective to find
Mikey.'' He walked across the room trying to look brave,
shoved a hand in his jeans pocket, pulled out a wad of crumpled
\$5's and \$10's, and set them on my desk.



I eyed the dough suspiciously. It looked sticky and damp. I
can't remember ever not wanting to touch money before. I
reached out gently and poked at it. Maybe \$45 bucks. Maybe less. It
wasn't enough to pay for the time it'd take me to take
a piss all over their sorry case. Whatever it was.



``Your mother know you're here, kid?''

``Mister, Mikey's been missing, and all our parents and
the cops say he ran away, but we know he got taken.''

``Taken by what, kid?''

``Taken by a nameless horror, sir.''



I looked at the dough again. ``I charge a hundred and fifty an
hour, kid. In this traffic it'd cost ya another two fifty
five just to get me to set foot in the Bronx.'' The kid looked
like he was going to cry. I swore under my breath, stood, and
grabbed the cash from my desk. Shoving it into my pocket I said,
``Never mind. I'll bill this Mikey's folks for the
difference if I find him alive.'' The kid started sobbing
then. Really hard. While he got it out of his system, I opened my
desk drawer, pulled out my trusty Beretta and checked the
magazine.



Once I got to the Bronx it didn't take me long to find out
what had happened. Sometimes my job calls on me to fight monsters
of a supernatural nature. Sometimes I find myself buried neck deep
in the blackest culture, the world of the gothic and occult. But
sometimes the monsters are more horrible than monsters because
sometimes the monsters are men. And this monster was a man. He was
a homeless pedophile. Mikey wasn't his first but, by god, he
was going to be the last. I pulled my revolver and pointed it at
him,



``This is the end of the line, hobo.''

``You won't kill me, Bavarious! I used to be a cop. Like
your father. It's against the law to kill me no matter how
many kids I raped and killed.''

He had me. I knew, and he know, and my father --- god rest him
--- had known, no matter how many kids you rape and kill it
only warrants murder in certain states and then only after a
lengthy judiciary process. But, looking at poor Mikey's
broken, rotten corpse, I just wasn't sure if any of that
really mattered.



The sick hobo followed my gaze to the body of his most recent
victim.



``Oh, him? Don't worry about him. He liked
it.''



And that's when I snapped. Everything became crystal clear. I
wasn't sure what was right or wrong anymore but there was one
thing I knew for damn sure. Mikey didn't like it.



I pulled my trigger. My Beretta belched hot lead. The shell hitting
the warehouse floor made a sound like a polite cough afterward. A
ragged, bloody hole exploded in the monster's gut. He
stopped, stared at his gory wound and began to vomit. Vomit flowed
from his mouth and, after a second, shot from the bullet wound in
his stomach too. I pulled the trigger again and again, each time it
was less for anger and more for mercy. I perforated his neck. He
kept vomiting. The vomit flowed from his mouth and gut and the hole
in his neck. I put a hole in his head --- right between the
eyes --- his eyes crossed looking up trying to see his death
wound. His body heaved again and again, and vomit poured from his
forehead too. Torrents of blood and bile and breakfast pouring from
four holes on his body, three of them man made.



Finally, I could take it no more, my stomach surrendered and I
vomited. As I vomited, my eyes slipped back to the body of the
monster's latest victim and I wept and my tears commingled
with the vomit. There we stood, the two of us, vomiting. The psudo
mythical hero and the psudo mythical monster over the poor broken
body that had so recently vomited a child's soul into the
afterlife. In a way, we were brothers, in vomit. He fell to his
knees. He died. And, although I stopped vomiting, eventually, I
could not stop sobbing. I cried so hard the flow of my tears washed
the vomit away. 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\by{Yogi Byron}


{\bf Horror D'oeuvres}



I am on the verge of tears by the time I arrive at Espace, as
I'm sure that I won't have a good table. However, the
maitre'd shows me my place, a cozy booth next to an aquarium,
and I feel relief wash over me in an awesome wave. I sit down. The
sound of knives scratching against bone china, however, sets my
nerves on edge. My name is Luke Bavarious. I am a private
detective. I like my work.



Complaints had been trickling in for a little over a year about
cases of food poisoning emanating from this restaurant. I look
carefully over the menu and order a lobster roll with arugula
bedding. I choose this food in particular because it is my
assignment to stop these complaints.



My suspicion is first aroused by a loud belch from the table
directly to my left. The gasses reverberate against the glass of
the aquarium and offend my nostrils. A dark and horrid man is
clutching his stomach, fork gripped tightly in his free hand. This
scene elicits a grimace of pain from his face, and, suddenly, he
shouts violently, jabbing the fork into his abdomen. A stream of
vile stomach acid and gastric juices billow forth, burning his
hands in acidic bile and causing him to vomit from behind pursed
lips onto the tablecloth in front of him. My Beretta is already
drawn as I attempt to calm the surprised crowd that is gaping at
the food-poisoned man. His wife has urinated onto the carpet and is
troubled by unwilling spasms that are shaking her body. I fire a
round into the plate of food that sits between them, while
grimacing. I snatch the ejected shell from my Beretta like
it's a flying bumblebee and place it in my mouth, clamping
down on the brass with my teeth to dull the pain of my miserable
and human, all too human, existence.



Blood is now mixing with the bile and urine into a disastrous
chemical. I fire a round with my Beretta into the man, who is
gripping the tablecloth in pain. He giggles as he is relieved of
his cruel fate, lapsing into the sweet embrace of untimely death. I
draw a bead on his poor wife, who is sitting in a pile of her own
waste like a squalid dog or cat. I fire twice. Three shells hit the
concrete. ``You!'' I yell at a waiter hiding behind the
aquarium. ``Let me speak to your manager!''



He wipes his miserable face with a cloth. ``Beggin' your
pardon, but{\ldots}I am the manager,'' he says. I motion
towards the table with my Beretta. ``Sit down.'' I say.
While he takes his seat before the lobster roll and arugula, I
catch a glimpse of myself reflected in the glass of the aquarium. A
white shirt and cummerbund are smoothed elegantly around my
midsection, and on my right side is a gleaming nametag. ``Luke
Bavarious, Head Waiter, Espace.'' Suddenly, I am sobbing. 

 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{I am NOT Luke Bavarius}
\by{Funk In Shoe}


Interviewee: LARRY BAVARIUS - 05/05/09









So what do you want to know?



{\em Question.}



Okay, see, this is something we're going to have to address
before it starts bugging me: You need to relax.

I see you're tensing up there, a little already, why is this?
When we spoke on the phone earlier - when you called me up and
asked for this interview and I told you it would be no problem and
to come right over whenever you saw fit --- earlier you came
off so easy going, on the phone. I made coffee, did I not?

Is this just a matter of you being the kind of person who really
knows her way around a phone but tends to come off sort of skittish
in person? No? Could you put that down Bic pen already? You know
the clicking, and all. I get skittish, too. Honestly it's
alright.

You DO seem horribly tense. I am not, let me assure you, Mr. Ehl
Bee. There is no need to go all star struck on me. I am as much of
a nobody as you are, probably more of a nobody.

Put the pen down, honey --- in lieu of that, just stop with the
clicking, please. I'm sorry. Do carry on.



{\em Question}.



Well the thing is, the way you're phrasing that is you want
me to tell you a certain mapped set of details about myself;
details you're likely more acutely familiar with than I am
myself.

I don't know that I am related to Luke, as such. We
haven't had much to do with each other since he published
that{\ldots} Oh. Don't make that face.

Okay, okay. Fine. So I am. Related. He's what you'd
call my identical half brother. I know right? It's a weird
way to put it and I apologize; I'm not trying to come off as
overly dramatic here or trying to yank you around or make myself
appear interesting or anything like that, really, it's just a
sort of neat way of recapping our shared genealogy.

And so but yes, I am a couple of years older than Luke and yes, we
do share a good amount of absolutely top notch DNA. I've
never been able to figure out exactly how much, you know,
percentagewise et cetera, it's sort of a stupendously tricky
prospect.



{\em Question.}



Because we got, obviously, the same mom and but so, as fate would
have it, different dads. Tricky, because while my own dear sweet
padre is an entity completely separated from Luke's ditto,
they are, nonetheless, identical twins. This, their twin-inicity,
if you will, is what has made all my attempts at coming to terms
with the whole DNA snafu so far pretty frustrating. By now
I've pretty much just given up. This, having the same mother
and two different fathers who happen to be {\em appear} completely
identical, is probably also why you're still fidgeting with
that {\em God damned Bic}, even when I asked you politely and
repeatedly to put it down, because it's freaking me
out.

I am not-I-repeat-not Luke Bavarius; and I am going to take the
fact that you're still not quite sure whether to believe me
or not on that, as a compliment that I am looking better than my
usual best today.



{\em Question.}



Well because look at me. Check out thith. See thith? Ow. This is
what the not-so-PC-crowd calls a hare lip. It's been fixed
up, but it's pretty obvious with the scar and all, especially
on the inside of the lip. Did you ever see a jacket photo of our
boy Luke with a scar like this? This male pattern baldness thing?
Luke dodged that bullet too. Where I'm 5.0 he's a good
6.1. It's a mystery, really. You should{\ldots}



Question.



{\ldots}I'm not finished, you should see our respective
family photos. For some reason he just turned out like a late and
slightly improved version of yours truly. Same parents, just
slightly better. It's bizarre. By the looks of it it's
the same parents in the same photo studio, doing the same awkward
pose with our respective and identical dads in the background, arms
wrapped around mom, wearing all red. Bizarre because so the kid in
the foreground is basically either me or, like, a really, really
pretty and tall and attractive {\em enhancement}of me. It's
just weird. I am not Luke. Convinced? Want me to whip out the
photos? No?



{\em Question}



Well I'm two years older. Dad and Not-Dad moved here together
and started a used car dealership on the eastside. You are aware of
all this, I am sure. Any profiler worth her salt, writing for such
a major magazine, will be aware of this. So but they moved here,
yes, opened up their dealership and started making good money right
off the bat. It was a couple of years after the bubble burst and
Dad and his brother were lucky-slash-clever enough to start their
business at a time when people were just starting to make money
again, but were still hesitant about, you know, spending it.
Everybody and their mom bought used cars back in those days.

And so Dad meets our mom some forty-odd years ago and they fall in
love pretty quick and Dad moves out of whatever east side apartment
he's sharing with his brother at the time, and in with
mom.



{\em Question}.



From what I've been able to ascertain, I came around some two
years later. Give or take. You'll have to --- stop
clicking --- you'll have to bear with me on the details.
At this point, the dealership is running like greased clockwork and
both Dad and Not-Dad are pulling in some serious moolah and Dad,
Not-Dad and mom start getting invited to you know, get-togethers,
shindigs, box socials, that sort of jazz around town with the
movers and shakers of whatever post-recession high society was in
function back in those days.



{\em Question}.



Well it started out as a sort of joke, you know.
Don't-You-Drink-Too-Much-Sweetie-Or-You'll-Get-Us-Mixed
up. Shits and giggles and lots of fun at parties with my Dad and
his brother showing up in identical suits and my mom pretending to
accidentally kiss the wrong clone et cetera.

Shits and giggles right up until, and you've seen this
coming, right up until the three of them actually go and get so
drunk that my Dad passes out in a bathroom at some fundraiser,
slumped over a toilet for hours so that to this day he's got
horrible problems with his back, and Mom goes and sticks her tongue
down the throat of Not-Dad by mistake and by the time he gets to
object they're both too drunk to even care and mom decides
right there that for whatever reason, Not-Dad is a much better
kisser than poor, passed out Dad ever was.



{\em Question.}



I don't remember much, except for him drinking a whole lot
and never wearing anything but his underwear around the house,
really. And the yelling-slash-stomping.

I remember asking him, once, like we're talking age three or
four here, where Mom had gone and he yelled at me. My dad is sort
of a dick. I told him he needed to stop yelling at me. He
didn't listen. I told him kids need to be respected and
listened to. No dice.

He would have to be, a dick, you know, to stick me with the short
end of the DNA stick like he's done. Thith fucking thplith
lip! Ow!

And so but Mom moves in with Not-Dad and lo and fucking behold THEY
spawn a kid too.



{\em Question}.



Yes. Luke. I see you have fathomed the basic concept of
{\em listening}, I am highly impressed. May I continue? Thank
you.

So naturally, with my Mom gone off to shack up with his Brother,
there's no fucking way in hell Dad's dealership is going to
stay afloat, these two guys can't stand the sight of each
other.



{\em Question}.



Just {\em imagine} that! It's like some bizarro-universe
incarnation of self-loathing. Imagine waking up, hung over, and
stumbling into the bathroom, looking into the mirror and seeing the
face of the guy your wife is currently fucking, who is not you.
Then, suddenly, you are sobbing. One cannot even be-fucking-GIN to
fathom{\ldots}

So yeah, anyway, there was that.



{\em Question}.



Well so they split it up. Put down a fuck-all huge chain fence
right down the middle of the store and the lot. Split the whole
place in two halves that were pretty much identical except for the
sign out front. Dad got the BAVA half, Not-Dad got RIUS.

And, foreseeably, they started harassing each other pretty much
right off the bat. He'd bring me with him to work every now
and then. I'd hang around in the lot and play in the oldest
most derelict cars, the ones he couldn't seem to get rid of
anyway, and I'd watch Dad scream his lungs off, whenever a
potential customer went the ``wrong'', if you will, way
around the fence and into the RIUS-lot.



{\em Question}.



Just insane stuff; like he had this thing where he'd jump
onto the fence and hang there shaking it like a fucking deranged
chimp, rattling the metal, shouting how the guy who owned the
RIUS-lot was a no-good-for-nothing wife-stealer who also happened
to sell exceptionally horrible cars that no man with half a fucking
brain would ever want to et cetera et cetera.



{\em Question}.



Well Not-Dad would do the exact same routine whenever one went into
the BAVA lot. Sticks and stones. I'm not going to sit here and
assign blame.



{\em Question}.



She never came around. I haven't seen her since she walked
out. He did bring Luke a whole bunch of times though. We'd
play. In the beginning, we'd play. There was always this
acute{\ldots} weirdness about it. Playing with him. Like seeing
yourself in a funhouse mirror that somehow made you just an eerily
tiny bit prettier than you are. We had to stop when they put up the
actual WALL --- as in the brick wall.



{\em Question}.



They put it up in a moment of clarity I guess? Business had gone
way downhill for both of them, what with all the shouting and
fence-rattling and whathaveyou. It was sort of a necessity. They
even split the bill.



{\em Question}.



Ah well so but it didn't stop there. Because after the wall,
Dad got into this habit of sneaking into the RIUS-lot and greeting
customers like he owned the place; he might as well could have,
it's not like anybody could tell the difference.

So he'd sneak into the RIUS-lot and greet potential buyers
and just do a hell of a good job at being the very worst salesman
he could possibly be, to scare them off.

He'd make a show of keeping an open bottle of Jack on his
person while talking to customers, luridly coming on to any female
buyers slash wives slash children --- this earned him a couple
of impressive beatings that had him just look an AWFUL lot like the
kind of person you would not buy a car from --- he would follow
the buyer around the RIUS-lot going ``oh heavens no, you
wouldn't want to buy THAT; two words: DEATH TRAPS'' et
cetera --- until Not-Dad would finally spot him from inside the
dealership and coming rushing it, swearing and screaming,
effectively scaring off pretty much everybody.

Of course, after a week or so, Not-Dad would reciprocate by pulling
the exact same kinds of stunts at the BAVA-lot and for a while
there everything was absolutely, completely apeshit. Care for a
drink?



{\em Question}.



Well Dad started getting up early in the morning to beat Not-Dad to
work and lurk around Not-Dad's lot, impersonating him.
Not-Dad started doing the exact same thing. After a year or so, Dad
would clock in at Not-Dad's lot at seven in the morning and
visa versa. After a year and a half, they'd pretty much
swapped lots and spent most of their days scaring off the other's
half's customers. They stopped selling cars over the course of a
couple of months, in order to make sure the other didn't sell any
either.



{\em Question}.



Well they went bankrupt. Both of them, and spectacularly so.



{\em Question}.



And so Luke beat me to it, is the gist of my story. He wrote this
entire thing down faster and much more eloquently than I found
myself able to. And don't think I did not try. I tried. The
day I heard that he'd gotten published, I had two hundred and
fifty type-written pages and was just about to finish up my own
rendition.



{\em Question}.



Just another matter in which Luke Bavarius has proved to be that
teeny, tiny bit better than me, I am afraid. He's the genius,
he's the author. He's the one with his god damed
non-split face on the cover of dust-jackets everywhere. And so here
we are. And here {\em you} are. Digging up the dirt for your
fucking profile.



{\em Question}.



I don't even fucking care. You think I haven't told
this story? Who {\em told} you this story? Was it Luke? Mr. Ehl
Bee, mr. Writing-under-a-Pseudonym-to-be-artsy-Biddick, with his
prodigious talent and his intense, {\em fucking} eyebrows that he
probably picks like a bitch? Was it? It wasn't. It was me. I
want you to stand up, walk over to that bookshelf right there. Go
ahead. Pull out his book. It's right there. Don't think
I haven't bought it. I'm not your average bitter fucking
idiot. I have money to spend. Pull it out of the shelf and look at
him, on the dust jacket. Monochrome and unsplit, brooding. Go
ahead. It's me.

Am I not the butt of a cruel, genealogical joke? My father
abandoned by love. I myself abanoned by fate. You want horror? Look
at his picture, then at me.

Do you not see this? Has the whole god forsaken world gone mad? I
am telling you this story. I am the first incarnation of this
story. Who is this Luke Bavarius? Go head. Look at his picture.
Look at this Davidesque, seemingly retouched rendition of yours
truly. See all that is shared between us. Am I not the narrator? I
am L. Bavarius. Do I not deserve recognition? Look at his
face.

Pick it up. Go the fuck ahead. 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\by{Zarimus}


{\bf Little Men}



``It has happened again.'' moaned the dark clad priest, his rosary
clenched in his left hand. With his right hand he held the old
phone handset indicative of the respectable poverty of the church
office. ``Can you come right away?'' Father Dennis almost sobbed into
the phone.

Evidently what he heard comforted him and he hung up with a
relieved laugh. He turned and smiled down at the silent young boy
playing with some small figures in the corner of the room. Father
Dennis stepped forward and patted the boy on the head in a friendly
way. ``Don't worry son, the detective will find out who brutally
murdered your father and that man in the alley.''

The boy did not look up, he was still playing with the small toys,
little metal figurines of soldiers and knights and trolls he had
been carrying in a small velvet purple bag ever since he and his
mother had arrived at the church.

In a short while there was a knock at the door and Father Dennis
rose to greet the gray coated figure who introduced himself as
Detective Luke Bavarious. ``The body is in the alley behind the
church building.'' offered Father Dennis. ``You remember Nick,
Detective?'' he said, pointing at the silent boy.

``Yes I do Father Dennis.'' said Luke Bavarious, gazing with intent
at the boy. ``Has he spoken yet?'' ``Not since his father was brutally
torn apart, just like the man in the alley.'' Father Dennis faced
the grim detective squarely. ``Is it a serial killer?''

Detective Bavarious said grimly, ``We don't know yet. Let me have a
look at that body.''

In the alleyway Luke nodded to the policeman guarding the crime
scene. ``Evening Bob. Know anything yet?''

The policeman shrugged. ``Just that he died in a lot of blood. His
arms ripped off.'' Luke raised an eyebrow in surprise. ``Just like
the boy's father. Who was this guy?'' The policeman didn't know, as
it turned out. Detective Bavarious wondered if they'd ever find out
who was responsible.

Back in the church office, the boy Nicholas carefully set down a
small metal figurine that resembled a policeman. He then opened a
tiny wooden box he took from his velvet bag and gazed silently at
the two broken figurines it held. Both had their arms torn off. The
boy picked up the policeman figurine and with a swift motion, tore
off both arms.

From the alley behind the church, he could already hear the
screaming.



{\bf The End} 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\by{CannedMacabre}


{\bf For the Children}



Norma's Diner is a horrible place to get a cup of joe. The only
reason I was there was to meet a mysterious client that had
insisted on anonymity. He had reached me twice by phone in the past
three weeks and only identified himself as Mr. M. I told him that I
would only take the case if we met face to face. Mr. M contacted me
again this morning by text message to say that we should meet here
at Norma's at 10:30 sharp.



Its now 10:45.



I'm Luke Bavarious, Private Detective, and I don't take a case
without knowing the client, and I don't like to wait.



The waitress pours me another cup of swill as I look over my notes
on Mr. M's case. He says he is being stalked and that threatening
messages are being sent to his e-mail and voice mail. He hints at
the fact that some people are trying to blackmail him. He even
casually ponders whether his life may be in danger. Its really not
much to go on but with the clock ticking, I am beginning to wonder
if someone might have already done the guy in.



Its 11:00.



The only reason that I haven't gotten up and walked out yet is that
a manila envelope with five 100 dollar bills was slipped under my
door this morning with the words ``from M'' on it. I figured that I
would at least wait out the hour before going about my day. Maybe I
will choke down another cup of the vomit they call coffee in this
dump. As I raise the cracked mug to my mouth I hear the little bell
on the door sound followed by a loud voice:



``HEY! What I tell you about those friggin skates in my
restaurant?''

I turn to see a smallish kid with a stunned look on his face nearly
crap himself. He has a giant book bag on his back and is wearing
those shoes with the wheels in the heels. Heelers? Heelies?



``S-sorry mister, I forgot.'' He says sheepishly and hangs his head
down in the embarrassment of all eyes being on him. He sits down at
the table across from me and takes out some school books and a
notebook. The waitress brings him a cherry Coke and puts a hand on
his shoulder for just a moment, then goes back to her cigarette
burning at the counter.



Poor kid.



I look down at my watch for a second and notice that ``M'' is now a
full hour late when I hear that sheepish little voice again.



``Sir, can I talk to you for a moment?'' the kid is right next to me
with his bag hanging half way off his shoulder.



``Uhhh{\ldots}Listen kid{\ldots}'' I start to say some rhetorical crap about
being a busy man or having some place to be, but something in my
gut tells me that not enough grown ups have made time for this
kid.



``You know what{\ldots}Yeah. Sure kid, have a seat.''

His eyes light up and he throws his bag into the seat next to me
and grabs his Coke form the other table.



``You're a private dick, right?'' The kid says.



``Uh{\ldots}yeah, Detective.'' I respond.



``Cooooool, I wanna be a P.I. too when I grow up. You carry a
gun?''



``Yeah, a Beretta, but it ain't all its cracked up to be. Sometimes
you gotta deal with a lot of scumballs and sometimes you just can't
help the people that hire you.'' I wasn't gonna BS the kid. If he
was keen on getting into this line of work, he better know
{\em exactly} what he was getting into.



``Besides, even if you do solve the case, you get the bad guy and he
gets what is coming to him, it can leave a bad taste in your
mouth.''



He nodded a bit in agreement and turned his eyes down towards his
drink. He was quiet for a moment and then suddenly he spoke in a
voice that was not at all sheepish or meek:



``Detective Bavarious, Mr. M wont be joining you today.'' he said in
a calm, controlled voice. ``In fact, I doubt that Mr. M will be
contacting you again at all.'' This statement chilled me to my bones
and instinctively I lowered one hand under the table to the Beretta
clipped to my belt.



I was all ears.



``You see, Det. Bavarious, Mr. M was being harassed, stalked and
blackmailed. and I am the one who was doing these things to him.''
The kid's voice was deeper now, and I must admit that he commanded
my attention as few others could.



``I targeted Mr. M for the crimes that he has committed against
children. He is a child molester and a murderer and I wish to see
him imprisoned for these crimes{\ldots}''



``Wait,'' I interrupted. ``A twelve year old kid has a man running so
scared that he pays a private investigator to find out who is
harassing him?''



``Det. Bavarious, my name is Nathaniel Stilling. On my twelfth
birthday my father beat me within an inch of my life and I spent
the next 4 months in a hospital. When I awoke from my coma I
promised myself two things: I would protect innocent children from
harm, and I would never have another birthday. That was 57 years
ago.''



I had no choice to believe him. From the beginning of our
conversation I had felt that I was in the presence of a wiser, more
virtuous man then myself. So when this kid, this small, sheepish
child told me he is a 69 year old man{\ldots} I believed him.



``Look son,'' he continued, ``I know that you have the power to put
this monster away.'' With that he pushed a DVD in an unmarked case
across the table.



``I wouldn't get curious about whats on that disc if I were you. The
things that man has done are not meant for our eyes.'' He slid out
of his chair and grabbed his book bag.



``Oh{\ldots} and Mr. M's real name is Michael Wilkinson. He is a biology
teacher at Washington Junior High School. When you give the cops
the disc, just tell them that it was given to you by another PI
that knew who your client is.''



The boy then gave himself a big push on one foot and skated towards
the door on his heel wheel.



``Dammit kid! I'm gonna skin your hide!'' The ape behind the counter
screamed.



``S-sorry mister{\ldots}I forgot again.''



The End. 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\by{BenBiddick}


you guys are phenomenal. I started going through these and am
loving it. dont worry about it Funk in Shoe. I'm just glad you put
something together for this event. Keep going all! 

 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\by{Ridgely\_Fan}


{\bf ****Part 1 of: The Cocoon****}



This place was new.



My eyes took several seconds to adjust to the dim light, while I
slowly drank in my surroundings. My head was throbbing, and my
throat was parched. And it was cold in here. Very, very cold.



I seemed to be in some sort of dungeon, as comical and absurd as
that sounds. Or the kind of thing an insane millionaire would build
to approximate a dungeon. Instead of cold, damp stone walls, there
were cold steel surfaces and unfinished concrete floors. Instead of
a brazier in the hallway, the ambient lighting was set low. They
got the stink right though, and of course the barred entryway that
looked like the door of a jail cell.



I began going through my head, trying to figure out whom I'd
pissed off enough to get myself into a place like this, when I
heard a voice from a hidden loudspeaker.



``Well well Mr. Landon. I see you're awake. I hope you
like your surroundings, you'll be here for some
time.''



``Who are you?'' I shouted. My voice was harsh and raspy.
``Why did you put me here?'' I was on the verge of tears.
If this was a prank or a trick, it was going way too far.



``My name is Bravarious. Luke Bravarious. It's my job to
keep the good people of this city safe, and that means keeping
horrid creatures like you locked up down here.''



This had to be a joke. But if it was a joke, why go to such
lengths? I put my hand to my forehead to think. There was something
slick there. As I retracted my hand I saw it: blood. This crazy
asshole must have knocked me unconscious to bring me here. The
speaker started again:



``Don't worry Mr. Landon, your headache shall soon pass.
Your kind heals quickly, even in your cocoon state. I can see
you're confused. All shall become clear shortly.''



This was some Silence of the Lambs shit. I remembered back to that
movie, the FBI agent said it was smart to get the serial killer to
recognize his victims as human. Maybe I can do something like that
here{\ldots}



``Mr. Bravarious, I can barely hear you through the speaker.
Why don't you come down and talk to me through the bars?
I'd like to talk man to man anyway.''



There was some silence. He seemed to be thinking it over. After a
short time (surprisingly short) I heard a familiar voice in the
doorway.



``I don't see a problem with that.'' 

 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\by{Ridgely\_Fan}


{\bf **** Part 2 of: The Cocoon****}



The man in the doorway was short and stocky. Pudgy even, though it
was hard to tell in his trenchcoat. His hair was thinning, and had
been clumsily combed to the side. His face shone from sweat or
grease. This guy needed a bath. At least it gave me some idea of
who I was dealing with.



``Mr. Bravarious, why did you take me here? Is this a joke? If
it is, I'll keep it between just us guys, you got me good.
Just let me go.''



I hoped he couldn't hear the fear or despair in my
voice.



``I can tell that you're scared Mr. Landon, but that
fear too will pass, as you emerge from your cocoon.''



This guy was crazy, but he was not going to be easy to manipulate.
I know it's not a good idea to feed into the fantasy of a
schizophrenic or crazy person, but I had to know what he was
talking about.



``What do you mean cocoon? Is this some metaphorical
thing?''



``Not exactly, Mr. Landon. You are one of an ancient race. A
race that has hunted humans for millennia. A predator that acts
like a parasite. Your kind leave its offspring in the form of a
human for humans to raise. When that offspring reaches adulthood,
it abandons its cocoon and emerges a hunter. Fast, powerful,
unstoppable, and hungry.



``I'm saying that you are one of these offspring. In just a
few weeks you will emerge. But instead of hunting humans, you will
stay here. I have prepared food for you.''



Bravarious pointed to a corner of the room, where I could now make
out a pile of decaying meat scraps. That explained the cold and the
stench. I wretched and nearly threw up.



``That's disgusting!''



Bravarious appeared calm. ``I thought you liked uncooked
meat.''



``I like a rare steak, not a rotting pile!''



``So your transformation has not yet started.''



It seemed like he had some twisted explanation for
everything.



``How do you even know I'm one of these
things?''



Bravarious started to look self-satisfied. Maybe I'd struck
the right chord.



``It was a simple matter of checking the records at an
orphanage where the last of your kind was known to feed. You had
certain{\ldots} traits. I confirmed these traits by watching you
for the last two weeks. There is no uncertainty Mr. Landon, you are
the monster I was assigned to capture.''



I hadn't seen anyone following me. Who knows if he really
had. It was just as likely that he was lying or had just imagined
it.



Still, how did he know I was adopted? Did he know about my suicide
attempts as a youth, about me dreaming of harming the others in the
orphanage, my insane pleas for them to kill me? The years of
therapy that my adopted parents paid for? How could he know? He
spoke again before I could ask.



``Now Mr. Landon I have other duties to attend here. I must
assume you'll be alright.''



``No!''



I had to think of something quickly. I rubbed my forehead
absentmindedly, breaking the scab that had formed there. Blood
flowed anew. I had an idea.



``Mr. Bravarious, I haven't turned into one of these
monsters yet. That means I'm still human. I'm human and
I'm hurt, and I might die of thirst. Please just give me some
water and some bandages before you go.''



He appeared to think this over very carefully. ``Very well,
you cannot harm me in that state. I shall return
shortly.''



He was right, I couldn't hurt him. What was I going to do? I
started feeling angry at my predicament, angry at this crazy
bastard for locking me up. The anger dissolved my fear. I had to do
something myself, I couldn't wait for the police or
whoever.



I heard footsteps, and crept beside the doorway.



``Mr. Landon, I am leaving your supplies beside the
do-``



Bravarious didn't get a chance to finish his sentence before
I grabbed him through the bars. He struggled at first, but I put a
stop to that by smashing his face into the door several times. An
eye for an eye.



I found the key to the dungeon in his pocket. The maniac also had
an old filthy Beretta, loaded and with the safety off.



As I let myself out and stepped into the hallway, I slid Bravarious
into the room to take my place. I was feeling much better. The joy
at my freedom, and my survival, was starting to cure my
headache.



Just before I closed the door, I smelled the meat in the corner. I
hadn't eaten for days. I started salivating. Looking down at
Bravarious, I felt a new urge. An urge that was new to me and yet
felt timeless. Prehistoric. This all made sense now. Yes, he was
right, it would be several weeks before I emerged, but he
didn't realize that before that came the hunger. I would need
to feed before my transformation. And so feed I did. 

 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\by{Ridgely\_Fan}


Oops.

Uh, my story features Luke Bavarious' distant Romanian cousin, Luke
Bravarious, also private investigator.



Also:

Edited to include the main theme and to fix some grammatical
problems. 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\by{raptorred}


This turned out a lot longer than I expected, but I had more fun
writing it than I'm willing to admit. {\em Except I just
did.}



{\bf THE BLOOD GAME}



Once there lived a maniacally demented hag. The kind of person
whose cruelty made the blood run cold and the nose hairs stand on
end. She made her dwelling in a blood-red house in suburbia, rife
with infantile girlie crap like odiferous flowers. And those stupid
little porcelain cats which weren't even real cats so they
didn't have blood or guts or anything in them. Also it was
1992.



Fortunately for her, there was one element in her dark life that
kept her existence from being as miserable a waste as a Slip
`n' Slide in December: her perfect son, Luke. Luke was
the age of a 12-year-old, with brown hair and searing obsidian eyes
that were like pits down into his soul and his blood-filled
innards. As sons go, Luke was practically the best. He sometimes
took the trash out. And he hardly ever skipped school or beat up
his stupid little sister until she cried and pooped her pants with
grimy blossoms of baby turds which were sometimes reddish enough to
pretend they were blood. But they weren't.



Luke hardly ever asked for anything. At least not unless he really
really super duper wanted it. And every quivering droplet of blood
in his body boiled with agonizing desire for a Sega Genesis with
Sonic the Hedgehog 2. He wanted it so bad he could puke. Puke until
he shrieked with the euphoric laughter brought on by true
happiness. A happiness he would never know. Not if his scheming
mother had her way.



``Honey, we can't afford it right now,''
Luke's mother hissed from her blood-red lips. ``Maybe
for Christmas.''



But Luke was as clever as he was dashing. He could tell she
didn't really care. She didn't even look up from the
boring pieces of paper covering the kitchen table. She spent most
of her time with those papyrus slips. Far more than she ever did
with him. Luke had had enough.



``You will pay for your cruelty,'' he announced. His
veins bulged with brutal wrath. Blood wrath.



``Lucas Theodore Bavarious! Go to your room!!'' If he
could have, he would have vomited blood in her ugly face. If you
could call the grotesque mask of suburbia a face. But she was on
the other side of the kitchen so he'd probably just get it
all over the floor or something. So he went to his room.



In his room, Luke's eyes went dark, darker than the slick
polish of a brand new 16-bit gaming machine that had his name on
it. His heart contorted into something like a wad of coagulated
bubble gum. Except it wasn't really that much like bubble
gum, it was blacker and more pulsating and filled with the
trembling sobs of jillions of powerless kids before him who had
been denied justice. Also it probably would not have tasted like
watermelons, which was Luke's favorite flavor. It would have
tasted like blood.



Somewhere in Mobius, Sonic the Hedgehog heard his cry.



That night, Luke's mother went to bed. Nobody knew it, but
she had a twisted secret that was vile and also murky. To get ready
for bed, she took out a big secret pan of polish. The polish was
made out of blood. She polished all of the skulls of little adopted
boys who died because they were denied the latest in awesome gaming
technology. She collected little boys like this for a long time in
secret. It was because she was crazy and evil and liked breaking
kids' spirits and tricking them into thinking she loved them.
But Luke was smart. He already knew such a selfish blood creature
couldn't be his real mom.



But when she got into her bed, she heard a sound. It was a strange
sound. It sounded like buttons dribbling blood, only spookier. Then
she heard another, even stranger sound. It was the ghostly wail of
a Super Spin Dash, which was this awesome new move that they just
put in the new Sonic game that lets you go up hills and stuff and
any mom that wasn't pure evil would understand why her kid
had to have it. If a kid didn't have something like that, the
blood that coursed through his slimy organs would start shaking.
And the blood was so angry and so filled with sorrowful hate that
it would also turn into acid. Then his guts would get bigger and
bigger like water balloons, only water balloons filled with blood
instead of water. Until they exploded, spewing blood and guts and
acid everywhere. Then the whole room would melt and the mom's
stupid floral print wallpaper would be ruined.



That's what happened to those other boys.



``Who's there?'' she asked, because she
didn't know what a Super Spin Dash sounded like. If she were
a good mom who bought her son stuff, she would know. Maybe it would
have been enough to save her. She was so scared that a little bit
of blood trickled out of her nose. It smelled like blood.



Then something see-through flickered in the darkness. It was like a
whip, but really it was a cord attached to a controller. The
controller was attached to a terrifyingly awesome ghost Sega
Genesis. The ghost of the console that Luke should have
owned.



Luke's mom tried to scream, but she was so scared that her
blood started to gush into her throat. She gurgled on bloody vomit
as two controllers (because Luke read in a magazine that Sonic 2
would have {\em two player mode} and it'd be more awesome
than sliced blood and that was one of like a million reasons he had
to have it or he would implode into a pile of bloody guts) thrashed
out of the darkness and wound themselves around her neck. Then one
controller started whipping her in the head. She started crying
because it hurt. Then the controller started hitting her harder.
She cried bloody tears this time because it hurt even more. They
mixed with the bloody puke to make a sort of martini that was two
parts blood, one part tears, one part vomit. And all parts
terror.



Then she tried to tear the controller out of the socket. But the
Sega Genesis is way too well made for a mere Mom to be able to
destroy it. It laughed at her with ghost beeps as her skin started
oozing blood for some reason that was really gross and scary. Then
one controller wound itself around her feet. The other kept winding
around her head. Her hair was full of blood and vomit and tears and
spiders for some reason. The Sega Genesis pulled and pulled and
pulled.



``Luke,'' his mom gasped, a trickle of vomit seeping from
her hypothalamus. It made a gooey line in the blood that was
rupturing form her pores. ``I am so sorry.''



But it was too late. The Sega Genesis pulled her whole body in
half. Out of it fell a huge brick of hardened vomit-tear-blood that
was shaped like the inside of her body. It was because she'd
had so much vomit and blood and tears inside of her that it melted
all of her guts and hardened into a shell. The shell was shaped
exactly like a mean old mom. But the Sega Genesis wasn't
finished.



A bell tolled in the distance. The siren for the Red Cross's
Bloodmobile whistled in the night. And the shell started shifting.
When Luke went into his mom's room the next day, there was no
sign of her. Instead was a perfect Sega Genesis. Made entirely from
hard blood.



From the depths of his mom's dark closet a voice echoed. A
voice that sounded strangely like the Coolest Blue Dude with
`tude around:



{\em ``Kids need to be listened to and
respected.''}



Suddenly, Tails was sobbing. 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\by{Lorentz Factor}


Mind you, I've not done any creative writing since I was thirteen.
But figured, what the hell.



{\bf It's just me, 'Luke'}



I stepped from the shadows, those last shadows that were hastily
escaping as the sun pours over the cityscape. I had awoken only
moments ago, the sun's light entering my head like the scream of a
newborn during a hangover. I could not remember what had happened.
I was working on a case in the north end of the city, the details
still not coming to me. I remember driving, perhaps I had an
accident. I simply could not remember. Retrieving my shades from my
breast pocket to halt the screaming rays of sunlight that were
pounding at my spinning head, I noticed a door in side of the
building I had found myself next to. I needed a place to sit while
I waited off this pain in my skull.



Opening the door, I was greeted with soft music from the big beat
band inside what appeared to be a small bar. Odd time for them to
be playing, I thought, but, never mind. I sat down at a table near
the door and grabbed the drink list. Interesting, they only seem to
serve whiskey sours{\ldots}fine by me, it's all I drink anyhow. After
ordering, the bartender returned with my drink, I asked him, ``Where
exactly am I?'' He chuckled, ``It's only 11pm and you're already
smashed,'' he continued his guffaws as he wandered back to his bar.
Sipping my drink, something the bar tender had said bothered me.
``11pm,'' but the sun had just come up; I checked my watch and it
said nine thirty-eight. My watch breaking wasn't new to me, I get
into rough spots quite often that my watch never makes it out of. I
decided I needed to find my way back to the office.



As I left the bar it seemed that twilight was approaching. My car
was nowhere to be found. I walked south on the street looking for
anything that seemed familiar, when I came to an alley. Something
about this alley. I still could not remember. I walked towards the
opening between the two buildings to the alley. I heard a voice
behind me, ``Sir, I'm sure you don't want to go that way, won't you
continue down the street?'' It was a small kid, a strangely dressed
child. His pants were a grayish knee length trouser held up by
thick suspenders that draped over his cotton shirt. His boots also
were odd, laced up they met the short trousers leaving only an inch
of bare skin between them. ``Move along kid, I think this alley is
important.'' I told him. ``I'm thinkin' sir, you're going to be
sorry,'' he was saying as he wandered off around an
intersection.



After my short talk with the child, I realized the sun had already
dropped behind the buildings to my west. I tried to get my
bearings. I wandered into the alley and the pounding in my head had
become so intense that my knees buckled. I tried to cry out in
pain, though the intensity of it all left me with little strength
and the sound escaped as more of a gurgle. The pain in my head
retreated with the sun's last light. I slowly stood from the fetal
ball I'd formed in my pain. As I was was rising a light shown
through the ingress of the alleyway. It looked like two headlights,
they were bright and I turned away. A man approached I heard him
shuffling through the broken stone of the ground in this ill kept
thoroughfare.



``You there! What are you doing? Turn around!''. These words, that
voice. It all came back to me. ``Beggin' your pardon, but{\ldots} you
don't want me to turn around,'' I told him. ``Sure I do. I got a
pistol pointed at your back so ya better.'' I knew what he was in
for, I myself have seen this. It was my fault, it was his fault. If
I kill him, I won't have to go through this again. ``Okay, you asked
for it,'' I told him as I approached still hanging to the shadows.
He asked me to step out of the dark, what the hell. My life would
end soon maybe I can stop this cycle here and now. As I approached
the horror that twisted his face was intense. I doubt he recognized
me, I hadn't myself at first. I rushed him, hoping to reach him
before he fired his Beretta. I lunged as the first slug pierced my
skull. Several more rounds pierced me, the pain offset by my wish
to end this cyclic horror. Blackness was encroaching on my vision.
Things began to swim. I tried to warn him, but I doubt he
understood the wet blood filled, ``I am you, I am Luke
Bavarious{\ldots}''. I collided with him we smashed into a window.
Everything went dark. My nightmare was over, but had also just
begun. 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\by{BatsBjorg}


Hope nobody else took this tactic -- I read through a lot of the
excellent and awesome entires in the thread, but wanted to get this
posted before time ran out. Without further ado:



{\bf The Horrid Beginning of It All}



Eleven-year-old Luke Bavarious stood frozen in the doorway to his
bedroom. He couldn't turn the light on. He wouldn't be
able to turn it back off from his bed. But he couldn't get to
his bed without the light on. He was in a real pickel.



``Dad!'' Luke Bavarious yelled. Another year, another
month maybe, and he'd be too old to yell for his daddy. But
yell he did. ``Dad?''



Luke Bavarious could hear the sounds of the Mets game from the
living room. He could also hear the sound of another Coors popping
open. His father's alcoholism had become publicly known sense
his mother had left. Luke Bavarious thought his father was probably
about halfway through his Coors consumption. The Coors consumption
varied based on how poorly the Mets were playing, and right now
they were on a hell of a skid. Luke Bavarious got a not-unwelcome
rush from thinking the word ``hell.'' Hell, hell, hell,
he thought. Shit, hell.



``DAD?'' One more time.



``GODDAMMIT Luke! What is it now. I toldja gota bed fiteen
mints ago!'' Maybe more than halfway through the night's
Coors.



``C'mere a sec!'' Luke Bavarious wouldn't
tell Bartholomew Bavarious what he wanted until he came to the
bedroom.



``Goddammit{\ldots}'' Luke Bavarious heard his father
mumbling curses under his breath, heard his shuffling steps down
the hallway, and then he was there. Luke Bavarious could smell the
putrid stink of stale Coors and BO oozing from his father's pores.
Or maybe his unwashed undershirt.



``Will you turn the light off for me after I get into
bed?''



``Jayzus! Notiss shit `gin!'' Luke Bavarious
watched, horridfied, as his father drunkenly reeled into the pitch
black bedroom. His father wiggled his ass at the closed closet
doors. ``Scareduh monshters? Monshter inna
closet?''



Luke Bavarious felt a thin stream of vomit rise up in his mouth,
then burn his throat as he forced it back down. His voice cracked.
``Dad, don't. Just{\ldots} just.. get the light,
wouldya?''



Bartholomew Bavarious ignored his son. Or maybe didn't hear
him over his own drunken whoops. ``Monshter inna closET!
Monshter inna closET!'' He sang over and over, in a childish
rhythm. Luke Bavarious stood, unblinking, unbelieving in the
doorway. He saw the closet doors rattle slightly.



``Dad!'' His voice pitched upward, like a little
girl's would. It was the last time in his life his voice
would break like that. ``Dad, seriously. That's not a
good idea{\ldots}''



``NOTTA GUDDEA? Oh fuck you, Luke Bavarious.'' And with
that, his father threw open the closet doors, completely unprepared
for the horrid behind them.



Luke Bavarious couldn't turn away. He saw a fountain of vomit
bubble up and spew forth from his father's mouth, but he
didn't notice his own vomit until later. It got all over his
feet.



The horrid in the closet shot two tentacles out as fast as
lightning. Bartholomew Bavarious' eyes bulged, the Coors
leaving his body in a flood of beer-scented piss that soaked into
the carpet. The horrid's tentacles wrapped around Bartholomew
Bavarious' throat. Two more wrapped around his arms. A slimy,
barbed tongue eased from the horrid's mouth. It slashed
Bartholomew Bavarious' face open, clear from one cheek to the
other. Blood erupted from the face, mixing with the beer-piss in a
rusty puddle.



``Oh dad!'' Luke choked out. The horrid turned its horrid
head for one horrid second. A glimmer of recognition flashed in its
horrid eyes, but only for a horrid second. Then it unhinged its
horrid, terrible jaws, vomiting forth a horrid stream of green,
acidic vomit. Bartholomew Bavarious' clothes started to steam
and simmer. The last thing Luke Bavarious saw were his
father's eyes plucked out and eaten, first one, then the
other.



A single tear rolled down Luke Bavarious' cheek. Then
suddenly, he was not sobbing. He knew what to do.



He sprinted to the bedroom his parents had once shared, back before
the Coors and the publicly known alcoholism. He took his
father's Beretta from the nightstand, relishing the feel of
it in his small hand. It was cool, in every meaning of the word. A
shock of what he would later know as desire prickled at his belly.
He raised the Beretta, testing it. He grabbed ammo and shoved the
gun in the waistband of his pants.



From the bedroom that was once his, he heard slurping sounds. He
decided to take the shoes he'd left by the front door instead
of his favorite sneakers. Now that he thought about it, those were
kids' shoes anyway, and Luke Bavarious was a man.



**Quick edit to fix an {\em unintentional} typo** 

 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\by{Twigand Berries}


{\bf The Sack of Horrors}



I polished off another set of ten and felt that good, deep burn. I
sat up from the bench and flexed, noting with pride the hills and
valleys of my bulging musculature. My sweat caused my sleeveless
shirt to stick to my body, and I thought to myself, ``Damn, Luke.
You look good.'' That's right. My name is Luke Bavarious and I am a
private detective.



And let me tell you, smacking punks and thugs around, you need to
be in great shape. And when I'm not cracking the skulls of dopers
and adulterers, I hit the gym, pump some iron, and sculpt my body
into a machine.



I couldn't very well meet up with my clients covered in sweat, so
like always, I hit the showers to clean up. As I approached my
locker, filled with my fitted suit, trenchcoat, and my Beretta
snuggled in its holster, my eyes were literally destroyed by a
sight that plagues my visits to this mosty holy Temple of the Body.
Sure enough, some old man was standing at the sink, shaving,
completely buck naked.



His wrinkly body sagged in every place imaginable. Hair sprouted
from various places hair should probably not sprout from. His skin
was covered in spots and possibly sores. What he does at the gym is
a complete mystery, as his flabby body and gigantic swollen stomach
betrayed no evidence of any cardio or properly balanced muscle
training whatsoever. But the worst was his balls. His old, wrinkly,
sack hanging down from his groin farther than it would seem humanly
possible. I almost vomited all over the changing room floor.



I grabbed my towel and hit the showers, this monstrous image burned
into my brain. As the water steamed off my red, ripped body I tried
to come up with a reason why these old men would ruin my work out
in this way. I come here to feel good and make myself into a god,
but every day I am assailed by these geriatric sacks of downward
flowing flesh, and am constantly reminded where we are all headed.
I scrubbed myself down, lingering my gaze over my own perfection,
to banish thoughts of old, naked balls out of my head. I needed a
drink.



Instead of heading to my office and checking my messages for new
cases to crack, I headed down to my local pub hoping some old
friends would have the same idea. Sure enough, Brad and Hooksey
were draining some pints, and I sidled up to the bar next to them.
My mind was still spastic over the horrors from the gym, so I
broached the topic to my friends.



``Brad, Hooksey{\ldots}you guys work out, it shows by the way, and I'm
wondering if you two encounter the same problem as I do,'' I
said.



``Do tell, Luke.'' Brad leaned in, interested.

``Yes, Mr. Bavarious. I love your stories!'' Hooksey exclaimed,
excitedly.



``Well, friends, you know how after you burn through your reps and
it's time to clean yourself up, you go for a shower, right?'' I
asked.



``Always.'' Brad said.

``I like to shower.'' Hooksey replied.



``Well, why is it that every time you go into the locker room, there
is some disgusting old man doing stuff naked? Like, I know you have
to change your clothes in there, and there will be a point where
you're naked, but these old guys are ridiculous. They get naked,
and then it seems like they don't want to get dressed again. They
stand around talking. They shave. They comb their wispy hair. They
spend more time naked in the locker room than they do exercising I
bet! And here I am trying to perfect my body, and I have to gaze
upon these leathery sacks of fat!'' I explained!



``It makes me want to punch their faces off,'' Brad agreed.

``I think I will vomit my puke up just thinking about their
disgusting naked bodies,'' Hooksey chimed in.



Now, while I was telling this story, some young, scrawny punk came
into the bar trying to sell some candy bars for the Girl Scouts or
something and he overheard the whole thing. This punk felt the need
to chime in.



``I don't know you gentlemen, but I couldn't help but overhear what
you are discussing. I think you should be ashamed of yourselves
talking about the elderly in this manner. They are deserving of
your respect. They won World War II so you can be free, and shame
on you for talking about them this way,'' the punk admonished.



``Hey, now{\ldots}'' Brad exclaimed!

``There are old germans!'' Hooksey rebutted.



My friends were red in the face at the nerve of this punk, but I
knew how to end this argument. I slid off my bar stool, and turned
to the punk. He looked up at me with fear in his eyes, and I
casually opened up my trenchcoat. His eyes wandered down past my
ripped pecs and spied the Beretta casually hanging out in its
holster. The blood left the punk's face and he ran on out of the
bar, urine soaking his trousers.



``Hahahahahaha,'' Brad laughed.

``Hahahahahhaa,'' Hooksey laughed.



I smiled, and turned back to my beer, thoughts of disgusting flabby
old ass gone for the evening.



* * *




The next day I awoke with the urge to pump some iron again. I
hurried down to my gym and entered the locker room to change into
my work out clothes. As I was squeezing into my sleeveless tee, I
looked towards the sink.



You guessed it. Just standing there, naked, in front of a full
length mirror was the most disgusting specimen of humanity you
could ever encounter. I would regale you with details of his
mottled, paper thin skin, or his liver spotted, veiny scalp, or
even how his biceps swung in the breeze, but it all pales in
comparison to the most disgusting old man balls I have ever
seen.



I stood like a deer in headlights staring at this inverted mushroom
hanging for kilometers beneath an enormous, hanging gut. The gray,
crispy thicket that it sprouted from. The scraggly forest of pubes
that grew to ungodly lengths off the wrinkly, vein covered surface.
The swirl of reds and purples that colored its sagging surface. The
bumps and grooves. It was awful.



I was transfixed in my disgust. But slowly I got a hold of myself
and my eyes raised from his lower regions, over his disgusting
flabby body, and onto his wrinkly face in the mirror. And to my
horror, his eyes matched mine in the mirror. He was watching me
watch him!



And he smiled. A gap toothed smile framed in crusted lips.



I ran from there. I entered the gym proper, fighting back vomit and
the desire to unload my Beretta into his nasty, smiling food
hole.



The only way to recover from this was to focus every fiber of my
being into my workout. And I racked up an obscene amount of weight
onto the bar and reclined onto the bench. Screw warming up. I was
going to pump that disgusting image right out of my mind with the
sweet burn of my muscles pounding out ten reps of my maximum
benchpress.



I hefted the bar off the cradle, balancing the weight between my
two pistons of might. I closed my eyes, and began to work my way
into the set.



{\bf One.}



The bar was lowered to my chest and I shot it back up with a
groan.



{\bf Two.}



My blood raced into my chest and arms, filling me with energy and
purging weakness.



{\bf Three.}



The burn began. It felt magnificent.



{\bf Four.}



I began to imagine the bar was some punk who dared to pull a gun on
me. And I was shoving his punk face off a cliff.



{\bf Five.}



I could feel the muscles in my biceps and triceps begin to quiver
with sweet burn.



{\bf Six.}



Maybe the punk was that punk from the bar. That punk who likes old
guy balls. Heh.



{\bf Seven.}



A warmth spread across my upper body as I heaved the bar up and
down, bringing it within a centimeter of my chest.



{\bf Eight.}



Images of disgusting balls were burned from my mind as I imagined
that punk kid being riddled with bullets, bursting from his back in
miniature explosions of flesh.



{\bf Nine.}



As I crested my ninth rep, suddenly the bar seemed to become twice,
no, ten times as heavy! I locked my elbows and gasped. It was
unbelievable! My elbows gave out and my arms began to shake as the
bar began to lower to my chest. I opened my eyes and looked
up.



I moaned in horror! It was impossible!



The bar was still there with the normal amount of weight on either
end. But between my gripping fists, in the exact center of the bar,
hung what could only be the {\bf THE SAME PAIR OF BALLS THAT
PREVIOUSLY HAD BEEN ATTACHED TO THAT OLD MAN!}



And for the love of god, they weighed a ton! In fact, the weight
was so much that the bar was slowly being lowered down to my chest!
I stared in terror at this unholy scrotum that hung from the bar
just inches from my chest. It was all there. The unexplained bumps.
The crispy gray pubes. The mottled coloring. Oh my god! There was a
sore on the underside of one of its orbs! As my arms shook and
slowly lost control of this tremendous weight, I stared at
pulsating veins that throbbed in a spiderweb encasing the two
misshapened testicles that were contained within its leathery
pouch.



My arms began to feel a million miles away. The numbness spread
along my humerus, over my clavicles, and into my quivering chest.
Sweat began to pour off me in sheets. I heard a distant mewling
sound, and realized it was me.



The balls slowly descended. When they were inches from my chest,
the impossibly long gray pubes tickling and entwining with my own
chest hair, I saw a bead of brackish sweat appear from the patch of
hair that was located at the join of this evil ball sack and the
bar. It came as if from hell. It slowly tracked its way down the
elongated skin pouch, over wrinkles and around encrusted follicles.
As it beaded at the bottom of one hellish testicle, I began to
scream wildly for help.



Tears sprang forth from my eyes, and I felt all strength fade from
me. The bar swiftly began lowering, and I knew my chest was going
to be crushed and my unblemished skin covered in sweaty old meat
sack. My life flashed before my eyes, and I realized my beautifully
sculpted body was about to be defiled for all time.



``You need a spot, young man?'' came a voice from heaven.



``God yes!'' I pleaded. And suddenly the crushing weight was lifted
off me. I began to sob in relief. My body was broken. I pulled
myself up to a sitting position and gazed up at my savior.



It was the old man! He stood there, dressed now in ridiculous
shorts and v-neck white t-shirt, wiping his hands after racking the
devil bar. How could this be? I stared at the weight bar that had
almost killed me, and low and behold, the satanic ball sack still
dangled from its length.



My fury gave me strength again! I leaped from the bench and grabbed
the old man, screaming ``You bastard! Why would you crush me with
your balls? I'll kill you!'' His face whitened in surprise and
fear.



``What are you talking about, son?'' he stammered.



I pointed at his dirty nut sack hanging from the bar. ``Fiend! You
almost crushed my ribs! You tried to dirty me with your geriatric
filth!''



``I don't know what you are talking about!'' the old man lied.



``Trying to trick me, huh? I'll show you!'' I screamed.



At this point a crowd had gathered, curious as to what the
altercation was about. I had to prove to them that this evil thing
was the source of the sack of horrors hanging from my bar. I
reached down and pulled his filthy shorts down and stood back,
pointing to where his groin was missing its satchel of bulbous
evil!



The crowd gasped, and I smiled in triumph as I turned to face the
old man. My smile quickly left my face, for, suddenly, the scrotum
of Hell had reappeared in their proper disgusting place. I quickly
turned to the bar, and sure enough, it was no longer encumbered
with its evil payload.



The crowd turned on me. No one would believe the horrors I had
endured. I was thrown out from the gym, and, in my crushing defeat
by the horrors of Hell, {\bf they did not refund my membership
deposit!}



The end. 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\by{henpod}


I cant help but think some entries are too long. If we are writing
in the style of the notable Mr Biddick, surely it shouldnt be
longer than about 7-800 words? 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\by{Helmet}


{\bf Kindness of Strangers}



Luke Bavarious was driving his squad car on Old Pine Road. A little
while ago, he had given an important lecture on drug abuse at the
local Middle School. Then he saw it: a black car parked in a field
where cars had no business being. He stopped. He walked over to
investigate. The black car had crashed into a huge, unforgiving
pine tree! Pine cones littered the ground like corpses after a
massacre. From the shadowy wreckage emitted a small voice. A
child's voice. ``Help me-e,'' it begged.



Under his bullet-proof vest, Luke felt his guts tie in a series of
knots, each more complicated and painful than the last. ``Dear
God, not a child,'' he whispered. Around the car a moat was
forming of gasoline, battery acid and blood. Luke Bavarious blinked
back tears and inched forward.



Inside the car was a man, dead at the wheel. An empty whiskey
bottle sat in the cup holder. Blood was everywhere. During impact,
the steering wheel had pushed through the man's mouth,
decapitated his tongue and snapped his spine like a \#2 pencil. Luke
looked away to keep from vomiting forth the complimentary meal he
had received in the school cafeteria.



That's when Luke noticed the boy buckled in the back seat.
Possibly a seventh-grader, judging by his size. ``Dad, are you
okay? I told you not to drive drunk,'' the boy said.



Luke stared. Perspiration sweated from his face. The boy's
eyes were gone, long gone, having catapulted from their sockets by
the car's sudden stop and the tendency of objects in motion
to stay in motion. The boy wept tears of blood from his disfigured
face. Luke now observed two splattered milky blobs oozing down the
front windshield like two unholy eggs from the bowels of
Hell.



Afflicted with overwhelming instant insanity, Luke placed his
Beretta to his own temple and pulled the trigger. Nothing happened!
He looked at his firearm and realized the safety was on. Bavarious
giggled madly and flicked the safety off, then common sense
returned to his disturbed mind. ``Poor little fella,'' he
muttered between clenched teeth.



``Is somebody there?'' the boy asked. ``Will you
h-help me?''



Luke fired one bullet, doing the job. 

 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\by{invision}


{\bf Creature Of The Night}





Bavarious. Luke Bavarious. I'm a detective. I carry a baretta. A
baretta so powerful only one man can handle it. And that man's name
is Bavarious.



Luke Bavarious opened the door to exit the doughnut shop when he
heard it. Or at least he thought he heard it. He thought he was
hearing things again. Or was he thinking that he was thinking that
he was hearing things again? He glanced down the dark alley to his
right. He was definitely not thinking he was hearing things. The
creature exploded forth from his midnight fortress of cardboard
boxes oozing with the sludge from the rain soaked streets. The
creature exploded towards Luke Bavarious. The creature was vomiting
tears from its neck.



Luke Bavarious calmy took a drag from his Lucky Strike cigarette,
then flicked it lazily, as if patting a dog on the head. He then
drew his baretta. He aimed it. He slowly squeezed the trigger as
one would squeeze a small centipede or other insignificant animal.
The shots rang out through the night, with the force of a
jackhammer shredding through the creatures skull. The creature
stopped dead in its tracks and slowly fell to its knees. It fell
from its knees to its belly, all the while vomiting from every
available creature orifice it could muster.



Luke took a swig from his flask of EverClear 100% all natural grain
alcohol hidden inside his duster. He placed the flask back inside
his duster. He vomited. He approached the creature{\ldots}



``Oh no. Oh God, NO!''



It was grandma. 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\by{Scissorfighter}


I tried to make it authentic Biddick Style. It also uses the
canonical ``body swap'' interpretation of the ending of ``The Horrid
Reflection.''



{\bf The Book}



Trent Fencer was a bully{\ldots} He liked most to bully children. He
hated all children. Even little Timmy

Ontario. What Trent didn't know was Timmy had found a book. A
horrid book. Timmy was angry one morning and decided to walk around
to clear some steam. He found the book poking out from under the
stairs of the house that he had moved into as his parents had
boughten it recently at an auction for houses that had to be put up
for sale due to the owner of the house having recently been
murdered in the house. It was a horrid house.



The book had leathery bindings and a feint smell of some
body-emitted liquid he couldn't quite recall. He thought briefly of
pus or urine but decided that wasn't quite it. He then remembered
that he was angry. He angrily threw open the cover and looked at
the writing. It was in Latin so entirely hieroglyphic, but he saw
pictures of instructions{\ldots} Instructions on how to raise the dead.
It didn't take long before he thought of Trent Fencer and felt
angry. He was angry with Trent because Trent loved all of his
friends and hated only him.



Trent Fencer was walking outside some houses early one morning. He
had gotten a message from his girlfriend Trish. Or so he had
thought! It said:



``Hi Trent. Meet me in the graveyard. I'm horny, can you please
ravage my hot body with sex?''



Trent high-fived himself immediately after reading it and quickly
put his feet into a pattern of motion that would carry him to his
destination. He was happy to receive that letter. He had built up a
lot of power. Nuclear power, figuratively, where in this metaphor
his father was the nuclear power plant. His dad told him before he
left that his pants were too low and he should mow the lawn. With
every complaint or chore request, Trent got more and more charged.
His uranium was nearly at full capacity and he needed to pump out
some electricity to the general populous.



He got there and turned his eye-muscles to gaze around at the
landscape. No Trish, only Timmy. Only Timmy and a book that sent
chills deep down into his spinal discs and lodged there. Horrid
book or no, he felt he could find another way to distribute power,
so to speak. His feet had already moved him up to in front of
Timmy's face and he barely noticed. His fist coiled back like a
cobra then launched forward like the challenger shuttle, exploding
on Timmy's cheek. Timmy's eyelids exploded open in a shocked
expression, while his neck exploded out in veins and his mouth
exploded in a red stream of blood.



``What is this book? Why are you bleeding red?'' Trent asked. ``Wait a
minute, red is the color of satan{\ldots}'' His brain had started
figuring out the vicious plot that had fallen onto him. Timmy no
longer looked painfilled and merely stepped back, revealing a
circle that Trent was standing in. Timmy then chanted the
hieroglyphics carefully. It was suddenly a dark and stormy night.
Thunder ripped through the sky like an explosion. The ground
rumbled and out came a putrid hand. The hand grabbed Trent's leg.
The hand them moved up further to his thigh and then revealed it
was connected to a putrid head. The head came from the dirt, the
very embodiment of the word ``horrid.'' Its eyes were sharp and
glaring, its pores were wide open, its earlobes had bulging lumps,
and it was missing an eye.



It had finally stood up from its grave. On its chest was a shiny
badge with the name ``Bavarius'' featured on it. It looked up at
Trent and Trent screamed. Trent stood there, paralized and
screaming. Timmy kept shouting orders from the ancient book. The
water then forced the book to slip from his hand. He bent down to
pick it up then picked it up and held it back up. He took one sniff
of the cover and suddenly knew what the smell was from before. He
dropped the book in horror.



``OH MY GOD!'' Timmy screamed. ``The smell{\ldots} it smells of vomit.''
With this sudden revelation, he knew what was next. The Bavarius
thing turned around as he knew it would. It stepped up to Timmy,
its hands raised. As Timmy's dismembered head was flying
through the air, his last thought was that revenge is morally wrong
and often hurts the revenger more than the revengee, and it's best
to take the high road in all conflicts. 

 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\by{January}


{\bf The Journey}



The name's Luke Bavarious, private detective. I've seen
some gruesome things in my time. Enough to make a man vomit blood.
That's why I carry a loaded Beretta. Ready to deal expedient
death to a sucker that needs it, or any misshapen foe. But one
morning in 1991, I stumbled into a tragedy that wouldn't be
brought to such an easy conclusion.



It was a seemingly ordinary day. I turned on the TV as I ate my
breakfast. I usually checked the news for the violent crime du
jour, but I wasn't in the mood. I left the television dial to
linger on a children's program, an animated story called
``The Journey''.



A young man decided to go on an expedition to a foreign land. He
selected a group of friends and relatives to join him. The young
visionary's face shone with pride as the preparations began.
Loved ones provided plenty of supplies and all the financial things
for the trip. A celebration was held when the group was ready to
set out.



But some time into the journey, misery befell the adventuring
party. Everyone developed a horrid sickness, the likes of which
none had ever seen. Their eyes sunk into their heads as their
frames grew gaunt and skeletal. Still, they pushed on. It was too
far to turn back.



As they trudged onward, their skin thinned and the color diminished
to putrid green. Pustules developed, swelled, and exploded like
liquid landmines, coating them in moist blankets of rust colored
blood. In the end, every one of them drank of the bitter mercy of
death, as they were reduced to nothing but fetid corpses.



When the story came to its revolting conclusion, I vomited a
fountain of spew, transforming my breakfast cereal into a
despicable acidic cocktail. I couldn't explain the severity
of my reaction. But what were they airing on TV? This looked like a
chapter from the work of a deviant mind --- a day in the life
of Luke Bavarious, perhaps --- not a children's
show.



I grabbed a Coors to soothe my throbbing nerves before work. I was
already late. As I drove, I started to question whether the events
of the morning had really happened. Maybe it had been a
dream.



When I drove past City Hall, I was surprised to see a large
gathering. Something told me I needed to investigate this instead
of continuing to my office. I pushed my way through the crowd to
enter the doors. All around, the atmosphere was one of revelry. A
young man was giving a speech. Banners waved, and well-wishers
cheered.



It was the same man from the story I had just seen! My mouth
dropped open like a gaping black hole as I pondered his cruel fate.
Immediately my veins pulsed and pounded, popping instinctually out
of my neck!



I noticed one young lady whose silence was telling. Far removed
from the merriment, she seemed as out of place as I. Tears trickled
from her bloodshot eyes. I had to I ask. ``Who is that young
man?''



``He's my brother,'' she said.



``He's going to die and take others with him!'' I
exclaimed. ``His plan is foolishness! We must stop
him!''



She did not respond. Her expression was of resignation.



``I must act if no one else will,'' I thought.
``Better one bloody mess than many.'' I drew my Beretta
and aimed it at the young man to make the fatal shot. At the sight
of my weapon, the sister heaved violently. Vomitus sprayed all over
my pants and on my Beretta. I hesitated.



``Don't,'' the girl sobbed. ``I already tried
to convince them not to go, but no one will listen. If you kill my
brother, they'll probably go anyway. We just have to let it
happen.''



I felt the questions frozen in my mind like impending doom.
``How do you know this? How do you know they will
die?''



Tears cascading down her pale cheeks, she looked me in the eye. I
knew the true meaning of hopelessness when she
replied{\ldots}



``I saw it on TV.'' 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\by{katiekawaii}


I dedicate this short story to the literary genius Ben Biddick. No
one could ever do you justice. But I think I gave it a good
shot.



{\bf Shiny Toy Gun}



I am a man. Some may call me a beast. I am also a detective.
Detective Luke Bavarious. I wasn't always a man. I used to be
a young boy. Carefree. But not for long.



It was said that when my mother gave birth I came out screaming. I
was just like that. Maybe it was a predictor of things to come.
Maybe. I got my first toy gun when I was nine. It was shiny
plastic, a Beretta. Fit in my hand like a glove. Like a glove fits
over a hand, that's how it fit in my hand. My mom
didn't want me to have it. It was my dad's idea. My
drunken father. He always came home late at night reeking of horrid
vomit. He wanted me to be tough. Tough like him.



I was always being bullied. A sixth grader, Max Attica. I told the
principal, but she didn't care. Sometimes it seemed like no
one did. My dad told me not to be so weak. He yelled at me one
night, ``Don't be so weak!'' he yelled. As he said
it I could smell the horrid stench of vomit and the stiff gin and
tonics he always drank. Hold the tonic. It made me want to puke. I
could see his neck exploding as his veins strained against the skin
with every syllable. ``You gonna let that Max Attica push you
`round, boy?''



``N-n-o S-s-ir,'' I stammered as I sobbed and cried and
held down my vomit. My father's vomit, which had been given
to me with the breathing of each horrid vomit- and gin-soaked
breath.



No, sir. Now I had my Beretta. It was just a toy, but I could
pretend. I had a good imagination. I took it to school with me in
my dark black backpack. Even then I favored the dark shade of the
night that would later be my beat in the city. It was 1953. Back
then nobody cared if a boy played with a toy gun at school back
then. Things are different now. I'm why things are
different.



It was a dark and cloudy day, the sun forced into shadow by the
ominous clouds overhead. Max's classroom was across from
mine, and as the bell rang and we filed inside he looked at me and
made the gesture children make to make a threat. A finger drawn
slowly across the neck. I imagined the blood gushing out of my neck
in a giant waterfall. He meant business.



I told the teacher, but like all grown-ups she didn't listen.
Nobody listened. This was my fight and mine alone. So I made it
mine. We came out of the classrooms for lunch. Our eyes met across
the hall. Eyes are the windows to the soul. Mine were black. He
came towards me with his hand twisted into a grotesque fist. I
pulled out my toy Beretta and aimed for his face, which was twisted
with hatred. He laughed. I pulled the trigger. There was a loud
sound, and Max's shirt turned rust. A real bullet.
That's impossible.



Suddenly, I was screaming. 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\by{rinski}


{\bf The Monsters in the Night}



Some would say I have seen it all. They luckily don't know
the half of it. I have both seen it all and then I have
additionally seen some more things. Unspeakably horrible things.
Things that would shatter your mind like a car wreck. For me,
it's just part of the job. You see, I am a monster hunter.
The name's Luke Bavarius. And I love my job. Because I hate
monsters.



I was at my office desk. I poured a cup of dark coffee. I
accidentally burned the coffee, making my office smelled like a
raging inferno. I drank the acrid blackness anyway. It tasted like
a punch in the throat. But it's pungency and aroma would keep
me awake. Awake through a night as black as coffee itself. I needed
it: I felt tired and dizzy for some reason. I put my feet up on the
desk. I took another sip of bitter liquid. Then the phone
rang.



My son's voice echoed through the cold, lifeless plastic of
the phone's receiver. I have three sons. They are volunteer
fire fighters. Usually they can't make calls while
volunteering. The call was therefore perplexing.



``Dad? Dad, you are in terrible danger!''

``Terrible danger? Me?'' I scoffed at his
insinuation.

``Son, don't you understand? I have seen it all. What
dangerous fate could possibly surprise me?''



Before anything else could even happen, a smash caught my
awareness. A window vomited glass fragments from its mahogany
frame. A terrible entity was intruding through a now-broken window!
Glass hit the ground like shells from my Baretta. Speaking of
which, I withdrew my steel companion from its sheath. Time to
investigate.



The commotion was caused by a horrid foe indeed. It was a seething
mass of tentacles attached to a pair of sickening butterfly wings.
Parts of it glowed like certain eels can glow.



``Son? I'm gonna have to put you on hold!'' I
predicted, stabbing the ``hold'' button with my left
index finger. I unholstered out my Baretta and flicked off the
safety because there was nothing safe about the situation.



Before the fight had begun, it was over. A mere twenty bullets
reduced the monster to a twitching heap of calamari. The
bullet-riddled monster could have made swiss cheese jealous. An
acrid stench filled the office. The stinks of vomit and blood and
putrid smoke and diherria mingled in an unholy potpurri. Its
pungency induced nausea. My eyes watered protective tears. The
atmosphere of my office was now more stench than oxygen, making
respiration difficult.



I coughed. I holstered my Baretta in its sheath. I picked up the
phone.

``Dad, you have got to get out of your office because you are
in terrible danger!''



SMASH! Another creature erupted into my office. The window
atomized. Glass fragments splashed the floor like razor sharp
raindrops.



``I appreciate your concern, son. But your ol' D-A-D can
handle a few monsters. I am a monster hunter by trade. And the hunt
is on.'' I hung up the phone with confidence.



This monster was no ordinary panther. It was covered in poison
quills that rustled like amber waves of death. Its face was that of
the common fly. Its arms were like a nefarious---suddenly, the
beast attacked, interrupting my mental registration of its
descriptive traits. No matter. My index finger instinctively
triggered the Beretta's firing mechanism. A steel barrage
sonic boomed towards the fiend. Soon it was just another lifeless
object cluttering up my office floor. Blood gushed from its wounds
like a Nile River of rusty fluid, courtesy of Luke Bavarius.



The stench staggered. I coughed, gritting back vomit.



Suddenly, a cacophony of smashes erupted. My remaining windows
exploded in a crystalline supernova. The air was thick with a
dangerous confetti of glass shards and monsters. Eight more
monsters had broken in, causing this turmoil.



``My property value has gone `out the
window.''' I said with gallows humor.



The odor elevated to a living nightmare about burning corpses. It
consumed my senses. I vomited. Twice. Some came out my nose. My
eyes burned. Tears stained my face with anguish and despair. I
faced my impeding annihilation with eternal sadness and morbid
frustration.



``N-N-NOOOO-O!'' I puked out sobs and some of the coffee
from before. I shot blindly, managing to kill one last monster. The
remainder closed on me like a curtain of death. Knowing I was done
for, I vomited one last time. Then passed out.



I awoke later with a start in a hospital. I coughed. The cough
tasted like ash and my mouth felt like a chimney. I called to a
nurse, ``Nurse what is going on?''



``I don't know how to tell you this, Luke{\ldots} but
there was a fire in your office. You inhaled the smoke and
hallucinated. Your son called to warn you, but by that point you
were virtually insane from fumes. Your other two sons were the
first ones one the scene. You{\ldots}''



Suddenly, she was sobbing. I sobbed too. For I had known all
along.



``Y-you murd-urdered th-them with-with your Barett-etta. Then
your third son showed up with more firefighters and you killed him
too.''



I thought I had seen it all. But none of the horrid monstrosities I
had seen could have prepared me. Not for this. Not for a
realization that hit me like the weight of a neutron star full of
freight trains that were carrying my murdered sons. I was the only
monster in this tale.



When I heard the news, my mind shattered like a car wreck. And I
screamed and screamed and screamed{\ldots}


 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\by{BigSkillet}


Too obscure?



{\bf The Screw That Turned}



``{\ldots}and his little heart, dispossessed, had stopped,'' said a man in
a powdered wig that was reading a story to a group of people.
Everyone else in the group was scared except for one, and he stood
up.



``That story sucked and the ghosts were gay,'' said the standing man,
who took a badge from his coat and showed it to the storyteller. It
read 'Luke Bavarious, P.I. PhD.'



``I should arrest you for being so boring,'' he said, drawing his gun
and aiming it at the storyteller.



``Oh bother, please don't, old chap,'' said the storyteller, who was
British. ``It isn't my fault, it's a true story and it really
happened that way. And it all happened in this very same house on
this day ten years ago!''



When he said that everybody else got scared because it meant they
were in a haunted house, but not Luke Bavarious. He just grinned
and put a cigarette in his mouth.



``You all stay here, I can handle this. I can arrest those ghosts,
and I'll show them the letter of the law the hard way.''



``Oh Luke, you're so brave,'' said one of the ladies who was sitting
in the room.



Luke Bavarious fired his gun into the air and then lit his
cigarette on the still-hot barrel. ``It's all in a day's work,
ma'am,'' he said, ``and I like my work.'' With that, he left the
room.



Luke Bavarious walked down the hallway with his gun drawn. The hall
was dark with shadows, but his glowing cigarette gave him all the
light he needed. Suddenly, outside of a window, he saw a shape.
Luke recognized it as a man, but the hallway was on the third
floor. There was nothing outside for him to stand on except the
darkness. It was one of the ghosts that the storyteller had warned
him about.



``Stop where you are!'' said Luke Bavarious, aiming his gun at the
window. The ghost stayed outside the window, an evil glimmer in his
ghostly British eyes.



``Put your hands up. You're under arrest for haunting this house and
I think you molested a kid in that story,'' Luke continued, but the
ghost ignored his order. Luke fired at the ghost, two bullets
shattering the window with a thunderous crash. When the smoke
cleared, the ghost had vanished.



Suddenly, he turned, and at the end of the hallway was another
ghost. It was smaller but still British, and Luke recognized it as
the ghost of the boy that had died.



``I've defeated the ghost that killed you, there's nothing to be
afraid of now,'' Luke said, approaching the boy.



``Please don't feel that I've been bad,'' said the boy. Luke stopped
and aimed his gun at the boy because his sixth sense told him it
was a trick. ``I had no intent to harm when I stole that
letter.''



``You're under arrest for stealing,'' Luke said. Two shells hit the
floor as he fired into the boy's ghost. When he went to inspect the
boy ghost's body he found a letter in his hand. It said: ``To my
dearest Luke. Please forgive me my son. Sincerely, the
ghost.''



Luke Bavarious dropped the letter and screamed as he felt his heart
stop from the true horror that was his fate all along. 

 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\by{HastyDeparture}


{\bf A Red Sky at Night}



The sun slowly sinks in the sky, an orange halo telling of the the
morrow's forecast. The forecast is always the same.



The forecast never changes, not for me, at least. Every day, I rise
with the sun, and step out the door of my small ranch-style home as
the sun clears the trees of my small suburban neighborhood. Every
day, I grab a large, black coffee and the morning paper from the
gas station on the corner. Every day, I park my black and white in
the side lot of Lakeview Central High School. Every day, I sit down
at my desk as Connie waltzes in the door, says, ``morning, Officer
Bavarious'', and moseys on over to the copy machine.



My name is Luke Bavarious, and I am a School Resource Officer. I'm
a cop in a high school. I wear a badge, I carry a Beretta, and I
don't take shit from anyone, especially not people half my
size.



They said that the regular doughnut-munchers weren't close enough
to the people, not tied-in with the community, and unfamiliar with
the hooligans in our fair town. They said that we needed someone to
fill that role, to keep tabs on the kids, to keep our children in
school and out of trouble. That's where I come in. I deal with the
kids who have a streak, and who, without help, are likely to become
the next generation of scum that plagues our streets. I keep the
peace; I enforce the law.



I know all the bad seeds, the troubled families, the broken homes.
I get to know them, I lend them a hand, and I set them straight. I
know them all like family. So when a young voice says ``hey, Officer
B'' as I'm looking out the window at the setting sun, it's no
surprise that I know who it is before I turn to face the teenage
boy in a hoodie and baggy jeans.



``Hello, Marcus. How was your day today? You go to class?''

``Of course, Officer B. You know me.''

``I know I know you. That's why I'm asking. You go to every
one?''

``Yes, Officer.''



Marcus was a good kid with a bad streak. I've known him since he
moved here his freshman year of high school. He moved out of a
trailer park with his mom and younger sister to avoid their
drunken, estranged husband. A rough upbringing; not uncommon. He's
got a record like many of the others I've helped, ranging from
little things like skipped classes and tardiness to a few more
serious infractions involving alchohol and marijuana. The same old,
tired shit. But he's been getting better.



``That's good, kiddo. That's good. You heading home? You know
nobody's supposed to be in the school this late. You gotta study
for those tests next week.''

``Well, you see{\ldots} I was wondering if you could, uh{\ldots} come look at
something.''

``What is it? You getting into trouble again?''

``I don't know, Officer B. That's what I want to you come
see.''



I look back out at the flaming ball in the sky, and remember that
even though my day is coming to a close, my job never ends.



``OK, Marcus. Show me.'' He nods solemnly. We walk out the door of my
office.



In silence, he leads me down the hall to the right, and up the
stairs to the second floor. We make a left, and start down the next
hallway. Marcus jogs ahead, and stops when he gets to the boys'
bathroom halfway down on the left. ``In here,'' he mumbles, almost
inaudibly. He goes in.



I step up to the door, held open from the inside by a beat-up
garbage can. It's almost pitch black inside; the lights are
out.



``Marcus?'' No answer. ``Marcus? You in here?''



A chill creeps up my spine, an unwelcome feeling that's all too
familiar for someone in my line of work.



I step into the shadows, and undo the strap on my holster. I hope
I'm just being paranoid, just feeling a little scared, but I know
it's not true. The door suddenly swings shut with a slam, and the
world as I know it is plunged into darkness. In an instant, I'm
gripping the Beretta tight in my sweaty hands; exactly the last
thing I want to have to do.



``What's going on, Marcus?'' I call out. The void answers, ``What's
going on, Marcus?'' It sounds just like my voice; an echo. A soft
sound appends the response; a shoe scraping the floor in the dark.
My eyes slowly adjust to the dark, and I notice a small window on
the far wall, just below the ceiling. The faint light coming
through reflects off something to my right - mirrors above the
dirty sinks. Another noise; my eyes dart back to the left.



I should have seen it coming, but it's too late; I feel the breath
in my lungs explode. I'm slammed into the nearest mirror. The glass
cracks, and so does my skull. I push away from the wall, repulsing
the weight of two, maybe three kids. I should have known. The
weight shifts, and my body hits the opposite wall and the urinals.
The nasty water splashes across my hands and stomach. Disgusting. I
turn away from the wall, to face the kids. Disgusting. The weight
hits my stomach, shots ring out in the darkness, and my breath
bursts forth like doves from a magician's hat. I'm no
magician.



I drop to one knee, my head turns toward the mirrors above the
brown stained sinks, and in an instant, I see all those young faces
I've helped staring back at me, their faces blank, emotionless. I
collapse on the floor.



As I lay on the cold, damp tile, I can see out the window. The sun
slowly dips below the horizon, painting luscious red streaks across
the sky. Red streaks the color of blood. Red streaks like the ones
painted across the walls of the boys' bathroom on the second
floor.





e: As I wrote it, the story drifted away from the theme, but that's
what happens. I'm sticking to it. 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\by{lucifer chikken}


{\bf The Warehouse}



Dripping water echoed through the empty warehouse. I stepped into a
slant of light thrown by security spotlights outside. The sliver of
light was intermittently chopped by an exhaust fan set into the
wall. I checked my old automatic watch, lost in meditation as the
second hand whirred smoothly around the dial. It was late. I wound
up at the old warehouse in the harbor on a hunch, there was a lot
of money riding on the investigation, and Luke Bavarius, P.I.
listened to hunches when it meant keeping the freezer flush with
starchy Hungry Man dinners.



In the distance, a low grunt crept through the darkness accompanied
by the clang of metal. The sound rattled me down to the very
marrow. Instinctively, my hand flew to my Beretta, two fingers
rubbing the sleek metal for security. I'd seen a lot of horrors in
the Big Apple, some things I'd never shake. The Beretta was my
partner through each of them.



Gritty footsteps crossed the dirty cement floor some distance in
front of me. Squinting, I caught a flash of pale skin, a glint of
metal. I pulled my gun from its holster, admiring its length as it
was unsheathed. Stalking forward, back tight against shipping
containers, I disengaged the safety and cocked the gun. Footsteps
scurried further into the depths of the warehouse.



I spoke to the darkness. ``Show yourself,
asshole.''



Legs flashed across a slit of light.



``No one should be here now,'' I muttered. My heart fired
adrenaline through my body. ``Shoot first, ask questions
later, Bavarius.''



I raised my weapon, aiming it at the sound. ``Stop right
there!'' I shouted, firing two shots into the darkness. An
anguished cry echoed off the tin ceiling, followed closely by a
thick thud of a body hitting the floor.



I honed in on the sound and stalked toward it. In the shadows,
another hulking figure loomed. ``What the fuck is
that?''



It emitted a low sound and moved. Its form seemed unearthly. My
colon clenched in response to the adrenaline rush. Must've drank
too much muddy coffee before this stakeout.



Again, my Beretta found itself ready to fire as I aimed at the
hulking figure. The sounds it was making, the low groans, were
unearthly. Whatever it was, it had to be done away with. My finger
twitched on the trigger.



``Don't do it, Mister.'' The weak voice came from my
right. My eyes darted between the veiled voice and the shadows in
front of me.



``What the hell are you?'' I called.



The voice didn't answer immediately. It just whimpered.



``What are you?!'' I demanded again, pouring all of the
testosterone pooled my balls into my voice.



``I'm{\ldots} hurt. Don't shoot it.''



``Shoot what?'' There was a pause. ``Shoot
what!''



``Please{\ldots} I'm just a kid{\ldots}''



Oh, hell. A kid. I bit the inside of my cheek to stave off the
encroaching vomit. I could envision the bile on its rise from my
ulcerated stomach. My hand shook. The figure groaned low again and
my finger impulsively squeezed away at the trigger. Violence
exploded once more, echoing through the tin-paneled warehouse. The
figure received my bullet, still unsure of its identity, I watched
its shadowed form waver in the shadows.



``No!'' The kid cried, his pubescent voice cracking with
pain and disgust. He had dragged his body toward me. My gun hand
fell limply to my side; I looked down at the kid with pity and
shame. A gleaming snail trail of blood darkened the cement floor
behind him.



``Why are you in here?''



The kids eyes were pale with death. You could almost hear the blood
draining from him in sick little spurts.



``You shot the giraffe,'' he wailed, low.



My attention snapped from the kid to the darkness in front of me. I
squinted, deciphering the dark figure wavering before me. Its long
neck gradually came into focus. I stepped closer to the beast. It
was vomiting blood from its neck, muscular spasms shooting through
the six foot long tube of meat; its long blue tongue drooped to the
side flaccidly. Long eyelashes fluttered over its cow-like brown
eyes.



Woozy, the giraffe suddenly dropped to its knobby knees, its neck
lolled dramatically to the side. The neck snapped over a row of
container drums, folding thickly like a bag of sand. The sound
reverberated through the hollow spaces in my bones. It wasn't
likely to be forgotten, to abandon those spaces, any time soon. I
clutched desperately at my stomach, trying not to vomit my liver
and onion dinner all over the floor.



I glanced at the kid. Exhalations escaped him in a long rattling
breaths. He'd be a goner without help.



``Ah shit,'' my chest heaved. ``Should've listened
to the kid, Bavarius.''



Sirens screamed toward the warehouse. From the wide doorway, the
rain-slicked streets of the Empire City opened their arms to me. I
pulled a Pall Mall from the emergency pack stashed in my pocket and
lit it up, muttering to myself, the cigarette bouncing between my
lips. ``New York. I ream her and ruin her, but the whore keeps
taking me back.''



Red lights whirled closer. Suddenly, I was sobbing. 

 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\by{ding dang doo}


I awoke from my slumber. The breeze of wind gently blowing wind
across my face. Sitting in the darkness, I thought of only one
thing: Luke Bavarious. The name. Repeating throughout my head,
puking it's mantra into my mind. Who was this man? I did not know,
but I intended to find out. I lit a Pall Mall cigarette and
proceeded to smoke it. Meanwhile, I dressed myself.



Into the dark and dimly lit night I wandered, smoking a Pall Mall
cigarette with my iips. I inhaled, and let my hate seethe. I
exhaled and let my hatred for love grow. Luke Bavarious. The name
echoed in my face. This name. A name like no other. I reached into
my pants and gripped my Baretta, and let a long sigh of relief.
Sometimes I forgot to put my Baretta in my pants. Tonight, I
remembered to do it. Strolling down the street in the dimly lit
night of darkness, I began to wander down the sidewalk. Luke
Bavarious. Why? Was this part of my grim imagination? Was he the
reason teachers and parents were afraid of me? This I had to find
out.



Finishing my Pall Mall cigarette, I crushed the butt of it against
a newborn baby, and slowly walked down a dimly lit dark alley. I
saw a shadowy figure of a man, or maybe it could've even been a
leopard. He let out a gasp of shock and started to ran into the
opposite direction. I quickly vomited and soon began chasing him.
Chase him I did, and I ran as fast as a machine with cyborg legs.
The chase was long and hard, and arduous. He ducked through
alleyways and jumped rooftops, but I had the scent of blood and
murder and puke in my nostrils, I was on his tail every step of the
way.



Until he stopped.







I found myself at my lousy apartment. Empty cans of beer littered
my floor. Numerous tissues surrounding my computer. The butts of
endless Pall Mall cigarettes emptied into countless newborn babies.
And he was standing in the corner. I cocked my head like a curious
dog, and asked, ``Who are you? And why are we here?''



Suddenly, he turned around, Pall Mall cigarette in his mouth. Luke
Bavarious. He chuckled and shot at me. And shot again. Then he shot
me again. With a Baretta. Then he shot me with his Baretta.



And as my neck puked blood from my neck and vomit spewed from every
faucet in my apartment, I heard the words, ``Did you hear Micheal
Jackson died?''



With my final breath, I sobbed, ``{\ldots}Don't stop{\ldots}till{\ldots}you get
enough.'' 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\by{Dominic Bones}


It'll happen tonight. Happens every night. Never stops.



{\bf AGAIN}



I sat on the edge of my bed, drinking a glass of water I had just
gotten from the kitchen. My dog Bud was laying at the foot of the
bed. I stared into the glass, watching my own reflection, and
watching the reflection of the creature behind me.



With a long face and empty eyes, and a mouth that could only be
described as slender. It stared over my shoulder, it's hands at its
sides. Sometimes I would think it was speaking to me, only to find
that it was Bud whimpering.



It always stared, yet when i turned I could not see it. when I
closed my eyes it would be there, clear as day, yet when I opened
them the creature would be gone. I could not explain it. The Dogs
howls were going through the night sometimes.



Why I could not say. Happened since I moved into this house. My
girlfriend and child had left me because I would just lie awake at
night. She said I had no emotion anymore. Said i should see a
therapist. my kid said he loved me but said that he couldnt have a
father that never helped him. he encouraged me to hug him and
promise him I'd always be there and to leave the house with mommy.
But he didn't really like that idea, so I didn't. Dog barked. Hear
the name Luke.



my dresser was an elegant wood paneling, and my floor had a lush
red carpet. Sometimes he would seep onto it and make it seem black.
i didn't know why, he just told me it would show me the way if i
followed him. I always just sat on the bed though. The dog was
scratching the bedpost now. heard the name Luke ringing in the back
of my head.



my glass of water was almost out. i looked out my window and saw
him there, and he asked for me. i would just shake my head, as i
had stopped spaeking. i had recieved a letter the other day that
said i had to mkae my payments, but he told me it wouldnt be an
issue. The dog attempted to lay on my lap. Heard ``Luke'', nothing
but Luke and white noise.



i told myself to go to sleep, but something was bothering me as if
something was buried deep in my head. i kenw that i couldnt just
take aspirin to get rid of it. i felt something at my foot but when
i looekd down it wasnt there. my bathroom mirror could be seen in
the crnoer of my eye, and he could be seen in the mirror. his
fingers pointed at the bed, thuogh i didnt turn t see what he was
pointing at. The dog jumped on the ground and stared at me.



he came up to me and mvoed my hand. he put it on the dogs back and
squeezed. i ddint know what was going on exactly but he asuserd me
it wuold all be arlihgt. my hand ddint stop suqeezing for an hour.
the dog didnt make any noise except the word ``Luke''.



soon i had began laying down and fell asleep. i suddenly felt
better. he had told me that i would soon be able to go to sleep. i
remembered this feeling happening the day before my girlfriend left
me. i fgiured that he just knew how to clam me down. i layed down
and put my haed to rest.



wehn the men came in the morning, i awkoe and walked down to the
mess hlal with them. tehy dont think hes real. the dcotor said i
was imagninig thnigs. she ddint know me thuogh. only he understood.
soon i flet a relaxation in her office like lsat night,before i saw
the lghit coming from the wnidow. he told me taht i cuold be in the
lghit. but i ddint want to. i olny wanted to be wehre he guided me
to. He spoke but I did not hear.



atfer i stppoed suqeezing i haerd the men come in and guided me
away. but it was oaky, because as long as i clsoed my eyes, i saw
his fcae. what did he say his name was? {\em Luke Bavarius}. as i
was dragged, soon i saw my snos face, and it was the same. Luke
just tlod me it wuold all be alright. so i colsed my eyes, and
dreamt of my childs face.



  All
spelling errors on purpose. Not drunk, I swear.   

 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\by{ding dang doo}



Dominic Bones posted:
{\ldots}words?




Yeah, let's go ahead and not get drunk and write stories, k? 

 



