%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{A Cursed Memory}

\by{Quovak}


My name is Luke Bavarious. I am a policeman. Recently my wife Vixie
Bavarious committed suicide. I've been sent in to deal with
Jack Rogue. He was supposed to be at the courthouse. I walked up to
the 162nd street mansion where he lived in New York. I slowly
walked up the dark creaking stairs slowly. I drew my trusty
Beretta. I knocked at the man's door. ``Open up!''
I said.

``What do you want?'' He said.

I screamed. ``It doesn't matter. If you don't open
this door, I'll shoot the the lock off with my
Beretta!''

``Fine. Hold on a second.''

``Too late!'' I shot the lock off with my Beretta. The
sharp kick of the gun was like a wave up my arm. It felt good. I
opened the door and went inside. In the entryway I saw a thirteen
year old boy standing in the middle of the room.

``Why weren't you at court?'' I said.

``You don't want to find out what I know.'' He
whispered.

``I think I do.'' I said, aiming my Beretta.

``My parents are getting a divorce. I don't want to have
to choose who has custody.''

The memory of my girlfriend killing herself rushed back to
me.

``Did you see your dad kill your mom? Or did you only hear the
shot?'' I called.

The kid screamed a bloodcurdling scream and ran upstairs. I raised
my Beretta and fired the first shot. He pulled out a gun and shot
me in my eye. The pain stung as the blood pooled onto the floor. I
couldn't help but vomit. The fluids mixed in the pool. He
shot again.

``Why are you doing this?'' I screamed. The blood kept
running down my face. The bullets tore it open. I fired again. The
bullets from my Beretta took the kid's balance. He screamed.
I heard the kid scream as he fell off the balcony into his rose
bushes. The thorns cut through his skin. His blood oozed out of
their holes. I walked over. ``You were subpoenaed. That means
you should have been in court.'' I said. My wounds were still
terribly dripping rusted blood from the wounds.

The kid was screaming and vomit left his torn lips. As he died he
called out. ``Vixie Bavarious didn't kill herself. Your
wife was killed{\ldots} by you.'' He knelt to the floor and
screamed again as he died.

I looked back at a mirror. Past the blood. And the scars, And the
vomit. And I remembered. The sound of the bullet I fired into my
girlfriend's chest. I remembered her blood falling onto the
carpet. Her spine snapping from the force of my Beretta. Her cries
of pain. Her corpse hitting the ground.

I walked past the kid's cut up body. His blood had dried up.
The vomit had caked on his torn vomit-stained pants. A chill rose
up my back. I started sobbing. I would turn in my badge the next
day and become a private detective. Anything to stop my
grief.


 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\chapter[Satanic Red]{Satanic Red: The Third to Last Case of Detective
Luke Bavarious}

\by{Anal Surgery}




I polished my Baretta with a rust-colored rag. I own both the gun
and the rag because I am a private detective. People come to me to
solve problems. Problems given to them by others with every sort of
type. I am a problem solver for them, the people to whom problems
were given. Today (9am on a Monday) was no different than last
Monday, until she walked in.



Anastasia Rexenstein. She poured into my office like a sexual
cocktail, her dress the color of rusty bulging neck-muscles. Her
eyes peered into your soul like a peering soul-seeing sage. Her
smile twisted like a grapevine as she threw a stack of cash in
front of me. ``I want you to find my daughter,
Bella-Monica'' she intoned. My eyes grew wider than
dictionaries as I looked at the financial stuff in front of
me.



``Okay'' I murmured.



Bella-Monica Rexenstein was last seen in the company of noted town
drunk, Firth Rockwell, at his sea-side cabin near the sea. Speeding
towards the location at 56 miles an hour, I began to hear the
giggle of destiny around me. Night spread across the sky like a
grape-juice stain, the color of darkness, and other dark things.
Rockwell was probably up to no good, so I triple-checked my
Baretta, which was given to me when I started my detective
business. It was loaded. So was I. With alcohol. The sea-side cabin
approached like a sick cat. ``Let's do this'' I said to
no one in particular.



I parked my vehicle and surreptitiously slunk towards the windows.
A light was on, red, the color the Devil lists as his favorite. My
eyes narrowed --- I hate the Devil. There was no sign of
Bella-Monica from the first window, so I approached the second
window as stealthified as I had the first. I still didn't see her,
so I proceeded to the west side of cabin and looked in that window.
I didn't see her there either, so I went to the south side to look
in that window. Nothing, just like what I thought came after death,
because I am an atheist detective, because of my experiences, which
are horrid. But as I came to the east side, I saw movement.



Inside, Firth Rockwell was wearing apparel, apparel which fluttered
wavily in the breeze of a fan. He was sharpening a knife, and
humming the old Irish folk-tune ``I Murder Down a Path''.
Inadvertently, I hummed along, as it brought back memories of my
drunken father, who would hum it after four Bud Lights. I felt
steam rising in me, which I wanted to blow off, in the form of
shooting Rockwell. But before I could Rockwell left the room.



Sneaking in through the backdoor, I heard footsteps stepping down
the steps to the basement. Furtively, I snuck down the same steps,
hoping to see something. But when I arrived in the underground
chamber, what I saw was a sight which I didn't want to see.



Bella-Monica was tied to a chair, with Firth Rockwell placing a
knife to her throat. I yelled at him ``Stop right there!
Villain!''. But he just smiled at me. And then he put on a
wig, and I realized the horrid truth. I vomited a rusty stream from
my lips, which included burning bile erupting from my nose. For
with the wig on, Firth Rockwell was Anastasia Rexenstein.



But then, she pulled the a wig off of Bella-Monica, and I vomited
again. For Bella-Monica was actually me! Bella-Monica screamed
harshly ``LISTEN TO ME-'' but I fired my gun at both of them,
exploding their faces in a shower of blood, brain matter, skull
bits, and gristle. I fled upstairs and vomited in the sink. For I
realized, I had just killed my twin brother. I was the last
Bavarious now. All I could do was sob. 

 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\chapter{I, Lucius Baiuvarius}

\by{Hantu}


It is mid winter in the year 177 of the Christian god. As I write
this, I, Lucius, son of Baiuvarius of Aalen am recovering from my
injuries. My grandfather and his father before him fought against
the Romans and their foreign ways. Both of them are long dead,
slain by Roman sword. My father was no warrior. He is a herder and
did his best to bring me up in the Roman ways so that I might
ingrain myself with the Romans and profit by it. Yet the warrior
blood runs deep. On my 17th birthday, I said goodbye to my family
and travelled to the new Roman fort of Castra Regina. There I
joined a ragtag unit of foederatus, made up of people of many
tribes.



My company consisted of 20 men, only a few I made friends with. We
were employed as light infantry or as Uhlan, my Swabian commander
calls it, arrow fodder for the Legio Tertia Italica against the
rebellious Marcomanni tribes. The pay was not much, but my youthful
adventurism was satiated. In my fifth year of service, I have been
in many battles. Many we won, others we lost. I have seen acts of
extreme bravery, worthy of the old gods. I have also seen villages
burned to the ground, the women raped, the men beheaded, the
children enslaved. Yet what I saw during my last encounter was
beyond anything a mortal should see.



It was two months ago. The first flakes of snow had fallen. The
campaigning season was over and I looked forward to a few months of
rest. I was sitting by the campfire with several others when a
legionnaire guard came to our encampment and talked to Uhlan. They
were out of earshot but I saw him gave Uhlan a piece of scroll and
left. Uhlan shook his head and walked towards us. ``By Belenus
and Camulus!'' he swore, ``A Roman patrol is lost in the
Black Marshes and we are to look for them.'' He spat on the
ground and swore again. ``It's not enough that we fight
and die for them, now we have to baby sit them too! Lucius, Hauff,
and Dumnorix, pack your gear and come with me. We will have to go
on foot as the ground is too rough.''



I reluctantly moved away from the comfortable fire and found my
longsword, leather armour and metal helmet. For some reason, I also
decided to bring along my long knife that I don't usually
carry on missions. I tied the knife in its scabbard around my torso
and put on my leather armour. This decision will end up saving my
life. Our small band of four sets out of the camp just as the
snowfall was beginning to get heavy. We made slow progress, even on
the Roman roads. After 2 days, we arrived at the edges of the Black
Marshes, tired and cold. Uhlan was unusually taciturn during the
journey. He was not a jocular man by any means but he seems to be
even more troubled than usual. Finally, I decided to ask him what
it is that's troubling him. He fell silent, only the
condensation from his breathing betraying his thoughts. ``Do
you know anything about the Black Marshes lad?'' he finally
spoke. I replied in the negative. ``The locals stayed away
from this place and for a good reason. None who ventured in ever
came out again. Those Roman fools are too arrogant to believe in
folk tales and look what happened to them. Yet here we are, on a
fool's errand. May Belenus protect us all.''



We camped in a clearing near the Black Marshes for a day while
Dumnorix and I scouted around for tracks. The fresh snow made this
task even more difficult. The afternoon sun was falling when out of
the corner of my eyes, I saw a glint of metal among the bushes, 20
yards away. I silently signalled to Dumnorix to come near and we
cautiously moved towards it, swords drawn. There is no doubt about
it. It is a Roman scutum, cleaved in half, not cleanly like by an
axe or sword but as if it was ripped into two by some great force.
On the ground, there were drag marks and copious blood and it let
deeper into the Black Marshes. I debated with Dumnorix about what
to do next. The Helvetian wants to follow the tracks into the marsh
before the snow completely covered it while I wanted to report our
discovery to Uhlan. We argued for a while until we decided on a
compromise. We will follow the tracks a little deeper until dusk
falls and then turn back.



The both of us cautiously moved into the marshes. Why I agreed to
this, I never knew. Every ten yards or so, I broke a twig and
pointed it towards the direction that we came. After an hour or
walking, we came to a small cave where the tracks and blood trail
thinned out suddenly. The sun was setting rapidly and an ominous
hush descended on the Black Marshes. I told Dumnorix that this is
as far as I will go and we should turn back before it gets too
dark. He agreed though he wanted to mark the location first. We
looked around in search of a large rock or stick that we can use as
a marker when the wind suddenly picked up. I was digging through
the snow cover when Dumnorix gave a sudden shout. I looked back but
he was no longer there. Snow was now being blown sideways and
quickly, I could see no further than my hands. I shouted for
Dumnorix many times but there was no reply, only the howling of the
wind. I clutched my longsword tightly and readied for battle.
Warily, I crouched towards the small cave to seek shelter from the
storm, my senses on alert for trouble.



The cave entrance was about 7 foot high and just wide enough to let
two man through. The surface was covered in lichen and the dank air
smelled of rotten vegetation or worse things. Inside was pitch
black with pools of stagnant water looking like broken shards of
mirrors. I hesitated but staying out here meant certain death by
freezing. Muttering a prayer to Lovantucarus, I went into the cave,
my trusty longsword drawn at the front. The howling of the wind
took on a haunting aspect in the cave, as if thousands of lost
souls whispering together. The hairs on my neck pricked up while my
heart was beating loudly in my ears. I could no longer see
anything, only vague shadows. A movement! Where? Was it my
imagination? Calm down. Trust my instincts. Another movement, this
time, closer! There is no more doubt. Someone or something is here
in the cave with me. ``Come out and show your self!'' I
yelled into the darkness. ``Come out you coward and fight like
a man!''



A sudden rush of air smelling of carrion and an inhuman growl went
directly towards my face. I instinctively crouched but something
hit hard on my right shoulder, just missing my head, causing me to
fall and end up face down on the damp cave floor. My sense of
direction is now gone. In the commotion, I lost grip of my
longsword. I grabbed my right shoulder and it was bleeding
profusely. My leather armour torn in pieces. I've had enough.
I tried to scramble up and run but a vaguely man-shaped thing
pounced on my torso pushing me down again with great force while
shredding at my chest. I nearly passed out from the impact but I
called upon strength buried deep inside me, the strength of a
cornered animal and flailed at my attacker with my fists. I must
have landed a lucky hit, as the thing jumped off and howled.
Remembering my hidden long knife, I tore away the shredded remnants
of my leather armour and unsheathed the knife. The thing lunged
again with an ear piercing shriek but this time I was ready. I
waited to the last second before, with a rapid thrust, I stabbed
the thing in its chest. My knife made contact and hot blood spewed
on my face.





The full moon was probably out now and dim light reflecting on the
pools of water lit up the scene. For the first time, inches from my
face, I could see my assailant. The horror that I saw could never
be truly described. It was vaguely human but where the eyes should
be, there were only blood soaked sockets. Hot carrion stench
emanated from the mucus filled holes where the nose should have
been and the face was also covered with leprous purple scars. There
were no lips, only a gaping putrid mouth dripping with venomous
saliva. I let out a scream of horror and kicked the thing away. The
thing was breathing heavily and so was I. It clutched at its chest
where the knife was stuck while blood sputtered from its mouth. I
saw my longsword lying on the cave floor and quickly picked it up.
I cautiously advanced towards the prone creature when with a
gurgling voice, it spoke. `` You have beaten me but I lay a
curse on your sons and their sons for eternity. Once every
generation, they will face a horrid enemy and that enemy will be
themselves!'' At the final word, it let out a final putrid
breath and ceased moving.



I slumped on the ground and stared at the corpse. I must have
stayed that way for an eternity when the pain of my injuries
reasserted. I crawled my way towards the cave entrance, trying to
understand what had happened. I was almost out of the cave when I
caught my reflection in a pool of water. Suddenly I was sobbing. 

 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Chamber Pop}
\by{Brushingworth}



Feebly, Luke Bavarious reached into his mouth and pushed on his
molar. He winced as it shifted unpleasantly in its socket. Pain
shot down his jaw and Bavarious clenched the edge of the sink. The
dried blood caked onto his hand cracked and fell into the sink in
large flat scabs. Bavarious raised his head and turned on the
water, hot all the way. Steam rose from the large sink. Bavarious
was in the basement of his office building. The door he had just
stumbled through was still open, letting in the night's
biting cold air; Bavarious didn't notice. He spat twice,
three times, into the sink and plunged his hands into the water,
clenching his fists at the near boiling temperature. The liquid was
quickly polluted to a dark red.



``Shit,'' Bavarious let out as he finally opened his
office door on the sixth floor. Inside the lamp on his desk lit the
dim room. Someone in the plastic chair preceding his desk turned.
What the fuck, Bavarious thought suddenly, but he let out no sound.
``Ah, you're back,'' said the small boy sitting in
front of him. ``I've been waiting almost an hour.''
``Well sorry kid,'' Bavarious responded as he trudged to
his desk chair, ``I've just about had enough people for
today.'' The kid stared at him unblinking. He was probably
thirteen or fourteen. ``Mr. Bavarious? I need to speak with
you about an important matter. Don't you think it's a
little funny that a kid like me is here to see you? Let me
introduce myself, I'm Oscar Crowley.'' While the kid was
talking, Bavarious unloaded his Berretta and gave the kid a
sarcastic glace every now and then. ``Alright listen
punk.'' Bavarious gestured with his Berretta as he spoke,
``Today's over. Finished. All that's left for me
is a bottle of Jack back home. If you've got some sort of way
of paying me outside of Monopoly money and lemonade stands than
tomorrow you can come back and give me your sob stories, tonight go
home. It's passed your bedtime anyways.''



Bavarious was spread eagle hanging upside down on the moldy couch.
He watched Law and Order on the TV upside down in front of him and
sipped whiskey from a bottle, most of which by this point dribbled
down his forehead. He didn't hear anything when the figure
slid open the kitchen window. From the fire escape a dark and dim
figure in combat boots stepped into the apartment. Bavarious, due
to an insurance commercial that annoyed him even in his inebriated
state, lifted the bottle for another swig and saw in the reflection
of the moving glass a dark figure lunging toward him. Bavarious
raised his hand to stop the intruder but the figure quickly batted
away his drunken defenses and closed two gloved hands around the
detective's throat. Bavarious' eyes bulged and he
coughed a mixture of alcohol and vomit. Flailing, Bavarious saw
that he was still holding the bottle of Jack and quickly smashed it
over the head of his assailant. After gasping for several minutes,
Bavarious got up to check on his unconscious prisoner. The man, if
it was a man, was clothed only in a long brown overcoat. His head
and face was covered by the coat's large hood. The
man's head was completely devoid of hair, Bavarious
couldn't tell if he was shaved or simply never grew any. His
face was what made Bavarious recoil. Under what should have been
the man's eyebrows (which were also missing) was nothing but
a series of gashes and burns. Large scars ripped up and down the
man's face, the larger ones continuing down into the robe
that Bavarious didn't want to look under. The only human
feature about the man's face was a vertical gash, about three
inches wide and four inches tall, where the intruder breathed
harshly.



{\em I need some coffee}. Bavarious walked unsteadily in the
gutter. He had left the man/thing in his apartment exactly where he
had fallen. Probably not something he would have done sober but,
tonight he wasn't in the mood for procedure. His boot caught
the edge of a storm drain and he tumbled, scraping his hand on the
concrete. He sat that way for awhile. Watching the dirty water
funnel into the sewer. When he was ready to keep moving, he looked
up. Standing right next to him was Oscar Crowley. ``I told
you,'' said Oscar disappointedly. ``What the fuck are you
talking about kid,'' Bavarious spat, feeling only slightly
embarrassed at his language in front of the boy. Turning, Oscar
walked away from Bavarious. ``You're gonna lose yourself
in darkness, man.''



{\em What?} Bavarious watched the little boy walk away and thought
about the cryptic message. Did the boy know something about the
monstrosity that had just attacked him? He had to find out. Getting
up, he stumbled down the street and turned into the alley he had
seen the boy enter. Suddenly, he halted. Down the three foot wide
alley was nothing but a couple of garbage cans, a dumpster and some
wires running through the water on the ground. What slowly dawned
on Bavarious was that this was the very same alley that he had
encountered the monstrous noise violator early that day. He slowly
walked to the end of the alley and back three times, looking for
any way the boy could have left the alley without him seeing. On
the third trip back he gave up and decided to go for that coffee
after all, but stopped halfway out. He had been running his hand
down the eastern brick wall of the alley and this time he felt a
faint vibration in the stone. He put his ear up to the wall and
listened. At first he didn't hear anything and the wall
seemed to have settled, but a few seconds later he hear a slight
thudding sound and felt the wall shake once again. Bavarious
scanned the wall for a window or drain that might lead inside the
building. Seeing nothing left the alley.



From the street the building didn't look like much. He
couldn't hear the thudding from this far, and the front wall
didn't seem to be shaking. The front had an old-fashioned
lighted sign that read ``Larry's RR'' and offered a
jukebox, soda fountain, and coffee. The front windows were broken
but had been boarded up by strong looking wood. BLACKOUT ARMISTICE
was splashed across the left board in black spray-paint. After
trying and failing to make sense of this felonious abstrusity,
Bavarious looked up to examine the upper floors of the building.
Most of the windows were boarded, plenty were broken, through a few
he saw a spare bookcase or desk but nothing was moving in any of
them. The longer he contemplated the lofts; he began to notice
something about the rooms. He couldn't quite focus on it
immediately, probably thanks to the last of the Jack still
digesting in his stomach. Suddenly he caught it. In a few of the
rooms he could see the same orange-tinted light faintly. Every so
often the light would flicker or go out altogether for a few
seconds. While this could have been attributed to a bad electrical
line, Bavarious noticed that in every one of the rooms the light
responded identically, as if the same bulb was burning out at the
end of every kitchen socket.



Bavarious pulled his Beretta. {\em I'm going in}. He
wasn't sure why he was going in, but he was sure he was
going. He leapt up onto the right display window and landed on
broken glass. With the butt of his gun, Bavarious smashed into the
wood. Chips flew away but the barricade seemed unharmed. He tried
several more times and then went the front door. Bavarious
couldn't see through the glass door but it seemed to be
blocked only by paper. I hope I'm not gonna regret this. He
pulled his leather sleeve over his right hand and slammed the butt
of the gun through the glass door. It shattered and the glass fell
on both sides of the door. Through the paper he could see the decay
of an old caf\'e and the same orange light. He reached through
the tear and tried to unlock the door. The lock seemed to be
rusted. Sighing, Bavarious steeped one leg then the other through
the door, kicking away the rest of the paper.



On the other side of the dining room the orange light poured
underneath a door that Bavarious thought looked like a bathroom. He
crossed the space quickly and approached the door. It was indeed a
bathroom, but the sign had been defaced. What had once been a
standard female figure had some sort of black stain on the front of
her skirt and was dripping black liquid from between her legs.
Bavarious thought it was the same spray-paint as the outside
proverb but he didn't examine it closely. He stood with his
hand on the door for a moment and suddenly he hear the same
thudding, much louder now, and a shuffling murmuring. Inhaling,
Bavarious opened the door with his Beretta drawn.



Inside Bavarious took one and a half steps before stopping dead in
his tracks. His eyes glazed over and the orange light of the room
shined off them like blisters. The room was cavernous. The entirety
of the building had been hollowed out and Bavarious could see the
rooms he had seen from the streets above. They seemed to be
perfectly untouched until they simply ran out of floor. They gaped
out into sepulchral like pockmarks as if someone with a wrecking
ball had tried to demolish the building from the inside out. On the
floor of the room were fold-out metal chairs arranged in rows
giving the building a church-like atmosphere. The chairs were
almost completely filled with people. Bavarious couldn't tell
much about them due to the brown hoods they were all wearing.
Somewhere in his brain Bavarious recognized them as the same that
the man who had tried to kill him had worn. The same part of his
brain that realized there were over four hundred of them. That part
of his brain wasn't really important to Bavarious at that
moment. In fact he barely even noticed the room or the people in
the chairs. His eyes swept past them and were drawn to the sight
they were all apparently there to witness.



At the far end of the room, a few yards to Bavarious' left,
was a man standing like an accursed teacher at a rusted wooden
fold-up table. Lying on the table were various medical instruments
and a small girl. Bavarious thought she might have been seven. She
had long tangled blonde hair that stretched past her shoulders and
ended soiled in the puddle of blood that she was lying in. The girl
had been split open vertically from neck down; the cut had not been
clean. The man at the table had removed most of the contents from
inside her but apparently left the connections. Spare blood vessels
and muscle ligaments crisscrossed over her and draped down to
various organs that were spread out on the table. Terrified,
Bavarious noticed that the girl was breathing slowly into a mask
that was connected to a makeshift airtank below the table.
Bavarious looked away and saw that at the front of the table, a few
feet from the first row of chairs, was the body of the man he had
shot earlier. The body was similarly dissected and seemed to be
waiting for some sort of terrible transplant procedure.



Bavarious stood frozen. He mouth was slightly open. Suddenly, he
saw a door across the room open and Oscar Crowley step out. He was
also petrified by the scene and stood standing for several moments.
When he saw the girl on the table, however, he shouted
``Sam!'' and charged up the room. The onlookers seemed
shocked as well and Oscar made it almost all the way to the front
of the room before one of the men in robes reached out and grabbed
the back of his shirt. He was stopped dead by the strength of the
man. Slowly the nearest of the congregation raised from their seats
and helped subdue the boy. He kicked and bit at all that came near
him but eventually they dragged him to the front of the room in
custody where the standing man removed the mask from the girl and
placed it over Oscar who spat into the mouthpiece but eventually
slowed his thrashing and eventually closed his eyes. From there
most of the group returned to their seats while a few laid Oscar
next to the splayed corpse. Suddenly, Bavarious realized he was
sobbing. 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\chapter{Luke Kills An American}

\by{duck monster}


Luke Barvarious stumbled into his classroom in Ho Chi Minh city.
Today they would be learning about the teachings of Chairman Mao,
the great Oarsman.



It was different here, ever since he was abandoned by his pot
smoking hippy father back in the 80s, nothing was the same as it
was back home.



And most of all he missed his father. Luke stayed up at night,
dreaming of the adventures through europe he took as a child with
his father, the musty streets of Spain, the wonderful aromas of
Paris, the cosmopolitain airs of venice. He enjoyed too the journey
through south east asia, visiting the big old temples and watching
father get blind drunk on Laotian rice wine.



But then one day father disappeared , and Luke was taken by the
police and given to a stern family in the Vietnamese communist
party. He tried to be a good son to his new family, but they would
never let him forget that he was from the people that had murdered
so many before.



And at school the children would taunt him, mocking his skin, his
eyes, his accent and his poor language skills. He couldn't remember
much of america, it was so long ago, but they'd never let him
forget he wasn't from here.



But one day Luke was walking into the local bar, where he was
earning some pocket money serving the Japanese businessmen and
local Communist party officials, when a white man called him
over.



``Hey kid, you look American. Wheres your folks?'', the man
said.



``Uh. I was orphaned and I live with a family here now.''



``Oh, thats too bad. Tell ya what kid, meet me after closing and
we'll have a talk about America!''



Lukes heart skipped. Maybe this kind man could tell him about the
land he could barely remember. Maybe this man could tell him what
happened to father.



Later that day Luke met the white man, and they went up to his
hotel room. The man showed him photos of Disney land, the white
house, and Luke marvelled at how rich and happy every one
seemed.



``If only..'' , he said, ``.. If only I had a way to get
there.''.



``Well son, I guess that'd cost money''.



``Yeah{\ldots} '' said luke.



``I know, I can give you money, but first you must do something for
me.''



The man hesitated then,



``Kid. Ever heard of a blowjob?''



With that , the man unclipped his belt, and his pants fell to his
feet. Luke immediately froze up. He might be a naive kid, but he
knew what this meant.



``{\bf Down down American pig! Down with imperialism! Down with yankee
perverts}'' Luke shouted as he stuck the man in the groin with his
fist and suddenly a team of Viet Cong burst into the room and
pumped the old pervert with lead.



As the man lied dying he looked up at luke and whispered ``I never
stopped loving you son.''. His eyes shed a tear, rolled back , and
he passed away.



Luke realised then, that America is the father of the world. But
now he was growing up, truly a child of vietnam. Having defeated
the Imperialist, the adults would surely respect and honor him now.

 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


{\bf Make My Day}

\by{Orgasmo}


The telephone rings. The cacophony breaks through the utter silence
of my New York flat overlooking Times Square.



I can barely move. Even breathing hurts. These late night bar
fights are getting rougher each night and one of these nights
I'm going to wake up at a hospital instead of my warm
bed.



I recalled earlier events. I was at a bar doing some recon on a
street gang by the name of the Dark Hawks, a gang of murderous
thieves. Their leader tried to make off with Lori's handbag
before I intervened. I grabbed the large man before he could make
off with it.



``What is your name, villain?!''



``The name is Brickwall. Let me show you why.'' All of a
sudden I was thrown through a brick wall. Through the rubble I
grabbed a sleek, unyielding object and showed him the business end
of my pool cue, cracking him and his four goons out cold. These bar
fights are often brutal. But I always win. My name is Luke
Bavarious.



The phone rings again. I let it go to voicemails.



My rippling muscles ached as I turn over to address the device that
is emitting the noise.

The caller ID showed that it was Marty. Who left the message. I hit
play.



``Luke, listen, I don't have much time. I'm down
here in the South Street Seaport and shit's about to go
dow-``



Click. The line went into an eerie quiet like a tombstone. He
sounded frantic. Perhaps I should have taken his call.



I got up, careful to not wake up Lori, and headed to the restroom.
I take a rough inventory of the various bleeding cuts and bruises
Brickwall had incurred upon me the night before.



Back in the room, I grabbed my Beretta from the nightstand. The
sleek black metal filled my hand and I felt its power coursing
through my veins. I cocked the hammer and chambered a bullet. Who
knows what evil darkness will be faced.



I set out into the dark and macabre night. I turned on my Walkman
and played the same song I listen to before I embark on all my
dangerous missions. I howled into the night:



{\em ``Pump up the jam

Pump it up

A pump it up - yo pump it



Pump up the jam

Pump it up

A pump it up - yo pump it



I don't want

A place to stay

Get - your booty - on the floor tonight

Make my day



I don't want

A place to stay

Get - your booty - on the floor tonight

Make my -}



A kid stepped out onto the path. His clothes were in tatters and he
smelled like an outhouse. Snot ran profusely down his nose and he
slurped it with his tongue.



''Sir, please don't go out to the docks. I foresee something
terrible happening.``



''Beat it, kid." I glared down at the rapscallion and pushed him
aside. He lost his balance and fell backwards into an open manhole
cover. His yelp was cut off when he landed on a mangled shopping
cart that lay at the bottom of the sewer and blood flew out of the
open manhole, landing all over Bavarious. The noxious mixture of
blood, snot, and the liquefied shit of the entire Lower East Side
sewer system covered my face and I vomited back into the sewer. I
lost control of all bodily function and for several minutes vomit
came out of my mouth and shit came out of my ass. Everytime I
turned around I resembled a human sprinkler of shit and vomit. With
the help of a lemon-scented wipee I regained my composure after
this unexpected ordeal and continued on my way.



At the Seaport, an eerie quiet abounded. One boat had some lights
on but it was offshore. I rappelled down the Brooklyn Bridge and
back-flipped onto the deck. I lay crouched for a few minutes, my
duster billowing in the wind, eyes scanning the deck for
movement.



I maneuvered towards one of the lit ports. Inside, several thugs
were playing poker. The guy nearest me had a deuce and a seven
off-suit. ``I'm all in,'' he growled.



I announced, to their shock, ``and I'm all
out{\ldots}'' and proceeded to open fire into the room,
spraying metal and lead into their shocked bodies. My Beretta rang
into the still night.



``{\ldots}of bullets.''



The scene before me was of utter horror. Dead or dying men lay
everywhere. Where chips used to be, brains now covered the table.
One man was choking as rust-colored blood sprayed intermittently
out of his neck. He looked at me in a shocked way and giggled. This
grotesque scene played out for a few minutes. Suddenly, he was
dead.



After the carnal scene was complete, I made my way down the stairs
stepping with my feet sideways like a ninja would take a flight of
stairs. I grabbed the sides of my duster so as to not give away my
whereabouts.



In the darkness, a hand gripped down upon my shoulder. Suddenly, I
was thrown through a brick wall and blacked out. The last thing I
heard was a terrible laugh that sounded like a burp.



When I awoke Marty was standing over me with a sneer. ``You
stupid son of a bitch. Did you think I'd really turn
informant? You've pissed off a lot of people, Bavarious. A
lot of people who wouldn't be sad if you took a long drink in
the Hudson.''



I tried to move but was stuck. My feet were incased in
cement.



``Ok, Brick, drop `im.''



With a sneer, the large man behind him pulled a lever and the floor
opened up beneath me. The cold water shocked me as I hurtled to the
bottom of the riverbed. When I finally hit bottom the force was so
large that my cellphone flipped open and accidentally called
Lori.



Back in the flat, Lori groggily picked up her cellphone in the
darkness.



``hello..?''



``MUGLARHGHARGH''



``I'm sorry?''



``RHUGLUGLRAH''



Click.



When her phone rang again, she let it go to voicemails. 

 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{White}
\by{kerimeton}

When the white ward doors opened on that chestnut autumn day I was
reminded of the front doors of my garden shed in Vermont. I
remember feeling cold the same way I did that day, not in a
classical sense but down to the bone. I was feeling an abominable
chill as if I had been pumped full of antifreeze the moment the
doors came into view. And also, much like my garden shed, I was
afraid was what was there. Whether my fears were tangible or not
was to be proven, I myself, I no longer cared for the suffering
trumped any fear or loathing I felt.



I walked down the plasticine hallways and kept my head down; chin
on chest. It was as if a weight of shame had been strapped to my
neck and my only option was to walk like a sorry prisoner.



``Admission?`` the barrel-chested nurse asked behind her oak
podium.



``Yes''



``Which ward`` she continued with the expression of an aghast
ape.



''Psychiatry``



``Name.'' She was curt and unwavering. No doubt the brain
behind that placid face was as rudimentary as a record
player.



"Luke Barvarious'' I paused. ``Barvarious,
Luke''



She nodded curtly as if to suggest that I had somehow made that
record player run more smoothly.



``Reason for admission''



It was neither a question nor a statement. She prattled it off as
if she was in bored haze.



``I don't know''



She paused and stared at me. It was hard and cold as if she was
trying to read my ill intentions. She failed due to a lack of
any.



``Mr.Barvarian''



``Barvarious''



``Mr. Barvarious'' she repeated, still saying it wrong,
``I suppose I can admit you to a psychologist but I cannot do
further for now.''



``I see''



``You understand'' she said with a matte expression,
``that is the procedure for all self admissions''



I took a seat in front of the office and waited. I was soon called
in and immediately expressed my distaste for the poor classical
music on the loudspeakers. The psychiatrist ignored me on that
point. She reminded me of a wooden plank in personality and
stature.



``The report says your 25?''



``Yes''



She seemed puzzled.



``Well, can I ask why you admitted yourself?''



``It started years ago'' I said in deep thought, ``I
remember that my mother was ill and the doctor was recommending
some futile medicine. I was barely 12 then but I knew he was
wrong.''



``I see''



I proceeded, ``I insisted and insisted but I failed to be
heard.''



``Interesting'', at this moment her assistant came in and
a word was whispered into her ear. I failed to realize the
significance of this and continued.



``It turns out I was right, but due to the fact of my age my
words were ignored and cast aside.''



The physiatrist seemed puzzled again but told me to continue.



``It's been going on even since a younger age. Nobody
takes me seriously. When I was young is was due to my youth and in
my older years it was because of my youthful
appearance.''



``I see''



``I recall observing a fire being put out on a Sunday evening.
I remember pleading the firemen to take the back route but I was
continually ignored,'' I paused in repose. ``Do you see
what I mean, where I'm coming from?''



The lady got up and treaded lightly on the floor. It appeared as if
she had taken a tome of information from what I had said. She
walked to the alcove and poured herself a glass of water. She told
me quietly that she wondered why this was affecting me now and why
it took so long for me to come to her. I replied that I
didn't think that was much help, to which the doctor replied
that she was the trained psychiatrist here.



We paused in stifling silence and I realized that the meeting was
over long before I came in. I felt choked in the stuffy room as if
I was wearing a sweater in a sauna. There was an uncomfortable aura
around the couch and the plants that I felt uncomfortable with. The
urge to stand up ran through my legs but was confronted with the
sound of a knock on the door.



The doctor stood up and led the uniformed men in, they held me down
and I knew resistance was futile. I could not understand the
predicament though I understood the pain of the tightened
straitjacket. Once again I was muffled and thrown in the room
leaving them only to wonder how I had escaped in the first place. 

 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{The Pus-Stained Email from Hell}
\by{Zahgaegun}


The sweat dripped off my forehead, running down my face and forming
salty pools on the ground. Pools like the pools of blood that
always form after I kill someone. I have seen a lot of blood pools
in my lifetime for I have killed a lot of people in a lot of very
messy ways.



It's what I do. My name is Luke Bavarious; hitman, soldier,
{\em killer}.



I had been called to this sweaty place, Arabia, to kill some guys.
This was an honorable job, a soldier's mission. ``We need some guys
killed so we called you'', they said on the phone. And here I was,
in this God-forsaken hellhole, hunched over this screen, hoping for
a morsel of communication from Home, something to feed my rotting
brain, to let me know that there was a Reason To Fight, To
Live.



Suddenly, the machine screamed out a bing-bong. New mail. It made
me smile because it reminded me of the time that I told that hooker
``You've got Male!'' while we did the sex. Now she's dead. That wiped
the smile off my face.



``I'm from the Internet'', the letter moaned onto the screen. ``We
have found your Hidden Stash of Writings from Long Ago.'' Dang, I
thought, I had hoped that no one would find that. The sweat drips
came faster now, the pools getting bigger like a child vomiting
blood{\ldots}-red cherry slurpees from the fear of riding the Viking
Ship at the county fair.



``Hurry'', it continued to moan, ``there are already many people here
pretending to be you.'' I typed fast as I could, pus-filled blisters
rising from the friction of the keyboard on my gnarled fingertips.
``I am coming'', I typed, ``Prepare the way.'' I tried to log in, but
the passwords they used were too long, too complicated for my
gnarled brain. I may only be thirteen, but my soul is almost 100
years old, due to all the killing.



Before I could get there, the sergeant bellowed my name. ``It is
time to kill'', he said while handing me a beretta and a knife.
``This is all we have left. Are you a bad enough dude to kill
everyone with just this?'' ``Yes'', said I, the cold steel of the
knife blade glinting off my eyeballs. ``Did you warn them?'', I
asked. ``Yes'', the sergeant burped. ``We flew over them and dropped
fliers warning them in whatever language they speak.'' ``Good. Then
it is fair.'', I said and walked off towards the gate of the
compound, the gate of my future and their destiny.



As he walked away, a private leaned towards the sergeant and said
``Warn them of what?''



``I warned them that The Writer is coming.'', he said. ``God have
mercy on their souls.'' 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter[Horrider Reflections]{The Horrid Reflection II: Horrider Reflections}

\by{Bonaventure}


The screamers screamed past with a screaming scream that screamed
in the ears of Luke Bavarious Junior. They were horrid and horrible
beings of indescribable horror. But if you had to describe one then
they looked exactly like Ghost Face the famous killer from the
Scream movies. Luke Bavarious Junior woke up with a scream because
he had been screaming in his dream when he was dreaming of the
screamers. ``What are ya screamin' for?'' said Luke
Bavarious Senior who is the protagonist of the story and who is
Luke Bavarious Junior's father and who came into the room
where Luke Bavarious was screaming.

``I saw the screamers again dad,'' Luke Bavarious Junior
whimpered.

``Gah!'' his dad Luke Bavarious, paranormal P.I. said. He
said ``Gah! You've been watching too much Scream. I told
you that stuff rots up your brains into blood. Now I'm going
to burn your Scream DVDs so you stop having
nightmares.''

``No! Not my Scream DVDs!'' screamed Luke Bavarious
Junior. ``I'll show you, dad{\ldots} I'll show you
that kids should be respected and listened to'' he grit his
teeth until they bled blood all over his chin.



``I'm off to work honey'' Luke Bavarious said to
his hot wife who was still in bed because---heh, women. Am I
right, fellas? Then he put a donut on his pillow next to the wife,
he got the donut from the donut shop across the street and every
day he put a donut on his pillow for his wife to eat, this is
important information to remember because it foreshadows the twist
ending that's coming up.



Luke Bavarious had been known as the paranormal detective ever
since The Case of the Horrid Reflection where he killed a
doppelganger. ``So you're Luke Bavarious.'' The
words vomited out of the mouth of the police chief. ``I hear
you've been known as the paranormal detective ever since you
killed a doppelganger.'' Luke nodded and chewed on his
noir-as-hell cigar. ``That's impressive stuff.
Dopplegangers are tough to beat cause they have the same moveset
and equipment you do.''

``Tell me about it, chief.'' Bavarious crammed a fist
into his mouth that was full of peanuts and then he chewed down the
peanuts into a horrid gloopy paste that slid down his disgusting
horrible throat.

``Well, you're just the man I need,'' said the
chief. ``We got reports of a doppelganger factory that's
taken over the old Frankenstein-making factory out on
I-45.''

``Say no more, chief.'' Bavarious cocked his Beretta and
doffed his really sweet fedora. Then he drove to the doppleganger
factory.



The doppelganger factory was filled with bile and amniotic fluid
and all sorts of gross blood and vomit. The dopplegangers were
being made in sacs of pus. Bavarious shot up the sacs of pus and
was covered in sheets of vomit and fat as the baby dopplegangers
writhed on the floor in a scary way. ``Luke Bavarious''
said the head doppelganger who had set up the doppelganger factory.
Bavarious narrowed his eyes. The doppelganger was horrid with
horrible pus scars all over his purpley face screwed up looking
gross.

``I thought I killed you, Luke Bavarious,'' said Luke
Bavarious, when he recognized himself as the doppelganger he
thought he killed but he didn't really.

``You thought you killed me, Luke Bavarious, but you
didn't really. I just feigned death by copying a dead guy at
that moment. We dopplegangers are good at copying stuff. Here,
I'll copy a guy vomiting acid at you!'' then he vomited
acid at Luke Bavarious, and boy it just stank to high heaven, ugh!
Bavarious was ready though and he shot the doppelganger making
machinery above the doppelganger and then the factory started to
explode in sparks and blood and black bile and white pus as the
doppelganger sacs all exploded and a billion baby dopplegangers
screamed out in dying death forever. The head doppelganger screamed
as all the blood and pus and bones exploded out of him like in a
Mortal Kombat fatality.

``Another day another time the earth was saved from
dopplegangers by Luke Bavarious'' said Luke Bavarious as he
walked away in slow motion. Behind him, the factory exploded.



That night in his home Luke Bavarious slept asleep, but Luke
Bavarious Junior was up and he sneaked off to the kitchen and
turned on the deep fryer. He had evil red eyes and he laughed,
``Haw, haw!'' He raised a voodoo doll in the air although
more accurately it's a European witchcraft doll because the
idea of sympathetic magic used through dolls doesn't have
anything to do with traditional voodoo but was instead an idea from
European ideas about witchcraft that was conflated with rumors
about voodoo okay but ANYWAY he takes the doll and he raises it
over the deep fryer and then he monologues: ``Haw, haw! Dad,
you might have saved the world from those dopplegangers but
I'll teach you to burn my Scream DVDs. Now when I want to
watch Sarah Michelle Gellar get killed in Scream 2 and masturbate
to it I'm going to have to search for ``Sarah Michelle
Gellar death Scream 2'' on youtube and like half of them are
going to be music videos and none of them are going to be good
quality and it's going to be a real pain in the neck!
I'll get revenge for that! You're going to learn a
lesson, dad. Kids should be respected and listened to, because if
you mess with them, maybe they have a voodoo doll---although
really it should be called a European witchcraft doll but
I'll get into that later---and then they'll do
THIS!'' and he threw the doll into the deep fryer and
uproariously began to cackle softly to himself with a silent
``Haw, haw, haw!''



The next morning, Mrs. Bavarious woke up and found a donut on Luke
Bavarius' bed. ``Oh, he must have already left!''
she pooed, and then she bit into the donut. A scream of horrid
terror burst her throat open as she bit into the donut and, like in
a sex scene starring one of the Wayans brothers, she was splayed
against the wall by a torrent of blood, guts, and Bavarian cream. 

 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\chapter{Wicked Workout}
\by{Akbar}



Luke Bavarious was on the prowl. Earlier that night, the detective
had received notice from the chief that some unidentified killer
was stalking the Upper East Side. Already five had been found dead.
Each was murdered in the same gruesome fashion: arms hyperextended,
hair ripped out to the follicle, legs bowed at the knees as if the
ligaments were carefully torn, and finally, a smile carved across
the face wide enough to completely cover the corpse in its own
liquid lifeforce.



{\em What kind of goddamn maniac are we dealing with here? The
Joker?} Bavarious thinks to himself as he carefully primes his
trusty Baretta, referencing the recent Batman film. He tenderly
fingers the safety. He steps out of his Ford Pinto into the cool
New York night.



He stalks the sidewalks seeing nothing but the steam rising out of
the sewers onto the dim streets. His eyes are optic daggers,
piercing into the darkness. His muscles are taut, ready to unleash
the leaden payload of his sidearm into villainous flesh. He sees
the telltale trail of fresh blood on the pavement.



{\em It's on.}



As he follows the sanguine highway into the alley behind a 24-Hour
Fitness, he begins to hear a slow pounding in the night air. Slowly
but surely, it grows louder and louder as he approaches the
wellspring of the molten vein-magma. Before, it was just a
thumping. Now, however, it is more recognizable: a beat. A melody.
A hot sensation rushes through Bavarious' body.



``Dance music!'' he ejaculates softly as he creeps to the
source: a partially-open doorway flooding the shadowy alleyway with
light. He nudges the door with his foot and peers into the hell
below. Bodies! Dozens of them. Strung up by the arms on chains
attached to huge meathooks, their feet barely reaching the ground.
The bodies were jerked hardily up and down to the cadence of the
music. Their arms strained against the tension. Their legs slapped
against the concrete floor over and over, as if horrifically
tapping along to the beat. The battered limbs heaved droplets of
blood and pulverized bone into the air. In front of them all was a
horrid taskmaster.



``Up and kick and down and step and up and kick
and{\ldots}REMEMBER TO SMILE!''



Bavarious could only see the back of the man, but he was already
repulsed to the point of vomiting. Dressed only in a red jersey,
dolphin shorts, and running shoes, the short man runs to and fro in
front of his victims, only a handful of which that were still
conscious or alive. The tormentor's bouffant hair bounces as
he taunts the wounded. The killer then takes out a wicked curve
blade out of his shorts and carves open a pleading woman's
face, laughing as he watches her throw up her fluid
existence.



{\em What the hell is this?} Bavarious thinks as he makes sure
that his Baretta is locked and loaded, regurgitated chicken dinner
still spewing out of his mouth. Jumping up, he yells out:



``FREEZE! THIS IS DETECTIVE BAVARIOUS OF THE NYPD! I HAVE A
BARETTA LOCKED ONTO YOUR HEAD AND I WILL FIRE IF YOU DO NOT
COMPLY!''



The demon in front of him does not. Instead, he leaps otherwordly
to the right, launching his disgusting body as approximately
fifty-five miles per hour. Bavarious reacts with equal speed,
letting loose with half a score of death slugs. All of them hit as
the swiss-cheesed body hits the floor with a thud. Bavarious races
up to confirm his kill, wiping away the now-crusty sick on his
chin.



Rather than a cadaver, however, he sees only the man, still facing
away from him. Still on his feet. Still alive. Filled with dread,
Bavarious unloads another barrage of rounds from his only true
friend, the Baretta he keeps on his hip. The bullets zip through
the gym teacher from hell as if nothing was there. In their wake,
they leave gaping holes that eject a clear liquid. The vitreous
material tumbles out of the entry wounds like a rain. A shower of
translucent gymnasts somersaulting through the air. The gashes
slowly close and leave no trace of their former existence, even in
the man's clothing.



``WHAT THE HELL ARE YOU?!'' the detective screams as he
discharges the rest of his lethal cargo, again to no avail. The man
finally slowly begins to turn around, revealing his bloated
face.



``Richard{\ldots}Simmons{\ldots}?'' Bavarious murmurs
into the air, putrid with aerosolized human body parts.



``No,'' the man says as he fully presents himself, and
then rips off his face revealing another underneath. It is an oddly
familiar visage. ``I'm you.''



Both Luke Bavariouses vomit. Tears.


 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Gold Ribbon}
\by{Swanky}



``Those things will kill you, ya know'', Percival
growled, spitting up blood onto his rope-bound hands.

``Don't worry; they're filtered'', Bavarious
coyly said as he blew smoke into Percival's battered
face.

Luke Bavarious wiped his hands of blood, as he had spent the better
part of the past six hours trying to coax the safe combo out of
this man. The night before Bavarious received a clean manilla
envelope on his doorstep. Inside that envelope was a picture of a
boy, inside a large safe, a bandana in his mouth with the words
``Wednesday, 8 PM 50,000 in a duffle bag at 1st and 1st or he
runs out of oxygen''.



Bavarious knew he was a go-to guy, but nothing got his gib like an
innocent kid whose life lie in his hands. Especially little Johnny
Powell, a doe-eyed kid he knew through a local Big Brother's,
Big Sister's program he used to participate in. Johnny loved
to talk, and just ramble on about science and school. He was one
bright kid. He might as well have been his own brother. Or even his
own son. Percival didn't have the money, and he knew that if
he went to the police that kid would be as good as dead. This kid
wanted to be a scientist when he grew up. Not a ball player or
astronaut, but a guy who does experiments. He was just a kid, after
all.



He recognized the handwriting of the note, and the brown shag
carpeting on the bottom of the picture clenched it. It was Percival
Johnson's house. Timmy Johnson's father. A good man, a
family man, but who knows what was going on in his head. Could have
been just money problems or even something worse. But that
doesn't matter. What's important is that he knows the
guy behind that picture. And where he lives.



Shortly after receiving that picture, Luke got in his black,
tinted-window sedan and scoped out Percival's house. The plan
was to camp out near Percival's home, then when Percival was
coming home from work, catch him while he's getting
undressed. Luke had his trusty sidearm and no regrets, save for
what poor Timmy might see. Scarring one life is better than ending
another, he repeated to himself.



Once he made his break into the house, everything was a blur.
Percival was shocked, but gave up a curiously easy fight.
Bavarious' heart was beating out of his chest as he dragged
the man, having been pistol-whipped and dazed, towards his basement
and that unmistakable brown shag carpet. Sure enough, as he threw
Percival down the stairs, he could see the safe out of the corner
of his eye. He just hoped poor Johnny was still alive.



He dragged Percival's laughing and oddly limp body over to
the safe, bound his hands and started a routine of inquiry as to
the combo of the safe.



He put the cigarette out on the shag carpet.



``I'm running out of patience, and soon my knife will
begin to ask questions. And he makes me look like a
gentleman.''

Percival began to come to a bit out of whatever stupor he seemed to
be in.

``Wait, what? Where{\ldots}where am I?''

``You're a few minutes away from losing your life unless
you give me your safe combo, pal.''

``But I'm{\ldots}oh, god, I'm so
sorry{\ldots}okay, 35{\ldots}35, 29, 53''



Luke looked at Percival like a lost kitten covered in flour, but he
had no time to ask why this man suddenly came-to. He propped up
Percival against the wall, but wondered if there was something even
more fishy than he originally thought. He positioned himself near
the safe expecting his journey to be nearly over.



He tapped on the safe like a father-to-be gently tapping on the
pregnant belly of his wife.

``Don't worry buddy, I'll get you out soon''.
He heard nothing.

``35{\ldots}29{\ldots}53''.

Click.

He turned the handle and opened the safe. Just as he was about to
look inside, expecting a sense of relief unlike anything he had
heard before, something happened.

Thud.



Luke slowly came back to consciousness, he found himself sitting
next to Percival, his hands, legs, thighs all bound very tightly
with wire. His head was pounding to hard to try to move, but he
knew he knew small, nimble fingers tied those knots. As he
struggled to raise his head to see the two figures coming towards
the lit part of the basement, he noticed it was little Tommy
holding a clip-board and, perfectly healthy, holding a wrench, was
little Johnny.



``Johnny{\ldots}what is this?'' Luke whispered, his eyes
begin to tear with his inevitable realization.

``Tommy and I are doing our science fair project, remember? He
was testing the effects of his mother's pills on Mr. Johnson.
We ground it up in his orange juice.''

``But{\ldots}what{\ldots}about{\ldots}''

``Part of my experiment was testing the effects of fear on
head injury''

``{\em Part}?'', Percival asked, his tone ever more
hopeless.

The unmistakable sound of a dentist drill could be heard in the
background.

``Yes, Mr. Bavarious. Part.''

Bavarious wept uncontrollably. 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\chapter{The Smoker}
\by{Cruo}

I stepped up to the door. The smell of the smoke was leaking
through the door. I was at the front door of Gus's Bar and
Grill. My hand started to shake a bit as I reached toward the
handle. I paused. I reached for my Beretta instead. My name is Luke
Bavarious, I am a private detective called in to investigate a
smoking complaint. I love my job.



I kicked in the front door with my boot, my Beretta ready for any
trouble I might find myself in. All I see is the bartender washing
out a mug at the bar with a terrified look on his face. With his
head he gestures to the corner. I follow his jerks and find my eyes
looking on the face of a boy. The boy was the age of a fifth
grader. At last, the source of the smoke has been discovered. I
yelled to the boy, ``Hey you! Yeah you in the corner, drop the
cigarette now!'' The boy only smiled and waved me to come
closer.



As I walked closer I got this horrid feeling that I knew the boy,
but I couldn't quite place it. I asked him why he thought it
was okay to smoke in this bar when the law clearly says it is
against the law. He flashed me another of his mischievous smiles
and asked, ``What's the matter Luke you don't
recognize me?''



Suddenly the thought came to me but I couldn't believe in my
own thought. ``I.. I.. wha.. who are you?''



``Really Luke, when was the last time you've looked in
the mirror?''



``No! This is impossible! You can't be!''



``Oh but I am Luke, I am you and you know it. Well{\ldots} I
was you.''



I was staring into the face of myself as a fifth grader. I
tentatively asked, ``Why are you here, what do you
want?''



``Luke, I was sent from the future to warn you of
something.''



``What do you mean the future, you're from the
past?''



``Shut up Luke, I was sent from the future, you wouldn't
understand so let me get back to my warning. I was sent to warn you
about finishing your little project.'' I was building a robot
in my garage in my spare time, that had to be what he was talking
about. ``Your little project may seem innocent enough now, but
it will be the end of mankind as you know it, and you must destroy
it before you finish, you must!''



Suddenly I saw a blue flash next to the boy who was myself from the
past but from the future. Some acid like substance sprayed out
through the flash instantly and the boys face started melting in
front of my eyes. It was terrifying, the skin and the blood and his
eyes and his tongue were all fusing together in a horrid tangle of
disgusting gore. I could see his bones through his melting face and
his screams were the stuff of nightmare. I started to intensely
vomit all that was held in my stomach, so intense that blood
started pouring out alongside the sick substance. My eyes were
bulging and my ears were pumping hard with the beat of my heart.
The boy was now a pile of melted flesh and blood and gore.

I dropped to my knees and scooped the pile of the once past future
self into my arms. Suddenly, I was sobbing. 

 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{The Homeless Monster}
\by{TarDolphinorShark}





Luke Bavarious sat weeping in his rust colored apartment. The kind
of apartment that wept pain and vomited sorrow from every bowed
ceiling tile to every dinged and dingy wall. It had been three
weeks since that fatal night and he just couldn't get it out
of his head. His once normal life was twisted into a tormented and
nightmareish existence. As he sat cleaning his Beretta, the very
Beretta he was issued from the precinct, he remembered that fateful
evening. Rain was vomiting from the sky and it sounded as if a
thousand wounds were spilling mucus and pus from their pierced
membranes. Luke walked down the street when suddenly he saw a
sobbing mess of a man. Homeless scum he thought. This man was
wearing a disheveled burlap sack with tears that looked like the
ripped flesh of a person who was left for dead long ago. Luke
grimaced at the homeless man, thinking to himself ``I'll
bet this is the guy the chief told me about, I won't have any
noise complaints on my watch!'' Suddenly he exploded into
action drawing his Beretta he steadied it at the homeless man who
whimpered at first, but gradually started to let loose a blood
curdling scream that smelled of death and reeked of vengeance.
``YOU LET ME BECOME THIS MESS OF A HUMAN!'' the homeless
man shouted. He leaped at Luke arms flailing wildly and razor sharp
fingernails digging into Luke's arm and revealing the rust
colored life force within him. Luke's Beretta skittered
across the alley just out of reach. ``Without my Beretta I
will have to handle this mad man using my bare hands'' Luke
thought to himself. As he exploded forward lungs heaving and arms
outstretched he made contact with the man. Wrapping his arms around
the homeless man's neck he wrenched and wrenched until the
neck split like a ripened banana, spilling a vibrant rouge all over
the asphalt. The gore was thick, and layered in between
Luke's fists which made it harder to grip his now reclaimed
Beretta. As he steadied his shot, he kept feeling a nagging
suspicion in the back of his Anger filled mind. He knew this man
once, but he could not place it. ``No matter.'' Luke
thought, This man is a burden on society and must be dealt with.
Luke cocked the hammer of his Beretta and as the hammer of justice
falls on those who do wrong, so did the hammer of the Beretta fall
on the firing pin launching round after round into what Luke
considered human garbage. The man's skull exploded and his
chest lit up with the continuous barrage of hot lead pouring from
the only real friend Luke had, his Beretta. The homeless man winced
one last time as snot and spit and vomit erupted from his mouth,
eyes, and nose like a morbid fountain. As he rolled over to die,
Luke saw something in his hand. Luke crouched down to gaze upon the
item, and noticed it was a picture, a picture of a familiar person.
LUKE BAVARIOUS, but who was the man in that picture? Luke stared at
the man, and then the photograph, the pieces finally coming
together. ``Father'' he thought, as he clutched the
picture in his hands like a hawk clutches a dying mouse. If I would
have known you'd end up like this I would have dropped out of
the academy, but I made my choice, and you made yours.
``Nobody makes noise on Luke Bavarious' watch!''
Luke said as he chambered one last round, and placed it right
between his rotting father's eyes.

e: for title 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\bf Monstrous}

\by{Blurry Gray Thing}


In the shadows of our overcrowded cities lurk unspeakable horrors.
No one knows or can imagine the horrid reality that lurks beneath
our wholesome fa\,cade. I am one of the few people who does. I
am a private detective. My name is Luke Bavarious. These are my
stories.



I was investigating a brutal serial killer operating in the bad
side of New York. When I saw his latest victim, I was stricken by
the horrid brutality of his violence. The murderer cut out the
homeless man's heart, stabbed him through the eyes, and
carved him open from buttocks to head. Vomit forced its way past my
teeth, and poured into the gutter, mixing with the unfortunate
victim's blood. That night, I went home and drank whiskey
until the alcoholic poison killed all the feeling in my
brain.



I used my detective skills to track the murderer to a warehouse in
the worst part of the city. I knew the killer had to be there. All
of the monstrous murders pointed to it. As I walked there, I felt
nauseous. The people all around me were garbage. Prostitutes and
thieves. They did not deserve to live. But they did not deserve to
be brutally murdered.



I stalked carefully into the warehouse. My combat boots carried me
silently through the shadows. I heard a man ranting and I saw a dim
light coming from a small room. It had to be him.



``Why are there so many of you now? Where are you all coming
from!?'' The man was insane. Whoever he was talking to
grunted.



``You can stop pretending! I know what you really are. I
won't let you get away with it! I'll kill all of
you!'' he was screaming. I had to save his victim.



I smashed open the door with my shoulder. There was an old man in
horribly ragged clothing tied to a chair. There was also a thin,
pale man with pitch-dark hair, holding a knife. The knife was rusty
and fat from all the blood it had drank. I raised my Beretta at his
head.



``Hold it! Let him go!'' I ordered the killer.



``No! Please, you don't understand,'' he said. His
face was twisted by tears and rage. He raised his knife to impale
the victim's face.



``No, you don't understand. Put down your weapon, or I
will shoot you,'' I ordered again. The rust-colored knife fell
out of his hands. He was sobbing. I started untying the old man.
The old man smelled like blood. I thought it was because he was
injured.



``No!'' screamed the murderer. ``Don't let him
loose! He'll kill us both! He's a monster! You
don't understand!''



``You are the only monster here, pal!'' I untied the old
man completely.



Suddenly, the homeless man let out a horrid roar. It almost
deafened me. I could not do anything to stop him. He flew at the
murderer teeth-first, like a human-sized vulture, and tore at his
neck. Blood the color of ripened apples exploded all over the tiny
room, and shone bright red in the light of a single bulb. I fired
my Beretta at what I had so incorrectly assumed was a victim. The
recoil shot through my arm but he did not stop. He tore apart the
man's skin, muscles, and arteries with horrible strength,
even as I squeezed round after round into his back. His growls
mixed with the sound of shells hitting the floor. Soon, the
murderer was a pile of ruined meat.



He turned around and looked at me with eyes dark as dry blood. I
knew my gun could not stop him. I dove to grab the murderer's
knife. I knew what I had to do. The old man dove to grab my
throat.



No one had ever solved that crime. I told the Chief of Police that
I found two more victims in an old warehouse, but couldn't
handle working the case any longer. The murders continued. Every
month, a new homeless man was found cut open, with his heart carved
out. The police knew it was all done with the same knife, but no
one knew who was doing it. 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\by{Gestalt Pie}
%
%
%
%cruft posted:
%I'll also make a thread about putting it all together,
%in case other goons want to bind their own
%books.
%
%
%
%
%Please, please link to your thread. This sounds fantastic. 
%
% 
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\bf Deja Vu}
\by{The Bananana}



Luke awoke in a bed. He stared at the ceiling and searched his mind
for his surroundings. He couldn't remember a thing. His head
ached, pounded as he struggled to sit up. He was in a clean white
room.

There was a noise. Familiar. Welcome.

Beneath the door drifted the smell of home. Of warm bread. Of eggs.
The sounds and clatter of morning seeped through as well. He swung
his legs over the side of the bed. His head was still aching, but
it was lessening.

He stood.

The sun's beams had warmed the floor. He stretched, lost his
balance, and feel back to the bed. He lay there, lying in the
light, when he began to listen.

A voice, He recognized it. Then another. He knew them both.

No, he thought, he must be dreaming.

He got up and turned towards the door. Behind him, through the
windows, the trees began dancing lightly in a sudden fresh
breeze.

He inched to the door, and reached for the knob, and recoiled in
pain, as the hot door burned his hand.

``What are you doing'' asked a young boy from the corner
of the room, surprising Luke.

He was small. Pale. He looked unwell.

``Wha{\ldots}who are you''? Luke said, studying the
stranger.

``That wasn't part of the deal'' the boy
replied.

Deal? Luke didn't know what the kid was talking about.

``Don't open the door'' the boy warned.

Luke knew what was on the other side. His family. His wife. His
son. Sitting, waiting. Her red locks swaying and bouncing as she
prepared their breakfast. His boy, sitting at the table, his feet
dangling from the chair, smiling and laughing.

The young boy persisted.

Don't open the door.'' He said again.

The room grew dark.

Luke looked outside, and watched as the trees now shook and swayed
violently amidst an angry grass sea, heaving beneath the dark sky,
as rain began to pelt the glass.

``What are you doing here? Who are you?'' Luke tried
again.

``You're not listening.'' the boy's eyes
narrowed and he continued,

``Enjoy it. Lay down this time. Stay and enjoy
it.''



The kid must have been sick. He wasn't making any
sense.

``I've got a son about your age, he's right in
there'' Luke said pointing to the door.

``Do you have any friends? I'm sure my boy will play
with you. Do you like pancakes? My wife, she makes the best
pancakes.''

``Luke'', the boy cut him off, ``Your son and wife
are dead. They've been dead, since the fire. You know the
deal. Stay here. Enjoy it.''

``What do you know about my wife and son? What do you mean
they're dead.'' He stared at the child

``Boy, I know your sick but you can't talk like that,
it's not right. Listen, listen to them, can't you hear
them, they're in there right now, look I'll show
you'' Luke turned to the door.

``Please Luke,'' The boys face was unchanged, his voice
placid but firm and sure. ``Don't open the
do{\ldots}''

``Hey!'' Luke interrupted, ``now I don't know
what in the hell you're going on about, but it ends right
now. Get out of here you sick freak, get out''! And the boy
was gone.

Luke rubbed his eyes. Had the boy really just vanished? As he
wondered what had just happened, he noticed that his head
didn't hurt any more. Outside the air was now enraged,
thrashing about flinging rain and debris everywhere. It made Luke
more even more uneasy, but he remembered the door, and he shook the
feeling off. He reached once again for the knob, as the roar filled
his ears.

And he grasped the knob and suddenly it was deafeningly quiet. He
turned and looked back outside. It was bright, very bright out, and
the trees and sky were calm. The door was cool to the touch, and
Luke pulled open the door, eager to see his family.

Black. Charred wood. Everything, all of it, consumed. HE steeped
through the crumbling doorway. The burnt skeleton of walls now
surrounded all the ash and rubble that was once his home. Outside,
surrounding the house were hundreds of people, just starring. Near
the pipes where the sink had been, lay the dark remains of a woman
clutching a child.

He couldn't breathe, he couldn't swallow. Grief and
sorrow were throttling him, and suddenly he let loose in heaving
spasms as he ran to his family. He knelt, sobbing, over what was
left of them.

``No'' he uttered

The crowd erupted in a bellowing barrage of whispers

``You did this''

``This is your fault''

``They came for you''

``Why did you let them die?''

``They came for you''

``No{\ldots}NO!'' Luke screamed, ``I couldn't
stop them{\ldots}''

``I tried to save them'', he continued.

Amidst the churning crowd suddenly stood the boy again.

``I asked you not to open the door this time. I asked you to
stay on the other side.''

``I{\ldots}I tried to save them'' Luke sputtered
out

``No'' reasoned the boy, ``no, you damned them. You
dug too deep into our affairs; you stuck your nose in our business.
It was you that did this to your wife. To your son. You are
responsible.''

``I tried{\ldots}I came home{\ldots}the flames, they were
everywhere'' Luke carried on, distantly.

``There's more.'' Said the boy,
``there's more for you''

``No, it doesn't matter now'', Luke said sitting
up, looking at the boy

His hollowed eyes and emotionless gaze should have terrified
Luke.

``You can't do anything to me now{\ldots}just kill me.
Kill me''

The boy's brows furrowed, his face twisted, pulled and broke.
He smiled, and then began to laugh.

``Kill you?'' He said regaining his composure,
``Why? Why would I kill you? No. We have something much worse
for you.'' And the crowd's accusing chants began to
bleed through the boy's speech. They screamed now. Angry,
haunting, they pierced through Luke's hands as he covered his
ears.

``No, NOO!'' he screamed as he began to beat his head
against the rubble. But it did nothing to lessen the shrieking
crowd. He had to end it. He saw the pipe, sticking out of the
foundation. Its jagged end would easily drive through his
head.

He stood, the cries and screams still pursuing and punishing him.
He took a breath and slammed his head down.



Luke awoke in a bed. He stared at the ceiling and searched his mind
for his surroundings. He couldn't remember a thing. His head
ached, pounded as he struggled to sit up. He was in a clean white
room.

There was a noise. Familiar. Welcome. 

 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\bf The Truly Horrid Reflection}
\by{and Into}





The shadows trickled through the alley like the breath of an aging,
slightly obese hard-boiled cop in the middle of extending an
over-wrought metaphor. But even in the face of a dark alley opening
up like the maw of blackest Death itself, I wasn't afraid--I
have a Beretta, and I have the name Bavarious. Luke Bavarious,
NYPD.



My partner Rogue was busy working a tough murder case. Rogue was
chosen as part of a task force to catch the Bronx Butcher, a serial
killer with a hobby of hunting and taunting his would-be pursuers.
Some men have all the luck. I've been put on the toughest
beat of all: noise complaints.



There are noises out there--a car door slammed, an alarm in the
night, a clown horn comically honked too loud--noises that wait in
the shadows, only to surprise and rape the sweet ears of the
innocent citizens of New York. But not if Bavarious has anything to
say about it. Luke Bavarious.



The alley off 42nd street is home to many things. And apparently
some of them make noise, because I've been called to
investigate. Staying just inside the cold cloak of the shadows I
edge down the alley. I saw a figure perched on a dumpster, his back
to me. He was sobbing and crying.



It's for nights like this I joined the force.



``New York Ordinances state that excessive noise is punishable
by fines not exceeding one hundred dollars for the first
offense,'' I said, smirking. ``But I bet that
you're a repeat offender, huh? You should have picked just
one: sobbing OR crying. But you've just gotta be a loud son
of a bitch and do both, don't ya? Well, I guess you just
weren't planning on the icy justice of Bavarious--Luke
Bavarious--were you? Now turn around.''



I raised my loaded Beretta, cocked it, and pointed it directly at
the figure's back, as per the NYPD protocols for how to
handle the grief-stricken.



``I said, `Turn around,''' I repeated, more
loudly and even more smirkingly. But still at a reasonable decibel
level, so as not to disturb the peace. The peace I've been
hired to protect.



``Excuse me, sir,'' the crying figure said between,
frankly, unnecessarily loud sobs. ``But you don't want
me to turn around{\ldots}.''



``Sure I do. I have a loaded, sleek, cocked Beretta pointed at
your back, so you better turn around,'' I said. I went ahead
and cocked the Beretta again, just for the effect, and because I
goddamn love me a good Beretta-cocking.



``Okay, you asked for it,'' the thing mumbled,
uncharacteristically low in volume.



From the gutter above, water-trickles breezed through the alley as
it turned toward me, and began slowly inching into the light.



First its combat boots emerged from the darkness. Then its knee.
Then its leg. Then its pelvis and hips. Then its chest actually
seemed to emerge slightly before its stomach, oddly, but its
shoulders came out next, just as one would anatomically expect.
Then its neck (it is kind of limboing now, for some reason).
Finally, its head came into clarity in the dim light.



If you could call it a head. His face was horrid. There was a
superfluity of purple scars. There was blood trickling from an
empty eye socket and his sole ear was ugly. There was no nose.
There were no lips. There were bruises and lumps all over the
cheeks. There was only thin stubble for eyebrows. Although there
was a well groomed and handsome mustache, this could not make up
for the fact that there were deep gashes and uneven scar tissue
across the forehead, the chin, the mandible{\ldots}



I really could go on, but the point is, he is an ugly motherfucker,
like burn-ward ugly, and the still-sobbing thing stared at me for
quite some time while I noted, like an obsessive cartographer,
every curve and contour of its face. In {\em excruciating} detail.
The thing's neck was a bit small in circumcrence compared to
its body, too, by the way. About 17% too small.



My exhaustive cataloguing of the ugly bastard complete, I finally
took a step back, in narratively delayed astonishment. I had to
grit my teeth to keep the vomit down. Damn bourbon and peyote
cocktails.



He took three more steps forward. ``I told ya,'' it
said.



If there's one thing Luke Bavarious hates more than loudness,
it is people or things that rub it in your face when they are
right. I shot the sad, monstrous I-told-ya-so in the jaw a few
times, adding more holes to the disfigured jerk. The bullets hit
the face terribly powerful. The gunshots rang out, more audible
than I would have preferred--but it is a necessary evil. Lifeless,
the beastly thing slunk anticlimactically to the asphalt.



But at his side some object fell--what is this--Strunk and
White's {\em Elements of Style}? Its pages unfurl, revealing
a check, signed ``Luke Bavarious, NYPD.''



I now recognize at my feet the broken body of the copy editor I had
hired to read over a draft of my memoir, the man who had
disappeared after receiving my papers and my first payment, the man
I thought had conned me and run off. I see him and what I have done
to him, what every mixed metaphor, switched tense, and redundant
adjective had driven him to become, what it drove him to do to
himself.



I tasted my tears and vomit mix into a martini of misery. I saw a
horrid reflection. Suddenly, I was sobbing. And crying. 

 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{The Horrid Realization}
\by{Baron von Eevl}



I stepped from the glare of traffic. The time had come again. I was
in the police station on 42nd street in New York. My hand shook
slightly with the bic pen I held in my hand. The matte white pen
had leaked in my pocket. Another shirt ruined. I am a desk jockey.
My name is Detective Luke Bavarious. I dislike this work.

People had been complaining about a drunken officer in their
neighborhood on his beat. I was transferred off the streets because
of these disturbances.

I edged into the Sergeant's office. I saw the tall, handsome figure
of the man I once respected sitting in his chair, facing towards
me. He was sighing. I raised my finger and slurred a series of
vulgar insults at the sitting figure.

``Bavarious, you drunken fool.'' The captain bellowed.

``Turn around!'' I shouted.

``Beggin' your pardon, Detective,'' he said, ``I'm already facing you.
If I turn around I would be facing a wall.''

``Sure I do. I'm a better cop than you could ever be, McClenaghan'' I
replied.

``Okay, that didn't even make sense,'' the sarge mumbled as he began
to turn red.

Fabian McClenaghan was my Sergeant. He and I joined the academy
together years ago and quickly became friends. He and I would share
all our secrets together at the shooting range and promised when we
died we'd be buried together there with our trusty barettas, shiny
sleek and deadly.

``Give me your badge, Bavarious.''

I inched forward and began to sweat all over. My ductile muscles
clenched and began to shiver. First my feet, deep in non-uniform
combat boots. Then my legs. Then my chest. Then my head. If you
call it a head. My head was so clouded with liquor I could barely
think. Was that what you called it? A head? It's that thing on top
of your neck. The one with all the holes.

I took a step back in astonishment. I gritted my teeth to keep the
vomit down.

McClenaghan stared at me with unbridled hate and shame. Ashamed of
hate.

``You look like you're going to be sick, Bavarious'' he grumbled,
concerned. ``Do you need me to grab my trashcan for you to throw up
in?''

``Hey buddy!'' I screamed. ``I don't need no trashcan from the likes
of you!'' I then vomited. The horrid cocktail of blood and last
night's spaghetti dinner came up and spilled all over the
Sergeant's floor, looking like some alien had died and it's guts
were spilled all over the floor of the Sergeant's office on the
floor.

``I told ya,'' he said.

I screamed and began to run away from him. He waved his hand high
in the air and screamed after me.

``Bavarious, give me your gun and your badge, you drunken fool!'' He
screamed.

``McClenaghaaaaaan!'' I screamed right back at him.

It was too late. I was running through an endless maze of cublicles
each as similar as the last. I ran faster. As I ran, I vomitted a
horrid smelling liquid of putrefaction all over my pen-ruined
shirt. Pen and vomit ruined. And spaghetti sauce. As I ran, others
began to run too, running from the awful weird vomit. The first
person ran faster than the second. The second person ran faster
than the third. The third person was not running very fast because
she was a woman and I'm not comfortable describing her further. The
second person slipped in the vomit and the first person easily
outpaced him. The third person was elsewhere at that point. Maybe
vomiting.

Being drunk, I began to see horribly awful images. A spider. A
person who is also part spider. A butcher's knife. A young boy, to
be respected and listened to, lit from below and looking very much
serious and respected. These were the typical hallucinations I had
when drunk, which causes horrible hallucinations.

My head smashed into the door terribly powerful. Muscles were
strained and torn as my head jerked to the side, smearing the
glass. I fell and landed on the hard linoleum flooring. Dazed I
vomited again and again. I felt the surge pushing back
rhythmically. I ran outside but continued to vomit. Spaghetti
hitting the pavement. Splatter hitting my shirt. Blood showering
me. I felt my own blood from the side of my mouth fall and drip. I
kept vomiting. My stomach was empty. I staggered. I tasted my
dinner and blood mixed into a horrid cocktail. It tasted like
vomit. My badge sparkled on the side of my waistband.
Bavarious.

I picked myself up and stumbled over to a mirror. Suddenly, I was
in my apartment. Suddenly, I was sobbing. 

 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
