%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{The Death Hamsters}
\by{Part of Everything}





Luke Bavarious strolled calmly through the mall, one hand
absentmindedly stroking the cold metal of the trusty Baretta in his
pocket. ``I need a pet,'' he thought, and he made a beeline for the
pet store at the end of the strip.



Suddenly a little boy sitting on a mall bench yelled out. ``Hey
mister! I don't think you should go in there,'' he hollered.



Luke squinted at the boy and drew closer. ``Why not?'' he
inquired.



The boy looked all around and then whispered in a hoarse voice, ``I
saw a man go in there earlier. He looked insane. He had a bag full
of something lumpy. I didn't trust him. He came out without the
bag. Nobody has come out since.''



Luke laughed. ``Balderdash,'' he chuckled, and strolled off towards
the pet store. The boy slumped in his seat with a frown.



Luke walked in through the door and the door chime beeped to signal
that a person had entered. He looked around and there was no one
but he didn't really care. He knew someone would come up when he
needed to make a purchase.



He tried to decide what kind of pet to get. There were dozens of
animals. He looked at some fish and then sadly shook his head. ``Too
watery,'' he muttered to himself, and moved on. There were some
green lizards there. They stuck to the glass with their toes and he
was fascinated at this miracle of God. But he decided against it
because they might decide to stick to him and then what would he
do.



He saw puppies and kittens that were so cute that Luke choked back
a sob of joy. He had had a puppy when he was a little boy but one
day a burglar was running through his backyard where the puppy was
playing. The burglar was evil and the puppy was in his way. He
picked up the puppy and twisted it in half and then threw the
bottom half against Luke's window while he was sleeping. Luke woke
up screaming and barfed. He had never forgotten that day. He wiped
away tears thinking about it.



He decided he wanted a hamster. They were so cute. The clerk had
not shown up yet and he began to wonder. He looked all around but
couldn't find her. Then he saw the door at the back was open a bit.
So he went there and when he looked he saw a sight that made him
scream very loudly.



The mangled corpse of the clerk was lying on the floor. There was
guts everywhere. She was covered with bloody hamsters. They were
evil hamsters and they were eating her like piranhas not in
water.



With shaking hands Luke drew his Baretta. He was ready to shoot but
then something soft landed on him. ``What the'' he said and looked
over his shoulder and he saw what he thought was a pom pom. But it
wasn't. It was a hamster. Then another one landed on his other
shoulder and 2 more on his head. Then they hissed and lunged.
``Hhh,'' Luke screamed as they ate his face.



A superhuman strength came over him then and he flung all of them
off. He shot some but there were too many. He could hardly see
because his eyes were full of blood. He tripped over a bag of dog
food and then he got an idea. He pulled his lighter out of his
pocket and lit the bag of food. It went up in flames and blocked
the hamsters. The hamsters shrieked and burned. Luke took his
chance and ran out.



The boy was waiting there, still on his bench. ``I told you,'' he
yelled at Luke. ``Something was weird. You should have
listened!''



Luke stumbled over to the boy. ``I'm so sorry,'' he choked. ``I should
have respected you. Listened to you. I didn't because you're only
10 years old. I was wrong.'' He pulled a chocolate bar out of his
pocket and gave it to the boy. The boy looked at him with a big
smile and shining eyes and was happy.



By then the police were there. One of them pinned a medal on Luke's
chest. ``You're a hero, son,'' he said in a deep voice with emotion.
``There was an insane man who put evil hamsters in the store. He's
in jail now. You stopped them from killing us all.''



Luke was proud. That night he was in the paper.



The End 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Son Of Bavarious}
\by{Madcosby}





Luke had walked these streets so many times, yet tonight they
seemed so unfamiliar. Clouds gathered ahead, and made the dark even
darker. Alleys were so dark - black as culture - and the constant
scurrying of rats and big cockroaches seemed to come from
everywhere.



Maybe it was all in my head, Luke Bavarious thought. Maybe I've had
enough of this job. For tonight was his last night as a cop, and he
was going to retire. He was the age of three third graders on
summer vacation.



Each alley he passed reminded him of his past here on East Dark
Chill Street. He remembered the time he saved that elderly lady who
turned out to have a swamp tentacle that attacked him and killed
his first partner, Jack Dynasty. He saw the mirror store that had
burned down after his reflection tried to burn down the
neighborhood.



Then he saw an alley he had never seen. Or had he? He had walked
these streets so many times he was shocked. The cold grasp of
surprise gripped his spine like the stickyness of masking tape on
soft paper. A figure, cloaked in darkness, stood at the end of the
alley. He pointed at Luke.



``Walk away{\ldots} '' it said, in a voice that made Luke's heart skip a
beat like a record player in the back of an off-road van. Luke's
adam's apple swung like a vertical pendelum, ``Come out and let me
see you.''



The shadow screamed, ``You'll have to kill me first!'', and reached
into his long trenchcoat that he had been wearing all this time and
pulled out a Colt 45 Shotgun.



Luke didn't hesitate. Chill Street had taught him wasting a second
could mean your life. So he pulled out his Beretta, which was also
retiring tonight. He pulled the trigger so fast, and six bullets
vomitted from the barrel.



One struck the shadowy figure in the arm, by the elbow. But the
creepy shadow did not fall.



``Nice try. But you can't kill what isn't there!'' And with that, the
shadowy figure was gone.



Suddenly, it was raining. And more suddenly, Luke felt a wound in
his arm, right where he shot the creature. Blood oozed from his arm
like mucus from a child with a cold from too many snowball fights.
Luke fell to the ground, clutching the wound.





The shadow emerged once again, and stood above Bavarious. In the
light, Luke could see clearly that the monster had the same
features as he: tall, well built like he worked out at a gym twice
a week, and a moustache. A dark moustache. But his murderer was
younger, like a child who was probably a fourth grader. It was like
looking in the mirror. A mirror of pain and agony, a place where no
one should see their reflection without remembering the pain of
losing a puppy or maybe a grandfather if youre older.



Now, without the echo of the alley, the doppleganger's voice was
not muddled by the darkness and sewers of the alley.``I cant let you
retire, Luke. I'm taking your job.'' It sounded to Luke like he was
listening to his own message on an answering machine. It was his
voice.



Luke turned cold. This was the end. He knew it. He wished he could
hold his wife one more time; he wished he could scream at the top
of his lungs and make the monster go away. But instead, he grabbed
his badge, and his trusty Berreta, and handed them to his killer.
It was time to pass the torch to a younger generation of cops.
That's what tonight was all about, Luke finally understood. The
future of law enforcement was children.



``Thank you, father.'' And with that, the apparation disappeared.
Suddenly, Luke was sobbing.



Then he was dead. East Dark Chill Street was his tomb. 

 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{The Long Finger of the Law}
\by{Dr Scoofles}





``Listen sweetheart{\ldots}'' I lean back in my chair and slide my feet
onto my desk as I light the cigarette that hangs between my lips
``thats the fee, flat rate, take it or leave it!'' I squint my flinty
eye at the dame sat across the desk from me. Not bad looking,
blonde wig slightly off centre and a few gaps in her kisser but a
man like me can't afford to be picky. A man like me takes what he
can get in this hard cold world.

``Mr Bavarious, you know I'm desperate to get my hands on those
pictures!'' she whispers breathily. She leans forward and as I catch
a waft of her breath I lean back. I bet she wants these pictures,
and bad. I took them last week as she slipped out of her lovers
bed. Her husband would pay to see these. The question is will this
broad pay more? My name is Luke Bavarious and I'm a P.I. I don't
deal in honour and justice, I deal in the truth and the truth is a
mean cold hearted son of a bitch. The truth ruins lives and tears
families apart. I open my desk draw, the envelope with the pictures
sits nestled between my gun and my bourbon. I take out the bottle
and pour two drinks. She takes a drag on the cigarettes and
continues

``I have no money, but I'll do whatever it takes.''

I think about it for a second. I know what she means, women with no
money have one currency that is valuable to a rouge like me. My
eyes take her in, her yellow fingers, scrawny neck and sagging
bust. I decide a man like me can afford to be picky after
all.

``Sorry sweetheart, you better leave.'' I slam back the bourbon and
cock my finger towards the door ``don't let it hit you on the way
out, lady.''



I finish up the second drink and decide I better get around to the
dear husbands house before it gets too dark. No time like the
present to finish this dirty job and get my money. I slip on my
trusty overcoat, pocket the pictures and my gun then slip out the
back door.



Night drew in fast, wrapping itself around me like a dark cape. I
walk quickly, partly to keep the cold out and partly to give myself
some distance. I knew that broad would follow me. Women ain't
smart. I turned to look behind me, let her know I'm onto her game.
Thats when it comes upon me, so damn fast I don't get a chance to
pull my gun. I feel a hiss of breath in my face, I recognize the
foul stench from earlier as yellow fingers scrabble at my neck! I
drop down and kick out, I feel her knee snap and the bone saws its
way raggedly through her meaty flesh. Blood spatters onto my face
and pours into my mouth. I swallow it then vomit gushes from my
mouth, bloody vomit and bile gushes all over my coat and all over
the crazy broad as she scrambles on top of me. Her fingers seem to
grow longer, longer as they feel about my coat. My God, I look in
horror as I see her writhing about, her fingers several meters long
as they feel around inside my coat, searching for the pictures. Her
hands are now two elongated nightmares, the bones snapping and
crackling as they bend and scrape around my fighting body.
Revulsion overwhelms me, I gag and cough as I feel her bony fingers
scraping into my pocket. They withdraw the pictures and in a moment
tears them to shreds. As I black out the last sight I see is her
jaw unhinging as she leans in towards me, to deliver the final
deadly kiss.





Edit - Yeah I just realized I have omitted entirely the
disrespecting of the kids. I can only hold up the feeble defence
that the woman is most certainly being disrespected by our dashing
P.I and is also young (ahem). That'll teach Luke to respect those
slightly younger than him{\ldots} Ahh sorry  
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{The King}
\by{Peas and Rice}





It was a slow week. Sometimes life is like that for a private eye.
I sat at my desk drinking whisky from a bottle, taking big gulps.
The Yankees were on TV. I love the Yankees. It was already dark
outside.



A noise at the door distracted me. A letter fell noisily through
the letter slot. Intrigued I stood up. It was addressed to me: Luke
Bavarious, Private Detective. But no return address.



I opened the envelope and read the typed note inside. ``Mr.
Bavarious, I need your help. My daughter was kidnapped and taken to
the Service Room at Times Square Subway Station. I need her back. I
can't tell you any more than this. Please help.''



An assignment. I picked up my new Colt .45 although I liked my
trusty Baretta too. I made sure all eleven bullets were in the
clip. I might need them. Then I finished the bottle of whisky and
walked out into the New York night, lighting a cigarette.



I walked to Times Square Station. It was mostly empty. Piles of
garbage sat waiting to be collected. The whole place stank like
rancid meat and decaying flesh.



I drew my Colt .45 and opened the door to the Service Room. It was
dark inside but I heard a strange high-pitched sound. It sounded
like a rat. I fumbled for the light switch and a single dull
40-watt bulb lit the room with a sickly yellow color.



It wasn't just one rat, it was a hundred rats! They looked at me
with vacant, black rat eyes. ``Where's the girl?!'' I demanded but
they didn't answer. Then the rats moved aside and a giant rat
waddled into the room. It was the biggest rat I've ever seen, the
size of a Labrador Retriever. It looked at me and then it
spoke!



``You'll never see the girl again. Don't you know she ran away from
home? If only her mother had listened to her! You have only come
for your doom!'' And then it laughed a high pitched ratty
laugh.



``I know who you are!'' I said, and I did. It was the King Rat of New
York! I'd heard stories but never seen it until now. I drew my Colt
.45 and aimed it at the King Rat's head. ``I'll take you down
fast!''



I fired one bullet, then another, then all of them into the King
Rat. The first one pierced his flesh and tore a jagged wound, and
blood pumped out onto the floor making it slick with red paste.
Then the others hit him and his body started exploding from the
force of the bullets. He was like a fountain in Las Vegas spewing
blood instead of water. Finally he fell down, dying. ``Now where's
the girl!'' I demanded.



``Get him{\ldots} my minions{\ldots}'' the dying King Rat said. I turned around
just in time to see the army of rodents descending on me. Their
tiny teeth bit into me, giving me diseases as I tried to fight them
off. I used all my bullets on the King Rat so my Colt .45 was
useless. I hit one but another jumped on my head and tore my scalp
with its claws. I blacked out from the pain as I crumpled to the
floor, covered in rats as they slowly but surely tore my flesh from
my body. I screamed and a rat crawled in my mouth, and I finally
succumbed to the horror of the King Rat.







Edited slightly to better match theme. 

 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{The Six Sides of Evil}
\by{reasonable form}


Barney Flann woke up with a start. With a cube in his mind. A cube
he had never seen before. Looking at his leg he saw his leg hair
barely coming in, because he was 8 years old and his age was
between 5 and 10.

``Barney it's time to stop dreaming!'' Barney's father, Aragorn,
laboriously squeaked.

And then he saw the rectangle that he would instantly recognize in
any situation. Any situation where he was not terrified. And since
Barney was never terrified, any situation.

But now, Barney had become terrified.

Instantly, he sprung into action to repair the rectangular hole in
the sewer under his house.

``Not now father I love you too much!'' Barney suggested to his
father whose veins in his right arm were solidifying into vomit. He
pulled out his auxyacetylene welding torch that he kept on him so
he could weld, and used it to burn the blood that was coming
through the pipe into a solid mass that would fix the pipe.

``That was my mothers blood!'' he yelled to nobody in particular
except for himself he realized in a sudden realization of deja
vu.

As he ran up the stairs to confirm his suspicions that his mother's
body had deflated as the blood poured down the drain. He noticed
another rectangle, but he quickly put it out of his mind and soon
he didn't notice it again. Now that he was in his mothers room he
could see he was correct, and he saw her lifeless body scream with
anguish as it realized its plight.

``THE HORROR!'' he yelped.

But then he noticed something else{\ldots}

``THE HORROR!'' he yelped as he saw that there was a rectangular
sized hole in her juggular.

Could it be that the 3 rectangles he had seen were part of
something bigger? Could it be that they would form{\ldots} the CUBE?
Barney would soon find out that this was the correct case. He
rushed back to see his dying father and discovered him infused with
life energy.

``Father, why are you so energized?'' Barney gulped.

``BECAUSE I HAVE SEEN THE MOUNTAIN TOP AND UPON IS ARE RECTANGLES!''
His father, Aragorn, who was named Aragorn after a particular event
led his father to read Animal Farm, babbled incessantly.

``No it doesn't have to be this way!'' Barney said as Barney pulled
out his Ferrari branded knife and slashed a triangle into his
father's heart so that all of the rectangular juices could flow
safely out. ``thank you son i love you'' his father said as his last
dying words.

And then, his father died.

``What shall I do now? How can I stop this infection of
rectangles!''

But quickly Barney remembered his grandmother, who they had locked
up in their basement ever since her death. He recalled the
basements location and ran to the door. But there was an evil thing
on the door, a rectangle! He ripped out his Saigo auto shotgun
loaded with fourty four magnum cartridges and prepared to fight the
fight.

``This is the most powerful 'handgun' in the world hehe'' he muttered
as he fired the shotgun one handed in the direction of the door.
Instantly, kidney stones rolled out of the door, but the kidney
stones were in the shape of rectangles. It too was horrid. Too
horrid to imagine was possible. But it was that horrid.

And as the millions of rectangles combined to form cubes he knew
that his evil grandmother was the source of it all!

``Who could have created these cubes?'' he recoiled from the vomit
flowing from his mouth and left ear as he realized it was his
grandmother.

And he realized he could not stop the cubes, that he too would be
lost in the face of ev-

``BECAUSE I HAVE SEEN THE MOUNTAIN TOP AND UPON IS ARE
RECTANGLES!''



edited because I can, and because I only want a few misspellings in
my masterpiece. 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{The Old Child}
\by{Smeef}



The chill of the night crept through the streets. I wasn't
even in the Big Apple anymore. I was way uptown.



``I ain't goin' nowhere tonight, Bavarious,''
my partner had said back in the car, stuffing a donut in his mouth.
``That ain't even our jurisdiction.''



If the creeps out there don't follow jurisdiction, then
neither do I. And I'd been tracking this creep for hours,
following on foot block my block.



He was one of those rich creeps. The worst kind. Nice suit but
grey, fat, and scummy. He had a cold sweat running on his
face.



At about 110th Street a kid had stopped me and said ``Don't go after
her. She's weird, man!'' Sometimes kids have the blackest
hearts.



When he turned and waddled into an alleyway, I could see that the
girl was still alright. She was right in front of him, his stiff
hands touching right at her shoulder blades. She was wearing a
schoolgirl outfit. It didn't take a judge and a jury to know
that he was guilty. It sure wasn't gonna take an executioner
to finish the rest.



I stepped into the alley and could see the silhouette of her feet
between his.



``Dead end, pal! No way out! Let her go!'' I drew my
Beretta, and the tactical flashlight illuminated his face as he
swung around.



``It's not me!'' he screamed. ``Thank god{\ldots}
Help me!''



``You have the right to remain silent, and I suggest you do
it! Let the girl go!'' I shouted.



``Get out of here!'' he grabbed the girl and started
flinging her violently.



``Let her go, scumbag!''



He crashed into a dumpster with her, and I saw his head clearly for
a millisecond. I might not get another chance. I might not get
another clear shot.



The flash of my Beretta lit up the alley, red blood sprayed into
the air, and the fat man flopped down like he was deflating.



I ran over to check his vitals. Dead. I looked over to see if the
girl was fine. She was cowered in the corner, crying. I put the
flashlight back on the dead man{\ldots} his guts were torn open like his
torso had vomited all over the place like.



I didn't shoot him in the guts.



No, she wasn't crying. She was laughing. Her awful laugh
sounded like styrofoam on styrofoam. I put the flashlight on her
face. I backed up. She had a face like a ninety-year-old old woman,
a few jagged teeth and black eyes. She had big, bloody hands with
long fingernails. Blood and guts were coming out of her mouth. She
kept laughing.



I shoulda listened to that damn kid.



I aimed again, and she came at me like a spider.


 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{The Ocean}
\by{jidohanbaiki}

The abrasive ocean waters lapped dangerously at his flippered feet.
Luke Bavarious was a marine biologist who took his job seriously.
He set his rusty bucket of herring into the sand with a crepitating
flatulence. In the distance, gray blades pierced the ocean, coming
closer and closer. There was a portentous whirring and clicking,
growing ever louder and more frantic, interrupted only sporadically
by the crash of waves.



Bavarious took fistfulls of herring in his fists. The herring were
slimy and slippery, so he squeezed the herring hard to keep them in
his grip. The bodily fluids from the herring leaked between his
fingers. He proceeded towards the malicious noise of the ocean,
slowly but determined, holding his fists of herring up to the sky,
as if in defiance to God. He stopped once the ocean reached his
hip. The gray blades swarmed around him. Luke smiled bitterly.
``Come and get it,'' he intoned.



Gray beaks poked out of the water, searching, wanting, smiling. But
those smiling mouths opened to reveal long rows of tiny, but sharp,
brilliant white teeth. Luke tossed the disgusting, smashed herring
into the waiting maws. ``Eat,'' Bavarious said, almost cursing.
``Eat!'' he commanded.



The dolphins splashed around him, taking their fill of the herring,
letting the herrings' slimy bodies slide down whole into their
stomachs. Bavarious began to laugh, at first just a chuckle. Then
he threw his fists covered in herring eyes and herring guts into
the air and erupted with demented revelry. ``Yes! Eat! Eat!'' he
screamed, his voice shrill with hysteria.



Luke Bavarious was a marine biologist who took his job seriously.
He was also a marine biologist who would leave no slight unavenged.
Little did the dolphins know that the herring was poisoned.



---



Donny had no legs ever since he could remember. A long time ago
when he was a child, he had lost them in a car accident, or so he
was told. He was also told that he also lost his parents. Every day
after school, his aunt would drive him out to the ocean so he could
swim with the dolphins as therapy. ``You're thirteen now,'' she said
bitterly as she drove him towards the sea. ``Don't you think it's
time you stopped swimming with those stupid fish?''



``They're not fish, and they're definitely not stupid.'' Donny said,
folding his arms over his stumps.



Once at the dock, his aunt rolled him in his wheelchair over the
wooden planks and tipped him into the waters below. ``I'll be back
in an hour,'' she shouted down to him. ``I've got to go to a meeting
at the bank.''



Donny floated, belly up in the ocean, his horrid little stumps
flailing uselessly. Soon, he felt something slippery slide
underneath him. It was his friend, Moon Dancer the dolphin. Donny
petted Moon Dancer's nose as he dreamed of the freedom he would
have if only he could become a dolphin. Then he sensed distress
from Moon Dancer. Donny grabbed the dolphin's head and pressed his
face to it. ``Take me there,'' said Donny.



He grabbed onto Moon Dancer's fin and they sped towards the
horizon. It was a wonderful feeling to move so fast and freely, but
the ride did not last. They approached a contorted figure in the
waters. Donny swam over to the struggling dolphin. ``Star Wave!
What's wrong?'' Donny asked.



Green bile and rust colored blood vomited from Star Wave's blow
hole. Star Wave opened his mouth and vomited out the poisoned
herring bones. Donny screamed and then vomited himself, and soon,
vomit mixed with tears in the ocean water. Attracted by the blood,
a shark appeared and landed a killing blow on Star Wave, putting
him out of his horrid misery and spreading violent red blood
through the ocean.



``Take me to who did this.'' Donny thought at Moon Dancer.



---



Miles away, Luke Bavarious dropped another bucket of herring onto
the sand with a squelch. He took fistfulls of poisoned herring, and
entered the ocean. In the distance, dolphins schooled. ``Come!''
Bavarious commanded, his powerful fists dripping with poisoned
herring entrails.



``You think you're so smart!'' he spat. ``But you won't ruin my
scientific research any longer! I was going to prove that you only
had fish intelligence, but you ruined my data and now I'm the
laughing stock of marine biologists!''



The dolphins did not come, but lingered on the horizon tauntingly.
He pounded the water with his herring fist, making a horrid
squelching noise. He then went farther and farther into the ocean,
until the water was up to his neck. The dolphins then swarmed
around him. ``Eat!'' He said, scattering the herring.



He laughed and laughed. Then he burbled as bitter, salty water
flowed into his mouth and nostrils. Moon Dancer swam up to him and
spat a poisoned herring in his face. Bavarious grabbed the herring
and beat Moon Dancer with it. ``Eat you stupid fish!''



Then a different dolphin swam by Luke's legs, then around his body.
It came out of the water and faced Bavarious. Bavarious screamed.
The dolphin had a human face; it was Donny. Bavarious fainted and
drowned.



Years later Luke Bavarious' bones were found washed up on shore,
but no one ever found Donny's. His aunt was thrown in jail for his
murder. From behind bars, she would mutter about dolphins with
human faces endlessly until one day her cellmate couldn't take it
anymore and strangled her to death. 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{The Horrific Release}
\by{Knuc If U Buck}





I inhaled the forbidden smoke of my favourite Marlboro Reds
cigarettes wistfully. Before I can reflect on the delicious but
deadly flavours of Virginia's finest I begin coughing. Violently.
Shuddering as I pull away the tissue that covered my mouth to
reveal bits of lung meat and black blood. The realisation that I
have lost control of my bowels and bladder hits me as hard as the
foul stench. My face reddens and tears burst from my bulging eye
sockets while I struggle for air. I begin sobbing. My name is Luke
Barvarious and I am a cancer patient and former NYC private
detective. I am about to die.

Recently, there have been rumours of children with terminal cancer
wandering out of the hospital, never to return. I have been asked
to use my detective skills to solve this case on special request
from the Chief of Medicine, Dr. Wolfgang Smith MD. I dutifully
accept.

Night falls after an entire day of a vicious experimental
chemotherapy combined with top secret military radiation. I am also
given an additional cocktail of drugs that enable me to walk under
my own power without doubling over into vividly horrific,
sweat-soaked nightmares. I set off towards the paediatric cancer
ward. Opening the cold sterile doors of ward 42, I immediately
recognise the soft footsteps of a wandering child.

``You there, turn around!'' I shouted down the corridor.

The silhouette disappears into the darkness.

I feared it would come to this.

I instinctively move my hand down to my trusty Beretta forgetting
momentarily that there is no place to holster it on my backless
hospital gown. Armed only with my wits I slink into the shadows
past the nurses station and follow the dark, impish figure through
the hospital and into the woods behind the main building.

Once into the woods I have to use all of my detective instincts to
keep up with my target. I track the child for was seems to be an
eternity, weaving between the thick trunks that guard the forest,
stopping against one every so often to catch my breath and wipe the
fresh bile from my stubble. As we reach a clearing I try to yell
once more, I begin to gasp for air desperately as the drug cocktail
begins to wear off. I grit my teeth to keep the cascade of bloody
lung chunks at bay. Looking up after containing myself I see a ring
of children.

The child I was following is being welcomed into the group. I
notice at this stage the the children are just rotting husks in
varying states of decay. They begin moving in a kind of reverie
cadence. Mesmerised, I pull myself up from the stump that I had
collapsed on and notice that the boy that I followed is beckoning
me to the zombie circle. Despite their gaunt, putrid features, my
detective instincts recognise them as the missing cancer patients.
As I make my way into the group I hear the sound of a dead man
coughing. Turning back, I see my own, fresh, urine stained corpse
slumped over a tree stump with the last remnants of my lungs spread
over a puddle of vomit lying next to me. What really caught my eye
though, was the smile on my crumpled lips. Suddenly, I was
free.



End. 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{The Last Case}
\by{henpod}

Detective Luke Bavarious woke with a snort. Today was the day, the
case to end all cases. This case would be the biggest one he had
ever undertaken and the thought made him nauseous. It had to be
done, It will be done.



He staggered off the urine stained mattress, his foot stepping in
something soft and rust coloured but he didn't care. He was
thirsty, but not thirsty for water, he walked over to his table and
grabbed the bottle of whiskey. He spun the top and swallowed the
horrid cocktail of whiskey and cigarette butts; he began to choke
but welcomed the sensation. It was good to feel something for
once.



His bloodshot eye saw something glint under an old T-bone. He
picked it up and wiped off the grease. It was his badge. It read
``Detective''.

``More like defective'' he muttered to himself and began
a horrible, scratchy giggle which began to get louder and louder,
like a washing machine in a dank, dirty laundrette. His laughter
stopped when he saw his reflection in the dusty mirror. What was
once a handsome chiselled face looked back at him with empty eyes
and a patchy beard like that of a rapist. He began to cry, the
tears ejected from his eyes like the cartridges from his berretta.
The berretta! He grabbed it, and put it to his head, pulling the
trigger. An empty click echoed through the empty room.



``No, not yet. One last case. The Mad Cannibal is still out
there, eating children, I must stop him.''



Ever since the incident in the alley, he was a changed man. He
wanted to die, and had been ready to, but then the Mad Cannibal
began his horrid campaign of terror and only him, Luke Bavarious,
could take him.



Slipping on his stained trenchcoat, loading his Berettas and taking
another horrid swig of brown whiskey, he staggered out like a
scarecrow into the night. He knew where the cannibal was, he had
been following him for weeks to an old warehouse where he would
take his victims and begin the ghastly practice. The sky was dark,
and the rain ran down his face like the bloody tears of the
cannibals victims. Lightning flashed, followed by thunder but
Bavarious wasn't scared, he was ready.



He crept up to the warehouse, and sure enough The Mad Cannibal was
there, towering over his latest victim, a young boy wearing a
hoodie and sweatpants. It was now or never. He kissed his Berettas
and dived head first through the glass window. He landed in a
shower of glass and blood, his eyes scanning the warehouse for the
horrid ghoul, but didn't see him. Suddenly a butchers knife
flew out of the darkness and struck his shoulder, colouring it with
an all too familiar rust. Out of the darkness, a figure emerged,
running towards him with a knife in each hand and murderous red
eyes. Suddenly he fell, the kid had tripped him up!



``Thanks kid, now get outta here'' Bavarious growled,
spitting blood onto the floor.

``But I can help mister, I want to help''

``GET OUT'' Bavarious snarled, raising his Berettas to
scan the darkness.



Suddenly, a horrid scream filled the warehouse and the cannibal
rushed out of the darkness again. Bavarious fired his pistols with
lightning speed, his Berettas vomiting bullet casings. The first
shot hit the cannibal in the stomach and he instantly spewed a
mixture of blood and human fingers. The second ripped through his
eyes, puncturing them like grotesque bicycle tyres. He was still
coming though, and Bavarious needed to reload. With lightning speed
he replaced the spent magazines, but the ghoul was gone again.
Following the trail of blood he found the madman sitting behind
some crates. He was wheezing and giggling in a pool of vomit, blood
pouring out of his eyes like a horrid waterfall.



``Im not going to arrest you'' Bavarious snarled,
``but I am going to kill you. Prepare to die you sick
bastard''



``Luke{\ldots}'' wheezed the rusty figure below.
``You wouldn't kill your brother would
you?''.



A lightning flash filled the room, and it was only then that
Bavarious saw the face of the cannibal in front of him. It was his
brother. An immense pressure of hatred and horror welled up inside
him. He staggered back holding his stomach, his eyes bloating like
a horrid fish. He howled upwards into the night, the vomit
exploding from his tortured innards like a revolting fountain of
misery. Behind him, The Mad Cannibal was gone.






%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{The Very Hungry Luke Bavarius}
\by{Mortonic}





In the light of the moon, a little egg lay on a leaf.



One sunday morning the warm sun came up and pop! Out of the egg
came a tiny and very hungry private detective, Luke Bavarius.



He started to look for some food.



On Monday he ate through some black culture . But he was still
hungry.



On Tuesday he ate through two Berettas. But he was still
hungry.



On Wednesday he ate through three piles of vomit. But he was still
hungry.



On Thursday he ate through four sparkly Bavarius badges. But he was
still hungry.



On Friday he ate through five gooooooold rings. But he was still
hungry.



On Saturday he ate through an entire Baconator! That night he had
stomach-ache!



The next day was Sunday again. Luke ate through one nice green
leaf, and after that he felt much better.



Now he wasn't hungry anymore - and he wasn't a little private
detective any more. He was a big fat private detective.



He built a small house, called a cocoon, around himself. He stayed
inside for more than two weeks. The he nibbled a hole in the cocoon
and pushed his way out {\ldots}



He was a horrid reflection!



He then began to read approximately 500 words of the Bible:



Genesis



1 First God made heaven \& earth 2 The earth was without form
and void, and darkness was upon the face of the deep; and the
Spirit of God was moving over the face of the waters. 3 And God
said, ``Let there be light''; and there was light. 4 And God saw that
the light was good; and God separated the light from the darkness.
5 God called the light Day, and the darkness he called Night. And
there was evening and there was morning, one day. 6 And God said,
``Let there be a firmament in the midst of the waters, and let it
separate the waters from the waters.'' 7 And God made the firmament
and separated the waters which were under the firmament from the
waters which were above the firmament. And it was so. 8 And God
called the firmament Heaven. And there was evening and there was
morning, a second day. 9 And God said, ``Let the waters under the
heavens be gathered together into one place, and let the dry land
appear.'' And it was so. 10 God called the dry land Earth, and the
waters that were gathered together he called Seas. And God saw that
it was good. 11 And God said, ``Let the earth put forth vegetation,
plants yielding seed, and fruit trees bearing fruit in which is
their seed, each according to its kind, upon the earth.'' And it was
so. 12 The earth brought forth vegetation, plants yielding seed
according to their own kinds, and trees bearing fruit in which is
their seed, each according to its kind. And God saw that it was
good. 13 And there was evening and there was morning, a third day.
14 And God said, ``Let there be lights in the firmament of the
heavens to separate the day from the night; and let them be for
signs and for seasons and for days and years, 15 and let them be
lights in the firmament of the heavens to give light upon the
earth.'' And it was so. 16 And God made the two great lights, the
greater light to rule the day, and the lesser light to rule the
night; he made the stars also. 17 And God set them in the firmament
of the heavens to give light upon the earth, 18 to rule over the
day and over the night, and to separate the light from the
darkness. And God saw that it was good. 19 And there was evening
and there was morning, a fourth day. 20 And God said, ``Let the
waters bring forth swarms of living creatures, and let birds fly
above the earth across the firmament of the heavens.'' 21 So God
created the great sea monsters and every living creature that
moves, with which the waters swarm, according to their kinds, and
every winged bird according to its kind. And God saw that it was
good. 22 And God blessed them, saying, ``Be fruitful and multiply
and fill the waters in the seas, and let birds multiply on the
earth.'' 23 And there was evening and there was morning, a fifth
day. 24 And God said, ``Let the earth bring forth living creatures
according to their kinds: cattle and creeping things and beasts of
the earth according to their kinds.'' And it was so. 25 And God made
the beasts of the earth according to their kinds and the cattle
according to their kinds, and everything that creeps upon the
ground according to its kind. And God saw that it was good. 26 Then
God said, ``Let us make man in our image, after our likeness; and
let them have dominion over the fish of the sea, and over the birds
of the air, and over the cattle, and over all the earth, and over
every creeping thing that creeps upon the earth.'' 27 So God created
man in his own image, in the image of God he created him; male and
female he created them. 28 And God blessed them, and God said to
them, ``Be fruitful and multiply, and fill the earth and subdue it;
and have dominion over the fish of the sea and over the birds of
the air and over every living thing that moves upon the earth.'' 29
And God said, ``Behold, I have given you every plant yielding seed
which is upon the face of all the earth, and every tree with seed
in its fruit; you shall have them for food. 30 And to every beast
of the earth, and to every bird of the air, and to everything that
creeps on the earth, everything that has the breath of life, I have
given every green plant for food.'' And it was so. 31 And God saw
everything that he had made, and behold, it was very good. And
there was evening and there was morning, a sixth day. 

 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{The Screaming Night}
\by{Oatgan}





The woman's shouting screams shattered the dark silence like
a broken bone after a high fall. ``Help meeee!'', she
screamed. There was no answering from the good citizens. At the
moment at least. Luke Bavarious, was not exactly a good citizen. He
was less than good, and rushed towards the attack at fast
speeds.



Earlier in the day, Luke was at a tavern. Drinking margaritas and
eating submarine sandwiches at the pool as he always does.
Luke's informant Manitoba approaches.



``Care for a light, B?'' Manitoba holds out a lighter,
literally vomiting fire.



``No way, Manitoba. I don't smoke after the accident.
You know that. Remember?'' Luke responded.



``Oh yeah'' said Manitoba. ``Look, I came here to
tell ya bout all these attacking that happened recently. Word is
some kind of half-man half-monster half-dog is wandering around in
the night and killing people in the dark alleys.'' Luke
finishes his drink and puts the sandwich in his pocket. He got up
and got another drink. This time it is a scotch on the rocks. Cheap
just the way he likes it.



As Luke is quickly racing towards the female screams he hears a
distant rumbling coming from the same direction as the female
screams are coming from. He thought time was running short. Wind
swept through his windswept hair as the cries drifted closer and
closer. He then heard a sound that sounded like a sharp object
tearing into flesh. The girl screamed no more. She was killed
before she was saved.



Luke continued to give chase. He ran until he was tired from
running to much. He ran more and followed the rumbling through the
alleys as the monster left strewn garbage and blood streaks in the
ground. He passes a homeless boy looking through a trash dumpster.
He stops and asks him if he has seen anything suspicious. The boy
replies negatively. He has seen nothing. His mind might change if
he gave him the sandwich sticking out of his dark flowing powerful
trench coat though. Luke says no. He continues chasing.



Luke came to a dead end. DAMMIT! What is that? A sewer? Luke heads
down into the city sewer system. The stench is bad. Like rotting
meat from last Thursday. He marches onward. Along the way he finds
spare body limbs. Owner, unknown. He also sees the homeless boy
again. This time the kid gives Luke a warning.



``You will not catch him. And you will not defeat him. He is
too evil.''



``What the hell do you know, kid.'' He says.
``You're just a freakin' homeless
kid.''

Luke pushes the boy down as he sloshes through the filth. The boy
falls face-first into the sewage. As Luke wades he sees a door at
the end of the tunnel he took. The door has a sign on it that reads
THIS IS THE LAIR A MONSTER FAREWELL TO ALL WHOM ENTER. Luke pays no
heed and barges through. He sees the homeless kid again.



``How did you get here, poop-head? I thought I ran past you
and I did!''



``Inconsequential,'' said the homeless boy. The boy then
shape shifted into a monster that looks kind of like a dog. Luke
drew his Beretta and fired wildly into the dog-monster. The monster
showed no signs of being affected like bleeding or flinching. In
frustration Luke threw the Beretta at the monster.



``I warned you more than once, human! Now you pay for not
listening to me and not giving me a sandwich!'' The monster
lunged at Luke and pinned Luke to the wet slimy ground. Luke could
not move. He could only struggle. Luke's face was peeled off.
The monster ate his face.



The End?



Writing this was actually quite fun. Thank you, Mr Biddick! 

 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter[The Orchestra of Nothing]{Luke Bavarious and the Orchestra of Nothing}
\by{Lynxifer}



I pulled my trenchcoat closer to my body, as the cruel autumn winds
flicked and bashed against my weary frame.

``Some night for a job.'' I announced to myself in my
head. Like every true pee aye, I felt it required that I narrate my
life, to the voices in my head, the voices that guided me and kept
me safe from the others.

The run down dreary doors passed me in a blur as I walked swiftly
down a street with eyes peering out of every window, my gun
shivering under my layers, eager to spill out and deal in its holy
cleansing.



I wasn't an angel, I wasn't some holy pariah. I was the
encapsulation of a human devil, ready to pass my judgement on you.
All of you who thought I was the ripe target of abuse and of
mocking, all of you who thought you were better, my gun and I are
always ready to knock you down a peg.



The street twisted into another and then, another as the wind raced
around me, the howling growing like a hungry wolf on the hunt. My
target was the old opera house off 3rd and 29th. In it's day,
it was probably a beacon of talent and beauty, but the sands and
ebbs of time had reduced it to a third rate nothing, its former
glory haunting it, the same as the drug dealers and scum that hound
its bricks and mortar.

The streets finally moulded into a conclusion as the opera house
came into view. Somehow I didn't expect it to be as clean and
fresh as it was. I rubbed the base of my gun's magazine as I
approached my goal, taking tentative steps. Although hired by the
manager of the house, I didn't trust the guy, he oozed a
slimy confidence that put me off base when he called me and
enlisted my services, his voice full of practised bravado and false
compassion.



The doors stood between my fate and me, I took hold of one of the
weathered brass handles and tugged with considerable force, which
yielded entrance to me. Taking the opportunity, I dashed into the
poorly lit entrance foyer and out of the harsh winds that had led
me here.

Inside, the manager was waiting for me. He was as grimy as I had
imagined, his hair slicked back like a funeral director and his
suit oddly positioned.

``Well har there, bud! You must be thar Private
Investigator.'' He said to me, his hand outstretched to shake
mine.

I did things my way. I looked at his hand, wrinkled my lips at it
and left my hands firmly at my coat.

``Hello.'' I said calmly.

He seemed genuinely upset at my refusal to meet him half way as he
retracted his hand. I felt vindicated as he ran his fingers through
his hair and wiped the oily residue on the back of his
trousers.

``Ahm sure I made myself clear on the telephones.'' He
said to me, fingering his top pocket slightly. ``Ah just need
you to find mah missing Orchestra.''

I sneered slightly. The fact that he claimed ownership of such a
beautiful thing when he himself had none, was sickening.

``I'll find them, don't worry.'' I replied,
offering no form of comfort in my voice.

Seeing that his snake oil charms would get him nowhere with me, He
slinked away, his greasy smell following him as he slinked into the
pitiful box he undoubtedly called an office.



I loosened my coat somewhat as I began my quest inside the house;
my first stop was the pit, as that was usually the location of an
Orchestra.

The corridors I found myself in were full of regal decoration and
warm lighting. I had to stop myself from examining my surroundings.
I had a job to do and I was going to do it.



The corridor gave way to the auditorium as I breached the unlocked
doors with my trenchcoat flapping in the slight wind coming from
the stage, the entire room dark and lit for a performance. I walked
with my chest puffed outwards as I approached the pit, my right
hand firmly on my gun, its cold metal serving to keep me
attentive.

I twisted my head as I peered into the foreboding pit and saw
nothing but empty seats and scores strewn around the floor. I was
about to stand up and abandon this line of inquiry, until the wind
from the stage picked up to a whistle. This was a break I needed as
I grabbed my gun and cocked it with deliberate action to put fear
into whatever was playing this game with me.

I walked towards the steps with army style stealth and crept up
them, peering towards the undecorated back of the stage.

As I slinked across the stage, I felt the wind intensify, until all
of a sudden the stage lights erupted into a ball of white-hot light
and illuminated the entire stage from its murky prison.

I twisted around with precise movement, my gun raised and ready
shoot, but became filled with horror was I surveyed the scene
presented to me.



Although the lights on the stage were blinding and piercing, my new
tormentor had left a small channel for me to survey my audience.
Ghouls. Zombies, Rotting Corpses. Call them what you will, they
were now watching my every move, their rotting flesh falling off,
and congealed blood spilling to the floor like rancid rain.

Whatever was going on, I wanted no part of it. This was not my gig,
I hadn't signed up for this, and it was my time to
leave.

Fate had conspired against my quick escape and had removed the
steps to my freedom, leaving only an expanse of nothing.



``AAAAAAAnd now!'' A voice rang out from behind me. I
twisted and saw a twisted figure of bone and seared flesh holding a
wireless microphone, wearing the same greasy suit as the
manager.

``The one, the ONLY. Luke. Bavarious!'' He announced to
the deathly audience.

I raised my gun to his head, and lined up the sights to his head. I
didn't like his style and thought he needed to learn of
justice, Bavarious style.



A noise, stopped me from enacting his punishment. A deathly clatter
of strings and pipes, arranged in a screech and howl. I spun
around, my gun ready to deal with this new nemesis as the source of
this new sound became apparent.

An orchestra of 12, probably the very orchestra I had been sent to
find, were there. Each in dirty and torn tuxedo's,
they're appearance was no better than the crowd of demons
watching this harrowing event unfold. Some were missing jaws, eyes,
some even missing limbs, but each player managing to play their
instrument of death in the symphony of horror.



I'd had enough of this game, the rules weren't to my
liking and the umpire was bent.

Like a holy angel, I raised my pistol to the Tuba player. Obviously
gluttonous in his previous life, I decided he was the first to
experience cleansing. I aimed for the largest portion of his head,
held my breath and squeezed the trigger.

The bang of the gun had silenced the approaching orchestra as the
round rippled through the air and smashed into the players head,
but bounced off like a ball on a wall.



I shook off my surprise and aimed for another, this time it was a
violin player. A once cute broad, but her new bandmates had
corrupted her into join the legion of the dead. Again, aiming for
the head as the band started playing their deathly march and
advancing faster this time, I peered down the sights and
squeezed.

Another veil of silence enveloped the house as the same happened
again, the round bouncing off harmlessly.



I could have fired the rest of my chamber on the advancing horde,
but I didn't think my metal protector deserved that
fate.

As the band approached, I heard the crowd moan and scream. I
guessed that this was the undead version of a cheer as the players
came closer and closer to me, closer to whatever endgame they had
decided for me.

I wasn't about to grant them this, I never planned to go out
this way and I had a long way to go yet.

As I considered the situation, the pieces of the puzzle fit into
place. I'd worked out why the orchestra had gone missing, why
they had turned into the grisly afterimage and why the audience had
joined them in the ranks of the undead.



Grasping my angel, I placed the barrel under my chin, aiming for my
precious grey matter and I squeezed.



The round screamed through my head and smashed through my
skull.



As I fell to the ground, I saw the orchestra scream out in pain and
begin to disintegrate, as if the blinding gleam of the stage lights
were holy light, coming the cleanse them.

The Audience was sharing the same fate, as they melted into a gloop
and started to run towards the stage area.

With my last breath, I placed my gun back in its holster, my job
done.



Two days later I woke up in the hospital. I could feel a bandage
wrapped around my head, holding my essence in.



``Well done.'' The cute nurse said, seeing I was awake.
``You found the orchestra.''



Like the Mounties, I always get my man. 

 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{The Horrid Erection}
\by{Cheesus Christ}


I stepped into the stall. The urge had come again. I was in the 4th
floor men's room of the Tri-County Technical College library.
The sleek basin of water in the toilet bowl beckoned for my cock
like a lost lover. I am a chronic masturbator. My name is Luke
Bavarious. I like to masturbate.



Sure, people had been complaining about weird noises coming from
the campus restrooms for about a year now, ever since I enrolled
last spring. Signs were placed on all the bulletin boards and
restroom entrances: ``RESTROOMS MONITORED BY
SECURITY.''



I edged my swollen crotch closer to the rim. Suddenly, I noticed I
was not alone. Peeking under the stall I saw a dark pair of legs
occupying the stall next to mine---the handicapped stall. I
thought I heard the faint sound of sobbing. No matter, I lowered my
fly and gripped my quivering organ.



``Keep it down, buddy,'' I shouted through the stall
divider.

``(Sniffle{\ldots} sob)''.

``KEEP IT DOWN!'' I shouted again.

``(Sniff){\ldots} beggin' your{\ldots}
(sob){\ldots}pardon,'' said the legs.



I began to pull on my delicate member, but found it impossible to
concentrate thanks to my weeping accomplice. Now, I've wanked
it co-op before; never bothered me. Hell, I've even wanked it
with people crying (Grandma Packard's funeral, `natch),
but this time? This time I just couldn't even raise a
chubby.



A breeze trickled over my waggling dick as I slapped the divider.
The sobs had grown louder, though now they were mixed with a deep
grunting sound. ``Shut the fuck up man, I can't even
think!'' I cried, though the noises only responded with
renewed intensity.



Enough is enough. After one last bang I knelt to the floor and
peered up at my discourteous neighbor.



``SHUT THE FU-'' and I could say no more. The occupant
twisted its convulsing body toward me. First its reverberating
forearms. Then its jiggling ball sack. Then its penis. If you call
it a penis. Its texture was horrid. There was an abundance of
purple scars. There was blood leaking from open sores along the
shaft and from its urethra. There was no hair. Only pulsating
veins.



I banged my head on the bottom of the stall in astonishment. I
gritted my teeth but spurts of vomit flew from my
mouth---Quiznos. He took a step towards my defenseless head and
I saw his Johnson glisten with lubricant in the dim florescent
light.



He screamed and arched his pelvis toward me. His stub of a hand was
flying furiously across his pole, which I could tell was ready to
commence its brutality. Then, he pulled the trigger.



His body recoiled as he loosed an animalistic scream. I heard a
splatter hit the floor beside my head and looked up just as his
One-Eyed Snake sprayed my gaping mouth with a wad of jizz. It kept
cumming with the assistance of his adrenaline. Only a split second
passed before he squeezed off another round onto my neck.



His Thing was inches away when it fired point-blank into my throat.
He slapped my head with his dick terribly powerful. I could see its
strained muscles as my head jerked to the side, smashing into the
floor. Dazed, I felt him fire again and again into my nose, eyes,
ears. I felt his recoil pushing back rhythmically. Man-juice
hitting the pavement, showering me. I felt my own cock fall limp
again the floor. He kept firing, but his magazine was empty. He
staggered. I tasted his semen and blood mixed into a horrid cock
tail. He stepped over me. A library card dropped the floor.
Bavarious.



I looked down at my hands and saw a horrid erection. Suddenly, I
was sobbing. 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{The Creature / Dying}
\by{brylcreem}


\section*{The creature. From the sewers.}

This wasn't going to happen. Again. Gene Beaver pulled off his light
suede jacket and sighed. Then he sighed again. He had started as a
trainee sewer inspector three months ago and immediately heard the
rumors. Rumors of a creature in the sewers.

Three years ago he had been happy. With a kid and another on the
way. Wife at home, making dinner. The whole nine yards. Then he came to
town. The kid. The prodigy they called him. Gene hated him. Hated him
enough to kill him? Perhaps. Or perhaps not. Either way, Gene hated him.

Two and half months later, his wife left him. With the kid. The kid from
out of town. Gene hated him, but he couldn't do anything about it.

It was Christmas, but Gene didn't feel jolly. Didn't feel jolly at
all. His wife was gone with the kids, and the kid and Gene was
alone. Alone at Christmas. The worst time of year to be alone. It was
sad. Suddenly, Gene sobbed.

No, this isn't right! He thought. Gene decided to change his life, to
make it better. A new life, in a new town.

Three years later, here he was. In the sewer, with a creature that
didn't show up.

Suddenly, Gene heard a sound. A sound from behind! Suddenly he turned
and came face to face with it! The creature! The rumors were real! The
creature was real!

Gene died quickly. In the sewers.

200 miles away, Louise shuddered in her sleep. The man next to her woke
and looked at her. And smiled!

\section*{Dying. Of arsenik!}



''Mommy? Where's Daddy?'' The questions kept
penetrating Louise's skull like a rusty icepick that had been
left outside too long. Long enough to develop rust. Cancer for
metal, Louise's father had always said in his father-voice. Now he
was dead. Like Gene.



``Daddy isn't here, sweetheart! We live with Tolkien now, remember?''
Louise had left Gene for Tolkien three years ago. It had been the
best years of her life. Until now. The kids made it that way. The
kids with their kid questions and their kid faces. Why were they
like that? They were kids, that's why.



Louise turned around. Suddenly! The kid winced. Louise slapped it
with her hand. Blood poured out of the mark left by her wedding
ring. Tolkien had bought it. On a Sunday.



They had visited Tolkien's parents. They lived in a small farmhouse
just off Route 66 in the desert. Miles to the neares neighbor. They
had horses, and Louise loved to ride them. Tolkien's parents were
rich. But it didn't show in the way they dressed. Tolkien's dad
wore shirts and blue jeans. Tolkien's mom wore shirts and blue
jeans. Tolkien had picked up the habit. He wore shirts and blue
jeans too. Soon, Louise were wearing shirts and blue jeans.



It was Sunday. Louise and Tolkien rode to town on a mighty steed.
They stopped at a jewellery store. Tolkien and Louise went inside
the jewellery store. Inside, the owner of the jewellery store
looked them up and down. She was the owner of the jewellery store,
and she didn't like poor people in her jewellery store, of which
she was the owner.



``Get out of my jewellery store!'' She said. ``We don't like poor
people in this jewellery store! I own this jewellery store!'' The
owner said.



``I have money!'' Tolkien said. He showed his money.



``Oh.'' The owner of the jewellery store said. ``Oh. Please shop. This
is my jewellery store''.



``Thank you.'' Tolkien said. ``I will'' he said.



Tolkien picked out a ring. He gave the money to the owner of the
jewellery store.



``Keep the change'' Tolkien said to the owner of the jewellery
store.



``Thank you very much'' the owner of the jewellery store said. Now
she could retire and buy a boat. Tolkien had been the 10.000th
customer and she had enough money to buy a boat and retire. So she
did, the next day.



In the meantime, Louise was happy with Tolkien. Tolkien wore shirts
and blue jeans. Louise wore shirts and blue jeans. The kids wore
pajamas. This was why Louise hated them.



She had been giving them arsenik for dinner every night. Her high
school biology teacher had taught her to make it in exchange for
sex. Louise had been 14 years old and she loved it. So did the
teacher. Louise told everything to the principal and he was fired.
Then he commited suicide. Louise didn't care.



Louise gave arsenik to her children. But what she didn't know, was
that the kids vomited from it. They vomited into the air ducts of
the house. And there the dust became infested with arsenik. Then
Louise and Tolkien breathed it and then they died.



The End. 
 




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{The Child}
\by{taurapo}


Luke Bavarius stared into the barrel of his Beretta, if only he had
the guts to pull the trigger of his Beretta, He nearly got erection
thinking about how the bullet from his Beretta would tear his brain
in half and a shower of blood would vomit from the back off his
head into the wall.



Suddenly he heard a scream come from the apartment above him,
without hesitation he drew his Beretta and headed up the
stairs.



It is there he witnessed a sight that made him vomit harder than he
ever vomited before, a child who couldn't have been older
than a year or six was being raped by what he could only describe
as a extremely hairy ape.



There was blood and vomit all over the floor as the oversized ape
like creature was endlessly pounding away on the child, Luke
Bavarius lifted his Beretta and pulled the trigger shooting the
abomination in the eye socket.



After the smoke cleared from his Beretta Luke Bavarius could
finally inspect the creature, he was shocked when the creature was
nowhere to be found, the only thing he saw in the hallway was the
lifeless corpse of a dead man.



A closer examination gave room for the ugly truth, the bullet form
Luke's Beretta had penetrated the skull of the now lifeless
corpse who Luke Bavarius recognized as Raymond Von Strathburgh an
ultra conservative right wing Christian with a PHD in
Creationism.



The thought of what he just did shot into Luke's mind faster
and harder than the bullet shot from his Beretta, his stomach
growled as vomit shot up to his head. But Luke Bavarius
couldn't open his mouth due to shock.



While pressurized vomit was shooting out of Luke's nose
another tenant ran into the hall and witnessed a sight that made
him projectile vomit down the stairs of the building, Luke realized
he couldn't allow the man 'a witness to the horrible vomit
inducing crime' to live.



Unwillingly Luke Bavarius raised his Beretta for the slaughter of
another innocent man, upon seeing Luke take aim the man froze with
fear while simultaneously shitting and pissing his pants, the
horror of the situation dawned upon Luke Bavarius as he decided to
do the thing most fitting.



He shot his Beretta, as his Beretta fell inside a huge pool of
blood mixed with vomit the now lifeless body of Luke Bavarius let
go off its boundaries and shit and piss flowed freely out of his
lifeless corpse.



The hall Stank with the stench of piss, Vomit and shit. The police
declared it a health hazard and had the entire block evacuated, all
but one officer who entered the building projectile vomited unto
another officer.



The tenant who witnessed the horrible crime went insane and was
sent to an asylum where he promptly killed 3 staff members before
committing suicide with Luke's berretta.



Two weeks later new tenants found the lifeless body of a little
girl inside Raymond's flat, she showed signs of repeated
sexual abuse, her rust colored dress was soaked in blood and semen.
Raymond's semen.


 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{The Mosquito of Death}
\by{Assless Chaps}



Luke Bavarious stumbled slowly through the New York City alley,
gently swatting the mosquitoes away from his skin with the butt of
his beretta. It was a hot and humid night, and the blood-suckers
were relentless in their pursuit of delicious, sticky human blood.
His delicious blood was made even more delicious after drinking
four Coors in a nearby bar. The mosquitoes knew it was delicious
and that Bavarious was too drunk to defend himself properly. Or so
they thought.



As Bavarious continued to wade through the refuse and urine-soaked
mattresses strewn about the alleyway, the mosquitoes became
ravenous. They swarmed him in droves, and he began frantically
waving his trusty beretta around, squishing the lowly bugs into a
mess of guts and recently-consumed human blood.



Suddenly Bavarious vomited. The alcohol had finally gotten to him,
and he spewed out chunks of peanuts and pretzels, mixed with beer.
He puked so hard he began puking blood out of his mouth. The blood
and vomit cocktail splattered to the ground, forming a vile and
horrid river of bodily fluids. If only he had listened to his young
son, Timmy, and stayed home that night, instead of going out and
drinking Coors, none of this would have happened.



The mosquitoes began to fly away from Bavarious. He thought in his
drunken mind that they were giving up, and that he would be able to
continue on his walk home, while the insects pursued more
easily-caught prey. Bavarious was wrong. Dead wrong.



Bavarious tripped over a rotting pile of dog feces, and landed
face-first onto the asphalt. As he raised his head, blood spurted
from his broken nose in every direction. Bavarious used all his
manly strength to pull himself up, and when he looked up, he saw
all the mosquitoes joining together, like a giant mosquito army, in
a frenzy due to the delectable scent of his flowing blood. They
grew in number, and eventually a million mosquitoes joined forces
and swarmed together. They began to morph into one hideous
creature. One giant mosquito! The most humongous mosquito ever
recorded in the history of mankind. A gargantuan travesty of a
beast.



Not deterred by this horrendous creature, Bavarious screamed at the
top of his lungs, ``EVIL-DOER! VILLAIN! YOU DO NOT FRIGHTEN
ME!'' As he screamed, flecks of spittle mixed with the
still-running blood from his broken nose, only attracting the giant
mosquito more.



The giant mosquito, the size of Bavarious at least, stood up on its
back two legs like a human, to do battle with Bavarious. Its long,
pointed proboscis inched closer to him, yearning for the sweet
taste of human blood. Luke Bavarious unholstered his beretta and
let loose a torrent of bullets that merely ricocheted off the giant
mosquito's hard insect body. {\em This is no ordinary
mosquito}, Bavarious thought to himself.



The massive insect lunged forward and sunk its sword-like
blood-sucking mouth-nose into Bavarious' neck. Bavarious
screamed in agony as blood flowed from his wound like a red rapid.
The pain caused him to lose control of all bodily functions. He
writhed in agony as the pain caused him to puke up the remnants of
his pretzels and peanuts, mixed with beer and the bile left over in
his stomach. He felt particularly uncomfortable as his bladder and
bowels emptied into the camouflage fatigues he wore. His apparel
was filthy. He was reduced to a slithering, screaming shell of a
man, covered in excrement, urine and vomit.



The mosquitobeast had had enough. It pulled its sucker from
Bavarious' neck with a wet, slimy burp. Bavarious watched in
pain, as the mosquito slowly turned and began to walk away, unable
to fly because it was so filled up with his beer-blood.



Suddenly, a white light beamed down on Bavarious. He squinted from
the blinding light, and could vaguely see the shadow of a man in
the light, far, far away. As the shadow-man moved closer, Bavarious
felt that he looked familiar.



``Grand-nd-pa?!'' he said.



``Yes. It is me, Luke Bavarious. Your grandfather: Brock
Bavarious. I am here to help.''



Soundlessly, Grandpa Brock showed Bavarious how to slay the beast.
And as quickly as he appeared, he was gone.



Bavarious mustered up the last of his strength and stood up. He
slowly stalked the giant mosquito and lunged forward, clinging to
the creature's back, like a child riding piggy-back on the
back of a man. As the mosquito let out an eardrum-bursting roar,
Bavarious grabbed its giant proboscis and yanked it hard. The
proboscis broke off and the creature's power was drained. Its
only way of eating was destroyed. It crumpled to the ground,
writhing in a puddle of its own blood mixed with the blood of all
of the victims of the millions of mosquitoes that made up this
disgusting creature. After a few seconds of painful screaming, the
creature died.



Bavarious didn't want to take any chances, so he raised the
broken-off proboscis and stabbed the mosquito right through its
insect heart.



``You suck,'' he said, as he hobbled away, ready to get
home and get some sleep.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{The Monster of Lake Grim}
\by{Sirocco}



I stepped out into the night. The clouds were dark and raining
shadows. The lake was calm. Dead fish rose to the surface. They
shone in the moonlight. I was here. Lake Grim.



I am Luke Bavarious. A detective from New York City. But I
wasn't in New York City anymore. I was at Lake Grim.
Investigating. My shoes squelched horrid vomit noises in the mud.
When I heard the sounds I stopped. I looked around, in a sudden
panic that threatened to overwhelm me. I fell forward and knelt in
the mud and vomited on the ground. Some of it went on my hands but
I didn't care. I was afraid. Reports from this area had
reported strange vomitings in the lakeside town Grim which was next
to Lake Grim. First you heard the vomit noise. And then you vomited
yourself. Then the blood. And then{\ldots} you were never heard
from again.



I stepped up. I knew if I wasn't careful enough I would fall
to the hands of the monster. If they were hands. That it had. The
boy had warned me about this. I had been foolish not to listen. I
looked around and restlessly put my hand near my Beretta. My TWO
Berettas. The breeze drifted through the trees and made waves on
the surface of the lake. My eyes scanned the lake.



``The monster must live in the lake,'' I said to
myself.



I walked down to the lake's shore and looked into the black,
swirling water. I saw my reflection. I was about to look away when
I felt the need to vomit rise from my stomach and into my mouth. I
vomited into my reflection, again and again, blood and saliva came
out too.



``This is horrid!'' I gasped, in between vomits.



A dark, black shape broke the surface of the lake. The monster of
Lake Grim had decided to show its face. I needed to act fast before
it was too late. I leapt back and pulled both Berettas out and
fired them at the shape but it kept on coming. Shells hit the
ground and got stuck in the mud. I tried to reload but the need to
vomit and the fear made my hands too shaky. I dropped the shells
and backed away from the monster.



``My weapons are useless!'' I cried. I tried to swing my
fist but my vision was blurry from salty tears of pain and fear and
horror. And I missed. I fell back on to my face and broke my nose.
Blood splattered everywhere on the ground like a rose trampled
underfoot. Then I vomited into the blood. And then I sneezed. I
turned over and looked up at the starlit sky. The night sky turned
black. The monster was looming over me, ready to do its evil
deed.



``Kill me! Just kill me now!'' I gargled, trying to speak
through a mixture of vomit, blood, boogers, and pus from where the
blood came from. ``Kill me!''



It stopped. Then it walked away, leaving me in the mud and the
grass, shaking without control.



And suddenly I was crying. 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{The Horrid Reflection - Redux}
\by{Cota Froise}





I sat at my computer. The email had come again. I was checking my
emails in between browsing the Something Horrid forums. My hand
shook slightly with the mouse in my hand. The white cursor was
positioned and ready, ready to click. I am an internet detective.
My name is Luke Bavarious. I like this work.

People had been complaining about horrid email attachments coming
from a mysterious stranger for about a year now and I finally
decided to see what was going on. I had decided to stop these
emails.

I leaned into the dim monitor light. I saw a single email sitting
in my `junk' folder, hiding away from me. It was
strange and suspicious. I raised my mouse and lined my cursor up
with the icon.

``You there{\ldots} What are you then?'' I whispered through the
darkness.

``Open up{\ldots}'' I whispered again.

``Beggin' your pardon, but{\ldots} you don't want to open that,'' my young
son said.

``Sure I do. I got a cursor pointed right at it so I'd
better,'' I replied.

``Okay, you asked for it,'' my son mumbled as he began to turn
around.

A chill trickled through the room as I clicked and the picture
began to load for me. I couldn't see it yet, it was loading on the
screen.

``Get onto the screen.''

It inched downward. First its back. Then its arms. Then its ass.
Then its legs. If you look at the legs. His ass was horrid. There
was an abundance of red flesh. There was blood leaking from a burst
blood vessel and he only had one gold ring. There was no face.
There was no head. Only a hole.

I took a step back in astonishment. I gritted my teeth to keep the
vomit down.

I took three more steps forward and I felt my tears glisten in the
dim light.

``I told ya,'' my son said.

He screamed and began to run away from me. My mouse was held high
in the air and was ready to commence my brutality. I clicked the
right button on my mouse. The click soothed my fear as I saw a
drop-down menu open and saw the `delete' option make a
white rectangle over the thing's ass. It kept resisting with the
assistance of my email provider's inferiority. It had only
been a split second before I brought up another drop-down menu over
its ass. The thing was inches away as I dragged and dropped it into
the Recycle Bin. Two more appeared on my desktop.

My palm smashed my forehead terribly powerful. Muscles were
strained and torn as my head jerked to the side, smashing a window.
I fell and landed in jagged glass. Dazed I stared again and again
into the thing's hole. I felt the vomit rising back rhythmically.
Glass hitting the floor. Me hitting the glass. Vomit showering me.
I felt my own blood from the side of my head fall and drip. I kept
staring. The hole was empty. I staggered. I tasted my tears and
blood mixed into a horrid cocktail. It fell down next to me. A name
sparkled on the side of his ring. Bavarious.

I looked up at the computer screen and saw a horrid reflection.
Suddenly, I was sobbing. 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{The Library}
\by{Combat Wombat}





My name is Luke Bavarious. I'm a PI, a private investigator. I
wasn't always a PI, I used to be a cop. A damn good cop, the best
on the force. But that was the past. There's no point dwelling upon
the past. It's not so bad though, a PI is like being a freelance
cop.



I had a new case, it had come in this morning as I was trying to
murder my hangover with a coctail of aspirin and coffee. The phone
pierced the silence and drove deep into my head with the force of a
semi-truck going 55 miles per hour. I swore never to get this drunk
again. I remember I had fought down the vertigo and struggled to
make sense of the words coming out of the earpiece. ``This was worse
than the time I killed myself in the alley,'' I thought to myself.
At least I hoped I thought to myself. What if I spoke it out loud?
I looked at the phone in my hands in horror. My hand trembled. It
suddenly became too much weight to bear. I remembered mumbling
something close to ``I'll be there'' and slammed the phone headset
back on it's cradle. At least I hoped that's what I said. It was
all too much to deal with.



I was struggling to piece together what the voice on the phone had
told me. The voice said something about noises in the library.
There were children there, they were afraid it was a stalker. The
police had found nothing and they couldn't watch the place all day.
That's where I came in.



I grabbed the bottle of aspirin and twisted the child proof safety
cap off. I downed the entire bottle and washed it down with the
remained of my coffee, now lukewarm and disgusting. Odd, I thought.
I just made this pot.



I grabbed my berretta and palm slammed a clip into it. As I made my
way towards the door with grim purpose I was accompanied by the
sounds of aluminum cans being crushed underfoot, cans that lay
scattered across my apartment like ammo shells. There had been a
war here last night, Coors were the bullets. I was the victor and
the defeated.



When I got to the library it was deserted. It was a cold, desolate
place lit only by the night lights. Rows upon rows of books lined
the shelves. Each one was like a tombstone, the library a masoleum.
It was all too much.



If there was a stalker I would need to stake him out. I searched
the library and found the perfect place, a hallowed out section of
a bookshelf that I could fit myself into. I removed the books and
squeezed myself into my new hiding place. As I began piling books
to cover myself up my fingers brushed against the covers of all the
books. I could feel the grain, the texture. The embossed lettering.
I hate embossed lettering. Some of the books had jackets with
embossed lettering on them. I tore those off and hid the jackets.
The books were much better without them. There wasn't anything I
could do about the ones that had embossed lettering on the covers
themselves.



Soon I was perfectly hidden, a specter. A ghost. Now I had to wait
and watch. My berretta felt cold and heavy in my hand. It was my
constant companion, my only friend in this cold, terrifying
world.



I waited out the hours. The cold blackness of night soon gave way
to morning and the library opened. Librarians streamed in and began
sorting the returns and placing them on the appropriate shelves.
Dewey Decimal would have been proud of these librarians.



Soon the place was filled with adults and children. My eyes were
sharp, alert. I had picked a perfect spot with a clean view of the
checkout counter and much of the library itself. I would find this
stalker.



I could see the effects of his presence, clear as day. People
looked around worriedly as if they were aware of someone watching
them. No, not someone. Something. I could feel it too. A deep,
murderous intent hanging on the air like heavy cobwebs. A cold,
unrelenting malice that permeated the very air. A thick, undulating
smog of contempt. It bore down on me, on everything. It terrified
me. I swallowed the vomit that threatened to climb up my
throat.



I could feel it everywhere. I could feel it's eyes on me. I could
see no trace of it, though.



The police came again, I guess they decided to take another look.
They inspected the place. They were dutiful and attentive, but my
hiding spot was too good. The stalker's must be even better. Soon
they left.



The stalker was still here.



Hours continued to crawl by like a wounded semi-truck limping down
a gravel road with a flat tire as oil, precious blood to the
vehicle, vomited forth from ruptured lines and leaving a death
trail on the rocks. My finger rested uneasily on the trigger of my
berretta. I had to be ready.



I was startled to attention by the voice of the head librarian as
she picked up the phone and punched in a number.



``Is this Luke Bavarious?'' I began to tremble. {\em No{\ldots}
no!}



``This is Pamela Dufrost at the Metropolitan Library, we've been
hearing strange noises and it's frightening the
children{\ldots}''



As I felt the icy grip of fatalistic, militant terror grip my heart
I could hear laughter. Was it coming from my own lips? No, it
couldn't be! I screamed, the noise erupting from my throat
like vomit.





Edit - I guess it has a very weak link to respecting children. Not
being a creepy time travelling stalker is an important message
right? 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Pearl}
\by{Phthalogreen}



I stand in the shadow. The sounds have been coming again and again
for thirty years. I'm in the old folks' home on 42nd
Street in New York. Right by the alley where it all started. My
hand shakes slightly with my pain meds in my hand.



Pearl, my ten-year-old granddaughter, sits on the bed across the
room. I keep my hat down and my collar up so she can't see my
face. I won't let her get any closer. I don't want her
to see what I've become.



``Why won't you take your medicine, Grandpa?'' she
asks.



``It won't help me,'' I say. ``There
isn't a cure for what I have.''



``It's okay, Grandpa,'' she says. ``You
don't have to take them if you don't want
to.''



Suddenly the nurse enters the room. Nurse Packard. She's the
old hag of the nursing home. Everyone hates her and everyone is
hated by her.



``You there! What are you doing? Swallow those meds!''
she shouts through the darkness.



I look at the pills and hesitate. They are huge and taste
horrid.



``That's it, I'll have to feed them to you!''
Nurse Packard shouts again.



``The pills don't help!'' Pearl cries.
``Don't you get it?''



``Quiet, kid,'' Nurse Packard yells. ``Turn
around,'' she says to me.



``No. He's sick. You don't want him to turn
around,'' Pearl says.



``Sure I do,'' she replies. ``Step out of the dark
and open your mouth.'' She doesn't know my mouth is
always open now. I stay put and pull my coat collar over my
chin.



With that she runs towards me and commences her brutality, grabbing
the pills from my hand. I keep my head down, but her clipboard
smashes my head terribly powerful.



``Grandpa!'' Pearl shouts. ``Stop it, you
hag!''



Nurse Packard ignores her. She giggles and forces her hand into my
mouth. The pills enter my throat.



Unable to control myself, I inch forward. I feel the light on my
legs. Then my chest. Then my head.



``Look away, Pearl!'' I shout. I lift my hat and Nurse
Packard screams at the sight of my scarred, purple face.



As the pills enter my stomach I feel it turning and tightening.
Putrid vomit erupts from my mouth and nose and splatters on Nurse
Packard's face. As the old woman screams, something pops in
her head and she drops to the floor, twitching. The vomit keeps
gushing toward the wriggling body on the floor.



Then my stomach is empty. I fall to my knees. My head is spinning.
But I hear Pearl's voice.



``Grandpa!'' she says. I feel her grabbing my coat.



``No! Don't look at my face!'' I shout.



``It's okay, Grandpa,'' Pearl says. ``I saw
you. I never looked away.''



Suddenly I am sobbing. I realize I was wrong to assume she was
weak. She has the right to see her Grandpa's face. I turn and
look at her.



``Grandpa,'' she says, hugging me. ``I want to know
something.''



``What, honey?'' I say.



``What is your real name? Mommy won't tell
me.''



I think for a moment. Then I pick Pearl up and put her on my
lap.



``My name,'' I say proudly, ``is Luke
Bavarious.''



[edit: typo fixes] 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Reunion Under a Blood Red Moon}
\by{Sleepless Dreamer}



The man stared at the figure wrapped in black sitting on the bench
in the middle of town at 3 in the morning. It was late, but he felt
it was his duty to talk to the lonely person who had seen better
days. After exchanging meaningless talk, the man in green asked the
man in black what placed him in this situation.

``It all started when that Bavarius kid moved in the 3 story
house by the cemetery. That kid, Luke, was a curious little punk,
but he just turned the whole neighbourhood around with his
investigations. That little jerk was probably too smart for his own
good, and brighter than any of the people around him, including his
parents. That kid fancied himself a detective, and he was quite
good at his ``detecting'' work, especially for a 13 year
old boy who listened to no one but himself. He was smart, he was
the first one to see right through the facade that suburban life
provided, he knew how fake everything was.''

The man in green asked: ``so he spotted his mother cheating on
his father or something?''

The dark person replied: ``no, he had been aware of that for
quite a while, he simply realized what was happening in the
graveyard at night. The most of the neighbourhood would gather
around a specific grave, late at night, around this hour, and they
would chant horrible songs of death and despair. A black magic
ceremony of the darkest kind, celebrating horrors man should not
know. Luke was a kid, but he knew what was happening there
wasn't right. His parents wouldn't believe him, and his
older brother, Frank, just said Luke probably had imagined
everything. His brother didn't care; he was 16 and had
started dating a slutty girl. He was more concerned about that then
the darkness that surrounded their house.''

The man in green smiled and said: ``it sounds like Luke was
just in need of attention; he was probably a bit jealous his
brother had started dating. I've seen that a lot in my line
of work.''

The brooding figure replied: ``Luke didn't need these
easy girls to be happy, and he did not invent anything because he
needed attention. He was right. The whole street would gather,
planning human sacrifices. One night, Luke snuck out of his
bedroom, into the graveyard, and observed what was happening. There
was more people than usual, and on a grave that served as an altar,
a girl was bound and gagged{\ldots} Frank's girlfriend. The
ceremony started, and Luke tried to get under the altar to untie
the poor girl. That's when a familiar voice caught his
attention. He could not quite figure out who it was, the voice was
transformed by dark magics. That's when he heard a sound that
will be burned in his memory forever: the sound of the girl's
throat being sliced open. Blood dripped at first, but it eventually
pour over Luke, the blood of this poor girl sacrificed to a dark
god. Luke waited for an hour, and then snuck away from the mass and
washed himself before going back home. The next day, he asked his
brother about his girlfriend, but was told that they had broken up
the night before.''

The man in green said: ``that's quite a story
you've got there, do you need a place to spend the night, I
know a shelter, and I could start seeing you as a patient, you see,
I'm a psychiatrist.''

The man in black looked up and said in a grave voice: ``I know
what you are Frank. I know what you've become. You feed on
men and women's souls and masquerade as a psychiatrist.
I'm here to stop you. I've known it for years, but
I'm not a kid anymore, people listen.''

The man in green snarled: ``Who do you think you are? Luke? I
killed you years ago, I sliced you up like a pig on that altar. You
bleed and cried, you pissed your pants when the knife when through
you.''

The figure in black rose, the street lights revealing his pale
complexion, his emaciated figure, and the darkness in his eyes. He
said: ``you killed me, but you failed to make sure I was
dead.'' Luke grabbed frank by the throat and crushed his
airways. ``You are going to hell, where you will be devoured
slowly by the people you have killed, until all that is left of you
is blood, tears and pains. And it will start over for
eternity.'' The dying Frank let out one last airless shout as
his soul went to hell.

Luke smiled and said to himself: ``Another job well done, and
now I can wear his skin to seem more human. I finally have a life
back.'' He looked up and saw Sandy, the girl his brother had
killed, waiting for him back to un-life like him. Things were
getting better.

\section*{Alternate Ending}

Luke said to himself: ``They always fall for the zombie
make-up.'' He looked up and saw the ghost of his mother, who
asked: ``Are you sure that was Frank?'' Luke replied:
``Yes mother, thank you for guiding me to him, and for saving
my life when Frank tried to kill me.'' ``Don't
thank me, she replied, I've been with you ever since I died,
thank you for not taking these pills that make me
disappear.''

Luke smiled and said to no one in particular: ``Psychiatrists,
what do they know?''

* * *


I actually like the alternate ending more than the original one,
however the alternate one is closer to what I usually write.



Hopefully I managed to make something bad and good at the same
time. 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Untitled}
\by{TheSpiritFox}


Luke walked into his room. Man! What a shitty day.



He hated this town. Ever since he'd been moved here, the days just
got longer and longer, more and more boring. From the hours long
train ride into the city to the four hours of processing to even
get past the train station, he'd been bored to tears for months
now. The shelling had begun two days ago, but it had yet to affect
his part of the city, so he ignored it like he ignored the usual
sounds of doors crashing down in the middle of the night. It was
never {\em his} door. He never got to play.



He'd talked to his mother about it, asked her why their family
never got to have fun like everyone else's. Why they never got to
go on the vacations his parents told him about. Why the police
didn't come and take them fun places. She told him it was because
he was special.



He hated being special.



Luke heard the front door open and close, the lock clicking as two
sets of footsteps walked into the small apartment.



Great. His parents were home.



He heard hushed, worried voices, and his heart jumped. Thats how
all the neighbors always talked before they went on vacation. His
parents were probably worried about what to bring, since people
always had to say yes and go immediately without packing if they
wanted to get in on a vacation. A small vibration shook the
building, as he realized that the shelling had finally moved to
their part of the city.



His mom had told him about the shells. They dropped pinata's into
the city which burst open, and people got to keep whatever they
grabbed out of it! He couldn't believe his luck, two events in one
day! Maybe when they left on vacation he'd pass near enough to a
shell to get to keep something.



He hoped his luck was turning.



There was a pounding on the door, and he burst out of his room
eagerly with his pillow and blanket.



``Open up!'' a rough voice shouted. His parents gave frightened looks
back and forth, he knew they'd been caught unprepared. Luckily, he
was a practical kid, all he needed was stuff to sleep with. His
parents opened the door to see a guy in some wierd kind of mask
like science on his face.



``You're to come with us. Now''



His parents obediently followed out the door, and Luke Bavarius
brought up the rear, his proud strut meant to show anyone who
watched that it was {\em his} turn now. He just knew that his
vacation would be far better than anyone else's had ever been. He
knew he was special, and he knew they'd only have made him wait
this long to prepare everything in advance.



They walked out the front door of the building, and he walked right
into his mothers back as he saw what had frozen the policeman with
science on his face. Two shells sitting there waiting in the front
yard, freshly landed.



Luke could not believe his good luck, in all his 10 years he'd
never gotten anything special for himself, and he could understand
how anyone would be frozen with excitement upon seeing not one, but
TWO untouched shells to be raided.



Luke darted past his parents frozen forms to the leftmost shell and
eagerly peered inside it. A small form moved, and leaped out. Luke
ducked out of the way and turned, seeing a small four legged animal
standing on the ground. It didn't seem to have any eyes, but looked
at him just the same.



``A pet!'' Luke thought. ``A pet! I've heard people used to have pets
but I never thought I'd have one of my own!''



Luke ran forward and grabbed the small animal before it had a
chance to move again, and heard the roar of a gun as a bullet
chipped the sidewalk not a foot from his foot. He looked up, the
science-police was pointing a gun at him! He wanted to shoot his
new pet!



Luke turned and ran, dashing behind playground equipment as his
parents screamed at him to put down the ``headcrab''



``A headcrab?'' he wondered. ``So thats what you're called, little
guy'' he quietly muttered to his new pet, hiding behind a large
piece of playground equipment.



``You'd better leave my pet alone! I'll make you sorry!'' he yelled,
mostly at the policeman. His parents were the ones who answered
though.



``Luke! Please you don't know whats going on! That thing's
dangerous!''



Luke stared incredulously at his new companion, and shouted back
``Why are you always trying to take everything away from me? Why
can't I have one thing, just ONE THING that other people have? If
I'm so special why am I always left out?!''



He knew he'd need his hands to get away, so he set his new pet down
on its four spiky legs and shushed it, telling it to calm down. It
kept trying to sit on his head though, and luke eventually relented
with a sigh, thinking it would be easier to have it sitting up
there than on his arms.



As soon as his new pet gained its throne, he felt a funny tickle at
the back of his neck. Suddenly, he couldn't move. He felt strange
little tendril-tickles under his skin and looked down to see his
veins growing, then eventually shattering and strange tendrils of
skin that looked kind of like his pet grew out of them instead. He
could see his skin rotting before his eyes, but it didn't hurt, so
it didn't scare him.



On the contrary, he felt strong. Luke was amazed at how he suddenly
felt like he could lift a car or jump 15 feet in the air without
trying.



His amazement was shattered a moment later as a flurry of bullets
tore through the playground area he'd just been hiding behind. But
before the first bullet was through the material enough to hit him,
he was eight feet away in a crouch.



It was a flash, but a very clear one. He felt like he could
remember each individual fraction of the half a second it had taken
him to dodge the bullets. But his wonder quickly turned to
anger.



The science police was trying to kill them both! Red rage caused
his heart to accelerate to a hummingbird like rate and a curtain
fell across his vision as he realized that science police wasn't
trying to take him anywhere fun, that in fact science police was
about to take away the only thing he'd ever truly loved. He sprang
completely over the playground equipment and charged straight at
the man. He saw the man shoot twice, felt the impacts and watched
skin and gore fall off of his body in equal amounts, but to him it
was no different than running into a mosquito that was flying
forward intending to bite.



He leaped again, and crashed down on the policeman. He knocked the
science off his face and stabbed a hand down at his head. He was
strong, his hand went completely through the policeman's head and
cracked the concrete below. Luke looked down at the mingled brain
and rotting arm, and vomited up a small amount of bile.



He immediately swallowed it, as his face was covered by his
headcrab.



Still enraged, he turned to see both of his parents there. They
were in on it too. They had stood there and let the science police
try to take his new pet headcrab away.



He roared inarticulately as he hurled himself at them, stabbing at
their chests with both of his new, stronger arms. His hands went
through, and his parents stared down at him in horror.



He could feel their pulsing hearts in his hand. He looked into
their eyes (strange, how he could see them through his pet's body)
and said ``I told you you'd be sorry''



They were. You should always listen to your kids. 

 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{The Cellar Of Death}
\by{Lord Humongus}


Luke walked down the house's scarred walls. The place was full of
hate, he could

feel it tingling in his bones. Like some sort of hate filled
bastard feeling. {\em Filled with hate.} he dismissed the
thought.



His parents were moving thier stuff into the old, creaking hate
filled house. Luke ran up to his obseqious parents, warnings of
hate emerging from his mouth accompanied by the screeches of
horror. His abusive father slapped him in the face and told him to
``Quit it, you dumb pecker.'' Luke couldn't. He had to warn
them.



Luke looked for anything to defend himself from the evil, but he
found nothing. He looked throughout the house for something. Only
to

come up empty handed. He walked out of the door wondering about
what he could do.



He ran into Suzy, his sister, she teased him and called him a
pussy. {\em She called me a cat that's not insulting why would she
call me

a cat?} thought Luke.



The sun hid under the horizion. The screams of animals filling the
empty night air. Luke arose from his bed. Suddenly a illmunescent
gigantic head appeared in his room. It opened its lips to talk. All
Luke could feel was hate in his brain.

Nasty, painful hate.



Luke awoke in his bed in the morning. He ran down to his parents
screaming and screeching like some annoying owl. His father rose
his hand. Luke closed his mouth shut.



He wandered down into the lone cold cellar of the hate house.
Looking for clues as to what was causing so much hate. He looked
around the

dusty cold floors. His came upon an old case full of dust. He
opened the golden latches, looking for anything that might be a
clue. Inside,

was a horrible book. He knew what must cause the hate. This book.
He threw it into the evening fire that was in the fireplace. His
dad slapped him in the face for doing that but he thought to
himself ``I just saved your life you fool.'' and smiled to himself
because he was so smart and stuff and found out about the
hate.



But it didn't work he was wrong. The hate returned each night, and
each day Luke received a slap to the face for being an annoying
little mutant. He slept scared under his covers each night the
horrible head would return to him and use all the hate and torture
him with its 's telepathic mind full of hate and ire. He awoke
every morning screaming at nothing. Until one night, he heard his
parents scream. He ran to thier room to see them being dragged into
a portal. A portal to hoboken. Luke laughed at them as they were
sucked into a trailer park abyss. Full of people you didnt want to
hang out with because they are all hate filled evil creatures from
the third nuclear war.



He hid the bodys in his bavarious cellar.



They should've listened! 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Untitled}
\by{King Plum the Nth}


I'd never been to San Diego before. Never been further west
than Iowa. But I like to travel and I like my job, so when my job
called on me to travel, I packed my Beretta and bought a one way
ticket to SoCal. One way because, in my line of work, you can never
be sure if you'll be coming back. My name is Luke Bavarious,
I'm a private detective and this is the story of how I died.



The bus disgorged its wretched few passengers into a diseased
corner of the city. In some ways, all cities are the same, and San
Diego was no different. You won't find a bus depo or the
train station in a nice part of town. No, the rich white folk pawn
this stuff off on the poor blacks. As if their urban lives
weren't hard enough; the man sweeps all his dirt under the
rug of the black culture's communities.



I hadn't been on the streets of San Diago more than ten
minutes when I was mugged the first time.



``The fuck you doin' in our neighborhood,
whitie?''



I could've cried. There were four of them. They were tough,
angry black youths, and if they pushed this too far, they'd
get hurt. ``Just passing through,'' I said.



``Passing like a piece of shit, mo'fucker. Gotta pay to
walk our streets.''



``It's public property,'' I didn't break eye
contact. Like dealing with an angry dog, when you talk to a gang
member, you can't show fear. ``I'm the public. Let
me past,'' I unbuttoned my jacket, flashed my Beretta.
``There's doesn't have to be any
trouble.''



The kid, their leader, lifted the hem of his hoody with a slow
insolent gesture to show off his own piece, a Glock. Two of the
others reached for the back of their waist bands. I tried again,
using their language: ``Don't start none, won't be
none.'' I'd tried in vein.



``Stupid mo'fucker.'' The leader jerked his piece
from his pants. His draw was admirably fast. These kids knew
violence, they were born it, it was their legacy. A cold, harsh
society had turned an indifferent shoulder to them and they had
risen to the challenge, becoming the only thing they could be in
this city. They were tough, but I was professional. My Beretta
barked four times, once for each of them, and the fight was over
before it began. They weren't dead, but they couldn't
threaten me anymore. I moved on. Violence isn't the answer,
but sometimes it can teach a lesson that needs to be learned.



The lady, Kelly, my client back in New York, had told me all about
San Diego. Said her old man had taken her and her sister, Amy,
there after the divorce. Kelly'd been a little girl, the
sister was a baby. ``The kids at my new school,'' she
said, ``taught me fast. My first day, they told me it
wasn't smart to wear so much red.'' We made love for
hours that night. It was glorious but I never felt like she was
really there under me. She was that little girl again, scared to
finish her first day at school in that pretty red dress.



So she'd gotten old enough and run away, all the way to New
York City. But her baby sister, fifteen now, was still trapped with
the father. Still trapped in San Diego. She'd hired me to go
find her, save her, and bring her back. ``He won't give
you any trouble, Luke. Just make sure you see him during the day.
He works at night.'' She'd paid me in cash and her
body.



I found the little cinderblock house she'd described and I
knocked at the door. The only answer was a dog barking in the next
yard. I walked around the front yard a bit, looked and saw I
wasn't being watched, and slipped around the corner of the
house. I let myself into the fenced off back yard, peering in
windows as I passed. The place looked deserted. Around back, I
found a narrow concrete stairway leading down to a basement door. I
figured what the hell and went down the stairs and tried the door.
It was open. I went in.



It was gloomy and smelled damp and it looked pretty empty. All I
saw was a couple of cardboard boxes, a water heater, a couple of
coffins. ``What the hell?!'' Curiosity is a big part of
my job but I wish I hadn't given into it then. I walked over
to the first coffin, lifted the lid. There was the too fresh body
of a man, thirty something, long black hair pulled straight back
from the temples, a trickle of blood running down from his livid
lips. I stared, shocked, and as I did, his eyes snapped open.
Before I could do more than gasp his hand was on my throat.



``Who are you,'' he demanded. ``What do you
want?''



``Your daughter,'' I choked. ``She sent
me.''



``My daughter?'' His eyes glanced to my right.
``She's right there.'' I looked as best I could and
saw a young woman, the spitting image of my client but a decade
younger.



``Oh,'' he said, rising from his coffin. ``You mean
the traitor.''



``She said{\ldots}'' I was choking to death in his grasp.
I produced the Beretta, painfully slow, but it was like he wanted
me to shoot him. I squeezed off the last few shots, right into his
gut. He didn't so much as flinch.



``I know what she said,'' he said. ``She said I was
harsh. That I abused them.'' He grimaced horribly and his eye
teeth erected into fangs. ``But she never understood. You have
to be tough to live in a city like this, Mr. Bavarious. I only
wanted to make my little girls tough.'' The world was fading,
purple splotches exploding in my vision. ``Amy will show you
what I mean.'' The girl hissed, drawing her lips back from
cobra-like fangs.



{\ldots}I guess you wouldn't say I died exactly. Could a dead
man tell you his tale? But that's the story of how I stopped
living. 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{The Boy That Lived}
\by{Irish Joe}





It all started when Luke Bavarious was aroused by a knock at his
door. ``Who is it?'' the mighty detective shouted from the comfort of
his bed. No answer but the sound of more knocking. Disgruntled,
Luke raised himself to his feet, still wavering from a night of
heavy drinking. ``Damn you all'' he shouted, approaching the door.
Leaning against the frame, he began to undo the lock when a shot
rang out. Looking down he saw a smoking crater where his peep hole
used to be. Thanking God he was too hung over to see anything, let
alone use his peep hole, Luke staggered back from the door and
reached for his Magnum Revolver lying on the coffee table.



The second shot didn't startle the brilliant gumshoe as much as the
vintage leather Ottoman lying between him and his gun. Falling head
first into the coffee table, Luke was barely able to grab his
Magnum Revolver, roll over, cock and fire the gun twice at the man
kicking in his front door before he passed out.



Luke awoke in the darkness of a car trunk. 'Its eerily quiet,' the
great protagonist remarked to himself. He then felt a sudden warmth
on the back of his leg. Luke reached around his muscular thighs to
feel about and find the source of the warmth. Blood! A second man
lie with Bavarious in the trunk. Before he could ponder further
upon this discovery, the car ground to a halt. Luke furiously
grabbed at the darkness searching for something, anything that
could be used as a weapon. As the mysterious driver exited the car
and approached the rear, Luke grasped on to the only thing he could
find, a large black iron tire iron.



The rattle of keys. The click of a lock. The sound of fury and
bone, crushing and yelping, cries of disbelief, anger and surprise.
Then silence as Luke Bavarious stood alone.



The awesome dick did not know who the two men were: one lying
bloodied on the ground with grey matter strewn to and fro on the
road, the other in the trunk, intestines drooping from a Magnum
hole in his stomache and half his face missing from one in his
head. It did not matter, for though it may sound strange to you,
dear reader, the fickle nature of Lady Death was all too familiar
to Luke Bavarious. She has pusued him with a vengence since the day
he was born all those years ago in an abortion clinic. 'The Boy Who
Lived' they called him. Lady Death had another name for him, 'The
One That Got Away." She tried as she might to catch him throughout
the years: car crashes, earthquakes, sicknesses and contagions,
shipwrecks. However, nothing could kill Luke Bavarious. And as the
trail of bodies he leaves behind continues to grow it seems that
nothing ever will. 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{A Tin of Popcorn}
\by{Dirty Sanchez}





``He was right, three left,'' I said aloud, my own voice startling me
as it broke the silence of the restroom. ``Not very many but they're
gonna have to do''. I lined the shells up on the sink like stalwart
little soldiers and paused for a moment to make sure nothing heard
me. I need to stop talking to myself.



``Won't be enough,'' the voice in my head replied. ``You saw what
happened to that deer. Three or Thirty, it won't be enough.''



The deer. The memories came back to me in a flood. Its hard to
believe that just this afternoon we were fooling around, shooting
cans by the campsite and sitting by the fire.



It all started with a can of overpriced popcorn. You know the kind,
one half covered with a powdery orange substance that's supposed to
be cheese and the rest a solid brick of caramel and popcorn that
requires an ice pick to break apart. The popcorn itself was not my
problem but rather the scrawny kid who brought it. Timmy was his
name, or was it Tommy? It doesn't matter. All that mattered were my
Captain's words to me in his office that morning.



``The Commissioner feels that we need to do more for the community,''
He said. ``I volunteered you to take a boy scout troop camping this
weekend.''



``You're joking,'' I replied.



``I never joke. You know that. Besides,'' He continued, ``Bavarius,
you've been a little weird since you returned to duty and you're
making everyone around here uneasy. Doing this will show you're
just a regular guy.''



``A regular guy,'' a voice echoed in my mind. ``I wish.''



``When?'' I asked.



``Saturday.''



``I'm busy.''



``Not any more. He will be here in a little while and they said he's
bringing you a gift. Make sure you smile.''



Sure enough, about two hours later a kid showed up with the can, a
bandanna, and an invitation to join them camping. He was a
squirrelly little fellow, who seemed to be as uncomfortable as I
was. Despite how ridiculous the situation, I determined to make the
best of it. What else could I do?



After shaking hands with the little guy and feigning gratitude, I
asked him where we were going.



``Timber wolf lake.'' He replied.



``I don't have any camping gear.''



``Oh, you don't have to bring anything, well have all the gear you
need. But don't forget to bring the popcorn.''



``This popcorn?'' I replied. I had no intention of eating the
garbage. Maybe I could give it away.



``Yes,'' he said, looking me straight in the eyes. ``Don't forget it.
Its a tradition.''



``I'm really not much for traditions,'' I said with a smirk.



``Its very Important.''



``Uh, Ok,'' I replied, still smirking.



``Great! See you Saturday. Nine O'clock,'' he said and bolted out the
door.

``That boy looks like a frightened animal,'' the voice in my head
remarked.



Saturday morning came and I dragged myself out of bed hung over and
smelling like the floor of a frat house basement. I showered, threw
on my clothes, and ran out the door. I would be late but at least I
would show up. Good thing I didn't have to pack anything.



When I finally arrived I was greeted by a pack of impatient and
excited boys and one pale, stern looking gentleman, who I could
only assume was their troop leader.



``Sorry,'' I mumbled. ``I'm not much for early mornings or
camping.''



``Don't worry about it,'' he offered. ``Thanks for coming. The rangers
won't let us camp here without a police escort. Not since those
campers disappeared last year. If you didn't come we could'nt go at
all.''



``Glad I could help,'' I lied. ``I'm Luke. Luke Bavarius.''



``Pleased to meet you Luke. I'm Tim.''



With the formalities out of the way, he rounded up his group and we
began our hike. After a few hours of walking my mind cleared and I
began to observe my fellow campers. A very unusual bunch. There
were eight of them. They all appeared to be about ten years old,
blond, and skinny. And there was something else. They were all very
quiet and jumpy. Once, shortly we passed the last park restroom, I
stepped upon and broke a stick which shattered the silence of our
hike. All eight boys stopped simultaneously, their heads snapping
toward me in unison. A second later, they seemed to realize what
they had done, put their heads down and continued walking.



``Creepy.'' the voice in my head commented. But what do I know about
kids?



We finally arrived at the campsite. The boys, a flurry of quick
movements, erected the tents, hung up the food, and gathered fire
wood. When the work was done they left me sitting on a log alone as
they went off to do whatever it is young boys do on a camping trip.
I took a second and looked around. The air out here was fresh and
invigorating. The temperature was perfect, the sky was blue, there
were sounds of nature everywhere. Suddenly feeling good for the
first time in ages, I picked up a discarded soda can and walked
down to where the boys were. Pulling my side arm out of my pant leg
I yelled ``Who wants to learn to shoot?''



Suddenly, the boys were all just standing there looking at me with
a blank expression. ``You brought your gun?'' Tim asked.



``Habit, I guess.'' I replied.



``You have much ammo?'' He asked.



``Twenty rounds.''



``Come here boys,'' he said loudly ``Mr. Luke is going to show you how
to shoot.''



The boys gathered around me and I put on a show. First they wanted
to see me hit the can from ten paces. Then, twenty paces. Next they
pointed out a log in the lake they wanted me to shoot. It seemed
that they couldn't get enough of watching me blow things apart. I
have to admit, I was enjoying it too. I also was working up an
appetite.



``So there you go boys,'' I announced.



``Come on!'' a boy shouted.



``Keep going!'' another added.



``I'd like to boys,'' I said, ``but I'm almost out of bullets.''



``You have three left.'' said the smallest boy, who seemed to be the
troop leader's son and was opening his mouth for the first time
since asking me to go with them.



``Maybe another time guys, I'm hungry.'' I said, ending the debate.
We walked back to the campsite and settled in for the night.



After a dinner of half-cooked hotdogs and baked beans heated in the
can, the silence settled back in and the sun began to go down. Tim,
the troop leader stood up to speak.



``Boys, I think it is time for dessert. Son, do you have the tin of
popcorn?''



``I, um, already gave it to him dad.''



``Oh. You didn't happen to bring it with you, did you Luke?''



``I'm sorry,'' I said sheepishly. ``I was in a hurry.''



Tim glared at his son who turned paler than usual and stared down
at his feet. ``Never mind then!'' he shouted. ``Bed time,
everyone!''



Without a word Tim and the boys turned and quickly disappeared into
their tents. Suddenly alone, I turned and walked to the tent that
had been designated as mine and laid down on the cool sleeping bag.
As I lay there the day's activity seemed to catch up to me and I
drifted off to sleep.



The sound that awoke me was like nothing I had heard before. It was
a sound of pure, primal terror. Instinctively, I jumped to my feet,
grabbed my Beretta and entered the darkness. The moon was full and
high in the sky. With the fire burned out and no other light
sources I could see quite clearly and distinctively. Too
clearly.



A flash of movement about fifty yards from the tent caught my eye,
but it took me a few moments to figure out what I was seeing. It
was a deer, running with something hanging off the side of it. It
was now making a gurgling sound as the creature attached to it tore
at its throat. In a heap the deer went down. I could hear it being
torn apart. I pulled my gun and shouted at the creature, thinking
it was a mountain lion or coyote. It looked up at me and in the
light of the moon and I realized what I was looking at. Or, perhaps
I should say, WHO I was looking at. There, perched on the
disemboweled buck was a young human-like creature in a Boy Scout
uniform. Blood dripping from fangs that protruded from his mouth,
he seemed to be sizing me up while also staring at my gun. The
sound of breaking brush began to come from all around me. I had a
choice to make. Fight or flight. I made a break for it.



In the moonlight I could see the trail we hiked out on almost as
clearly as I could during the day. The adrenaline flowing through
my veins allowed me to run faster and further than I had since my
days in the marine corps. At first I thought I could hear someone
behind me, but eventually there was nothing but the sound of my own
footsteps. I rounded a bend in the trail and saw in the distance
the restroom that we passed on the way to the campsite. Unable to
run any longer, I lunged for the door, found it unlocked, and dove
inside, latching it behind me.



The restroom only had one door and no windows. I was cornered but
at least I only had to defend a single point of entry. I ejected
the clip from my pistol and counted the rounds. Only three rounds
left.



``Won't be enough,'' the voice in my head replied. ``You saw what
happened to that deer. Three or Thirty, it won't be enough.''



``I'm afraid there is more than three of us,'' the voice behind me
says. I can feel the hot breath and sets of eyes on me.



``If you only ate the popcorn we prepared for you then you would
still be asleep right now,'' another voice, a child's voice, says
from the shadows.



``I'm not much for traditions,'' I whisper as the teeth close upon my
throat. 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{The First and Second Stories}
\by{O Tempora! O Mores!}


\section*{The first story!}



The bottle had clouded the room almost as much as the cigars. I
could hardly breathe without inhaling more smoke---it was so bad,
the door opening barely shifted the fog. But that may have just
been my mind.

``I got a case for you,'' he said. ``I been lookin' for this girl
goin' on three weeks now. You find her, you bring 'er to me. For
your trouble,'' and he tossed a stack of bills on the table. The
sound was like a sledgehammer to the skull. ``You got a picture,'' I
asked, the words slurring together in a muddle. He tossed a
polaroid on the table, the sound like a smack to the face. The door
closed, and I passed out.

When I woke up, I was surprised that I didn't choke on the fog in
the room, as thick as it was, and at least now I could see the door
again, with its golden-painted name: Luke Bavarious, P.I. I rolled
out of the chair, and watched the room spin. I'd hit the bottle
hard last night, and I felt the bile rising. I forced it back down,
my head spinning. I stood up, and picked up the picture. She was
pretty, I'd give the man that. But that smile{\ldots} she liked fun. She
liked a lotta fun. I turned it over, and saw a string of numbers
written there. It was too long for a phone number{\ldots} Wait.
One-two-three{\ldots} Ten digits. Four. Two. Three. A number and an
address? This guy coulda picked her up himself. What'd he need me
for?

I picked up the stack of bills, and headed for the door. I grabbed
my coat as I meandered past, and the bills. Past due. Past due.
Late. Hmm{\ldots} this one was already paid for? Since when had I paid a
bill? Advertisement. That damn client who wanted another look
around. Hey. Here's the place. Damn fine building for a pretty
little girl.

I got up to the door, and knocked. A soft voice called, ``Come in,''
and I did. She wasn't wearing much, and it was cool in there. Damn,
but she was pretty. And that was a thin little slip to be wearing
with company, but hey, who cared, it was just us. She walked over,
smiling slightly, and asked, ``Are you looking for me?'' ``A man asked
me to find you, and gave me this picture{\ldots}'' I said, but my mind
wasn't on what I was saying, she was too fine to think about
anything else. I'd been alone a long time, and here she was,
standing real close.

``Aww, don't be all about the work,'' she said, her smile suggesting
such exquisite delights, and her dark, seductive eyes pulling me
into an intimate embrace of desire and pleasure. I felt passion
stirring lazily, swelling in my chest, like an exceptionally loud
burp, but always finding more room to fill, until it finally took
up all of the space it could manage, as it got more and more
intense. Like a storm ravaging my soul, it burned in me, a desire
to have her, this pretty little thing. She saw my need, my want,
and opened her mouth, to say the affirmation that already was
showing through the way her bosom swelled with air, stretching the
thin fabric to its limits, threatening to release her breasts like
racehorses from the starting line, until it suddenly did, and the
smooth skin made me lose track of my own senses, as her smile
deepened and she pulled me close, her soft but firm body pressed
against mine, our two forms moving as one towards the room, satin
sheets already on the bed, a heaven of fabric and lust.

She pulled off my trenchcoat without my noticing, as I undid the
buttons on the back of her slip. Her hands pushed aside the ruffles
of my shirt as she looked for the buttons, like a man running his
fingers through sand to find his glasses lens. I didn't notice she
had undone the buttons until her hands wound through my chest hair,
tugging like a rider at a horse, and pulled me down, as somehow,
like a magician's trick, my pants were lying on the chair, and my
boxers too. She wasn't wearing much under the slip at all, mostly
just skin. There was a little darkening of hair, but my, she had a
fine body. Athletic, too. She knew what she was doing, and I got
lost in the flow, the rhythm, the back-and-forth of it all, as a
flower of light blossomed in my mind, my eyes closed in ecstatic
pleasure and joy as I felt like new life had flowed into my aching
bones and washed away everything that was wrong, and she squealed a
sound of pure delight that rang like a bell in my mind with a
sparkling love and glory as I dropped away, exhausted.

Waking up was hard after what had gone on before, but I managed to
pull myself together enough to smell the iron and the sticky-sweet
smell. My eyes opened, and I saw red. Lots of red, all over the
mirrors and the walls and the ceiling and spilled onto the
bedsheets where we had lain the night before. The room stank of
blood, as I saw spatters across the dresser and sprays on the
mirror, which had dripped down some, and traced red trails across
my image. As I moved on the bed, it squished with blood and oozed
out red, onto the already soaked sheets and into the dark red pool
around me. I saw her body on the floor, bullet holes riddling her
side, and still somehow pumping out the gory flood, slowly, pump{\ldots}
pump{\ldots} {\ldots} pump-{\ldots} as the dark red dried around her, and all over
the room it still rolled down, a sad end to a pretty girl like
her.

I was back where it all started, in the office. There was more
smoke this time, it was like a dream. The booze burned, but not as
much as the memory of her lying there, her vital fluids pumping out
onto the floor, already drowning in blood. She had been so pretty,
too{\ldots} I reached for another bottle, and forgot the glass this
time. It wasn't like it was the taste that mattered anymore, it was
the forgetting. I pulled out more tobacco, and added a little extra
from my hidden drawer. I needed to get rid of these memories. The
smoke was different now, the taste was more bitter, but I didn't
care. She would go away. As the haze took everything, she walked
through the fog and everything else faded, but she was clear. She
stood there, pretty as she was when I saw her first, and wearing a
little black silk thing too, it was so thin and sheer, you could
see every detail, and my, wasn't she fine. She started to pull it
off, and slowly, slowly, it dropped to the floor, too softly to
hear. She turned, and started to dance. I just wanted to forget.
Here she was. Relief. I wanted her to go away. Release. Let me
forget you, I wanted to scream. Let me die in peace! The smoke was
acrid now, burning and black. The pain was fleeting, and the dark
was better. The room was painted red, a red fog that spread through
the smoke to coat the wall, and pour out onto the floor, a sticky,
dark red pool that shined lazily under the swinging light.

fin.





\section*{The second story!}





I stood at the corner of Selby and Rice glaring at the bright neon
sign hanging over The Purple Mermaid Motel.

``Years of being a private detective and this is all I
get?'' I swore under my breath and gracefully walked through
the revolving doors. The dim lighting over the front desk glowed
ominousness, casting shadows on the stained carpet over the cheap
linoleum flooring. I curled my lip and walked cautiously to the
small man perched on a bar stool and gazing down on the desk, only
moving to adjust his glasses and scratch something with a ball
point pen.

``Excuse me, are you David Dawson?'' I asked placing my
hands on the counter, attempting to look intimidating. I quickly
removed my hands noticing a large cockroach scuttling along the
banister.

``Yeah, who want's ta know?'' he continued to look down
rather than up at my face, which was frustrating to begin with, but
to actually question who I was{\ldots} that was another
frustration.

`` Luke Bavarious, Privet detective, per your request.''
I could feel my lips tightening into a straight line as I held on
to the 't' entirely too long. Dawson turned up to face me, a mask
of filth covered his what I assumed white skin and his blue eyes
seemed magnified by his horribly dirty spectacles.

``Yea' came sooner than I espected.'' he stood up and
walked from behind the desk to shake my hand. He shook my hand
entirely too long and pressed his body unnaturally close to me in a
hug. I restrained myself from pushing him away and walking out of
this cheep rat hole, the money was too good to turn away.

``That's what I'm known for'' I muttered, looking around
the room for some clue as to the 'disturbance'

``What seems to be the problem?'' I asked, my voice
taking on the familiar tone of compassion and intrigue.

``Well, some of my regular guest{\ldots}'' there are GUESTS in
this place let alone regulars? ``say they've been hearin'
some{\ldots}'' he paused to think of the word.

``Sounds?'' I supplied and he nodded.

``Damn you are good{\ldots}'' I suppressed the desire to roll
my eyes and simply smiled at the complement. ``Well, I was
hopin' you could make us{\ldots}comfortable again, putten our minds at
rest, ya know?'' oh it would take more than a simple sweep to
put my mind at rest in this place{\ldots} I nodded again and dazzled him
with my 'everything-will-be-okay' smile.

``Show me to the room.''

* * *

I unpacked my tool kit and began scanning the room for simple
signs; rats, roaches, people playing tricks. Luckily, I couldn't
find anything that pointed towards rats and roached, but the idea
of someone leaning into the paper thin walls and creating an 'eerie
sound' made me satisfied. I decided to spend one night in the room
to make sure I was right. Easiest \$400 I've ever made{\ldots} my
thoughts trailed off as I slipped into the semi-attractive bed and
shut off the light. Quickly, I turned it back on and strained my
ears. Calm yourself{\ldots} don't get so worked up. I shrugged my
shoulders and turned the light off for the second time. Nestling
into the pillow, I shut my eyes tight and concentrated on my
breathing.

``lllluuuukkkkkeee'' I sat up straight and looked around
the darkened room. I chuckled softly to myself, the room being
entirely too small for another body to go unnoticed. I shrugged
again and settled back into my routine.

``lllllllluuuuuuuuuukkkkkkkkkkkeeeeeeeeeeeeeeeeee'' I
turned the light on one more time and jumped out of the bed. There
is only a logical explanation for this. The only person in this
piece of crap is Dawson, which must mean he is behind the wall{\ldots} I
silently grabbed my gun and slid a magazine into the belt, leaning
against the wall I positioned myself. I kicked the wall and the
plaster gave way with ease, taking one look inside the hollow wall
my mouth ran dry.

12:21 Standing before me was a large man's body, or what was left.
The eyes were removed and caked blood filled the outer rim of the
sockets, his teeth were broken and jagged inside his mouth, lips
torn off to reveal rotting flesh and maggots. My skin crawled as he
opened his mouth once more and uttered my name.

``llllllllluuuuuuuuuukkkkkkkkkkkkkeeeeeeeeeee'' my eyes
widened in horror and I rushed out of the room, leaving my tools
and clothing behind I dashed down the stairway and into the main
room.

``Dija fix it?'' Dawson asked, holding up the money. I
grabbed the bills and rushed out the door without a word, quickly
across the street and into the bar.

``I quit'' I muttered, ordering my first round.

I had barely begun my first drink before I heard it.

``llllllllllllluuuuuuuuuuuuukkkkkkkkkkeeeeee'' I felt my
heartbeat quicken, my pulse erratic and sweat start to pound from
my veins. He's here? My thoughts seemed childish and rhetorical, of
course he was. I took a shallow and shaky breath, hands and lip
quivering in fear, stood up and walked towards the door. I threw a
twenty on the counter and pushed my way through the doors. There he
stood in the glow of the parking lot, flesh falling off as he
stood.

``lllllllllllllllluuuuuuuuuuuuuuukkkkkkkkkkkkkkeeeeeee''
I cocked my gun and fired one, two, three. I could feel the fire
back effect and emptied my clip into the corpse. He only smiled, or
what I thought would be, and opened his mouth again, saliva
dripping down onto the concrete. My heart thudded against my chest,
ragged breathing tearing through me like a cold blade. I threw my
gun to the side, useless to me now, and closed my eyes. You can do
it! I urged myself forward and threw myself on top of him. My fists
met flesh, tearing and ripping at the body in an attempt to ward it
away. My eyes shut tightly, I continued to pound my fists into the
cold man hoping that this would finally take his retched face from
my memories. I dug through my pocket and took out my switchblade,
releasing the blade I stabbed and ripped at the face tearing it
apart before my very eyes.

12:46
``lllllllllllllluuuuuuuuuuuuuuuuukkkkkkkkkkkkeeeeeee'' I
stabbed and stabbed and stabbed until the body ceased and the mouth
released one final word.

``Luke?'' I opened my eyes and saw Dawson laying in a
bloody pile under me, his face ripped to shreds by{\ldots}my blade. I
glanced around for the body of the cold man, but I couldn't find it
anywhere. My heart began to pound again, filling my ears with
rushing blood, drowning out the screams and chants of the gathered
spectators. I barely noticed the cuffs being slapped on my shaking
wrists or the rough push into the white van. As I gazed out the
small window in the van I heard short breathing and a slight
chuckle. Slowly I turned my head and gazed into the eyes of the
corpse.

``llllllllllllllllluuuuuuuuuuuuuukkkkkkkkkkkkkkkkeeeeeeeeee''

 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Nobodys Savior}
\by{Pro-Swordbro}





My grandma always said I'd be nothing. I'd approach her with an
aspiration, she'd mock, criticize; ``You're too dumb to be an
astronaut'', ``How you gonna rap if you don't know meters?''. She was
french.



I miss her.



I am a police officer. My name is Luke Bavarious, badge number
\#25912. I used to freelance, I saw the worst this cruel polluted
world could offer me. Drug users; marijuana in their veins and
hatred in their eyes, crooked cops who took bribes and sold justice
to the highest bidder, I think I even saw a man with a tail
once.



However, what worried me most was what was staring back at me in
the mirror.



I bought a new gun recently. From some punk kid in an alley, handed
him a couple crumpled twenties, he handed me this Beretta. It felt
solid in my hands, the metal was cold, cold as this goddamn
December night. I walked out toward 42'nd street with a fresh bulge
in my coat pocket. Something had happened here, the memories
wouldn't come. They rarely do. It's hard to hold on.



My last night in my practice was in this neighborhood, I thought.
Probably busting some drug ring, mabye saved some old lady from a
mugger, or some old drunkard from himself.



Word around town is someone's killing kids. Stabbing them with a
knife, impaling them from behind. A child told me, his name was
Julian. When I heard this I vomited. According to this kid, someone
with a cross on his neck and a knife in his hand was following him
and his little friend. Julian's mom came to pick him up, he begged
the mom to take his friend home. The man had made himself scarce.
Him and the mom drove off.



I gazed around with my eyes, everything was quiet, it was still; it
was as still as it was quiet. How am I going to find this
sonofabitch? The police sure as hell aren't, the ones who are not
incompetent are all marijuana addicts, no help they are.



It was up to me, Luke Bavarious, badge number \#25912 to find this
demon, to avenge these horrible deaths.



My phone rang. ``Just let it ring Bavarious, whoever it is would
provide no help''

RING

RING

RING

I surrendered to it, flipped it open.



Luke.

Yes?

I might have something on that knife wielding maniac you are always
talking about.

What?

Some guy with a crucifix was murmuring to himself near Biddick
Park, this afternoon.

*click*



It was a few hours until morning, The sky was vomiting snow as I
walked to my apartment, the snow crunched under my combat
boots.



I haven't eaten in days, I can't keep anything down. I tried to
watch TV. Something scary was on, It was alright.

As I got up after the movie ended, I could practically swear I saw
a face in the window. A face.



I'm losing it.



I gazed at the clock, it was 6 at night. Where had the time
went?



The stairs proved no more than an organized hill for me, I exited
into the street and made my way to Biddick Park.



People looked at me with admiration in their eyes, and why wouldn't
they? I'm a hero, I'm a {\ldots}savior? No, not that far. I fingered my
Beretta in my pocket.



I thought in my head of Julian as I approached the dimly lit park,
a more brave witness there never was. Goes to show that kids need
to be respected and listened to.



I noticed a man leaning against a building. He was wearing a Run
DMC shirt, I immediately recognized that as a rap group, I'm quite
interested in black culture. I had a hunch he wasn't my man
though.



It was then I noticed a man following a child, twenty to thirty
feet behind, My experience taught me how to spot a tail. I used to
be a cop. I took a route to intercept him, something gleamed in his
hand, this is him. I approached him, and held my Beretta to his
head. ``You there, turn around!'' I shouted. He pivoted and glared at
me, a cross dangling from his neck. This was it, this was the man
who had murdered that kid. His eyes were gleaming black, I gritted
my teeth to keep the vomit down.



He made a sudden move suddenly, bringing his knife up across my
neck. I fired at him.



My neck vomited blood. His neck vomited blood.



There was nothing I could do but sink down to the ground, lying in
the snow, my monster beside me, gurgling; blood? vomit?
whatever.



``You know, you and I aren't that much different'', he giggled.
Suddenly I was sobbing. 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Words Will Never Hurt Me{\ldots}}
\by{Detective Thompson}





Young Bin Beddick was angry. He could feel the foamy rage rushing
through his ducts and into his brain. His parents didn't
understand him. They did not understand him. Did they understand
him? No. He could still hear his dad's stinging words echoing
like the tones of the Liberty Bell, ringing in his ears.

``What is this crap?'' his father bellowed like a walrus.
Bin had showed his dad his latest story. Bin was proud of the
story. But his father just crumpled the paper up, and tossed it in
his face.

``I will not allow this heathen tome within my house!''
he raged at the young Bin, before sending him to his room without
supper. His mother laughed her awful laugh, which sounded like the
cackling of a mother pig.

It was dark that night. As Bin bubbled like a cauldron of hatred
and spit, night-dim clouds began vomiting rain and lightning onto
the earth. Bin wished he could shoot lighting at his parents. But
no, he had better ways to get back at them. The pen would be his
weapon. Despite his young age of thirteen, Bin was capable of
writing like a pro. His teacher told him his writing could make
James Joyce and Shakespeare spew jealous tears from their eye
ducts. Bin's fellow students quaked in awe whenever he gave
one of his weekly readings, weekly readings that had been insisted
upon by the principal, Mr. Howard. Mr. Howard hoped the other
students would learn something from Bin. So far, all they learned
was fear. And jealousy.

So Bin picked up his pen, his fingers closing around it like steel
claws closing around the neck of an unsuspecting victim. Bin smiled
as he set to work, his pen flying across the page, his pen
releasing little black trails of ink, dark coffin worms that formed
words of terror and evil. Bin would show his parents what it was
like to be burdened with such talent. If it were ever to happen,
Bin felt tonight was the night he could give life to his words, for
real. How little did he know, he was too right{\ldots}

As Bin finished his tale of fierce revenge and bitter anguish, he
heard a cough from behind him. The sound of a man clearing his
throat. Reflexive instinct twisted Bin's neck around, until
he caught sight of the man behind him. Tall, shadowed, wearing a
heavy black trench coat and gripping something in his right hand.
That something was the sleek, metallic shape of a Beretta pistol.
The kind a detective might carry.

``Who are you?'' Bin asked with something more like
confusion than fright. Bin was made of stuff much too dense for
fright.

``Luke Bavarious,'' came the words, spilling from the
man's shadowy mouth like soup from a Grandma's lips.
Bin's eyes went wide, then turned mechanically like a
robot's eyes to the pages in front of him. At the top of the
first page, like a crow roosting above in a branch, sat the title
of his story. `Luke Bavarious'.

The man chuckled. Bin gasped, bewildered beyond thought.

``But{\ldots} but how?'' he stammered, again, not with fear
but with unknowledge.

``You gave me life, Bin. Your pure and simple rage came
together and hardened like a Jell-O mold in the fridge, creating
me, the perfect tool of your anger!'' Luke Bavarious nearly
shouted with glee. Bin hoped his parents wouldn't hear.

``But what are you doing here?'' Bin wondered aloud. Luke
smirked. He gestured with his Beretta toward Bin's door,
beyond which his parents were undoubtedly sitting like sheep before
the TV. Before Bin could speak a word, Luke Bavarious charged forth
like a rhino charging a hunter. Luke Bavarious smashed down
Bin's door. Bin could only follow him out into the living
room, where his parents were watching some inane television
program. When they noticed Luke Bavarious, both his mother and
father shrieked like lambs with their faces cut off. Bin's
father leapt to his feet. Luke Bavarious raised the Beretta pistol
and fired, the bullet entering his father's brain, Satan-red
blood gushing forth from the hole in the back of his skull. He was
dead. Bin's mother tried to run, but Luke Bavarious shot her
in the back. She fell like a few dozen sacks of potatoes.

``Oh, my spine!'' she whimpered. Her spine indeed. Bin
could see into the bullet hole, see her spinal column wriggling
like a snake caught in a bear trap.

``Mother!'' Bin cried.

``Why Bin, why?'' was all she could sputter from her
bloody mouth. Then she died.

``No! I didn't want this to happen!'' Bin screamed
at Luke Bavarious with all the rage of a volcano in Pompeii.

``Oh but you did, Bin. You did,'' Luke Bavarious
chucklingly spoke. Then he pointed the Beretta at Bin.

``Why me?'' Bin shrieked.

``Because, you are a bad boy, Bin. And bad boys must be
punished!'' Luke Bavarious said his final words as he pulled
the trigger of the Beretta. The bullet from the Beretta slammed
into Bin like the 42nd Street Subway slamming into a hobo that
jumped onto the tracks for some loose change. Bin collapsed, rusty
blood erupting like a fountain from every orifice in his face and
from the hole in his chest. A final, horrid chuckle escaped Luke
Bavarious' lips before fading away, dying with his creator.
Bin couldn't understand it. Luke Bavarious was a good guy in
his stories. How did this happen. And then, just before dying in a
pool of the blood from his body, it hit him, like a bat hitting a
skull.

``If only my parents respected me, then this never would have
happened!''

Then he died. 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter[Dead Tired]{Dead Tired\\Horrid Reflection: Gaiden}
\by{Count Snapula}



Luke Bavarious woke up from a horrid dream in his Manhattan
apartment. He was vomiting sweat from every pore in his body. It
was exactly 6:36 in the evening, according to his digital clock. It
was blinking red. The color of satan. Luke had been having the same
nightmare for a week now. He was on duty looking into noise
disturbances when he was assaulted by a horrid monster, that was
maybe himself. Not even his trusty Beretta could save him from the
undead menace. Detective Bavarious grimaced grimly as he put on a
dirty wifebeater and some slacks that smelled faintly of hobo
urine.



Walking to his refrigerator, Bavarious picked up the ubiquitous
Beretta off the toilet on the way there. He searched through the
crisper intensely, only to find a week-old tuna sandwich and a
single piece of knockwurst.



``Jesus fucking christ. I wish my wife didn't leave me,'' bemoaned
Bavarious as he settled for the tuna. The bitterness over his ugly
divorce almost masked the taste of sour mayonnaise. With some
sustenance in his stomach, he began shaving over the kitchen sink.
Though Bavarious was uncannily dexterous with a Gillette{\copyright}
Fusion razor, something caught his eye in the reflection of the
faucet, and he made a deep gash in his face. Rust-colored blood
began to spray out, but fortunately Bavarious was able to hold back
the flood with a wash cloth.



``Man, I must be going crazy or somethin','' muttered Bavarious to
himself as he opened his last can of Coor's Light, which responded
with a concerned '{\em pfffssssssht}'. Turning around to look out
the window and watch homeless people fight over garbage until his
shift began, Luke finally saw the culprit of the Razor Incident: an
enormous crow, black as midnight, holding a human eye in his beak.
Never to be caught off guard, Bavarious emptied his clip into the
horrid avian intruder. As he went to confirm the death of the crow,
he saw something that drained all the blood from his face.



Below on the fire escape was his ex-wife, her intestines trailing
out of her corpse and one eye pecked out of its socket. Seeing
this, Bavarious vomited uncontrollably out the window and onto the
grisly scene.



``Who could have done something like this?!'' Shouted Luke Bavarious,
once he had regained control of his bowels. Suddenly, he felt his
hands bound behind him, with the familiar click of handcuffs.



``You did, Detective Luke Bavarious.'' Replied an NYPD officer, who
had just walked in with three others through his open apartment
door. Suddenly, those dreams all made sense to him. ``You've done
well by me, Luke Bavarious,'' whispered a terrible, gravelly voice
in his ear. He could tell it wasn't the cop taking him to the
street, because he had been punched in the balls as a kid and now
he talked like Elmo.



``What have you done?!'' Luke struggled to break free from his
captors. But in the end, he knew it was true. The real captor was
himself.



``Go to sleep, Luke. I'll take care of this,'' the voice whispered
smugly. Luke suddenly passed out, then. When he woke up, he was
covered in rusty red blood down to his buttocks, and all four cops
were dead. 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Black River}
\by{Creflo Chronicle}





The horrid, crushing sound of a gushing river broke through Luke
Bavarius's rushing mind. He had awoken from a deep sleep to the
sound. The horrid sound. He had a hangover from too many Coors, and
it was driving him mad. Ever since the alley, where the ghoul had
deformed him, he drank every night until he blacked out. Otherwise,
there were the dreams. The horrid dreams.

But now the river had woke him up. It made no sense. He lived in
the city, not by a river. And the sound was driving him mad. He
vomited.

He got out of bed and shook the horrid vomit off his hands. He went
to his window. He looked out of his window. His apartment had been
moved from the busy city to a deserted hill overnight. At the foot
of the hill was a river. A black river. He went to his front door.
He opened it. He stepped outside. Rough stone steps lead from his
door down to below the surface of the rushing river. He turned
around and looked at his apartment. It was as though a giant had
reached in to his apartment building and scooped his apartment out
and then dropped it on top of the hill. The grass on the hill was
brown and dead. Around the base of the hill there was a dark,
impenetrable forest. Bavarius thought he could see faces peering
out at him from between the trees. Suddenly, night fell. Luke ran
in to his apartment.

The moon was the only light to be seen. There were no stars. The
moon shone down and was reflected on to the river.

Two fiends rose out of the river, walking up the stairs. They were
as tall as a tall man, but fat and obese. They looked the way
babies would look if they were as tall as a tall man. They were
white with black splotches like an albino who had had mud thrown on
him. They were naked. Bavarius quivered with fear, and held his
Beretta close to comfort him.

The manbabies reached his door and stopped. They shouted to him
inside the house in unison. ``Luke Bavarius!'' they shouted. ``Let us
in and we will save you from some pain!'' Their voices were like a
sick man vomiting while trying to talk.

``No!'' Luke shouted.

The manbabies each raised a hand and pressed it against the door.
The door flew off it's hinges and slammed into a wall like from an
explosion. The manbabies entered Luke's apartment.

Bavarius was still shaking with fear, but his killer instincts
kicked in. He leveled his trusty Beretta and fired 4 quick shots: 2
in each of the ghouls' heads. The bullets struck them and black
ichor vomited out of the wounds. Soon though it congealed and
clogged the holes. The manbabies smiled and walked forward. ``No!''
Luke shouted. They didn't listen. They walked him out of his
sliding glass door that used to lead to his balcony. It no longer
led to his balcony. He wasn't in the city any more.

Outside there was a flat black stone, like a chunk of a freshly
paved road, but it looked natural. The manbabies led him to it and
held him against it, one at either end. The one by his head held
his arms down against the stone. The one by his legs held his feet
down against the stone.

Skinny, emaciated people emerged from the forest and came up to the
stone. In their hands they held sharp shards of rock. One by one,
they stepped up and cut a deep gash in Bavarius's skin. He screamed
horridly. Wherever his rust-colored blood vomited from his body
onto the grass, the grass came to life with a rich golden sheen.
The life spread across the grass slowly.

``No!'' Luke shouted.

Luke died.

When the last of his blood had left the wounds, the manbabies each
grasped their end tightly and tugged, ripping his body in half.
Each tucked their half under their arm and trudged down the stairs
and under the horrid black river. As they submerged, the river
seemed to dry up, leaving a barren riverbed.

``It is good,'' the leader of the tribe said to his woman. ``Our crops
will grow again.''

``Yes, it is good,'' said his woman, patting her pregnant stomach.
``Little Luke Bavarius will not starve.''



The End 
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{The Area the Moon Ignored}
\by{slackerpride}



The moon was glowing, sending its light all over the town. All over
the town except for one part. That was where Detective Luke
Bavarius heading.



The calls came in tonight --- like they had every night for the
last ten years. ``Officers,'' the voices said, ``I
saw something in the darkness{\ldots}maybe a man, I'm not sure.''
``Ya gotta believe me Mac, there is something dark going on
there.'' ``It maybe occult related, I've read
articles!'' No one ever cared enough to believe it, but the
Chief's patience with the never ending calls finally came to an end
tonight.



The same day his patience with Detective Bavarius ended also.



The sounds of his shoes hitting the pavement made a rhythm that
sounded eerily like a heartbeat. {\em Good}, thought Bavarius,
{\em now I won't have to listen to mine} . Bavarius' reached into
his pocket and felt the cold steel of his Beretta on his skin. He
didn't want to have to use it, but he was ready to. {\em That's why I
go to the gun range}, Bavarius thought grinning to himself. His
teeth glowing like the moon.



Suddenly, it started raining. The sky vomited it's tears on
Bavarius, thankfully he was wearing his hat. {\em Never leave home
without}, Bavarius mused. It was coming down in sheets, like
cats and dogs, and it made everything slick --- except for
Bavarius' vision, which was as sharp as ever.



Chief didn't see that. Chief didn't see anything, except for the
bottom of a brown bottle. No one else knew but Bavarius and he
never said anything to anyone. He had caught chief one night
outside the back of McLeary's puking his guts out maybe ten years
ago. It was tinged rust colored, no doubt a horrible cocktail of
bloody Mary mix and blood most foul. Bavarius and him locked eyes
--- and ever since then they've been at each others
throats.



Suddenly, he was on the outskirts of the dark part of town. New
York City was big, but there were parts that were small. This was
one of those parts. Bavarius took a step into the darkness ---
his heartbeat stopping and blood chilling his body. Things were
different here. They were strange. This was the area the moon
ignored.



That grip around his gun was tight now. Bavarius pulled down his
hat, shielding his face from the rain that was falling. He wanted a
cigarette but remembered he quit last week. {\em Damn}, Bavarius
thought, {\em a Chesterfield would do me good now}. But there was
no time for smoke right now, Bavarius had to keep his vision sharp.
But it was hard, because it was dark. There was no light. The moon
even ignored this area of town.



Then, off to his left, near a diminutive pile of offal storage,
there was a rattle. It sounded like a chain, but Bavarius wasn't
sure. His one strength, vision was compromised by the darkness of
the moonless section of city. The rain fell, filling his ears with
constant buzzing like someone was selling bees nearby at discounted
prices. {\em Crazy thought}, Bavarius thought, {\em but this is New
York City --- anything is possible}.



``I agree Detective Luke Bavarius, a voice came from the pile
of rotting smelly garbage and various garbage cans.



``Who is there?''



``Oh Bavarius, I think you know me well.''



``Listen,'' Bavarius said gruffly, ``I'm not above
firing a shot into those cans. It's dark here and no one will see
anything.''



``He will. He knows everything I know.''



``Who is he,'' Bavaruis asked cocking his gun. {\em What's
going on}, Bavarius thought glancing from side to side. The
academy hadn't trained him to deal with hell on Earth.



``You wish to know what is going on{\ldots}I can read those
thoughts well. I was born with this gift{\ldots}though some might call
it a curse.''



``You can read my thoughts?''



``I can see into the dark corners of your soul Bavarius
--- mind reading is but a minor talent.''



``No bother asking then. Just tell me what's going
on.''



There was a laugh, a hellish laugh that rang off the dark walls
like a booming sonic boom from a low flying jet airplane. There was
more rattling and Bavarius now wished he had that cigarette so he
could shine some light on the area. There was more rattling frOm
that area.



``Just come out --- if you're going to kill me, let me see
you first,'' Bavarius bartered with the thing from the
trash.



Laughing the thing thus spoke, ``Very well{\ldots}you shall see me
and know where I come from.''



The can rattled once more and then, as if on cue, a nearby broken
street light flickered to life. It wasn't a lot of light but enough
to stun Bavarius to his soul. He --- or it --- dragged
itself from behind the can. It was no more then three feet tall.
There were no eyes.



``I need not eyes Bavarius --- I see
everything.''



The street light flickered off again.



``Jesus,'' Bavarius garbled out of his cracked open and
dry mouth.



``Not even close.''



The creature was red and looked like walking vomit mixed with bits
of trash. It smelled like a horrible combination of garbage, vomit,
death and dank darkness. If it wasn't for the constant stream of
rain washing his shocked face, Bavarius' eyes would be blinded with
fear tears.



``That's right, that night you saw the Chief vomiting, that's
when I was born. You see he is not human nor am I. He is my father
--- a creature from the depth of an unimaginable hell ---
he birthed me that moonless night. You are the only person to know
our secret. You will be the only one to ever know. Because,
Detective Bavarius, you shall die tonight.''



And then the creature made his way towards him, quick like a sly
brown fox. Bavarius squeezed the trigger and felt the recoil as he
sent six bullets towards the approaching creature. The bullets tore
through the walking vomit and shattered into the garbage cans
behind him. Laughing, the creature kept coming forward.



Bavarius wanted to run --- his every instinct wanted him to do
it --- but his cop's instincts took over. He was going to stay
and fight even if it meant death. Bavarius dropped his gun, took
off his hat and threw his trench-coat on the floor. He rolled up
his sleeves and glared at the creature like a beast gone
wild.



``Let's death dance you nasty bastard,'' Bavarius
growled, the hair on his neck rising.



``A foolish mistake.''



And then the creature leapt like a dancer towards Bavarius. This
thing was growling, shooting his nasty breath towards Bavarius. But
Bavarius didn't move. He was determined to catch this thing and
body slam it to the cold wet concrete if possible. Perhaps he could
cuff it before the thing got away.



Suddenly, as if God flipped a switch, the area the moon ignored was
awash in moonlight. A beam of it hit Bavarius' badge which hung
from his neck like a necklace. That beam hit the creature and it's
manic laughing changed into horrid screaming. Before it reached
Bavarius and possiblY killed him, it erupted like a fireworks
display.



The bloody vomit creature spattered all over Bavarius's face and
body. His white shirt was now rusty looking with blobs of trash
sticking to it. Bavarius could taste it --- not just the
creature'S gooey body but impending revenge.



The rain let up and the moon disappeared behind some clouds.
Bavarius placed his fedora back on his head and put his jacket back
on. He also reached down and grabbed his gun. Feeling inside his
jacket pocket, he felt something. Bavarius pulled it out --- it
was his last cigarette from last week. It would taste gross, but
Bavarius was already knee deep in gross. He struck a match and lit
it up.



Cocking his baretta, Bavarius stood and grinned. He knew what he
must do next. He knew it was going to be ugly. He took a nice long
drag from his stale smoke and exhaled. He placed that loaded gun
back into his rain soaked jacket pocket.



``I'm coming for you Chief.'' 

 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{The Killer B}
\by{Yaos}





Luke Bavarius looked down at the ground, it turned a putrid rusty
caused by the bullet holes in his latest victim, Zigmatron
McGlutenon. Luke Bavarius brought his Barreta up to his nose and
took a smell. ``This smells good, it smells like'' but
stopped in mid sentence because he thought he heard something so he
looked around but there was nothing there except some things, so he
continued speaking loudly, ``death''. Every time Luke
killed somebody it reminded him of the time his son told him that
he should not go out, and when he did and came back his son was
dead! His son had died a long time ago, almost 3 months now today.
Luke found his son's body but no head because his head was torn
off. They searched for days but no head was ever found. They even
used dogs that are good at finding heads without bodies.



``Why do I keep doing this'', Luke thought to himself.
``I can't keep killing, it won't bring back my son Luke
Jr.'' Then somebody said that this was not true at all, but
who could it be?



``But that's not true Mr. Bavarius, killing can bring back
your son, because I can help you.'' Luke saw a man he had
never seen before that looked like he was 50 years old with gray
hair and balding. His sweater smelled of blood. ``Luke, I know
something that you do not, your son is not really dead!'' But
how can this be?



``I don't understand, I buried his body in the ground myself
and his head was gone! You can't keep living without a head! And
who are?'' Luke was distrustful of the stranger.



``But you can live with a head Luke, and your son still has a
head, he's not really dead at all because the body you found was a
fake and that's why you did not find his head because there was no
head to find.'' Suddenly it all made sense very quickly, Luke
Jr. did not feel like any body Luke had felt before and he always
thought that something was wrong and now he had the proof. ``I
am Ugundun, you need my help and I have a shop that can help
you!!''



``We can't talk here Ugundun, we need to go to your store
before more thugs show up to kill us.''



So they went to Ugundun's store, where Luke had gone many times to
buy guns and bullets from from Ugundun, but it was weird that he
did not know who Ugundun was, that was very odd indeed.
``Let's have a beer'' and so they had a beer while they
talked about Luke Jr.



``Do you want my help Luke?'' He did want his help.
``Good, but first you must kill somebody for me.''



``But, I'm done killing people, I promised my dead son Luke
Jr.'' Luke was angry that Ugundun wanted him to kill, but
after a while he decided he would help Ugundun if it meant he could
get Luke Jr. back. ``So who do I need to kill''?



``You need to kill this man.'' Ugundun handed Luke
Bavarius a picture of something that looked like a man but was not
a man, it was a two legged dog.



``But it's not a man, it's a two legged dog!'' Luke
Bavarius was about to rip up the picture but Ugundun stopped
him.



``You should know that appearances can be deceiving, you found
out your son is not dead and even though you ignored him you can
still get him back.'' Luke Bavarius knew Ugundun was right so
he ran off to go kill the two legged dog.



Luke Bavarius walked into the park where the dog was hiding out, as
he walked through the park he patted his trusty Baretta that he has
used many times to kill people with. And there it was, the two
legged dog! But it was not like the picture, he was covered in
rusty blood and vomit. ``Dad'' it yelled out.



``I'm not your dad dog.'' Luke Bavarius was angry at the
dog for lieing to him.



``No dad, I am your son, I'm Luke Jr. Don't you remember
me?'' The dog slowly walked up to Luke, and as he walked
closer he turned into Luke Jr.!



``Luke Jr. It's you! I thought you were dead! I'll always
listen to you again!'' Luke hugged Luke Jr. and gave him a
kiss and a hug.



``I love you dad, how did you find me?'' Luke explained
to Luke Jr. how he found him. ``Ugunden was the one that
turned me into a dog dad, you have to stop him!'' Suddenly it
all made sense, that's why Ugunden knew his son was not dead it was
because Ugunden had taken him all the time! Ugunden hated how much
Luke Bavarius loved Luke Jr. because Luke Jr. was a great child and
did everything right and everybody loved him and liked him and
Ugunden wanted him to kill Luke Jr. but Luke Bavarius did not kill
Luke Jr. Now it was time for Ugunden to die.



Luke Bavarius walked into Ugunden's shop, he threw a dog's head
with a bullet hold between the eyes on the table and said the job
was done. Blood and urine oozed out of the dog's eye sockets and
bullet hole. Ugunden took a look at the head and started laughing
and laughing. ``Ha ha ha Luke, that was not a dog, that was
your son!''



``I know that Ugunden, my son told me.'' Ugunden looked
surprised.



``But why did you kill your son if you knew the dog was your
son?'' Ugunden looked scared and Luke Bavarius knew he was
scared.



``I did not kill my son Ugunden, I killed this dog to trick
you. Now you're going to be punished! Luke Jr. get in
here!''



Luke Jr. Lept through a window while shooting Luke Bavariuses
Barreta and other gun, the glass showered out and covered Ugunden
giving him many cuts and scratches. Some of the broken glass got
stuck in Ugunden's eyes which made him blind and vomit. Because
Ugunden could not see and he was covered in glass cuts he started
screaming and vomiting and running around getting vomit and urine
and blood all over the place. Luke Bavarius opened his coat up and
started throwing rats and dog guts all over Ugunden which made
Ugunden defecate and urinate and vomit and bleed even more. The
rats started eating the dog guts which made Luke Jr. and Luke
Bavarious start vomiting also. The rats tried to eat the vomit and
feces and urine but it made them sick so they vomited and exploded
covering the inside of Ugunden's shop with rat guts and blood and
feces and urine and vomit. Ugunden was still screaming and running
around and he ran out the front door of his shop. A large semi
truck was driving down the road and the driver did not see Ugunden
in time and he ran over Ugunden. Ugunden's head exploded from the
truck's tires, all the guts and vomit he had not vomited out shot
out of him like there was an explosion. The driver of the semi
truck tried to stop but it made the truck skid out of control and
the truck ran into a pet store. All the animals inside started
hooting and hollering and they all ran out and they were all on
fire. The truck was filled with gunpowder so it exploded killing
all the animals.



``Thank you for helping me dad, I am your son and I will
always love you even though you did not listen to me.'' Luke
Jr. gave his dad a hug.



``I love you too son and I will listen to you from now
on''. Luke Bavarius started to walk away, as he did Luke Jr.
Raised his weapon and pointed it at the back of Luke Bavariuses
head.



``I know you'll listen to me for the rest of your life
dad.'' Luke Jr. pulled the trigger.



The End?
 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Character Sketch}
\by{Ghost Hat}



I frowned as I looked at the crime scene. The lawn had been well
kept once, but now it was all wild. The grass had been green once,
but now it was all brown from the blood. The blood was from a
corpse named James McDaniels. He was ten years old. He was murdered
here last week in front of his house. James McDaniels' father
had hired me to find out who killed his son{\ldots} or what.



My name is Luke Bavarius. I'm a private eye. I'm whom
they call when the police can't handle a case. Or if they
don't want to. This is one of those cases because James
McDaniels' father, James McDaniels Senior, is a crime boss
for the mafia and the cops don't like him. I don't like
him either, but I'm a desperate man.



I looked around and inspected the white chalk circles from where
his body was found. There were two. One for his body and one for
his head. The kid had been decapitated viciously. Just thinking
about it made me taste vomit in the back of my throat. At first the
police had suspected the kid's father. It makes sense. The
crime boss's case of alcoholism was publicly known. But he
had an alibi in his frightened wife and anyways it didn't
make sense since he hired me to investigate his son's murder.
A guilty man wouldn't do that.



It might have been a rival gang, or even a cop trying to get back
at McDaniels Senior, but I didn't think so. The crime was too
violent. The force used to tear off the kid's head, the
distance it had been thrown, the amount of blood{\ldots} it had to
be personal.



I didn't like to think that another kid could do this. I
didn't even know how since to rip even a kid's head off
you would need at least the strength of a gorilla. But I
couldn't dismiss a lead until I followed up on it. An
investigator follows his instincts and mine said I was on to
something fishy here.



At the school I questioned everybody. Everybody who could have had
contact with James McDaniels. As I talked to more and more people,
I started to draw a picture in my head. The picture was one of
James McDaniels, and soon the picture got more and more detailed.
He was sent to the principal a lot because he picked on other kids.
He would torture, beat, and steal from anyone smaller than him. He
was a bully of the worse kind, just like his dad. I guess
it's true that the apple really doesn't fall far from
the tree.



``Is there anybody James really picked on? More than everybody
else?'' I asked a little boy during lunch. He was maybe a
third grader, and he didn't seem too unhappy about his late
tormenter being dead. Who could blame him.



The boy looked thoughtful for a moment and then pointed to a dark
corner in the cafeteria. He said with a mouthful of hamburger,
``Tommy. James hated Tommy because Tommy was never afraid of
him.''



I thanked him gratefully and looked over in the corner. A boy was
there and it was strange. Every other kid here was eating lunch and
laughing with each other. But not this kid. Not Tommy. He was alone
and hunched obsessively over a bunch of papers. I think he was
drawing, though I couldn't see what from here. I knew I had
to talk to this kid.



``Hey Tommy, what are you drawing?'' I asked carefully,
sneaking a peek at his masterpiece. It was a picture of the
cafeteria and all the kids in it. I figured it'd be a
child-like scribble, the sort of stuff normal kids do, but I was
surprised to see that it was pretty good. ``Hey, you're
better than I am,'' I joked.



``It's just practice,'' Tommy mumbled, covering the
drawing with his hands. He looked away from me and stared hard at
the wall.



I paused hesitantly. I don't talk to lots of kids in this
line of work, but I knew that I had to try. ``Tommy, I need to
talk to you about James McDaniels, okay? I'm trying to catch
the guy who murdered him, and I need a big guy like you to help
me.''



Suddenly the school bell rang and all the kids got up to leave.
Tommy shot up like the red plastic of the kid's chair he sat
on had burned him. He grabbed his backpack. ``What can I do?
I'm just a kid,'' he snarled angrily as he shoved past
me, rushing off to math class.



I blinked as I watched him go, and then I squinted down at the
papers he had left. He was going to be in a lot of trouble if any
of this was homework, but as I pushed the papers around I saw that
there weren't any words on them, just drawings. Some were of
nice things, but most of them were grotesque and disgusting, blood,
flesh, and vomit so realistic it turned my stomach. One of them
caught my eye in particular and I picked it up.



It was a creature all shadowy and dark. Its tail looked vicious and
I could feel the terrible expression on its face in my very soul.
But what caught my eye the most was the head it held in its hand. I
recognized that head. I recognized the house behind it. It was
James McDaniels' head and that was his house too!



That night I staked out Tommy's house. The sky was as stormy
as my mood. The clouds turned and swirled around as viciously as
the insides of my stomach. Even the lightning made me feel like
vomiting, but I smoked a Marlboro instead. It calmed me down enough
to think. I didn't know how, but I knew that Tommy was a
murderer. I needed to prove it somehow and get him put away, maybe
put away for life.



The broken clock radio flashed 12:00 A.M. in glowing green light.
All the lights in Tommy's house were off. Strange kid. All
alone, but he ain't scared of the dark. Tommy's parents
had gone off to a fancy party hours ago. Tommy's dad wore a
tux and his mom, a nice looking dame, wore a sleek little number. I
didn't expect them back any time soon.



The rain pattered on the top of my beat-up Oldsmobile like hundreds
of little mice feet. The lightning flashed and Tommy's house
was lit up in black and white, like some old horror movie. I
wasn't scared, but I reached inside my jacket and stroked my
Beretta. Thunder grumbled like a monster, a hungry one at that. My
imagination went a little wild as I thought of all those pictures
Tommy drew. That kid could draw all right.



The rain kept pattering away. Pattering away like thousands of
little mice feet now. But suddenly, with a loud thump, something
huge landed on the roof! It shook the car and I bounced inside and
looked up in surprise. The surprise turned to horror as I saw a
huge indentation above me. That was no mouse! No, I doubted it was
even a really big rat!



I pulled out my loaded Beretta and aimed at the roof above me and
fired three rounds in quick succession. I know I missed it though
because I felt the thing leap off the roof and land on the street
outside the car. Nothing but rain came through the holes, good news
for my seat cushions but I wouldn't have minded the cleaning
bill. It was too dark with night and rain to see outside the
window, so I opened the car door and leapt outside, squeezing my
pistol blindly into the air. The thunder cracked then, even louder
than my gunshots and I heard a scream louder than them both
combined.



I peered into the wetness and saw a dark figure clutching at the
side of its neck. Thick black blood oozed from between its fingers
and as it screamed again, more vomited from the creature's
mouth. I moved closer, clutching my Beretta with white knuckles. I
was staring at the creature's head, but I realized what a
mistake that was when I recognized that horrid expression on the
monster's grimacing face.



I leapt back. Just in time as a whip, faster than a speeding semi,
struck right where my skull would have been. It was the
creature's tail. This thing. This man that was more monster
than human was the beast from Tommy's drawing. My brain was
struck with awe, but luckily my hands didn't care about what
my brain thought. My fingers squeezed at the Beretta's
trigger over and over again, filling the creature full of holes.
Black blood sprayed out from all over the creature's body,
mixing with the pure rain, like mixing demon urine with holy
water.



The creature gave one last angry garble as it lurched towards me. I
could have sworn it said something in English but I don't
know what. My brain was on automatic as I fired my semi-automatic,
the barrel spewing out bullet after bullet. Finally the beast
staggered and collapsed, right at my feet. Its tail gave one last
feeble lash and subsided. Up close I could see how truly hideous it
really was, with pulsing black veins and oozing pustules all over
its body. I licked my lips and tasted salt, which surprised me
since rainwater is fresh. I was crying.



I knew I couldn't stop now. My hands shook with the
nervousness I had felt from the assault of Tommy's monster,
but I reminded myself of whom I was. I was Luke Bevarious. I was a
private investigator. I had faced down lots of tougher situations
than some kid with a coloring book.



I went inside the house. It was much quieter inside the house than
it was outside. The water dripping off my coat sounded loud in my
ears as I went from room to room, searching for the boy I knew must
be there. Finally I found him.



It must have been his bedroom. I spotted a bed and dresser out of
the corner of my eye, but mostly I saw the drawings. Hundreds and
hundreds of drawings stuck all over the walls and the ceiling, the
floor and every bit of furniture. And in the middle of the floor
was Tommy. He sat beside a flickering candle and didn't
bother to look up at me when I opened the door.



Tommy was drawing.



``Put down the pencil,'' I said, my voice sounding harsh
and gravelly. ``I got a pistol pointed at your head, boy. My
fingers have minds of their own sometimes, I can't promise
anything if you don't.''



``You're just in time,'' Tommy said with a soft
smile. I was surprised when he did what I told him to do, tossing
the pencil playfully off to the side. But something was off. His
smile was more than just a regular kid's smile. My eyes
widened in horror as I bolted forward and snatched up the
just-finished drawing. I gazed at it with terror as I turned around
to face the door I had just used.



Yes, it was just like the drawing. The kid was good. Really
good.



The End.
 



