\chapauth{A Child's Letter}
\chapter{Yellow Eyes}



``I'm not lying, Daddy!'' whimpered Kaitilin Axelplax, a six-year old
girl with an admittedly active imagination. ``I promise
you---{\em promise} you---that I saw it again! Saw
{\em them} again!''



Hubert Axelplax smiled his sick and twisted smile while
nonchalantly wiping the rust-colored tobacco drippings oozing down
his chin. Delicately, he set his Coors on ane Igloo cooler doubling
as an end table.



``Kai, what've I told you 'bout {\em lyin',} you little
{\em bitch!''} Without warning---though she knew it was
coming---Hubert, with speed belying his significantly
overweight frame, backhanded Kaitilin, sending her flying into the
wall. She collapsed in a heap, knocking over a floor lamp in the
process.



She stood, fought to find her balance, then, reeling from the blow,
vomited profusely all over the threadbare couch. Rust-colored blood
seeped wistfully from her gashed eyebrow.



``I {\em swear,} Daddy! I saw the thing with yellow eyes! It was in
the mirror!'' Again, she threw up. Hubert took three long strides
towards his daughter's trembling form and unbuckled his belt in one
fluid motion.



``You're {\em just} like her, you know that? Just like that
{\em whore} of a mother of yours!''



He raised the heavy leather strap above his wickedly grinning head
and---



* * *



Luke Bavarious' radio cackled to life: {\em All units, we've got a
10-34 near Forty-second and somewhere near Dyer. Possible 10-45;
10-52.}



Distractedly, Bavarious holstered his Beretta, taking a moment to
admire its clean lines, its intoxicating heaviness.



Suicide would have to wait.



He took one last, long drag on his cigarette, then tossed the
remainder out the window of his car. Baravious picked up his radio
and responded, ``Dispatch, this is Bavarious. I'm in the vinicity;
10-76. I'll check it out. Over.''



{\em 10-4, Bavarious. Out.}



For the first time in a long time, Bavarious smiled. Nothing like
an old fashioned assault with possibly fatalities to enliven the
night. He had to admit it: he liked this work.



Within minutes, Bavarious arrived at his destination. He parked in
an alley and realized he must be the first officer on the scene.
Everything seemed eerily quiet---especially for New York. Like
liquid, with practiced movement, he unholstered his sidearm and
kicked in the door.



The apartment building's lobby was empty. Bavarious involuntarily
shivered, then made his way up the first flight of stairs. As he
walked gingerly through the halls, when he was just outside of
apartment 209, he thought he heard muffled giggling. He realized it
was the only sound he'd heard since entering the structure.
Adopting a professional demeanor, he knocked.



No one answered.



He knocked again and followed with: ``Police! Open up!''



He thought he could faintly make out the sounds of a children's
program, probably coming from a television. The giggling subsided,
replaced with whispered commands. Something ponderous within the
apartment dragged---or was dragged---across the
floor.



Then, silence.



Bavarious was about to knock again when, suddenly, the door opened,
and a little girl---no more than six or seven, answered.



``Hello, Officer!'' she giggled. Bavarious surveyed her quizzically,
noted the poorly bandaged laceration above her eye, then looked
past her into the depths of the apartment's foyer. He thought he
glimpsed something twist subtly in the shadows. He blinked.



``Uh, good evening, Miss. Are your parents home?''



``I don't h---I mean, no, officer, they're not. My mama died
when I was little, and my daddy, he's{\ldots}um{\ldots}he's---''



She seemed to cock her head, as though hearing an inaudible
voice.



``---he's out buying more beer.'' She suppressed a laugh.



``Is he?'' mused Bavarious. ``Miss, what happened to your
forehead?''



Suddenly, the girl's demeanor changed, plunging from sunny to
downright icy.



``Officer, it's past my bedtime. I need to---you need to
leave.''



``Mi---''



``{\em Right} now.''



Though he couldn't explain it, Bavarious sensed an impossible
authority in her voice. An authority that hadn't been there moments
ago. He glanced at her again and thought for a moment her eyes were
glowing, yellow, bending his will to hers. He shook his head and
looked back into the apartment---anything to get away from that
jaundiced gaze! That's when he noticed what appeared to be a
rust-colored trail leading from an overturned Igloo cooler toward
another room in the apartment.



``I'm afraid I can't do that, Miss,'' he intoned as he brushed past
her, intently avoiding her piercing eyes.



Curiously, she said nothing.



His Beretta held out before him, a talisman against the darkness,
he followed the trail into a bathroom. There, in the tub and amid
the stink of beer and feces, lay the body of what Bavarious assumed
was the little girl's father. The man's belt was still clutched in
his hand.



The man's hand was resting on the countertop, a good seven or eight
feet away from the rest of him.



Unable to control his emotions, Bavarious puked all over the fetid
corpse, displacing several flies. As the chunks rolled slowly down
the disemboweled form, giggling erupted from behind him. He
jumped.



``I told you you needed to leave,'' breathed the little girl, whose
eyes had ceased glowing and now positively {\em surged} with
wicked yellow light. He noticed for the first time that her hands
were the color of rust.



Bewitched, Bavarious could do nothing as her arms shimmered and
became a writhing mass of tentacles. He told his brain to send an
impulse to his trigger finger, but it wouldn't obey him. It had a
new master now.



{\em Good night, Officer Bavarious.} projected the little
gi---



{\em Her name is Kaitilin. How do I know that? How d---}



{\em I---yes, good night, Kaitilin. I'll{\ldots}be{\ldots}going{\ldots}now.
If{\ldots}if that's all right{\ldots}}



* * *



Luke Bavarious awoke outside of an apartment building somewhere
near Forty-second Street and Dyer Avenue, sprawled across the hood
of his car. The sun had just begun to rise above the tangled mass
of skyscrapers all around him. His mouth tasted like vinegar, and
he smelled like a slaughterhouse.



``What am I doing here,'' he wondered aloud.



The sun thrust a glinting beam of radiance through a break in the
buildings; it fell with purpose on a second-story window of the
apartments in front him. Following its path, he thought for a
moment he saw two points of yellow light blink, then vanish.



``Weird,'' he muttered. 
 



