\chapauth{A Child's Letter}
\chapter{The Mirror}

Luke Bavarious' eyes rolled around in their sockets, finally allowing
him to focus again on the bathroom mirror. His Beretta still in hand, he
wiped the few remaining flecks of sick from his mouth.

{\em What can't I remember? I don't have any idea what I've,
  what's\ldots uggh!  Too much shitty tequila}, he concluded. Again, he
vomited.

The reflection gazing back at him nodded even as Bavarious nodded.

{\em I can't live like this! I'm a cop, dammit! I'm a cop! I'm a
  copI'macopI'macopI'macop}, he thought, his mind shrieking the mantra,
causing liquid rust to ooze from his flaring nostrils.

The reflection gazing back at him blinked. Bavarious did not.

{\em What the hell?!}

Suddenly, rancid vomit streamed from the Bavarious in the mirror,
splattering the glass and causing the other to recoil. Bavarious
stepped---or stumbled, rather---back, raised his weapon, and aimed for
the reflection's chest.

{\sc Boom!}

Red pain arced across his frame moments after he pulled the
trigger. Shards of silvered glass protruded evilly from his hands and
chest, callously inviting Bavarious' tattered sports coat to greedily
lick away every spent drop of blood.

On the other side of what had been the mirror, the ``reflection'' stood,
grinning lustily at its fallen doppelgänger.

``Who\ldots what\ldots what are you!'' wondered Bavarious aloud.

{\em I am you}, projected the specter as it placed a shaking withered
hand on either side of the mirror's frame and thrust an impossibly long
and spidery leg through the opening.

``The {\em fuck} you are!'' shouted Bavarious, who fired three more
rounds into the advancing creature. As every mushrooming burst of metal
rage ripped into it, Bavarious felt as though {\em he} had been shot.

``What are you {\em doing} to me!'' he roared, or tried to: his voice,
hoarse, weakly reverberated throughout the dismal room. His crimson
lifeforce spread out before him, pooling in a macabre circle.

{\em What am I doing to you? The question, Luke, is what are you doing
  to you.}

{\em I don't know what you're---shit, now {\em I'm} doing it---}

``I don't know what you're talking about!''

{\em I know}, it smiled as it injected itself into Baravious'
reality. {\em I know.}

That's when Bavarious realized the smile wasn't one of joy or elation;
rather, it was one of rueful, inescapable sadness. The kind of smile one
smiles when, having done everything to avoid a foregone conclusion, the
conclusion looms inevitable.

{\em I don't want to die}, whined Bavarious. {\em What do I do?}

``You...die, Luke,'' it whispered.

Gently---lovingly, it stroked Bavarious' cheek with its bony
fingers. With every tortured breath, Bavarious felt his body contort,
stretch out, become more like that of the entity now cradling his
convulsing head.

Maybe it was a trick of the greenish ultraviolet light; maybe it was his
uncontrollable spasms, but Bavarious was almost---no, he was one hundred
percent positive that the monster was somehow {\em condensing},
coalescing: somehow, its thready arms and legs were gaining proportion
even as its previously gaunt features seemed to swell with health.

Through the multifaceted, bloodstained reflection of a shattered
bathroom mirror, the last thing Bavarious ever saw was {\em himself}
reach down and collect his Beretta.

{\em I'm a cop}, he sighed.

``I'm a cop,'' he said aloud, tucking his sidearm within the confines of
his tattered sports coat and walking briskly from the room.
