\chapauth{ack!}
\chapter{The Dock}



This lake seemed ordinary enough. The drive to this lake seemed
also ordinary enough, though the road was windy and tedious. The
unfortunate youngest child of the Bavarius family, Luke, endured
riding in the very back seat of the Buick station wagon. With each
twist on the windy road to the lake, Luke suppressed his twisting
stomachs urge to purge and vomit due to the car sickness his seat
on this ride caused him. ``I hate this drive and I told them
we shouldn't go this year. I hate being the youngest. I
always have to sit back here and get car sick, but that
doesn't matter to anyone, especially my dad who never listens
to me'', Luke thought while feeling the bile raise to his
throat. ``This ride better end soon'' he wished, but the
ride was really just beginning.



Upon reaching the cabin at the lake they drove to, Luke's
family unpacked for a week's vacation during the summer break
from school. Luke ran to catch up to his older siblings who were
faster than him as they each ran to claim their bunks in the cabin.
The ride left him more nauseas than ever and he had no hope of
getting a bunk in the main room. As usual, his bunk would be the
one in the back room at the back of the house. Once again he found
himself at the back of it all in the most uncomfortable place and
anything he said about it would go unnoticed and uncared about.
Needing fresh air to clear his head and most importantly, his
churning stomach of suppressed oral violence which was nearing
critical mass, Luke ventured outside, alone. He knew this trip
would be bad and the start was proving it.



Behind the cabin was a trail. Dreary and barren, this trail had
seen no visitors all year. Vines grew across its misshapen
cobblestones. He tried to skip as children do, but the uneven
stones reached up to trip him. Even the ground he walked on tried
to make his life miserable. Luke pressed on.



At the end of the trail, which led from the house to the lake, a
dock that rivaled an elderly woman's wrinkled and cracked
skin wound its way above the lake's depths. No one knew the
origins of the dock, but it had endured every frigid winter and
every scorching summer since its birth. Neglected and uncared
without a repairman's hands to repair it, the dock barely
held together with each board twisting and splintering.



Creeping like a silent cat on the hunt for its prey, Luke crept
onto the dock. Engulfed in the mist of the lake which surrounded
him like a funeral curtain, he made his way to the end where he sat
on the end of the dock and put his feet into the water. The
coolness felt good to him and made his stomach settle and no more
churn like a vile popcorn machine ready to spew forth a vomit of
undigested cheese and crackers that was his only meal for the
day.



Peering into the waters, Luke was surprised at the stillness and
the clearness of the lake. As the cruel world spun around him, he
could see through the very depths to the bottom which shimmered. He
could see his reflection coming in and out of shape. As he stared,
it seems time froze and the world stopped turning. His face became
without a shape and disappeared entirely. The faces of his siblings
floated by instead, pushing him out of the way. Then after that,
the faces of his parents, who never listened or cared for their
youngest child mocked him in his place.



Feeling colder than ever before, Luke felt a fiery fury explode in
his blood boiling heart. His mind spun deeper and darker than the
largest tornados in Kansas. His eyes bulged, each vain throbbing
and pumping their purple liquid to increase his vision. The real
picture began to form. This lake was a mirror, a portal, a crystal
ball to show his life, show his future.



The water's blue gave way to rust as each body flowed by
while blood drained from within. ``This is my life'',
Luke realized, ``this is my work. Whoever won't listen,
whoever won't get out of the way, this is where I must put
them, this is where they will pay''.



Snapping awake, Luke glared at his aged reflection in the window
lighted by the moonlight in the night sky. His thoughts settled as
his memory cleared and the pain rose burning and bright like the
devouring flares of the Sun.

``No!! This was not me!!``



''You did this, Horace Manslasher. You took my family that day while
I was at the dock and no one would join me. Now I'm coming
for you.'' 
 



