\chapter{Wicked Workout}
\by{Akbar}



Luke Bavarious was on the prowl. Earlier that night, the detective
had received notice from the chief that some unidentified killer
was stalking the Upper East Side. Already five had been found dead.
Each was murdered in the same gruesome fashion: arms hyperextended,
hair ripped out to the follicle, legs bowed at the knees as if the
ligaments were carefully torn, and finally, a smile carved across
the face wide enough to completely cover the corpse in its own
liquid lifeforce.



{\em What kind of goddamn maniac are we dealing with here? The
Joker?} Bavarious thinks to himself as he carefully primes his
trusty Baretta, referencing the recent Batman film. He tenderly
fingers the safety. He steps out of his Ford Pinto into the cool
New York night.



He stalks the sidewalks seeing nothing but the steam rising out of
the sewers onto the dim streets. His eyes are optic daggers,
piercing into the darkness. His muscles are taut, ready to unleash
the leaden payload of his sidearm into villainous flesh. He sees
the telltale trail of fresh blood on the pavement.



{\em It's on.}



As he follows the sanguine highway into the alley behind a 24-Hour
Fitness, he begins to hear a slow pounding in the night air. Slowly
but surely, it grows louder and louder as he approaches the
wellspring of the molten vein-magma. Before, it was just a
thumping. Now, however, it is more recognizable: a beat. A melody.
A hot sensation rushes through Bavarious' body.



``Dance music!'' he ejaculates softly as he creeps to the
source: a partially-open doorway flooding the shadowy alleyway with
light. He nudges the door with his foot and peers into the hell
below. Bodies! Dozens of them. Strung up by the arms on chains
attached to huge meathooks, their feet barely reaching the ground.
The bodies were jerked hardily up and down to the cadence of the
music. Their arms strained against the tension. Their legs slapped
against the concrete floor over and over, as if horrifically
tapping along to the beat. The battered limbs heaved droplets of
blood and pulverized bone into the air. In front of them all was a
horrid taskmaster.



``Up and kick and down and step and up and kick
and{\ldots} {\bf remember to smile!}''



Bavarious could only see the back of the man, but he was already
repulsed to the point of vomiting. Dressed only in a red jersey,
dolphin shorts, and running shoes, the short man runs to and fro in
front of his victims, only a handful of which that were still
conscious or alive. The tormentor's bouffant hair bounces as
he taunts the wounded. The killer then takes out a wicked curve
blade out of his shorts and carves open a pleading woman's
face, laughing as he watches her throw up her fluid
existence.



{\em What the hell is this?} Bavarious thinks as he makes sure
that his Baretta is locked and loaded, regurgitated chicken dinner
still spewing out of his mouth. Jumping up, he yells out:



``{\bf Freeze! This is detective Bavarious of the NYPD! I have a
Baretta locked onto your head and I will fire if you do not
comply}!''



The demon in front of him does not. Instead, he leaps otherwordly
to the right, launching his disgusting body as approximately
fifty-five miles per hour. Bavarious reacts with equal speed,
letting loose with half a score of death slugs. All of them hit as
the swiss-cheesed body hits the floor with a thud. Bavarious races
up to confirm his kill, wiping away the now-crusty sick on his
chin.



Rather than a cadaver, however, he sees only the man, still facing
away from him. Still on his feet. Still alive. Filled with dread,
Bavarious unloads another barrage of rounds from his only true
friend, the Baretta he keeps on his hip. The bullets zip through
the gym teacher from hell as if nothing was there. In their wake,
they leave gaping holes that eject a clear liquid. The vitreous
material tumbles out of the entry wounds like a rain. A shower of
translucent gymnasts somersaulting through the air. The gashes
slowly close and leave no trace of their former existence, even in
the man's clothing.



``{\bf What the hell are you}?!'' the detective screams as he
discharges the rest of his lethal cargo, again to no avail. The man
finally slowly begins to turn around, revealing his bloated
face.



``Richard{\ldots}Simmons{\ldots}?'' Bavarious murmurs
into the air, putrid with aerosolized human body parts.



``No,'' the man says as he fully presents himself, and
then rips off his face revealing another underneath. It is an oddly
familiar visage. ``I'm you.''



Both Luke Bavariouses vomit. Tears.


 



