\chapauth{Anal Surgery}
\chapter[Satanic Red]{Satanic Red: The Third to Last Case of Detective Luke Bavarious}




I polished my Baretta with a rust-colored rag. I own both the gun
and the rag because I am a private detective. People come to me to
solve problems. Problems given to them by others with every sort of
type. I am a problem solver for them, the people to whom problems
were given. Today (9am on a Monday) was no different than last
Monday, until she walked in.



Anastasia Rexenstein. She poured into my office like a sexual
cocktail, her dress the color of rusty bulging neck-muscles. Her
eyes peered into your soul like a peering soul-seeing sage. Her
smile twisted like a grapevine as she threw a stack of cash in
front of me. ``I want you to find my daughter,
Bella-Monica'' she intoned. My eyes grew wider than
dictionaries as I looked at the financial stuff in front of
me.



``Okay'' I murmured.



Bella-Monica Rexenstein was last seen in the company of noted town
drunk, Firth Rockwell, at his sea-side cabin near the sea. Speeding
towards the location at 56 miles an hour, I began to hear the
giggle of destiny around me. Night spread across the sky like a
grape-juice stain, the color of darkness, and other dark things.
Rockwell was probably up to no good, so I triple-checked my
Baretta, which was given to me when I started my detective
business. It was loaded. So was I. With alcohol. The sea-side cabin
approached like a sick cat. ``Let's do this'' I said to
no one in particular.



I parked my vehicle and surreptitiously slunk towards the windows.
A light was on, red, the color the Devil lists as his favorite. My
eyes narrowed --- I hate the Devil. There was no sign of
Bella-Monica from the first window, so I approached the second
window as stealthified as I had the first. I still didn't see her,
so I proceeded to the west side of cabin and looked in that window.
I didn't see her there either, so I went to the south side to look
in that window. Nothing, just like what I thought came after death,
because I am an atheist detective, because of my experiences, which
are horrid. But as I came to the east side, I saw movement.



Inside, Firth Rockwell was wearing apparel, apparel which fluttered
wavily in the breeze of a fan. He was sharpening a knife, and
humming the old Irish folk-tune ``I Murder Down a Path''.
Inadvertently, I hummed along, as it brought back memories of my
drunken father, who would hum it after four Bud Lights. I felt
steam rising in me, which I wanted to blow off, in the form of
shooting Rockwell. But before I could Rockwell left the room.



Sneaking in through the backdoor, I heard footsteps stepping down
the steps to the basement. Furtively, I snuck down the same steps,
hoping to see something. But when I arrived in the underground
chamber, what I saw was a sight which I didn't want to see.



Bella-Monica was tied to a chair, with Firth Rockwell placing a
knife to her throat. I yelled at him ``Stop right there!
Villain!''. But he just smiled at me. And then he put on a
wig, and I realized the horrid truth. I vomited a rusty stream from
my lips, which included burning bile erupting from my nose. For
with the wig on, Firth Rockwell was Anastasia Rexenstein.



But then, she pulled the a wig off of Bella-Monica, and I vomited
again. For Bella-Monica was actually me! Bella-Monica screamed
harshly ``{\bf listen to me}---'' but I fired my gun at both of them,
exploding their faces in a shower of blood, brain matter, skull
bits, and gristle. I fled upstairs and vomited in the sink. For I
realized, I had just killed my twin brother. I was the last
Bavarious now. All I could do was sob. 

 






