\chapauth{and Into}
\chapter{The Truly Horrid Reflection}





The shadows trickled through the alley like the breath of an aging,
slightly obese hard-boiled cop in the middle of extending an
over-wrought metaphor. But even in the face of a dark alley opening
up like the maw of blackest Death itself, I wasn't afraid--I
have a Beretta, and I have the name Bavarious. Luke Bavarious,
NYPD.



My partner Rogue was busy working a tough murder case. Rogue was
chosen as part of a task force to catch the Bronx Butcher, a serial
killer with a hobby of hunting and taunting his would-be pursuers.
Some men have all the luck. I've been put on the toughest
beat of all: noise complaints.



There are noises out there--a car door slammed, an alarm in the
night, a clown horn comically honked too loud--noises that wait in
the shadows, only to surprise and rape the sweet ears of the
innocent citizens of New York. But not if Bavarious has anything to
say about it. Luke Bavarious.



The alley off 42nd street is home to many things. And apparently
some of them make noise, because I've been called to
investigate. Staying just inside the cold cloak of the shadows I
edge down the alley. I saw a figure perched on a dumpster, his back
to me. He was sobbing and crying.



It's for nights like this I joined the force.



``New York Ordinances state that excessive noise is punishable
by fines not exceeding one hundred dollars for the first
offense,'' I said, smirking. ``But I bet that
you're a repeat offender, huh? You should have picked just
one: sobbing OR crying. But you've just gotta be a loud son
of a bitch and do both, don't ya? Well, I guess you just
weren't planning on the icy justice of Bavarious--Luke
Bavarious--were you? Now turn around.''



I raised my loaded Beretta, cocked it, and pointed it directly at
the figure's back, as per the NYPD protocols for how to
handle the grief-stricken.



``I said, `Turn around,''' I repeated, more
loudly and even more smirkingly. But still at a reasonable decibel
level, so as not to disturb the peace. The peace I've been
hired to protect.



``Excuse me, sir,'' the crying figure said between,
frankly, unnecessarily loud sobs. ``But you don't want
me to turn around{\ldots}.''



``Sure I do. I have a loaded, sleek, cocked Beretta pointed at
your back, so you better turn around,'' I said. I went ahead
and cocked the Beretta again, just for the effect, and because I
goddamn love me a good Beretta-cocking.



``Okay, you asked for it,'' the thing mumbled,
uncharacteristically low in volume.



From the gutter above, water-trickles breezed through the alley as
it turned toward me, and began slowly inching into the light.



First its combat boots emerged from the darkness. Then its knee.
Then its leg. Then its pelvis and hips. Then its chest actually
seemed to emerge slightly before its stomach, oddly, but its
shoulders came out next, just as one would anatomically expect.
Then its neck (it is kind of limboing now, for some reason).
Finally, its head came into clarity in the dim light.



If you could call it a head. His face was horrid. There was a
superfluity of purple scars. There was blood trickling from an
empty eye socket and his sole ear was ugly. There was no nose.
There were no lips. There were bruises and lumps all over the
cheeks. There was only thin stubble for eyebrows. Although there
was a well groomed and handsome mustache, this could not make up
for the fact that there were deep gashes and uneven scar tissue
across the forehead, the chin, the mandible{\ldots}



I really could go on, but the point is, he is an ugly motherfucker,
like burn-ward ugly, and the still-sobbing thing stared at me for
quite some time while I noted, like an obsessive cartographer,
every curve and contour of its face. In {\em excruciating} detail.
The thing's neck was a bit small in circumcrence compared to
its body, too, by the way. About 17% too small.



My exhaustive cataloguing of the ugly bastard complete, I finally
took a step back, in narratively delayed astonishment. I had to
grit my teeth to keep the vomit down. Damn bourbon and peyote
cocktails.



He took three more steps forward. ``I told ya,'' it
said.



If there's one thing Luke Bavarious hates more than loudness,
it is people or things that rub it in your face when they are
right. I shot the sad, monstrous I-told-ya-so in the jaw a few
times, adding more holes to the disfigured jerk. The bullets hit
the face terribly powerful. The gunshots rang out, more audible
than I would have preferred--but it is a necessary evil. Lifeless,
the beastly thing slunk anticlimactically to the asphalt.



But at his side some object fell--what is this--Strunk and
White's {\em Elements of Style}? Its pages unfurl, revealing
a check, signed ``Luke Bavarious, NYPD.''



I now recognize at my feet the broken body of the copy editor I had
hired to read over a draft of my memoir, the man who had
disappeared after receiving my papers and my first payment, the man
I thought had conned me and run off. I see him and what I have done
to him, what every mixed metaphor, switched tense, and redundant
adjective had driven him to become, what it drove him to do to
himself.



I tasted my tears and vomit mix into a martini of misery. I saw a
horrid reflection. Suddenly, I was sobbing. And crying. 

 



