\chapauth{Anonymous}
\chapter{In the Mirror}
% The author asked to remain anonymous.  Their explanation:
%
%    My username is really dumb. That's about it.
%
% Weird.  They also released this story into the public domain.


Out of the darkness came Rothard Mavalero. Grunting and thumping,
he was the city undertaker. It was not a job many would like but he
had kept it for fifty years. Some people thought that was unnatural
but they did not know the half of it. And if they knew the whole of
it they would have run in terror. Bodies interested him. He liked
the way they looked. He liked the way they felt. But most of all he
liked the way they tasted.



Today it was Mavalero's favorite kind of body. A floater from the
river. It was still fresh, like a recently caught fish. The coroner
wasn't at work yet. Nobody would know what he was doing. He dragged
the bloated corpse and looked into its eyes. Suddenly, he began to
pry the eyeball from its socket. A sweet ``snap'' sound happened as
the elastic snapped. He licked the slimy eyeball, savoring the
salty taste. Then, as the deceased's other eye seemed to watch him,
he bit into the juicy retina. It tasted chewy and meaty, just like
he had expected.



Mavalero looked down at the body tauntingly. Blood was oozing from
the empty socket. He liked that it was helpless. He stabbed at the
face to make more blood come out, then dipped his finger into the
blood-filled socket and tested the quality of the victim. When he
was done with the little game, he started to pry at the other eye.
This one did not come out so easily. It felt like it was glued into
the socket, and he had to tug and tug. But finally, with the help
of his pocket knife, it came loose. The eye stared Mavalero in the
face. He did not care. Rothard Mavalero was a very bad man. He
downed the second eye with pride, smacking his lips as he smiled in
his conquest.



But as he began to ponder what he would eat next he saw something
in the corner of his eye. He didn't know what it was. His heart
raced like a galloping horse. He turned slowly towards what he had
seen. Then he sighed with relief, because it was just the mirror.
He had seen his own reflection.



{\em {\ldots}or did he?}



He looked at the reflection, but his face looked unfamiliar. He
turned his head, and his mirror self seemed to delay a little bit
before copying him. With a piercing, inhuman scream, Rothard
Mavalero realized what he was seeing. It was not a mirror, but a
window into a room that had been cleverly copied to resemble his
evil laboratory in every respect. The man was not his reflection,
but the young but hardened detective Luke Bavarius in disguise.
Bavarius had seen everything: the body, the eye eating, the
blood.



He felt a nervousness arise in his throat. He struggled to hold his
posture as he waited for his certain death at the hands of the
private eye. Vomitus dribbled out the mouth of Rothard Mavalero.
Then, as he watched, Bavarius reached through the glass and
strangled him alive. 
 



