\chapter[The Surprise]{The Unexpected Shocking Surprise}
\by{antiloquax}





Luke Bavarious didn't know why he was called to an abandoned
church. But he had been called. By the man who had killed his
father. And it was the church where his father was murdered.



As he approached the crumbling iron gates of the church, a pale
white boy with black eyes from out of nowhere tugged at his tan
rain jacket.



``Do not go in there, mister,'' said the young boy.



``Nonsense!'' laughed Luke Bavarious haughtily.



``What is in there will destroy you!'' said the young
boy.



Luke Bavarious pulled out his Colt Python and pointed it at the
boys pale white head that was now sweaty with perspiration and
fear. ``I said nonsense,'' said Luke Bavarious.



But fear and bile clung to Luke's throat as he entered the
church. He plunged through the rusty wooden oak doors and reached
for his gun. Then he remembered he was already holding his gun.
Then he crept along the church.



As he tiptoed quietly through the rotting and crumbling church, he saw
that everything was black except for places that were illuminated by the
pale blue light of the moon. It was a full moon. A full moon just like
the night his father died.



At the altar of the church there was a shadow. Luke Bavarious
cocked his pistol and pointed it at the figure. The figure was tall
and intimidating and terrifying. But Luke Bavarious had seen worse
in his time.



``Stop! Show yourself!'' said Luke Bavarious. But the
shadowy figure did not show itself. It was still a shadow.



Blam. That was the sound of Luke Bavarious' gun as he shot
the shadow and killed it. Even in the moonlight, he could see the
glistening red blood shimmer in the moonlight as it spewed upward
and outward and everywhere else and covered the old and rotting
crucifix with gore and rust colored blood.



Luke Bavarious wanted to vomit---not because of the head that
had exploded and the brains that were on his clothes, but because
he had finally killed the man who had killed his father. The man
who had killed his father had never been caught.



Until that night.



But suddenly the echoing sound of the gunshot was interrupted by
clapping. Clapping hands. Clapping hands of the man who had really
killed Luke Bavarious' father. Luke Bavarius had shot the
wrong man.



``Well done,'' said a voice that belonged to the rough
clapping hands. ``You have passed the test, Luke Bavarious. I
have been waiting for you.''



As Luke Bavarious began to feel the enormity of what he had just
done, the walls begin to spin. Madness and insanity tried to clasp
their hands on Luke's soul and he fell to his knees and
vomited sickly sweet bile and whiskey. His eyes blurred with rage
and tears. And the tears of rage too. And he didn't know what
he could do.



``Luke Bavarious, I killed your father!'' said a mocking
voice.



Blam.



This was not Luke Bavarious' gun. It was the gun of the man
he had just killed.



``What!?'' screamed the voice in the dark.



The man Luke Bavarious thought he had killed was still alive and
had been waiting to shoot the third man who was the man in the
dark.



``No!'' cried the voice in the dark. Luke could see now
and saw that it was the body of his old friend from school who had
grown up with him. Now he was dead. The man who had killed his
father was dead. And so was the other man, who had succumbed to his
injuries.



``Well,'' said Luke Bavarius to no one in particular,
``I should go home.''



As he left, Luke Bavarious again met the pale white boy. But now
the pale white boy was covered in urine and feces because he was
terrified. But what was this? He was also smiling. Smiling the
smiling smile of a child who had lost a battle but won a different
battle.



``Such nonsense you little children believe,'' laughed
Luke Bavarious mockingly.



And Luke left the church forever. But as he left he could feel
someone watching him. It was the eyes of a third man. The man who
had really killed his father. 
 



