\chapter{The Mosquito of Death}
\by{Assless Chaps}



Luke Bavarious stumbled slowly through the New York City alley,
gently swatting the mosquitoes away from his skin with the butt of
his beretta. It was a hot and humid night, and the blood-suckers
were relentless in their pursuit of delicious, sticky human blood.
His delicious blood was made even more delicious after drinking
four Coors in a nearby bar. The mosquitoes knew it was delicious
and that Bavarious was too drunk to defend himself properly. Or so
they thought.



As Bavarious continued to wade through the refuse and urine-soaked
mattresses strewn about the alleyway, the mosquitoes became
ravenous. They swarmed him in droves, and he began frantically
waving his trusty beretta around, squishing the lowly bugs into a
mess of guts and recently-consumed human blood.



Suddenly Bavarious vomited. The alcohol had finally gotten to him,
and he spewed out chunks of peanuts and pretzels, mixed with beer.
He puked so hard he began puking blood out of his mouth. The blood
and vomit cocktail splattered to the ground, forming a vile and
horrid river of bodily fluids. If only he had listened to his young
son, Timmy, and stayed home that night, instead of going out and
drinking Coors, none of this would have happened.



The mosquitoes began to fly away from Bavarious. He thought in his
drunken mind that they were giving up, and that he would be able to
continue on his walk home, while the insects pursued more
easily-caught prey. Bavarious was wrong. Dead wrong.



Bavarious tripped over a rotting pile of dog feces, and landed
face-first onto the asphalt. As he raised his head, blood spurted
from his broken nose in every direction. Bavarious used all his
manly strength to pull himself up, and when he looked up, he saw
all the mosquitoes joining together, like a giant mosquito army, in
a frenzy due to the delectable scent of his flowing blood. They
grew in number, and eventually a million mosquitoes joined forces
and swarmed together. They began to morph into one hideous
creature. One giant mosquito! The most humongous mosquito ever
recorded in the history of mankind. A gargantuan travesty of a
beast.



Not deterred by this horrendous creature, Bavarious screamed at the
top of his lungs, ``{\bf Evil-doer! Villain! You do not frighten
me!}'' As he screamed, flecks of spittle mixed with the
still-running blood from his broken nose, only attracting the giant
mosquito more.



The giant mosquito, the size of Bavarious at least, stood up on its
back two legs like a human, to do battle with Bavarious. Its long,
pointed proboscis inched closer to him, yearning for the sweet
taste of human blood. Luke Bavarious unholstered his beretta and
let loose a torrent of bullets that merely ricocheted off the giant
mosquito's hard insect body. {\em This is no ordinary
mosquito}, Bavarious thought to himself.



The massive insect lunged forward and sunk its sword-like
blood-sucking mouth-nose into Bavarious' neck. Bavarious
screamed in agony as blood flowed from his wound like a red rapid.
The pain caused him to lose control of all bodily functions. He
writhed in agony as the pain caused him to puke up the remnants of
his pretzels and peanuts, mixed with beer and the bile left over in
his stomach. He felt particularly uncomfortable as his bladder and
bowels emptied into the camouflage fatigues he wore. His apparel
was filthy. He was reduced to a slithering, screaming shell of a
man, covered in excrement, urine and vomit.



The mosquitobeast had had enough. It pulled its sucker from
Bavarious' neck with a wet, slimy burp. Bavarious watched in
pain, as the mosquito slowly turned and began to walk away, unable
to fly because it was so filled up with his beer-blood.



Suddenly, a white light beamed down on Bavarious. He squinted from
the blinding light, and could vaguely see the shadow of a man in
the light, far, far away. As the shadow-man moved closer, Bavarious
felt that he looked familiar.



``Grand-nd-pa?!'' he said.



``Yes. It is me, Luke Bavarious. Your grandfather: Brock
Bavarious. I am here to help.''



Soundlessly, Grandpa Brock showed Bavarious how to slay the beast.
And as quickly as he appeared, he was gone.



Bavarious mustered up the last of his strength and stood up. He
slowly stalked the giant mosquito and lunged forward, clinging to
the creature's back, like a child riding piggy-back on the
back of a man. As the mosquito let out an eardrum-bursting roar,
Bavarious grabbed its giant proboscis and yanked it hard. The
proboscis broke off and the creature's power was drained. Its
only way of eating was destroyed. It crumpled to the ground,
writhing in a puddle of its own blood mixed with the blood of all
of the victims of the millions of mosquitoes that made up this
disgusting creature. After a few seconds of painful screaming, the
creature died.



Bavarious didn't want to take any chances, so he raised the
broken-off proboscis and stabbed the mosquito right through its
insect heart.



``You suck,'' he said, as he hobbled away, ready to get
home and get some sleep.


