\chapter{The Earache}
\by{bagrada}



The night was dark and muggy, the heat weighing down on me like a
heavy winter jacket in the spring. The ringing in my dull aching
ear was the only sound. I stuck in my pinky and wiggled it, then
frowned at the sticky piss-yellow wax left on my finger. Not for
the first time, I thought about seeing a doctor. I shook my head.
My ear has never been right since that day in the pond, so long
ago. Time enough for doctors in the morning. Tonight, I had a girl
to save.



``You have to help our friend, Mr. Bavarious!'' the kids
had said. ``She's been kidnapped by some freaky
cult!'' The cops didn't believe them. Neither did their
parents. But I did. I knew the dangers of not listening to kids. My
sister{\ldots} if I'd listened to her she'd still be
alive today. I'd told her she was just a kid too, that I
didn't have to listen to her, that I could swim where ever I
want. I almost died that day. Instead she died, died much too
young, died saving me. I loaded my beretta and nodded to them.
``Don't worry; I'll bring your sis{\ldots} I mean
your friend back to you.'' The boy shook his head sadly and
looked at me as I left.



As I approached the abandoned warehouse where they said their
friend was taken, I glanced to the stars and felt a shiver run down
my spine as they seemed to blink in the night sky. A coppery rusty
scent floated on the stale breeze. I was close. I walked up to the
old wooden door, with my finger on the trigger, and kicked it open.
{\bf Light}. Bright searing light. Red rusty light. Purple smoky light.
Spirally yellow light. Grey and black and white colorless light. I
didn't hear the broken door clatter to the ground in front of
me or the vomit that suddenly projected from my throat, just the
constant droning ringing in my ear, louder now.



The lights faded as I tried to blink through the afterimages to
look around the room. All around an old stone altar were the
cultists, theirs eyes bleeding, their robes coated in glistening
puke, their mouths slack in death. On the altar floated the
girl{\ldots} or parts of her. She was split in two; her eyes still
smoking, her hands still raised to the sky in prayer. The left side
of her mouth opened in a bright smile, while a few feet away the
right side gaped wider as if she were screaming. She was pinned in
the air like a butterfly to an insect spreading board. In between
her two halves, something moved, then the world ended around
me.



The air became thick, muddy and gritty, like I was back beneath the
pond again that awful day. The lights returned{\ldots} rusty red,
black and white, vomit green. The horrible spiraling yellow. The
girl melted away, her long blonde hair splashing to the floor, and
I felt the air shift as something floated towards me. The ringing
in my ears was now the tolling of great bells, driving me to my
knees as my gut heaved and tried in vain to find something else,
anything more, to throw up. I felt something bitingly cold and
scalding hot brush my arm as the colors floated past me, and then
my arm wasn't there anymore. It floated off into the lights
which were now many bright balloons, all painted with crying faces
I could almost recognize. I blinked and the balloons popped
revealing a swarm of fireflies, each with a uniquely colored light.
So beautiful and horrible as they flew by me towards the door,
their lights blinking in a pattern my mind fought not to
understand. The tolling of the bells was now a tinkling song that
made me want to float along with it, if only I could recognize the
tune. The fireflies were floating spiders, then darting fish, then
the drowning faces of my dead sister. I staggered to my feet and
turned towards the door as the colors wafted through and became
dark. I took a few stumbling steps after them but stopped when my
foot kicked something metal and heavy{\ldots} the beretta I'd
dropped. Whispers suddenly, in my ear. My little sister.
``Breathe, Luke.''



I gasped for air, realizing I hadn't taken a breath since
kicking the door, and fought my way to the center of the room,
kicking the bodies of the cultists aside, and then gathering the
messy blonde hair and other unrecognizable bits into a clump in the
crook of my remaining arm. ``It's okay.'' I said.
``I've got you.'' With the smell of rusty blood in
my nose, the taste of bile and vomit in my mouth, the ghost of my
left arm screaming that it's still with me, the afterimages
of the wondrous lights seared into the back of my eyes, and the
constant and steady ringing in my ears keeping me company, I
staggered out into the now starless night. ``Don't worry
sis. I'll get you home.'' 
 



