\chapter{The Horrid Realization}
\by{Baron von Eevl}



I stepped from the glare of traffic. The time had come again. I was
in the police station on 42nd street in New York. My hand shook
slightly with the bic pen I held in my hand. The matte white pen
had leaked in my pocket. Another shirt ruined. I am a desk jockey.
My name is Detective Luke Bavarious. I dislike this work.

People had been complaining about a drunken officer in their
neighborhood on his beat. I was transferred off the streets because
of these disturbances.

I edged into the Sergeant's office. I saw the tall, handsome figure
of the man I once respected sitting in his chair, facing towards
me. He was sighing. I raised my finger and slurred a series of
vulgar insults at the sitting figure.

``Bavarious, you drunken fool.'' The captain bellowed.

``Turn around!'' I shouted.

``Beggin' your pardon, Detective,'' he said, ``I'm already facing you.
If I turn around I would be facing a wall.''

``Sure I do. I'm a better cop than you could ever be, McClenaghan'' I
replied.

``Okay, that didn't even make sense,'' the sarge mumbled as he began
to turn red.

Fabian McClenaghan was my Sergeant. He and I joined the academy
together years ago and quickly became friends. He and I would share
all our secrets together at the shooting range and promised when we
died we'd be buried together there with our trusty barettas, shiny
sleek and deadly.

``Give me your badge, Bavarious.''

I inched forward and began to sweat all over. My ductile muscles
clenched and began to shiver. First my feet, deep in non-uniform
combat boots. Then my legs. Then my chest. Then my head. If you
call it a head. My head was so clouded with liquor I could barely
think. Was that what you called it? A head? It's that thing on top
of your neck. The one with all the holes.

I took a step back in astonishment. I gritted my teeth to keep the
vomit down.

McClenaghan stared at me with unbridled hate and shame. Ashamed of
hate.

``You look like you're going to be sick, Bavarious'' he grumbled,
concerned. ``Do you need me to grab my trashcan for you to throw up
in?''

``Hey buddy!'' I screamed. ``I don't need no trashcan from the likes
of you!'' I then vomited. The horrid cocktail of blood and last
night's spaghetti dinner came up and spilled all over the
Sergeant's floor, looking like some alien had died and it's guts
were spilled all over the floor of the Sergeant's office on the
floor.

``I told ya,'' he said.

I screamed and began to run away from him. He waved his hand high
in the air and screamed after me.

``Bavarious, give me your gun and badge, you drunken fool!'' He
screamed.

``McClenaghaaaaaan!'' I screamed right back at him.

It was too late. I was running through an endless maze of cublicles
each as similar as the last. I ran faster. As I ran, I vomitted a
horrid smelling liquid of putrefaction all over my pen-ruined
shirt. Pen and vomit ruined. And spaghetti sauce. As I ran, others
began to run too, running from the awful weird vomit. The first
person ran faster than the second. The second person ran faster
than the third. The third person was not running very fast because
she was a woman and I'm not comfortable describing her further. The
second person slipped in the vomit and the first person easily
outpaced him. The third person was elsewhere at that point. Maybe
vomiting.

Being drunk, I began to see horribly awful images. A spider. A
person who is also part spider. A butcher's knife. A young boy, to
be respected and listened to, lit from below and looking very much
serious and respected. These were the typical hallucinations I had
when drunk, which causes horrible hallucinations.

My head smashed into the door terribly powerful. Muscles were
strained and torn as my head jerked to the side, smearing the
glass. I fell and landed on the hard linoleum flooring. Dazed I
vomited again and again. I felt the surge pushing back
rhythmically. I ran outside but continued to vomit. Spaghetti
hitting the pavement. Splatter hitting my shirt. Blood showering
me. I felt my own blood from the side of my mouth fall and drip. I
kept vomiting. My stomach was empty. I staggered. I tasted my
dinner and blood mixed into a horrid cocktail. It tasted like
vomit. My badge sparkled on the side of my waistband.
Bavarious.

I picked myself up and stumbled over to a mirror. Suddenly, I was
in my apartment. Suddenly, I was sobbing. 

 



