\chapter[L.B.; V.H.E.]{L.B.; V.H.E. (the extended directors cut, with deleted scenes)}
\by{Barometer}


Luke sat in the dimly lighted corner of an underused and
over-bright bar.

``Almost noon'' he thought to himself ``they should be fast asleep by
now.''

Shifting his considerable bulk, he managed to stand on his one good
leg, supporting himself with a hand on the table while his other
hand reached for his cane; an old waking cane bought form a dealer
in Soho many years past.

``God I've really let myself go since the accident'' he whispered to
no-one ``maybe I'll look into that Pilates shit{\ldots}or
something.''

He rolled his one good eye towards the pretty barmaid, a buxom
blonde who was eyeing him suspiciously. His meaty paw fished out a
couple of bills and dropped them unceremoniously onto the wet
tabletop, next to his three empty glasses.

``Hurr'' he spewed ``That'll teach her not to return my
flirtations{\ldots}uppity bitch.'' He gave her a smile that would wither
a rose, showing his rotten teeth that were green and yellow as
vomit.

Lurching forward like some hellish zombie, he headed for the
door.

Once outside, on the street, he shielded his eyes from the bright
sunshine ``Jesus I hate Kansas!'' he shouted, and a couple of elderly
people strolling by averted their gaze. He snarled at them, like
some wild animal that had been too long held in a cage and was only
now getting it's first taste of sweet freedom. ``fuckers'' he
mumbled.

Luke was an old man now, even though he was only forty. He had seen
so much; things that would make your skin crawl right off your
body. Things that could curdle milk by just being discussed. Luke
was a Vampire hunter, in the classical sense. Luke was very, very
good at his job.Checking the swordcane with a swift motion, and
satisfying himself that it was still good and sharp and made of the
finest ebony, he trundled down the street towards the old Biddick
Mansion looking like some undead pimp, rolling towards his best
girl.

``Those goddamn Vampires'll be vomiting blood from their throats,
ere this day is finished'' he vowed to heaven above ``Or my name's
not; Luke Bavarious, Vampire Hunter Extraordinaire!''

A boy of about 12 happened to be standing nearby, and when he heard
this his eyes sparkled with a devilish glee.

``Hey, mister{\ldots}you goin' up to the ol Biddick place?''

``So what if I am, you little shit?'' Luke gnashed his rotten
teeth

``Better not, I hear them folks is crazy{\ldots}and they got some kinda
dawg that wanders the grounds during the daytime. Never see 'em
lessen it's nighttime.''

Bavarious gave the tyke a once-over, and answered ``Izzat
right{\ldots}well, guess it's a good thing I have this Beretta then,
huh?'' as he spoke, Luke eased his brown courdory overcoat aside,
showing off a holstered Beretta 9mm, worn gunslinger style, with the
butt facing forward. ``I imagine {\em this} will take care of that old
{\em dawg}'' he imitated the boys thick accent. He swooned a bit form
the heat, and sweating copiusly, continued his roll down the street.
Following at a short distance, the boy followed, shoeless and dressed
only in blue coveralls, worn form use and neglect. His bare feet were
covered in sores and wounds garnered from his time playing in the dirt
and rocks surrounding the little no-name town they were in. His eyes
were wide, and full of anticipation. He had never before seen a man this
grossly overweight, and was intrigued.

After a few minutes, Luke felt as if the eyes of Satan himself were
upon him, so he swung around fiercely, whipping out his sidearm
``{\bf who dat}?!'' he cried his good eye searching and looking crazily
around until it alighted on the small figure in front of him.

The boy jumped from fright, and for a moment he felt as if his his
heart was going to burst from his chest, spewing crimson blood
across the dusty sidewalk ``{\bf it's just me mister}'' he shouted,
thinking the geezer must be hard of hearing if he had not noticed
him following by then ``{\bf I wanna help, mister!}''

``{\bf Help?}'' Shouted Luke, unconsciously imitating the boy and
shouting back;``{\bf I don't}---'' he suddenly realised he was shouting,
and dropped his voice seeing that another couple across the street were
watching, intently`` I Don't need your help, kid{\ldots}now, buzz
off{\ldots}get lost{\ldots}scram. Comprende?''

The nameless waif wondered what the hell ``Comprende'' meant, but the
rest of the message was clear enough. ``Fine, you ol' bastard{\ldots}go
on, get yourself killed, see if I care!'' and with that, he ran
off.

It took Luke another ten minutes of lurching to gain the front gate of
the fenced in yard surrounding the mansion. ``Hmmmm, I don't {\em see}
any big dog'' He continued to roll his single, jaundiced eye back and
forth, looking in vain for any sign of a guard dog. Satisfied that there
was no sign of such a beast, he opened the gate and hobbled up the front
path to the stairs leading onto the porch. He unintentionally
farted. Once in front of the massive oak double-doors, he swung his eye
around for another look. Again, there was nothing to challenge him, and
as he considered knocking, the doors parted of their own accord,
affording him access to the darkened foyer of the seemingly uninhabited
mansion.

``{\em Creeeeeeeeeak}'' went the doors, and when they were fully apart,
L.B. (As his one and only friend called him) took stock of the room
revealed before his eye.

It was a small room, comfortable and sparsly decorated. There were
a couple cameos on the wall, and a small desk, covered in what
looked to be unopened mail. L.B. knew there were Vampires in this
place, he could smell the stink of hell itself in this place and he
figured that like all of their ilk, they would be holed up in the
basement, sleeping their undead sleep in coffins filled with the
dirt of their original resting places.

He shifted his weight ``God-{\em damn} it I gotta lose some poundage''
he cursed. After a cursory search of the downstairs, he found what
appeared to be a locked door to the basement, and he put his left ear up
to it and listened.

``Hmmmmm, sounds like a heart beating{\ldots}that's odd'' He tried the
door, but as he had surmised; it was locked!

Suddenly the door came crashing in on him, and the portal vomited
forth a huge, black dog{\ldots}some kind of mutant Great Dane he thought
fleetingly, as it quickly bit into his neck, tearing out his
windpipe and causing Luke to make the most horrid sounds even he,
in his long career of monster slaying, had ever heard.

Somehow, his fat right hand had reacted instinctively and the
Beretta was alive in his hand! Bullets tore through the monstrous
dogs body, knocking it backwards and slamming it against the wall.
As it writhed in its death throes, Luke attempted to staunch his
wound, but he knew it was too late his plump hands could find no
purchase, and the wound was surely a mortal one. His vision was
blurring to the point that he could barely make out the small shape
coming up from the basement.

``You shoulda listened to me, mister'' Said the boy in a quiet tone
``I woulda showed you the cellar door, and then ol Blackwood there
woulda never bit ya!''

``Gurgle..cough, spit'' was all Luke could get out, and as the life
ebbed from him, laying on that dirty linoleum kitchen floor, all he
could think was; ``Shit, why didn't I listen to that kid?'' The boy
crouched down in front of him, and just as his eye glazed over he
caught sight of a family portrait on the wall{\ldots}some cheesy mall
photobooth picture, enlarged, of the boy{\ldots}with the name ``Ben'' in
faux spraypaint letters and some other bling he couldn't quite make
out, before the Angel of Death took him.

``Ma and Pa are gonna be {\em so pissed} that you killed
Blackwood{\ldots}'' said the boy to the corpse, glancing over to the
lifeless dog ``Maybe ma will raise ya, so they can punish ya!'' again
his eyes filled with an evil gleam.

With that, he gave a shrill laugh, and ran as fast as he could back
down the stairs, anticipation bubbling forth like boiling coffee. 

 



