\chapauth{Batmanuel}
\chapter{The Stranger. Bavarious.}



{\bf For mature readers only}



``Whiskey.'' The stranger sat hunched over in the dark
corner of the bar. I would have missed him if it weren't for
my curiosity and his harsh cigarette tinged voice. I sat the glass
down, opened the bottle and poured. ``Leave the
bottle.''



``What's troubling you, Mack?'' I asked as I pulled
my hand away from the bottle. He didn't look up. I tended to
pry, but I got the feeling that this guy wasn't someone to
fuck with.



Minutes passed and I forgot all about this stranger. Smoke hung
aimlessly in the air as someone busted out a trick shot in the
billiards game on the other side of the dark tavern. Maybe a fight
would break out. The regulars hate it when new people come in with
that slick shit. Almost right on cue, Jimmy Dean, a hulk of a man,
grabbed the trick shot artist around the neck and slammed his face
on to the table. This collision proved hard enough to send the
balls rolling in every direction. In practically the same breath,
the guy was thrown out onto the pavement. I let this shit happen.
No cops. Justice prevails and everything returns to a despairing
level of normality.



I turn my attention back to the stranger only to find him gone and
a fifty dollar gold coin on the bar. Under the coin was a business
card with one word on it: Bavarious. How I missed a man dressed in
all black, wearing a knee length black leather trench coat duster,
walk right out the door is beyond me. He had to have crossed right
in front of my field of vision, but I must have been too distracted
by the fight to notice him leave. Whatever.



I couldn't sleep that night. A feeling of uneasiness stuck
with me after my brief encounter with the stranger. He just wanted
a drink, right, lots of people do that, nothing weird about them.
All I could think of was his name. Bavarious. What did it
mean?



The next day, I enter the shit hole and take over for the night. I
expect much of the same. The regulars were already there and most
likely drunk. The stale air welcomed me as I pushed through the
wooden doors of the tavern. I felt a chill rush down my spine as I
looked towards the end of the bar. I didn't even make it
behind the bar before I heard a familiar voice that would remind me
of exactly why I could not sleep.



``Whiskey.'' Fuck. The stranger sat in the exact same
spot. `Same shit, different night' I thought to myself.
As if he didn't remember the minute details from the night
before, his grizzled voice said, ``Leave the
bottle.''



``So, are you drowning your sorrows away?'' I tended to
pry. He didn't look up, so I turned back to cleaning a yellow
beer stained mug. My mind wandered and I began to picture a lost
love. For some reason, I came to the conclusion that he fit the
motif of a heartbroken pathetic being taking everything he did
wrong out on himself. After this, he's probably going to the
nearest bridge and tease ending it all by dangling one foot over
the railing. Pathetic bitches never actually jump since
they're always back the next day drinking the same drink. If
not the bridge, he'll probably stare down the cold steel
barrel of a Beretta. Visions of my ideal womanly being played in my
head and I wanted to join him in downing the fuel of the unwanted.
The poor bastard losing the dark haired, tan skinned, beauty
running through a meadow on a sunny day, must be hell. I snapped
back to reality, shook my head and spun around towards this guy
with another bottle of whiskey. Almost exactly like the night
before, I fail to see him leave and I'm left to wonder why he
leaves the coin. One fucking tip.



``Hey Marv, did you see that cowboy looking son of a bitch
leave?'' Marv, the rat-faced bug-eyed shrew of a motherfucker,
shook his head with a look of confusion. I didn't look too
much into it, as the smoke hovering in the air tends to get to my
head. Unlike the night before, I was able to thwart any thoughts on
the guy. I mean, I was never the obsessive little bitch type. I
tended to pry, but that was part of the job title. I had to talk to
these characters while they drank the night away.



These nights always seem to run together. The same rituals repeat
themselves. The same poor saps gather in this shit hole. The same
rain falls outside. Jimmy and his gang exchange the same stories.
The same game of pool is played. The same fight breaks out. The
same song plays on the jukebox in the corner. The same `out
of service' sign hangs on the bathroom door. The same tourist
loses a wheel on the same pothole and drags his scared wife
who'd much rather stay in the car inside to use our phone.
The same poor fools come and go like fucking clockwork. I
can't complain.



Every night for the past week, the Stranger sat in the same stool
under the same shadow, said the same four words, drank the same
whiskey, left the same goddamn coin and vanished the same way. If
it weren't for the same bad vibes that surrounded him, I
would not have even noticed him.



I still have trouble sleeping at night. It's not that I
don't want to sleep; it's just that I can't. I
stopped trying. Techniques that bobble heads preach up and down to
levels of total effectiveness fail. Pills don't work, lying
in bed passively watching infomercial after infomercial have the
effects of making me wonder what exactly will blend. When I am able
to close my eyes, my mind begins to play a constant slide show of
the worst things imaginable. Decapitations. Bodies buried in
shallow graves. Houses burning. Screams fill my ears and I awake in
a cold sweat. I can't breathe. These problems began the first
night the stranger came into my dive.



I find myself feeling nothing but disdain when I gaze upon my
tattered reflection in the mirror. The unshaven man staring back is
not me. Bloodshot eyes sunken deep into hollow cheeks. I lift my
hand up and it shakes as if my blood created vibrations as it moved
through my protruding veins. The mirror not only shows a vacant
waste of a man, but also serves as a vessel for vengeful shadows
that dance around in the dimness created by the talking heads on
their soapboxes of lies. I look again at my shaking hand to find it
in a tightly clenched fist flying towards the primitive zombie in
the glass imprisonment. The glass shatters into a sea of red.



``Whiskey.'' He's there. Right fucking there. No
one knows where he comes from. No one even bothers to notice this
motherfucker. ``Leave the bottle.''



``You know, you've been coming in here for a while now
and it's the same four fucking words.'' I tended to pry,
but it has gotten to the point where this dude needs a crowbar
upside the head! I wanted answers or just a simple response.
``And man, you don't need to leave a fucking gold coin
lying there. That's too much goddamn money.''



As always, he finished off the bottle and left. As always, a
dirtied gold coin was on the counter. It was right then that I came
up with the worst idea of my life. Worse than moving out to this
fucking desolate place. This dumbass decision is probably my only
regret. Given the circumstances, this was a pretty sound idea and
very simple in execution. I called on Jimmy Dean and his gang to
rough the stranger up a bit. Easy as that. Not to really hurt him,
but to serve as an initiation of sorts.



Jimmy Dean was the type of brute that would fit in prison,
professional wrestling or driving a truck for a repossession
company. The brute, with his shoulder length hair, beard, sharply
clad in leather and denim, carried himself with a high enough level
of untapped fury that assured me that a show was just on the
horizon. His gang lacked the size, and I'd say intelligence,
but Jimmy aint exactly a member of Mensa. It was clear that the
6'6'' tall Jimmy was the leader of the group. These
hours of darkness were going to be something to remember.



``Whiskey.'' Like clockwork. I couldn't help but
crack a smile knowing that this dude was about to get fucked up.
``Leave the bottle.''



The jukebox in the corner began playing ``Here Comes the
Sun.'' Jimmy Dean and his cronies approached the stran\-ger.
Unpromisingly, the green pained lights shuttered as the air became
stale. Marv sat in the stool to the left of the stranger, the other
guy behind him and Jimmy stood to his right. ``Who the fuck
are you?'' Jimmy asked in a slow but forceful tone as he
reached for the bottle. He picked it up, unscrewed the cap and took
a swig. He set the bottle down in a violent enough motion to cause
the liquid to splash on the bar. The stranger didn't flinch.
Hands still clasped around the glass, eyes still looking down.
``This isn't the a film noir. Hey asshole, I'm
talking to you!''



Jimmy reached out for the strangers collar. The temperature in the
room rose, but I felt cold enough to see my breath. My spine felt
severed as I fell back towards the wall behind me. Jimmy now had a
fistful of shirt and was close to unleashing a mallet of a fist on
this guy, when, in the blink of an eye, it was all over. The
stranger threw a swift enough boot to Jimmy's kneecap that
created a sound comparable to a thunderclap. As Jimmy doubled over
in immense pain, the stranger swung his hand around grabbing the
side of Jimmy's head, and, in a fluid motion, flung it down
towards the bar. The hard wood surface of the bar gave way to the
man's fucking head! The wood splintered around the hole that
was now host to a man's head. A second later, the man
standing behind the stranger took flight towards the pool tables,
slammed into the wall and became one with a pool cue. Marv, the
third man, suffered a brutal shot to the throat that sent blood
flying out of his mouth. He collapsed to the floor clutching his
sunken windpipe and gasping for air. I couldn't move.



The stranger turned his gaze to me. His eyes created black holes
amongst the leathery, sandblasted, sun damaged face. His black hair
dangled in strands from under his black hat. He reached up, stroked
the stubble on his chin and sighed. After surveying the
destruction, he non-chalantly picked up his glass, downed it,
reached into his pocket and pulled out a coin. His eyes never moved
from mine, and then a moment of clarity came upon me. The
uneasiness. I froze. I could see flames in the blackness. He stared
a hole directly through my soul. The carnage still existed among an
eerie peacefulness. He flipped the coin in the air, caught it with
his right hand, smiled and placed it on the counter. He then tipped
his hat and left. I remember seeing lights. 

 



