\chapauth{BatsBjorg}
\chapter{The Horrid Beginning of It All}


Eleven-year-old Luke Bavarious stood frozen in the doorway to his
bedroom. He couldn't turn the light on. He wouldn't be
able to turn it back off from his bed. But he couldn't get to
his bed without the light on. He was in a real pickel.



``Dad!'' Luke Bavarious yelled. Another year, another
month maybe, and he'd be too old to yell for his daddy. But
yell he did. ``Dad?''



Luke Bavarious could hear the sounds of the Mets game from the
living room. He could also hear the sound of another Coors popping
open. His father's alcoholism had become publicly known sense
his mother had left. Luke Bavarious thought his father was probably
about halfway through his Coors consumption. The consumption
varied based on how poorly the Mets were playing, and right now
they were on a hell of a skid. Luke Bavarious got a not-unwelcome
rush from thinking the word ``hell.'' Hell, hell, hell,
he thought. Shit, hell.



``{\bf Dad?}'' One more time.



``{\bf Goddammit} Luke! What is it now. I toldja gota bed fiteen
mints ago!'' Maybe more than halfway through the night's
Coors.



``C'mere a sec!'' Luke Bavarious wouldn't
tell Bartholomew Bavarious what he wanted until he came to the
bedroom.



``Goddammit{\ldots}'' Luke Bavarious heard his father
mumbling curses under his breath, heard his shuffling steps down
the hallway, and then he was there. Luke Bavarious could smell the
putrid stink of stale Coors and BO oozing from his father's pores.
Or maybe his unwashed undershirt.



``Will you turn the light off for me after I get into
bed?''



``Jayzus! Notiss shit `gin!'' Luke Bavarious
watched, horridfied, as his father drunkenly reeled into the pitch
black bedroom. His father wiggled his ass at the closed closet
doors. ``Scareduh monshters? Monshter inna
closet?''



Luke Bavarious felt a thin stream of vomit rise up in his mouth,
then burn his throat as he forced it back down. His voice cracked.
``Dad, don't. Just{\ldots} just.. get the light,
wouldya?''



Bartholomew Bavarious ignored his son. Or maybe didn't hear him over his
own drunken whoops. ``Monshter inna clos{\bf et}!  Monshter inna
clos{\bf et}!'' He sang over and over, in a childish rhythm. Luke
Bavarious stood, unblinking, unbelieving in the doorway. He saw the
closet doors rattle slightly.



``Dad!'' His voice pitched upward, like a little
girl's would. It was the last time in his life his voice
would break like that. ``Dad, seriously. That's not a
good idea{\ldots}''



``{\bf Notta guddea}? Oh fuck you, Luke Bavarious.'' And with
that, his father threw open the closet doors, completely unprepared
for the horrid behind them.



Luke Bavarious couldn't turn away. He saw a fountain of vomit
bubble up and spew forth from his father's mouth, but he
didn't notice his own vomit until later. It got all over his
feet.



The horrid in the closet shot two tentacles out as fast as
lightning. Bartholomew Bavarious' eyes bulged, the Coors
leaving his body in a flood of beer-scented piss that soaked into
the carpet. The horrid's tentacles wrapped around Bar\-thol\-omew
Bavarious' throat. Two more wrapped around his arms. A slimy,
barbed tongue eased from the horrid's mouth. It slashed
Bartholomew Bavarious' face open, clear from one cheek to the
other. Blood erupted from the face, mixing with the beer-piss in a
rusty puddle.



``Oh dad!'' Luke choked out. The horrid turned its horrid
head for one horrid second. A glimmer of recognition flashed in its
horrid eyes, but only for a horrid second. Then it unhinged its
horrid, terrible jaws, vomiting forth a horrid stream of green,
acidic vomit. Bartholomew Bavarious' clothes started to steam
and simmer. The last thing Luke Bavarious saw were his
father's eyes plucked out and eaten, first one, then the
other.



A single tear rolled down Luke Bavarious' cheek. Then
suddenly, he was not sobbing. He knew what to do.



He sprinted to the bedroom his parents had once shared, back before
the Coors and the publicly known alcoholism. He took his
father's Beretta from the nightstand, relishing the feel of
it in his small hand. It was cool, in every meaning of the word. A
shock of what he would later know as desire prickled at his belly.
He raised the Beretta, testing it. He grabbed ammo and shoved the
gun in the waistband of his pants.



From the bedroom that was once his, he heard slurping sounds. He
decided to take the shoes he'd left by the front door instead
of his favorite sneakers. Now that he thought about it, those were
kids' shoes anyway, and Luke Bavarious was a man.







