\chapauth{Ben Biddick}
\chapter{The Cough}

He was so sick. He had a terminal disease. He vomited tears from his
eyes. He threw up over and over again. He was always sweating. Sweating
to the point of dehydration and delirium. The doctor couldn't find out
what was wrong. He just knew that my friend was going to die. Anyone
could see that! The doctor was dismissed from trying to help. He could
do about as much as I could.

I sat by my friend day and night. Crying and cursing right along with
him. It was driving me insane. My friend was going to die and I could do
nothing to stop it! His bed sheets were soaked with the odor and liquid
of perspiration. He was rambling on, mumbling nonsense. What could I do?
My brain! His body! He screamed with all of our agony.

I prayed constantly to God, First I prayed that my friend would
heal. After no letup from this horrid sickness, I prayed that the Lord
would take my friend's soul so that I could rest! You call me inhuman?!
You can never understand. You did not see your best friend frothing and
foaming, sweating unrelentlessly, going to the bathroom on himself and
laying in it for days! That is what is inhuman, not me.

The idea finally sprang into my mind. I laugh with the thought of some
rest from this terrible nursing. I giggled with delirium myself! I would
be rid of this forever! Yes, I would do it!

I grabbed a urine stained pillow from the floor and shoved it over the
face of my friend. I first heard him choke and giggle, than in a few
seconds that seemed centuries, his body tensed. He scratched at me. He
tried to get the pillow away but he was too frail. Ha! He soon began to
relax eternally.. Soon enough, the man was dead.

I took the pillow from my friend's face. He had no pulse. His chest
showed no movement. He was dead. Suddenly, a wave of depression and
sadness drenched my body. I cradled my friend's sweat-soaked head and
began to cry. He was so cold and so gone. He had died with his eyes
open. I was too tired to close them.

I staggered out the door. I would finally be able to rest. Oh, Lord
forgive me, I could rest. What was that? Something peculiar sounded from
the room behind me. It was a dead man's cough\ldots
