\chapauth{Ben Biddick}
\chapter{Human Existence}

Rogue Davix looked at his arm. Just above the wrist, three large, scabby
lumps bulged. They moved in and out, like they were being inflated and
deflated again and again. The first lump increased the rhythm as each
other lump formed. The first lump was going faster than the second lump,
and the second lump was going faster than the third lump and so on. The
flesh around the three lumps was cracked, flaky, and dry. Rogue squeezed
his fist together in pain and wiggled at the burning pain. He squinted
at the four men in lab coats. Why were they doing this? The four men had
each given Rogue a shot and that was when these lumps had sprung
up. Were they mad scientists? What the hell were they doing?

``Stop this!'' Rogue screamed. ``Villains!''

Purple liquid suddenly spurted from a tiny hole forming in the first
lump. Three drops came out and dripped down the minute cascade. Yellow
liquid suddenly erupted from the cracks in the flesh around the sores
and spurted upward about a foot. One of the men in lab coats quickly put
a beaker on the arm and collected some of the fluid. He took the sample
to a small machine and poured it into an aperture where green light
flowed from its opening. The scanner on the front lit up in strange
markings that Rogue couldn't read. The four men watched it carefully and
sighed at what they saw. One or two of them looked over at Davix and
startled him as the expression cut through his pain straight to his
soul.

Suddenly, two more lumps began to be born. They pushed their way up and
Rogue screamed in even more agony. After those, three more lumps began
to push. They sprung up and the first two lumps exploded, throwing flesh
and blood everywhere. A chain reaction happened and the lumps increased
in creation. The lumps covered Rogue at an alarming rate. They exploded
one of at a time. Rogue squirmed at the pain.

One of the men in lab coats ran to a control panel and pressed a
button. A transparent screen lowered in front and around Rogue. Blood
and a variety of colors of liquid hit the screen and dripped down. Rogue
stopped squirming and had uncontrollable tremors. His tongue stuck out
and his teeth clapped down on it. The tongue bounced off Rogue's body
and fell to the floor. His fingernails pushed their way back into his
skin, squirting blood in spatters. Yellow liquid squirted a foot into
the air from the dry skin around the exploding scabs. Rogue soon died.

The men in lab coats all sat down and looked at the lump of flesh
strapped in the chair. They sighed in disgust and one of them cried.

``The destruction of planet Earth's environment and ozone is
terrible. This species called human cannot live on our planet, the tests
we have given show that. They will no longer exist. There is nothing to
be done.''
