\chapauth{Ben Biddick}
\chapter{I Venture Down the Path}

Militant. That is what I was, militant. Or was I insane? Inhuman?
Demonic? I was created by militancy. Created with the emotions of hate
and anger. Born with the desire to kill. Muscular cular and
wild. Intelligent and lethal. Born and created with the love of
suffering. The lust for dangerous highs. Fueled by the rushes of
hate. Non-narcotic but just as addictive. The passion of no
compassion. Murder at will with the utmost impunity.

Impunity succeeds with the victim unwanted or uncared for. For instance,
taking the life of a drifter, or homeless person. My prey was of that
type which would succumb to me.

My shadowy facial and bodily features were exposed to the filtered
light. A streetlight's glow was seen through the many halls and
passageways of the certain domains of the different entities of this
cruel world. My victim was approaching.

Some old, drunken man was walking down the alley. He was singing the old
folk song, ``I Venture Down the Path.''

I held the sides of my apparel so that the wind of the night could not
flutter it. I stepped forward. My ductile muscles bulged with the
anticipation of the rush. My teeth were observable as a smile presented
itself upon my lips.

The reeking man walked into me, for his drinking had impaired his
vision. He stopped in the middle of his wretched song as he cursed me
for being in his way. Hatred arose from my demonic soul as the man
proceeded with his vulgar and insulting language.

``I'm quite sorry,'' I snarled to the drunk.

``You b-better b-be,'' he belched, releasing his foul breath.

``Friend, it is you that I am sorry for,'' I bellowed.

His expression was inquiry as I began to beat the poor fellow. He
staggered and fell as I brutally struck him. My heart was alive with the
beautiful feeling of hate and love; the love of hate.

I stood up. The deed was done. I sucked in the night air and felt it
flow through my body. The rush slowed as I wiped the blood from my
knuckles. I began down the alley, the tune of ``I Venture Down the Path''
whistling from my lips\ldots
