\chapauth{Ben Biddick}
\chapter{Grandma}

All she did was sit in that chair. She was my grandma. Grandma
Packard. She was the old hag of her town. Everyone hated her and
everyone was hated by her. She never left her house and I guess she
never left that damn chair. I was fifteen when it happened and I hadn't
seen her out of that old rocking chair my entire life. The chair was old
and rickedy and creaked when it rocked. I'd think that the creaking of
that chair would drive her insane! She hated me dearly. She never showed
any love or affection to me, but to all the other children she did. That
was the reason I hated her so much. She never had time for me. All she
could do was drool and sit in the rocking chair. Yes, I hated her. Right
to my soul. I had such an incapacity for her. I hated her at a higher
level every time I saw her. It just kept rising. She was at least ninety
something. I really didn't care to know anything about her. She shared
her love with no one but her grandchildren---with me the exception.

I was glad when she died. She never left that chair---she even died in
it. It was pitiful. Her weak heart had finally given up.

We inherited the house, and we had to make major repairs and we had to
have major cleaning sprees, but I could finally be free of her evil
sneer that shook me with uncontrollable fear. How I hated her.

I had to have that room. Not by choice believe me. The room she had
rocked her heart to death in. I quivered at the thought of living in it,
but I had to since my little sister and brother were afraid of it.

It was the first night to sleep in it: the room. I had my covers totally
concealing my body---a habit I had developed in my days as a toddler. The
moon was unusually bright and the light showed through the thin blanket
because I had placed my bed by the window. I soon fell asleep.

I opened my eyes. I thought I heard footsteps in my room. Was it mother?
I saw the shape of a woman pass through the moonlight interrupting the
flow onto my blanket. Sweat broke out from my back and fear swelled
inside my stomach. I wanted to scream for help, but I was too terrified.

``Eddie Packard, why did you hate me?'' asked a woman's voice in a
taunting tone.

I was too horrified to answer. I heard a thud that sounded like the
woman was placing something on the floor. I gritted my teeth with total,
terrible anxiety.

``I know you're under there, Eddie,'' the voice crackled.

I could not move. My heart beat so loud the woman must have heard it.

From right next to the bed, I heard the familiar creaking of Granny
Packard's rocking chair. She was going to drive me insane.
