\chapauth{Ben Biddick}
\chapter{Impatience and Curiosity}

They said I was discontent with life. I forgive them though. Looking
back on my life's ending, I weep. Everything wasted. How could they know
why? They thought I was happy with life. They thought I loved every
single one of them. They thought I was satisfied, they thought.

The death of my body was self-imposed. I loaded a pistol, and put it to
my head. Without any hesitation or fear, I pulled the trigger. My soul
then retreated from my physical into into a terrible world of nothing.

I do not know why I committed the act. My life was stable financially. I
was soon to be married to the beautiful maiden, Annabel Lee. We never
quarreled, so the cause of my death wasn't inspired by heartbreak. There
was no forethought or common sense involved. Curiosity. Is curiosity
with the after-death world an excuse? Curiosity wasn't the entire reason
for my self-imposed death. It was also impatience. I couldn't find
anything exciting. My assets had enabled me to travel. I had a nice
house. Enough money for all the financial things. I had plenty of
friends. Ones that cared for me, not only my money. I had my soon-to-be
wife. I had my family. I'd run out of imagination to create goals and
achievements. My brain then came across the thought of my only frontier:
death. Would you call me insane.

Now I just float here, in the darkness of purgatory, not doing
anything. For what is there to do? I have long given up trying to get
out. It is eternal punishment for taking away the most important thing
God gave humans. I only with I could die again\ldots
