\chapauth{Ben Biddick}
\chapter{Willy}

I sat on my chair and opened a can of beer. The TV was on and I was
looking for a break from reality. It was 1953. I had just bought the TV
and was adjusting to the adaptation of sight and sound together.

The Korean War was on in the Far East and a number of the younger
generation of the town in which I lived had gone off to fight, including
my grandson, Willy. I had fought in WWI, my son John had fought in WWII,
and now Willy had gone off to fight in the Korean War. I prayed for
Willy often, for I knew the ravages of war.

I soon had fallen asleep on the chair when a certain annoying sound came
from the door. It was a certain scratching. A horridly fearful sound. I
woke with a start and walked to the door. The scratching came again and
then a moan. A terrible low moan, filled with anguish, pain, sadness,
and fear. I took a step back. Another moan. It caused fear to waltz up
and down my spine.

``Who's there?'' I shouted to the other side of the gate.

All there was was an attempt at the word: Grandpa.

``Willy?'' I asked the voice, and my sanity.

I swung the door open in anticipation. There was Willy, lying on the
front steps. He was dressed in combat fatigues and had no left leg. His
thigh was raw meat. Blood had turned the green pants into rust all the
way across Willy's buttocks, top right leg, and lower back.

``Grand-nd-pa,'' Willy stuttered, ``I can't walk. What is wrong?''

The young man was bewildered to the point of delirium. I hugged the boy
and cried. I shut my eyes to the agony and squeezed the young boy.

``Oh, Will,'' I shuttered.

I then opened my eyes and I was holding nothing. I rubbed my eyes, and
retreated in shock and bewilderment. I went back into my house in a
stupor and called John's house. All I could say when John lifted the
phone was, ``Willy---''

``Grandpa,'' I heard accompanied with sobs and shrieks, ``Willy's dead. His
left leg was blown off by a grenade and he bled to death.''

All I could do was hang up.
