\chapauth{benitocereno}
\chapter{The Beginning}


Minutes later, to the sound of gunshots, Rogue Davix aw\-oke from his
horrible dream. The lumps, all of the lumps, were nothing more than
a satanic vision. The dreams were always the same. Aliens,
darkness, another world. If he didn't have amnesia maybe he
would have had some clue as to why he was haunted every night. But
it was a dark and dangerous secret, only willing to unlock itself
when he proved himself worthy.



He brushed it off because he was not sleeping well. There were
strange noises outside of his apartment at night. Evil noises.
Noises so black they could snuff out the light of decency in the
strongest of men. He complained several times but no one would take
care of it. That is why he decided to hire Luke Bavarious,
PI.



Rogue jumped out of bed and ran to his window. Luke Bavarious had
unloaded his Beretta into a stumbling ghoul, but the ghoul would
not stop. Luke struggled but was not able to stop the monsters
advances. They were coming towards Rogue's window!



{\em Crash!} The window splintered into a thousand fragments and
flew everywhere. The muscular fighters traded blows. Blood and vile
fluid splattered everywhere. After minutes of fighting it finally
seemed that Luke was the winner- the ghoul fell to the ground and
cocked his head to the side, his bile vomited across the floor.
Luke collapsed to the floor and began to sob, his face disfigured
by the shattered glass and powerful blows delivered by the now
fallen ghoul, the evil merchant of pain. Rogue ran over to help him
up.



``Luke, it's okay, you won.'' Rogue said, trying to
comfort him.

``No, it's just{\ldots} no, I'm one of
them!'' Luke screamed as he looked into a mirrored
fragment.

``No you're not, it's not what you have on the
outside that matters Luke; it's what's on the inside.
And we both know what you are. You're Luke
Bavarious.''

``You{\ldots} you're right. But we can't stay
here.'' He pulled himself together and stood up, triumphantly,
defying the gods trying to keep him down.



Luke was right, outside more sounds began to stir. The ghouls could
smell the evil cocktail of blood and vomit wafting through the broken
window, and they were hungry. Luke handed Rogue his spare Beretta.



``I hope you know how to use this,'' he snarled
through his clenched teeth. Rogue popped the safety off.



The ghouls poured in through the window. Luke kicked open the
apartment door and they both ran to the fire escape.
``We're gonna have to go up!'' Rogue said as he saw
the advancing horde of darkness.



``What's causing this!? Why is this happening?''
Rogue panicked as he fired into the ghouls while climbing the
stairs. His bullets landed in their limbs, barely slowing them
down.



``I don't know, but some people say it's the
Ozone! Without it, people are transforming into these{\ldots}
things! More and more lately! Either that or you just {\em really}
pissed someone off!'' Luke unloaded a clip into the closest
ghoul's skull; brains flew out of the back of its head like a
playdoh press. Images of the horrible dream flashed through
Rogue's head.



They circled the top of the fire escape and stepped onto the
rooftop. Once there Luke turned his trusted Beretta onto the fire
escape itself. {\em Bam, bam, bam,} he shot the retaining bolts
loose. With one swift kick he dislodged the staircase, sending it
and its undead inhabitants to the ground stories below. It was then
that they observed their situation.



The rooftops across the horizon, hundreds of them, were covered in
ghouls. It wouldn't be long until they found a way onto their
roof. The blood red sun rose in the distance, casting the shadows
of the ghouls across the rooftops, giving them an intangible bridge
to their goal. The flesh of Luke Bavarious and Rogue Davix.

Rogue admired his gun with a thousand yard stare.



``Two bullets left{\ldots} I guess we're lucky,'' Rogue
sighed.

``That's two more than we're going to need,''
Luke smirked.

``What do you mean?''

``You saved my life back there when I was ready to throw in
the towel. Now it's time I save yours. You don't remember a thing,
do you?`` Luke paused{\ldots} ''we're getting off of this
planet.'' Luke shot his Beretta into the air, but the bullet
stopped inches from where it left the barrel and resonated with a
metallic thud.



Luke's ship appeared from the naked air, the bullet held in
place by its force field, an impressive blue craft from the
stars.



``Is this{\ldots} the end of Earth?'' Rogue asked.

``No, no son. This is only the beginning.''



Basking in the clarity of the moment, the fog lifted, Rogue grabbed
onto his father's hand as he pulled him into the ship. Luke
hit the burners just as the monsters made their way onto the roof,
turning them into clouds of flying pink mist, their screams silent
against the engines' roar.



They had a lot of zombies to kill, it was time to get to work. 

 



