\chapauth{BigSkillet}
\chapter{The Screw That Turned}

``{\ldots}and his little heart, dispossessed, had stopped,'' said a man in
a powdered wig that was reading a story to a group of people.
Everyone else in the group was scared except for one, and he stood
up.



``That story sucked and the ghosts were gay,'' said the standing man,
who took a badge from his coat and showed it to the storyteller. It
read 'Luke Bavarious, P.I. PhD.'



``I should arrest you for being so boring,'' he said, drawing his gun
and aiming it at the storyteller.



``Oh bother, please don't, old chap,'' said the storyteller, who was
British. ``It isn't my fault, it's a true story and it really
happened that way. And it all happened in this very same house on
this day ten years ago!''



When he said that everybody else got scared because it meant they
were in a haunted house, but not Luke Bavarious. He just grinned
and put a cigarette in his mouth.



``You all stay here, I can handle this. I can arrest those ghosts,
and I'll show them the letter of the law the hard way.''



``Oh Luke, you're so brave,'' said one of the ladies who was sitting
in the room.



Luke Bavarious fired his gun into the air and then lit his
cigarette on the still-hot barrel. ``It's all in a day's work,
ma'am,'' he said, ``and I like my work.'' With that, he left the
room.



Luke Bavarious walked down the hallway with his gun drawn. The hall
was dark with shadows, but his glowing cigarette gave him all the
light he needed. Suddenly, outside of a window, he saw a shape.
Luke recognized it as a man, but the hallway was on the third
floor. There was nothing outside for him to stand on except the
darkness. It was one of the ghosts that the storyteller had warned
him about.



``Stop where you are!'' said Luke Bavarious, aiming his gun at the
window. The ghost stayed outside the window, an evil glimmer in his
ghostly British eyes.



``Put your hands up. You're under arrest for haunting this house and
I think you molested a kid in that story,'' Luke continued, but the
ghost ignored his order. Luke fired at the ghost, two bullets
shattering the window with a thunderous crash. When the smoke
cleared, the ghost had vanished.



Suddenly, he turned, and at the end of the hallway was another
ghost. It was smaller but still British, and Luke recognized it as
the ghost of the boy that had died.



``I've defeated the ghost that killed you, there's nothing to be
afraid of now,'' Luke said, approaching the boy.



``Please don't feel that I've been bad,'' said the boy. Luke stopped
and aimed his gun at the boy because his sixth sense told him it
was a trick. ``I had no intent to harm when I stole that
letter.''



``You're under arrest for stealing,'' Luke said. Two shells hit the
floor as he fired into the boy's ghost. When he went to inspect the
boy ghost's body he found a letter in his hand. It said: ``To my
dearest Luke. Please forgive me my son. Sincerely, the
ghost.''



Luke Bavarious dropped the letter and screamed as he felt his heart
stop from the true horror that was his fate all along. 

 






