\chapauth{Blurry Gray Thing}
\chapter{Monstrous}


In the shadows of our overcrowded cities lurk unspeakable horrors.
No one knows or can imagine the horrid reality that lurks beneath
our wholesome fa\,cade. I am one of the few people who does. I
am a private detective. My name is Luke Bavarious. These are my
stories.



I was investigating a brutal serial killer operating in the bad
side of New York. When I saw his latest victim, I was stricken by
the horrid brutality of his violence. The murderer cut out the
homeless man's heart, stabbed him through the eyes, and
carved him open from buttocks to head. Vomit forced its way past my
teeth, and poured into the gutter, mixing with the unfortunate
victim's blood. That night, I went home and drank whiskey
until the alcoholic poison killed all the feeling in my
brain.



I used my detective skills to track the murderer to a warehouse in
the worst part of the city. I knew the killer had to be there. All
of the monstrous murders pointed to it. As I walked there, I felt
nauseous. The people all around me were garbage. Prostitutes and
thieves. They did not deserve to live. But they did not deserve to
be brutally murdered.



I stalked carefully into the warehouse. My combat boots carried me
silently through the shadows. I heard a man ranting and I saw a dim
light coming from a small room. It had to be him.



``Why are there so many of you now? Where are you all coming
from!?'' The man was insane. Whoever he was talking to
grunted.



``You can stop pretending! I know what you really are. I
won't let you get away with it! I'll kill all of
you!'' he was screaming. I had to save his victim.



I smashed open the door with my shoulder. There was an old man in
horribly ragged clothing tied to a chair. There was also a thin,
pale man with pitch-dark hair, holding a knife. The knife was rusty
and fat from all the blood it had drank. I raised my Beretta at his
head.



``Hold it! Let him go!'' I ordered the killer.



``No! Please, you don't understand,'' he said. His
face was twisted by tears and rage. He raised his knife to impale
the victim's face.



``No, you don't understand. Put down your weapon, or I
will shoot you,'' I ordered again. The rust-colored knife fell
out of his hands. He was sobbing. I started untying the old man.
The old man smelled like blood. I thought it was because he was
injured.



``No!'' screamed the murderer. ``Don't let him
loose! He'll kill us both! He's a monster! You
don't understand!''



``You are the only monster here, pal!'' I untied the old
man completely.



Suddenly, the homeless man let out a horrid roar. It almost
deafened me. I could not do anything to stop him. He flew at the
murderer teeth-first, like a human-sized vulture, and tore at his
neck. Blood the color of ripened apples exploded all over the tiny
room, and shone bright red in the light of a single bulb. I fired
my Beretta at what I had so incorrectly assumed was a victim. The
recoil shot through my arm but he did not stop. He tore apart the
man's skin, muscles, and arteries with horrible strength,
even as I squeezed round after round into his back. His growls
mixed with the sound of shells hitting the floor. Soon, the
murderer was a pile of ruined meat.



He turned around and looked at me with eyes dark as dry blood. I
knew my gun could not stop him. I dove to grab the murderer's
knife. I knew what I had to do. The old man dove to grab my
throat.



No one had ever solved that crime. I told the Chief of Police that
I found two more victims in an old warehouse, but couldn't
handle working the case any longer. The murders continued. Every
month, a new homeless man was found cut open, with his heart carved
out. The police knew it was all done with the same knife, but no
one knew who was doing it. 
 




