\chapter[Horrider Reflections]{The Horrid Reflection II: Horrider Reflections}
\by{Bonaventure}


The screamers screamed past with a screaming scream that screamed
in the ears of Luke Bavarious Junior. They were horrid and horrible
beings of indescribable horror. But if you had to describe one then
they looked exactly like Ghost Face the famous killer from the
Scream movies. Luke Bavarious Junior woke up with a scream because
he had been screaming in his dream when he was dreaming of the
screamers. ``What are ya screamin' for?'' said Luke
Bavarious Senior who is the protagonist of the story and who is
Luke Bavarious Junior's father and who came into the room
where Luke Bavarious was screaming.

``I saw the screamers again dad,'' Luke Bavarious Junior
whimpered.

``Gah!'' his dad Luke Bavarious, paranormal P.I. said. He
said ``Gah! You've been watching too much Scream. I told
you that stuff rots up your brains into blood. Now I'm going
to burn your Scream DVDs so you stop having
nightmares.''

``No! Not my Scream DVDs!'' screamed Luke Bavarious
Junior. ``I'll show you, dad{\ldots} I'll show you
that kids should be respected and listened to'' he grit his
teeth until they bled blood all over his chin.



``I'm off to work honey'' Luke Bavarious said to
his hot wife who was still in bed because---heh, women. Am I
right, fellas? Then he put a donut on his pillow next to the wife,
he got the donut from the donut shop across the street and every
day he put a donut on his pillow for his wife to eat, this is
important information to remember because it foreshadows the twist
ending that's coming up.



Luke Bavarious had been known as the paranormal detective ever
since The Case of the Horrid Reflection where he killed a
doppelganger. ``So you're Luke Bavarious.'' The
words vomited out of the mouth of the police chief. ``I hear
you've been known as the paranormal detective ever since you
killed a doppelganger.'' Luke nodded and chewed on his
noir-as-hell cigar. ``That's impressive stuff.
Dopplegangers are tough to beat cause they have the same moveset
and equipment you do.''

``Tell me about it, chief.'' Bavarious crammed a fist
into his mouth that was full of peanuts and then he chewed down the
peanuts into a horrid gloopy paste that slid down his disgusting
horrible throat.

``Well, you're just the man I need,'' said the
chief. ``We got reports of a doppelganger factory that's
taken over the old Frankenstein-making factory out on
I-45.''

``Say no more, chief.'' Bavarious cocked his Beretta and
doffed his really sweet fedora. Then he drove to the doppleganger
factory.



The doppelganger factory was filled with bile and amniotic fluid
and all sorts of gross blood and vomit. The dopplegangers were
being made in sacs of pus. Bavarious shot up the sacs of pus and
was covered in sheets of vomit and fat as the baby dopplegangers
writhed on the floor in a scary way. ``Luke Bavarious''
said the head doppelganger who had set up the doppelganger factory.
Bavarious narrowed his eyes. The doppelganger was horrid with
horrible pus scars all over his purpley face screwed up looking
gross.

``I thought I killed you, Luke Bavarious,'' said Luke
Bavarious, when he recognized himself as the doppelganger he
thought he killed but he didn't really.

``You thought you killed me, Luke Bavarious, but you
didn't really. I just feigned death by copying a dead guy at
that moment. We dopplegangers are good at copying stuff. Here,
I'll copy a guy vomiting acid at you!'' then he vomited
acid at Luke Bavarious, and boy it just stank to high heaven, ugh!
Bavarious was ready though and he shot the doppelganger making
machinery above the doppelganger and then the factory started to
explode in sparks and blood and black bile and white pus as the
doppelganger sacs all exploded and a billion baby dopplegangers
screamed out in dying death forever. The head doppelganger screamed
as all the blood and pus and bones exploded out of him like in a
Mortal Kombat fatality.

``Another day, another time the earth is saved from dopplegangers by
Luke Bavarious,'' said Luke Bavarious, walking away in slow
motion. Behind him, the factory exploded.



That night in his home Luke Bavarious slept asleep, but Luke
Bavarious Junior was up and he sneaked off to the kitchen and
turned on the deep fryer. He had evil red eyes and he laughed,
``Haw, haw!'' He raised a voodoo doll in the air although
more accurately it's a European witchcraft doll because the
idea of sympathetic magic used through dolls doesn't have
anything to do with traditional voodoo but was instead an idea from
European ideas about witchcraft that was conflated with rumors
about voodoo okay but {\em anyway} he takes the doll and he raises it
over the deep fryer and then he monologues: ``Haw, haw! Dad,
you might have saved the world from those dopplegangers but
I'll teach you to burn my Scream DVDs. Now when I want to
watch Sarah Michelle Gellar get killed in Scream 2 and masturbate
to it I'm going to have to search for ``Sarah Michelle
Gellar death Scream 2'' on youtube and like half of them are
going to be music videos and none of them are going to be good
quality and it's going to be a real pain in the neck!
I'll get revenge for that! You're going to learn a
lesson, dad. Kids should be respected and listened to, because if
you mess with them, maybe they have a voodoo doll---although
really it should be called a European witchcraft doll but
I'll get into that later---and then they'll do
{\bf this}!'' and he threw the doll into the deep fryer and
uproariously began to cackle softly to himself with a silent
``Haw, haw, haw!''



The next morning, Mrs. Bavarious woke up and found a donut on Luke
Bavarius' bed. ``Oh, he must have already left!''
she pooed, and then she bit into the donut. A scream of horrid
terror burst her throat open as she bit into the donut and, like in
a sex scene starring one of the Wayans brothers, she was splayed
against the wall by a torrent of blood, guts, and Bavarian cream. 

 





