\chapauth{Brolita}
\chapter{Mac}



This morning, I woke up to find myself dead.



I don't know how it happened, or why. That's why I'm here. Easy
G's, a dive on the bad side of town. Mac, the guy who runs the
place, is a good friend of mine. Always around to lend an ear.
Tonight, I hope he has two.



My name is Luke. Luke ``Lucky'' Bavarious. I'm a private dick. At
least, I was, before I died. My dad was a cop. A cop that didn't
play by the rules. That's how he died. He broke the rules. Then the
rules broke him.



My dad died when I was 13. He didn't listen to me. I knew the
streets. He thought, because he was old, because he was
experienced, that he knew more about the dark realities of the city
than I did. I tried to warn him. He didn't listen to me.



It was a night just like tonight. Except both of us were still
alive. At least, for now. My dad was called in to investigate a
shooting. Prescott Avenue. The worst street in the worst
neighborhood in the worst city. I remember him drinking when he got
the call. He didn't always drink. Only when he {\em knew}. When he
knew something was going down. When he knew he would be cheating
Death. When he knew that one drink may be his last. He {\em knew}.
And {\em I knew}.



I've blamed myself for my father's death. I've blamed him. I've
blamed the alcohol. I've blamed it all. But the one thing I can't
blame is the person who killed him. I can't do that, because I
don't know who it is. I've spent my life searching for him. I
became a cop, because I thought I could find him. I couldn't. I was
fired for using excessive force on a drunk one day. Served him
right, the swine.



Tonight, maybe, I'll find who I'm looking for.



I breeze into the bar like a shadow. That's pretty much all I am
now. A shadow. A shadow to my father, who is now a shadow himself.
The world is full of shadows, shadows that we don't see until it's
too late. I've been through a lot of crap in my time, seen a lot of
things a sane man would be better off without seeing. Luckily for
me, I'm not a sane man. I guess that's why they call me
Lucky.



Mac's behind the bar. I slam some money down. ``I'll need a strong
one tonight, Mac. Gimme a Screwdriver.'' I wince at the sound of the
word. I killed a man once. Stabbed him through the head with a
screwdriver. Phillips head. Poor Phillip.



Mac pours me a stiff one. ``Rough day?'' He asks. ``I'm just getting
started,'' I say, lighting up a cigarette. Red Apples. Menthol. It
stings like fibreglass, and I almost want to vomit. I take a drink
to cool down my throat. ``Mac,'' I say, my hands shaking, ``I'm
dead.''



Mac looks up at me. To my astonishment, he's not surprised. He
knows.



``I know,'' he says. ``I'm the one that killed you.''



My shaking hands curl into shaking fists. Mac. My friend. My brother. My
killer. I lunge across the bar. ``You {\bf rotten murderer}!''  I scream
at him. I can't think. I can't breathe. My cigarette falls out of my
mouth.



I grab his neck. From my holster, I pull my baretta.



I don't even hear him laughing as I pull the trigger. 

 



