\chapter{Chamber Pop}
\by{Brushingworth}



Feebly, Luke Bavarious reached into his mouth and pushed on his
molar. He winced as it shifted unpleasantly in its socket. Pain
shot down his jaw and Bavarious clenched the edge of the sink. The
dried blood caked onto his hand cracked and fell into the sink in
large flat scabs. Bavarious raised his head and turned on the
water, hot all the way. Steam rose from the large sink. Bavarious
was in the basement of his office building. The door he had just
stumbled through was still open, letting in the night's
biting cold air; Bavarious didn't notice. He spat twice,
three times, into the sink and plunged his hands into the water,
clenching his fists at the near boiling temperature. The liquid was
quickly polluted to a dark red.



``Shit,'' Bavarious let out as he finally opened his
office door on the sixth floor. Inside the lamp on his desk lit the
dim room. Someone in the plastic chair preceding his desk turned.
What the fuck, Bavarious thought suddenly, but he let out no sound.
``Ah, you're back,'' said the small boy sitting in
front of him. ``I've been waiting almost an hour.''
``Well sorry kid,'' Bavarious responded as he trudged to
his desk chair, ``I've just about had enough people for
today.'' The kid stared at him unblinking. He was probably
thirteen or fourteen. ``Mr. Bavarious? I need to speak with
you about an important matter. Don't you think it's a
little funny that a kid like me is here to see you? Let me
introduce myself, I'm Oscar Crowley.'' While the kid was
talking, Bavarious unloaded his Berretta and gave the kid a
sarcastic glace every now and then. ``Alright listen
punk.'' Bavarious gestured with his Berretta as he spoke,
``Today's over. Finished. All that's left for me
is a bottle of Jack back home. If you've got some sort of way
of paying me outside of Monopoly money and lemonade stands than
tomorrow you can come back and give me your sob stories, tonight go
home. It's passed your bedtime anyways.''



Bavarious was spread eagle hanging upside down on the moldy couch.
He watched Law and Order on the TV upside down in front of him and
sipped whiskey from a bottle, most of which by this point dribbled
down his forehead. He didn't hear anything when the figure
slid open the kitchen window. From the fire escape a dark and dim
figure in combat boots stepped into the apartment. Bavarious, due
to an insurance commercial that annoyed him even in his inebriated
state, lifted the bottle for another swig and saw in the reflection
of the moving glass a dark figure lunging toward him. Bavarious
raised his hand to stop the intruder but the figure quickly batted
away his drunken defenses and closed two gloved hands around the
detective's throat. Bavarious' eyes bulged and he
coughed a mixture of alcohol and vomit. Flailing, Bavarious saw
that he was still holding the bottle of Jack and quickly smashed it
over the head of his assailant. After gasping for several minutes,
Bavarious got up to check on his unconscious prisoner. The man, if
it was a man, was clothed only in a long brown overcoat. His head
and face was covered by the coat's large hood. The
man's head was completely devoid of hair, Bavarious
couldn't tell if he was shaved or simply never grew any. His
face was what made Bavarious recoil. Under what should have been
the man's eyebrows (which were also missing) was nothing but
a series of gashes and burns. Large scars ripped up and down the
man's face, the larger ones continuing down into the robe
that Bavarious didn't want to look under. The only human
feature about the man's face was a vertical gash, about three
inches wide and four inches tall, where the intruder breathed
harshly.



{\em I need some coffee}. Bavarious walked unsteadily in the
gutter. He had left the man/thing in his apartment exactly where he
had fallen. Probably not something he would have done sober but,
tonight he wasn't in the mood for procedure. His boot caught
the edge of a storm drain and he tumbled, scraping his hand on the
concrete. He sat that way for awhile. Watching the dirty water
funnel into the sewer. When he was ready to keep moving, he looked
up. Standing right next to him was Oscar Crowley. ``I told
you,'' said Oscar disappointedly. ``What the fuck are you
talking about kid,'' Bavarious spat, feeling only slightly
embarrassed at his language in front of the boy. Turning, Oscar
walked away from Bavarious. ``You're gonna lose yourself
in darkness, man.''



{\em What?} Bavarious watched the little boy walk away and thought
about the cryptic message. Did the boy know something about the
monstrosity that had just attacked him? He had to find out. Getting
up, he stumbled down the street and turned into the alley he had
seen the boy enter. Suddenly, he halted. Down the three foot wide
alley was nothing but a couple of garbage cans, a dumpster and some
wires running through the water on the ground. What slowly dawned
on Bavarious was that this was the very same alley that he had
encountered the monstrous noise violator early that day. He slowly
walked to the end of the alley and back three times, looking for
any way the boy could have left the alley without him seeing. On
the third trip back he gave up and decided to go for that coffee
after all, but stopped halfway out. He had been running his hand
down the eastern brick wall of the alley and this time he felt a
faint vibration in the stone. He put his ear up to the wall and
listened. At first he didn't hear anything and the wall
seemed to have settled, but a few seconds later he hear a slight
thudding sound and felt the wall shake once again. Bavarious
scanned the wall for a window or drain that might lead inside the
building. Seeing nothing left the alley.



From the street the building didn't look like much. He couldn't hear the
thudding from this far, and the front wall didn't seem to be
shaking. The front had an old-fashioned lighted sign that read ``Larry's
RR'' and offered a jukebox, soda fountain, and coffee. The front windows
were broken but had been boarded up by strong looking wood. {\sc
  Blackout Armistice} was splashed across the left board in black
spray-paint. After trying and failing to make sense of this felonious
abstrusity, Bavarious looked up to examine the upper floors of the
building.  Most of the windows were boarded, plenty were broken, through
a few he saw a spare bookcase or desk but nothing was moving in any of
them. The longer he contemplated the lofts; he began to notice something
about the rooms. He couldn't quite focus on it immediately, probably
thanks to the last of the Jack still digesting in his stomach. Suddenly
he caught it. In a few of the rooms he could see the same orange-tinted
light faintly. Every so often the light would flicker or go out
altogether for a few seconds. While this could have been attributed to a
bad electrical line, Bavarious noticed that in every one of the rooms
the light responded identically, as if the same bulb was burning out at
the end of every kitchen socket.



Bavarious pulled his Beretta. {\em I'm going in}. He
wasn't sure why he was going in, but he was sure he was
going. He leapt up onto the right display window and landed on
broken glass. With the butt of his gun, Bavarious smashed into the
wood. Chips flew away but the barricade seemed unharmed. He tried
several more times and then went the front door. Bavarious
couldn't see through the glass door but it seemed to be
blocked only by paper. I hope I'm not gonna regret this. He
pulled his leather sleeve over his right hand and slammed the butt
of the gun through the glass door. It shattered and the glass fell
on both sides of the door. Through the paper he could see the decay
of an old caf\'e and the same orange light. He reached through
the tear and tried to unlock the door. The lock seemed to be
rusted. Sighing, Bavarious steeped one leg then the other through
the door, kicking away the rest of the paper.



On the other side of the dining room the orange light poured
underneath a door that Bavarious thought looked like a bathroom. He
crossed the space quickly and approached the door. It was indeed a
bathroom, but the sign had been defaced. What had once been a
standard female figure had some sort of black stain on the front of
her skirt and was dripping black liquid from between her legs.
Bavarious thought it was the same spray-paint as the outside
proverb but he didn't examine it closely. He stood with his
hand on the door for a moment and suddenly he hear the same
thudding, much louder now, and a shuffling murmuring. Inhaling,
Bavarious opened the door with his Beretta drawn.



Inside Bavarious took one and a half steps before stopping dead in
his tracks. His eyes glazed over and the orange light of the room
shined off them like blisters. The room was cavernous. The entirety
of the building had been hollowed out and Bavarious could see the
rooms he had seen from the streets above. They seemed to be
perfectly untouched until they simply ran out of floor. They gaped
out into sepulchral like pockmarks as if someone with a wrecking
ball had tried to demolish the building from the inside out. On the
floor of the room were fold-out metal chairs arranged in rows
giving the building a church-like atmosphere. The chairs were
almost completely filled with people. Bavarious couldn't tell
much about them due to the brown hoods they were all wearing.
Somewhere in his brain Bavarious recognized them as the same that
the man who had tried to kill him had worn. The same part of his
brain that realized there were over four hundred of them. That part
of his brain wasn't really important to Bavarious at that
moment. In fact he barely even noticed the room or the people in
the chairs. His eyes swept past them and were drawn to the sight
they were all apparently there to witness.



At the far end of the room, a few yards to Bavarious' left,
was a man standing like an accursed teacher at a rusted wooden
fold-up table. Lying on the table were various medical instruments
and a small girl. Bavarious thought she might have been seven. She
had long tangled blonde hair that stretched past her shoulders and
ended soiled in the puddle of blood that she was lying in. The girl
had been split open vertically from neck down; the cut had not been
clean. The man at the table had removed most of the contents from
inside her but apparently left the connections. Spare blood vessels
and muscle ligaments crisscrossed over her and draped down to
various organs that were spread out on the table. Terrified,
Bavarious noticed that the girl was breathing slowly into a mask
that was connected to a makeshift airtank below the table.
Bavarious looked away and saw that at the front of the table, a few
feet from the first row of chairs, was the body of the man he had
shot earlier. The body was similarly dissected and seemed to be
waiting for some sort of terrible transplant procedure.



Bavarious stood frozen. He mouth was slightly open. Suddenly, he
saw a door across the room open and Oscar Crowley step out. He was
also petrified by the scene and stood standing for several moments.
When he saw the girl on the table, however, he shouted
``Sam!'' and charged up the room. The onlookers seemed
shocked as well and Oscar made it almost all the way to the front
of the room before one of the men in robes reached out and grabbed
the back of his shirt. He was stopped dead by the strength of the
man. Slowly the nearest of the congregation raised from their seats
and helped subdue the boy. He kicked and bit at all that came near
him but eventually they dragged him to the front of the room in
custody where the standing man removed the mask from the girl and
placed it over Oscar who spat into the mouthpiece but eventually
slowed his thrashing and eventually closed his eyes. From there
most of the group returned to their seats while a few laid Oscar
next to the splayed corpse. Suddenly, Bavarious realized he was
sobbing. 
 






