\chapauth{CannedMacabre}
\chapter{For the Children}


Norma's Diner is a horrible place to get a cup of joe. The only
reason I was there was to meet a mysterious client that had
insisted on anonymity. He had reached me twice by phone in the past
three weeks and only identified himself as Mr.\ M. I told him that I
would only take the case if we met face to face. Mr.\ M contacted me
again this morning by text message to say that we should meet here
at Norma's at 10:30 sharp.



Its now 10:45.



I'm Luke Bavarious, Private Detective, and I don't take a case
without knowing the client, and I don't like to wait.



The waitress pours me another cup of swill as I look over my notes
on Mr.\ M's case. He says he is being stalked and that threatening
messages are being sent to his e-mail and voice mail. He hints at
the fact that some people are trying to blackmail him. He even
casually ponders whether his life may be in danger. Its really not
much to go on but with the clock ticking, I am beginning to wonder
if someone might have already done the guy in.



Its 11:00.



The only reason that I haven't gotten up and walked out yet is that
a manila envelope with five 100 dollar bills was slipped under my
door this morning with the words ``from M'' on it. I figured that I
would at least wait out the hour before going about my day. Maybe I
will choke down another cup of the vomit they call coffee in this
dump. As I raise the cracked mug to my mouth I hear the little bell
on the door sound followed by a loud voice:



``{\bf Hey}! What I tell you about those friggin skates in my
restaurant?''

I turn to see a smallish kid with a stunned look on his face nearly
crap himself. He has a giant book bag on his back and is wearing
those shoes with the wheels in the heels. Heelers? Heelies?



``S-sorry mister, I forgot.'' He says sheepishly and hangs his head
down in the embarrassment of all eyes being on him. He sits down at
the table across from me and takes out some school books and a
notebook. The waitress brings him a cherry Coke and puts a hand on
his shoulder for just a moment, then goes back to her cigarette
burning at the counter.



Poor kid.



I look down at my watch for a second and notice that ``M'' is now a
full hour late when I hear that sheepish little voice again.



``Sir, can I talk to you for a moment?'' the kid is right next to me
with his bag hanging half way off his shoulder.



``Uhhh{\ldots}Listen kid{\ldots}'' I start to say some rhetorical crap about
being a busy man or having some place to be, but something in my
gut tells me that not enough grown ups have made time for this
kid.



``You know what{\ldots}Yeah. Sure kid, have a seat.''

His eyes light up and he throws his bag into the seat next to me
and grabs his Coke form the other table.



``You're a private dick, right?'' The kid says.



``Uh{\ldots}yeah, Detective.'' I respond.



``Cooooool, I wanna be a P.I. too when I grow up. You carry a
gun?''



``Yeah, a Beretta, but it ain't all its cracked up to be. Sometimes
you gotta deal with a lot of scumballs and sometimes you just can't
help the people that hire you.'' I wasn't gonna BS the kid. If he
was keen on getting into this line of work, he better know
{\em exactly} what he was getting into.



``Besides, even if you do solve the case, you get the bad guy and he
gets what is coming to him, it can leave a bad taste in your
mouth.''



He nodded a bit in agreement and turned his eyes down towards his
drink. He was quiet for a moment and then suddenly he spoke in a
voice that was not at all sheepish or meek:



``Detective Bavarious, Mr.\ M wont be joining you today.'' he said in
a calm, controlled voice. ``In fact, I doubt that Mr.\ M will be
contacting you again at all.'' This statement chilled me to my bones
and instinctively I lowered one hand under the table to the Beretta
clipped to my belt.



I was all ears.



``You see, Det. Bavarious, Mr.\ M was being harassed, stalked and
blackmailed. and I am the one who was doing these things to him.''
The kid's voice was deeper now, and I must admit that he commanded
my attention as few others could.



``I targeted Mr.\ M for the crimes that he has committed against
children. He is a child molester and a murderer and I wish to see
him imprisoned for these crimes{\ldots}''



``Wait,'' I interrupted. ``A twelve year old kid has a man running so
scared that he pays a private investigator to find out who is
harassing him?''



``Det. Bavarious, my name is Nathaniel Stilling. On my twelfth
birthday my father beat me within an inch of my life and I spent
the next 4 months in a hospital. When I awoke from my coma I
promised myself two things: I would protect innocent children from
harm, and I would never have another birthday. That was 57 years
ago.''



I had no choice to believe him. From the beginning of our
conversation I had felt that I was in the presence of a wiser, more
virtuous man then myself. So when this kid, this small, sheepish
child told me he is a 69 year old man{\ldots} I believed him.



``Look son,'' he continued, ``I know that you have the power to put
this monster away.'' With that he pushed a DVD in an unmarked case
across the table.



``I wouldn't get curious about whats on that disc if I were you. The
things that man has done are not meant for our eyes.'' He slid out
of his chair and grabbed his book bag.



``Oh{\ldots} and Mr.\ M's real name is Michael Wilkinson. He is a biology
teacher at Washington Junior High School. When you give the cops
the disc, just tell them that it was given to you by another PI
that knew who your client is.''



The boy then gave himself a big push on one foot and skated towards
the door on his heel wheel.



``Dammit kid! I'm gonna skin your hide!'' The ape behind the counter
screamed.



``S-sorry mister{\ldots}I forgot again.''



The End. 
 





