\chapter{The Horrid Erection}
\by{Cheesus Christ}


I stepped into the stall. The urge had come again. I was in the 4th
floor men's room of the Tri-County Technical College library.
The sleek basin of water in the toilet bowl beckoned for my cock
like a lost lover. I am a chronic masturbator. My name is Luke
Bavarious. I like to masturbate.



Sure, people had been complaining about weird noises coming from the
campus restrooms for about a year now, ever since I enrolled last
spring. Signs were placed on all the bulletin boards and restroom
entrances: {\sc Restrooms Monitored By Security}.



I edged my swollen crotch closer to the rim. Suddenly, I noticed I
was not alone. Peeking under the stall I saw a dark pair of legs
occupying the stall next to mine---the handicapped stall. I
thought I heard the faint sound of sobbing. No matter, I lowered my
fly and gripped my quivering organ.



``Keep it down, buddy,'' I shouted through the stall
divider.

``(Sniffle{\ldots} sob)''.

``{\bf Keep it down}!'' I shouted again.

``(Sniff){\ldots} beggin' your{\ldots}
(sob){\ldots}pardon,'' said the legs.



I began to pull on my delicate member, but found it impossible to
concentrate thanks to my weeping accomplice. Now, I've wanked
it co-op before; never bothered me. Hell, I've even wanked it
with people crying (Grandma Packard's funeral, `natch),
but this time? This time I just couldn't even raise a
chubby.



A breeze trickled over my waggling dick as I slapped the divider.
The sobs had grown louder, though now they were mixed with a deep
grunting sound. ``Shut the fuck up man, I can't even
think!'' I cried, though the noises only responded with
renewed intensity.



Enough is enough. After one last bang I knelt to the floor and
peered up at my discourteous neighbor.



``{\bf Shut the fu---}'' and I could say no more. The occupant
twisted its convulsing body toward me. First its reverberating
forearms. Then its jiggling ball sack. Then its penis. If you call
it a penis. Its texture was horrid. There was an abundance of
purple scars. There was blood leaking from open sores along the
shaft and from its urethra. There was no hair. Only pulsating
veins.



I banged my head on the bottom of the stall in astonishment. I
gritted my teeth but spurts of vomit flew from my
mouth---Quiznos. He took a step towards my defenseless head and
I saw his Johnson glisten with lubricant in the dim florescent
light.



He screamed and arched his pelvis toward me. His stub of a hand was
flying furiously across his pole, which I could tell was ready to
commence its brutality. Then, he pulled the trigger.



His body recoiled as he loosed an animalistic scream. I heard a
splatter hit the floor beside my head and looked up just as his
One-Eyed Snake sprayed my gaping mouth with a wad of jizz. It kept
cumming with the assistance of his adrenaline. Only a split second
passed before he squeezed off another round onto my neck.



His Thing was inches away when it fired point-blank into my throat.
He slapped my head with his dick terribly powerful. I could see its
strained muscles as my head jerked to the side, smashing into the
floor. Dazed, I felt him fire again and again into my nose, eyes,
ears. I felt his recoil pushing back rhythmically. Man-juice
hitting the pavement, showering me. I felt my own cock fall limp
again the floor. He kept firing, but his magazine was empty. He
staggered. I tasted his semen and blood mixed into a horrid cock
tail. He stepped over me. A library card dropped the floor.
Bavarious.



I looked down at my hands and saw a horrid erection. Suddenly, I
was sobbing. 
 



