\chapter{The Library}
\by{Combat Wombat}





My name is Luke Bavarious. I'm a PI, a private investigator. I
wasn't always a PI, I used to be a cop. A damn good cop, the best
on the force. But that was the past. There's no point dwelling upon
the past. It's not so bad though, a PI is like being a freelance
cop.



I had a new case, it had come in this morning as I was trying to
murder my hangover with a coctail of aspirin and coffee. The phone
pierced the silence and drove deep into my head with the force of a
semi-truck going 55 miles per hour. I swore never to get this drunk
again. I remember I had fought down the vertigo and struggled to
make sense of the words coming out of the earpiece. ``This was worse
than the time I killed myself in the alley,'' I thought to myself.
At least I hoped I thought to myself. What if I spoke it out loud?
I looked at the phone in my hands in horror. My hand trembled. It
suddenly became too much weight to bear. I remembered mumbling
something close to ``I'll be there'' and slammed the phone headset
back on it's cradle. At least I hoped that's what I said. It was
all too much to deal with.



I was struggling to piece together what the voice on the phone had
told me. The voice said something about noises in the library.
There were children there, they were afraid it was a stalker. The
police had found nothing and they couldn't watch the place all day.
That's where I came in.



I grabbed the bottle of aspirin and twisted the child proof safety
cap off. I downed the entire bottle and washed it down with the
remained of my coffee, now lukewarm and disgusting. Odd, I thought.
I just made this pot.



I grabbed my berretta and palm slammed a clip into it. As I made my
way towards the door with grim purpose I was accompanied by the
sounds of aluminum cans being crushed underfoot, cans that lay
scattered across my apartment like ammo shells. There had been a
war here last night, Coors were the bullets. I was the victor and
the defeated.



When I got to the library it was deserted. It was a cold, desolate
place lit only by the night lights. Rows upon rows of books lined
the shelves. Each one was like a tombstone, the library a masoleum.
It was all too much.



If there was a stalker I would need to stake him out. I searched
the library and found the perfect place, a hallowed out section of
a bookshelf that I could fit myself into. I removed the books and
squeezed myself into my new hiding place. As I began piling books
to cover myself up my fingers brushed against the covers of all the
books. I could feel the grain, the texture. The embossed lettering.
I hate embossed lettering. Some of the books had jackets with
embossed lettering on them. I tore those off and hid the jackets.
The books were much better without them. There wasn't anything I
could do about the ones that had embossed lettering on the covers
themselves.



Soon I was perfectly hidden, a specter. A ghost. Now I had to wait
and watch. My berretta felt cold and heavy in my hand. It was my
constant companion, my only friend in this cold, terrifying
world.



I waited out the hours. The cold blackness of night soon gave way
to morning and the library opened. Librarians streamed in and began
sorting the returns and placing them on the appropriate shelves.
Dewey Decimal would have been proud of these librarians.



Soon the place was filled with adults and children. My eyes were
sharp, alert. I had picked a perfect spot with a clean view of the
checkout counter and much of the library itself. I would find this
stalker.



I could see the effects of his presence, clear as day. People
looked around worriedly as if they were aware of someone watching
them. No, not someone. Something. I could feel it too. A deep,
murderous intent hanging on the air like heavy cobwebs. A cold,
unrelenting malice that permeated the very air. A thick, undulating
smog of contempt. It bore down on me, on everything. It terrified
me. I swallowed the vomit that threatened to climb up my
throat.



I could feel it everywhere. I could feel it's eyes on me. I could
see no trace of it, though.



The police came again, I guess they decided to take another look.
They inspected the place. They were dutiful and attentive, but my
hiding spot was too good. The stalker's must be even better. Soon
they left.



The stalker was still here.



Hours continued to crawl by like a wounded semi-truck limping down
a gravel road with a flat tire as oil, precious blood to the
vehicle, vomited forth from ruptured lines and leaving a death
trail on the rocks. My finger rested uneasily on the trigger of my
berretta. I had to be ready.



I was startled to attention by the voice of the head librarian as
she picked up the phone and punched in a number.



``Is this Luke Bavarious?'' I began to tremble. {\em No{\ldots}
no!}



``This is Pamela Dufrost at the Metropolitan Library, we've been
hearing strange noises and it's frightening the
children{\ldots}''



As I felt the icy grip of fatalistic, militant terror grip my heart
I could hear laughter. Was it coming from my own lips? No, it
couldn't be! I screamed, the noise erupting from my throat
like vomit.





Edit - I guess it has a very weak link to respecting children. Not
being a creepy time travelling stalker is an important message
right? 
 



