\chapter{The Horrid Reflection - Redux}
\by{Cota Froise}





I sat at my computer. The email had come again. I was checking my
emails in between browsing the Something Horrid forums. My hand
shook slightly with the mouse in my hand. The white cursor was
positioned and ready, ready to click. I am an internet detective.
My name is Luke Bavarious. I like this work.

People had been complaining about horrid email attachments coming
from a mysterious stranger for about a year now and I finally
decided to see what was going on. I had decided to stop these
emails.

I leaned into the dim monitor light. I saw a single email sitting
in my `junk' folder, hiding away from me. It was
strange and suspicious. I raised my mouse and lined my cursor up
with the icon.

``You there{\ldots} What are you then?'' I whispered through the
darkness.

``Open up{\ldots}'' I whispered again.

``Beggin' your pardon, but{\ldots} you don't want to open that,'' my young
son said.

``Sure I do. I got a cursor pointed right at it so I'd
better,'' I replied.

``Okay, you asked for it,'' my son mumbled as he began to turn
around.

A chill trickled through the room as I clicked and the picture
began to load for me. I couldn't see it yet, it was loading on the
screen.

``Get onto the screen.''

It inched downward. First its back. Then its arms. Then its ass.
Then its legs. If you look at the legs. His ass was horrid. There
was an abundance of red flesh. There was blood leaking from a burst
blood vessel and he only had one gold ring. There was no face.
There was no head. Only a hole.

I took a step back in astonishment. I gritted my teeth to keep the
vomit down.

I took three more steps forward and I felt my tears glisten in the
dim light.

``I told ya,'' my son said.

He screamed and began to run away from me. My mouse was held high
in the air and was ready to commence my brutality. I clicked the
right button on my mouse. The click soothed my fear as I saw a
drop-down menu open and saw the `delete' option make a
white rectangle over the thing's ass. It kept resisting with the
assistance of my email provider's inferiority. It had only
been a split second before I brought up another drop-down menu over
its ass. The thing was inches away as I dragged and dropped it into
the Recycle Bin. Two more appeared on my desktop.

My palm smashed my forehead terribly powerful. Muscles were
strained and torn as my head jerked to the side, smashing a window.
I fell and landed in jagged glass. Dazed I stared again and again
into the thing's hole. I felt the vomit rising back rhythmically.
Glass hitting the floor. Me hitting the glass. Vomit showering me.
I felt my own blood from the side of my head fall and drip. I kept
staring. The hole was empty. I staggered. I tasted my tears and
blood mixed into a horrid cocktail. It fell down next to me. A name
sparkled on the side of his ring. Bavarious.

I looked up at the computer screen and saw a horrid reflection.
Suddenly, I was sobbing. 
 



