\chapter[Dead Tired]{Dead Tired\\Horrid Reflection: Gaiden}
\by{Count Snapula}



Luke Bavarious woke up from a horrid dream in his Manhattan
apartment. He was vomiting sweat from every pore in his body. It
was exactly 6:36 in the evening, according to his digital clock. It
was blinking red. The color of satan. Luke had been having the same
nightmare for a week now. He was on duty looking into noise
disturbances when he was assaulted by a horrid monster, that was
maybe himself. Not even his trusty Beretta could save him from the
undead menace. Detective Bavarious grimaced grimly as he put on a
dirty wifebeater and some slacks that smelled faintly of hobo
urine.



Walking to his refrigerator, Bavarious picked up the ubiquitous
Beretta off the toilet on the way there. He searched through the
crisper intensely, only to find a week-old tuna sandwich and a
single piece of knockwurst.



``Jesus fucking christ. I wish my wife didn't leave me,'' bemoaned
Bavarious as he settled for the tuna. The bitterness over his ugly
divorce almost masked the taste of sour mayonnaise. With some
sustenance in his stomach, he began shaving over the kitchen sink.
Though Bavarious was uncannily dexterous with a Gillette{\copyright}
Fusion razor, something caught his eye in the reflection of the
faucet, and he made a deep gash in his face. Rust-colored blood
began to spray out, but fortunately Bavarious was able to hold back
the flood with a wash cloth.



``Man, I must be going crazy or somethin','' muttered Bavarious to
himself as he opened his last can of Coor's Light, which responded
with a concerned '{\em pfffssssssht}'. Turning around to look out
the window and watch homeless people fight over garbage until his
shift began, Luke finally saw the culprit of the Razor Incident: an
enormous crow, black as midnight, holding a human eye in his beak.
Never to be caught off guard, Bavarious emptied his clip into the
horrid avian intruder. As he went to confirm the death of the crow,
he saw something that drained all the blood from his face.



Below on the fire escape was his ex-wife, her intestines trailing
out of her corpse and one eye pecked out of its socket. Seeing
this, Bavarious vomited uncontrollably out the window and onto the
grisly scene.



``Who could have done something like this?!'' Shouted Luke Bavarious,
once he had regained control of his bowels. Suddenly, he felt his
hands bound behind him, with the familiar click of handcuffs.



``You did, Detective Luke Bavarious.'' Replied an NYPD officer, who
had just walked in with three others through his open apartment
door. Suddenly, those dreams all made sense to him. ``You've done
well by me, Luke Bavarious,'' whispered a terrible, gravelly voice
in his ear. He could tell it wasn't the cop taking him to the
street, because he had been punched in the balls as a kid and now
he talked like Elmo.



``What have you done?!'' Luke struggled to break free from his
captors. But in the end, he knew it was true. The real captor was
himself.



``Go to sleep, Luke. I'll take care of this,'' the voice whispered
smugly. Luke suddenly passed out, then. When he woke up, he was
covered in rusty red blood down to his buttocks, and all four cops
were dead. 
 



