\chapter{The Smoker}
\by{Cruo}

I stepped up to the door. The smell of the smoke was leaking
through the door. I was at the front door of Gus's Bar and
Grill. My hand started to shake a bit as I reached toward the
handle. I paused. I reached for my Beretta instead. My name is Luke
Bavarious, I am a private detective called in to investigate a
smoking complaint. I love my job.



I kicked in the front door with my boot, my Beretta ready for any
trouble I might find myself in. All I see is the bartender washing
out a mug at the bar with a terrified look on his face. With his
head he gestures to the corner. I follow his jerks and find my eyes
looking on the face of a boy. The boy was the age of a fifth
grader. At last, the source of the smoke has been discovered. I
yelled to the boy, ``Hey you! Yeah you in the corner, drop the
cigarette now!'' The boy only smiled and waved me to come
closer.



As I walked closer I got this horrid feeling that I knew the boy,
but I couldn't quite place it. I asked him why he thought it
was okay to smoke in this bar when the law clearly says it is
against the law. He flashed me another of his mischievous smiles
and asked, ``What's the matter Luke you don't
recognize me?''



Suddenly the thought came to me but I couldn't believe in my
own thought. ``I.. I.. wha.. who are you?''



``Really Luke, when was the last time you've looked in
the mirror?''



``No! This is impossible! You can't be!''



``Oh but I am Luke, I am you and you know it. Well{\ldots} I
was you.''



I was staring into the face of myself as a fifth grader. I
tentatively asked, ``Why are you here, what do you
want?''



``Luke, I was sent from the future to warn you of
something.''



``What do you mean the future, you're from the
past?''



``Shut up Luke, I was sent from the future, you wouldn't
understand so let me get back to my warning. I was sent to warn you
about finishing your little project.'' I was building a robot
in my garage in my spare time, that had to be what he was talking
about. ``Your little project may seem innocent enough now, but
it will be the end of mankind as you know it, and you must destroy
it before you finish, you must!''



Suddenly I saw a blue flash next to the boy who was myself from the
past but from the future. Some acid like substance sprayed out
through the flash instantly and the boys face started melting in
front of my eyes. It was terrifying, the skin and the blood and his
eyes and his tongue were all fusing together in a horrid tangle of
disgusting gore. I could see his bones through his melting face and
his screams were the stuff of nightmare. I started to intensely
vomit all that was held in my stomach, so intense that blood
started pouring out alongside the sick substance. My eyes were
bulging and my ears were pumping hard with the beat of my heart.
The boy was now a pile of melted flesh and blood and gore.

I dropped to my knees and scooped the pile of the once past future
self into my arms. Suddenly, I was sobbing. 

 



