\chapter{The Torrid Connection}
\by{Danger408}


Cleaning his Beretta for the third time that day, and taking a swig
of cheap whiskey, Luke Bavarious pondered his current case.



``This is going nowhere'' he thought. The case was
different, it wasn't about helping others --- it was
about helping himself. After seeing the face, the one so much like
his own, yet so different; things had changed. He tried to forget,
but all he could remember was the blood, all of the blood, the
blood everywhere. ``Was that really me?'' He didn't
know.



He glanced down at the picture of his son he always had on his
desk. The divorce had been rough, and he hadn't seen him in
while. Taking another swig from his bottle, suddenly he turned as
he heard a knock at the door, followed by two more in quick
succession. He hid the bottle behind his desk, hoping to appear a
bit more professional.



He didn't have to respond however, as the mystery person had
already opened the door.



``Hello,'' A beautiful woman started, ``I need your
help.''



``Have we met?'' He asked.



``I don't believe we have,'' she replied. ''I
got your name from a friend. It's doesn't matter though
- I have a case for you. My husband is missing. I need you to find
him, and I hear you're the best at what you do.''



``I'm not taking any more cases{\ldots} I have a lot of
personal shit to deal with. Besides, you really don't want me
to take the case.'' He paused for a moment. She looked
familiar, a face he knew he had seen, perhaps in another life, but
couldn't put his finger on who it was. She looked good
though.



``I'll do anything.'' She pleaded as she removed
her shirt. Luke had always prided himself as being a man of ethics,
but ethics only went so far. As he removed his shirt, he added,
``I'll take the case!''



They commenced sexuality. It had been a long time for both of them,
too long in fact, as it seemed like it would be over before they
even started.



As he lit up a pair of cigarettes, he once again got the feeling
that he knew her from somewhere. He knew her named started with an
``L'' but he couldn't remember the rest.



``Are you sure we haven't met before?'' He
asked.



``Now that you mention it, I think we have.'' She added
as she began to pull at her face.



She stretched and tugged, as vomit-like ooze poured out of her. She
tore away pieces of herself, discarding them on the floor like a
used condom. It seemed that the only thing left was a bloody mess
--- until she wiped it off, revealing a familiar face{\ldots}
His own.



Scared half to death, and knowing that the other half would soon be
complete, he managed to say, ``Listen to me{\ldots} Whatever
you do{\ldots} Don't touch my son{\ldots}'' He knew he
should have spent more time with the kid.



Finishing him off in more ways the one, the once-woman's
transformation was complete. Dressing in his cloths, and putting on
his badge, she was the new Luke Bavarious. Was it a monster? Or
could the real Luke from the future? Some questions aren't
meant to be answered. 
 






