\chapter{The Last Night of Luke Bavarious}
\by{Decatur Fist}







Check the machine. No missed calls. No word from Davix.
Nothing.



With a sigh that poured from his mouth with a torrent of non-amused
frustration

Luke Bavarious pulled a small slip of paper from his pocket and
wadded it up and tossed it into the waste receptacle with the
precision of a black man that shoots basketball in a Lakers jersey.
As a fan of black culture Bavarious was known for his hoop skills.
They had even saved his life once and then again on another
separate occasion.



Davix was dead, and that was that. There was no sugar coating any
longer. It must have been brutal. When you're surrounded by a
cacophony of death you think about death a lot. Davix had even said
during a haunting and stormy night that he hoped that he would go
in his sleep.



It didn't happen like that. Luke Bavarious could envision in
his head a vision of Davix dying by the hands of that beast.
Bavarious could see the hand of the beast smashing into
Davix' face terribly powerful. It was a bodacious site. One
to be remembered for an eternity of doomsdays.



You need a drink. Clear your mind. Stay on guard.



Something strange had happened earlier today, it was why Luke
Bavarious now had the small piece of paper that he had just wadded
up and thrown away just moments ago before the ticking sounds of
the clock hauntingly swept its hand across the face of the clock
bringing time forward to this moment.



The boy had told him that Davix would die, and Bavarious too if he
didn't listen. Bavarious had laughed a laugh and chortled a
chuckle at the thought of him and Davix going out on the same day.
However, it looked like the boy was batting half of a perfect
batting average now.



He had shown up on Market Street and followed him all the way down
Pine, up West, and finally had the courage to talk to him once
stopping on Center. He was wearing a grey hoodie and seemed to be
no more than 13. He had dark stormy and haunting eyes, and you
could tell he wanted to be taken seriously.



He had a pension for horror and a knack for stories. He claimed to
be the creator and destructor. His name was Biddick. He was to be
taken seriously by all accounts.



Bavarious had told the boy that he didn't have time for him,
and that he needed to leave, but there was a thirst that needed to
be quenched that longed for the answer of why the boy would show up
after following him and then having the balls that were big enough
to make him say such nonsense to him.



The boy told Bavarious he would be sorry. Bavarious ignored him and
ordered a tuna on wheat.





Alone.



The sounds came slowly at first, but then with a quickening of
rapid speed. Claws clawing razor sharp against banana peel soft
skin. There was a sound of terrible nursing. Like wounds being
cauterized by the flame of a thousand dying invalids.



They were here for Bavarious. He laughed a strange giggling laugh
that sounded like a maniac pumping gas into a Ford Fairlane. He
opened the window and let them vomit into the window and take
him.



They took him with a great brutality. 

 



