\chapauth{Detective Thompson}
\chapter{Words Will Never Hurt Me{\ldots}}





Young Bin Beddick was angry. He could feel the foamy rage rushing
through his ducts and into his brain. His parents didn't
understand him. They did not understand him. Did they understand
him? No. He could still hear his dad's stinging words echoing
like the tones of the Liberty Bell, ringing in his ears.

``What is this crap?'' his father bellowed like a walrus.
Bin had showed his dad his latest story. Bin was proud of the
story. But his father just crumpled the paper up, and tossed it in
his face.

``I will not allow this heathen tome within my house!''
he raged at the young Bin, before sending him to his room without
supper. His mother laughed her awful laugh, which sounded like the
cackling of a mother pig.

It was dark that night. As Bin bubbled like a cauldron of hatred
and spit, night-dim clouds began vomiting rain and lightning onto
the earth. Bin wished he could shoot lighting at his parents. But
no, he had better ways to get back at them. The pen would be his
weapon. Despite his young age of thirteen, Bin was capable of
writing like a pro. His teacher told him his writing could make
James Joyce and Shakespeare spew jealous tears from their eye
ducts. Bin's fellow students quaked in awe whenever he gave
one of his weekly readings, weekly readings that had been insisted
upon by the principal, Mr.\ Howard. Mr.\ Howard hoped the other
students would learn something from Bin. So far, all they learned
was fear. And jealousy.

So Bin picked up his pen, his fingers closing around it like steel
claws closing around the neck of an unsuspecting victim. Bin smiled
as he set to work, his pen flying across the page, his pen
releasing little black trails of ink, dark coffin worms that formed
words of terror and evil. Bin would show his parents what it was
like to be burdened with such talent. If it were ever to happen,
Bin felt tonight was the night he could give life to his words, for
real. How little did he know, he was too right{\ldots}

As Bin finished his tale of fierce revenge and bitter anguish, he
heard a cough from behind him. The sound of a man clearing his
throat. Reflexive instinct twisted Bin's neck around, until
he caught sight of the man behind him. Tall, shadowed, wearing a
heavy black trench coat and gripping something in his right hand.
That something was the sleek, metallic shape of a Beretta pistol.
The kind a detective might carry.

``Who are you?'' Bin asked with something more like
confusion than fright. Bin was made of stuff much too dense for
fright.

``Luke Bavarious,'' came the words, spilling from the
man's shadowy mouth like soup from a Grandma's lips.
Bin's eyes went wide, then turned mechanically like a
robot's eyes to the pages in front of him. At the top of the
first page, like a crow roosting above in a branch, sat the title
of his story. `Luke Bavarious'.

The man chuckled. Bin gasped, bewildered beyond thought.

``But{\ldots} but how?'' he stammered, again, not with fear
but with unknowledge.

``You gave me life, Bin. Your pure and simple rage came
together and hardened like a Jell-O mold in the fridge, creating
me, the perfect tool of your anger!'' Luke Bavarious nearly
shouted with glee. Bin hoped his parents wouldn't hear.

``But what are you doing here?'' Bin wondered aloud. Luke
smirked. He gestured with his Beretta toward Bin's door,
beyond which his parents were undoubtedly sitting like sheep before
the TV. Before Bin could speak a word, Luke Bavarious charged forth
like a rhino charging a hunter. Luke Bavarious smashed down
Bin's door. Bin could only follow him out into the living
room, where his parents were watching some inane television
program. When they noticed Luke Bavarious, both his mother and
father shrieked like lambs with their faces cut off. Bin's
father leapt to his feet. Luke Bavarious raised the Beretta pistol
and fired, the bullet entering his father's brain, Satan-red
blood gushing forth from the hole in the back of his skull. He was
dead. Bin's mother tried to run, but Luke Bavarious shot her
in the back. She fell like a few dozen sacks of potatoes.

``Oh, my spine!'' she whimpered. Her spine indeed. Bin
could see into the bullet hole, see her spinal column wriggling
like a snake caught in a bear trap.

``Mother!'' Bin cried.

``Why Bin, why?'' was all she could sputter from her
bloody mouth. Then she died.

``No! I didn't want this to happen!'' Bin screamed
at Luke Bavarious with all the rage of a volcano in Pompeii.

``Oh but you did, Bin. You did,'' Luke Bavarious
chucklingly spoke. Then he pointed the Beretta at Bin.

``Why me?'' Bin shrieked.

``Because, you are a bad boy, Bin. And bad boys must be
punished!'' Luke Bavarious said his final words as he pulled
the trigger of the Beretta. The bullet from the Beretta slammed
into Bin like the 42nd Street Subway slamming into a hobo that
jumped onto the tracks for some loose change. Bin collapsed, rusty
blood erupting like a fountain from every orifice in his face and
from the hole in his chest. A final, horrid chuckle escaped Luke
Bavarious' lips before fading away, dying with his creator.
Bin couldn't understand it. Luke Bavarious was a good guy in
his stories. How did this happen. And then, just before dying in a
pool of the blood from his body, it hit him, like a bat hitting a
skull.

``If only my parents respected me, then this never would have
happened!''

Then he died. 
 



