\chapauth{ding dang doo}
\chapter{Untitled}


I awoke from my slumber. The breeze of wind gently blowing wind
across my face. Sitting in the darkness, I thought of only one
thing: Luke Bavarious. The name. Repeating throughout my head,
puking it's mantra into my mind. Who was this man? I did not know,
but I intended to find out. I lit a Pall Mall cigarette and
proceeded to smoke it. Meanwhile, I dressed myself.



Into the dark and dimly lit night I wandered, smoking a Pall Mall
cigarette with my iips. I inhaled, and let my hate seethe. I
exhaled and let my hatred for love grow. Luke Bavarious. The name
echoed in my face. This name. A name like no other. I reached into
my pants and gripped my Baretta, and let a long sigh of relief.
Sometimes I forgot to put my Baretta in my pants. Tonight, I
remembered to do it. Strolling down the street in the dimly lit
night of darkness, I began to wander down the sidewalk. Luke
Bavarious. Why? Was this part of my grim imagination? Was he the
reason teachers and parents were afraid of me? This I had to find
out.



Finishing my Pall Mall cigarette, I crushed the butt of it against
a newborn baby, and slowly walked down a dimly lit dark alley. I
saw a shadowy figure of a man, or maybe it could've even been a
leopard. He let out a gasp of shock and started to ran into the
opposite direction. I quickly vomited and soon began chasing him.
Chase him I did, and I ran as fast as a machine with cyborg legs.
The chase was long and hard, and arduous. He ducked through
alleyways and jumped rooftops, but I had the scent of blood and
murder and puke in my nostrils, I was on his tail every step of the
way.



Until he stopped.







I found myself at my lousy apartment. Empty cans of beer littered
my floor. Numerous tissues surrounding my computer. The butts of
endless Pall Mall cigarettes emptied into countless newborn babies.
And he was standing in the corner. I cocked my head like a curious
dog, and asked, ``Who are you? And why are we here?''



Suddenly, he turned around, Pall Mall cigarette in his mouth. Luke
Bavarious. He chuckled and shot at me. And shot again. Then he shot
me again. With a Baretta. Then he shot me with his Baretta.



And as my neck puked blood from my neck and vomit spewed from every
faucet in my apartment, I heard the words, ``Did you hear Micheal
Jackson died?''



With my final breath, I sobbed, ``{\ldots}Don't stop{\ldots}till{\ldots}you get
enough.'' 
 






