\chapauth{Dirty Sanchez}
\chapter{A Tin of Popcorn}





``He was right, three left,'' I said aloud, my own voice startling me
as it broke the silence of the restroom. ``Not very many but they're
gonna have to do''. I lined the shells up on the sink like stalwart
little soldiers and paused for a moment to make sure nothing heard
me. I need to stop talking to myself.



``Won't be enough,'' the voice in my head replied. ``You saw what
happened to that deer. Three or Thirty, it won't be enough.''



The deer. The memories came back to me in a flood. Its hard to
believe that just this afternoon we were fooling around, shooting
cans by the campsite and sitting by the fire.



It all started with a can of overpriced popcorn. You know the kind,
one half covered with a powdery orange substance that's supposed to
be cheese and the rest a solid brick of caramel and popcorn that
requires an ice pick to break apart. The popcorn itself was not my
problem but rather the scr\-awny kid who brought it. Timmy was his
name, or was it Tommy? It doesn't matter. All that mattered were my
Captain's words to me in his office that morning.



``The Commissioner feels that we need to do more for the community,''
He said. ``I volunteered you to take a boy scout troop camping this
weekend.''



``You're joking,'' I replied.



``I never joke. You know that. Besides,'' He continued, ``Bavarius,
you've been a little weird since you returned to duty and you're
making everyone around here uneasy. Doing this will show you're
just a regular guy.''



``A regular guy,'' a voice echoed in my mind. ``I wish.''



``When?'' I asked.



``Saturday.''



``I'm busy.''



``Not any more. He will be here in a little while and they said he's
bringing you a gift. Make sure you smile.''



Sure enough, about two hours later a kid showed up with the can, a
bandanna, and an invitation to join them camping. He was a
squirrelly little fellow, who seemed to be as uncomfortable as I
was. Despite how ridiculous the situation, I determined to make the
best of it. What else could I do?



After shaking hands with the little guy and feigning gratitude, I
asked him where we were going.



``Timber wolf lake.'' He replied.



``I don't have any camping gear.''



``Oh, you don't have to bring anything, well have all the gear you
need. But don't forget to bring the popcorn.''



``This popcorn?'' I replied. I had no intention of eating the
garbage. Maybe I could give it away.



``Yes,'' he said, looking me straight in the eyes. ``Don't forget it.
Its a tradition.''



``I'm really not much for traditions,'' I said with a smirk.



``Its very Important.''



``Uh, Ok,'' I replied, still smirking.



``Great! See you Saturday. Nine O'clock,'' he said and bolted out the
door.

``That boy looks like a frightened animal,'' the voice in my head
remarked.



Saturday morning came and I dragged myself out of bed hung over and
smelling like the floor of a frat house basement. I showered, threw
on my clothes, and ran out the door. I would be late but at least I
would show up. Good thing I didn't have to pack anything.



When I finally arrived I was greeted by a pack of impatient and
excited boys and one pale, stern looking gentleman, who I could
only assume was their troop leader.



``Sorry,'' I mumbled. ``I'm not much for early mornings or
camping.''



``Don't worry about it,'' he offered. ``Thanks for coming. The rangers
won't let us camp here without a police escort. Not since those
campers disappeared last year. If you didn't come we could'nt go at
all.''



``Glad I could help,'' I lied. ``I'm Luke. Luke Bavarius.''



``Pleased to meet you Luke. I'm Tim.''



With the formalities out of the way, he rounded up his group and we
began our hike. After a few hours of walking my mind cleared and I
began to observe my fellow campers. A very unusual bunch. There
were eight of them. They all appeared to be about ten years old,
blond, and skinny. And there was something else. They were all very
quiet and jumpy. Once, shortly we passed the last park restroom, I
stepped upon and broke a stick which shattered the silence of our
hike. All eight boys stopped simultaneously, their heads snapping
toward me in unison. A second later, they seemed to realize what
they had done, put their heads down and continued walking.



``Creepy.'' the voice in my head commented. But what do I know about
kids?



We finally arrived at the campsite. The boys, a flurry of quick
movements, erected the tents, hung up the food, and gathered fire
wood. When the work was done they left me sitting on a log alone as
they went off to do whatever it is young boys do on a camping trip.
I took a second and looked around. The air out here was fresh and
invigorating. The temperature was perfect, the sky was blue, there
were sounds of nature everywhere. Suddenly feeling good for the
first time in ages, I picked up a discarded soda can and walked
down to where the boys were. Pulling my side arm out of my pant leg
I yelled ``Who wants to learn to shoot?''



Suddenly, the boys were all just standing there looking at me with
a blank expression. ``You brought your gun?'' Tim asked.



``Habit, I guess.'' I replied.



``You have much ammo?'' He asked.



``Twenty rounds.''



``Come here boys,'' he said loudly ``Mr.\ Luke is going to show you how
to shoot.''



The boys gathered around me and I put on a show. First they wanted
to see me hit the can from ten paces. Then, twenty paces. Next they
pointed out a log in the lake they wanted me to shoot. It seemed
that they couldn't get enough of watching me blow things apart. I
have to admit, I was enjoying it too. I also was working up an
appetite.



``So there you go boys,'' I announced.



``Come on!'' a boy shouted.



``Keep going!'' another added.



``I'd like to boys,'' I said, ``but I'm almost out of bullets.''



``You have three left.'' said the smallest boy, who seemed to be the
troop leader's son and was opening his mouth for the first time
since asking me to go with them.



``Maybe another time guys, I'm hungry.'' I said, ending the debate.
We walked back to the campsite and settled in for the night.



After a dinner of half-cooked hotdogs and baked beans heated in the
can, the silence settled back in and the sun began to go down. Tim,
the troop leader stood up to speak.



``Boys, I think it is time for dessert. Son, do you have the tin of
popcorn?''



``I, um, already gave it to him dad.''



``Oh. You didn't happen to bring it with you, did you Luke?''



``I'm sorry,'' I said sheepishly. ``I was in a hurry.''



Tim glared at his son who turned paler than usual and stared down
at his feet. ``Never mind then!'' he shouted. ``Bed time,
everyone!''



Without a word Tim and the boys turned and quickly disappeared into
their tents. Suddenly alone, I turned and walked to the tent that
had been designated as mine and laid down on the cool sleeping bag.
As I lay there the day's activity seemed to catch up to me and I
drifted off to sleep.



The sound that awoke me was like nothing I had heard before. It was
a sound of pure, primal terror. Instinctively, I jumped to my feet,
grabbed my Beretta and entered the darkness. The moon was full and
high in the sky. With the fire burned out and no other light
sources I could see quite clearly and distinctively. Too
clearly.



A flash of movement about fifty yards from the tent caught my eye,
but it took me a few moments to figure out what I was seeing. It
was a deer, running with something hanging off the side of it. It
was now making a gurgling sound as the creature attached to it tore
at its throat. In a heap the deer went down. I could hear it being
torn apart. I pulled my gun and shouted at the creature, thinking
it was a mountain lion or coyote. It looked up at me and in the
light of the moon and I realized what I was looking at. Or, perhaps
I should say, {\em who} I was looking at. There, perched on the
disemboweled buck was a young human-like creature in a Boy Scout
uniform. Blood dripping from fangs that protruded from his mouth,
he seemed to be sizing me up while also staring at my gun. The
sound of breaking brush began to come from all around me. I had a
choice to make. Fight or flight. I made a break for it.



In the moonlight I could see the trail we hiked out on almost as
clearly as I could during the day. The adrenaline flowing through
my veins allowed me to run faster and further than I had since my
days in the marine corps. At first I thought I could hear someone
behind me, but eventually there was nothing but the sound of my own
footsteps. I rounded a bend in the trail and saw in the distance
the restroom that we passed on the way to the campsite. Unable to
run any longer, I lunged for the door, found it unlocked, and dove
inside, latching it behind me.



The restroom only had one door and no windows. I was cornered but
at least I only had to defend a single point of entry. I ejected
the clip from my pistol and counted the rounds. Only three rounds
left.



``Won't be enough,'' the voice in my head replied. ``You saw what
happened to that deer. Three or Thirty, it won't be enough.''



``I'm afraid there is more than three of us,'' the voice behind me
says. I can feel the hot breath and sets of eyes on me.



``If you only ate the popcorn we prepared for you then you would
still be asleep right now,'' another voice, a child's voice, says
from the shadows.



``I'm not much for traditions,'' I whisper as the teeth close upon my
throat. 
 



