\chapter{Again}
\by{Dominic Bones}


I sat on the edge of my bed, drinking a glass of water I had just
gotten from the kitchen. My dog Bud was laying at the foot of the
bed. I stared into the glass, watching my own reflection, and
watching the reflection of the creature behind me.



With a long face and empty eyes, and a mouth that could only be
described as slender. It stared over my shoulder, it's hands at its
sides. Sometimes I would think it was speaking to me, only to find
that it was Bud whimpering.



It always stared, yet when i turned I could not see it. when I
closed my eyes it would be there, clear as day, yet when I opened
them the creature would be gone. I could not explain it. The Dogs
howls were going through the night sometimes.



Why I could not say. Happened since I moved into this house. My
girlfriend and child had left me because I would just lie awake at
night. She said I had no emotion anymore. Said i should see a
therapist. my kid said he loved me but said that he couldnt have a
father that never helped him. he encouraged me to hug him and
promise him I'd always be there and to leave the house with mommy.
But he didn't really like that idea, so I didn't. Dog barked. Hear
the name Luke.



my dresser was an elegant wood paneling, and my floor had a lush
red carpet. Sometimes he would seep onto it and make it seem black.
i didn't know why, he just told me it would show me the way if i
followed him. I always just sat on the bed though. The dog was
scratching the bedpost now. heard the name Luke ringing in the back
of my head.



my glass of water was almost out. i looked out my window and saw
him there, and he asked for me. i would just shake my head, as i
had stopped spaeking. i had recieved a letter the other day that
said i had to mkae my payments, but he told me it wouldnt be an
issue. The dog attempted to lay on my lap. Heard ``Luke'', nothing
but Luke and white noise.



i told myself to go to sleep, but something was bothering me as if
something was buried deep in my head. i kenw that i couldnt just
take aspirin to get rid of it. i felt something at my foot but when
i looekd down it wasnt there. my bathroom mirror could be seen in
the crnoer of my eye, and he could be seen in the mirror. his
fingers pointed at the bed, thuogh i didnt turn t see what he was
pointing at. The dog jumped on the ground and stared at me.



he came up to me and mvoed my hand. he put it on the dogs back and
squeezed. i ddint know what was going on exactly but he asuserd me
it wuold all be arlihgt. my hand ddint stop suqeezing for an hour.
the dog didnt make any noise except the word ``Luke''.



soon i had began laying down and fell asleep. i suddenly felt
better. he had told me that i would soon be able to go to sleep. i
remembered this feeling happening the day before my girlfriend left
me. i fgiured that he just knew how to clam me down. i layed down
and put my haed to rest.



wehn the men came in the morning, i awkoe and walked down to the
mess hlal with them. tehy dont think hes real. the dcotor said i
was imagninig thnigs. she ddint know me thuogh. only he understood.
soon i flet a relaxation in her office like lsat night,before i saw
the lghit coming from the wnidow. he told me taht i cuold be in the
lghit. but i ddint want to. i olny wanted to be wehre he guided me
to. He spoke but I did not hear.



atfer i stppoed suqeezing i haerd the men come in and guided me
away. but it was oaky, because as long as i clsoed my eyes, i saw
his fcae. what did he say his name was? {\em Luke Bavarius}. as i
was dragged, soon i saw my snos face, and it was the same. Luke
just tlod me it wuold all be alright. so i colsed my eyes, and
dreamt of my childs face.



