\chapauth{Donde Esta}
\chapter{The Promise}


5 A.M. is a shitty time for burnt coffee.



As I, Luke Bavarious, stared in to my barren mug and gently touched
the still fresh wound on the side of my head, a reflection in the
still slick bottom forced a sob from the trenches of my gut.



It was him.



That night in the alley way, four sleepless and coffee spurn nights
ago, I saw something that can only be described as awful, and I
shot it. I shot it dead.



He came at me and he came at me hard, but Ol' Betsy finally
laid him to rest. As he slumped over my side, covered in warm
oozing liquid, I caught a reflection of something far worse than
the disfigured wretch I had just put down. It was him; the man of
my non-existent nightmares.



I caught his reflection in the broken glass and he was smiling,
smiling an unnatural and hideous grin. I was in no position to
defend myself. While I might be able to load a Beretta faster than
anyone else this side of the Hudson, being in his presence, time
seemed to slow to a halt.



His wild arms flapped about as if the cool alleyway breeze had been
given life. Entirely too tall and entirely too pale to be human,
only one thing came to mind: Slender Man.



Two weeks before that, I had gotten a call from an extremely upset
and distraught mother. She said that her son came home and he
wouldn't stop talking about how the ``Slender Man''
had just played with him and some of the other children at Bryant
Park just off of W 41st St.



Her son went on to tell her how ``Slendy'', as the boy
had nicknamed him, had taken a particular interest in Suzy Carlton.
He said that Slendy took her into the alleyway and she came back
with a strange purple mark on her arm. She thought it was awesome
and all the other children wanted one too, but Slendy said that
they would have to wait and that he, ``Would be back for
everyone!'' Her son was the only one who was scared of
him.



I scoffed at the lady and told her that I had more important things
to do than investigate some street performer handing out stickers
to children in the park. I didn't care if her kid got stiffed
a purple tattoo from some freak. I hung up on her.



I shouldn't have hung up on her.



As I laid in the street, looking at the piece of glass I was
terrified. Sobbing, making all the connections in my mind, I stared
at him. Stared into his devilish eyes, wondering what it was that
he wanted from me.



As he approached me, arms dangling all around, he bent down in a
way that a human should not be able to and stuck his face nearly an
inch from mine.



In that moment, the only thing I wished for was death; quick and
sudden death. Instead, the Slender Man would give me something much
worse: a promise.



He looked me in the eyes and with a smile he whispered in a voice
which came out in chortles, ``Don't
worry{\ldots}Bavarious{\ldots}I'll be back for you
too.'' It was a promise which kept me awake for four nights,
and a promise I expected him to keep.



Now, looking into my cup, I watched as he stood behind me. I did my
best not to show my fear.



I looked at the badge lying out on the table. A gold shield made of
brass and time. It wasn't much, just a symbol, but it gave me
the courage to speak.



``Mr. Slender, why'd you go after those children?''
I asked, trying to sound as calm as possible.



``The children give me{\ldots}'' it sounded now as if it
were trying to speak while a river of maple syrup ran through its
throat, ``{\ldots}they give me lifeeeeeee''.



``So why are you here{\ldots}Slendy?'' I asked
cautiously, doing my best to distract him while positioned my hand
on the holster under my robe.



``Little{\ldots}David Sanders{\ldots}didn't last very
long{\ldots}and his mother{\ldots}was{\ldots}lacking,'' he
said smugly.



``Well Slendy, that night in the alleyway, you should have
taken your chance because now I'm ready for you,'' I
barked, as I spun around and emptied a whole clip into his
chest.



He shrieked and recoiled as black, viscous liquid leaked out onto
my kitchen floor and ate away at it like acid.



With his defenses down I fought through the mess of flailing arms
and pistol whipped him with the still burning hot barrel of my
Berretta.



``You shouldn't have fucked with those kids, Slendy. You
shouldn't have fucked with Luke Bavarious,'' I yelled at
him.



He wasn't done. Despite my damage, he was still functioning,
though severely wounded.



``I'll be{\ldots}back
for{\ldots}you{\ldots}Bavarious,'' he coughed out, between
sputters of demon blood.



He dashed out the door and before I could get to it, the thing was
out of sight.



With a little boy's death that could have been prevented on
my conscience, I now know my purpose in life. If I had only
listened to him.



The Slender Man may have just made me a promise, but I'm
going to beat him to it. Luke Bavarious is now on the case. 

 






