\chapter{The Horrid Assignment}
\by{Dr.\ Mulholland}





Luke Bavarious walked through the front doors of the police
station. He pushed the doors open. Inside was his boss, Johnny
Zepeder.



``Bavarious!''

``What do you want Johnny.'' Bavarious said.

``I have a new assignement for you! I hope you will take this new
assignment!''



Luke Bavarious took the new assignment and opened the manilla
envellope like a kid ripping apart a Christmas present that the kid
had been waiting for. Inside the manilla envellope was a new
assignment: Kill the local mafia boss.



Bavarious looked up from his new assignment at his boss.
``Johnny.''



``What is it, Bavarious?''

``This doesn't sound like-{\ldots}''



Bavarious keeled over and from his mouth cascaded a river of vomit.
His eyes vomited tears too. The tears and vomit he was vomiting
pooled on the floor in a horrible cocktail of tears and
vomit.



``Bavarious!''



Bavarious could say nothing. The cocktail kept pouring out of his
mouth.



``Dear God, I'll get a doc-''



Johnny's neck exploded with blood vomiting out of the veins.
Bavarious screamed. He turned around and screamed again. He raised
his Baretta (all New York detectives have one.).



Bavarious turned around and looked at his boss. ``I'm quite sorry,''
Bavarious said. Johnny said ``you'd b-better b-be'' and belched out
one last spray of blood stained vomit. Bavarious turned and walked
out the doors, pushing the doors aside to get through.



Bavarious looked at his new assignment that he just got. Kill the
mob boss. But why? Bavarious was not a killer. He was a good man, a
good Christian man. But he has a Baretta. Barettas are for killing.
He must kill the boss. He grabbed his Baretta and loaded it and got
in his car and hit the gas.



Bavarious arrived at the mob boss's house. He got out of his car
and shut the door behind him and then locked it. He walked to the
front door and knocked on it three times. Then he realized. The
house had been abandoned since the horrid tragedy that had happened
there 50 years ago. He saw it in his mind{\ldots}



``Hi, Daddy'' said the kid. The kid smiled. Kids are so wonderful and
carefree in this terrible world.

``Hi there kiddo'' said the dad. The dad looked to be about 35 and
had a beer gut.

The dad turned around and walked out of the house, pushing the
door, opening it, and then pulling it, closing it. The kid turned
around and turned on the TV to get out of the horrors of this
wretched life. It was 1959. The kid just got the TV as a birthday
present. His birthday was yesterday.



The kid heard horrid noises from outside. He got up and opened the
door. His dad was lying on the ground with a silhouette on him. He
looked up at the man who was casting the silhouette. He had a can
of beer in his right hand and a Baretta in the other. Suddenly a
semi drove across their front lawn at the speed of fifty five miles
an hour, running the man and his dad over at the same time. Blood
vomited all over the front of the semi and all over the nice clean
green cut grass.





Bavarious woke up; he had fallen asleep. He had dreamed of what
happened in the mob bosses house 50 years ago. Then he realized. He
was the kid of his dreams. Bavarious let out a scream and turned
and ran and went out the front door. He tried to open the door on
his Ford Contour but it wouldn't open. Suddenly, a headless corpse
with a can of Coors walked across the lawn towards him. Getting
closer and closer. Bavarious screamed. He got out his Baretta and
fired. And fired again. The bullets punched bulletholes through his
rotting stinky flesh but they didn't hurt him.



Bavarious screamed and vomited again. The remainders of his lunch
floated around in a blood tinged mess all over his Ford Contour.
The Coors holding headless man kept getting closer. Bavarious could
only do one thing. This was the only option. His father would have
wanted it this way. He stuck the Baretta into his mouth and pulled
the trigger. But he had used all of his bullets. He vomited again,
pouring vomit down the barrel of his gun. He screamed. Finally the
Coors man was two feet away from him{\ldots}



``Luke Bavarious, why did you hate me?''

``Who, who are you?''

``I am an artist. I am the man who killed your father in a
semi.''

He screamed. 
 



