\chapauth{Dr Scoofles}
\chapter{The Long Finger of the Law}





``Listen sweetheart{\ldots}'' I lean back in my chair and slide my feet
onto my desk as I light the cigarette that hangs between my lips
``thats the fee, flat rate, take it or leave it!'' I squint my flinty
eye at the dame sat across the desk from me. Not bad looking,
blonde wig slightly off centre and a few gaps in her kisser but a
man like me can't afford to be picky. A man like me takes what he
can get in this hard cold world.

``Mr Bavarious, you know I'm desperate to get my hands on those
pictures!'' she whispers breathily. She leans forward and as I catch
a waft of her breath I lean back. I bet she wants these pictures,
and bad. I took them last week as she slipped out of her lovers
bed. Her husband would pay to see these. The question is will this
broad pay more? My name is Luke Bavarious and I'm a P.I. I don't
deal in honour and justice, I deal in the truth and the truth is a
mean cold hearted son of a bitch. The truth ruins lives and tears
families apart. I open my desk draw, the envelope with the pictures
sits nestled between my gun and my bourbon. I take out the bottle
and pour two drinks. She takes a drag on the cigarettes and
continues

``I have no money, but I'll do whatever it takes.''

I think about it for a second. I know what she means, women with no
money have one currency that is valuable to a rouge like me. My
eyes take her in, her yellow fingers, scrawny neck and sagging
bust. I decide a man like me can afford to be picky after
all.

``Sorry sweetheart, you better leave.'' I slam back the bourbon and
cock my finger towards the door ``don't let it hit you on the way
out, lady.''



I finish up the second drink and decide I better get around to the
dear husbands house before it gets too dark. No time like the
present to finish this dirty job and get my money. I slip on my
trusty overcoat, pocket the pictures and my gun then slip out the
back door.



Night drew in fast, wrapping itself around me like a dark cape. I
walk quickly, partly to keep the cold out and partly to give myself
some distance. I knew that broad would follow me. Women ain't
smart. I turned to look behind me, let her know I'm onto her game.
Thats when it comes upon me, so damn fast I don't get a chance to
pull my gun. I feel a hiss of breath in my face, I recognize the
foul stench from earlier as yellow fingers scrabble at my neck! I
drop down and kick out, I feel her knee snap and the bone saws its
way raggedly through her meaty flesh. Blood spatters onto my face
and pours into my mouth. I swallow it then vomit gushes from my
mouth, bloody vomit and bile gushes all over my coat and all over
the crazy broad as she scrambles on top of me. Her fingers seem to
grow longer, longer as they feel about my coat. My God, I look in
horror as I see her writhing about, her fingers several meters long
as they feel around inside my coat, searching for the pictures. Her
hands are now two elongated nightmares, the bones snapping and
crackling as they bend and scrape around my fighting body.
Revulsion overwhelms me, I gag and cough as I feel her bony fingers
scraping into my pocket. They withdraw the pictures and in a moment
tears them to shreds. As I black out the last sight I see is her
jaw unhinging as she leans in towards me, to deliver the final
deadly kiss.





Edit - Yeah I just realized I have omitted entirely the
disrespecting of the kids. I can only hold up the feeble defence
that the woman is most certainly being disrespected by our dashing
P.I and is also young (ahem). That'll teach Luke to respect those
slightly younger than him{\ldots} Ahh sorry  
 



