\chapauth{duck monster}
\chapter{Luke Kills An American}


Luke Barvarious stumbled into his classroom in Ho Chi Minh city.
Today they would be learning about the teachings of Chairman Mao,
the great Oarsman.



It was different here, ever since he was abandoned by his pot
smoking hippy father back in the 80s, nothing was the same as it
was back home.



And most of all he missed his father. Luke stayed up at night,
dreaming of the adventures through europe he took as a child with
his father, the musty streets of Spain, the wonderful aromas of
Paris, the cosmopolitain airs of venice. He enjoyed too the journey
through south east asia, visiting the big old temples and watching
father get blind drunk on Laotian rice wine.



But then one day father disappeared , and Luke was taken by the
police and given to a stern family in the Vietnamese communist
party. He tried to be a good son to his new family, but they would
never let him forget that he was from the people that had murdered
so many before.



And at school the children would taunt him, mocking his skin, his
eyes, his accent and his poor language skills. He couldn't remember
much of america, it was so long ago, but they'd never let him
forget he wasn't from here.



But one day Luke was walking into the local bar, where he was
earning some pocket money serving the Japanese businessmen and
local Communist party officials, when a white man called him
over.



``Hey kid, you look American. Wheres your folks?'', the man
said.



``Uh. I was orphaned and I live with a family here now.''



``Oh, thats too bad. Tell ya what kid, meet me after closing and
we'll have a talk about America!''



Lukes heart skipped. Maybe this kind man could tell him about the
land he could barely remember. Maybe this man could tell him what
happened to father.



Later that day Luke met the white man, and they went up to his
hotel room. The man showed him photos of Disney land, the white
house, and Luke marvelled at how rich and happy every one
seemed.



``If only..'' , he said, ``.. If only I had a way to get
there.''.



``Well son, I guess that'd cost money''.



``Yeah{\ldots} '' said luke.



``I know, I can give you money, but first you must do something for
me.''



The man hesitated then,



``Kid. Ever heard of a blowjob?''



With that , the man unclipped his belt, and his pants fell to his
feet. Luke immediately froze up. He might be a naive kid, but he
knew what this meant.



``{\bf Down down American pig! Down with imperialism! Down with yankee
perverts}'' Luke shouted as he stuck the man in the groin with his
fist and suddenly a team of Viet Cong burst into the room and
pumped the old pervert with lead.



As the man lied dying he looked up at luke and whispered ``I never
stopped loving you son.''. His eyes shed a tear, rolled back , and
he passed away.



Luke realised then, that America is the father of the world. But
now he was growing up, truly a child of vietnam. Having defeated
the Imperialist, the adults would surely respect and honor him now.

 




