\chapter{Untitled}
\by{fishguzzler}


Son of a bitch, there's a storm on --- no lightning, so I
do this little dance between the light switch and the bed, partly
because my room is just too dark, no light leaking in through the
levelors, and partly because I can't let my mom see the light
on when she trundles past for another batch of rainbow cookies
--- six neat little rows by five in the box, and four at a time
carefully arranged on a little white saucer-plate, and about a box
and a half gone by the end of the night, which means at least
eleven trips down the hall past my room to the kitchen on a night
when she's watching HBO in bed, pretty much every night
--- but mostly because there's a mad badger in my closet,
an evil monster with beady little eyes glowing faintly green.
Actually, I don't really know what `beady' means.
But I know what a monster is, even if, come to think of it, I
actually don't know what a badger looks like. But I imagine
it looks just like this little bastard in the closet. Maybe not so
mean.

I can hear the television from the next room, though the walls are
ancient and incredibly thick --- I once put my fist into one,
broke through the new plaster, and then through something brittle
and white, until I sliced my whole hand open on a rough mixture of
sand and antique horse-hair that exploded into powder even as it
broke my left pinky and the knuckle of my pointer finger. I can
hear the television because of the heating vent on the wall between
the closet and my bureau, which conducts the voices from the
television with perfect clarity into my room and provides me with
fair warning every time there's a commercial break.
That's when I make my move. I'm fifteen, and I may be a
little pudgy, or maybe a little more than a little, but I'm
extremely light-footed, so I leap down from the bed and tip-toe
sprint to the door as my mother's clomping footsteps
reverberate back and forth in my little acoustic capsule ---
it's not because she's monstrously overweight, though
she must have gained over two-hundred pounds in the last three
years, it's just that she's such a hard stepper. I fly
barefoot across mathematically smooth and cold wood flooring that,
I know, I wouldn't feel if I could really fly. I keep my eyes
trained on the door of the closet and flick off the light,
crouching with my left hand poised on the light switch and my right
hand gripping the doorknob, white-knuckled, the scar where I split
the shit open standing out whitest, crisp even in the
near-blackness as I glare past it into that shadowed crevice with
the mad chittering sounds coming from inside. But it always quiets
as she passes my door, as though it doesn't want to be heard;
I still don't know how she doesn't hear it through the
walls when she's in her room. Stupid old cow.

But tonight she's doing alright, I think, because she's
only made three trips down the hall to the kitchen, three trips
lasting three to five minutes each over the course of three hours,
which is a real record-low for her since things got bad, like maybe
now she's finally getting over it --- or maybe
she's just gotten too fat to walk and decided to start
bringing the box with her from now on. Either way, I've still
had to squat here three times so far in the dark, smelling that
musty yellow odor like rotten tomatoes mixed with, I don't
know, curry or something, listening to that thing cackle and
scratch at the back of the closet door, swinging it open millimeter
by millimeter, because I never dare to leave it closed ---
I'm too scared not to try and hear what he's doing in
there, plus I know perfectly well that he knows we both know that
he can open the fucking door if he wants to. I've seen him do
it, not in minute, scratching increments, but fast.

Tonight the door has stayed put, and I haven't heard a sound
from the little monster. Even his stink, the one everyone else
can't smell, seems to be receding. Normally it hits me at odd
points during the day because it's burned into my fucking
skin, but tonight it seems to be clearing away, the dissipating
pestilential fog.

I hear my mother put down her dish in the kitchen, but the cupboard
does not creak open. The sink splashes on instead, a sound I hear
more through the pipes in the walls than through the air. Is she
washing the dish already, packing it in, with so much less than a
box consumed? Maybe she is getting over it, at least realizing that
a box and a half of delicious rainbow cookies per evening
won't help --- but more likely, she's probably just
got a stomach virus or something. I hear her stomp into the
bathroom, even whistling the tune we all used to sing, ``Your
Face is All over the Place'', which is sung to the tune of
``Your Kiss is what I Miss''. I smile in the dark, no
fear now, thinking it's gone, and maybe this will be the time
it doesn't come back.

There is a muffled thud from the bathroom, and a short, sharp cry
from mom. It brings to mind an image of my mother, beached, prone
in her fuzzy white robe on the bathroom floor, writhing in pain and
as-yet half-realized fear, the muscles in her neck bulging, showing
clearly for the first time in almost two years, as that little
fucker chews through cotton and into her chest. Blood spattering.
Chimp-like, upright badger-monster body, head like a nasty little
dog, Chihuahua or something, only with a cerrated nose like an
alligator, or one of those colorful baboon-things. Snarling bubbles
into the blood welling through the shorn muscle and cracked bone of
her left breast like a child with his chocolate milk{\ldots} Chittering.
Laughing at us. Oh my god her heart.

Instead of flinging the door open and running to the bathroom, I
smack the light on and sprint to the closet door, throw it open and
freeze, staring right into those unforgiving dog-black but
compassionless spheres. So it rears before me, wipes it's
dripping chin with a bony little wrist. Cackles. Now you're
mother is dead too. First him, now her. First him, now her. 

 



