\chapter{I am {\bf not} Luke Bavarius}
\by{Funk In Shoe}


Interviewee: LARRY BAVARIUS - 05/05/09


So what do you want to know?


{\em Question.}


Okay, see, this is something we're going to have to address
before it starts bugging me: You need to relax.

I see you're tensing up there, a little already, why is this?
When we spoke on the phone earlier - when you called me up and
asked for this interview and I told you it would be no problem and
to come right over whenever you saw fit --- earlier you came
off so easy going, on the phone. I made coffee, did I not?

Is this just a matter of you being the kind of person who really
knows her way around a phone but tends to come off sort of skittish
in person? No? Could you put that down Bic pen already? You know
the clicking, and all. I get skittish, too. Honestly it's
alright.

You DO seem horribly tense. I am not, let me assure you, Mr. Ehl
Bee. There is no need to go all star struck on me. I am as much of
a nobody as you are, probably more of a nobody.

Put the pen down, honey --- in lieu of that, just stop with the
clicking, please. I'm sorry. Do carry on.



{\em Question}.



Well the thing is, the way you're phrasing that is you want
me to tell you a certain mapped set of details about myself;
details you're likely more acutely familiar with than I am
myself.

I don't know that I am related to Luke, as such. We
haven't had much to do with each other since he published
that{\ldots} Oh. Don't make that face.

Okay, okay. Fine. So I am. Related. He's what you'd
call my identical half brother. I know right? It's a weird
way to put it and I apologize; I'm not trying to come off as
overly dramatic here or trying to yank you around or make myself
appear interesting or anything like that, really, it's just a
sort of neat way of recapping our shared genealogy.

And so but yes, I am a couple of years older than Luke and yes, we
do share a good amount of absolutely top notch DNA. I've
never been able to figure out exactly how much, you know,
percentagewise et cetera, it's sort of a stupendously tricky
prospect.



{\em Question.}



Because we got, obviously, the same mom and but so, as fate would
have it, different dads. Tricky, because while my own dear sweet
padre is an entity completely separated from Luke's ditto,
they are, nonetheless, identical twins. This, their twin-inicity,
if you will, is what has made all my attempts at coming to terms
with the whole DNA snafu so far pretty frustrating. By now
I've pretty much just given up. This, having the same mother
and two different fathers who happen to be {\em appear} completely
identical, is probably also why you're still fidgeting with
that {\em God damned Bic}, even when I asked you politely and
repeatedly to put it down, because it's freaking me
out.

I am not-I-repeat-not Luke Bavarius; and I am going to take the
fact that you're still not quite sure whether to believe me
or not on that, as a compliment that I am looking better than my
usual best today.



{\em Question.}



Well because look at me. Check out thith. See thith? Ow. This is
what the not-so-PC-crowd calls a hare lip. It's been fixed
up, but it's pretty obvious with the scar and all, especially
on the inside of the lip. Did you ever see a jacket photo of our
boy Luke with a scar like this? This male pattern baldness thing?
Luke dodged that bullet too. Where I'm 5.0 he's a good
6.1. It's a mystery, really. You should{\ldots}



Question.



{\ldots}I'm not finished, you should see our respective
family photos. For some reason he just turned out like a late and
slightly improved version of yours truly. Same parents, just
slightly better. It's bizarre. By the looks of it it's
the same parents in the same photo studio, doing the same awkward
pose with our respective and identical dads in the background, arms
wrapped around mom, wearing all red. Bizarre because so the kid in
the foreground is basically either me or, like, a really, really
pretty and tall and attractive {\em enhancement}of me. It's
just weird. I am not Luke. Convinced? Want me to whip out the
photos? No?



{\em Question}



Well I'm two years older. Dad and Not-Dad moved here together
and started a used car dealership on the eastside. You are aware of
all this, I am sure. Any profiler worth her salt, writing for such
a major magazine, will be aware of this. So but they moved here,
yes, opened up their dealership and started making good money right
off the bat. It was a couple of years after the bubble burst and
Dad and his brother were lucky-slash-clever enough to start their
business at a time when people were just starting to make money
again, but were still hesitant about, you know, spending it.
Everybody and their mom bought used cars back in those days.

And so Dad meets our mom some forty-odd years ago and they fall in
love pretty quick and Dad moves out of whatever east side apartment
he's sharing with his brother at the time, and in with
mom.



{\em Question}.



From what I've been able to ascertain, I came around some two
years later. Give or take. You'll have to --- stop
clicking --- you'll have to bear with me on the details.
At this point, the dealership is running like greased clockwork and
both Dad and Not-Dad are pulling in some serious moolah and Dad,
Not-Dad and mom start getting invited to you know, get-togethers,
shindigs, box socials, that sort of jazz around town with the
movers and shakers of whatever post-recession high society was in
function back in those days.



{\em Question}.



Well it started out as a sort of joke, you know.
Don't-You-Drink-Too-Much-Sweetie-Or-You'll-Get-Us-Mixed
up. Shits and giggles and lots of fun at parties with my Dad and
his brother showing up in identical suits and my mom pretending to
accidentally kiss the wrong clone et cetera.

Shits and giggles right up until, and you've seen this
coming, right up until the three of them actually go and get so
drunk that my Dad passes out in a bathroom at some fundraiser,
slumped over a toilet for hours so that to this day he's got
horrible problems with his back, and Mom goes and sticks her tongue
down the throat of Not-Dad by mistake and by the time he gets to
object they're both too drunk to even care and mom decides
right there that for whatever reason, Not-Dad is a much better
kisser than poor, passed out Dad ever was.



{\em Question.}



I don't remember much, except for him drinking a whole lot
and never wearing anything but his underwear around the house,
really. And the yelling-slash-stomping.

I remember asking him, once, like we're talking age three or
four here, where Mom had gone and he yelled at me. My dad is sort
of a dick. I told him he needed to stop yelling at me. He
didn't listen. I told him kids need to be respected and
listened to. No dice.

He would have to be, a dick, you know, to stick me with the short
end of the DNA stick like he's done. Thith fucking thplith
lip! Ow!

And so but Mom moves in with Not-Dad and lo and fucking behold THEY
spawn a kid too.



{\em Question}.



Yes. Luke. I see you have fathomed the basic concept of
{\em listening}, I am highly impressed. May I continue? Thank
you.

So naturally, with my Mom gone off to shack up with his Brother,
there's no fucking way in hell Dad's dealership is going to
stay afloat, these two guys can't stand the sight of each
other.



{\em Question}.



Just {\em imagine} that! It's like some bizarro-universe
incarnation of self-loathing. Imagine waking up, hung over, and
stumbling into the bathroom, looking into the mirror and seeing the
face of the guy your wife is currently fucking, who is not you.
Then, suddenly, you are sobbing. One cannot even be-fucking-GIN to
fathom{\ldots}

So yeah, anyway, there was that.



{\em Question}.



Well so they split it up. Put down a fuck-all huge chain fence
right down the middle of the store and the lot. Split the whole
place in two halves that were pretty much identical except for the
sign out front. Dad got the BAVA half, Not-Dad got RIUS.

And, foreseeably, they started harassing each other pretty much
right off the bat. He'd bring me with him to work every now
and then. I'd hang around in the lot and play in the oldest
most derelict cars, the ones he couldn't seem to get rid of
anyway, and I'd watch Dad scream his lungs off, whenever a
potential customer went the ``wrong'', if you will, way
around the fence and into the RIUS-lot.



{\em Question}.



Just insane stuff; like he had this thing where he'd jump
onto the fence and hang there shaking it like a fucking deranged
chimp, rattling the metal, shouting how the guy who owned the
RIUS-lot was a no-good-for-nothing wife-stealer who also happened
to sell exceptionally horrible cars that no man with half a fucking
brain would ever want to et cetera et cetera.



{\em Question}.



Well Not-Dad would do the exact same routine whenever one went into
the BAVA lot. Sticks and stones. I'm not going to sit here and
assign blame.



{\em Question}.



She never came around. I haven't seen her since she walked
out. He did bring Luke a whole bunch of times though. We'd
play. In the beginning, we'd play. There was always this
acute{\ldots} weirdness about it. Playing with him. Like seeing
yourself in a funhouse mirror that somehow made you just an eerily
tiny bit prettier than you are. We had to stop when they put up the
actual WALL --- as in the brick wall.



{\em Question}.



They put it up in a moment of clarity I guess? Business had gone
way downhill for both of them, what with all the shouting and
fence-rattling and whathaveyou. It was sort of a necessity. They
even split the bill.



{\em Question}.



Ah well so but it didn't stop there. Because after the wall,
Dad got into this habit of sneaking into the RIUS-lot and greeting
customers like he owned the place; he might as well could have,
it's not like anybody could tell the difference.

So he'd sneak into the RIUS-lot and greet potential buyers
and just do a hell of a good job at being the very worst salesman
he could possibly be, to scare them off.

He'd make a show of keeping an open bottle of Jack on his person while
talking to customers, luridly coming on to any female buyers slash wives
slash children --- this earned him a couple of impressive beatings that
had him just look an AWFUL lot like the kind of person you would not buy
a car from --- he would follow the buyer around the RIUS-lot going ``oh
heavens no, you wouldn't want to buy {\em that}; two words: {\em death
  traps}'' et cetera --- until Not-Dad would finally spot him from
inside the dealership and coming rushing it, swearing and screaming,
effectively scaring off pretty much everybody.

Of course, after a week or so, Not-Dad would reciprocate by pulling
the exact same kinds of stunts at the BAVA-lot and for a while
there everything was absolutely, completely apeshit. Care for a
drink?



{\em Question}.



Well Dad started getting up early in the morning to beat Not-Dad to
work and lurk around Not-Dad's lot, impersonating him.
Not-Dad started doing the exact same thing. After a year or so, Dad
would clock in at Not-Dad's lot at seven in the morning and
visa versa. After a year and a half, they'd pretty much
swapped lots and spent most of their days scaring off the other's
half's customers. They stopped selling cars over the course of a
couple of months, in order to make sure the other didn't sell any
either.



{\em Question}.



Well they went bankrupt. Both of them, and spectacularly so.



{\em Question}.



And so Luke beat me to it, is the gist of my story. He wrote this
entire thing down faster and much more eloquently than I found
myself able to. And don't think I did not try. I tried. The
day I heard that he'd gotten published, I had two hundred and
fifty type-written pages and was just about to finish up my own
rendition.



{\em Question}.



Just another matter in which Luke Bavarius has proved to be that
teeny, tiny bit better than me, I am afraid. He's the genius,
he's the author. He's the one with his god damed
non-split face on the cover of dust-jackets everywhere. And so here
we are. And here {\em you} are. Digging up the dirt for your
fucking profile.



{\em Question}.



I don't even fucking care. You think I haven't told
this story? Who {\em told} you this story? Was it Luke? Mr. Ehl
Bee, mr. Writing-under-a-Pseudonym-to-be-artsy-Biddick, with his
prodigious talent and his intense, {\em fucking} eyebrows that he
probably picks like a bitch? Was it? It wasn't. It was me. I
want you to stand up, walk over to that bookshelf right there. Go
ahead. Pull out his book. It's right there. Don't think
I haven't bought it. I'm not your average bitter fucking
idiot. I have money to spend. Pull it out of the shelf and look at
him, on the dust jacket. Monochrome and unsplit, brooding. Go
ahead. It's me.

Am I not the butt of a cruel, genealogical joke? My father
abandoned by love. I myself abanoned by fate. You want horror? Look
at his picture, then at me.

Do you not see this? Has the whole god forsaken world gone mad? I
am telling you this story. I am the first incarnation of this
story. Who is this Luke Bavarius? Go head. Look at his picture.
Look at this Davidesque, seemingly retouched rendition of yours
truly. See all that is shared between us. Am I not the narrator? I
am L. Bavarius. Do I not deserve recognition? Look at his
face.

Pick it up. Go the fuck ahead. 
 






