\chapter{Invisible Monsters}
\by{Ghost Hat}




Nobody could see! Nobody could see! It was a nightmare. Abby ran
for her life, as hard as she possibly could. What else was there to
do when a monster was chasing you? Her lungs gasped for air already
and her limps burned with exhaustion, but that thing didn't even
breath hard.



It wasn't the monster chasing her that frightened her the most
though. It was the fact that she was the only one who could see
it.



Lurking about the corners. Hiding in the shadows. She thought it
was her imagination. She thought she had been going insane. They
said you showed the first signs of schi\-zo\-phre\-nia when you became a
teenager. But then, it must have slipped up, for she had seen it
squarely, with both eyes. What's more, it knew.



And then it gave chase.



Down the sidewalks, across the streets despite the busy roads. She
must have been nearly killed five times by squealing cars. She
barely kept herself from tripping several times down the steep
hills. And still it chased her, it seemed to like watching her run.
Enjoying itself perhaps. It loped in plain sight.



But only she saw! Only Abby saw the monster. Everybody else saw a
crazed girl running through the streets, no thought for her own or
others' safety. How did Abby know this? Nobody had believed her
when she said she was seeing things. Nobody screamed and ran
despite the fact a monster ran loose upon the same streets. Maybe
she {\em was} crazy, but she wasn't going to stop long enough to
find out.



How she wished she had paid better attention! Though even if
she had spotted the creature earlier she would not have known how
to defend herself against it. It had been following her for weeks
though. Weeks in which some shadowy thing had been watching her,
plotting against her{\ldots}



No time! Abby ran.



``You stupid kid!'' some guy screamed as Abby swerved past him. The
streets were full of people, making it hard for Abby to run at full
speed. She had to slow to dive and jump between and around them.
And there were carts everywhere. The beast! The beast was catching
up! Run! Run!



An alleyway. Not a place she would normally go. That's wear drug
addicts and homeless people hung out, but it meant there would be
no people. No people meant no obstacles. Abby ra! She ran down the
alleyway.



It took a moment for Abby to realize her mistakes. People might
have noticed if the monster had jumped her in front of them. Even
if they couldn't see it, they would see that something wrong with
her. With no people around, it could kill her in privacy. That was
her first mistake. The other was that this alley ended with a brick
wall. 10 feet high.



{\em Oh no,} Abby thought, gasping for breath so hard she couldn't
speak. She had enough to scream however. She felt the wind rushing
by as the monster swooped in on wings of black. So close now that
she could see purple in those leathery wings. So close she could
see its gleaming yellow eyes. No pupils. Just shimmering metallic
yellow.



It swooped in and landed with a great gust of wind on the cement
ground. It stood on two legs, like a man. But it was no man. Abby
was suddenly trapped between the brick wall and it. And then it
opened its mouth wide and inside it were hundreds of sharp, silver
teeth. It hissed and Abby screamed as it bent forth to devour
her.



Another rush of air, but from behind the creature. A sudden blur
and then the creature was on the ground, wings spread flat. It
screamed a terrible scream and Abby covered her ears in terror.
Animal instincts took over and she hid behind a dumpster, eyes
squeezed shut, hands clamped over ears. She would never leave this
place. She would stay, stay and hide forever.



She did not see what had overcome the creature. All a blur. She did
not see the man who had saved her until he tapped her on the
shoulder, and then pulled her out much to her horror. It had to be
that creature! That awful creature!



``Agggh!'' she screamed as loudly as she could. Abby writhed and
tried to break free, still blind. Still crazy. Still insane with
fear.



``Stop crying. You've been saved,'' said a voice. Abby
looked up, blinking heavy tears from her eyes, and found a man. An
ordinary man.



Abby was silent, just staring in disbelief. Just a man. And behind
him. Nothing. The creature was suddenly gone. As if it had never
been there in the first place. She panted, sweating, hair a mess,
skin as white as snow. Just a man. And yet. ''You saw it? You saw
it?" she hissed, horrified for what the answer could be.



``Of course I did,'' the man said in a voice as soothing
as butter. ``And it's gone now. It will never bother you
again.''



Abby gave a choke of laughter and could not help but hug the man,
her entire body trembling. The ordinary man reciprocated with one
arm, his other sliding towards his back pocket. He thought, in a
distant sort of way, that the child in his arms was warm. But the
blood from her throat would be warmer. 

 



