\chapauth{Ghost Hat}
\chapter{Character Sketch}



I frowned as I looked at the crime scene. The lawn had been well
kept once, but now it was all wild. The grass had been green once,
but now it was all brown from the blood. The blood was from a
corpse named James McDaniels. He was ten years old. He was murdered
here last week in front of his house. James McDaniels' father
had hired me to find out who killed his son{\ldots} or what.



My name is Luke Bavarius. I'm a private eye. I'm whom
they call when the police can't handle a case. Or if they
don't want to. This is one of those cases because James
McDaniels' father, James McDaniels Senior, is a crime boss
for the mafia and the cops don't like him. I don't like
him either, but I'm a desperate man.



I looked around and inspected the white chalk circles from where
his body was found. There were two. One for his body and one for
his head. The kid had been decapitated viciously. Just thinking
about it made me taste vomit in the back of my throat. At first the
police had suspected the kid's father. It makes sense. The
crime boss's case of alcoholism was publicly known. But he
had an alibi in his frightened wife and anyways it didn't
make sense since he hired me to investigate his son's murder.
A guilty man wouldn't do that.



It might have been a rival gang, or even a cop trying to get back
at McDaniels Senior, but I didn't think so. The crime was too
violent. The force used to tear off the kid's head, the
distance it had been thrown, the amount of blood{\ldots} it had to
be personal.



I didn't like to think that another kid could do this. I
didn't even know how since to rip even a kid's head off
you would need at least the strength of a gorilla. But I
couldn't dismiss a lead until I followed up on it. An
investigator follows his instincts and mine said I was on to
something fishy here.



At the school I questioned everybody. Everybody who could have had
contact with James McDaniels. As I talked to more and more people,
I started to draw a picture in my head. The picture was one of
James McDaniels, and soon the picture got more and more detailed.
He was sent to the principal a lot because he picked on other kids.
He would torture, beat, and steal from anyone smaller than him. He
was a bully of the worse kind, just like his dad. I guess
it's true that the apple really doesn't fall far from
the tree.



``Is there anybody James really picked on? More than everybody
else?'' I asked a little boy during lunch. He was maybe a
third grader, and he didn't seem too unhappy about his late
tormenter being dead. Who could blame him.



The boy looked thoughtful for a moment and then pointed to a dark
corner in the cafeteria. He said with a mouthful of hamburger,
``Tommy. James hated Tommy because Tommy was never afraid of
him.''



I thanked him gratefully and looked over in the corner. A boy was
there and it was strange. Every other kid here was eating lunch and
laughing with each other. But not this kid. Not Tommy. He was alone
and hunched obsessively over a bunch of papers. I think he was
drawing, though I couldn't see what from here. I knew I had
to talk to this kid.



``Hey Tommy, what are you drawing?'' I asked carefully,
sneaking a peek at his masterpiece. It was a picture of the
cafeteria and all the kids in it. I figured it'd be a
child-like scribble, the sort of stuff normal kids do, but I was
surprised to see that it was pretty good. ``Hey, you're
better than I am,'' I joked.



``It's just practice,'' Tommy mumbled, covering the drawing with his
hands. He looked away from me and stared hard at the wall.



I paused hesitantly. I don't talk to lots of kids in this
line of work, but I knew that I had to try. ``Tommy, I need to
talk to you about James McDaniels, okay? I'm trying to catch
the guy who murdered him, and I need a big guy like you to help
me.''



Suddenly the school bell rang and all the kids got up to leave.
Tommy shot up like the red plastic of the kid's chair he sat
on had burned him. He grabbed his backpack. ``What can I do?
I'm just a kid,'' he snarled angrily as he shoved past
me, rushing off to math class.



I blinked as I watched him go, and then I squinted down at the
papers he had left. He was going to be in a lot of trouble if any
of this was homework, but as I pushed the papers around I saw that
there weren't any words on them, just drawings. Some were of
nice things, but most of them were grotesque and disgusting, blood,
flesh, and vomit so realistic it turned my stomach. One of them
caught my eye in particular and I picked it up.



It was a creature all shadowy and dark. Its tail looked vicious and
I could feel the terrible expression on its face in my very soul.
But what caught my eye the most was the head it held in its hand. I
recognized that head. I recognized the house behind it. It was
James McDaniels' head and that was his house too!



That night I staked out Tommy's house. The sky was as stormy
as my mood. The clouds turned and swirled around as viciously as
the insides of my stomach. Even the lightning made me feel like
vomiting, but I smoked a Marlboro instead. It calmed me down enough
to think. I didn't know how, but I knew that Tommy was a
murderer. I needed to prove it somehow and get him put away, maybe
put away for life.



The broken clock radio flashed 12:00 A.M. in glowing green light.
All the lights in Tommy's house were off. Strange kid. All
alone, but he ain't scared of the dark. Tommy's parents
had gone off to a fancy party hours ago. Tommy's dad wore a
tux and his mom, a nice looking dame, wore a sleek little number. I
didn't expect them back any time soon.



The rain pattered on the top of my beat-up Oldsmobile like hundreds
of little mice feet. The lightning flashed and Tommy's house
was lit up in black and white, like some old horror movie. I
wasn't scared, but I reached inside my jacket and stroked my
Beretta. Thunder grumbled like a monster, a hungry one at that. My
imagination went a little wild as I thought of all those pictures
Tommy drew. That kid could draw all right.



The rain kept pattering away. Pattering away like thousands of
little mice feet now. But suddenly, with a loud thump, something
huge landed on the roof! It shook the car and I bounced inside and
looked up in surprise. The surprise turned to horror as I saw a
huge indentation above me. That was no mouse! No, I doubted it was
even a really big rat!



I pulled out my loaded Beretta and aimed at the roof above me and
fired three rounds in quick succession. I know I missed it though
because I felt the thing leap off the roof and land on the street
outside the car. Nothing but rain came through the holes, good news
for my seat cushions but I wouldn't have minded the cleaning
bill. It was too dark with night and rain to see outside the
window, so I opened the car door and leapt outside, squeezing my
pistol blindly into the air. The thunder cracked then, even louder
than my gunshots and I heard a scream louder than them both
combined.



I peered into the wetness and saw a dark figure clutching at the
side of its neck. Thick black blood oozed from between its fingers
and as it screamed again, more vomited from the creature's
mouth. I moved closer, clutching my Beretta with white knuckles. I
was staring at the creature's head, but I realized what a
mistake that was when I recognized that horrid expression on the
monster's grimacing face.



I leapt back. Just in time as a whip, faster than a speeding semi,
struck right where my skull would have been. It was the
creature's tail. This thing. This man that was more monster
than human was the beast from Tommy's drawing. My brain was
struck with awe, but luckily my hands didn't care about what
my brain thought. My fingers squeezed at the Beretta's
trigger over and over again, filling the creature full of holes.
Black blood sprayed out from all over the creature's body,
mixing with the pure rain, like mixing demon urine with holy
water.



The creature gave one last angry garble as it lurched towards me. I
could have sworn it said something in English but I don't
know what. My brain was on automatic as I fired my semi-automatic,
the barrel spewing out bullet after bullet. Finally the beast
staggered and collapsed, right at my feet. Its tail gave one last
feeble lash and subsided. Up close I could see how truly hideous it
really was, with pulsing black veins and oozing pustules all over
its body. I licked my lips and tasted salt, which surprised me
since rainwater is fresh. I was crying.



I knew I couldn't stop now. My hands shook with the
nervousness I had felt from the assault of Tommy's monster,
but I reminded myself of whom I was. I was Luke Bevarious. I was a
private investigator. I had faced down lots of tougher situations
than some kid with a coloring book.



I went inside the house. It was much quieter inside the house than
it was outside. The water dripping off my coat sounded loud in my
ears as I went from room to room, searching for the boy I knew must
be there. Finally I found him.



It must have been his bedroom. I spotted a bed and dresser out of
the corner of my eye, but mostly I saw the drawings. Hundreds and
hundreds of drawings stuck all over the walls and the ceiling, the
floor and every bit of furniture. And in the middle of the floor
was Tommy. He sat beside a flickering candle and didn't
bother to look up at me when I opened the door.



Tommy was drawing.



``Put down the pencil,'' I said, my voice sounding harsh
and gravelly. ``I got a pistol pointed at your head, boy. My
fingers have minds of their own sometimes, I can't promise
anything if you don't.''



``You're just in time,'' Tommy said with a soft
smile. I was surprised when he did what I told him to do, tossing
the pencil playfully off to the side. But something was off. His
smile was more than just a regular kid's smile. My eyes
widened in horror as I bolted forward and snatched up the
just-finished drawing. I gazed at it with terror as I turned around
to face the door I had just used.



Yes, it was just like the drawing. The kid was good. Really
good.



The End.
 



