\chapauth{gigz}
\chapter{What Went Wrong}



There is blood everywhere. My clothes are drenched with it, my
hands slippery. I look down at the dead body of Mrs. Trencher, her
throat still gurgling as she gasps for a final breath. The pencil
in my hand is a dark crimson. Slowly beads of her blood fall to the
already massive pool of blood on the floor. I look up and see that
everyone is staring in horror. It then occurs to me that I am
laughing harder than I ever have in my life.

Flash.

I wake up with a start, scared out of my mind. I am gripping my
pencil so hard I can hear the cheap wood start to splinter. It was
a dream. That's all it was. Hell of a dream though. My name
is Luke Bavarious. I am seventeen years old, and a senior in high
school. I am not shut-in, I am not excluded by my peers, and I am
not ridiculed and mocked. Frankly, people just like me and I get
along with everybody. I think something has happened to me. I just
have no idea what.

Mrs. Trencher is my English Literature professor. I have never
harbored any sort of ill-will towards her. Her tests can be a
bitch, but she is not a disagreeable person. Her classroom habits
don't evoke the anger of any student. She is all-around well
liked and respected. She gives us candy when we study for tests as
a class. She gives us candy when we aren't studying.

There is no reason that dream should have happened. I got plenty of
sleep last night. I wasn't up late, and I fell asleep right
away. I woke up on time, I had a bowl of cereal and a glass of
orange juice, and I made it to school without being rushed.

It's 11:32. Class is continuing as normal, and Mrs. Tren\-cher
didn't notice me sleeping. Then again, she is the type of
professor that continues on with her lesson with, or without, your
participation. If you miss the material, it is your own fault. I
shake my head and continue copying her lecture notes into my
notebook. At this point, I have zoned out and am copying the notes
without paying any attention to what they are. I'll read them
over lunch, so I at least know what she is talking about.

``The elements of gothic fiction are easy to identify. In
almost all of them, a woman is trapped in a circumstance she cannot
escape from. This is usually a house. She has little time before
she suffers `a fate worse than death.' There is
something or someone keeping her in the house, by means of force or
obligation. Somewhere in the text, her savior will enter the house,
learn of the situation and save her from that Hellish
fate.''



Flash.



I look up from my notebook, and see the blonde pony-tail of the
classmate in front of me. With my face torn in a bloodthirsty rage,
I reach forward and grab a hold of it. I yank it back towards me,
her face now staring at the ceiling in pain and confusion. Without
a word, I lunge forward and plunge my pencil deep into her left
eye. She screams. I scream. She is screaming from the pain, I am
screaming because I am delighted. I twist the pencil deeper into
her eye-socket. She convulses, and I hold fast. I stand up, leaving
Jenny to writhe in her chair. I look at my hand. I slowly drag my
tongue across my middle finger, savoring the taste of her
blood.

I laugh harder than I have ever laughed in my life.



Flash.



I wake up on the floor next to my desk, tears stinging my eyes.
Everyone is crowded around me; Mrs. Trencher has sent Jenny off for
the nurse. Her eye is fine. I look up at the concerned faces
hovering over me.

``I'm fine; really{\ldots}I've just been feeling a
little ill. That's all.'' The words have to be choked
out through the tears. I try to stand, only to find a hand on my
shoulder, keeping me at my position on the ground.

``Francis, are you sure you're okay? You shouldn't
try to move. Jenny went to get the nurse, just sit tight.''
Mrs. Trencher's voice is thick with worry. She was one of the
few who cared about her students. For a split second, at the
mention of Jenny's name, I had the image of my pencil twisted
deep into her cornea. I almost throw-up.

``N-no, I'm okay, really{\ldots}''I pull myself to
my feet, using my desk as a crutch. I'm not really okay as I
say I am. I am unsure on my feet, and my vision is blurry.
Everything is swimming, but at least there isn't any blood. I
look around at my classmates; every one of them is staring at me
horrified. I'm not the first person to faint in class.
Melissa did two weeks ago in Biology. We were dissecting frogs, and
she is squeamish. As it turns out, I had screamed in absolute
terror, fallen out of my desk, and laid on the floor convulsing in
tears.

Jenny walks through the classroom door, a very scared looking Ms.
Surough, the school nurse, in tow. I look up at Jenny, tears still
fresh in my eyes. Ms. Surough sets an arm around my shoulders and
leads me out of the room. I numbly follow her direction towards the
nurse's office. Something is wrong with me, and I don't
know what.

Ms. Surough tells me to lie down on the couch in her office. I
happily oblige.

``So, what happened, Francis? Are you okay?'' Her voice
stays level, but you can tell she is concerned. You can see it in
her eyes. The only thing I can think of when I look at her is the
image of my brutally attacking Jenny. What the fuck is
happening?

``I'm fine, really. I just think I'm
overtired{\ldots}I didn't eat this morning. I think
that's it. Just overtired and a little stressed from work.
Really, I'm okay.'' I'm trying to convince myself
more so than Ms. Surough.

That's it, really. I'm just stressed from work. I guess
I did go to bed too late, and didn't eat enough for
breakfast. I'm okay. Really, I'm O.K.

I am O.K. 
 



