\chapauth{Hamelin}
\chapter{The Painter}





The boy who wanted to be a painter stared at his canvas. His canvas
was blank and it stared back at him. He had many other blank
canvasses and they also stared at him. All the big squares of white
were empty like his mind. He could think of nothing to paint onto
the canvas. It drove him crazy. He would never be popular if he had
nothing but blank canvasses! All of his friends told him that he
would never be a painter. He knew he would show them.



Since there were no ideas in his head the wannabe painter put on
his jacket and went to the art museum. There were a lot of
paintings at the art museum. The difference between these paintings
and his were that these paintings existed and his didn't.

``I wish I could paint paintings like these!'' The boy said out loud
to no one.

``Paintings like these huh?'' A tall shadow suddenly appeared over
the boy's head.

``Would you like to have paintings like these in this museum?'' The
shadow continued.

The boy spun around and standing there blocking light was a tall
gentleman. He was wearing a black overcoat over a black suit. The
gentleman smiled.

``Yes! Yes I would! Can you help?'' The desperate wanna be painter
clapped his hands together with joy.

From the gentleman's overcoat the gentleman grabbed a small wooden
box and handed it over. The box was made of dark wood and was very
smooth.

``Take this box home, what is in it will help you put everything
onto your canvas.''

``Really? Thank you sir!'' The boy jumped up and down
with joy.

The tall gentleman walked away without another word.



Before he knew it the boy was home again. He locked the door and
excitedly opened the box. Inside the box was a paintbrush. The boy
took the paintbrush into his hand and it gave him an idea. He
started to paint. He painted and painted. The sun went down while
he painted, the sun came up and he was still painting. He painted
on every single canvas in his home until he could paint no
more.



Days passed and no one heard anything from the painter. He didn't
show up to school. No one saw him at the park. After a week a group
of his friends broke into his house. They wanted to know if the boy
was ok. What they saw when they broke down the door were hundreds
of canvasses in an empty house. Paintings of furniture, paintings
of household objects, paintings of carpets, paintings of his
parents. Paintings of everything that would be in a house but none
of those things. As they dug through house they found the painter's
last painting sitting on his easel. It was a painting of the
painter himself.



Most of the paintings were put in the art museum. Everyone in the
town was impressed by the paintings. Everyone wanted to meet the
boy who painted all the amazing paintings. They would ask the
museum employees about him. They would only say that no one knew
where he was. They only found his paintings in his house. 

 



