\chapter{I, Lucius Baiuvarius}
\by{Hantu}


It is mid winter in the year 177 of the Christian god. As I write
this, I, Lucius, son of Baiuvarius of Aalen am recovering from my
injuries. My grandfather and his father before him fought against
the Romans and their foreign ways. Both of them are long dead,
slain by Roman sword. My father was no warrior. He is a herder and
did his best to bring me up in the Roman ways so that I might
ingrain myself with the Romans and profit by it. Yet the warrior
blood runs deep. On my 17th birthday, I said goodbye to my family
and travelled to the new Roman fort of Castra Regina. There I
joined a ragtag unit of foederatus, made up of people of many
tribes.



My company consisted of 20 men, only a few I made friends with. We
were employed as light infantry or as Uhlan, my Swabian commander
calls it, arrow fodder for the Legio Tertia Italica against the
rebellious Marcomanni tribes. The pay was not much, but my youthful
adventurism was satiated. In my fifth year of service, I have been
in many battles. Many we won, others we lost. I have seen acts of
extreme bravery, worthy of the old gods. I have also seen villages
burned to the ground, the women raped, the men beheaded, the
children enslaved. Yet what I saw during my last encounter was
beyond anything a mortal should see.



It was two months ago. The first flakes of snow had fallen. The
campaigning season was over and I looked forward to a few months of
rest. I was sitting by the campfire with several others when a
legionnaire guard came to our encampment and talked to Uhlan. They
were out of earshot but I saw him gave Uhlan a piece of scroll and
left. Uhlan shook his head and walked towards us. ``By Belenus
and Camulus!'' he swore, ``A Roman patrol is lost in the
Black Marshes and we are to look for them.'' He spat on the
ground and swore again. ``It's not enough that we fight
and die for them, now we have to baby sit them too! Lucius, Hauff,
and Dumnorix, pack your gear and come with me. We will have to go
on foot as the ground is too rough.''



I reluctantly moved away from the comfortable fire and found my
longsword, leather armour and metal helmet. For some reason, I also
decided to bring along my long knife that I don't usually
carry on missions. I tied the knife in its scabbard around my torso
and put on my leather armour. This decision will end up saving my
life. Our small band of four sets out of the camp just as the
snowfall was beginning to get heavy. We made slow progress, even on
the Roman roads. After 2 days, we arrived at the edges of the Black
Marshes, tired and cold. Uhlan was unusually taciturn during the
journey. He was not a jocular man by any means but he seems to be
even more troubled than usual. Finally, I decided to ask him what
it is that's troubling him. He fell silent, only the
condensation from his breathing betraying his thoughts. ``Do
you know anything about the Black Marshes lad?'' he finally
spoke. I replied in the negative. ``The locals stayed away
from this place and for a good reason. None who ventured in ever
came out again. Those Roman fools are too arrogant to believe in
folk tales and look what happened to them. Yet here we are, on a
fool's errand. May Belenus protect us all.''



We camped in a clearing near the Black Marshes for a day while
Dumnorix and I scouted around for tracks. The fresh snow made this
task even more difficult. The afternoon sun was falling when out of
the corner of my eyes, I saw a glint of metal among the bushes, 20
yards away. I silently signalled to Dumnorix to come near and we
cautiously moved towards it, swords drawn. There is no doubt about
it. It is a Roman scutum, cleaved in half, not cleanly like by an
axe or sword but as if it was ripped into two by some great force.
On the ground, there were drag marks and copious blood and it let
deeper into the Black Marshes. I debated with Dumnorix about what
to do next. The Helvetian wants to follow the tracks into the marsh
before the snow completely covered it while I wanted to report our
discovery to Uhlan. We argued for a while until we decided on a
compromise. We will follow the tracks a little deeper until dusk
falls and then turn back.



The both of us cautiously moved into the marshes. Why I agreed to
this, I never knew. Every ten yards or so, I broke a twig and
pointed it towards the direction that we came. After an hour or
walking, we came to a small cave where the tracks and blood trail
thinned out suddenly. The sun was setting rapidly and an ominous
hush descended on the Black Marshes. I told Dumnorix that this is
as far as I will go and we should turn back before it gets too
dark. He agreed though he wanted to mark the location first. We
looked around in search of a large rock or stick that we can use as
a marker when the wind suddenly picked up. I was digging through
the snow cover when Dumnorix gave a sudden shout. I looked back but
he was no longer there. Snow was now being blown sideways and
quickly, I could see no further than my hands. I shouted for
Dumnorix many times but there was no reply, only the howling of the
wind. I clutched my longsword tightly and readied for battle.
Warily, I crouched towards the small cave to seek shelter from the
storm, my senses on alert for trouble.



The cave entrance was about 7 foot high and just wide enough to let
two man through. The surface was covered in lichen and the dank air
smelled of rotten vegetation or worse things. Inside was pitch
black with pools of stagnant water looking like broken shards of
mirrors. I hesitated but staying out here meant certain death by
freezing. Muttering a prayer to Lovantucarus, I went into the cave,
my trusty longsword drawn at the front. The howling of the wind
took on a haunting aspect in the cave, as if thousands of lost
souls whispering together. The hairs on my neck pricked up while my
heart was beating loudly in my ears. I could no longer see
anything, only vague shadows. A movement! Where? Was it my
imagination? Calm down. Trust my instincts. Another movement, this
time, closer! There is no more doubt. Someone or something is here
in the cave with me. ``Come out and show your self!'' I
yelled into the darkness. ``Come out you coward and fight like
a man!''



A sudden rush of air smelling of carrion and an inhuman growl went
directly towards my face. I instinctively crouched but something
hit hard on my right shoulder, just missing my head, causing me to
fall and end up face down on the damp cave floor. My sense of
direction is now gone. In the commotion, I lost grip of my
longsword. I grabbed my right shoulder and it was bleeding
profusely. My leather armour torn in pieces. I've had enough.
I tried to scramble up and run but a vaguely man-shaped thing
pounced on my torso pushing me down again with great force while
shredding at my chest. I nearly passed out from the impact but I
called upon strength buried deep inside me, the strength of a
cornered animal and flailed at my attacker with my fists. I must
have landed a lucky hit, as the thing jumped off and howled.
Remembering my hidden long knife, I tore away the shredded remnants
of my leather armour and unsheathed the knife. The thing lunged
again with an ear piercing shriek but this time I was ready. I
waited to the last second before, with a rapid thrust, I stabbed
the thing in its chest. My knife made contact and hot blood spewed
on my face.





The full moon was probably out now and dim light reflecting on the
pools of water lit up the scene. For the first time, inches from my
face, I could see my assailant. The horror that I saw could never
be truly described. It was vaguely human but where the eyes should
be, there were only blood soaked sockets. Hot carrion stench
emanated from the mucus filled holes where the nose should have
been and the face was also covered with leprous purple scars. There
were no lips, only a gaping putrid mouth dripping with venomous
saliva. I let out a scream of horror and kicked the thing away. The
thing was breathing heavily and so was I. It clutched at its chest
where the knife was stuck while blood sputtered from its mouth. I
saw my longsword lying on the cave floor and quickly picked it up.
I cautiously advanced towards the prone creature when with a
gurgling voice, it spoke. `` You have beaten me but I lay a
curse on your sons and their sons for eternity. Once every
generation, they will face a horrid enemy and that enemy will be
themselves!'' At the final word, it let out a final putrid
breath and ceased moving.



I slumped on the ground and stared at the corpse. I must have
stayed that way for an eternity when the pain of my injuries
reasserted. I crawled my way towards the cave entrance, trying to
understand what had happened. I was almost out of the cave when I
caught my reflection in a pool of water. Suddenly I was sobbing. 

 



