\chapauth{HastyDeparture}
\chapter{A Red Sky at Night}


The sun slowly sinks in the sky, an orange halo telling of the the
morrow's forecast. The forecast is always the same.



The forecast never changes, not for me, at least. Every day, I rise
with the sun, and step out the door of my small ranch-style home as
the sun clears the trees of my small suburban neighborhood. Every
day, I grab a large, black coffee and the morning paper from the
gas station on the corner. Every day, I park my black and white in
the side lot of Lakeview Central High School. Every day, I sit down
at my desk as Connie waltzes in the door, says, ``morning, Officer
Bavarious'', and moseys on over to the copy machine.



My name is Luke Bavarious, and I am a School Resource Officer. I'm
a cop in a high school. I wear a badge, I carry a Beretta, and I
don't take shit from anyone, especially not people half my
size.



They said that the regular doughnut-munchers weren't close enough
to the people, not tied-in with the community, and unfamiliar with
the hooligans in our fair town. They said that we needed someone to
fill that role, to keep tabs on the kids, to keep our children in
school and out of trouble. That's where I come in. I deal with the
kids who have a streak, and who, without help, are likely to become
the next generation of scum that plagues our streets. I keep the
peace; I enforce the law.



I know all the bad seeds, the troubled families, the broken homes.
I get to know them, I lend them a hand, and I set them straight. I
know them all like family. So when a young voice says ``hey, Officer
B'' as I'm looking out the window at the setting sun, it's no
surprise that I know who it is before I turn to face the teenage
boy in a hoodie and baggy jeans.



``Hello, Marcus. How was your day today? You go to class?''

``Of course, Officer B. You know me.''

``I know I know you. That's why I'm asking. You go to every
one?''

``Yes, Officer.''



Marcus was a good kid with a bad streak. I've known him since he
moved here his freshman year of high school. He moved out of a
trailer park with his mom and younger sister to avoid their
drunken, estranged husband. A rough upbringing; not uncommon. He's
got a record like many of the others I've helped, ranging from
little things like skipped classes and tardiness to a few more
serious infractions involving alchohol and marijuana. The same old,
tired shit. But he's been getting better.



``That's good, kiddo. That's good. You heading home? You know
nobody's supposed to be in the school this late. You gotta study
for those tests next week.''

``Well, you see{\ldots} I was wondering if you could, uh{\ldots} come look at
something.''

``What is it? You getting into trouble again?''

``I don't know, Officer B. That's what I want to you come
see.''



I look back out at the flaming ball in the sky, and remember that
even though my day is coming to a close, my job never ends.



``OK, Marcus. Show me.'' He nods solemnly. We walk out the door of my
office.



In silence, he leads me down the hall to the right, and up the
stairs to the second floor. We make a left, and start down the next
hallway. Marcus jogs ahead, and stops when he gets to the boys'
bathroom halfway down on the left. ``In here,'' he mumbles, almost
inaudibly. He goes in.



I step up to the door, held open from the inside by a beat-up
garbage can. It's almost pitch black inside; the lights are
out.



``Marcus?'' No answer. ``Marcus? You in here?''



A chill creeps up my spine, an unwelcome feeling that's all too
familiar for someone in my line of work.



I step into the shadows, and undo the strap on my holster. I hope
I'm just being paranoid, just feeling a little scared, but I know
it's not true. The door suddenly swings shut with a slam, and the
world as I know it is plunged into darkness. In an instant, I'm
gripping the Beretta tight in my sweaty hands; exactly the last
thing I want to have to do.



``What's going on, Marcus?'' I call out. The void answers, ``What's
going on, Marcus?'' It sounds just like my voice; an echo. A soft
sound appends the response; a shoe scraping the floor in the dark.
My eyes slowly adjust to the dark, and I notice a small window on
the far wall, just below the ceiling. The faint light coming
through reflects off something to my right - mirrors above the
dirty sinks. Another noise; my eyes dart back to the left.



I should have seen it coming, but it's too late; I feel the breath
in my lungs explode. I'm slammed into the nearest mirror. The glass
cracks, and so does my skull. I push away from the wall, repulsing
the weight of two, maybe three kids. I should have known. The
weight shifts, and my body hits the opposite wall and the urinals.
The nasty water splashes across my hands and stomach. Disgusting. I
turn away from the wall, to face the kids. Disgusting. The weight
hits my stomach, shots ring out in the darkness, and my breath
bursts forth like doves from a magician's hat. I'm no
magician.



I drop to one knee, my head turns toward the mirrors above the
brown stained sinks, and in an instant, I see all those young faces
I've helped staring back at me, their faces blank, emotionless. I
collapse on the floor.



As I lay on the cold, damp tile, I can see out the window. The sun
slowly dips below the horizon, painting luscious red streaks across
the sky. Red streaks the color of blood. Red streaks like the ones
painted across the walls of the boys' bathroom on the second
floor.





e: As I wrote it, the story drifted away from the theme, but that's
what happens. I'm sticking to it. 
 






