\chapter{Kindness of Strangers}
\by{Helmet}


Luke Bavarious was driving his squad car on Old Pine Road. A little
while ago, he had given an important lecture on drug abuse at the
local Middle School. Then he saw it: a black car parked in a field
where cars had no business being. He stopped. He walked over to
investigate. The black car had crashed into a huge, unforgiving
pine tree! Pine cones littered the ground like corpses after a
massacre. From the shadowy wreckage emitted a small voice. A
child's voice. ``Help me-e,'' it begged.



Under his bullet-proof vest, Luke felt his guts tie in a series of
knots, each more complicated and painful than the last. ``Dear
God, not a child,'' he whispered. Around the car a moat was
forming of gasoline, battery acid and blood. Luke Bavarious blinked
back tears and inched forward.



Inside the car was a man, dead at the wheel. An empty whiskey
bottle sat in the cup holder. Blood was everywhere. During impact,
the steering wheel had pushed through the man's mouth,
decapitated his tongue and snapped his spine like a \#2 pencil. Luke
looked away to keep from vomiting forth the complimentary meal he
had received in the school cafeteria.



That's when Luke noticed the boy buckled in the back seat.
Possibly a seventh-grader, judging by his size. ``Dad, are you
okay? I told you not to drive drunk,'' the boy said.



Luke stared. Perspiration sweated from his face. The boy's
eyes were gone, long gone, having catapulted from their sockets by
the car's sudden stop and the tendency of objects in motion
to stay in motion. The boy wept tears of blood from his disfigured
face. Luke now observed two splattered milky blobs oozing down the
front windshield like two unholy eggs from the bowels of
Hell.



Afflicted with overwhelming instant insanity, Luke placed his
Beretta to his own temple and pulled the trigger. Nothing happened!
He looked at his firearm and realized the safety was on. Bavarious
giggled madly and flicked the safety off, then common sense
returned to his disturbed mind. ``Poor little fella,'' he
muttered between clenched teeth.



``Is somebody there?'' the boy asked. ``Will you
h-help me?''



Luke fired one bullet, doing the job. 

 






