\chapter{The Last Case}
\by{henpod}

Detective Luke Bavarious woke with a snort. Today was the day, the
case to end all cases. This case would be the biggest one he had
ever undertaken and the thought made him nauseous. It had to be
done, It will be done.



He staggered off the urine stained mattress, his foot stepping in
something soft and rust coloured but he didn't care. He was
thirsty, but not thirsty for water, he walked over to his table and
grabbed the bottle of whiskey. He spun the top and swallowed the
horrid cocktail of whiskey and cigarette butts; he began to choke
but welcomed the sensation. It was good to feel something for
once.



His bloodshot eye saw something glint under an old T-bone. He
picked it up and wiped off the grease. It was his badge. It read
``Detective''.

``More like defective'' he muttered to himself and began
a horrible, scratchy giggle which began to get louder and louder,
like a washing machine in a dank, dirty laundrette. His laughter
stopped when he saw his reflection in the dusty mirror. What was
once a handsome chiselled face looked back at him with empty eyes
and a patchy beard like that of a rapist. He began to cry, the
tears ejected from his eyes like the cartridges from his berretta.
The berretta! He grabbed it, and put it to his head, pulling the
trigger. An empty click echoed through the empty room.



``No, not yet. One last case. The Mad Cannibal is still out
there, eating children, I must stop him.''



Ever since the incident in the alley, he was a changed man. He
wanted to die, and had been ready to, but then the Mad Cannibal
began his horrid campaign of terror and only him, Luke Bavarious,
could take him.



Slipping on his stained trenchcoat, loading his Berettas and taking
another horrid swig of brown whiskey, he staggered out like a
scarecrow into the night. He knew where the cannibal was, he had
been following him for weeks to an old warehouse where he would
take his victims and begin the ghastly practice. The sky was dark,
and the rain ran down his face like the bloody tears of the
cannibals victims. Lightning flashed, followed by thunder but
Bavarious wasn't scared, he was ready.



He crept up to the warehouse, and sure enough The Mad Cannibal was
there, towering over his latest victim, a young boy wearing a
hoodie and sweatpants. It was now or never. He kissed his Berettas
and dived head first through the glass window. He landed in a
shower of glass and blood, his eyes scanning the warehouse for the
horrid ghoul, but didn't see him. Suddenly a butchers knife
flew out of the darkness and struck his shoulder, colouring it with
an all too familiar rust. Out of the darkness, a figure emerged,
running towards him with a knife in each hand and murderous red
eyes. Suddenly he fell, the kid had tripped him up!



``Thanks kid, now get outta here'' Bavarious growled,
spitting blood onto the floor.

``But I can help mister, I want to help''

``{\bf Get out}'' Bavarious snarled, raising his Berettas to scan the
darkness.



Suddenly, a horrid scream filled the warehouse and the cannibal
rushed out of the darkness again. Bavarious fired his pistols with
lightning speed, his Berettas vomiting bullet casings. The first
shot hit the cannibal in the stomach and he instantly spewed a
mixture of blood and human fingers. The second ripped through his
eyes, puncturing them like grotesque bicycle tyres. He was still
coming though, and Bavarious needed to reload. With lightning speed
he replaced the spent magazines, but the ghoul was gone again.
Following the trail of blood he found the madman sitting behind
some crates. He was wheezing and giggling in a pool of vomit, blood
pouring out of his eyes like a horrid waterfall.



``Im not going to arrest you'' Bavarious snarled,
``but I am going to kill you. Prepare to die you sick
bastard''



``Luke{\ldots}'' wheezed the rusty figure below.
``You wouldn't kill your brother would
you?''.



A lightning flash filled the room, and it was only then that
Bavarious saw the face of the cannibal in front of him. It was his
brother. An immense pressure of hatred and horror welled up inside
him. He staggered back holding his stomach, his eyes bloating like
a horrid fish. He howled upwards into the night, the vomit
exploding from his tortured innards like a revolting fountain of
misery. Behind him, The Mad Cannibal was gone.






