\chapauth{Hired Gun}
\chapter{The Bodies of Bavarii}


It was a haunting and horrid night in the city. Luke Bavarious sat
at the bar. He knew that nights like these only brought trouble.
All night, he had been feeling like he was being followed. He
sipped his drink and sighed. If only he was back at home with his
family. His wife and son had been killed in a tragic Beretta
incident. Thinking of their deaths made Bavarious want to vomit.
Instead, he had another drink. This was his fourth one
tonight.



After paying for his drinks, Bavarious put on his jacket and walked
out onto the dark street. He knew that every alley and dark corner
could be hiding a horrifying secret. He still felt the presence
following him, but he put it out of his mind. Cautiously yet
fearlessly, Bavarious began the five block walk to his apartment. A
few minutes later, he suddenly heard the unmistakably terrible
sounds of screams. These were no ordinary screams. These were
screams of murder. Bavarious ran into the alley, his Beretta in
hand. It was so dark that he couldn't see anything. He also
suddenly felt that he was no longer being followed.



Suddenly a flash of lightning lit up the sky and illuminated the
scene in the alley. Bavarious could barely stop himself from
vomiting when he realized that there was blood everywhere. And he
was covered in it. Each drop of rain smeared the blood into his
face and his clothes. Another flash of lightning revealed the true
horror of the alley. The blood came from two bodies. The bodies of
his wife and son. Their deaths were no accident after all.
Bavarious stared at his Beretta. He noticed that half the clip was
empty.



As sirens rang in the distance, Bavarious knew he had no other
choice. As blood and vomit flowed down the alley, the sound of one
final gunshot pierced the night. The body of Luke Bavarious fell
next to his son. For a moment, the two pairs of dead eyes met. 

 






