\chapauth{invision}
\chapter{Creature Of The Night}




Bavarious. Luke Bavarious. I'm a detective. I carry a baretta. A
baretta so powerful only one man can handle it. And that man's name
is Bavarious.



Luke Bavarious opened the door to exit the doughnut shop when he
heard it. Or at least he thought he heard it. He thought he was
hearing things again. Or was he thinking that he was thinking that
he was hearing things again? He glanced down the dark alley to his
right. He was definitely not thinking he was hearing things. The
creature exploded forth from his midnight fortress of cardboard
boxes oozing with the sludge from the rain soaked streets. The
creature exploded towards Luke Bavarious. The creature was vomiting
tears from its neck.



Luke Bavarious calmy took a drag from his Lucky Strike cigarette,
then flicked it lazily, as if patting a dog on the head. He then
drew his baretta. He aimed it. He slowly squeezed the trigger as
one would squeeze a small centipede or other insignificant animal.
The shots rang out through the night, with the force of a
jackhammer shredding through the creatures skull. The creature
stopped dead in its tracks and slowly fell to its knees. It fell
from its knees to its belly, all the while vomiting from every
available creature orifice it could muster.



Luke took a swig from his flask of EverClear 100% all natural grain
alcohol hidden inside his duster. He placed the flask back inside
his duster. He vomited. He approached the creature{\ldots}



``Oh no. Oh God, NO!''



It was grandma. 
 






