\chapter{The Boy That Lived}
\by{Irish Joe}





It all started when Luke Bavarious was aroused by a knock at his
door. ``Who is it?'' the mighty detective shouted from the comfort of
his bed. No answer but the sound of more knocking. Disgruntled,
Luke raised himself to his feet, still wavering from a night of
heavy drinking. ``Damn you all'' he shouted, approaching the door.
Leaning against the frame, he began to undo the lock when a shot
rang out. Looking down he saw a smoking crater where his peep hole
used to be. Thanking God he was too hung over to see anything, let
alone use his peep hole, Luke staggered back from the door and
reached for his Magnum Revolver lying on the coffee table.



The second shot didn't startle the brilliant gumshoe as much as the
vintage leather Ottoman lying between him and his gun. Falling head
first into the coffee table, Luke was barely able to grab his
Magnum Revolver, roll over, cock and fire the gun twice at the man
kicking in his front door before he passed out.



Luke awoke in the darkness of a car trunk. 'Its eerily quiet,' the
great protagonist remarked to himself. He then felt a sudden warmth
on the back of his leg. Luke reached around his muscular thighs to
feel about and find the source of the warmth. Blood! A second man
lie with Bavarious in the trunk. Before he could ponder further
upon this discovery, the car ground to a halt. Luke furiously
grabbed at the darkness searching for something, anything that
could be used as a weapon. As the mysterious driver exited the car
and approached the rear, Luke grasped on to the only thing he could
find, a large black iron tire iron.



The rattle of keys. The click of a lock. The sound of fury and
bone, crushing and yelping, cries of disbelief, anger and surprise.
Then silence as Luke Bavarious stood alone.



The awesome dick did not know who the two men were: one lying
bloodied on the ground with grey matter strewn to and fro on the
road, the other in the trunk, intestines drooping from a Magnum
hole in his stomache and half his face missing from one in his
head. It did not matter, for though it may sound strange to you,
dear reader, the fickle nature of Lady Death was all too familiar
to Luke Bavarious. She has pusued him with a vengence since the day
he was born all those years ago in an abortion clinic. 'The Boy Who
Lived' they called him. Lady Death had another name for him, 'The
One That Got Away." She tried as she might to catch him throughout
the years: car crashes, earthquakes, sicknesses and contagions,
shipwrecks. However, nothing could kill Luke Bavarious. And as the
trail of bodies he leaves behind continues to grow it seems that
nothing ever will. 
 



