\chapter{The School}
\by{IShallRiseAgain}


John Jones was your average every-day student at Livingston Middle
School. He was also very late. He hurried into his classroom for
the gifted students of which he was the smartest and coolest. He
hated his teacher, Miss Diabloclous, she was always giving them
homework and pop quizzes. ``Your late, John Jones! You get a
detention!'' shrieked Miss Diabloclous. ``Third one this
week'' thought John as he sat down with a smirk.



When school was over he headed over to Miss Diablocluos's
room. Another student, George Smith, was already there. ``You
boys have been behaving badly, and we can't have that can
we?'' proclaimed Miss Diabloclous. Suddenly her face started
stretching and contorting, and she grew ghastly fangs. George was
screaming and vomiting at the same time. Her jaws stretched, and
she bit off the head of George. His arteries started spewing
copious amounts of blood all over the place. Licking the blood off
her face, Miss Diablocluos shouted ``Your next!'' John
was ready though and pulled out his berretta. ``Pop Quiz time,
what happens when I shoot a bullet through your brain?'', he
exclaimed and then unleashed a hail of bullets into her head.



A police officer rushed in to see what was going on. Upon seeing
the grotesque body of Miss Diablocluos, he turned to John.
Expecting praise for killing the abomination of nature, he was
surprised when the officer unloaded a full clip into him with his
own berretta. Sighing the officer stated, ``Damn public
schools!''. 
 



