\chapter{The Ocean}
\by{jidohanbaiki}

The abrasive ocean waters lapped dangerously at his flippered feet.
Luke Bavarious was a marine biologist who took his job seriously.
He set his rusty bucket of herring into the sand with a crepitating
flatulence. In the distance, gray blades pierced the ocean, coming
closer and closer. There was a portentous whirring and clicking,
growing ever louder and more frantic, interrupted only sporadically
by the crash of waves.



Bavarious took fistfulls of herring in his fists. The herring were
slimy and slippery, so he squeezed the herring hard to keep them in
his grip. The bodily fluids from the herring leaked between his
fingers. He proceeded towards the malicious noise of the ocean,
slowly but determined, holding his fists of herring up to the sky,
as if in defiance to God. He stopped once the ocean reached his
hip. The gray blades swarmed around him. Luke smiled bitterly.
``Come and get it,'' he intoned.



Gray beaks poked out of the water, searching, wanting, smiling. But
those smiling mouths opened to reveal long rows of tiny, but sharp,
brilliant white teeth. Luke tossed the disgusting, smashed herring
into the waiting maws. ``Eat,'' Bavarious said, almost cursing.
``Eat!'' he commanded.



The dolphins splashed around him, taking their fill of the herring,
letting the herrings' slimy bodies slide down whole into their
stomachs. Bavarious began to laugh, at first just a chuckle. Then
he threw his fists covered in herring eyes and herring guts into
the air and erupted with demented revelry. ``Yes! Eat! Eat!'' he
screamed, his voice shrill with hysteria.



Luke Bavarious was a marine biologist who took his job seriously.
He was also a marine biologist who would leave no slight unavenged.
Little did the dolphins know that the herring was poisoned.



---



Donny had no legs ever since he could remember. A long time ago
when he was a child, he had lost them in a car accident, or so he
was told. He was also told that he also lost his parents. Every day
after school, his aunt would drive him out to the ocean so he could
swim with the dolphins as therapy. ``You're thirteen now,'' she said
bitterly as she drove him towards the sea. ``Don't you think it's
time you stopped swimming with those stupid fish?''



``They're not fish, and they're definitely not stupid.'' Donny said,
folding his arms over his stumps.



Once at the dock, his aunt rolled him in his wheelchair over the
wooden planks and tipped him into the waters below. ``I'll be back
in an hour,'' she shouted down to him. ``I've got to go to a meeting
at the bank.''



Donny floated, belly up in the ocean, his horrid little stumps
flailing uselessly. Soon, he felt something slippery slide
underneath him. It was his friend, Moon Dancer the dolphin. Donny
petted Moon Dancer's nose as he dreamed of the freedom he would
have if only he could become a dolphin. Then he sensed distress
from Moon Dancer. Donny grabbed the dolphin's head and pressed his
face to it. ``Take me there,'' said Donny.



He grabbed onto Moon Dancer's fin and they sped towards the
horizon. It was a wonderful feeling to move so fast and freely, but
the ride did not last. They approached a contorted figure in the
waters. Donny swam over to the struggling dolphin. ``Star Wave!
What's wrong?'' Donny asked.



Green bile and rust colored blood vomited from Star Wave's blow
hole. Star Wave opened his mouth and vomited out the poisoned
herring bones. Donny screamed and then vomited himself, and soon,
vomit mixed with tears in the ocean water. Attracted by the blood,
a shark appeared and landed a killing blow on Star Wave, putting
him out of his horrid misery and spreading violent red blood
through the ocean.



``Take me to who did this.'' Donny thought at Moon Dancer.



---



Miles away, Luke Bavarious dropped another bucket of herring onto
the sand with a squelch. He took fistfulls of poisoned herring, and
entered the ocean. In the distance, dolphins schooled. ``Come!''
Bavarious commanded, his powerful fists dripping with poisoned
herring entrails.



``You think you're so smart!'' he spat. ``But you won't ruin my
scientific research any longer! I was going to prove that you only
had fish intelligence, but you ruined my data and now I'm the
laughing stock of marine biologists!''



The dolphins did not come, but lingered on the horizon tauntingly.
He pounded the water with his herring fist, making a horrid
squelching noise. He then went farther and farther into the ocean,
until the water was up to his neck. The dolphins then swarmed
around him. ``Eat!'' He said, scattering the herring.



He laughed and laughed. Then he burbled as bitter, salty water
flowed into his mouth and nostrils. Moon Dancer swam up to him and
spat a poisoned herring in his face. Bavarious grabbed the herring
and beat Moon Dancer with it. ``Eat you stupid fish!''



Then a different dolphin swam by Luke's legs, then around his body.
It came out of the water and faced Bavarious. Bavarious screamed.
The dolphin had a human face; it was Donny. Bavarious fainted and
drowned.



Years later Luke Bavarious' bones were found washed up on shore,
but no one ever found Donny's. His aunt was thrown in jail for his
murder. From behind bars, she would mutter about dolphins with
human faces endlessly until one day her cellmate couldn't take it
anymore and strangled her to death. 
 



