\chapter{Shiny Toy Gun}
\by{katiekawaii}


I am a man. Some may call me a beast. I am also a detective.
Detective Luke Bavarious. I wasn't always a man. I used to be
a young boy. Carefree. But not for long.



It was said that when my mother gave birth I came out screaming. I
was just like that. Maybe it was a predictor of things to come.
Maybe. I got my first toy gun when I was nine. It was shiny
plastic, a Beretta. Fit in my hand like a glove. Like a glove fits
over a hand, that's how it fit in my hand. My mom
didn't want me to have it. It was my dad's idea. My
drunken father. He always came home late at night reeking of horrid
vomit. He wanted me to be tough. Tough like him.



I was always being bullied. A sixth grader, Max Attica. I told the
principal, but she didn't care. Sometimes it seemed like no
one did. My dad told me not to be so weak. He yelled at me one
night, ``Don't be so weak!'' he yelled. As he said
it I could smell the horrid stench of vomit and the stiff gin and
tonics he always drank. Hold the tonic. It made me want to puke. I
could see his neck exploding as his veins strained against the skin
with every syllable. ``You gonna let that Max Attica push you
`round, boy?''



``N-n-o S-s-ir,'' I stammered as I sobbed and cried and
held down my vomit. My father's vomit, which had been given
to me with the breathing of each horrid vomit- and gin-soaked
breath.



No, sir. Now I had my Beretta. It was just a toy, but I could
pretend. I had a good imagination. I took it to school with me in
my dark black backpack. Even then I favored the dark shade of the
night that would later be my beat in the city. It was 1953. Back
then nobody cared if a boy played with a toy gun at school back
then. Things are different now. I'm why things are
different.



It was a dark and cloudy day, the sun forced into shadow by the
ominous clouds overhead. Max's classroom was across from
mine, and as the bell rang and we filed inside he looked at me and
made the gesture children make to make a threat. A finger drawn
slowly across the neck. I imagined the blood gushing out of my neck
in a giant waterfall. He meant business.



I told the teacher, but like all grown-ups she didn't listen.
Nobody listened. This was my fight and mine alone. So I made it
mine. We came out of the classrooms for lunch. Our eyes met across
the hall. Eyes are the windows to the soul. Mine were black. He
came towards me with his hand twisted into a grotesque fist. I
pulled out my toy Beretta and aimed for his face, which was twisted
with hatred. He laughed. I pulled the trigger. There was a loud
sound, and Max's shirt turned rust. A real bullet.
That's impossible.



Suddenly, I was screaming. 
 






