\chapter{White}
\by{kerimeton}

When the white ward doors opened on that chestnut autumn day I was
reminded of the front doors of my garden shed in Vermont. I
remember feeling cold the same way I did that day, not in a
classical sense but down to the bone. I was feeling an abominable
chill as if I had been pumped full of antifreeze the moment the
doors came into view. And also, much like my garden shed, I was
afraid was what was there. Whether my fears were tangible or not
was to be proven, I myself, I no longer cared for the suffering
trumped any fear or loathing I felt.



I walked down the plasticine hallways and kept my head down; chin
on chest. It was as if a weight of shame had been strapped to my
neck and my only option was to walk like a sorry prisoner.



``Admission?`` the barrel-chested nurse asked behind her oak
podium.



``Yes''



``Which ward`` she continued with the expression of an aghast
ape.



''Psychiatry``



``Name.'' She was curt and unwavering. No doubt the brain
behind that placid face was as rudimentary as a record
player.



"Luke Barvarious'' I paused. ``Barvarious,
Luke''



She nodded curtly as if to suggest that I had somehow made that
record player run more smoothly.



``Reason for admission''



It was neither a question nor a statement. She prattled it off as
if she was in bored haze.



``I don't know''



She paused and stared at me. It was hard and cold as if she was
trying to read my ill intentions. She failed due to a lack of
any.



``Mr.Barvarian''



``Barvarious''



``Mr. Barvarious'' she repeated, still saying it wrong,
``I suppose I can admit you to a psychologist but I cannot do
further for now.''



``I see''



``You understand'' she said with a matte expression,
``that is the procedure for all self admissions''



I took a seat in front of the office and waited. I was soon called
in and immediately expressed my distaste for the poor classical
music on the loudspeakers. The psychiatrist ignored me on that
point. She reminded me of a wooden plank in personality and
stature.



``The report says your 25?''



``Yes''



She seemed puzzled.



``Well, can I ask why you admitted yourself?''



``It started years ago'' I said in deep thought, ``I
remember that my mother was ill and the doctor was recommending
some futile medicine. I was barely 12 then but I knew he was
wrong.''



``I see''



I proceeded, ``I insisted and insisted but I failed to be
heard.''



``Interesting'', at this moment her assistant came in and
a word was whispered into her ear. I failed to realize the
significance of this and continued.



``It turns out I was right, but due to the fact of my age my
words were ignored and cast aside.''



The physiatrist seemed puzzled again but told me to continue.



``It's been going on even since a younger age. Nobody
takes me seriously. When I was young is was due to my youth and in
my older years it was because of my youthful
appearance.''



``I see''



``I recall observing a fire being put out on a Sunday evening.
I remember pleading the firemen to take the back route but I was
continually ignored,'' I paused in repose. ``Do you see
what I mean, where I'm coming from?''



The lady got up and treaded lightly on the floor. It appeared as if
she had taken a tome of information from what I had said. She
walked to the alcove and poured herself a glass of water. She told
me quietly that she wondered why this was affecting me now and why
it took so long for me to come to her. I replied that I
didn't think that was much help, to which the doctor replied
that she was the trained psychiatrist here.



We paused in stifling silence and I realized that the meeting was
over long before I came in. I felt choked in the stuffy room as if
I was wearing a sweater in a sauna. There was an uncomfortable aura
around the couch and the plants that I felt uncomfortable with. The
urge to stand up ran through my legs but was confronted with the
sound of a knock on the door.



The doctor stood up and led the uniformed men in, they held me down
and I knew resistance was futile. I could not understand the
predicament though I understood the pain of the tightened
straitjacket. Once again I was muffled and thrown in the room
leaving them only to wonder how I had escaped in the first place. 

 



