\chapauth{King Plum the Nth}
\chapter{Untitled}


I'd never been to San Diego before. Never been further west
than Iowa. But I like to travel and I like my job, so when my job
called on me to travel, I packed my Beretta and bought a one way
ticket to SoCal. One way because, in my line of work, you can never
be sure if you'll be coming back. My name is Luke Bavarious,
I'm a private detective and this is the story of how I died.



The bus disgorged its wretched few passengers into a diseased
corner of the city. In some ways, all cities are the same, and San
Diego was no different. You won't find a bus depo or the
train station in a nice part of town. No, the rich white folk pawn
this stuff off on the poor blacks. As if their urban lives
weren't hard enough; the man sweeps all his dirt under the
rug of the black culture's communities.



I hadn't been on the streets of San Diago more than ten
minutes when I was mugged the first time.



``The fuck you doin' in our neighborhood,
whitie?''



I could've cried. There were four of them. They were tough,
angry black youths, and if they pushed this too far, they'd
get hurt. ``Just passing through,'' I said.



``Passing like a piece of shit, mo'fucker. Gotta pay to
walk our streets.''



``It's public property,'' I didn't break eye
contact. Like dealing with an angry dog, when you talk to a gang
member, you can't show fear. ``I'm the public. Let
me past,'' I unbuttoned my jacket, flashed my Beretta.
``There's doesn't have to be any
trouble.''



The kid, their leader, lifted the hem of his hoody with a slow
insolent gesture to show off his own piece, a Glock. Two of the
others reached for the back of their waist bands. I tried again,
using their language: ``Don't start none, won't be
none.'' I'd tried in vein.



``Stupid mo'fucker.'' The leader jerked his piece
from his pants. His draw was admirably fast. These kids knew
violence, they were born it, it was their legacy. A cold, harsh
society had turned an indifferent shoulder to them and they had
risen to the challenge, becoming the only thing they could be in
this city. They were tough, but I was professional. My Beretta
barked four times, once for each of them, and the fight was over
before it began. They weren't dead, but they couldn't
threaten me anymore. I moved on. Violence isn't the answer,
but sometimes it can teach a lesson that needs to be learned.



The lady, Kelly, my client back in New York, had told me all about
San Diego. Said her old man had taken her and her sister, Amy,
there after the divorce. Kelly'd been a little girl, the
sister was a baby. ``The kids at my new school,'' she
said, ``taught me fast. My first day, they told me it
wasn't smart to wear so much red.'' We made love for
hours that night. It was glorious but I never felt like she was
really there under me. She was that little girl again, scared to
finish her first day at school in that pretty red dress.



So she'd gotten old enough and run away, all the way to New
York City. But her baby sister, fifteen now, was still trapped with
the father. Still trapped in San Diego. She'd hired me to go
find her, save her, and bring her back. ``He won't give
you any trouble, Luke. Just make sure you see him during the day.
He works at night.'' She'd paid me in cash and her
body.



I found the little cinderblock house she'd described and I
knocked at the door. The only answer was a dog barking in the next
yard. I walked around the front yard a bit, looked and saw I
wasn't being watched, and slipped around the corner of the
house. I let myself into the fenced off back yard, peering in
windows as I passed. The place looked deserted. Around back, I
found a narrow concrete stairway leading down to a basement door. I
figured what the hell and went down the stairs and tried the door.
It was open. I went in.



It was gloomy and smelled damp and it looked pretty empty. All I
saw was a couple of cardboard boxes, a water heater, a couple of
coffins. ``What the hell?!'' Curiosity is a big part of
my job but I wish I hadn't given into it then. I walked over
to the first coffin, lifted the lid. There was the too fresh body
of a man, thirty something, long black hair pulled straight back
from the temples, a trickle of blood running down from his livid
lips. I stared, shocked, and as I did, his eyes snapped open.
Before I could do more than gasp his hand was on my throat.



``Who are you,'' he demanded. ``What do you
want?''



``Your daughter,'' I choked. ``She sent
me.''



``My daughter?'' His eyes glanced to my right.
``She's right there.'' I looked as best I could and
saw a young woman, the spitting image of my client but a decade
younger.



``Oh,'' he said, rising from his coffin, ``you mean
the traitor.''



``She said{\ldots}'' I was choking to death in his grasp.
I produced the Beretta, painfully slow, but it was like he wanted
me to shoot him. I squeezed off the last few shots, right into his
gut. He didn't so much as flinch.



``I know what she said,'' he said. ``She said I was
harsh. That I abused them.'' He grimaced horribly and his eye
teeth erected into fangs. ``But she never understood. You have
to be tough to live in a city like this, Mr.\ Bavarious. I only
wanted to make my little girls tough.'' The world was fading,
purple splotches exploding in my vision. ``Amy will show you
what I mean.'' The girl hissed, drawing her lips back from
cobra-like fangs.



{\ldots}I guess you wouldn't say I died exactly. Could a dead
man tell you his tale? But that's the story of how I stopped
living. 
 



