\chapter{The Horrific Release}
\by{Knuc If U Buck}





I inhaled the forbidden smoke of my favourite Marlboro Reds
cigarettes wistfully. Before I can reflect on the delicious but
deadly flavours of Virginia's finest I begin coughing. Violently.
Shuddering as I pull away the tissue that covered my mouth to
reveal bits of lung meat and black blood. The realisation that I
have lost control of my bowels and bladder hits me as hard as the
foul stench. My face reddens and tears burst from my bulging eye
sockets while I struggle for air. I begin sobbing. My name is Luke
Barvarious and I am a cancer patient and former NYC private
detective. I am about to die.

Recently, there have been rumours of children with terminal cancer
wandering out of the hospital, never to return. I have been asked
to use my detective skills to solve this case on special request
from the Chief of Medicine, Dr. Wolfgang Smith MD. I dutifully
accept.

Night falls after an entire day of a vicious experimental
chemotherapy combined with top secret military radiation. I am also
given an additional cocktail of drugs that enable me to walk under
my own power without doubling over into vividly horrific,
sweat-soaked nightmares. I set off towards the paediatric cancer
ward. Opening the cold sterile doors of ward 42, I immediately
recognise the soft footsteps of a wandering child.

``You there, turn around!'' I shouted down the corridor.

The silhouette disappears into the darkness.

I feared it would come to this.

I instinctively move my hand down to my trusty Beretta forgetting
momentarily that there is no place to holster it on my backless
hospital gown. Armed only with my wits I slink into the shadows
past the nurses station and follow the dark, impish figure through
the hospital and into the woods behind the main building.

Once into the woods I have to use all of my detective instincts to
keep up with my target. I track the child for was seems to be an
eternity, weaving between the thick trunks that guard the forest,
stopping against one every so often to catch my breath and wipe the
fresh bile from my stubble. As we reach a clearing I try to yell
once more, I begin to gasp for air desperately as the drug cocktail
begins to wear off. I grit my teeth to keep the cascade of bloody
lung chunks at bay. Looking up after containing myself I see a ring
of children.

The child I am following is being welcomed into the group. I
notice at this stage the the children are just rotting husks in
varying states of decay. They begin moving in a kind of reverie
cadence. Mesmerised, I pull myself up from the stump that I had
collapsed on and notice that the boy that I followed is beckoning
me to the zombie circle. Despite their gaunt, putrid features, my
detective instincts recognise them as the missing cancer patients.
As I make my way into the group I hear the sound of a dead man
coughing. Turning back, I see my own, fresh, urine stained corpse
slumped over a tree stump with the last remnants of my lungs spread
over a puddle of vomit lying next to me. What really caught my eye
though, was the smile on my crumpled lips. Suddenly, I was
free.



End. 
 



