\chapter{The Ninjas}
\by{KryonikMessiah}





Luke Bavarious was walking through a busy street, the landscape
riddled with urban decay. A building here, windows shattered, foul
smoke emitting from it's fetid chimney. A rusted out car
there, looking as if it had been sitting there for a good decade or
five. And all around was the constant buzz of midday traffic.
Bavarious, however, had other plans on his mind, as he walked into
a building. The building was tall{\ldots}.too tall.



`This building is tall{\ldots} {\em too} tall', Bavarious
thought to himself, one hand clutched to a Smith and Wesson .44 in
his pants and the other holding a beer. Suddenly, out of the corner
of his eyes, Bavarious saw a flash! As he turned around to
investigate, a ninja appeared! ``Come on, you commie
scum!'' said Bavarious, as he fired at the ninja. But the
ninja cut the bullet in half! Bavarious jumped back and stared the
ninja straight in the face as they began circling each other in
this old, decrepit factory.



Bavarious narrowed his eyes. These ninjas were a tricky sort. Just
as he narrowed his eyes, a board broke over the back of his head.
Turning around, Luke Bavarious glared at another ninja in anger,
who was shivering with fear, a wet spot covering the crotch of his
costume as he held the piece of a broken board. Bavarious snatched
the pants right off the ninja, and turned around just in time as
the other ninja was leaping at him with a karate kick. Bavarious
wrapped the pants around his face, and he fell to the ground
choking, but then the other ninja made his move!



Bavarious found a knife in his shoulder, which began spraying green
vomit and blood all over the Ninja, and he pulled it out and turned
around, only to duck the broken board. He stabbed the knife into
the ninja's hand, nailing it to the ground, and picked up the
broken piece of board, driving it through the Ninja's head in
one fell swoop, and it exploded into a spray of brains and blood!
Luke Bavarious was on the lookout for more ninjas, when suddenly he
saw two children, a little boy and a little girl, standing maybe
ten feet away from him. A dead ninja was on the ground, and the two
kids were happily tearing his eyeballs out of his skull. Luke
Bavarious grimaced at this, when suddenly, he realized his gun was
missing just as another ninja burst through the wall.



That, however, was fine. The little girl picked up a pistol off the
ground, which went un-noticed by the ninja, who sworded out his
katana at great attack. Taking a chop at the little boy, he was
stopped in his tracks as Luke Bavarious tossed a vomit covered
pillow at him, which struck him in the face, and the little girl
accidentally pulled the trigger, shooting the ninja square between
his legs.



The next day, all ninjas fled the city. Their three brothers in
arms had fallen, and no ninja was mighty enough to stand up to Luke
Bavarious. Children the world over rejoiced.



The End
 



