\chapauth{lemonlime}
\chapter{A Butter Knife}




Martin Boswell was always required to remain at table until Mr.
Boswell dismissed him. Some nights Martin would sit in his creaky
old wooden chair, picking at a tattered and threadbare corner of
its cushion, until long past midnight. Since eating his supper
never took more than an hour, Martin would be left with a very long
time in which to sit, pick at his lumpy old cushion and watch his
father watching the butter knife. This knife was dull, scratched
stainless steel with a rounded tip and a very slight serration; no
different than any other butter knife that might grace another,
happier supper table.



At first Mr. Boswell would turn it around and around, so that the
lamplight flashed off its blade hypnotically. Then, holding the
handle lightly between his thumb and all four fingers, as one would
hold the bow of a cello, he would run that knife's dainty little
teeth slowly up and down the length of his forearm, occasionally
pausing to turn tight little circles over the network of veins
decorating the inside of his wrist and displaying to all the
precarious restraint in which his very life's blood was held.
Martin had used his father's butter knife once when Mr. Boswell was
at work; from that day forth, seeing his father's shivers never
failed to provoke an answering shiver in himself.



Then Mr. Boswell would turn the butter knife's attentions to his
scarred, scabbed hands, those stained and stinking hands which had
fired the little gun that shot Martin's mother in the back as she
tried to run for the last time. He would drag those hateful smiling
teeth back and forth across the back of his hand as though
buttering an english muffin, hour after hour, until the skin began
to abrade and swell and eventually bleed.



At first the wound was a minor one. But after being kept open by
Mr. Boswell's nightly ritual for the better part of a year it began
to grow wider and deeper. His flesh became purple and black and the
stench of putrefaction was so strong that no one would willingly go
near Mr. Boswell except for Luke Bavarious, a former police
detective turned bodyguard, and Martin.



One night, around 11 o'clock, Martin saw bone. Not even the memory
of the four days of torment his mother suffered in the root cellar
as she died of her gunshot wounds could keep him in his chair then.
In his bedroom, Martin stripped off his soiled clothes and set them
to soak in the bathtub, then opened the window to clear the odor
and began to wonder whether a jump would really kill him. He didn't
feel like adding to the number buried in that grisly root cellar,
yet he knew that if he tried to creep out of any of the doors he'd
be instantly caught by the keen eye of Bavarious.



There was a knock at his bedroom door, and it opened. Luke
Bavarious stood there and he said, ``I'm sorry, Kid, what you're
gotta live with is wrong. Just run back as quick as you can. Get in
your chair and I'll come in a bit later to shake him out of it. I
promise I'll hurry.''



Martin threw on a clean set of clothes and dashed back downstairs.
His father never even looked at him as he took his seat as quietly
as he left it. Mr. Boswell did not shift his attention from the
butter knife until Bavarious walked into the dining room, claiming
to have seen an intruder across the courtyard. Martin was
immediately ordered to his bedroom for the night, and as he left
the table Martin felt a gratitude and devotion for Luke Bavarious
that he could never have imagined just fifteen minutes
before.



That night taught Martin that while Mr. Boswell was watching his
butter knife, he could go anywhere and do anything without his
father seeing him. Only Luke Bavarious could keep him from leaving
during those times. One night, as Mr. Boswell sat mesmerized by the
clean red blood that seeped from his corrupted flesh, Martin went
to the linen closet and pulled out a backpack in which he'd stashed
clothing, food and a little money. Bavarious met him at the
door.



``Let me go, Luke, please,'' Martin begged. ``You know he'll kill me
too, as soon as he sees that I want to leave.''



After looking at Martin for a moment, Luke said, ``I know, kid.
After what he did to your Mom, I knew that I'd only leave this
house when I was dead. Mr. Boswell, he'd kill me in a second if he
knew I was standing here talking to you and not killing you. No way
can I let you stay here. Your father doesn't love or respect you.
But he was a good man once, and I can't bear to live with having
done something to betray his trust in me. No, there's only one way
it's gotta be.''



With that, Luke Bavarious pulled out the Beretta he'd carried since
early childhood, applied the muzzle to his temple and squeezed the
trigger. A scalding wave of blood drenched Martin's face as he
stood frozen there. He turned suddenly and ran away into the
night.



It would be a long time before Martin Boswell stopped running. He
crossed oceans and traversed lands stranger than he'd ever imagined
during the long empty hours sitting at his father's dining room
table. During that time, Martin was a beggar, a slave and a whore.
When he woke up one morning in a place where the air was so thick
it could be used as a sandwich spread and the rain fell as warm as
blood, he knew he was home.



Martin would forget, sometimes, why he'd run. He'd be eating supper
at a cafe and the light shining off one of the diners' butter
knives would make him shiver with some dark lust. But none of that
mattered. Every time he felt the hot rain wash down his face Martin
would feel the blood Luke Bavarious had shed, the sacrifice he'd
make of his own body, so that Martin could be reborn into a new
life. 
 





