\chapter[Destiny Calls]{Destiny Calls: A Luke Bavarius Mystery}
\by{Livestock}


Luke Bavarius was on edge. For months he'd been receiving
terrifying phone calls from a mad man. The telephone would ring,
Bavarius would pick up, and that horrible voice would speak.



``You're dead, Luke Bavarius. {\em Deeaaaadddd{\ldots}}''



``Who is this?'' Luke would respond. ``I'll get you! I'm a cop, you
idiot!''



``It doesn't matter, Luke. The law cannot stop me.''



Luke wondered what the calls meant. They happened every night at
midnight. Luke knew that midnight held special significance to
satanic cults and the criminal element. In his work as a gritty New
York City detective he had made many enemies. He could scarcely
keep track of all the men he put behind bars, let alone which ones
still harbored a grudge.



Luke could barely sleep. In his dreams he was chased by shadows.
Glimpses of dark alleyways and shattered mirrors haunted his
slumber. Luke was near his breaking point. What did it all
mean?



{\em Ring!} The telephone rang. It was midnight again. Heavy beads
of sweat started oozing from Luke's forehead like anchors dropping
from ships at port.



``Who is it?'' Luke answered angrily.



``Now, now, Luke. Don't be so angry. It's just your old
friend.''



``You're no friend.''



``And you're dead, Luke Bavarius. {\em Deeaaaadddd{\ldots}}''



Luke slammed the phone down. His heart was racing like Big Brown in
the Kentucky Derby: fast and determined. Luke took a swig from his
flask. He knew he had to do something. How long could this go on?
Not much longer, Luke thought.



It was time to involve his friends at the station. Luke called in a
favor from Jim Centauri, an expert at tracing phone calls. Jim
hooked his equipment up to Luke's phones, and the two waited until
midnight. Nothing happened.



``Damnit!'' Luke yelled. ``He calls every night. {\em Every
night!}



''It's probably just a prankster, Luke. Don't let it get you down.
Anyway, maybe he got tired of calling you.``



Jim packed up his equipment and headed home. Luke thanked him, but
felt disappointed he had no answers. Then it happened. The thing
Luke was least prepared for.



{\em Ring!}



''Not again!`` Luke yelled, staring at the ringing telephone. He
debated answering, or letting it sing its horrible, shrill song.
Finally, Luke could wait no more. He reached his left hand out and
clutched the phone, squeezing so tight it would die if it were
alive.



''Nice try, Luke. But you'll have to figure out who I am on your
own.``



''Who are you?`` Luke demanded, his voice surging with anger.



''Don't you know, Luke. Don't you know who I am?``



''It's only a matter of time before I find out.``



''Sooner than that, Luke. Don't you recognize my voice?``



Suddenly a horrible realization came over Luke. ''No. No! No!!!`` he
cried out. He looked to his right, and he was holding a second
telephone.



''All this time, Luke. It was you. It was me. It was
{\em us}!"



Luke heard a click. He looked to his left. The telephone in his
left hand was gone. Now it was a cocked Beretta pointed at his
skull. Suddenly he gulped. {\em Click.} 

 






