\chapter{The Cellar Of Death}
\by{Lord Humongus}


Luke walked down the house's scarred walls. The place was full of
hate, he could

feel it tingling in his bones. Like some sort of hate filled
bastard feeling. {\em Filled with hate.} he dismissed the
thought.



His parents were moving thier stuff into the old, creaking hate
filled house. Luke ran up to his obseqious parents, warnings of
hate emerging from his mouth accompanied by the screeches of
horror. His abusive father slapped him in the face and told him to
``Quit it, you dumb pecker.'' Luke couldn't. He had to warn
them.



Luke looked for anything to defend himself from the evil, but he
found nothing. He looked throughout the house for something. Only
to

come up empty handed. He walked out of the door wondering about
what he could do.



He ran into Suzy, his sister, she teased him and called him a
pussy. {\em She called me a cat that's not insulting why would she
call me

a cat?} thought Luke.



The sun hid under the horizion. The screams of animals filling the
empty night air. Luke arose from his bed. Suddenly a illmunescent
gigantic head appeared in his room. It opened its lips to talk. All
Luke could feel was hate in his brain.

Nasty, painful hate.



Luke awoke in his bed in the morning. He ran down to his parents
screaming and screeching like some annoying owl. His father rose
his hand. Luke closed his mouth shut.



He wandered down into the lone cold cellar of the hate house.
Looking for clues as to what was causing so much hate. He looked
around the

dusty cold floors. His came upon an old case full of dust. He
opened the golden latches, looking for anything that might be a
clue. Inside,

was a horrible book. He knew what must cause the hate. This book.
He threw it into the evening fire that was in the fireplace. His
dad slapped him in the face for doing that but he thought to
himself ``I just saved your life you fool.'' and smiled to himself
because he was so smart and stuff and found out about the
hate.



But it didn't work he was wrong. The hate returned each night, and
each day Luke received a slap to the face for being an annoying
little mutant. He slept scared under his covers each night the
horrible head would return to him and use all the hate and torture
him with its 's telepathic mind full of hate and ire. He awoke
every morning screaming at nothing. Until one night, he heard his
parents scream. He ran to thier room to see them being dragged into
a portal. A portal to hoboken. Luke laughed at them as they were
sucked into a trailer park abyss. Full of people you didnt want to
hang out with because they are all hate filled evil creatures from
the third nuclear war.



He hid the bodys in his bavarious cellar.



They should've listened! 
 



