\chapauth{Lorentz Factor}
\chapter{It's just me, `Luke'}



I stepped from the shadows, those last shadows that were hastily
escaping as the sun pours over the cityscape. I had awoken only
moments ago, the sun's light entering my head like the scream of a
newborn during a hangover. I could not remember what had happened.
I was working on a case in the north end of the city, the details
still not coming to me. I remember driving, perhaps I had an
accident. I simply could not remember. Retrieving my shades from my
breast pocket to halt the screaming rays of sunlight that were
pounding at my spinning head, I noticed a door in side of the
building I had found myself next to. I needed a place to sit while
I waited off this pain in my skull.



Opening the door, I was greeted with soft music from the big beat
band inside what appeared to be a small bar. Odd time for them to
be playing, I thought, but, never mind. I sat down at a table near
the door and grabbed the drink list. Interesting, they only seem to
serve whiskey sours{\ldots}fine by me, it's all I drink anyhow. After
ordering, the bartender returned with my drink, I asked him, ``Where
exactly am I?'' He chuckled, ``It's only 11pm and you're already
smashed,'' he continued his guffaws as he wandered back to his bar.
Sipping my drink, something the bar tender had said bothered me.
``11pm,'' but the sun had just come up; I checked my watch and it
said nine thirty-eight. My watch breaking wasn't new to me, I get
into rough spots quite often that my watch never makes it out of. I
decided I needed to find my way back to the office.



As I left the bar it seemed that twilight was approaching. My car
was nowhere to be found. I walked south on the street looking for
anything that seemed familiar, when I came to an alley. Something
about this alley. I still could not remember. I walked towards the
opening between the two buildings to the alley. I heard a voice
behind me, ``Sir, I'm sure you don't want to go that way, won't you
continue down the street?'' It was a small kid, a strangely dressed
child. His pants were a grayish knee length trouser held up by
thick suspenders that draped over his cotton shirt. His boots also
were odd, laced up they met the short trousers leaving only an inch
of bare skin between them. ``Move along kid, I think this alley is
important.'' I told him. ``I'm thinkin' sir, you're going to be
sorry,'' he was saying as he wandered off around an
intersection.



After my short talk with the child, I realized the sun had already
dropped behind the buildings to my west. I tried to get my
bearings. I wandered into the alley and the pounding in my head had
become so intense that my knees buckled. I tried to cry out in
pain, though the intensity of it all left me with little strength
and the sound escaped as more of a gurgle. The pain in my head
retreated with the sun's last light. I slowly stood from the fetal
ball I'd formed in my pain. As I was was rising a light shown
through the ingress of the alleyway. It looked like two headlights,
they were bright and I turned away. A man approached I heard him
shuffling through the broken stone of the ground in this ill kept
thoroughfare.



``You there! What are you doing? Turn around!''. These words, that
voice. It all came back to me. ``Beggin' your pardon, but{\ldots} you
don't want me to turn around,'' I told him. ``Sure I do. I got a
pistol pointed at your back so ya better.'' I knew what he was in
for, I myself have seen this. It was my fault, it was his fault. If
I kill him, I won't have to go through this again. ``Okay, you asked
for it,'' I told him as I approached still hanging to the shadows.
He asked me to step out of the dark, what the hell. My life would
end soon maybe I can stop this cycle here and now. As I approached
the horror that twisted his face was intense. I doubt he recognized
me, I hadn't myself at first. I rushed him, hoping to reach him
before he fired his Beretta. I lunged as the first slug pierced my
skull. Several more rounds pierced me, the pain offset by my wish
to end this cyclic horror. Blackness was encroaching on my vision.
Things began to swim. I tried to warn him, but I doubt he
understood the wet blood filled, ``I am you, I am Luke
Bavarious{\ldots}''. I collided with him we smashed into a window.
Everything went dark. My nightmare was over, but had also just
begun. 
 






