\chapter[The Orchestra of Nothing]{Luke Bavarious and the Orchestra of Nothing}
\by{Lynxifer}



I pulled my trenchcoat closer to my body, as the cruel autumn winds
flicked and bashed against my weary frame.

``Some night for a job.'' I announced to myself in my
head. Like every true pee aye, I felt it required that I narrate my
life, to the voices in my head, the voices that guided me and kept
me safe from the others.

The run down dreary doors passed me in a blur as I walked swiftly
down a street with eyes peering out of every window, my gun
shivering under my layers, eager to spill out and deal in its holy
cleansing.



I wasn't an angel, I wasn't some holy pariah. I was the
encapsulation of a human devil, ready to pass my judgement on you.
All of you who thought I was the ripe target of abuse and of
mocking, all of you who thought you were better, my gun and I are
always ready to knock you down a peg.



The street twisted into another and then, another as the wind raced
around me, the howling growing like a hungry wolf on the hunt. My
target was the old opera house off 3rd and 29th. In it's day,
it was probably a beacon of talent and beauty, but the sands and
ebbs of time had reduced it to a third rate nothing, its former
glory haunting it, the same as the drug dealers and scum that hound
its bricks and mortar.

The streets finally moulded into a conclusion as the opera house
came into view. Somehow I didn't expect it to be as clean and
fresh as it was. I rubbed the base of my gun's magazine as I
approached my goal, taking tentative steps. Although hired by the
manager of the house, I didn't trust the guy, he oozed a
slimy confidence that put me off base when he called me and
enlisted my services, his voice full of practised bravado and false
compassion.



The doors stood between my fate and me, I took hold of one of the
weathered brass handles and tugged with considerable force, which
yielded entrance to me. Taking the opportunity, I dashed into the
poorly lit entrance foyer and out of the harsh winds that had led
me here.

Inside, the manager was waiting for me. He was as grimy as I had
imagined, his hair slicked back like a funeral director and his
suit oddly positioned.

``Well har there, bud! You must be thar Private
Investigator.'' He said to me, his hand outstretched to shake
mine.

I did things my way. I looked at his hand, wrinkled my lips at it
and left my hands firmly at my coat.

``Hello.'' I said calmly.

He seemed genuinely upset at my refusal to meet him half way as he
retracted his hand. I felt vindicated as he ran his fingers through
his hair and wiped the oily residue on the back of his
trousers.

``Ahm sure I made myself clear on the telephones.'' He
said to me, fingering his top pocket slightly. ``Ah just need
you to find mah missing Orchestra.''

I sneered slightly. The fact that he claimed ownership of such a
beautiful thing when he himself had none, was sickening.

``I'll find them, don't worry.'' I replied,
offering no form of comfort in my voice.

Seeing that his snake oil charms would get him nowhere with me, He
slinked away, his greasy smell following him as he slinked into the
pitiful box he undoubtedly called an office.



I loosened my coat somewhat as I began my quest inside the house;
my first stop was the pit, as that was usually the location of an
Orchestra.

The corridors I found myself in were full of regal decoration and
warm lighting. I had to stop myself from examining my surroundings.
I had a job to do and I was going to do it.



The corridor gave way to the auditorium as I breached the unlocked
doors with my trenchcoat flapping in the slight wind coming from
the stage, the entire room dark and lit for a performance. I walked
with my chest puffed outwards as I approached the pit, my right
hand firmly on my gun, its cold metal serving to keep me
attentive.

I twisted my head as I peered into the foreboding pit and saw
nothing but empty seats and scores strewn around the floor. I was
about to stand up and abandon this line of inquiry, until the wind
from the stage picked up to a whistle. This was a break I needed as
I grabbed my gun and cocked it with deliberate action to put fear
into whatever was playing this game with me.

I walked towards the steps with army style stealth and crept up
them, peering towards the undecorated back of the stage.

As I slinked across the stage, I felt the wind intensify, until all
of a sudden the stage lights erupted into a ball of white-hot light
and illuminated the entire stage from its murky prison.

I twisted around with precise movement, my gun raised and ready
shoot, but became filled with horror was I surveyed the scene
presented to me.



Although the lights on the stage were blinding and piercing, my new
tormentor had left a small channel for me to survey my audience.
Ghouls. Zombies, Rotting Corpses. Call them what you will, they
were now watching my every move, their rotting flesh falling off,
and congealed blood spilling to the floor like rancid rain.

Whatever was going on, I wanted no part of it. This was not my gig,
I hadn't signed up for this, and it was my time to
leave.

Fate had conspired against my quick escape and had removed the
steps to my freedom, leaving only an expanse of nothing.



``AAAAAAAnd now!'' A voice rang out from behind me. I
twisted and saw a twisted figure of bone and seared flesh holding a
wireless microphone, wearing the same greasy suit as the
manager.

``The one, the {\em only}. Luke. Bavarious!'' He announced to
the deathly audience.

I raised my gun to his head, and lined up the sights to his head. I
didn't like his style and thought he needed to learn of
justice, Bavarious style.



A noise, stopped me from enacting his punishment. A deathly clatter
of strings and pipes, arranged in a screech and howl. I spun
around, my gun ready to deal with this new nemesis as the source of
this new sound became apparent.

An orchestra of 12, probably the very orchestra I had been sent to
find, were there. Each in dirty and torn tuxedo's,
they're appearance was no better than the crowd of demons
watching this harrowing event unfold. Some were missing jaws, eyes,
some even missing limbs, but each player managing to play their
instrument of death in the symphony of horror.



I'd had enough of this game, the rules weren't to my
liking and the umpire was bent.

Like a holy angel, I raised my pistol to the Tuba player. Obviously
gluttonous in his previous life, I decided he was the first to
experience cleansing. I aimed for the largest portion of his head,
held my breath and squeezed the trigger.

The bang of the gun had silenced the approaching orchestra as the
round rippled through the air and smashed into the players head,
but bounced off like a ball on a wall.



I shook off my surprise and aimed for another, this time it was a
violin player. A once cute broad, but her new bandmates had
corrupted her into join the legion of the dead. Again, aiming for
the head as the band started playing their deathly march and
advancing faster this time, I peered down the sights and
squeezed.

Another veil of silence enveloped the house as the same happened
again, the round bouncing off harmlessly.



I could have fired the rest of my chamber on the advancing horde,
but I didn't think my metal protector deserved that
fate.

As the band approached, I heard the crowd moan and scream. I
guessed that this was the undead version of a cheer as the players
came closer and closer to me, closer to whatever endgame they had
decided for me.

I wasn't about to grant them this, I never planned to go out
this way and I had a long way to go yet.

As I considered the situation, the pieces of the puzzle fit into
place. I'd worked out why the orchestra had gone missing, why
they had turned into the grisly afterimage and why the audience had
joined them in the ranks of the undead.



Grasping my angel, I placed the barrel under my chin, aiming for my
precious grey matter and I squeezed.



The round screamed through my head and smashed through my
skull.



As I fell to the ground, I saw the orchestra scream out in pain and
begin to disintegrate, as if the blinding gleam of the stage lights
were holy light, coming the cleanse them.

The Audience was sharing the same fate, as they melted into a gloop
and started to run towards the stage area.

With my last breath, I placed my gun back in its holster, my job
done.



Two days later I woke up in the hospital. I could feel a bandage
wrapped around my head, holding my essence in.



``Well done.'' The cute nurse said, seeing I was awake.
``You found the orchestra.''



Like the Mounties, I always get my man. 

 



