\chapter{Son Of Bavarious}
\by{Madcosby}





Luke had walked these streets so many times, yet tonight they
seemed so unfamiliar. Clouds gathered ahead, and made the dark even
darker. Alleys were so dark - black as culture - and the constant
scurrying of rats and big cockroaches seemed to come from
everywhere.



Maybe it was all in my head, Luke Bavarious thought. Maybe I've had
enough of this job. For tonight was his last night as a cop, and he
was going to retire. He was the age of three third graders on
summer vacation.



Each alley he passed reminded him of his past here on East Dark
Chill Street. He remembered the time he saved that elderly lady who
turned out to have a swamp tentacle that attacked him and killed
his first partner, Jack Dynasty. He saw the mirror store that had
burned down after his reflection tried to burn down the
neighborhood.



Then he saw an alley he had never seen. Or had he? He had walked
these streets so many times he was shocked. The cold grasp of
surprise gripped his spine like the stickyness of masking tape on
soft paper. A figure, cloaked in darkness, stood at the end of the
alley. He pointed at Luke.



``Walk away{\ldots} '' it said, in a voice that made Luke's heart skip a
beat like a record player in the back of an off-road van. Luke's
adam's apple swung like a vertical pendelum, ``Come out and let me
see you.''



The shadow screamed, ``You'll have to kill me first!'', and reached
into his long trenchcoat that he had been wearing all this time and
pulled out a Colt 45 Shotgun.



Luke didn't hesitate. Chill Street had taught him wasting a second
could mean your life. So he pulled out his Beretta, which was also
retiring tonight. He pulled the trigger so fast, and six bullets
vomitted from the barrel.



One struck the shadowy figure in the arm, by the elbow. But the
creepy shadow did not fall.



``Nice try. But you can't kill what isn't there!'' And with that, the
shadowy figure was gone.



Suddenly, it was raining. And more suddenly, Luke felt a wound in
his arm, right where he shot the creature. Blood oozed from his arm
like mucus from a child with a cold from too many snowball fights.
Luke fell to the ground, clutching the wound.





The shadow emerged once again, and stood above Bavarious. In the
light, Luke could see clearly that the monster had the same
features as he: tall, well built like he worked out at a gym twice
a week, and a moustache. A dark moustache. But his murderer was
younger, like a child who was probably a fourth grader. It was like
looking in the mirror. A mirror of pain and agony, a place where no
one should see their reflection without remembering the pain of
losing a puppy or maybe a grandfather if youre older.



Now, without the echo of the alley, the doppleganger's voice was
not muddled by the darkness and sewers of the alley.``I cant let you
retire, Luke. I'm taking your job.'' It sounded to Luke like he was
listening to his own message on an answering machine. It was his
voice.



Luke turned cold. This was the end. He knew it. He wished he could
hold his wife one more time; he wished he could scream at the top
of his lungs and make the monster go away. But instead, he grabbed
his badge, and his trusty Berreta, and handed them to his killer.
It was time to pass the torch to a younger generation of cops.
That's what tonight was all about, Luke finally understood. The
future of law enforcement was children.



``Thank you, father.'' And with that, the apparation disappeared.
Suddenly, Luke was sobbing.



Then he was dead. East Dark Chill Street was his tomb. 

 



