\chapter{Luke From Payroll}
\by{mboger}


I sat down at my desk. The sound had come again. It was my phone
ringing. My hand shook slightly with the heavy receiver in my hand.
The sleek receiver was transmitting and receiving, ready to take
the call. I work in the payroll department. My name is Luke
Bavarious. I hate my fucking job.



People had been complaining about discrepancies in their paychecks
for about a year now, so I finally decided to execute the plan I
had been working on for as long as I can remember. I was assigned
to raise the Demon Lord Gol'Sothog from the fiery pits of
hell.



I spoke into the phone, ``Payroll, this is Bavarious. Luke
Bavarious.''



On the other end of the line, ``Hey, Lou, this is Bill Taylor over
in{\ldots}''



``Luke,'' I interrupted. ``The name is Luke Bavarious.''



``Ok, sorry. Whatever. The reason I'm calling is{\ldots}''



``Say it,'' I interrupted again.



``What?''



I was starting to lose my cool. ``Luke. Bavarious. {\bf Luke! Fucking!
Bavarious!}''



``Jesus, Luke! Sorry! Luke Bavarious, Luke Bavarious, Luke
Bavarious,'' Bill sniveled into the phone. He doesn't deserve to
live and it was then I made up my mind. ``Man, you need to switch to
decaf. Listen, -Luke-. I have a problem on my last paycheck. I had
3 hours of overtime last week that I wasn't paid for and Debbie
over in HR told me to take it up with you.''



Over the last year or so, I, Luke Bavarious, have been slowly
syphoning money out of employee paychecks to fund my Demon Lord
Gol'Sothog sacrificial altar. Twenty bucks here, fifty bucks there.
It adds up.



``Not a problem, Bob,'' intentionally mistaking his name and then
pausing for him to respond. He doesn't. He's so pathetic, he makes
me vomit in my mouth a little bit and then I have to force myself
to swallow it down. He's barely worthy of sacrificing to
Gol'Thogthog, but he'll do. And because he made me swallow my own
vomit, his sacrifice will be slow and painful. ``I see the missing
hours here. Why don't you come up to my office and I'll square you
away.''



``Sounds good. I'll be right up!'' The phone disconnects.



He's fallen for my ruse. Hook. Line. And Sinker. And Luke
Bavarious.



I have about two minutes to prepare, but that's two more minutes
than I need. I'm Luke Bavarious, always prepared. I'm hiding behind
the door with a syringe full of knock-out serum when Bill enters my
office. He doesn't even put up a struggle as I slide the syringe
into his neck, the needle vomiting forth sweet slumber into his
veins.



Bill doesn't wake up until just after midnight. I had waited until
everyone had left the office for the night before loading Bill into
the back of my Dodge SRT-4. A lot of people think the SRT-4 is just
a Dodge Neon with a turbo, but fuck those guys, I love this car. I
drove my totally sweet SRT-4 to the secret location of the Demon
Lord Gol'Sahblah sacrificial altar and waited.



Bill's eyes open and he tries to speak, but he can't. Did I mention
that my knock-out serum was also a paralyzing toxin? Bavarious!
Bill is laying on a solid gold altar, surrounded by dark, fiendish
incense burners. Expensive incense. I had to import it from
Thailand and everything. This is why I was skimming money from
paychecks. Have you ever priced a solid gold sacrificial altar? I
mean, it's not like you can just walk into Bed Bath and Beyond and
pick one out. This shit is expensive.



I raise the jewel encrusted ceremonial sacrificial dagger over
Bill's body. His eyes widen in terror. It's the only movement he's
capable of making, thanks to the knock-out / paralyzing toxic serum,
which also wasn't cheap, by the way. I can't stress enough how much
money this whole thing has set me back.



I began chanting. With each long forgotten word uttered, I can feel
the power in the room increasing. A dark mist begins to swirl and
in that mist I see another dimension. Closer, closer, two worlds
are becoming one. There is only one last thing left to do. I plunge
the dagger into Bill's heart and the ever so slowly twist the
blade. I lean over and whisper into Bill's hear, ``Bavarious.''



I'm then instantly thrown to the ground as an interdimensional rift
opens, unleashing the Demon Lord Gol'Sobeys from his hellish
prison. The Demon Lord smiles at me and I smile back.



``{\bf You have done well, Luke Bavarious. Now that I am free, there
  will be no stopping me. I will rule this world and everyone who
  inhabits it.}''



``All glory be to Gol'Bladder!,'' I shout.



``{\bf You have shown yourself to be a faithful servant. As such, you
  shall be rewarded. You will be my right hand when I enslave this puny
  world. You will hold the highest rank in my army. The rank of Payroll
  Administrator.}''



I staggered backwards and fell onto a desk that had materialized
behind me. A nameplate sparkled on the side of the desk. Bavarious.
I picked up the phone and heard a horrible ring tone. Suddenly, I
was sobbing.



The moral of the story: Kids should be respected and listened
to.



