\chapter{The Cave}
\by{Monkey Trouble}


The name's Bavarious. Luke Bavarious, P.I.



My morning began with a mysterious phonecall. An unidentifiable
voice, wracked with sobbing, incoherently pleading for help. The
only words I was able to decipher were ``help'', ``old cave'' ``outside
town''. That could only mean the old, disused coal mine on the
outskirts of town. Whoever the poor shmuck was, I decided to
investigate.



I followed the overgrown dirt track from the edge of town, until I
was staring into the dark, gaping mouth of the cave. As I clicked
on my flashlight, I heard a voice behind me.



``Mister. Hey, Mister.''



There was a small blond-haired boy on a rusted red bicycle behind
me.



``You shouldn't go in there, it's dangerous.'' he said.



``Beat it, kid, you shouldn't be messing around out here.'' I said
gruffly.



A small smile twitched at the corner of his mouth. ``Ok, but don't
say I didn't warn you.''



I watched him turn the bike around and ride off. As I stood at the
cave entrance, I felt a strange itching sensation on my right hand.
Looking down, I saw a wart I hadn't noticed before right next to my
index finger. Dismissing it, I drew my beretta and headed into the
darkness of the cave.





As I shone my flashlight into the murky depths of the cave, I could
see it went on for miles in front of me. The itching sensation had
started to travel all over my body, getting more intense. I was
eager to find whoever was in trouble and get the hell out of
here.



{\bf Bang.} A gunshot cut through the air like a knife. I hit the
deck, rolling behind a pile of rocks and scanning my surroundings
for my would-be attacker. It was only then that I realised the shot
had come from my own gun.



I looked down at my gun hand, and recoiled in horror. Where the
wart had been, there was now a fully grown finger{\ldots}{\em and it was
curled around the trigger!}I swiped at it with my other hand and
it responded by trying to turn my own gun on me.



Seeing no other choice, I dropped my flashlight and grabbed my
knife from my pocket and started to saw into the strange digit. I
vomited in pain as the blood flowed from the cut. My flashlight lay
on the floor, casting it's light onto me, and I watched as the
finger continued to grow even as it hit the floor. The flesh
writhed and I realised it was growing into a hand, then an
arm!



The itching sensation suddenly wracked my whole body, and I ripped
open my shirt to reveal several pairs of hands growing from my
chest! I vomited again in disgust, once again going to work with
the knife, vomiting blood and vomit from all over me. Suddenly I
was sobbing.



As the piles of bloody flesh on the floor surrounding me continued
to grow, I felt a hand clamp down on my shoulder, and I was spun
around to face{\ldots}myself. I gazed in horror around me as I realised
all of the parts I had chopped off were growing into other versions
of me!



This{\ldots}is the dawning of the age of Bavarious.



The End{\ldots}? 
 






