\chapauth{nmg}
\chapter{The Horrid in the Arcade}



Bavarius woke with a startle. He had a hangover from the 3 Coors
beers he drank last night to help him relax and his head was
horrific with vomit and pain. Suddenly he remembered what happened
yesterday. It was his worse case yet ever.



It all started yesterday when he got a telephone call from the
Chief. ``Bavarius I need you to go down to the arcade to investigate
a noise complaint'' he said. ``OK'' said Bavarius.



His head and heart pounding like a drill, Bavarius loaded a clip
into his Barretta and fingered the safety. Nervously he went to his
Chevy Camero and hit the ignition. He punched the gas then realized
his car needed more gas. ``That's fine'' he thought. I have enough
gas to make it to the arcade.



He peeled out of his driveway and sped down the street doing 55
miles per hour. Suddenly he arrived at the arcade. He opened the
door and went inside expecting what he did not find. Instead he
found what he did not expect to find. What he found was a horrific
site.



Blood and vomit and tears streaked the walls and the Space
Invaders. There were kids bodies laying everywhere, torn apart and
still bleeding blood. ``Who could do this.'' thought Bavarius. ``I am
going to catch who did this and find out how he could do this.'' So
he looked around.



Suddenly he heard a movement. It sounded like wet vomit scraping on
sand paper. In a flash he drew his Baratta and loaded a clip. Then
he spun around to face the noise. ``Whoever you are, I have a Bereta
and know how to use it, scum.'' he said.



Suddenly he saw movement. A man or what was once a man or woman
came dashing out from behind Missile Command. {\sc Out\ldots{} Of\ldots{}
Credits\ldots{}!} it screeched in a slow southern drawl. ``No monster,
you're out of life'' said Bavarius as he squeezed the trigger
rapidly and deliberately.



One shot to the head, two in each hand, and one in the heart for
good measure. Also he shot the thing in the legs and nose.



The woman howled and fell back then started licking up blood and
vomit. It seemed to give him strength. So Bavarius emptied the rest
of his clip into the thing's head then reloaded. He blew out her
brains so bad that it exploded in a cloud of vomit and regret.
She's not coming back from that, he thought to himself. Frozen with
guilt, the man slowly began to run.



Then he called the Chief and said ``cased closed.'' as he walked out
to his Camarro. He tried to start it but it was out of gas so he
walked to the gas station and bought some gas and put it in a gas
can then walked back and filled up his car with gas. 

 



