\chapter{The First and Second Stories}
\by{O Tempora! O Mores!}


\section*{The first story!}



The bottle had clouded the room almost as much as the cigars. I
could hardly breathe without inhaling more smoke---it was so bad,
the door opening barely shifted the fog. But that may have just
been my mind.

``I got a case for you,'' he said. ``I been lookin' for this girl
goin' on three weeks now. You find her, you bring 'er to me. For
your trouble,'' and he tossed a stack of bills on the table. The
sound was like a sledgehammer to the skull. ``You got a picture,'' I
asked, the words slurring together in a muddle. He tossed a
polaroid on the table, the sound like a smack to the face. The door
closed, and I passed out.

When I woke up, I was surprised that I didn't choke on the fog in
the room, as thick as it was, and at least now I could see the door
again, with its golden-painted name: Luke Bavarious, P.I. I rolled
out of the chair, and watched the room spin. I'd hit the bottle
hard last night, and I felt the bile rising. I forced it back down,
my head spinning. I stood up, and picked up the picture. She was
pretty, I'd give the man that. But that smile{\ldots} she liked fun. She
liked a lotta fun. I turned it over, and saw a string of numbers
written there. It was too long for a phone number{\ldots} Wait.
One-two-three{\ldots} Ten digits. Four. Two. Three. A number and an
address? This guy coulda picked her up himself. What'd he need me
for?

I picked up the stack of bills, and headed for the door. I grabbed
my coat as I meandered past, and the bills. Past due. Past due.
Late. Hmm{\ldots} this one was already paid for? Since when had I paid a
bill? Advertisement. That damn client who wanted another look
around. Hey. Here's the place. Damn fine building for a pretty
little girl.

I got up to the door, and knocked. A soft voice called, ``Come in,''
and I did. She wasn't wearing much, and it was cool in there. Damn,
but she was pretty. And that was a thin little slip to be wearing
with company, but hey, who cared, it was just us. She walked over,
smiling slightly, and asked, ``Are you looking for me?'' ``A man asked
me to find you, and gave me this picture{\ldots}'' I said, but my mind
wasn't on what I was saying, she was too fine to think about
anything else. I'd been alone a long time, and here she was,
standing real close.

``Aww, don't be all about the work,'' she said, her smile suggesting
such exquisite delights, and her dark, seductive eyes pulling me
into an intimate embrace of desire and pleasure. I felt passion
stirring lazily, swelling in my chest, like an exceptionally loud
burp, but always finding more room to fill, until it finally took
up all of the space it could manage, as it got more and more
intense. Like a storm ravaging my soul, it burned in me, a desire
to have her, this pretty little thing. She saw my need, my want,
and opened her mouth, to say the affirmation that already was
showing through the way her bosom swelled with air, stretching the
thin fabric to its limits, threatening to release her breasts like
racehorses from the starting line, until it suddenly did, and the
smooth skin made me lose track of my own senses, as her smile
deepened and she pulled me close, her soft but firm body pressed
against mine, our two forms moving as one towards the room, satin
sheets already on the bed, a heaven of fabric and lust.

She pulled off my trenchcoat without my noticing, as I undid the
buttons on the back of her slip. Her hands pushed aside the ruffles
of my shirt as she looked for the buttons, like a man running his
fingers through sand to find his glasses lens. I didn't notice she
had undone the buttons until her hands wound through my chest hair,
tugging like a rider at a horse, and pulled me down, as somehow,
like a magician's trick, my pants were lying on the chair, and my
boxers too. She wasn't wearing much under the slip at all, mostly
just skin. There was a little darkening of hair, but my, she had a
fine body. Athletic, too. She knew what she was doing, and I got
lost in the flow, the rhythm, the back-and-forth of it all, as a
flower of light blossomed in my mind, my eyes closed in ecstatic
pleasure and joy as I felt like new life had flowed into my aching
bones and washed away everything that was wrong, and she squealed a
sound of pure delight that rang like a bell in my mind with a
sparkling love and glory as I dropped away, exhausted.

Waking up was hard after what had gone on before, but I managed to
pull myself together enough to smell the iron and the sticky-sweet
smell. My eyes opened, and I saw red. Lots of red, all over the
mirrors and the walls and the ceiling and spilled onto the
bedsheets where we had lain the night before. The room stank of
blood, as I saw spatters across the dresser and sprays on the
mirror, which had dripped down some, and traced red trails across
my image. As I moved on the bed, it squished with blood and oozed
out red, onto the already soaked sheets and into the dark red pool
around me. I saw her body on the floor, bullet holes riddling her
side, and still somehow pumping out the gory flood, slowly, pump{\ldots}
pump{\ldots} {\ldots} pump-{\ldots} as the dark red dried around her, and all over
the room it still rolled down, a sad end to a pretty girl like
her.

I was back where it all started, in the office. There was more
smoke this time, it was like a dream. The booze burned, but not as
much as the memory of her lying there, her vital fluids pumping out
onto the floor, already drowning in blood. She had been so pretty,
too{\ldots} I reached for another bottle, and forgot the glass this
time. It wasn't like it was the taste that mattered anymore, it was
the forgetting. I pulled out more tobacco, and added a little extra
from my hidden drawer. I needed to get rid of these memories. The
smoke was different now, the taste was more bitter, but I didn't
care. She would go away. As the haze took everything, she walked
through the fog and everything else faded, but she was clear. She
stood there, pretty as she was when I saw her first, and wearing a
little black silk thing too, it was so thin and sheer, you could
see every detail, and my, wasn't she fine. She started to pull it
off, and slowly, slowly, it dropped to the floor, too softly to
hear. She turned, and started to dance. I just wanted to forget.
Here she was. Relief. I wanted her to go away. Release. Let me
forget you, I wanted to scream. Let me die in peace! The smoke was
acrid now, burning and black. The pain was fleeting, and the dark
was better. The room was painted red, a red fog that spread through
the smoke to coat the wall, and pour out onto the floor, a sticky,
dark red pool that shined lazily under the swinging light.

fin.





\section*{The second story!}





I stood at the corner of Selby and Rice glaring at the bright neon
sign hanging over The Purple Mermaid Motel.

``Years of being a private detective and this is all I
get?'' I swore under my breath and gracefully walked through
the revolving doors. The dim lighting over the front desk glowed
ominousness, casting shadows on the stained carpet over the cheap
linoleum flooring. I curled my lip and walked cautiously to the
small man perched on a bar stool and gazing down on the desk, only
moving to adjust his glasses and scratch something with a ball
point pen.

``Excuse me, are you David Dawson?'' I asked placing my
hands on the counter, attempting to look intimidating. I quickly
removed my hands noticing a large cockroach scuttling along the
banister.

``Yeah, who want's ta know?'' he continued to look down
rather than up at my face, which was frustrating to begin with, but
to actually question who I was{\ldots} that was another
frustration.

`` Luke Bavarious, Privet detective, per your request.''
I could feel my lips tightening into a straight line as I held on
to the 't' entirely too long. Dawson turned up to face me, a mask
of filth covered his what I assumed white skin and his blue eyes
seemed magnified by his horribly dirty spectacles.

``Yea' came sooner than I espected.'' he stood up and
walked from behind the desk to shake my hand. He shook my hand
entirely too long and pressed his body unnaturally close to me in a
hug. I restrained myself from pushing him away and walking out of
this cheep rat hole, the money was too good to turn away.

``That's what I'm known for'' I muttered, looking around
the room for some clue as to the 'disturbance'

``What seems to be the problem?'' I asked, my voice
taking on the familiar tone of compassion and intrigue.

``Well, some of my regular guest{\ldots}'' there are {\em guests} in
this place let alone regulars? ``say they've been hearin' some{\ldots}''
he paused to think of the word.

``Sounds?'' I supplied and he nodded.

``Damn you are good{\ldots}'' I suppressed the desire to roll
my eyes and simply smiled at the complement. ``Well, I was
hopin' you could make us{\ldots}comfortable again, putten our minds at
rest, ya know?'' oh it would take more than a simple sweep to
put my mind at rest in this place{\ldots} I nodded again and dazzled him
with my 'everything-will-be-okay' smile.

``Show me to the room.''

* * *

I unpacked my tool kit and began scanning the room for simple
signs; rats, roaches, people playing tricks. Luckily, I couldn't
find anything that pointed towards rats and roached, but the idea
of someone leaning into the paper thin walls and creating an 'eerie
sound' made me satisfied. I decided to spend one night in the room
to make sure I was right. Easiest \$400 I've ever made{\ldots} my
thoughts trailed off as I slipped into the semi-attractive bed and
shut off the light. Quickly, I turned it back on and strained my
ears. Calm yourself{\ldots} don't get so worked up. I shrugged my
shoulders and turned the light off for the second time. Nestling
into the pillow, I shut my eyes tight and concentrated on my
breathing.

``lllluuuukkkkkeee'' I sat up straight and looked around
the darkened room. I chuckled softly to myself, the room being
entirely too small for another body to go unnoticed. I shrugged
again and settled back into my routine.

``lllllllluuuuuuuuuukkkkkkkkkkkeeeeeeeeeeeeeeeeee'' I
turned the light on one more time and jumped out of the bed. There
is only a logical explanation for this. The only person in this
piece of crap is Dawson, which must mean he is behind the wall{\ldots} I
silently grabbed my gun and slid a magazine into the belt, leaning
against the wall I positioned myself. I kicked the wall and the
plaster gave way with ease, taking one look inside the hollow wall
my mouth ran dry.

12:21 Standing before me was a large man's body, or what was left.
The eyes were removed and caked blood filled the outer rim of the
sockets, his teeth were broken and jagged inside his mouth, lips
torn off to reveal rotting flesh and maggots. My skin crawled as he
opened his mouth once more and uttered my name.

``llllllllluuuuuuuuuukkkkkkkkkkkkkeeeeeeeeeee'' my eyes
widened in horror and I rushed out of the room, leaving my tools
and clothing behind I dashed down the stairway and into the main
room.

``Dija fix it?'' Dawson asked, holding up the money. I
grabbed the bills and rushed out the door without a word, quickly
across the street and into the bar.

``I quit'' I muttered, ordering my first round.

I had barely begun my first drink before I heard it.

``llllllllllllluuuuuuuuuuuuukkkkkkkkkkeeeeee'' I felt my
heartbeat quicken, my pulse erratic and sweat start to pound from
my veins. He's here? My thoughts seemed childish and rhetorical, of
course he was. I took a shallow and shaky breath, hands and lip
quivering in fear, stood up and walked towards the door. I threw a
twenty on the counter and pushed my way through the doors. There he
stood in the glow of the parking lot, flesh falling off as he
stood.

``lllllllllllllllluuuuuuuuuuuuuuukkkkkkkkkkkkkkeeeeeee''
I cocked my gun and fired one, two, three. I could feel the fire
back effect and emptied my clip into the corpse. He only smiled, or
what I thought would be, and opened his mouth again, saliva
dripping down onto the concrete. My heart thudded against my chest,
ragged breathing tearing through me like a cold blade. I threw my
gun to the side, useless to me now, and closed my eyes. You can do
it! I urged myself forward and threw myself on top of him. My fists
met flesh, tearing and ripping at the body in an attempt to ward it
away. My eyes shut tightly, I continued to pound my fists into the
cold man hoping that this would finally take his retched face from
my memories. I dug through my pocket and took out my switchblade,
releasing the blade I stabbed and ripped at the face tearing it
apart before my very eyes.

12:46
``lllllllllllllluuuuuuuuuuuuuuuuukkkkkkkkkkkkeeeeeee'' I
stabbed and stabbed and stabbed until the body ceased and the mouth
released one final word.

``Luke?'' I opened my eyes and saw Dawson laying in a
bloody pile under me, his face ripped to shreds by{\ldots}my blade. I
glanced around for the body of the cold man, but I couldn't find it
anywhere. My heart began to pound again, filling my ears with
rushing blood, drowning out the screams and chants of the gathered
spectators. I barely noticed the cuffs being slapped on my shaking
wrists or the rough push into the white van. As I gazed out the
small window in the van I heard short breathing and a slight
chuckle. Slowly I turned my head and gazed into the eyes of the
corpse.

``llllllllllllllllluuuuuuuuuuuuuukkkkkkkkkkkkkkkkeeeeeeeeee''

 



