\chapter{The Screaming Night}
\by{Oatgan}





The woman's shouting screams shattered the dark silence like
a broken bone after a high fall. ``Help meeee!'', she
screamed. There was no answering from the good citizens. At the
moment at least. Luke Bavarious, was not exactly a good citizen. He
was less than good, and rushed towards the attack at fast
speeds.



Earlier in the day, Luke was at a tavern. Drinking margaritas and
eating submarine sandwiches at the pool as he always does.
Luke's informant Manitoba approaches.



``Care for a light, B?'' Manitoba holds out a lighter,
literally vomiting fire.



``No way, Manitoba. I don't smoke after the accident.
You know that. Remember?'' Luke responded.



``Oh yeah'' said Manitoba. ``Look, I came here to
tell ya bout all these attacking that happened recently. Word is
some kind of half-man half-monster half-dog is wandering around in
the night and killing people in the dark alleys.'' Luke
finishes his drink and puts the sandwich in his pocket. He got up
and got another drink. This time it is a scotch on the rocks. Cheap
just the way he likes it.



As Luke is quickly racing towards the female screams he hears a
distant rumbling coming from the same direction as the female
screams are coming from. He thought time was running short. Wind
swept through his windswept hair as the cries drifted closer and
closer. He then heard a sound that sounded like a sharp object
tearing into flesh. The girl screamed no more. She was killed
before she was saved.



Luke continued to give chase. He ran until he was tired from
running to much. He ran more and followed the rumbling through the
alleys as the monster left strewn garbage and blood streaks in the
ground. He passes a homeless boy looking through a trash dumpster.
He stops and asks him if he has seen anything suspicious. The boy
replies negatively. He has seen nothing. His mind might change if
he gave him the sandwich sticking out of his dark flowing powerful
trench coat though. Luke says no. He continues chasing.



Luke came to a dead end. {\em Dammit!} What is that? A sewer? Luke heads
down into the city sewer system. The stench is bad. Like rotting
meat from last Thursday. He marches onward. Along the way he finds
spare body limbs. Owner, unknown. He also sees the homeless boy
again. This time the kid gives Luke a warning.



``You will not catch him. And you will not defeat him. He is
too evil.''



``What the hell do you know, kid.'' He says.
``You're just a freakin' homeless
kid.''

Luke pushes the boy down as he sloshes through the filth. The boy falls
face-first into the sewage. As Luke wades he sees a door at the end of
the tunnel he took. The door has a sign on it that reads {\sc This is
  the lair a monster farewell to all whom enter}. Luke pays no heed and
barges through. He sees the homeless kid again.



``How did you get here, poop-head? I thought I ran past you
and I did!''



``Inconsequential,'' said the homeless boy. The boy then
shape shifted into a monster that looks kind of like a dog. Luke
drew his Beretta and fired wildly into the dog-monster. The monster
showed no signs of being affected like bleeding or flinching. In
frustration Luke threw the Beretta at the monster.



``I warned you more than once, human! Now you pay for not
listening to me and not giving me a sandwich!'' The monster
lunged at Luke and pinned Luke to the wet slimy ground. Luke could
not move. He could only struggle. Luke's face was peeled off.
The monster ate his face.



The End?


 



