\chapauth{on time for once}
\chapter{The Playground}



When I awoke I was tied up in a dark basement and the little boy
was standing over me. The first time I saw him I had laughed at him
because he was constantly vomiting, the putrid liquid pouring out
of his mouth and nose as if he were a water fountain of vomit. It
didn't seem so funny now.



Now that I was tied up, he seemed much more threatening. He stepped
closer. His warm vomit was now hitting me in the crotch. Where was
it all coming from, anyway? There was so much of it I
couldn't believe it could possibly have all been inside this
small child. Was his face a portal to a parallel dimension? A
parallel dimension of vomit?



As he pistol whipped me with my own Beretta I choked and giggled
and thought about how I, Luke Bavarious, private detective, had
ended up in this situation.



It had started because the children's playground was always
covered in blood and vomit. Every day it would be cleaned, but
every morning it would be covered in blood and vomit again. This
had been going on for several years now and we had finally decided
to see what was going on. I was assigned to stop the blood and
vomit.



I went to the playground one evening and hid under a slide with my
Beretta and my night vision goggles. It wasn't quite dark yet
and there were a few children still playing. One of them was the
vomiting boy, which explained the vomit. Oh, how I laughed.
Hopefully there would be an equally mundane explanation for the
blood. Perhaps the boy had a beautiful blood-vomiting mother. I
would have to talk to her and ask them to clean the playground
themselves after they were finished using it so the city would not
have to pay so many cleaners. I would offer to help her clean the
playground, and maybe we would end up doing sex on a swing. I like
swings.



I was distracted by my fantasy and forgot to watch the playground
for a few minutes. When I looked up again the blood was there and
the children were gone. I got out from under the slide and glanced
around. What had happened? Where was the beautiful woman? Suddenly
something hit me in the back and vomit sprayed over my head. The
boy! The vomiting boy! He must have been on the slide I was hiding
under, and now he had jumped off it onto my back! I tried to get
him off me but he held a urine stained pillow over my face until I
passed out.



And now here I was, in this basement. I could see now that under
the vomit the boy's face and clothes were covered in blood.
And so were his teeth, his sharp horrible teeth. I knew then that
he had eaten the other children. Now he was going to eat me.
Suddenly, I was sobbing.



A man in a lab coat ran in. He was also vomiting.



``Daddy!'' vomited the boy excitedly.



``Son!'' the man vomited, running over to his son,
``Stop! This one is not like the others!''



He injected me with something. Suddenly, I was vomiting. The man
collected some of my vomit in a beaker then poured it into a
machine. Writing in a language I couldn't read appeared on
the machine's screen.



``See, son?'' vomited the man, pointing at the screen,
``This one is not like the others. It will not grow up to be
evil. The strange results you got were not because it will be even
worse than the others but because it is already too old for your
tests to be accurate!''



``You're right, daddy!'' the boy vomited,
``Let's put it back!'' He injected me with
something else and I passed out. As I lost consciousness I heard
him vomit ``We should try another playground, they seem to
have noticed what we are doing here.''



The next morning I woke up under the slide in a puddle of vomit,
with a bad headache and no memory of what had happened. For some
reason, though, I felt certain that this playground would remain
clean from now on. 
 



