\chapter{The Exploding Curse}
\by{overnightmike}



A dark night filled with trial and unrestiness was ahead. The bar
tender said unimportant things which I heard. A vague feeling was
consuming me like I was consuming alcoholic beverages. When? When
will the signs come again and would they let me live? Being a
gritty person himself the bartender did not question my long
drinking mainly because I am a very mature person. I could not
shake the vague feeling. It was everywhere.



I felt like vomiting but did not. Instead I was glad I had a
large-caliber handgun.



The door to the tavern burst open, but the bartender never saw who
walked into the door because he had died of fright. I saw his rusty
blood. He was the lucky one of the two of us, who were the only two
people in the bar. Besides the signs, which had arrived. At least I
didn't have to wonder anymore. My legs burst open in a liquid
explosion.



My whole being was pain. Excruciating on the floor of a bad bar in
a skid-row section of town. The signs had left but their work was
completed. For now.



I passed out from the pain of having exploded legs. But I woke up
sometime later and poured some booze on them to make the pain stop,
I could not walk, so I wrapped them in dirty, booze soaked bar
towels, which were plentiful behind the bar. I was left to lay in
the bar with the dead bartender who was putrid with corpse-stink.
That was My Fate. My Punishment. My Own Prison.



Everything was quiet. The dead bartender said, ``What's your name,
cursed one?''



``Burke Dreadnought,'' I said, quivering in fear at the talking
abomination from hell.



``Do you know why you are here at this time, do you know what pain
really is?'' the corpse hissed at me, spraying me and everything
with green putrid goo while the words garbled out.



``My legs exploded so I think I can talk about pain,'' I wiped the
blood off of my gratuitous chin stubble while saying.



``Oh yeah, not yet you can't!'' The corpse began levitating and
suddenly I remembered. Bavarious! The curse all of a sudden made
sense!



Summer 1967. I'm a rookie cop, green and not jaded at all and Luke
Bavarious is showing me the ropes of the hard, rain-slicked streets
of Miami. The Haunted House Murder Case. Fourteen people dead in
the span of one night. Bavarious wasn't assigned to the case but he
was the first one to the scene with me in tow. He growled out
instructions, brazenly brandishing his large-caliber handgun like
he always did. We found a kid. Left at the scene. Not murdered
thankfully.



``The Haunting will follow you unless you put an end to the cure,''
the kid said while shaking because he had vomited so much. ``The
curse must be lifted by giving the bones in the basement a proper
burial. There were ritual murders here back in prohibition times by
an evil bootlegger. Now he haunts the house by killing everyone in
it all the time!''



Bavarious growled, ``You make me want to puke! I'm here to get to
the bottom of this!''



After we left the scene I said meekly to the scowling Bavarious, ``I
think we should give those bones a proper burial bacause kids
should be listened to.''



``Ha! Let's go catch some scumbags!'' Bavarious put on his sunglasses
and went back to his squad car. Six years later I quit the force
and started drinking. That was when the signs came to the bar to
remind me of the curse and the kid I should have listened to.



My legs were spewing gore trails all over and I finally remember
that I always carry a large-caliber handgun. I shot the
curse-zombie bartender right between his red devilish eyes. His
last words were, ``Soon, soon you will know the horrible depths of
hell as I know them, Burke Dreadnought!''



I am in the bar still. I will die here but if I could walk I would
go into a basement in Miami, and dig up the remains of the mad
bootlegger's victims and give them a proper burial. I would dig
them out of the same basement they found Luke Bavarious in last
year, raving about curses to this day in a mental asylum.



The End?



 



