\chapter{The Smile}
\by{Paracetamol Boy}



{\em Narrated by Luke Bavarius}



I woke to a darkened room. The streetlights outside my window cast
eerie shadows onto the floor. My mouth tasted carpet. My entire
body was immobilised with searing pain. I managed, with great
difficulty, to turn my swollen face toward my left. The living area
was littered with broken furniture.



So it had come to this. My wife had taken the kids and left me for
dead in what was once our family apartment in the central hub of
New York City. Blood seeped out the open wounds of my trunk and
saturated my dark blue clothing with an even darker sheen. There
the knife lay still, blade digging into the carpet in front of my
face. My own knife, that my own wife had turned on me.



I could hear the soft wails of the police sirens from the streets
below. That was the least of my worries. Despite my dizzied state,
my thoughts drifted to my lovely kids, Johnny and Sasha. I wondered
if I would see them again, if they were safe. The steadily
loudening sirens registered faintly in the back of my mind{\ldots}



Suddenly, I had a flash of mental clarity. It was the insight of a
dying man. I could not fight to live. I had lost too much blood,
the evidence of this mixing with the contents of my voided bladder
and slowly pooling around me like a seeping fountain of death. I
was a broken man. There was the chance an arterial bypass would
keep me alive, but even if I lived there was nothing to live for. I
didn't want to let anyone else think otherwise for me.



The knife was only inches from my face. My good arm, my left arm,
could move but only with mind-numbing pain. Slowly, agonizingly, I
brought the arm closer and closer toward the knife. I grasped its
handle and lifted it from the carpet. Each action was excruciating.
But pain is only temporary, for in death there is the ultimate
release. My thoughts drifted again to Johnny and Sasha, as I used
every ounce of my remaining strength to roll onto my back. I
positioned the knife in front of my chest and closed my
eyes{\ldots}



``Daddy.'' I recognised the voice and opened my eyes. In the dark, I
could see two small silhouettes sitting cross-legged beside
me.

``Johnny?''

The silhouette on the left nodded at me and smiled. The smile had
no lips, only teeth. I shook.

``Daddy, what are you doing?'' the shadow on the right enquired
meekly. Sasha?

``Daddy{\ldots}daddy's going away for a while,'' I whispered. The knife
was still in my hand, in front of my chest, frozen in place.

``Look{\ldots}daddy can't be with you guys for very long anymore. I won't
be alive for long{\ldots}I must go.''

``But you can't go, Daddy.'' The silhouette on the left was still
smiling, the white of his teeth glowing eerily in the darkness. ``If
you go{\ldots}I'll eat Sasha.'' The teeth spread to a grin.



``Johnny{\ldots}'' I gasped. As I looked on, Johnny's grin seemed to grow
wider and wider. The rows of teeth separated to form a hole between
them, and the hole widened to a yawning chasm of unfathomable
darkness. A different voice emanated from the hole. ``Daddy,'' it
drawled. ``If you go{\ldots}I'll eat Sasha.''



Still in immense pain, I balked, speechless, at the two shadows in
front of me, one sitting silently, the other leering at me, teeth
as far apart as a basketball, face torn apart by a chasm.

My vision blurred and it became increasingly difficult to breathe.
The knife dropped from my hand. Between ragged breaths, I gasped
weakly. ``Johnny{\ldots}you have your mother's smile.''



Then, as suddenly as they had appeared, the silhouettes were gone,
leaving only the space they had occupied.



I wept bitterly. 
 



