\chapauth{Peas and Rice}
\chapter{The King}





It was a slow week. Sometimes life is like that for a private eye.
I sat at my desk drinking whisky from a bottle, taking big gulps.
The Yankees were on TV. I love the Yankees. It was already dark
outside.



A noise at the door distracted me. A letter fell noisily through
the letter slot. Intrigued I stood up. It was addressed to me: Luke
Bavarious, Private Detective. But no return address.



I opened the envelope and read the typed note inside. ``Mr.
Bavarious, I need your help. My daughter was kidnapped and taken to
the Service Room at Times Square Subway Station. I need her back. I
can't tell you any more than this. Please help.''



An assignment. I picked up my new Colt .45 although I liked my
trusty Baretta too. I made sure all eleven bullets were in the
clip. I might need them. Then I finished the bottle of whisky and
walked out into the New York night, lighting a cigarette.



I walked to Times Square Station. It was mostly empty. Piles of
garbage sat waiting to be collected. The whole place stank like
rancid meat and decaying flesh.



I drew my Colt .45 and opened the door to the Service Room. It was
dark inside but I heard a strange high-pitched sound. It sounded
like a rat. I fumbled for the light switch and a single dull
40-watt bulb lit the room with a sickly yellow color.



It wasn't just one rat, it was a hundred rats! They looked at me
with vacant, black rat eyes. ``Where's the girl?!'' I demanded but
they didn't answer. Then the rats moved aside and a giant rat
waddled into the room. It was the biggest rat I've ever seen, the
size of a Labrador Retriever. It looked at me and then it
spoke!



``You'll never see the girl again. Don't you know she ran away from
home? If only her mother had listened to her! You have only come
for your doom!'' And then it laughed a high pitched ratty
laugh.



``I know who you are!'' I said, and I did. It was the King Rat of New
York! I'd heard stories but never seen it until now. I drew my Colt
.45 and aimed it at the King Rat's head. ``I'll take you down
fast!''



I fired one bullet, then another, then all of them into the King
Rat. The first one pierced his flesh and tore a jagged wound, and
blood pumped out onto the floor making it slick with red paste.
Then the others hit him and his body started exploding from the
force of the bullets. He was like a fountain in Las Vegas spewing
blood instead of water. Finally he fell down, dying. ``Now where's
the girl!'' I demanded.



``Get him{\ldots} my minions{\ldots}'' the dying King Rat said. I turned around
just in time to see the army of rodents descending on me. Their
tiny teeth bit into me, giving me diseases as I tried to fight them
off. I used all my bullets on the King Rat so my Colt .45 was
useless. I hit one but another jumped on my head and tore my scalp
with its claws. I blacked out from the pain as I crumpled to the
floor, covered in rats as they slowly but surely tore my flesh from
my body. I screamed and a rat crawled in my mouth, and I finally
succumbed to the horror of the King Rat.







Edited slightly to better match theme. 

 



