\chapauth{Phthalogreen}
\chapter{Pearl}



I stand in the shadow. The sounds have been coming again and again
for thirty years. I'm in the old folks' home on 42nd
Street in New York. Right by the alley where it all started. My
hand shakes slightly with my pain meds in my hand.



Pearl, my ten-year-old granddaughter, sits on the bed across the
room. I keep my hat down and my collar up so she can't see my
face. I won't let her get any closer. I don't want her
to see what I've become.



``Why won't you take your medicine, Grandpa?'' she
asks.



``It won't help me,'' I say. ``There
isn't a cure for what I have.''



``It's okay, Grandpa,'' she says. ``You
don't have to take them if you don't want
to.''



Suddenly the nurse enters the room. Nurse Packard. She's the
old hag of the nursing home. Everyone hates her and everyone is
hated by her.



``You there! What are you doing? Swallow those meds!''
she shouts through the darkness.



I look at the pills and hesitate. They are huge and taste
horrid.



``That's it, I'll have to feed them to you!''
Nurse Packard shouts again.



``The pills don't help!'' Pearl cries.
``Don't you get it?''



``Quiet, kid,'' Nurse Packard yells. ``Turn
around,'' she says to me.



``No. He's sick. You don't want him to turn
around,'' Pearl says.



``Sure I do,'' she replies. ``Step out of the dark
and open your mouth.'' She doesn't know my mouth is
always open now. I stay put and pull my coat collar over my
chin.



With that she runs towards me and commences her brutality, grabbing
the pills from my hand. I keep my head down, but her clipboard
smashes my head terribly powerful.



``Grandpa!'' Pearl shouts. ``Stop it, you
hag!''



Nurse Packard ignores her. She giggles and forces her hand into my
mouth. The pills enter my throat.



Unable to control myself, I inch forward. I feel the light on my
legs. Then my chest. Then my head.



``Look away, Pearl!'' I shout. I lift my hat and Nurse
Packard screams at the sight of my scarred, purple face.



As the pills enter my stomach I feel it turning and tightening.
Putrid vomit erupts from my mouth and nose and splatters on Nurse
Packard's face. As the old woman screams, something pops in
her head and she drops to the floor, twitching. The vomit keeps
gushing toward the wriggling body on the floor.



Then my stomach is empty. I fall to my knees. My head is spinning.
But I hear Pearl's voice.



``Grandpa!'' she says. I feel her grabbing my coat.



``No! Don't look at my face!'' I shout.



``It's okay, Grandpa,'' Pearl says. ``I saw
you. I never looked away.''



Suddenly I am sobbing. I realize I was wrong to assume she was
weak. She has the right to see her Grandpa's face. I turn and
look at her.



``Grandpa,'' she says, hugging me. ``I want to know
something.''



``What, honey?'' I say.



``What is your real name? Mommy won't tell
me.''



I think for a moment. Then I pick Pearl up and put her on my
lap.



``My name,'' I say proudly, ``is Luke
Bavarious.''



[edit: typo fixes] 
 



