\chapter{Nobodys Savior}
\by{Pro-Swordbro}





My grandma always said I'd be nothing. I'd approach her with an
aspiration, she'd mock, criticize; ``You're too dumb to be an
astronaut'', ``How you gonna rap if you don't know meters?''. She was
french.



I miss her.



I am a police officer. My name is Luke Bavarious, badge number
\#25912. I used to freelance, I saw the worst this cruel polluted
world could offer me. Drug users; marijuana in their veins and
hatred in their eyes, crooked cops who took bribes and sold justice
to the highest bidder, I think I even saw a man with a tail
once.



However, what worried me most was what was staring back at me in
the mirror.



I bought a new gun recently. From some punk kid in an alley, handed
him a couple crumpled twenties, he handed me this Beretta. It felt
solid in my hands, the metal was cold, cold as this goddamn
December night. I walked out toward 42'nd street with a fresh bulge
in my coat pocket. Something had happened here, the memories
wouldn't come. They rarely do. It's hard to hold on.



My last night in my practice was in this neighborhood, I thought.
Probably busting some drug ring, mabye saved some old lady from a
mugger, or some old drunkard from himself.



Word around town is someone's killing kids. Stabbing them with a
knife, impaling them from behind. A child told me, his name was
Julian. When I heard this I vomited. According to this kid, someone
with a cross on his neck and a knife in his hand was following him
and his little friend. Julian's mom came to pick him up, he begged
the mom to take his friend home. The man had made himself scarce.
Him and the mom drove off.



I gazed around with my eyes, everything was quiet, it was still; it
was as still as it was quiet. How am I going to find this
sonofabitch? The police sure as hell aren't, the ones who are not
incompetent are all marijuana addicts, no help they are.



It was up to me, Luke Bavarious, badge number \#25912 to find this
demon, to avenge these horrible deaths.



My phone rang. ``Just let it ring Bavarious, whoever it is would
provide no help''

RING

RING

RING

I surrendered to it, flipped it open.



Luke.

Yes?

I might have something on that knife wielding maniac you are always
talking about.

What?

Some guy with a crucifix was murmuring to himself near Biddick
Park, this afternoon.

*click*



It was a few hours until morning, The sky was vomiting snow as I
walked to my apartment, the snow crunched under my combat
boots.



I haven't eaten in days, I can't keep anything down. I tried to
watch TV. Something scary was on, It was alright.

As I got up after the movie ended, I could practically swear I saw
a face in the window. A face.



I'm losing it.



I gazed at the clock, it was 6 at night. Where had the time
went?



The stairs proved no more than an organized hill for me, I exited
into the street and made my way to Biddick Park.



People looked at me with admiration in their eyes, and why wouldn't
they? I'm a hero, I'm a {\ldots}savior? No, not that far. I fingered my
Beretta in my pocket.



I thought in my head of Julian as I approached the dimly lit park,
a more brave witness there never was. Goes to show that kids need
to be respected and listened to.



I noticed a man leaning against a building. He was wearing a Run
DMC shirt, I immediately recognized that as a rap group, I'm quite
interested in black culture. I had a hunch he wasn't my man
though.



It was then I noticed a man following a child, twenty to thirty
feet behind, My experience taught me how to spot a tail. I used to
be a cop. I took a route to intercept him, something gleamed in his
hand, this is him. I approached him, and held my Beretta to his
head. ``You there, turn around!'' I shouted. He pivoted and glared at
me, a cross dangling from his neck. This was it, this was the man
who had murdered that kid. His eyes were gleaming black, I gritted
my teeth to keep the vomit down.



He made a sudden move suddenly, bringing his knife up across my
neck. I fired at him.



My neck vomited blood. His neck vomited blood.



There was nothing I could do but sink down to the ground, lying in
the snow, my monster beside me, gurgling; blood? vomit?
whatever.



``You know, you and I aren't that much different'', he giggled.
Suddenly I was sobbing. 
 



