\chapauth{Quovak}
\chapter{A Cursed Memory}


My name is Luke Bavarious. I am a policeman. Recently my wife Vixie
Bavarious committed suicide. I've been sent in to deal with
Jack Rogue. He was supposed to be at the courthouse. I walked up to
the 162nd street mansion where he lived in New York. I slowly
walked up the dark creaking stairs slowly. I drew my trusty
Beretta. I knocked at the man's door. ``Open up!''
I said.

``What do you want?'' He said.

I screamed. ``It doesn't matter. If you don't open
this door, I'll shoot the the lock off with my
Beretta!''

``Fine. Hold on a second.''

``Too late!'' I shot the lock off with my Beretta. The
sharp kick of the gun was like a wave up my arm. It felt good. I
opened the door and went inside. In the entryway I saw a thirteen
year old boy standing in the middle of the room.

``Why weren't you at court?'' I said.

``You don't want to find out what I know.'' He
whispered.

``I think I do.'' I said, aiming my Beretta.

``My parents are getting a divorce. I don't want to have
to choose who has custody.''

The memory of my girlfriend killing herself rushed back to
me.

``Did you see your dad kill your mom? Or did you only hear the
shot?'' I called.

The kid screamed a bloodcurdling scream and ran upstairs. I raised
my Beretta and fired the first shot. He pulled out a gun and shot
me in my eye. The pain stung as the blood pooled onto the floor. I
couldn't help but vomit. The fluids mixed in the pool. He
shot again.

``Why are you doing this?'' I screamed. The blood kept
running down my face. The bullets tore it open. I fired again. The
bullets from my Beretta took the kid's balance. He screamed.
I heard the kid scream as he fell off the balcony into his rose
bushes. The thorns cut through his skin. His blood oozed out of
their holes. I walked over. ``You were subpoenaed. That means
you should have been in court.'' I said. My wounds were still
terribly dripping rusted blood from the wounds.

The kid was screaming and vomit left his torn lips. As he died he
called out. ``Vixie Bavarious didn't kill herself. Your
wife was killed{\ldots} by you.'' He knelt to the floor and
screamed again as he died.

I looked back at a mirror. Past the blood. And the scars, And the
vomit. And I remembered. The sound of the bullet I fired into my
girlfriend's chest. I remembered her blood falling onto the
carpet. Her spine snapping from the force of my Beretta. Her cries
of pain. Her corpse hitting the ground.

I walked past the kid's cut up body. His blood had dried up.
The vomit had caked on his torn vomit-stained pants. A chill rose
up my back. I started sobbing. I would turn in my badge the next
day and become a private detective. Anything to stop my
grief.


 






