\chapauth{raptorred}
\chapter{The Blood Game}


Once there lived a maniacally demented hag. The kind of person
whose cruelty made the blood run cold and the nose hairs stand on
end. She made her dwelling in a blood-red house in suburbia, rife
with infantile girlie crap like odiferous flowers. And those stupid
little porcelain cats which weren't even real cats so they
didn't have blood or guts or anything in them. Also it was
1992.



Fortunately for her, there was one element in her dark life that
kept her existence from being as miserable a waste as a Slip
`n' Slide in December: her perfect son, Luke. Luke was
the age of a 12-year-old, with brown hair and searing obsidian eyes
that were like pits down into his soul and his blood-filled
innards. As sons go, Luke was practically the best. He sometimes
took the trash out. And he hardly ever skipped school or beat up
his stupid little sister until she cried and pooped her pants with
grimy blossoms of baby turds which were sometimes reddish enough to
pretend they were blood. But they weren't.



Luke hardly ever asked for anything. At least not unless he really
really super duper wanted it. And every quivering droplet of blood
in his body boiled with agonizing desire for a Sega Genesis with
Sonic the Hedgehog 2. He wanted it so bad he could puke. Puke until
he shrieked with the euphoric laughter brought on by true
happiness. A happiness he would never know. Not if his scheming
mother had her way.



``Honey, we can't afford it right now,''
Luke's mother hissed from her blood-red lips. ``Maybe
for Christmas.''



But Luke was as clever as he was dashing. He could tell she
didn't really care. She didn't even look up from the
boring pieces of paper covering the kitchen table. She spent most
of her time with those papyrus slips. Far more than she ever did
with him. Luke had had enough.



``You will pay for your cruelty,'' he announced. His
veins bulged with brutal wrath. Blood wrath.



``Lucas Theodore Bavarious! Go to your room!!'' If he
could have, he would have vomited blood in her ugly face. If you
could call the grotesque mask of suburbia a face. But she was on
the other side of the kitchen so he'd probably just get it
all over the floor or something. So he went to his room.



In his room, Luke's eyes went dark, darker than the slick
polish of a brand new 16-bit gaming machine that had his name on
it. His heart contorted into something like a wad of coagulated
bubble gum. Except it wasn't really that much like bubble
gum, it was blacker and more pulsating and filled with the
trembling sobs of jillions of powerless kids before him who had
been denied justice. Also it probably would not have tasted like
watermelons, which was Luke's favorite flavor. It would have
tasted like blood.



Somewhere in Mobius, Sonic the Hedgehog heard his cry.



That night, Luke's mother went to bed. Nobody knew it, but
she had a twisted secret that was vile and also murky. To get ready
for bed, she took out a big secret pan of polish. The polish was
made out of blood. She polished all of the skulls of little adopted
boys who died because they were denied the latest in awesome gaming
technology. She collected little boys like this for a long time in
secret. It was because she was crazy and evil and liked breaking
kids' spirits and tricking them into thinking she loved them.
But Luke was smart. He already knew such a selfish blood creature
couldn't be his real mom.



But when she got into her bed, she heard a sound. It was a strange
sound. It sounded like buttons dribbling blood, only spookier. Then
she heard another, even stranger sound. It was the ghostly wail of
a Super Spin Dash, which was this awesome new move that they just
put in the new Sonic game that lets you go up hills and stuff and
any mom that wasn't pure evil would understand why her kid
had to have it. If a kid didn't have something like that, the
blood that coursed through his slimy organs would start shaking.
And the blood was so angry and so filled with sorrowful hate that
it would also turn into acid. Then his guts would get bigger and
bigger like water balloons, only water balloons filled with blood
instead of water. Until they exploded, spewing blood and guts and
acid everywhere. Then the whole room would melt and the mom's
stupid floral print wallpaper would be ruined.



That's what happened to those other boys.



``Who's there?'' she asked, because she
didn't know what a Super Spin Dash sounded like. If she were
a good mom who bought her son stuff, she would know. Maybe it would
have been enough to save her. She was so scared that a little bit
of blood trickled out of her nose. It smelled like blood.



Then something see-through flickered in the darkness. It was like a
whip, but really it was a cord attached to a controller. The
controller was attached to a terrifyingly awesome ghost Sega
Genesis. The ghost of the console that Luke should have
owned.



Luke's mom tried to scream, but she was so scared that her
blood started to gush into her throat. She gurgled on bloody vomit
as two controllers (because Luke read in a magazine that Sonic 2
would have {\em two player mode} and it'd be more awesome
than sliced blood and that was one of like a million reasons he had
to have it or he would implode into a pile of bloody guts) thrashed
out of the darkness and wound themselves around her neck. Then one
controller started whipping her in the head. She started crying
because it hurt. Then the controller started hitting her harder.
She cried bloody tears this time because it hurt even more. They
mixed with the bloody puke to make a sort of martini that was two
parts blood, one part tears, one part vomit. And all parts
terror.



Then she tried to tear the controller out of the socket. But the
Sega Genesis is way too well made for a mere Mom to be able to
destroy it. It laughed at her with ghost beeps as her skin started
oozing blood for some reason that was really gross and scary. Then
one controller wound itself around her feet. The other kept winding
around her head. Her hair was full of blood and vomit and tears and
spiders for some reason. The Sega Genesis pulled and pulled and
pulled.



``Luke,'' his mom gasped, a trickle of vomit seeping from
her hypothalamus. It made a gooey line in the blood that was
rupturing form her pores. ``I am so sorry.''



But it was too late. The Sega Genesis pulled her whole body in
half. Out of it fell a huge brick of hardened vomit-tear-blood that
was shaped like the inside of her body. It was because she'd
had so much vomit and blood and tears inside of her that it melted
all of her guts and hardened into a shell. The shell was shaped
exactly like a mean old mom. But the Sega Genesis wasn't
finished.



A bell tolled in the distance. The siren for the Red Cross's
Bloodmobile whistled in the night. And the shell started shifting.
When Luke went into his mom's room the next day, there was no
sign of her. Instead was a perfect Sega Genesis. Made entirely from
hard blood.



From the depths of his mom's dark closet a voice echoed. A
voice that sounded strangely like the Coolest Blue Dude with
`tude around:



{\em ``Kids need to be listened to and
respected.''}



Suddenly, Tails was sobbing. 
 







