\chapter{The Six Sides of Evil}
\by{reasonable form}


Barney Flann woke up with a start. With a cube in his mind. A cube
he had never seen before. Looking at his leg he saw his leg hair
barely coming in, because he was 8 years old and his age was
between 5 and 10.

``Barney it's time to stop dreaming!'' Barney's father, Aragorn,
laboriously squeaked.

And then he saw the rectangle that he would instantly recognize in
any situation. Any situation where he was not terrified. And since
Barney was never terrified, any situation.

But now, Barney had become terrified.

Instantly, he sprung into action to repair the rectangular hole in
the sewer under his house.

``Not now father I love you too much!'' Barney suggested to his
father whose veins in his right arm were solidifying into vomit. He
pulled out his auxyacetylene welding torch that he kept on him so
he could weld, and used it to burn the blood that was coming
through the pipe into a solid mass that would fix the pipe.

``That was my mothers blood!'' he yelled to nobody in particular
except for himself he realized in a sudden realization of deja
vu.

As he ran up the stairs to confirm his suspicions that his mother's
body had deflated as the blood poured down the drain. He noticed
another rectangle, but he quickly put it out of his mind and soon
he didn't notice it again. Now that he was in his mothers room he
could see he was correct, and he saw her lifeless body scream with
anguish as it realized its plight.

``THE HORROR!'' he yelped.

But then he noticed something else{\ldots}

``THE HORROR!'' he yelped as he saw that there was a rectangular
sized hole in her juggular.

Could it be that the 3 rectangles he had seen were part of
something bigger? Could it be that they would form{\ldots} the CUBE?
Barney would soon find out that this was the correct case. He
rushed back to see his dying father and discovered him infused with
life energy.

``Father, why are you so energized?'' Barney gulped.

``BECAUSE I HAVE SEEN THE MOUNTAIN TOP AND UPON IS ARE RECTANGLES!''
His father, Aragorn, who was named Aragorn after a particular event
led his father to read Animal Farm, babbled incessantly.

``No it doesn't have to be this way!'' Barney said as Barney pulled
out his Ferrari branded knife and slashed a triangle into his
father's heart so that all of the rectangular juices could flow
safely out. ``thank you son i love you'' his father said as his last
dying words.

And then, his father died.

``What shall I do now? How can I stop this infection of
rectangles!''

But quickly Barney remembered his grandmother, who they had locked
up in their basement ever since her death. He recalled the
basements location and ran to the door. But there was an evil thing
on the door, a rectangle! He ripped out his Saigo auto shotgun
loaded with fourty four magnum cartridges and prepared to fight the
fight.

``This is the most powerful 'handgun' in the world hehe'' he muttered
as he fired the shotgun one handed in the direction of the door.
Instantly, kidney stones rolled out of the door, but the kidney
stones were in the shape of rectangles. It too was horrid. Too
horrid to imagine was possible. But it was that horrid.

And as the millions of rectangles combined to form cubes he knew
that his evil grandmother was the source of it all!

``Who could have created these cubes?'' he recoiled from the vomit
flowing from his mouth and left ear as he realized it was his
grandmother.

And he realized he could not stop the cubes, that he too would be
lost in the face of ev-

``BECAUSE I HAVE SEEN THE MOUNTAIN TOP AND UPON IS ARE
RECTANGLES!''



edited because I can, and because I only want a few misspellings in
my masterpiece. 
 



