\chapter{The Cocoon}
\by{Ridgely\_Fan}

\section*{Part 1}

This place was new.



My eyes took several seconds to adjust to the dim light, while I
slowly drank in my surroundings. My head was throbbing, and my
throat was parched. And it was cold in here. Very, very cold.



I seemed to be in some sort of dungeon, as comical and absurd as
that sounds. Or the kind of thing an insane millionaire would build
to approximate a dungeon. Instead of cold, damp stone walls, there
were cold steel surfaces and unfinished concrete floors. Instead of
a brazier in the hallway, the ambient lighting was set low. They
got the stink right though, and of course the barred entryway that
looked like the door of a jail cell.



I began going through my head, trying to figure out whom I'd
pissed off enough to get myself into a place like this, when I
heard a voice from a hidden loudspeaker.



``Well well Mr. Landon. I see you're awake. I hope you
like your surroundings, you'll be here for some
time.''



``Who are you?'' I shouted. My voice was harsh and raspy.
``Why did you put me here?'' I was on the verge of tears.
If this was a prank or a trick, it was going way too far.



``My name is Bravarious. Luke Bravarious. It's my job to
keep the good people of this city safe, and that means keeping
horrid creatures like you locked up down here.''



This had to be a joke. But if it was a joke, why go to such
lengths? I put my hand to my forehead to think. There was something
slick there. As I retracted my hand I saw it: blood. This crazy
asshole must have knocked me unconscious to bring me here. The
speaker started again:



``Don't worry Mr. Landon, your headache shall soon pass.
Your kind heals quickly, even in your cocoon state. I can see
you're confused. All shall become clear shortly.''



This was some Silence of the Lambs shit. I remembered back to that
movie, the FBI agent said it was smart to get the serial killer to
recognize his victims as human. Maybe I can do something like that
here{\ldots}



``Mr. Bravarious, I can just barely hear you through the speaker.
Why don't you come down and talk to me through the bars?
I'd like to talk man to man anyway.''



There was some silence. He seemed to be thinking it over. After a
short time (surprisingly short) I heard a familiar voice in the
doorway.



``I don't see a problem with that.'' 

\section*{Part 2} 

The man in the doorway was short and stocky. Pudgy even, though it
was hard to tell in his trenchcoat. His hair was thinning, and had
been clumsily combed to the side. His face shone from sweat or
grease. This guy needed a bath. At least it gave me some idea of
who I was dealing with.



``Mr. Bravarious, why did you take me here? Is this a joke? If
it is, I'll keep it between just us guys, you got me good.
Just let me go.''



I hoped he couldn't hear the fear or despair in my
voice.



``I can tell that you're scared Mr. Landon, but that
fear too will pass, as you emerge from your cocoon.''



This guy was crazy, but he was not going to be easy to manipulate.
I know it's not a good idea to feed into the fantasy of a
schizophrenic or crazy person, but I had to know what he was
talking about.



``What do you mean cocoon? Is this some metaphorical
thing?''



``Not exactly, Mr. Landon. You are one of an ancient race. A
race that has hunted humans for millennia. A predator that acts
like a parasite. Your kind leave its offspring in the form of a
human for humans to raise. When that offspring reaches adulthood,
it abandons its cocoon and emerges a hunter. Fast, powerful,
unstoppable, and hungry.



``I'm saying that you are one of these offspring. In just a
few weeks you will emerge. But instead of hunting humans, you will
stay here. I have prepared food for you.''



Bravarious pointed to a corner of the room, where I could now make
out a pile of decaying meat scraps. That explained the cold and the
stench. I wretched and nearly threw up.



``That's disgusting!''



Bravarious appeared calm. ``I thought you liked uncooked
meat.''



``I like a rare steak, not a rotting pile!''



``So your transformation has not yet started.''



It seemed like he had some twisted explanation for
everything.



``How do you even know I'm one of these
things?''



Bravarious started to look self-satisfied. Maybe I'd struck
the right chord.



``It was a simple matter of checking the records at an
orphanage where the last of your kind was known to feed. You had
certain{\ldots} traits. I confirmed these traits by watching you
for the last two weeks. There is no uncertainty Mr. Landon, you are
the monster I was assigned to capture.''



I hadn't seen anyone following me. Who knows if he really
had. It was just as likely that he was lying or had just imagined
it.



Still, how did he know I was adopted? Did he know about my suicide
attempts as a youth, about me dreaming of harming the others in the
orphanage, my insane pleas for them to kill me? The years of
therapy that my adopted parents paid for? How could he know? He
spoke again before I could ask.



``Now Mr. Landon I have other duties to attend here. I must
assume you'll be alright.''



``No!''



I had to think of something quickly. I rubbed my forehead
absentmindedly, breaking the scab that had formed there. Blood
flowed anew. I had an idea.



``Mr. Bravarious, I haven't turned into one of these
monsters yet. That means I'm still human. I'm human and
I'm hurt, and I might die of thirst. Please just give me some
water and some bandages before you go.''



He appeared to think this over very carefully. ``Very well,
you cannot harm me in that state. I shall return
shortly.''



He was right, I couldn't hurt him. What was I going to do? I
started feeling angry at my predicament, angry at this crazy
bastard for locking me up. The anger dissolved my fear. I had to do
something myself, I couldn't wait for the police or
whoever.



I heard footsteps, and crept beside the doorway.



``Mr. Landon, I am leaving your supplies beside the
do-``



Bravarious didn't get a chance to finish his sentence before
I grabbed him through the bars. He struggled at first, but I put a
stop to that by smashing his face into the door several times. An
eye for an eye.



I found the key to the dungeon in his pocket. The maniac also had
an old filthy Beretta, loaded and with the safety off.



As I let myself out and stepped into the hallway, I slid Bravarious
into the room to take my place. I was feeling much better. The joy
at my freedom, and my survival, was starting to cure my
headache.



Just before I closed the door, I smelled the meat in the corner. I
hadn't eaten for days. I started salivating. Looking down at
Bravarious, I felt a new urge. An urge that was new to me and yet
felt timeless. Prehistoric. This all made sense now. Yes, he was
right, it would be several weeks before I emerged, but he
didn't realize that before that came the hunger. I would need
to feed before my transformation. And so feed I did. 

 



% bz We could correct this for the dude if we wanted to
%\by{Ridgely\_Fan}
%
%
%Oops.
%
%Uh, my story features Luke Bavarious' distant Romanian cousin, Luke
%Bravarious, also private investigator.
%
%
%
%Also:
%
%Edited to include the main theme and to fix some grammatical
%problems. 
% 
%
%
%


