\chapter{The Mansion of Horror}
\by{rinski}





Luke Bavarius stood before the haunted mansion of GhostRaven
Mansion. Black bats circled above, haloing the yellow moon. Luke
reached into his pocket. The cold steel of his Baretta reassured
him.



Legend had it the mansion contained untold riches. Luke liked the
sound of that.



Earlier that day a local kid had tried to stop Luke.

``Don't go to the haunted mansion. It's too
dangerous. It kills people. It never loses.''

``I think I can handle myself, kid.'' Luke said,
smirking.



THUD! Luke kicked the mansion's heavy wooden doors open. He
was in a large living room, 50 feet wide. All the furniture was
covered with ghostly white sheets and a chandelier hung ominously
overhead. There were lit torches on the walls.



Suddenly, all of the furniture exploded. Luke shielded his face
with his arms. Splinters tore at his leather jacket. The splinters
reformed into a giant wood golem. The golem surged to life.
It's eyes glowed with arcane evil.



Luke smirked.



He grabbed a torch from the wall. He threw it. The wooden giant
burst into blue flames. It burned as though it were made of tinder
and lighter fluid. The giant fell to its knees in wooden agony and
then unexploded back into furniture. The haunted white sheets flew
back to again cover the furniture.



``Getting the treasure from this haunted mansion will be a
breeze.'' Luke asserted, smirking.



The next room was a gigantic ball room with chandeliers and a
wooden floor. One wall was covered in old oil paintings. The other
wall was a gigantic window with giant red curtains. He could see
the garden. The hedges looked ominous. ``Probably plant
monsters.'' Luke murmured. He took a step into the room.
Suddenly, zombies were clawing their way out of the wooden floor.
Their empty eye sockets were slick with green rot. It glinted
sickly in the moon light. Luke's nostrils were attacked by
the zombie's horrid stench.



Then Luke was attacked by the zombies themselves.



Luke pulled out his Baretta. He emptied a few bullets into the
mushy heads of the advancing undead army. The bullet wounds oozed
blood and pus but the zombies just kept coming.



``They just keep coming!'' Luke joked, smirking.



He had to act fast. He ran around the zombies and their zombie
holes so he wouldn't trip. Zombies dove at him. Luke dodged
the deft attacks. Zombies dove left and right. Barely, Luke made it
to the other side of the room. As soon as he stepped out of the
room there was a flash. All the zombies disappeared and the floor
grew back. The room looked exactly as it did initially. Luke was
astonished. He stepped back into the room. Zombies poured from the
floor like oozing pus. Luke stepped back. The zombies disappeared.
Luke chuckled. He did this for one minute then moved to the next
room.



The next room was the kitchen. Immediately, all of the knives flew
out of the drawers. The knives hovered lazily in the air. Then the
knives flew at him. They cut through the air. Literally. Blood
droplets condensed out of the air. Luke dodged out of the way of
the knives attack. The knives flew past him into the meat locker,
killing the monster that was hiding inside. The knives made quick
work of the monster, then turned to attack Luke once again. Luke
simply shut the meat locker's door. The knives clattered
against the solid iron door. Luke smirked.



Luke entered the hallway out of the kitchen and was immediately
attacked by a giant spider monster. ``What the!'' Luke
uttered. But before he'd even finished uttering, the spider
lurched forward. It's poison jaws opened. They tried to clamp
closed on Luke's arm. Luke dodged backwards as the jaws
clamped shut. The jaws etched a wound in Luke's arm, but were
unable to deliver their venomous payload. In one fluid motion Luke
drew his Baretta. He shot two bullets into the spider's
bulging bug eyes. Two bullet casings clattered on the floor. The
wound belched forth a thick green blood. The blood hissed as it hit
the floor, dissolving it. The spider recoiled. Its insectoid brain
was riddled with pain and fear and two bullets. But it was too
late. Luke grabbed a sword from the wall. He brought it down on the
spider monster's neck. The head was cleanly sliced off of the
twitching body. The spider collapsed in a heap of bloody legs. The
wounds vomited their acidic syrup and the floor kept
dissolving.



``I'd better get out of here.'' Luke intoned,
smirking.



As Luke was escaping down the hall, he saw a room filled to the
brim with treasure. He stood there, mouth agape. He was going to be
rich. He ran into the room. Suddenly, the room shimmered and
disappeared. Luke fell into a void. He screamed. At the bottom of
the void, as far as the eye could see in every direction, was an
unspeakably horrid beast. It was made of mouths and eyestalks and
tentacles. It covered the entire floor in every direction.



Luke retched a scream. He tumbled towards the gaping maw of the
horrible creature. There was no escape. As Luke fell, a figure
appeared in front of him. It was the boy from before.



``The mansion never loses.'' The boy said, watching Luke
fall.



Luke choked on a sob. It was the last sound he ever made. As Luke
fell into the giant open mouth, the monster started biting him
lightning fast. The bites were so fast that the teeth broke the
sound barrier. Luke was dead before he knew it. He exploded into
bloody slices that fell down into the beast's stomach
acid.



``The mansion never loses.'' The boy repeated. He
smirked. Then he disappeared.


 



