\chapauth{rinski}
\chapter{The Monsters in the Night}


Some would say I have seen it all. They luckily don't know
the half of it. I have both seen it all and then I have
additionally seen some more things. Unspeakably horrible things.
Things that would shatter your mind like a car wreck. For me,
it's just part of the job. You see, I am a monster hunter.
The name's Luke Bavarius. And I love my job. Because I hate
monsters.



I was at my office desk. I poured a cup of dark coffee. I
accidentally burned the coffee, making my office smelled like a
raging inferno. I drank the acrid blackness anyway. It tasted like
a punch in the throat. But it's pungency and aroma would keep
me awake. Awake through a night as black as coffee itself. I needed
it: I felt tired and dizzy for some reason. I put my feet up on the
desk. I took another sip of bitter liquid. Then the phone
rang.



My son's voice echoed through the cold, lifeless plastic of
the phone's receiver. I have three sons. They are volunteer
fire fighters. Usually they can't make calls while
volunteering. The call was therefore perplexing.



``Dad? Dad, you are in terrible danger!''

``Terrible danger? Me?'' I scoffed at his
insinuation.

``Son, don't you understand? I have seen it all. What
dangerous fate could possibly surprise me?''



Before anything else could even happen, a smash caught my
awareness. A window vomited glass fragments from its mahogany
frame. A terrible entity was intruding through a now-broken window!
Glass hit the ground like shells from my Baretta. Speaking of
which, I withdrew my steel companion from its sheath. Time to
investigate.



The commotion was caused by a horrid foe indeed. It was a seething
mass of tentacles attached to a pair of sickening butterfly wings.
Parts of it glowed like certain eels can glow.



``Son? I'm gonna have to put you on hold!'' I
predicted, stabbing the ``hold'' button with my left
index finger. I unholstered out my Baretta and flicked off the
safety because there was nothing safe about the situation.



Before the fight had begun, it was over. A mere twenty bullets
reduced the monster to a twitching heap of calamari. The
bullet-riddled monster could have made swiss cheese jealous. An
acrid stench filled the office. The stinks of vomit and blood and
putrid smoke and diherria mingled in an unholy potpurri. Its
pungency induced nausea. My eyes watered protective tears. The
atmosphere of my office was now more stench than oxygen, making
respiration difficult.



I coughed. I holstered my Baretta in its sheath. I picked up the
phone.

``Dad, you have got to get out of your office because you are
in terrible danger!''



{\em Smash!} Another creature erupted into my office. The window
atomized. Glass fragments splashed the floor like razor sharp
raindrops.



``I appreciate your concern, son. But your ol' D-A-D can
handle a few monsters. I am a monster hunter by trade. And the hunt
is on.'' I hung up the phone with confidence.



This monster was no ordinary panther. It was covered in poison
quills that rustled like amber waves of death. Its face was that of
the common fly. Its arms were like a nefarious---suddenly, the
beast attacked, interrupting my mental registration of its
descriptive traits. No matter. My index finger instinctively
triggered the Beretta's firing mechanism. A steel barrage
sonic boomed towards the fiend. Soon it was just another lifeless
object cluttering up my office floor. Blood gushed from its wounds
like a Nile River of rusty fluid, courtesy of Luke Bavarius.



The stench staggered. I coughed, gritting back vomit.



Suddenly, a cacophony of smashes erupted. My remaining windows
exploded in a crystalline supernova. The air was thick with a
dangerous confetti of glass shards and monsters. Eight more
monsters had broken in, causing this turmoil.



``My property value has gone `out the
window.''' I said with gallows humor.



The odor elevated to a living nightmare about burning corpses. It
consumed my senses. I vomited. Twice. Some came out my nose. My
eyes burned. Tears stained my face with anguish and despair. I
faced my impeding annihilation with eternal sadness and morbid
frustration.



``{\bf N-n-noooo-o!}'' I puked out sobs and some of the coffee from
before. I shot blindly, managing to kill one last monster. The remainder
closed on me like a curtain of death. Knowing I was done for, I vomited
one last time. Then passed out.



I awoke later with a start in a hospital. I coughed. The cough
tasted like ash and my mouth felt like a chimney. I called to a
nurse, ``Nurse what is going on?''



``I don't know how to tell you this, Luke{\ldots} but
there was a fire in your office. You inhaled the smoke and
hallucinated. Your son called to warn you, but by that point you
were virtually insane from fumes. Your other two sons were the
first ones one the scene. You{\ldots}''



Suddenly, she was sobbing. I sobbed too. For I had known all
along.



``Y-you murd-urdered th-them with-with your Barett-etta. Then
your third son showed up with more firefighters and you killed him
too.''



I thought I had seen it all. But none of the horrid monstrosities I
had seen could have prepared me. Not for this. Not for a
realization that hit me like the weight of a neutron star full of
freight trains that were carrying my murdered sons. I was the only
monster in this tale.



When I heard the news, my mind shattered like a car wreck. And I
screamed and screamed and screamed{\ldots}


 






