\chapter{Nebulous Cupboard}
\by{Rummanging}





This city is my mistress; it is my wife; it is my secretary. All
that one can feel about a city, I feel it about this one, and more.
My best friend. I watch the public stream past my window, like a
river flowing past rocks, the rocks being my small 1 bedroom
apartment, which was by now dirty and neglected.



When I leave for my patrol, I do not check for my gun. It is as
much a part of me as my toenails are of me. I am forced to bring as
well, my cellular phone. In an ideal world, I could never talk to
anybody, and all would be good, but it is not so I must. As the
rickety door rickets behind me as I leave, I cycle though my
address book.



{\em ABE



CYNTHIA



MOM



PIZZA HUT



DIRECTORIES



INFO HOTLINE}



I ring for ``Abe'', as I am accustomed to doing. A gruff
New York accent shrieks in my ear.



``Bavarious! Thank Christ you rang, something's not
right, need your help immediately! It's coming for me Luke,
it's {\bf comiii} --- ``. I interrupt him. ``Abe,
what is this? Where are You?''. I can tell from the tone of
his voice something isn't right. ``Why didn't you
phone ME if something's wrong!'' I said.



``Dammit Bavarious, I ran out of credit, now get your ass over
here!''. I slapped the phone shut like the jaws of an
overprotective crocodile, and sprinted for Abe's hut. It
would be a long run from here, but I can tell he needed me.



His wooden hut was hidden deep in the forest, the outside seemed
normal, well as normal as it could seem, Abe being an
unconventional character to say the least. In one slick
simultaneuous motion, I kicked the door forcefully, sending the
thing flying inwards, and swept my Beretta up from my ankle
holster, a task made significantly more difficult from the kick.
The lights were all not on, leaving the place shrouded in darkness.
I heard a noise from a closet, and rushed to meet the source. The
thin door was locked, so I shot 6 holes in it, allowing me to see
inside. There was nothing inside but my bullets. I carried on with
my sweep.



The lounge: empty. The kitchen: empty. The bathroom: empty, save
for one poo in the bowl. The Stench was fresh, and strong. Whatever
left this vile gift was still here. I turn my head to check my
countenance in the mirror. I am entranced, until I hear a scream
from upstairs, distinctly Abe. I dart out of the room, and it
lumbers after me, slowly and scarily. I find Abe's shrouded
figure huddled in the corner of a blackened room. ``Abe, is
that you, have you been drinking again? You said you'd
quit{\ldots}'' I enquired. He looked me in the eye, and raised his
other hand. The light was so poor, I could not tell what was in it.
Until he flicked the lighter on. The small light illuminated his
tear soaked face, running down his cheeks, carving streams through
the dirt caked on his face. The dirty rag of material hanging from
the bottle neck became visible. ``I'm sorry
Bavarious'' he whimpered, and before I had the time to react,
to light the rag and tossed the bottle high in the air, shattering
on the ceiling above him. Shards of glass and licks of flame fell
down like hell fire onto his crumpled body. The house was wooden,
and the fire spread like wildfire. ``{\bf Aaaaabbbbeeeeeee}'' I
cried, crying for the loss of a friend. I was forced to vacate the
house as fast as I could, the flames consuming the hut like the
mouth of Lucifer. Just as I was maybe 20 feet from the hut, it
exploded, sending shrapnel every which way. Something rock hard
struck my head, I hit the floor like a rock, out cold.



Some unknown time later, the black mist tentatively receded from my
vision, allowing me to see. It took moments before I recalled where
I was, and I quickly looked back behind me. Nought but a single
cupboard stood. I crawled to it, my legs too burned to work.
Scrambling through the debris, I reached the un-charred doors,
pock-marked by 6 familiar bullet holes. I tried the doors, now
inexplicably unlocked. As the doors swung open, the bloodied corpse
of a small child fell outwards onto me, still clutching his
teddy-bear. I held the child as he held the bear, desperate for
solace in our final moments. I jerked my head back and screamed to
the heavens, and the skies opened. 
 



