\chapauth{Safe Driver}
\chapter{Hell Cab}


``Wake up, Bavarius! Wake up! Wake up!'' The
dispatcher's voice screeched through the radio.



Luke Bavarius was asleep behind the wheel again.



``Wasn't sleeping, just resting my eyes.''

The radio buzzed back ``{\ldots}1977 Ruminate Way, pick
up.''



At night the fares usually tip well. Mostly it's vomiting
drunks with wallets that are just as loose as their mouths.
Luke's been pulling a lot of late shifts driving his taxi.
They help keep his mind occupied from the hand life dealt him. His
wife is gone now; it's just Luke. The cancer came out of
nowhere. It cashed in his wife's last chips. It ate her up
from the inside, destroying their lives. All Luke could do was pray
and make empty promises as the doctors ran their constant tests and
hooked up more tubes everyday. It never went back to being right,
she never got better.



With all of his time being devoted to his dying wife, Luke
ostracized everyone else around him. Even their only child, Bryson
Bavarius was ostracized {\ldots} ostracized with extreme prejudice
that it would make you vomit. Luke's neglecting of the rest
of his family lead to more trouble for them. Bryson Bavarius needed
daily injections to keep his type X diabetes under control. The
injections never came. Bryson accidentally ate an entire bowl of
sugar. The moment the sugar touched his lips, Bryson's face
exploded like a pus filled vomit balloon. He died. When Luke found
his body weeks later, the room reeked of rotting vomit and glucose.
Luke told his wife that the boy could not make it to the hospital,
he was just too sad. His wife got worse with each passing
day.



Luke would never forget his wife's final words; it has
haunted him since that day. ``You lied.'' In her final
twitches a pressurized pocket of vomit burst from her mouth. Then
it was over and it was just Luke and his night shift.



The address dispatch sent Luke to was an empty lot; nothing there
but silence. Luke began circling around the lot. It was probably a
crank call. Out of nowhere the read door is yanked open and a
passenger jumps in.

``Christ, I didn't even see you! Gave me a scare there,
well where to?''

Luke looked into the rear view mirror. The passenger's
familiar eyes were empty and cold. The passenger smiled and
Luke's heart skipped a beat. The smile turned into a
grimace.



``Drive Luke, you're just going to drive.'' The
voice was hollow.



Luke's taxi pulled into gear. None of the streets were
familiar anymore. They turned into endless circles of blurred
buildings and drab scenery. Luke had never been so scared in his
entire life, and he did not know why. He vomited on his lap. The
taste was like the final taste he had of his dying wife.
Bile.



The same horrible voice broke Luke's confusion,

``Keep on driving Luke, we're almost there.''



They made it. Luke Bavarius didn't wake up. 

 






