\chapauth{scarycactusjunior}
\chapter{The Runaway}






Jimbo hawked a giant ball of phlegm between his dangling feet off
the boat dock and stared into the murky water as he watched his
creation sink to the murky inky depths of the lake. Watching it, he
thought long and hard about his current situation with his Pa. Pa
was starting to frighten him with his publicly known alcoholism.
Every horrible night Pa would sit on the porch of the rustic swamp
cabin in the wicker rocking chair by the front door and drink his
Coors repeatedly for hours. And then, with his eyes horridly
bloodshot he would come stomping back into the cabin and find Jimbo
for the nightly beating. Sometimes the beatings were so bad they
would leave Jimbo in a sobbing heap, his blood and tears mixing
together on his lips. Pa wasn't always like this, Jimbo had
vague memories of happier times; the sunshine days of his early
childhood when his mother was still alive and Pa hadn't drank
so much.

Jimbo heard the front door of the cabin slam, followed by
Pa's heavy, booted footfalls. The wicker rocker began to
creak. Jimbo noticed that the sun was rapidly sinking, the drinking
would begin soon, followed by the almost ritualistic beating.

Jimbo thought to himself. He thought that he didn't have to
return to the cabin. He could make Pa come looking for him in the
swamp, at night, while drunk. Decided, Jimbo arose and proceeded to
make his way deep into the swamp, trying to get as far away from
the cabin before full dark made it impossible to find his way
through the swamp. He tried not to think of how the cypress trees
looked like forlorn entities locked forever in their torment
because of the way the fading daylight lit them, or of the stories
his friend Benny used to tell about the Swamp Creature.

The Swamp Creature was said to be a being of such hideous
countenance that it would drive any who were unfortunate to see its
horrible face completely and totally insane. Privately Jimbo
thought it was the thing that had made the crocodile eat his mother
all those years ago. Jimbo remembered the sight of all that blood
on the water; red blood on black water that boiled and roiled like
a vicious tempest. Jimbo shuddered and tried to push those thoughts
out of his mind.

Distracted as he was, Jimbo slipped on a patch of slimy mud and
slid on his buttocks a little way into the swamp-water. He jumped
up quickly and stared wild-eyed around him, looking out for crocs.
His heart was pounding; he could feel the blood pounding in his
ears. Suddenly, he was very afraid. He fought the sob welling up
within him and went on his way. It was too late to turn back.

He saw something then, a glint of gold in the reeds. Bending down
to get a closer look, he noticed it was a badge of some sort. Jimbo
picked it up and felt a feeling dread wash over him; it was a
slightly tarnished police badge. Jimbo read the name on it
aloud.

``Bavarius{\ldots}''

There was a squelching sound behind him, and Jimbo turned around to
come face-to-face with a creature straight out of nightmares. It
looked like it had been a man once, but now it had no eyes and only
one shriveled ear remained. It looked almost half-melted and
inhuman.

Jimbo vomited great jets of putrid vomit into the swamp. Some of it
landed on the Creature and made it even more horrendous to look at.
Jimbo vomited again until he could vomit no more. Tears sprang into
his eyes and he sobbed loudly, vainly. The Swamp Creature moved its
stumpy arm to catch the paralyzed Jimbo and crush him into the
once-chest. It breathed its foul swampy breath into Jimbo's
face as it spoke.

``I am Luke Bavarius.''

At only thirteen years old, young Jimbo went instantly
insane.



Two days later, there was an article in the newspaper about a
bizarre murder that had happened out at Old Man James's
cabin. Old Man James had been found dead in his wicker rocking
chair, a brass police badge shoved into his jugular. He had not
even dropped the beer he had been holding. On the cabin walls
behind him, written in blood and vomit was a single cryptic word
scrawled over and over: ``Bavarius''. Police searched the
cabin and found James's son rocking on his heels in the back
room, wearing only urine-stained briefs and giggling softly to
himself. He was taken into custody and placed in the State mental
hospital, where he remains to this day singing softly to himself
over and over.

``Bavarius.'' 
 



