\chapter{The Book}
\by{Scissorfighter}


Trent Fencer was a bully{\ldots} He liked most to bully children. He
hated all children. Even little Timmy

Ontario. What Trent didn't know was Timmy had found a book. A
horrid book. Timmy was angry one morning and decided to walk around
to clear some steam. He found the book poking out from under the
stairs of the house that he had moved into as his parents had
boughten it recently at an auction for houses that had to be put up
for sale due to the owner of the house having recently been
murdered in the house. It was a horrid house.



The book had leathery bindings and a feint smell of some
body-emitted liquid that he couldn't quite recall. He thought briefly of
pus or urine but decided that wasn't quite it. He then remembered
that he was angry. He angrily threw open the cover and looked at
the writing. It was in Latin so entirely hieroglyphic, but he saw
pictures of instructions{\ldots} Instructions on how to raise the dead.
It didn't take long before he thought of Trent Fencer and felt
angry. He was angry with Trent because Trent loved all of his
friends and hated only him.



Trent Fencer was walking outside some houses early one morning. He
had gotten a message from his girlfriend Trish. Or so he had
thought! It said:



``Hi Trent. Meet me in the graveyard. I'm horny, can you please
ravage my hot body with sex?''



Trent high-fived himself immediately after reading it and quickly
put his feet into a pattern of motion that would carry him to his
destination. He was happy to receive that letter. He had built up a
lot of power. Nuclear power, figuratively, where in this metaphor
his father was the nuclear power plant. His dad told him before he
left that his pants were too low and he should mow the lawn. With
every complaint or chore request, Trent got more and more charged.
His uranium was nearly at full capacity and he needed to pump out
some electricity to the general populous.



He got there and turned his eye-muscles to gaze around at the
landscape. No Trish, only Timmy. Only Timmy and a book that sent
chills deep down into his spinal discs and lodged there. Horrid
book or no, he felt he could find another way to distribute power,
so to speak. His feet had already moved him up to in front of
Timmy's face and he barely noticed. His fist coiled back like a
cobra then launched forward like the challenger shuttle, exploding
on Timmy's cheek. Timmy's eyelids exploded open in a shocked
expression, while his neck exploded out in veins and his mouth
exploded in a red stream of blood.



``What is this book? Why are you bleeding red?'' Trent asked. ``Wait a
minute, red is the color of satan{\ldots}'' His brain had started
figuring out the vicious plot that had fallen onto him. Timmy no
longer looked painfilled and merely stepped back, revealing a
circle that Trent was standing in. Timmy then chanted the
hieroglyphics carefully. It was suddenly a dark and stormy night.
Thunder ripped through the sky like an explosion. The ground
rumbled and out came a putrid hand. The hand grabbed Trent's leg.
The hand them moved up further to his thigh and then revealed it
was connected to a putrid head. The head came from the dirt, the
very embodiment of the word ``horrid.'' Its eyes were sharp and
glaring, its pores were wide open, its earlobes had bulging lumps,
and it was missing an eye.



It had finally stood up from its grave. On its chest was a shiny
badge with the name ``Bavarius'' featured on it. It looked up at
Trent and Trent screamed. Trent stood there, paralized and
screaming. Timmy kept shouting orders from the ancient book. The
water then forced the book to slip from his hand. He bent down to
pick it up then picked it up and held it back up. He took one sniff
of the cover and suddenly knew what the smell was from before. He
dropped the book in horror.



``{\bf Oh my God!}'' Timmy screamed. ``The smell{\ldots} it smells of
vomit.''  With this sudden revelation, he knew what was next. The
Bavarius thing turned around as he knew it would. It stepped up to
Timmy, its hands raised. As Timmy's dismembered head was flying through
the air, his last thought was that revenge is morally wrong and often
hurts the revenger more than the revengee, and it's best to take the
high road in all conflicts.

 






