\chapter{The Monster of Lake Grim}
\by{Sirocco}



I stepped out into the night. The clouds were dark and raining
shadows. The lake was calm. Dead fish rose to the surface. They
shone in the moonlight. I was here. Lake Grim.



I am Luke Bavarious. A detective from New York City. But I
wasn't in New York City anymore. I was at Lake Grim.
Investigating. My shoes squelched horrid vomit noises in the mud.
When I heard the sounds I stopped. I looked around, in a sudden
panic that threatened to overwhelm me. I fell forward and knelt in
the mud and vomited on the ground. Some of it went on my hands but
I didn't care. I was afraid. Reports from this area had
reported strange vomitings in the lakeside town Grim which was next
to Lake Grim. First you heard the vomit noise. And then you vomited
yourself. Then the blood. And then{\ldots} you were never heard
from again.



I stepped up. I knew if I wasn't careful enough I would fall
to the hands of the monster. If they were hands. That it had. The
boy had warned me about this. I had been foolish not to listen. I
looked around and restlessly put my hand near my Beretta. My TWO
Berettas. The breeze drifted through the trees and made waves on
the surface of the lake. My eyes scanned the lake.



``The monster must live in the lake,'' I said to
myself.



I walked down to the lake's shore and looked into the black,
swirling water. I saw my reflection. I was about to look away when
I felt the need to vomit rise from my stomach and into my mouth. I
vomited into my reflection, again and again, blood and saliva came
out too.



``This is horrid!'' I gasped, in between vomits.



A dark, black shape broke the surface of the lake. The monster of
Lake Grim had decided to show its face. I needed to act fast before
it was too late. I leapt back and pulled both Berettas out and
fired them at the shape but it kept on coming. Shells hit the
ground and got stuck in the mud. I tried to reload but the need to
vomit and the fear made my hands too shaky. I dropped the shells
and backed away from the monster.



``My weapons are useless!'' I cried. I tried to swing my
fist but my vision was blurry from salty tears of pain and fear and
horror. And I missed. I fell back on to my face and broke my nose.
Blood splattered everywhere on the ground like a rose trampled
underfoot. Then I vomited into the blood. And then I sneezed. I
turned over and looked up at the starlit sky. The night sky turned
black. The monster was looming over me, ready to do its evil
deed.



``Kill me! Just kill me now!'' I gargled, trying to speak
through a mixture of vomit, blood, boogers, and pus from where the
blood came from. ``Kill me!''



It stopped. Then it walked away, leaving me in the mud and the
grass, shaking without control.



And suddenly I was crying. 
 



