\chapauth{slackerpride}
\chapter{The Area the Moon Ignored}



The moon was glowing, sending its light all over the town. All over
the town except for one part. That was where Detective Luke
Bavarius heading.



The calls came in tonight --- like they had every night for the
last ten years. ``Officers,'' the voices said, ``I
saw something in the darkness{\ldots}maybe a man, I'm not sure.''
``Ya gotta believe me Mac, there is something dark going on
there.'' ``It maybe occult related, I've read
articles!'' No one ever cared enough to believe it, but the
Chief's patience with the never ending calls finally came to an end
tonight.



The same day his patience with Detective Bavarius ended also.



The sounds of his shoes hitting the pavement made a rhythm that
sounded eerily like a heartbeat. {\em Good}, thought Bavarius,
{\em now I won't have to listen to mine} . Bavarius' reached into
his pocket and felt the cold steel of his Beretta on his skin. He
didn't want to have to use it, but he was ready to. {\em That's why I
go to the gun range}, Bavarius thought grinning to himself. His
teeth glowing like the moon.



Suddenly, it started raining. The sky vomited it's tears on
Bavarius, thankfully he was wearing his hat. {\em Never leave home
without it}, Bavarius mused. It was coming down in sheets, like
cats and dogs, and it made everything slick --- except for
Bavarius' vision, which was as sharp as ever.



Chief didn't see that. Chief didn't see anything, except for the
bottom of a brown bottle. No one else knew but Bavarius and he
never said anything to anyone. He had caught chief one night
outside the back of McLeary's puking his guts out maybe ten years
ago. It was tinged rust colored, no doubt a horrible cocktail of
bloody Mary mix and blood most foul. Bavarius and him locked eyes
--- and ever since then they've been at each others
throats.



Suddenly, he was on the outskirts of the dark part of town. New
York City was big, but there were parts that were small. This was
one of those parts. Bavarius took a step into the darkness ---
his heartbeat stopping and blood chilling his body. Things were
different here. They were strange. This was the area the moon
ignored.



That grip around his gun was tight now. Bavarius pulled down his
hat, shielding his face from the rain that was falling. He wanted a
cigarette but remembered he quit last week. {\em Damn}, Bavarius
thought, {\em a Chesterfield would do me good now}. But there was
no time for smoke right now, Bavarius had to keep his vision sharp.
But it was hard, because it was dark. There was no light. The moon
even ignored this area of town.



Then, off to his left, near a diminutive pile of offal storage,
there was a rattle. It sounded like a chain, but Bavarius wasn't
sure. His one strength, vision was compromised by the darkness of
the moonless section of city. The rain fell, filling his ears with
constant buzzing like someone was selling bees nearby at discounted
prices. {\em Crazy thought}, Bavarius thought, {\em but this is New
York City --- anything is possible}.



``I agree Detective Luke Bavarius, a voice came from the pile
of rotting smelly garbage and various garbage cans.



``Who is there?''



``Oh Bavarius, I think you know me well.''



``Listen,'' Bavarius said gruffly, ``I'm not above
firing a shot into those cans. It's dark here and no one will see
anything.''



``He will. He knows everything I know.''



``Who is he,'' Bavaruis asked cocking his gun. {\em What's
going on}, Bavarius thought glancing from side to side. The
academy hadn't trained him to deal with hell on Earth.



``You wish to know what is going on{\ldots}I can read those
thoughts well. I was born with this gift{\ldots}though some might call
it a curse.''



``You can read my thoughts?''



``I can see into the dark corners of your soul Bavarius
--- mind reading is but a minor talent.''



``No bother asking then. Just tell me what's going
on.''



There was a laugh, a hellish laugh that rang off the dark walls
like a booming sonic boom from a low flying jet airplane. There was
more rattling and Bavarius now wished he had that cigarette so he
could shine some light on the area. There was more rattling frOm
that area.



``Just come out --- if you're going to kill me, let me see
you first,'' Bavarius bartered with the thing from the
trash.



Laughing the thing thus spoke, ``Very well{\ldots}you shall see me
and know where I come from.''



The can rattled once more and then, as if on cue, a nearby broken
street light flickered to life. It wasn't a lot of light but enough
to stun Bavarius to his soul. He --- or it --- dragged
itself from behind the can. It was no more then three feet tall.
There were no eyes.



``I need not eyes Bavarius --- I see
everything.''



The street light flickered off again.



``Jesus,'' Bavarius garbled out of his cracked open and
dry mouth.



``Not even close.''



The creature was red and looked like walking vomit mixed with bits
of trash. It smelled like a horrible combination of garbage, vomit,
death and dank darkness. If it wasn't for the constant stream of
rain washing his shocked face, Bavarius' eyes would be blinded with
fear tears.



``That's right, that night you saw the Chief vomiting, that's
when I was born. You see he is not human nor am I. He is my father
--- a creature from the depth of an unimaginable hell ---
he birthed me that moonless night. You are the only person to know
our secret. You will be the only one to ever know. Because,
Detective Bavarius, you shall die tonight.''



And then the creature made his way towards him, quick like a sly
brown fox. Bavarius squeezed the trigger and felt the recoil as he
sent six bullets towards the approaching creature. The bullets tore
through the walking vomit and shattered into the garbage cans
behind him. Laughing, the creature kept coming forward.



Bavarius wanted to run --- his every instinct wanted him to do
it --- but his cop's instincts took over. He was going to stay
and fight even if it meant death. Bavarius dropped his gun, took
off his hat and threw his trench-coat on the floor. He rolled up
his sleeves and glared at the creature like a beast gone
wild.



``Let's death dance you nasty bastard,'' Bavarius
growled, the hair on his neck rising.



``A foolish mistake.''



And then the creature leapt like a dancer towards Bavarius. This
thing was growling, shooting his nasty breath towards Bavarius. But
Bavarius didn't move. He was determined to catch this thing and
body slam it to the cold wet concrete if possible. Perhaps he could
cuff it before the thing got away.



Suddenly, as if God flipped a switch, the area the moon ignored was
awash in moonlight. A beam of it hit Bavarius' badge which hung
from his neck like a necklace. That beam hit the creature and it's
manic laughing changed into horrid screaming. Before it reached
Bavarius and possiblY killed him, it erupted like a fireworks
display.



The bloody vomit creature spattered all over Bavarius's face and
body. His white shirt was now rusty looking with blobs of trash
sticking to it. Bavarius could taste it --- not just the
creature's gooey body but impending revenge.



The rain let up and the moon disappeared behind some clouds.
Bavarius placed his fedora back on his head and put his jacket back
on. He also reached down and grabbed his gun. Feeling inside his
jacket pocket, he felt something. Bavarius pulled it out --- it
was his last cigarette from last week. It would taste gross, but
Bavarius was already knee deep in gross. He struck a match and lit
it up.



Cocking his Baretta, Bavarius stood and grinned. He knew what he
must do next. He knew it was going to be ugly. He took a nice long
drag from his stale smoke and exhaled. He placed that loaded gun
back into his rain soaked jacket pocket.



``I'm coming for you Chief.'' 

 



