\chapter{Reunion Under a Blood Red Moon}
\by{Sleepless Dreamer}



The man stared at the figure wrapped in black sitting on the bench
in the middle of town at 3 in the morning. It was late, but he felt
it was his duty to talk to the lonely person who had seen better
days. After exchanging meaningless talk, the man in green asked the
man in black what placed him in this situation.

``It all started when that Bavarius kid moved in the 3 story
house by the cemetery. That kid, Luke, was a curious little punk,
but he just turned the whole neighbourhood around with his
investigations. That little jerk was probably too smart for his own
good, and brighter than any of the people around him, including his
parents. That kid fancied himself a detective, and he was quite
good at his ``detecting'' work, especially for a 13 year
old boy who listened to no one but himself. He was smart, he was
the first one to see right through the facade that suburban life
provided, he knew how fake everything was.''

The man in green asked: ``so he spotted his mother cheating on
his father or something?''

The dark person replied: ``no, he had been aware of that for
quite a while, he simply realized what was happening in the
graveyard at night. The most of the neighbourhood would gather
around a specific grave, late at night, around this hour, and they
would chant horrible songs of death and despair. A black magic
ceremony of the darkest kind, celebrating horrors man should not
know. Luke was a kid, but he knew what was happening there
wasn't right. His parents wouldn't believe him, and his
older brother, Frank, just said Luke probably had imagined
everything. His brother didn't care; he was 16 and had
started dating a slutty girl. He was more concerned about that then
the darkness that surrounded their house.''

The man in green smiled and said: ``it sounds like Luke was
just in need of attention; he was probably a bit jealous his
brother had started dating. I've seen that a lot in my line
of work.''

The brooding figure replied: ``Luke didn't need these
easy girls to be happy, and he did not invent anything because he
needed attention. He was right. The whole street would gather,
planning human sacrifices. One night, Luke snuck out of his
bedroom, into the graveyard, and observed what was happening. There
was more people than usual, and on a grave that served as an altar,
a girl was bound and gagged{\ldots} Frank's girlfriend. The
ceremony started, and Luke tried to get under the altar to untie
the poor girl. That's when a familiar voice caught his
attention. He could not quite figure out who it was, the voice was
transformed by dark magics. That's when he heard a sound that
will be burned in his memory forever: the sound of the girl's
throat being sliced open. Blood dripped at first, but it eventually
pour over Luke, the blood of this poor girl sacrificed to a dark
god. Luke waited for an hour, and then snuck away from the mass and
washed himself before going back home. The next day, he asked his
brother about his girlfriend, but was told that they had broken up
the night before.''

The man in green said: ``that's quite a story
you've got there, do you need a place to spend the night, I
know a shelter, and I could start seeing you as a patient, you see,
I'm a psychiatrist.''

The man in black looked up and said in a grave voice: ``I know
what you are Frank. I know what you've become. You feed on
men and women's souls and masquerade as a psychiatrist.
I'm here to stop you. I've known it for years, but
I'm not a kid anymore, people listen.''

The man in green snarled: ``Who do you think you are? Luke? I
killed you years ago, I sliced you up like a pig on that altar. You
bleed and cried, you pissed your pants when the knife when through
you.''

The figure in black rose, the street lights revealing his pale
complexion, his emaciated figure, and the darkness in his eyes. He
said: ``you killed me, but you failed to make sure I was
dead.'' Luke grabbed frank by the throat and crushed his
airways. ``You are going to hell, where you will be devoured
slowly by the people you have killed, until all that is left of you
is blood, tears and pains. And it will start over for
eternity.'' The dying Frank let out one last airless shout as
his soul went to hell.

Luke smiled and said to himself: ``Another job well done, and
now I can wear his skin to seem more human. I finally have a life
back.'' He looked up and saw Sandy, the girl his brother had
killed, waiting for him back to un-life like him. Things were
getting better.

\section*{Alternate Ending}

Luke said to himself: ``They always fall for the zombie
make-up.'' He looked up and saw the ghost of his mother, who
asked: ``Are you sure that was Frank?'' Luke replied:
``Yes mother, thank you for guiding me to him, and for saving
my life when Frank tried to kill me.'' ``Don't
thank me, she replied, I've been with you ever since I died,
thank you for not taking these pills that make me
disappear.''

Luke smiled and said to no one in particular: ``Psychiatrists,
what do they know?''

* * *


I actually like the alternate ending more than the original one,
however the alternate one is closer to what I usually write.



Hopefully I managed to make something bad and good at the same
time. 
 



