\chapauth{Smeef}
\chapter{The Old Child}



The chill of the night crept through the streets. I wasn't
even in the Big Apple anymore. I was way uptown.



``I ain't goin' nowhere tonight, Bavarious,''
my partner had said back in the car, stuffing a donut in his mouth.
``That ain't even our jurisdiction.''



If the creeps out there don't follow jurisdiction, then
neither do I. And I'd been tracking this creep for hours,
following on foot block my block.



He was one of those rich creeps. The worst kind. Nice suit but
grey, fat, and scummy. He had a cold sweat running on his
face.



At about 110th Street a kid had stopped me and said ``Don't go after
her. She's weird, man!'' Sometimes kids have the blackest
hearts.



When he turned and waddled into an alleyway, I could see that the
girl was still alright. She was right in front of him, his stiff
hands touching right at her shoulder blades. She was wearing a
schoolgirl outfit. It didn't take a judge and a jury to know
that he was guilty. It sure wasn't gonna take an executioner
to finish the rest.



I stepped into the alley and could see the silhouette of her feet
between his.



``Dead end, pal! No way out! Let her go!'' I drew my
Beretta, and the tactical flashlight illuminated his face as he
swung around.



``It's not me!'' he screamed. ``Thank god{\ldots}
Help me!''



``You have the right to remain silent, and I suggest you do
it! Let the girl go!'' I shouted.



``Get out of here!'' he grabbed the girl and started
flinging her violently.



``Let her go, scumbag!''



He crashed into a dumpster with her, and I saw his head clearly for
a millisecond. I might not get another chance. I might not get
another clear shot.



The flash of my Beretta lit up the alley, red blood sprayed into
the air, and the fat man flopped down like he was deflating.



I ran over to check his vitals. Dead. I looked over to see if the
girl was fine. She was cowered in the corner, crying. I put the
flashlight back on the dead man{\ldots} his guts were torn open like his
torso had vomited all over the place like.



I didn't shoot him in the guts.



No, she wasn't crying. She was laughing. Her awful laugh
sounded like styrofoam on styrofoam. I put the flashlight on her
face. I backed up. She had a face like a ninety-year-old old woman,
a few jagged teeth and black eyes. She had big, bloody hands with
long fingernails. Blood and guts were coming out of her mouth. She
kept laughing.



I shoulda listened to that damn kid.



I aimed again, and she came at me like a spider.


 



