\chapter{Thursday}
\by{Smokey}

\section*{Chapter 1}

Luke Bavarious sat on the sidelines feeling completely helpless as
he watched his team lose yet another game to their cross town
rivals, the Anencephaly High Babies. ``That Dan thinks he's soooo
good at basketball, but one day I'll show him!'' he silently
mouthed to a passerby who made the unfortunate mistake of making
eye contact with him. He decided he had seen enough and couldn't
watch anymore, mainly due to the fact that the game was over.
Suddenly, he had to poop.



Luke made his way to the dumpster behind the gymnasium. As he
pulled his overalls down to relieve himself, he noticed a pair of
girls walking along a path about 25 feet to the right of him . ``I
must have sex to those girls!'' Luke yelled at the birds flying over
head. He quickly finished his business and tossed his diaper into a
nearby tree.



``Oh, you like those girls do you?'' a deep voice boomed from
above.



Luke looked up and saw a large, muscular black man sitting in a
tree branch directly above him. The man hopped down and immediately
began dribbling a basketball with both hands, or ``double dribbling''
as it's referred to in the NBA.



``Sure, I like those girls and I want to lose my virginity by
carefully placing me boner inside of their girl boners, what do you
think about that!'' answered Luke.



''You know what you'd like better than losing your virginity?''
the man coyly asked. ``Never having sex, that's what!''



``Wow I never thought about it like that! Heeeey{\ldots}what's your
name anyhow mister?'' asked Luke.



``My name is AC Green, and i'm a virgin.''



\section*{Chapter 2}

The next morning, AC picked Luke up in his light blue 2003 Dodge
Caravan. They whistled the theme song to ``The Adams
Family'' in perfect unison as they headed to the karate dojo
to learn some much needed self defense.



``You're going to eventually find that women will try
and make you do things you don't want to do Luke, and that
sometimes the word ``NO'' just isn't enough to stop
them from hassling you.'' AC said, his eyes searching for a
parking spot the entire time. ``That's why we're
going to learn some self defense moves today''.



They spent the next 4 hours rolling around the matt and throwing
nasty elbows and flying jump kicks at invisible female assailants,
the rest of the class watching in awe and slight confusion as AC
and Luke kept yelling ``No means no lady!'' and
``That's my penis! You leave him be woman!''



An hour later, as Luke was exiting the police car, he turned and
asked the officer, ``What's gonna happen to him? What
will you do with AC?''



``He's a dangerous man and we've been after him for a long
time. You should thank your lucky stars we caught him before he did
anything to you kid!'' shouted the policeman back at
Luke.



``Well at least he'll stay abstinent in prison!''
Luke said.



Their laughter echoed throughout the otherwise quiet
neighborhood.



Kids need to be respected too!

The End
 



