\chapter{Bavarious Reasons}
\by{SummerGlaucoma}





I am stuck here, in this place of must and yellowed paper. The
place holds over my face a page, a urine-stained billow. My mouth,
a tool of evil and destruction, vomits bile, blood and
giggles.



{\em Who am I?} I thought, trying to hug the thought as hard as
humanly possible.



{\em Who am I? Who amI? whoami?whoamiwhoam---}





My name is Luke Bavarious. I'm a cop. I like the work.



I have a barrette. I keep it with me in case I've got to put up my
1990s supercop hockey mullet and think real hard.



I'm thinking now. What kind of name is Bavarious? It is the steam, the
steam from the Fatherland's best beer region? And why Luke?  Cool hands,
warm heart? Or do I walk in the sky, over to {\bf Gran-Nd-Pa}'s arms, my
left leg caught, with my seven-league boots, in The Barn?



I know we all in this book live in a library basement. Our book is
next to some new kind of backwards comic book from Japan.



When it rains, The Artists' ink runs and lets us visit, and let me
tell you, it's nice to get a furlough -- Okay, fine, that kid who
made us didn't specify breaks. I'm AWOL most of the time. So sue
me! -- in the more -- ahem! -- adult, of those comics. That kid
didn't make any single dames.



Bavarious. Hmf. I don't even know what continent my people live on.
Maybe it's a cover name.



Bavarious.



Bavarious.



Bavarious.



An idea sneaks into my head, slashing its way in through my waxy
ear canal.



I am emitting an evil smirk.



I need to borrow something from Ken-wa over there in Samurai
Land.



\section*{Next Week, Iraq, Ben's Point Of View}



My name is Ben Biddick. I'm a soldier. Do I like my work? Well,
that depends. I don't like gritty food. I don't like being away
from my parents (they're great -- I'll have to tell you some time
when we get a weekend pass about the time I wrote a book of crappy,
embarrassing stories, and they got it published with this vanity
press! Nope. No shit. None here, anyway). But I am proud of what
I'm doing here, for the Iraqi people, and for the freedoms I
love.



Besides, you guys are the tightest buds I could ever wish for. Shut
up, Johnston! Yeah, well, you too!



Oh, rad! Mail call!



It's a package from that Internet forum that told me about how they
loved my stories. Yeah! I'll show you guys later. It's rad.



Weird. Oh, well. I guess the only copy that Abe dude could find was
this soggy thing. I guess it'll dry out pretty fast here once I
take off the bubble wrap.



Why do I feel so -- uneasy?



What was that flicker -- did Abe put some confetti in with this?
Awesome!



{\em But confetti doesn't wear its hair in a blond, barretted
ponytail.



Good Christ--} (he thought)



No, Johnston! Only {\em your} mom sends nudes. My mom is a
saint.



{\em Yeah? Well, you'd look worried, too. If--}



[a small figure darts towards me, swinging the hundred-times-folded
Kyoto steel with maniacal glee]



Luke Bavarious?



``Why yes{\ldots}! ''



But, Luke: How-- Why do you even {\em own} a katana?



``For Bavarious Reasons!''



Look there! {\em I am pointing to the page. A -- How did a he-she
from Japan get there? A he-she with a Samurai House's
medallion--?!}



Luke says some magic words in some prehistoric Asian language,
pointing the sword at me.



I started to shrink and grow more illustrationlike.



I am drawn to the page, as much as I was when I was a kid. But for
not the same reasons. The child walks towards the page. I am
little. I am dressed in the same faux-b-baller shit I dressed in as
a little kid. I am a G.I. Joe-sized High-Topped Son of a
Bitch.



Bavarious is full size now and god is he ugly as a real human. ``I'm
Luke Bavarious,'' he says to my buddies, ``and I'm a cop. Now, let's
see about this noise disturbance -- Where's this horrid Al Q.
Aida?''



Amid the predictable laughter, I hear the Simoom begin to blow. The
book slams shut.



My name is Ben Biddick. I'm a cop. I like my work.





Suddenly, I was sobbing. 
 



