\chapter{Gold Ribbon}
\by{Swanky}



``Those things will kill you, ya know'', Percival
growled, spitting up blood onto his rope-bound hands.

``Don't worry; they're filtered'', Bavarious
coyly said as he blew smoke into Percival's battered
face.

Luke Bavarious wiped his hands of blood, as he had spent the better
part of the past six hours trying to coax the safe combo out of
this man. The night before Bavarious received a clean manilla
envelope on his doorstep. Inside that envelope was a picture of a
boy, inside a large safe, a bandana in his mouth with the words
``Wednesday, 8 PM 50,000 in a duffle bag at 1st and 1st or he
runs out of oxygen''.



Bavarious knew he was a go-to guy, but nothing got his gib like an
innocent kid whose life lie in his hands. Especially little Johnny
Powell, a doe-eyed kid he knew through a local Big Brother's,
Big Sister's program he used to participate in. Johnny loved
to talk, and just ramble on about science and school. He was one
bright kid. He might as well have been his own brother. Or even his
own son. Percival didn't have the money, and he knew that if
he went to the police that kid would be as good as dead. This kid
wanted to be a scientist when he grew up. Not a ball player or
astronaut, but a guy who does experiments. He was just a kid, after
all.



He recognized the handwriting of the note, and the brown shag
carpeting on the bottom of the picture clenched it. It was Percival
Johnson's house. Timmy Johnson's father. A good man, a
family man, but who knows what was going on in his head. Could have
been just money problems or even something worse. But that
doesn't matter. What's important is that he knows the
guy behind that picture. And where he lives.



Shortly after receiving that picture, Luke got in his black,
tinted-window sedan and scoped out Percival's house. The plan
was to camp out near Percival's home, then when Percival was
coming home from work, catch him while he's getting
undressed. Luke had his trusty sidearm and no regrets, save for
what poor Timmy might see. Scarring one life is better than ending
another, he repeated to himself.



Once he made his break into the house, everything was a blur.
Percival was shocked, but gave up a curiously easy fight.
Bavarious' heart was beating out of his chest as he dragged
the man, having been pistol-whipped and dazed, towards his basement
and that unmistakable brown shag carpet. Sure enough, as he threw
Percival down the stairs, he could see the safe out of the corner
of his eye. He just hoped poor Johnny was still alive.



He dragged Percival's laughing and oddly limp body over to
the safe, bound his hands and started a routine of inquiry as to
the combo of the safe.



He put the cigarette out on the shag carpet.



``I'm running out of patience, and soon my knife will
begin to ask questions. And he makes me look like a
gentleman.''

Percival began to come to a bit out of whatever stupor he seemed to
be in.

``Wait, what? Where{\ldots}where am I?''

``You're a few minutes away from losing your life unless
you give me your safe combo, pal.''

``But I'm{\ldots}oh, god, I'm so
sorry{\ldots}okay, 35{\ldots}35, 29, 53''



Luke looked at Percival like a lost kitten covered in flour, but he
had no time to ask why this man suddenly came-to. He propped up
Percival against the wall, but wondered if there was something even
more fishy than he originally thought. He positioned himself near
the safe expecting his journey to be nearly over.



He tapped on the safe like a father-to-be gently tapping on the
pregnant belly of his wife.

``Don't worry buddy, I'll get you out soon''.
He heard nothing.

``35{\ldots}29{\ldots}53''.

Click.

He turned the handle and opened the safe. Just as he was about to
look inside, expecting a sense of relief unlike anything he had
heard before, something happened.

Thud.



Luke slowly came back to consciousness, he found himself sitting
next to Percival, his hands, legs, thighs all bound very tightly
with wire. His head was pounding to hard to try to move, but he
knew he knew small, nimble fingers tied those knots. As he
struggled to raise his head to see the two figures coming towards
the lit part of the basement, he noticed it was little Tommy
holding a clip-board and, perfectly healthy, holding a wrench, was
little Johnny.



``Johnny{\ldots}what is this?'' Luke whispered, his eyes
begin to tear with his inevitable realization.

``Tommy and I are doing our science fair project, remember? He
was testing the effects of his mother's pills on Mr. Johnson.
We ground it up in his orange juice.''

``But{\ldots}what{\ldots}about{\ldots}''

``Part of my experiment was testing the effects of fear on
head injury''

``{\em Part}?'', Percival asked, his tone ever more
hopeless.

The unmistakable sound of a dentist drill could be heard in the
background.

``Yes, Mr. Bavarious. Part.''

Bavarious wept uncontrollably. 
 





