\chapter[What Lurks Behind Our Eyes]{What Lurks Behind Our Eyes: The Horrid Reflection Revisited}
\by{Syphilicious!}





Thursday night, and everything is quiet. Unusual for me, but in my
current settings it should be expected; instead of walking my beat
in the thug-infested alleys of our dear city, I am far out in the
country, at Old Woman McCannshire's place, engaged in a staring
contest with the termites that crawl in and out of the floor of her
porch as I wait for her to answer the door. The middle of nowhere
does not properly describe my location; I'd been driving so long
that I'm probably already halfway out. My name is Luke Bavarius,
and I'm a detective, but tonight I appear to be the guy that drives
around checking under old biddies' beds for monsters.



Even the pranks get men sent out these days. A prank is what I
would have thought this would be, if I didn't know the old woman
calling was too addled to even have a teenager's sense of humor.
McCannshire thinks her house is haunted by spirits, and wants one
of us ``wonderful young men you have working down there'' to come
check it out. I'm almost glad I forgot to bring my spare ammunition
for my Beretta out here; I've used that thing enough today
considering my nerves are just about as shot as those three bank
robbers, and if this goose chase got any more boring I'd probably
put it in my mouth and make brain gumbo.



The unlatching of bolts awakens me from my reverie, and my head
snaps back up into the proper position. ``You win this time,
termites,'' I mutter, wiping a thin string of drool from my chin.
Slowly, the door creaks open, and I am treated to the sight of Mrs.
McCannshire in a wispy white nightgown. Perhaps in the prime of her
youth this might have been something I could have tolerated or even
enjoyed, but the broad has long been in her more tender years of
age, her face has more wrinkles than the wandering Jew's underwear,
and her nightgown is greasy with the mysterious secretions of the
elderly. I try to focus on the mangy grey poodle she cradles in one
arm, a dirty little mutt that she probably pampers like nobody's
business. She really fits the picture of an old bag of bones, and
as soon as she opens her mouth I can tell how far gone she really
she is.



``Are you the detective Officer Dent sent over to help with the
spirits in my house?'' She speaks slowly and clearly, her eyes twin
moons of gawkish innocence. I don't know which kind of dementia
would be worse: the flavor Mrs. McCannshire possesses where one is
magically returned to the age of nine or the other one where you
think the walls are talking to you. Although, considering why I was
here, it's possible she suffered from the latter too.



``Uh{\ldots}yes. Yes, ma'am. Officer Dent is my, uh, superior.'' I stepped
past her and walked inside, trying to ignore the subdued growl the
mutt in her hands had started up upon sight of me. The place was
clean to a point; there were numerous tables and shelves bedecked
with pictures and family heirlooms, all meticulously dusted, but
the carpet was smeared with dirty pawprints and general dust and
filth, it's frayed and ragged material likely not blessed by the
gentle touch of a vaccuum cleaner for years. The carpet and walls
were an ugly matching beige and all the miscellaneous objects,
despite constant care, had lost their luster. The only sign of real
color came from the bathroom behind the door opposite the one I had
come in, wherein an even more hideous bright lime green covered the
small amount of wall I could see around the door.



I turned to face her, reaching into the folds of my trenchcoat and
drawing out a pack of cigarettes and my lighter. ``Now, what seems
to be the problem here?'' A lazy puff of smoke floated serenely past
my raised eyebrow from my now lit cigarette.



``Well,'' she said, setting the dog down onto the carpet where it did
an annoying little dance around our legs, barking and whining,
``I've been noticing things for several days now, but only this
morning did it get really bad. You see, every time I use the
bathroom I feel someone is watching me.''



``How can you tell?''



``Well, at first it was just an uneasy feeling. But then I started
hearing voices that would say things that I couldn't make out. Then
I started seeing faces out of the corner of my eye or in a
reflection. And this is happening quite often, mind you. It's
happened every time I go in there, and these days I tend to{\ldots}oh,
how should I say it{\ldots}do my business more often, mostly because
my--''



``I understand, I understand,'' I said hurriedly. ``Please,
continue.''



``Well, uh, this morning, I saw a face in the mirror behind me. And
I didn't just see it, either; it was directly behind me, an entire
person, and he didn't go away until I turned round.''



My eyebrow, which had just started to head home for the day, turned
right back around and marched up my forehead. This sounded
legitimately interesting. Whatever had actually happened, seeing a
person plain as day was a lot better than imaginary sounds or
tricks of light that even happened to people who weren't sitting
outside Death's doorstep in motorized wheelchairs. There was really
only one thing to do.



``Well, I guess you'll have to show me the bathroom then, Mrs.
McCannshire.''



``Right you are, dear.'' She seems to notice that my gaze had strayed
to the pictures on the small table next to the front door, and as
she hobbles past me towards the bathroom she begins to talk about
her dead husband. Half listening to her talk about the dangers of
late term prostate cancer and wincing at the intimate descriptions
she gives of the times she went with him for his checkups, I search
for an ashtray and find one nestled in between boxes of tissue and
stack of gardening books. I rub the flame out and leave the stub,
resolving not to smoke any more until I leave the house. The old
woman doesn't need all that smoke.



As I join her in the bathroom, I see that her poodle has the same
idea. It flies past me and sits whining at her feet until she
relents and picks it up again. I stand next to her and look around
the room. The mirror is old but clean, and the porcelain throne in
the corner is the same. I look into the sink, and from the short,
curly gray hairs lining the rim I deduce that she washes the dog in
it; either that or she's more up on the trends of women of today
than you'd think of a gal her age.



The horror of the thought further distracts me, and I begin to
develop that thousand yard stare as she tells me about the various
scary encounters she has experienced while voiding her bowels,
unnecessarily clueing me in on the second part in her stories too.
Technically I am looking at the hot water handle, but I am miles
away, back on a real cop's beat or in the arms of a good woman,
whichever one does a better job of distracting me from her current
tale of a mysterious voice whispering in what she thinks is Latin
and the effects of the creamed corn she had with lunch two days
ago. Suddenly I spy in the reflection from the mirror that the dog
has the same idea. The yappy little thing now sits silent and
unmoving in her arms, staring intently into the eyes of its
reflection.



At first I am grateful for the relative silence that its new object
of interest has provided, but after a minute it begins to make my
skin go all goosey. I've never seen a dog sit that still for
anything. I slowly move my hand in front of its face, nodding to
show Mrs. McCannshire I am listening at a pause in her latest story
involving the cupboard swinging open and almost hitting her in the
head and how the fright really helped ``loosen things, down there''.
I pass my hand back in forth in front of the dog's vision to no
effect. In a moment of clarity I drudge up the dog's name out of
its owner's ramblings.



``Jasper! Hey, Jasper!'' At once the dog is a flurry of motion,
leaping out of her hands and latching onto the watch around my
wrist with its teeth. I stumble backwards into the main room and
fall to the floor, frantically batting at the hideous ball of fur
as it growls like a recently castrated bear. Instinct takes over;
my mind recognizes when I am in a fight for my life even when the
opponent is a 15-pound owl pellet. Without thinking I wrap the palm
of the hand it grips around its head and bash it repeatedly against
the edge of a bookshelf next to me, then stagger to my feet and
swing it around the room, screaming to match its rabid cries. All
of a sudden it flies free with a high pitched yelp and collides
with the table on which the ashtray rested and the table and its
contents tumble to the ground.



I approach cautiously, waiting for my opponent to make some sign of
life. At once the small pile of picture frames and knicknacks
erupts as Jasper flies straight towards my face.



I have anticipated it; it passes fruitlessly over my head as I lean
backwards almost parallel to the floor, and I hear its frenzied
growling suddenly muffled. I push my spine back into place with one
hand and spin around only to see Jasper hanging from the ledge of a
desk, his jaw wrapped around it and his teeth grinding into it as
if he imagined it to be my arm. I act quickly, sparing no mercy.
With several steps I come upon the helpless creature and I lift a
booted foot to hover a foot away from the back of its skull.



``Chew on this, pooch.''



There is a loud, wet crack as its skull explodes like a balloon
filled with bones and blood. It's corpse falls silently to the
floor, followed by the lower half of his jaw and head. The top half
rests on top of the desk, firmly embedded into the wood. I curse
silently to myself and wipe my foot off on the carpet, leaving
behind a red smear flecked with hair and bits of bone.



All at once I come to my senses, and I turn to see Mrs. McCannshire
standing at the bathroom door. For a second we both stand staring
wordlessly at each other, then she utters a soft cry and flees back
into the bathroom. I hear a soft click as she locks the door behind
her.



I sigh and walk over, knocking on the door. ``Mrs. McCannshire, I'm
sorry about Jasper, okay? I shouldn't have{\ldots}done that, but he was,
I mean he was attacking me. There was nothing else I could
do.''



I continued to apologize while I listened to her sobs, trying to
look anywhere but back at that head, or that part of it, those
sightless eyes silently judging me. I've killed people before in my
line of work, and I see their faces when I close my eyes, but now
this mutt was getting to me more than any of them ever did. It was
an irritable little thing, but why did it up and attack me like
that? What did it see in that mirror?



I notice that the crying on the other side of the door has stopped,
and for a moment I feel relief. ``Mrs. McCannshire, if you can just
come out here we can talk about this. Again, I'm sorry about your
dog, but--''



I am interrupted by the click of the lock, and as the door slowly
comes ajar I help her open it. She stands there, head down, and she
looks so depressed that I can't help but resume my apologies. ``If
there's anything I can do to pay you back for what I did, you name
it. I really can't tell you how sorry I am, I'll get you a new dog,
whatever you want. I'm sure I{\ldots}could{\ldots}uh{\ldots}''



The look in her eyes when she raises her head is different than
what you'd think a hysterical old woman would have. They're more
intelligent than they were before, those eyes, and they seem to
possess more menace than I assume an old lady like that would be
able to muster.



One bony hand wraps around my throat with otherworldy strength,
choking off the rest of the sentence. She lifts me off my feet,
pulls back, and for a brief moment everything is serene.



Then I hit the wall. I slide down next to the open front door, and
after my eyes uncross and the black in front of my eyes goes away I
use the knob to pull myself up. I check for broken bones and don't
find good news in the ribs area, but other than that I am fine, if
bruised.



``Well, you've got a good arm, I have to give you that.'' I think
over my options, running my tongue over my teeth. I can't hurt her;
she's obviously just possessed by whateve possessed that dog in the
mirror. I have to get the spirit out of her, or incapacitate her,
but I don't know how to perform exorcisms and at her age a gust of
wind could kill her. Although if she's able to throw like that
maybe she's a lot stronger in other ways too. What if I tied her
up?



Something makes my train of thought come to a screeching halt. It
hasn't reached the station, it's gone straight off the tracks.
There were no survivors.



My brain is recieving messages my tongue shouldn't be sending. It's
not finding something that should be there. I grab a polished
silver cup off a table and flash my teeth at my reflection. There's
a black square where there should be a nice little white one.



I've lost a tooth.



This bitch is going to die.



I toss the cup and pull my piece, my finger already on the trigger.
Worse men talk about how their guns sing songs that only ever have
a few notes; that's played out, and anyway my Beretta never saw the
appeal in singing. It yells, and it only ever needs to raise its
voice once to win an argument with someone.



As I aim down the sights at the old girl now barrelling towards me
from accross the room with a horrifying screech, I recall something
about not having ammunition, and I anticipate the empty little
click. Cursing wildly, I hurl the gun at her, and it bounces off
her forehead ineffectively. I reach for the knife strapped to my
leg down at my ankle, but it is too late; she knocks it out of my
hand with one swift strike just as I am bringing it up and it
clatters against the wall. She slams me up against the same patch
of wall that I'd said hello to twenty seconds ago and holds me at
arm's length against the wall, my head more than two feet higher
than hers and my feet off the ground clattering against the wall.
Both hands are wrapped around my neck and I am rapidly losing
oxygen. You need to do something now, I think. Or you're done,
Luke. You're done.



Frantically my hands search for something, anything, to fight her
off with, finding nothing. I'm simply too far off the ground to
reach anything. I turn my head as much as her steel fingers allow,
and through my darkening vision I can barely see an umbrella stand
with one large black umbrella in it. In vain I stretch my left hand
towards the handle, my fingers finding air and then brushing the
handle. I strain as hard as I can as the pain advances and my sight
blackens, and suddenly I have a grip, I grasp it with the very tips
of my fingers, bring it up to my hand. She is laughing now,
piercing and mocking, delighting in her triumph. She doesn't keep
it up for long. I raise the umbrella high above my head then stab
it down into her open mouth and throat, pushing it into her
esophagus as she spits and gurgles, her hands clutching even
tighter at my neck. The handle is just past her teeth, my hand
gripping it firmly even as she bites into my wrist. I use my thumb
to find the release and push it up.



The umbrella is spring operated, the fabric edged with sharp metal.
Her neck evaporates in a cloud of blood and her head shoots up into
the hair, twirling in the air like a basketball and falling to the
ground with I and the rest of her body.



After a while, coughing and wheezing, I push her corpse off of me
and use the blood-soaked umbrella to stand up. As soon as I try to
walk towards the nearest chair, I stumble and trip over her head.
Standing up again, I look back down at the bloody mess on the
carpet and on me. I feel bile rising in my throat, and I turn to
run to the bathroom.



I push past the door and stagger to the sink, where I vomit noisily
and stand for a while, staring into this puddle of my own sick.
After what seems like forever I look up and into my reflection in
the mirror. I am hunched over the sink, my hands still grasping the
sides, my mouth hanging open and a thin trail of vomit hanging from
my lower lip. My eyes are wet with tears from the choking and the
vomiting.



Truly I am a pitiful sight. I give myself a weak smile, as if it
will cheer me up. I can't help but notice that something is off in
my reflection, but I can't think what. Then I tongue the gap where
my tooth used to be. My reflection does not. It still has the full
set.



The reflection straightens its back and wipes the vomit away, dries
its eyes with the sleeve of its shirt, and all I can do is stare in
dumb incomprehension. It is the same short black hair, the same
baby blue eyes, the same trenchcoat, the same man, yet it moves of
its own free will. It is me and yet it is not me.



It has an almost condecending look in its eyes as it reaches down
below the sink, to its ankle. It comes back up, my knife in its
hands, its knife, and I cannot move a muscle.



There is a flash of metal. He cuts through my throat like
cheesecake. The arterial spray gives a good portion of the shitty
green paint job a new coat from the opposite side of the color
wheel. There is a brief sense of motion, and I taste ceramic, my
body thudding to the bathroom floor. I move my mouth wordlessly as
red begins to creep along the grout in between the white tiles. I
hear a shuffle of fabic as my other self steps through the mirror
and lowers himself from the sink to the floor. He steps over my
body, taking care to not step in the advancing pool of blood.



My vision begins to cloud for the last time as he casts the knife
absentmindedly down in front me. It slides to a halt next to my
forehead. He begins to walk towards the front door, then stops,
turns around. He walks cooly back to me, crouches in front of me,
grimacing at the blood that is in danger of soiling the knee of his
pants. He looks me in the eyes, and begins to say something, then
thinks better of it. He does nothing for a second, simply watches
me dying, then reaches over, placing an index and middle finger on
my eyelids, and then he slides them shut.



``Good night, Luke.'' 
 



