\chapter{The Homeless Monster}
\by{TarDolphinorShark}





Luke Bavarious sat weeping in his rust colored apartment. The kind of
apartment that wept pain and vomited sorrow from every bowed ceiling
tile to every dinged and dingy wall. It had been three weeks since that
fatal night and he just couldn't get it out of his head. His once normal
life was twisted into a tormented and nightmareish existence. As he sat
cleaning his Beretta, the very Beretta he was issued from the precinct,
he remembered that fateful evening. Rain was vomiting from the sky and
it sounded as if a thousand wounds were spilling mucus and pus from
their pierced membranes. Luke walked down the street when suddenly he
saw a sobbing mess of a man. Homeless scum he thought. This man was
wearing a disheveled burlap sack with tears that looked like the ripped
flesh of a person who was left for dead long ago. Luke grimaced at the
homeless man, thinking to himself ``I'll bet this is the guy the chief
told me about, I won't have any noise complaints on my watch!'' Suddenly
he exploded into action drawing his Beretta he steadied it at the
homeless man who whimpered at first, but gradually started to let loose
a blood curdling scream that smelled of death and reeked of vengeance.
``{\bf You let me become this mess of a human!}'' the homeless man
shouted. He leaped at Luke arms flailing wildly and razor sharp
fingernails digging into Luke's arm and revealing the rust colored life
force within him. Luke's Beretta skittered across the alley just out of
reach. ``Without my Beretta I will have to handle this mad man using my
bare hands'' Luke thought to himself. As he exploded forward lungs
heaving and arms outstretched he made contact with the man. Wrapping his
arms around the homeless man's neck he wrenched and wrenched until the
neck split like a ripened banana, spilling a vibrant rouge all over the
asphalt. The gore was thick, and layered in between Luke's fists which
made it harder to grip his now reclaimed Beretta. As he steadied his
shot, he kept feeling a nagging suspicion in the back of his Anger
filled mind. He knew this man once, but he could not place it. ``No
matter.'' Luke thought, This man is a burden on society and must be
dealt with.  Luke cocked the hammer of his Beretta and as the hammer of
justice falls on those who do wrong, so did the hammer of the Beretta
fall on the firing pin launching round after round into what Luke
considered human garbage. The man's skull exploded and his chest lit up
with the continuous barrage of hot lead pouring from the only real
friend Luke had, his Beretta. The homeless man winced one last time as
snot and spit and vomit erupted from his mouth, eyes, and nose like a
morbid fountain. As he rolled over to die, Luke saw something in his
hand. Luke crouched down to gaze upon the item, and noticed it was a
picture, a picture of a familiar person.  {\em Luke Bavarious}, but who
was the man in that picture? Luke stared at the man, and then the
photograph, the pieces finally coming together. ``Father'' he thought,
as he clutched the picture in his hands like a hawk clutches a dying
mouse. If I would have known you'd end up like this I would have dropped
out of the academy, but I made my choice, and you made yours.  ``Nobody
makes noise on Luke Bavarious' watch!''  Luke said as he chambered one
last round, and placed it right between his rotting father's eyes.

e: for title 
 





