\chapauth{taurapo}
\chapter{The Child}


Luke Bavarius stared into the barrel of his Beretta, if only he had
the guts to pull the trigger of his Beretta, He nearly got erection
thinking about how the bullet from his Beretta would tear his brain
in half and a shower of blood would vomit from the back off his
head into the wall.



Suddenly he heard a scream come from the apartment above him,
without hesitation he drew his Beretta and headed up the
stairs.



It is there that he witnessed a sight that made him vomit harder than he
ever vomited before, a child who couldn't have been older
than a year or six was being raped by what he could only describe
as a extremely hairy ape.



There was blood and vomit all over the floor as the oversized ape
like creature was endlessly pounding away on the child, Luke
Bavarius lifted his Beretta and pulled the trigger shooting the
abomination in the eye socket.



After the smoke cleared from his Beretta Luke Bavarius could
finally inspect the creature, he was shocked when the creature was
nowhere to be found, the only thing he saw in the hallway was the
lifeless corpse of a dead man.



A closer examination gave room for the ugly truth, the bullet form
Luke's Beretta had penetrated the skull of the now lifeless
corpse that Luke Bavarius recognized as belonging to Raymond Von Strathburgh: an
ultra-conservative right-wing Christian with a Ph.D.\ in
Creationism.



The thought of what he just did shot into Luke's mind faster
and harder than the bullet shot from his Beretta, his stomach
growled as vomit shot up to his head. But Luke Bavarius
couldn't open his mouth due to shock.



While pressurized vomit was shooting out of Luke's nose
another tenant ran into the hall and witnessed a sight that made
him projectile vomit down the stairs of the building, Luke realized
he couldn't allow the man 'a witness to the horrible vomit
inducing crime' to live.



Unwillingly Luke raised his Beretta for the slaughter of
another innocent man, upon seeing Luke take aim the man froze with
fear while simultaneously shitting and pissing his pants, the
horror of the situation dawned upon Luke Bavarius as he decided to
do the thing most fitting.



He shot his Beretta, as his Beretta fell inside a huge pool of
blood mixed with vomit the now lifeless body of Luke Bavarius let
go off its boundaries and shit and piss flowed freely out of his
lifeless corpse.



The hall Stank with the stench of piss, Vomit and shit. The police
declared it a health hazard and had the entire block evacuated, all
but one officer who entered the building projectile vomited unto
another officer.



The tenant who witnessed the horrible crime went insane and was
sent to an asylum where he promptly killed 3 staff members before
committing suicide with Luke's berretta.



Two weeks later new tenants found the lifeless body of a little
girl inside Raymond's flat, she showed signs of repeated
sexual abuse, her rust colored dress was soaked in blood and semen.
Raymond's semen.


 



