\chapter{Deja Vu}
\by{The Bananana}


Luke awoke in a bed.

He stared at the ceiling; his head ached, pounded as he struggled to sit
up. He was in a clean white room.

There was a noise. Familiar. Welcome.

The window, with drawn curtains yellowed with age, easily let light into
the room. The sun flooded the room, bouncing off the floor with a soft
mahogany glow, and gave the entire room a hospitable warmth. The
blanket, worn and frayed with use, was nonetheless comfortable, and only
added to the rooms ivory radiance. Beyond the tarnished brass rail
footboard was the only other thing in the room that wasn't. A black
door, defiant and bold, contrasted the pearlescent efforts of the rest
of the room.

Beneath the door drifted the smell of home. Of warm bread. Of eggs. The
sounds and clatter of morning seeped through as well; of voices
murmuring, talking, laughing, accompanied by a symphony of pots and
pans.

Luke swung his legs over the side of the bed. His head still ached, but
it was lessening; he still couldn't remember a thing, everything before
waking up just felt like a hazy dream. He searched the room for his
personal affects to no avail. No shoes or clothes, no wallet or keys,
and most importantly, no holster.

He didn't like any of it but, at least for now, he felt in no real
danger, and decided to take a look around and see what he could find out
about\ldots about everything.

He stood.

He savored the feel of the sun warmed floor. He stretched, reaching for
the speckled ceiling before he lost his balance and feel back onto the
bed. He lay there, basking in the light, when he began to listen more
closely to the sounds behind the door.

That voice. He recognized it! The other too! He knew them both.

No, he thought. He had to be dreaming. There was no way he had heard
right.

He got up and turned towards the door. Behind him, through the window,
the trees began dancing lightly in a sudden fresh breeze.

He stepped to the door, and reached for the knob. He felt a warm heat
radiating from the door. But the voices persisted. He had to know who
was just beyond the door. He grabbed the knob, and instantly recoiled in
pain as the burning hot steel bit into his hand.

``What are you doing'' asked a young boy from the corner of the room.

He had startled Luke, and was lucky the cold steel of his Berretta wasn'
t weighing against his chest like it normally did. The child, no more
than 10 years old looked pale and unwell. He looked as though his mother
had dressed him for church, black Sunday suit, shined black shoes, even
his jet black hair looked as though it had been slicked back by an
overbearing mother.

``Wha\ldots who are you? What am I doing here? Do\ldots Do you live
here, is this your home''? Luke said, studying the strange child.

``That wasn't part of the deal'' the boy replied eerily un-phased by
Luke's questions.

Deal? Luke didn't know what the kid was talking about.

``Don't open the door'' the boy warned.

Luke knew what was on the other side. The voices he had heard, the
voices he could hear right now, were of his family. His wife. His
son. Sitting, waiting. He could hear them now, as he listened, he could
see them in his mind. Her red locks swaying and bouncing as she prepared
their breakfast. His boy, sitting at the table, his feet dangling from
the chair, smiling and laughing.

The young boy continued.

``Don't open the door.'' He said again.

The room grew dark.

Luke looked outside, and watched as the trees now shook and swayed
violently amidst an angry grass sea, heaving beneath the dark sky, as
rain began to pelt the glass.

``What are you doing here? Who are you?'' Luke tried again.

``You're not listening.'' the boy's eyes narrowed and he carried on,
``Enjoy it. Lay back down this time. Stay and enjoy it.''

The kid must be sick, Luke thought to himself, he's not making any
sense.

``I've got a son about your age, he's right in there'' Luke said
pointing to the door, trying to distract the child, ``Do you have any
friends? I'm sure my boy will play with you. Do you like pancakes? My
wife, she makes the best pancakes.''

``Luke'', the boy cut him off, ``Your son and wife are dead. They've
been dead, since the fire. You know that. You know the deal. Stay
here. Enjoy it.''

``What do you know about my wife and son? What do you mean they're
dead.'' He stared at the child, ``Boy, I know your sick but you can't
talk like that, it's not right. Listen, listen to them, can't you hear
them, they're in there right now, look I'll show you'' Luke turned to
the door.

``Please Luke,'' The boys face was unchanged, his voice placid but
firm. ``Don't open the do\ldots{}''

``Hey!'' Luke yelled interrupting the boy, ``now I don't know what in
the hell you're going on about, but it ends right now. Get out of here
you sick freak, get out! Get ou-'' Luke searched for something to
threaten the boy with, grabbing a lamp that had been behind him, but he
turned back only to find the boy had disappeared, he was gone.

Luke rubbed his eyes. Had the boy really just vanished? It was
impossible. As he stood there wondering what had just happened, he
noticed that his head didn't hurt any more. He turned to search the
room again, search for the boy, search for his belongings. He looked out
the window. Outside the air was now enraged, thrashing about flinging
rain and debris everywhere. It made Luke more even more uneasy, but he
remembered the door, and he shook the feeling off. He reached once again
for the knob, as the roar filled his ears.

He grasped the knob tightly preparing for the searing pain when suddenly
it was deafeningly quiet. He turned and looked back outside. It was
bright, very bright out, and the trees and sky were calm. The door was
cool to the touch, and Luke pulled open the door, eager to see his
family.

Black. Charred wood. Everything, all of it, consumed. He steeped through
the crumbling doorway.

A burnt frame stood in place of former walls; the ghastly skeleton now
surrounded all the ash and rubble that had been a home. Outside,
surrounding the house were people. Fire crews, emergency personnel,
neighbors, all of them just standing around the house, all of them just
silently, chillingly starring. Luke was standing in what used to be a
kitchen, when he recognized it. This was his house, this used to be his
home. Where the sink had been rose a pair of pipes, jagged and singed,
but sturdy and resilient. And then he saw them. Across the blackened
room lay the dark remains of a woman clutching a child.

He couldn't breathe, he couldn't swallow. Grief and sorrow were
throttling him, and suddenly he let loose in heaving spasms as he ran to
his family. He knelt, sobbing, over what was left of them.

``No'' he uttered

The crowd erupted in a bellowing barrage of whispers that come from
everywhere and nowhere at once. Not on person's mouth was moving and
yet their voices were infinite, filling the air with an angry accusatory
heat.

``You did this''

``This is your fault''

``They came for you''

``Why did you let them die?''

``They came for you''

``No\ldots {\bf no!}'' Luke screamed, ``I couldn't stop them\ldots{}''

``I tried to save them'', he continued.

Amidst the churning crowd suddenly stood the boy again.

``I asked you not to open the door this time. I asked you to stay on the
other side.''

``I\ldots I tried to save them'' Luke sputtered out.

``No'' reasoned the boy, ``no, you damned them. You dug too deep into
our affairs; you stuck your nose in our business. When we sent our men
here to fire the house, we sent them for you. It was you that did this
to your wife. To your son. You are responsible.''

``I tried\ldots I came home\ldots the flames, they were everywhere'' Luke carried
on, distantly.

``But don't worry. There's more.'' Said the boy, ``We have much more
for you''

``No,'' Luke said sitting up, looking at the boy. ``it doesn't matter
now''

The child stared back with hollowed eyes and an emotionless gaze that
should have terrified Luke.

``You can't do anything to me now\ldots just kill me. Kill me''

The boy's brows furrowed, his face twisted, pulled and broke. He
smiled, and then began to laugh.

``Kill you?'' He said regaining his composure, ``Why? Why would I kill
you? No. We have something much worse for you.'' The crowd's maddening
chants began to bleed through the boy's speech. They seemed to scream
now, everyone of them and none of them at once. Angry, haunting howls
pierced through Luke's hands as he covered his ears.

``No, {\bf noo!}'' he screamed as he began to beat his head against the
rubble. But it did nothing to lessen the shrieking crowd. He had to end
it. He looked around and saw the pipe sticking out of the foundation. It'
ll do he thought.

He stood, the cries and screams still pursuing and punishing him. He
struggled over to the pipe, rusty and charred. He'd have to be
quick. He'd only get one chance. He took a breath and slammed his head
down.

Luke awoke in a bed.

He stared at the ceiling; his head ached, pounded as he struggled to sit
up. He was in a clean white room.

There was a noise. Familiar. Welcome.




