\chapauth{THE WORST DOCTOR}
\chapter{The Snake Lady}


There was a kid who came up to me one evening after I had left my
precinct, sniffling and tugging on the left leg of my pants. He had
snot all over his face and I was pretty disgusted. But my job is to
help people, not to pass judgment, so I decided to give him the
benefit of the doubt. Maybe he had cash on him.

``What's wrong, kid?'' I asked. An ominous breeze
blew from the south. It was going to rain. I didn't ask him
why he was by the bar at such an age. A kid's gotta do what a
kid's gotta do.

``Some lady stole my candy,'' he told me, wiping the snot
from his nose and the tears in his eyes in an upward motion. Both
bodily fluids ended up on his forehead.

``Well,'' I said, popping the collar of my Armani jacket.
``I can handle that. Stay here, sport.''

I gave him a pat on the head, not unlike the pats my father used to
give me when I hadn't completely screwed everything up, and
went into the building.



There was nothing in there that was particularly special, save for
a few local drunks hanging out in the corner. The bartender gave me
a nod, a knowing one; he could tell from my hat and flashy badge
that I meant business. That's what it is to be a private
detective, after all. I sidled up to the bar and took a seat on a
rickety barstool, ordering my usual: an appletini. A girl at the
bar eyed me. She looked like a bitch. I knew I had found my
target.



``Hi,'' she said once I got my drink. The light leaked
from the neon signs that said {\sc Paradise}. I chuckled as
I sipped my cocktail gingerly. How ironic.

``What can I do you for,'' I asked. I didn't mean
it the way I made it sound.

``It's not often a man like you comes to town,''
She said, giggling. I noticed she was wearing a rusty
necklace.

``Yes,'' I said simply. I don't like to waste
words. She put her hand on my arm and looked at me with glimmering
eyes. I said nothing.

Suddenly she was grabbing onto my arm and digging her horrid nails
into my flesh. I cried out. My skin was on fire. She drew blood and
laughed like my grandmother used to.

At that moment I knew I hated her.



``You're a thief and a liar!'' I yelled, kicking my
barstool into her lower half. She fell down and brought my
appletini with her as she tried in vain to grab the bar for
support. The people around us piled out of the bar while screaming
and running. I was glad they knew enough to leave at this moment.
It was going to get ugly.

``Bavarioussssss,'' she quipped, her tongue long and thin
like a snake. Her rusty necklace was rusted. Even more rusted than
before. She had no legs now. She was like a snake on the bottom.
Cruel and unforgiving. She was going to squeeze me. I knew
it.



I felt like vomiting. A thin stream spluttered from my mouth. It
got all over my new boots. I was blind with seething rage as I dove
toward her, knocking over bottles of Jack Daniels. I began to punch
and punch and punch. I was screaming though I didn't know
why. She fought back feebly. She tried to kick me but she had no
legs anymore. I laughed. How unfortunate.



She was bleeding a lot. It got all over me. Luckily I had tucked my
tie into my belt. It wouldn't get in my way. She scratched at
me again and called me mean things. There was blood, awful blood,
leaking from her eyes. It was red. Dark red. The color of a heart
after it's been taken out of a body. I was going to take her
heart out of her body. Then I thought against it. Too messy.



Finally I drove the rusty necklace into her. She died of rust
poisoning. She giggled one last time at me before slumping onto the
floor. Then she disappeared in a cloud of smoke.

``Should've gotten your tetanus shot,'' I
commented. I gathered up the kid's candy, colorful wrappers
that may as well have contained pure cane sugar, and went
outside.



The kid was there, snot dried in his hair. He was wringing his
shirt with his grubby little hands when he saw me, fearing the
worst. I dropped the candy on the ground in front of him, and lit a
cigarette for myself.

``Don't let it happen again, champ,'' I said. He
nodded and understood. As he walked away, munching on his dental
problem candy, I was reminded a little bit of myself. Life before I
became a detective. A simple, idle life with no worries. But that
was all behind me now.



I'm Luke Bavarious, detective extraordinaire. 

 



