\chapauth{The Iron Fury}
\chapter{The Horrid Refraction}


{\em This entry picks up immediately after {\rm The Horrid Reflection}
ends.}


Suddenly, I was sobbing. Once the tears ceased leaping from my
blood-drenched sockets, I took a moment to recollect myself. My
muscles tensed. I looked down at the dark, mangled body next to me.
What the fuck, I thought. I still had glass in my face. My head
throbbed. I rolled the corpse onto its back. And vomited. I vomited
so hard, so long, that a vessel burst in my eye, coloring it red as
Satan's ass. Its body had dissolved into phlegmy puss. The alley
stunk of fear and sweat and blood. And now vomit.

The glow of some unspeakable evil hung heavy, looming over the dark
corridor. It pulsated. I had to get out of there. I had to think
about what just happened.

I got to my lodgings and cleaned up. As I was picking glass out of
my shattered skull, a knock sounded. Heavy- angry almost- on the
thick wooden door. Inching to the corner of the room, I determined
to wait them out. I had darker matters to attend to. What was that
thing I had glimpsed in that dim alley? Why did it wear my badge?
Why was it--

``Bavarious! I know you're there!'' a feminine voice bellowed. I
could sense there would be no introspective pondering for me this
evening. I edged to the door. Skin standing at attention, hairs all
prickle, I passed my hairy appendage over the door knob. Slowly, I
creaked it open. Standing before me was a person I had thought,
hell, hoped I would never see again.

Nora Fury. A halo of fiery red curls cascaded about her, wild and
unrestrained. Just like she was. A single cigarette smouldered in
her claw-like grasp. As soon as she was in the dank room, a slap
encircled my raw face. Blazed like the fury for which she was aptly
named.

``How dare you leave me in Mexico,'' she sneered. I sneered back at
her sneer.

``How dare you shack up with that drug lord,'' I returned with equal
disdain. ``Can't we just move on? You're a tough dame. I knew you
would come out on top. Here, lemme pour you a drink.''

I knew that when Nora was mad, she was a hellcat under the covers.
Maybe a nice distraction would ease my beleaguered mind. I turned
to the crimson cabinet behind my desk and my hands found their way
to two glasses and a bottle of whiskey.

``So what d'ya need from me, Sugar?'' I smarmed, holding out the
stiff libation. It dropped to the floor, shattering at my feet.
There was no one in the room.
 



