\chapter{Untitled}
\by{TheSpiritFox}


Luke walked into his room. Man! What a shitty day.



He hated this town. Ever since he'd been moved here, the days just
got longer and longer, more and more boring. From the hours long
train ride into the city to the four hours of processing to even
get past the train station, he'd been bored to tears for months
now. The shelling had begun two days ago, but it had yet to affect
his part of the city, so he ignored it like he ignored the usual
sounds of doors crashing down in the middle of the night. It was
never {\em his} door. He never got to play.



He'd talked to his mother about it, asked her why their family
never got to have fun like everyone else's. Why they never got to
go on the vacations his parents told him about. Why the police
didn't come and take them fun places. She told him it was because
he was special.



He hated being special.



Luke heard the front door open and close, the lock clicking as two
sets of footsteps walked into the small apartment.



Great. His parents were home.



He heard hushed, worried voices, and his heart jumped. Thats how
all the neighbors always talked before they went on vacation. His
parents were probably worried about what to bring, since people
always had to say yes and go immediately without packing if they
wanted to get in on a vacation. A small vibration shook the
building, as he realized that the shelling had finally moved to
their part of the city.



His mom had told him about the shells. They dropped pinata's into
the city which burst open, and people got to keep whatever they
grabbed out of it! He couldn't believe his luck, two events in one
day! Maybe when they left on vacation he'd pass near enough to a
shell to get to keep something.



He hoped his luck was turning.



There was a pounding on the door, and he burst out of his room
eagerly with his pillow and blanket.



``Open up!'' a rough voice shouted. His parents gave frightened looks
back and forth, he knew they'd been caught unprepared. Luckily, he
was a practical kid, all he needed was stuff to sleep with. His
parents opened the door to see a guy in some wierd kind of mask
like science on his face.



``You're to come with us. Now''



His parents obediently followed out the door, and Luke Bavarius
brought up the rear, his proud strut meant to show anyone who
watched that it was {\em his} turn now. He just knew that his
vacation would be far better than anyone else's had ever been. He
knew he was special, and he knew they'd only have made him wait
this long to prepare everything in advance.



They walked out the front door of the building, and he walked right
into his mothers back as he saw what had frozen the policeman with
science on his face. Two shells sitting there waiting in the front
yard, freshly landed.



Luke could not believe his good luck, in all his 10 years he'd
never gotten anything special for himself, and he could understand
how anyone would be frozen with excitement upon seeing not one, but
TWO untouched shells to be raided.



Luke darted past his parents frozen forms to the leftmost shell and
eagerly peered inside it. A small form moved, and leaped out. Luke
ducked out of the way and turned, seeing a small four legged animal
standing on the ground. It didn't seem to have any eyes, but looked
at him just the same.



``A pet!'' Luke thought. ``A pet! I've heard people used to have pets
but I never thought I'd have one of my own!''



Luke ran forward and grabbed the small animal before it had a
chance to move again, and heard the roar of a gun as a bullet
chipped the sidewalk not a foot from his foot. He looked up, the
science-police was pointing a gun at him! He wanted to shoot his
new pet!



Luke turned and ran, dashing behind playground equipment as his
parents screamed at him to put down the ``headcrab''



``A headcrab?'' he wondered. ``So thats what you're called, little
guy'' he quietly muttered to his new pet, hiding behind a large
piece of playground equipment.



``You'd better leave my pet alone! I'll make you sorry!'' he yelled,
mostly at the policeman. His parents were the ones who answered
though.



``Luke! Please you don't know whats going on! That thing's
dangerous!''



Luke stared incredulously at his new companion, and shouted back
``Why are you always trying to take everything away from me? Why
can't I have one thing, just ONE THING that other people have? If
I'm so special why am I always left out?!''



He knew he'd need his hands to get away, so he set his new pet down
on its four spiky legs and shushed it, telling it to calm down. It
kept trying to sit on his head though, and luke eventually relented
with a sigh, thinking it would be easier to have it sitting up
there than on his arms.



As soon as his new pet gained its throne, he felt a funny tickle at
the back of his neck. Suddenly, he couldn't move. He felt strange
little tendril-tickles under his skin and looked down to see his
veins growing, then eventually shattering and strange tendrils of
skin that looked kind of like his pet grew out of them instead. He
could see his skin rotting before his eyes, but it didn't hurt, so
it didn't scare him.



On the contrary, he felt strong. Luke was amazed at how he suddenly
felt like he could lift a car or jump 15 feet in the air without
trying.



His amazement was shattered a moment later as a flurry of bullets
tore through the playground area he'd just been hiding behind. But
before the first bullet was through the material enough to hit him,
he was eight feet away in a crouch.



It was a flash, but a very clear one. He felt like he could
remember each individual fraction of the half a second it had taken
him to dodge the bullets. But his wonder quickly turned to
anger.



The science police was trying to kill them both! Red rage caused
his heart to accelerate to a hummingbird like rate and a curtain
fell across his vision as he realized that science police wasn't
trying to take him anywhere fun, that in fact science police was
about to take away the only thing he'd ever truly loved. He sprang
completely over the playground equipment and charged straight at
the man. He saw the man shoot twice, felt the impacts and watched
skin and gore fall off of his body in equal amounts, but to him it
was no different than running into a mosquito that was flying
forward intending to bite.



He leaped again, and crashed down on the policeman. He knocked the
science off his face and stabbed a hand down at his head. He was
strong, his hand went completely through the policeman's head and
cracked the concrete below. Luke looked down at the mingled brain
and rotting arm, and vomited up a small amount of bile.



He immediately swallowed it, as his face was covered by his
headcrab.



Still enraged, he turned to see both of his parents there. They
were in on it too. They had stood there and let the science police
try to take his new pet headcrab away.



He roared inarticulately as he hurled himself at them, stabbing at
their chests with both of his new, stronger arms. His hands went
through, and his parents stared down at him in horror.



He could feel their pulsing hearts in his hand. He looked into
their eyes (strange, how he could see them through his pet's body)
and said ``I told you you'd be sorry''



They were. You should always listen to your kids. 

 



