\chapter{Brian}
\by{Torgo!}



Brian hated the new house. Ever since his family moved in he could tell
there was something not right about it. He especially hated his room. It
was an old dusty old room that smelled like death. Their were cobwebs in
his closet and the room smelled like many years gone by.



The first few nights in the house came and went without any events.
On the eighth night though Brian was awoken by a noise eminating
from the closet. It sounded like a big dog was trapped inside. All
Brian could hear was clawing and low grunts and what sounded like a
big dog walking in circles in the closet. Brian cowered under the
sheets afraid to peer out. After ten minutes or so the sounds went
away. Brian lay awake the entire night.



In the morning Brian told his parents about what had happened. They
just told him that it's normal. That old houses have a way of
making sounds like that. Brian didn't believe them though. He knew
what he heard wasn't just a house. It was something else. Something
unnartural.



The next night Brian was awoken to the sounds again. As Brian lay
under his sheets he heard what sounded like sniffing and pawing
coming from the closet. He also heard something else this time.
What sounded like the sharpest fangs tearing apart meat. He also
heard chewing. As Brian peered out from under his sheets he saw a
pool of blood forming under the door. He quickly leaped out of bed
and down the hall to his parent's room. ``You've got to come quick
to my room and look!'' His parents slowly lumbered to his room.
``Their, in my closet!'' His Dad looked in the room but didn't see
anything. He even went to the closet and looked in the door but
didn't see anything.



For the next few weeks nothing happened{\ldots}



Today was Brian's Dad's birthday. Brian and his mom went to the
local mall and picked out some nice presents to give to him. His
mom bought him a toolset that had wrenches and screwdrivers and
Brian got his dad a nice necklace. While Brian's dad was at work
they made him his favorite meal and made a nice cake. Brian's dad
really enjoyed his meal and wore the necklace all the time after
that.



Brian was a lot happier these days because he hadn't heard anything
from the closet for a while.



Another thing that happened is that Brian and his family decided to
start raising rabbits. They had started with 5 five rabbits but now
they had 9.



One day Brian went outside to feed them and was shocked because
there only 3 left. The fence had been broken into and their were
large tracks.



Soon after this Brian started hearing noises from his closet again.
It was the same as before. All Brian could do was cower under the
sheets until the morning light returned.



One dark and wintery night Brian was hiding under the blankets
while he heard the rustling from his closet. As Brian shook and
shivered the noises were growing louder and more violent. Suddenly
he heard the creature burst forth! It shattered through the closet
and crashed into the opposing wall. Brian was now paralyzed with
fear. He dared not look out from his sheets. He could hear the
creature walking towards him, its claws clacking on the floor. He
could hear the beast sniff his sheets. Suddenly he felt the
creature leap onto his bed. Through the weaving of his sheets he
could see glowing red eyes and a large grimacing mouth full of
fangs. But the most shocking thing of all is that he could just
make out the glimmering of something hanging from the creatures
neck in the moonlight. It was the necklace he bought his
father!



``You were always my child'', the creature snarled to him. ``And now I
will give you the Dark Gift!'' ``After all like Father like son!'' The
creature then bit Brian on the face and the transformation began. 

 



