\chapauth{Tufty}
\chapter[Dames, they're all the Same]{Dames, they're all the Same: a Luke Bavarious detective story inspired by the works of Ben Biddick}





I'm a private detective. Luke Bavarious is my name. Bavarious by
name, Bavarious by nature. I own this city. The feds think they've
got this place locked up tight, but the criminal scum of the
underworld run rampant through the darkened streets committing
crimes and vandalism. This is where I come in. My name is Luke
Bavarious, and I'm a private detective.



I'm a man with nothing to live for and nothing to lose, and there's
only two things in my life that I wouldn't want to lose, and
they're both Berettas. One is a gun, and I keep it locked and
loaded in my desk drawer, and the other is my sexy secretary, Gina
Beretta. An Italian seductress packing a big chest, tiny waist, and
a loaded gun. There's nothing sexier than a woman with a gun.



The phone on my desk rings, I pick it up. It's Gina. ``There's
someone here to see you.'' says Gina. ``Send them in.'' I reply. Into
my room walks the most gorgeous dame I've ever seen in my life. I'm
talking beautiful - tall, brunette, and an ass like a couple of
melons. Says she has a job for me - the big one, my ticket out of
this hell hole they call a city. She tells me that a couple of big
time crooks are planning a heist on the New York City Bank, and she
wants me to stop them. ``But how do you know this, and why are you
telling me?'' I ask. ``One of those jerks is my ex-boyfriend, and the
idiot left the bank's blueprints and a copy of their plan at my
place before he dumped me.'' ``Hmmm{\ldots} that does sound stupid. I'll
take the job.''



Fast forward to a week later and I'm waiting outside the New York
City Bank. According to the plans, the crooks should be here any
minute. I lean against a street light and light up a smoke, the
wispy trail of smoke rises into the cool night air. I hear a click
like the sound of a cockroach being squashed, and I feel a cold,
hard object poke against my back. ``Don't move, Bavarious'' says a
rough voice filled with pure and utter hatred. The dame set me up!
I knew I never should have trusted her, dames are all the same.
With the lightning-quick speed of a cobra I kick my leg backwards
and send the gun flying out of my assailant's hand. It lands on the
road before skidding down a drain into the sewers. Before my
attacker could even react I've drawn my gun and spun around.
Suddenly, with shock and disbelief I see that the face of my
attacker is actually that of the dame who hired me for this job!
She must have been changing her voice to fool me. She looks
different this time, her eyes are as red as freshly spilt blood and
her skin has a greyish twinge, like a freshly embalmed corpse. ``Why
did you try to set me up?'' I ask her, pressing the gun into her
chest. ``Because{\ldots}'' I press the gun harder into her chest,
impatient for an answer. ``Because, Luke{\ldots} I am your sister.'' My
head reels as my world comes crashing down around me. My sister? I
have a sister? I think back to my childhood and don't remember
having a sister. Thinking of his troubled past and childhood caused
Bavarious to vomit. He did not like to think about his past. As the
vomit pooled on the floor, he could see the reflection of the dame,
his supposed sister, in the slick surface of the pool of vomit. The
sight of her like that brought it all back to me, but in my
distracted state, the dame gives me her best right hook right in my
jaw, and the world turns black{\ldots} 
 



