\chapter{The Sack of Horrors}
\by{Twigand Berries}


I polished off another set of ten and felt that good, deep burn. I
sat up from the bench and flexed, noting with pride the hills and
valleys of my bulging musculature. My sweat caused my sleeveless
shirt to stick to my body, and I thought to myself, ``Damn, Luke.
You look good.'' That's right. My name is Luke Bavarious and I am a
private detective.



And let me tell you, smacking punks and thugs around, you need to
be in great shape. And when I'm not cracking the skulls of dopers
and adulterers, I hit the gym, pump some iron, and sculpt my body
into a machine.



I couldn't very well meet up with my clients covered in sweat, so
like always, I hit the showers to clean up. As I approached my
locker, filled with my fitted suit, trenchcoat, and my Beretta
snuggled in its holster, my eyes were literally destroyed by a
sight that plagues my visits to this mosty holy Temple of the Body.
Sure enough, some old man was standing at the sink, shaving,
completely buck naked.



His wrinkly body sagged in every place imaginable. Hair sprouted
from various places hair should probably not sprout from. His skin
was covered in spots and possibly sores. What he does at the gym is
a complete mystery, as his flabby body and gigantic swollen stomach
betrayed no evidence of any cardio or properly balanced muscle
training whatsoever. But the worst was his balls. His old, wrinkly,
sack hanging down from his groin farther than it would seem humanly
possible. I almost vomited all over the changing room floor.



I grabbed my towel and hit the showers, this monstrous image burned
into my brain. As the water steamed off my red, ripped body I tried
to come up with a reason why these old men would ruin my work out
in this way. I come here to feel good and make myself into a god,
but every day I am assailed by these geriatric sacks of downward
flowing flesh, and am constantly reminded where we are all headed.
I scrubbed myself down, lingering my gaze over my own perfection,
to banish thoughts of old, naked balls out of my head. I needed a
drink.



Instead of heading to my office and checking my messages for new
cases to crack, I headed down to my local pub hoping some old
friends would have the same idea. Sure enough, Brad and Hooksey
were draining some pints, and I sidled up to the bar next to them.
My mind was still spastic over the horrors from the gym, so I
broached the topic to my friends.



``Brad, Hooksey{\ldots}you guys work out, it shows by the way, and I'm
wondering if you two encounter the same problem as I do,'' I
said.



``Do tell, Luke.'' Brad leaned in, interested.

``Yes, Mr. Bavarious. I love your stories!'' Hooksey exclaimed,
excitedly.



``Well, friends, you know how after you burn through your reps and
it's time to clean yourself up, you go for a shower, right?'' I
asked.



``Always.'' Brad said.

``I like to shower.'' Hooksey replied.



``Well, why is it that every time you go into the locker room, there
is some disgusting old man doing stuff naked? Like, I know you have
to change your clothes in there, and there will be a point where
you're naked, but these old guys are ridiculous. They get naked,
and then it seems like they don't want to get dressed again. They
stand around talking. They shave. They comb their wispy hair. They
spend more time naked in the locker room than they do exercising I
bet! And here I am trying to perfect my body, and I have to gaze
upon these leathery sacks of fat!'' I explained!



``It makes me want to punch their faces off,'' Brad agreed.

``I think I will vomit my puke up just thinking about their
disgusting naked bodies,'' Hooksey chimed in.



Now, while I was telling this story, some young, scrawny punk came
into the bar trying to sell some candy bars for the Girl Scouts or
something and he overheard the whole thing. This punk felt the need
to chime in.



``I don't know you gentlemen, but I couldn't help but overhear what
you are discussing. I think you should be ashamed of yourselves
talking about the elderly in this manner. They are deserving of
your respect. They won World War II so you can be free, and shame
on you for talking about them this way,'' the punk admonished.



``Hey, now{\ldots}'' Brad exclaimed!

``There are old germans!'' Hooksey rebutted.



My friends were red in the face at the nerve of this punk, but I
knew how to end this argument. I slid off my bar stool, and turned
to the punk. He looked up at me with fear in his eyes, and I
casually opened up my trenchcoat. His eyes wandered down past my
ripped pecs and spied the Beretta casually hanging out in its
holster. The blood left the punk's face and he ran on out of the
bar, urine soaking his trousers.



``Hahahahahaha,'' Brad laughed.

``Hahahahahhaa,'' Hooksey laughed.



I smiled, and turned back to my beer, thoughts of disgusting flabby
old ass gone for the evening.



* * *




The next day I awoke with the urge to pump some iron again. I
hurried down to my gym and entered the locker room to change into
my work out clothes. As I was squeezing into my sleeveless tee, I
looked towards the sink.



You guessed it. Just standing there, naked, in front of a full
length mirror was the most disgusting specimen of humanity you
could ever encounter. I would regale you with details of his
mottled, paper thin skin, or his liver spotted, veiny scalp, or
even how his biceps swung in the breeze, but it all pales in
comparison to the most disgusting old man balls I have ever
seen.



I stood like a deer in headlights staring at this inverted mushroom
hanging for kilometers beneath an enormous, hanging gut. The gray,
crispy thicket that it sprouted from. The scraggly forest of pubes
that grew to ungodly lengths off the wrinkly, vein covered surface.
The swirl of reds and purples that colored its sagging surface. The
bumps and grooves. It was awful.



I was transfixed in my disgust. But slowly I got a hold of myself
and my eyes raised from his lower regions, over his disgusting
flabby body, and onto his wrinkly face in the mirror. And to my
horror, his eyes matched mine in the mirror. He was watching me
watch him!



And he smiled. A gap toothed smile framed in crusted lips.



I ran from there. I entered the gym proper, fighting back vomit and
the desire to unload my Beretta into his nasty, smiling food
hole.



The only way to recover from this was to focus every fiber of my
being into my workout. And I racked up an obscene amount of weight
onto the bar and reclined onto the bench. Screw warming up. I was
going to pump that disgusting image right out of my mind with the
sweet burn of my muscles pounding out ten reps of my maximum
benchpress.



I hefted the bar off the cradle, balancing the weight between my
two pistons of might. I closed my eyes, and began to work my way
into the set.



{\bf One.}



The bar was lowered to my chest and I shot it back up with a
groan.



{\bf Two.}



My blood raced into my chest and arms, filling me with energy and
purging weakness.



{\bf Three.}



The burn began. It felt magnificent.



{\bf Four.}



I began to imagine the bar was some punk who dared to pull a gun on
me. And I was shoving his punk face off a cliff.



{\bf Five.}



I could feel the muscles in my biceps and triceps begin to quiver
with sweet burn.



{\bf Six.}



Maybe the punk was that punk from the bar. That punk who likes old
guy balls. Heh.



{\bf Seven.}



A warmth spread across my upper body as I heaved the bar up and
down, bringing it within a centimeter of my chest.



{\bf Eight.}



Images of disgusting balls were burned from my mind as I imagined
that punk kid being riddled with bullets, bursting from his back in
miniature explosions of flesh.



{\bf Nine.}



As I crested my ninth rep, suddenly the bar seemed to become twice,
no, ten times as heavy! I locked my elbows and gasped. It was
unbelievable! My elbows gave out and my arms began to shake as the
bar began to lower to my chest. I opened my eyes and looked
up.



I moaned in horror! It was impossible!



The bar was still there with the normal amount of weight on either
end. But between my gripping fists, in the exact center of the bar, hung
what could only be the {\em the same pair of balls that previously had
  been attached to that old man!}



And for the love of god, they weighed a ton! In fact, the weight
was so much that the bar was slowly being lowered down to my chest!
I stared in terror at this unholy scrotum that hung from the bar
just inches from my chest. It was all there. The unexplained bumps.
The crispy gray pubes. The mottled coloring. Oh my god! There was a
sore on the underside of one of its orbs! As my arms shook and
slowly lost control of this tremendous weight, I stared at
pulsating veins that throbbed in a spiderweb encasing the two
misshapened testicles that were contained within its leathery
pouch.



My arms began to feel a million miles away. The numbness spread
along my humerus, over my clavicles, and into my quivering chest.
Sweat began to pour off me in sheets. I heard a distant mewling
sound, and realized it was me.



The balls slowly descended. When they were inches from my chest,
the impossibly long gray pubes tickling and entwining with my own
chest hair, I saw a bead of brackish sweat appear from the patch of
hair that was located at the join of this evil ball sack and the
bar. It came as if from hell. It slowly tracked its way down the
elongated skin pouch, over wrinkles and around encrusted follicles.
As it beaded at the bottom of one hellish testicle, I began to
scream wildly for help.



Tears sprang forth from my eyes, and I felt all strength fade from
me. The bar swiftly began lowering, and I knew my chest was going
to be crushed and my unblemished skin covered in sweaty old meat
sack. My life flashed before my eyes, and I realized my beautifully
sculpted body was about to be defiled for all time.



``You need a spot, young man?'' came a voice from heaven.



``God yes!'' I pleaded. And suddenly the crushing weight was lifted
off me. I began to sob in relief. My body was broken. I pulled
myself up to a sitting position and gazed up at my savior.



It was the old man! He stood there, dressed now in ridiculous
shorts and v-neck white t-shirt, wiping his hands after racking the
devil bar. How could this be? I stared at the weight bar that had
almost killed me, and low and behold, the satanic ball sack still
dangled from its length.



My fury gave me strength again! I leaped from the bench and grabbed
the old man, screaming ``You bastard! Why would you crush me with
your balls? I'll kill you!'' His face whitened in surprise and
fear.



``What are you talking about, son?'' he stammered.



I pointed at his dirty nut sack hanging from the bar. ``Fiend! You
almost crushed my ribs! You tried to dirty me with your geriatric
filth!''



``I don't know what you are talking about!'' the old man lied.



``Trying to trick me, huh? I'll show you!'' I screamed.



At this point a crowd had gathered, curious as to what the
altercation was about. I had to prove to them that this evil thing
was the source of the sack of horrors hanging from my bar. I
reached down and pulled his filthy shorts down and stood back,
pointing to where his groin was missing its satchel of bulbous
evil!



The crowd gasped, and I smiled in triumph as I turned to face the
old man. My smile quickly left my face, for, suddenly, the scrotum
of Hell had reappeared in their proper disgusting place. I quickly
turned to the bar, and sure enough, it was no longer encumbered
with its evil payload.



The crowd turned on me. No one would believe the horrors I had
endured. I was thrown out from the gym, and, in my crushing defeat
by the horrors of Hell, {\bf they did not refund my membership
deposit!}



The end. 
 






