\chapter{The Scarecrow}
\by{Unununium}


Luke parked his car at the side of the road. He walked over to the
massive corn field and squinted. Somewhere out there was his big
break. If the legend held true, he knew he'd have it set. Trying to
be silent, Luke pulled apart rows of corn and began to make his way
to the center of the field. Looking out, he knew he had a long way
to go. His revolver sat snuggly in his jean pockets. He wasn't
afraid to use it if he was heard.

Luke's sneakers sunk into the moist soil, as he crept through the
corn field. He knew something was up. The full moon shined brightly
into the center of the corn field. In the center of the field stood
a mounted scarecrow. Its eyes beamed like an illuminating light,
and the straw covering its bare body poked out through seams on its
clothing. Luke was here for a purpose. As an FBI investigator, it
was his job to trot through this corn field to investigate the
claim that underneath the rugged clothing of this lifeless
scarecrow lays a corpse. He barged through a petite opening in the
corn field, and reached the scarecrow. The scarecrow was a morbid
mass of lifeless straw. A knife was tied into the scarecrows hand
with a piece of string. Luke unfastened the rope holding the
scarecrow unto the cross. The scarecrow then toppled over, landing
on Luke. It was heavier then he imagined. Luke rolled over, getting
out from underneath the scarecrow.

Luke looked out into the corn field. It was an infinite abyss of
yellow and green plants. From his viewpoint, he couldn't see out of
the corn field. Luke turned back, and noticed in shock that the
scarecrow was now standing. Luke took a step back, but the
scarecrow moved in closer. With one luxurious swipe, the monument
of hay and straw sliced through Luke's neck with its knife. Luke
vomited wildly through his neck while disturbing and tremendously
rust colored blood came out through the same orifice. A stream of
strawberry-red blood dripped from the scarecrows metallic and
majestic knife, that soon entered into Luke's head. Luke dropped to
his knees. He gurgled like a drowning infant as he struggled to
breathe. Luke vomited blood through the hole in his head as
bubble-gum colored brain matter and blood exited Luke's head with
the scarecrows knife. Luke wasn't quite dead yet, he slowly crawled
away from the deadly straw body, but it was too late. A gust of
wind and magic picked Luke's body up into the air. Like quills, the
scarecrows straw exited his body and pierced into Luke's flesh.
Luke let out one final scream, before he died. Luke's lifeless body
floated magically to the brown wooden cross. As the lifeless
scarecrow soon faded into the ground, Luke's body strapped onto the
cross. The scarecrow was now gone, but a new scarecrow has come to
take its place. 
 



