\chapauth{VelvetEvoker}
\chapter{Station 666}


Tommy and his best friend Bobby were twelve years old. They lived
in a small town that reeked of pestilence and a terrible oldness.
Bobby's parents were very strict with their son and
wouldn't even get him a television, so all they had was an
old antique radio that once belonged to Bobby's
grandpa.



Tommy and Bobby knew there was something wrong with the radio, but
no one would listen. Many times they had asked an adult to come
take a closer look at the radio, because they knew if anyone else
got the same feeling they were getting they'd burn the radio
any bury the remains. Many times Tommy and Bobby tried to throw it
out, but it was too heavy for the children to carry and the adults
would not let them throw it away because it was their old
grandpa's antique.



One night when Tommy was sleeping over at Bobby's house, he
noticed something strange. No matter where it was left the day
before, the dial would start turning and eventually it'd end
up on the frequency of 666. Tommy tried turning it as low as it
would go, and in a few hours it'd be back at 666. It was the
same thing if he tried to turn it higher.



Later that night they turned the radio on while it was at station
666, but it did not seem to be an active station. Nothing but
static spewed forth from the speakers, but in the static was the
sound of dread. Bobby's mom said that it was odd but it must
just be the dial's default setting, so still nothing could be
done about the radio.



The next day at school Tommy agreed to sleep over at Bobby's
house and leave the station on all night to see if anything
happened. However, nothing happened all night and they were tired
so they began to fall asleep. They were awoken again at exactly
midnight by a terrible screeching noise, followed by a voice.



The voice spoke in an unknown language that was possibly even older
than the radio. It was such a terrible voice that it sounded like
nails on a chalkboard and both boys had to cover their ears. Bobby
took his hand off of his ears and they were covered in blood, but
Tommy wasn't bleeding.



Suddenly Bobby leaned over as if he was about to vomit, but instead
of puke a clawed hand came out of his mouth. The hand continued to
emerge, followed by a shoulder, until Bobby's mouth could
take it no more and his head split in two, with his brains slopping
down his back and his jaw trailing down his stomach.



Finally the demon had emerged, covered in Bobby's blood and
stomach fluids. ``I am Xavid Viarabous, and no one has
survived the sound of my voice for a thousand years.''



Suddenly Tommy reached into his sleeping bag and pulled out an old
Beretta he found in the field. On it were the initials
`L.B.'. ``I survived.'' he said. Then he shot
the demon.



The radio was still not thrown out for two days. Tommy turned it to
station 666, and from midnight to 12:01 he could hear Bobby
screaming. 
 






