\chapter{The Horrid Lighter}
\by{WhereTheFishLives}





This is a long story about Luke Bavarius when he saw the shadows in
the world when he was younger in 7th grade. Bavarius is me. I saw
the them, the shadows. And it has turned my brain into darkness. I
was walking with my best friend Victor and Praeton when we found
the terrible thing. A sickly sparkle flashed the corner of my eye
and caused me to turn instinctively towards it. It was a silver
lighter, but not any silver lighter you've ever seen. It has a
skull on it with a eye made of ruby pressed into it. ``Cool'' said
Victor as he brushed the dust and soil from the lighter that was
buried centuries ago. It had a certain look that cut to my soul and
made my stomach tighten on its contents.



Victor shifted it open and his expression changed to one of evil.
My teeth clenched as I could feel scaredness take me over. Praeton
began to tremor in delerium as sickly vomit shot from his mouth
like a giant waterfall. Once the vomit was spent, a terrible white
cloud came from the eyes and from his face. The cloud had Praeton's
face. Praeton's face had a certain shocked and unhappy expression.
It would be soon be too late for Praeton. The soul was sucked into
the lighter like an evil waterfall. And the lighter's fire was
switched out for a red indescribable flame as the soul went in into
it.



``Praeton, No!'' I shouted from fear. It was too late, though. I
could tell. He was already changed in a certain way. So I ran away
from the evil duo.



My fearful brain didn't know what else to do. It told my rubbery
legs to run and they did run. The shock of the pounding of my feet
on the ground went up through me. Up through my knees and then my
legs. Then my chest and my soul and then into my brain with a
terrible power. The power shot through me like an jackhammer. My
adreniline squeezed my jaw tighter and yet tighter to fight back my
morning breakfast. Which was prevented from being vomited out by my
teeth. The wind felt strongly against my face. Blinding me. But I
didn't have time to notice. I only had time to run.



All of a sudden I was already at the door of my house when i burst
through it. ``Grand-nd dad? Help!'' I shouted! As I shot slowly like
a bullet from a gun through a sea of adrenaline. But there was no
Grandad, only Praeton who was already there. The silence was
deafening. The only sound was the horrid lighter clicking
deafeningly. I was in an abundance of shock.



``Where's my grandad fiend?!''



``He's in here with us'' Praton made a grand gesture to the lighter
in his hand.



``N-N-No,'' I stammered as I went to the closet and got out the
Baretta. The black gun metal was cool against the palm of my hand.
The blackness of the gun matched my heart's darkness as I aimed at
Praeton.

``I'm gonna take you out!''

``Ha Ha Ha Ha ha'' he laughed. ``Bullets can't hurt me!'' he said
smirkingly. I knew I only had one clip with which to dispatch this
wretched thing. To back to wherever it came from. I fired and a
bullet went directly between his eyes but didn't stop him. Again I
fired, and again, and again I fired a total of 14 times.



``Looks like someone's out of bullets!'' He cackled devilishly. Now
it was my turn to laugh



``Hahahaha! Looks like someone doesn't know anything about the
Beretta M9!'' I triumphantly shouted. With my last bullet I fired.
The 9mm bullet slickly exploded from the barrel and into the
demonic lighter which was still in his hand. While the bullet
struck, metal on metal, the souls were vomited all out of the
it.



``Nooooo!'' cried the thing as he turned to rust. ``It's all over
now.'' While the Beretta fell to the ground in slow motion I was
instantly {\em insane}. 
 



