\chapauth{Yaos}
\chapter{The Killer B}





Luke Bavarius looked down at the ground, it turned a putrid rusty
caused by the bullet holes in his latest victim, Zigmatron
McGlutenon. Luke Bavarius brought his Barreta up to his nose and
took a smell. ``This smells good, it smells like'' but
stopped in mid sentence because he thought he heard something so he
looked around but there was nothing there except some things, so he
continued speaking loudly, ``death''. Every time Luke
killed somebody it reminded him of the time his son told him that
he should not go out, and when he did and came back his son was
dead! His son had died a long time ago, almost 3 months now today.
Luke found his son's body but no head because his head was torn
off. They searched for days but no head was ever found. They even
used dogs that are good at finding heads without bodies.



``Why do I keep doing this'', Luke thought to himself.
``I can't keep killing, it won't bring back my son Luke
Jr.'' Then somebody said that this was not true at all, but
who could it be?



``But that's not true Mr. Bavarius, killing can bring back
your son, because I can help you.'' Luke saw a man he had
never seen before that looked like he was 50 years old with gray
hair and balding. His sweater smelled of blood. ``Luke, I know
something that you do not, your son is not really dead!'' But
how can this be?



``I don't understand, I buried his body in the ground myself
and his head was gone! You can't keep living without a head! And
who are?'' Luke was distrustful of the stranger.



``But you can live with a head Luke, and your son still has a
head, he's not really dead at all because the body you found was a
fake and that's why you did not find his head because there was no
head to find.'' Suddenly it all made sense very quickly, Luke
Jr. did not feel like any body Luke had felt before and he always
thought that something was wrong and now he had the proof. ``I
am Ugundun, you need my help and I have a shop that can help
you!!''



``We can't talk here Ugundun, we need to go to your store
before more thugs show up to kill us.''



So they went to Ugundun's store, where Luke had gone many times to
buy guns and bullets from from Ugundun, but it was weird that he
did not know who Ugundun was, that was very odd indeed.
``Let's have a beer'' and so they had a beer while they
talked about Luke Jr.



``Do you want my help Luke?'' He did want his help.
``Good, but first you must kill somebody for me.''



``But, I'm done killing people, I promised my dead son Luke
Jr.'' Luke was angry that Ugundun wanted him to kill, but
after a while he decided he would help Ugundun if it meant he could
get Luke Jr. back. ``So who do I need to kill''?



``You need to kill this man.'' Ugundun handed Luke
Bavarius a picture of something that looked like a man but was not
a man, it was a two legged dog.



``But it's not a man, it's a two legged dog!'' Luke
Bavarius was about to rip up the picture but Ugundun stopped
him.



``You should know that appearances can be deceiving, you found
out your son is not dead and even though you ignored him you can
still get him back.'' Luke Bavarius knew Ugundun was right so
he ran off to go kill the two legged dog.



Luke Bavarius walked into the park where the dog was hiding out, as
he walked through the park he patted his trusty Baretta that he has
used many times to kill people with. And there it was, the two
legged dog! But it was not like the picture, he was covered in
rusty blood and vomit. ``Dad'' it yelled out.



``I'm not your dad dog.'' Luke Bavarius was angry at the
dog for lieing to him.



``No dad, I am your son, I'm Luke Jr. Don't you remember
me?'' The dog slowly walked up to Luke, and as he walked
closer he turned into Luke Jr.!



``Luke Jr. It's you! I thought you were dead! I'll always
listen to you again!'' Luke hugged Luke Jr. and gave him a
kiss and a hug.



``I love you dad, how did you find me?'' Luke explained
to Luke Jr. how he found him. ``Ugunden was the one that
turned me into a dog dad, you have to stop him!'' Suddenly it
all made sense, that's why Ugunden knew his son was not dead it was
because Ugunden had taken him all the time! Ugunden hated how much
Luke Bavarius loved Luke Jr. because Luke Jr. was a great child and
did everything right and everybody loved him and liked him and
Ugunden wanted him to kill Luke Jr. but Luke Bavarius did not kill
Luke Jr. Now it was time for Ugunden to die.



Luke Bavarius walked into Ugunden's shop, he threw a dog's head
with a bullet hold between the eyes on the table and said the job
was done. Blood and urine oozed out of the dog's eye sockets and
bullet hole. Ugunden took a look at the head and started laughing
and laughing. ``Ha ha ha Luke, that was not a dog, that was
your son!''



``I know that Ugunden, my son told me.'' Ugunden looked
surprised.



``But why did you kill your son if you knew the dog was your
son?'' Ugunden looked scared and Luke Bavarius knew he was
scared.



``I did not kill my son Ugunden, I killed this dog to trick
you. Now you're going to be punished! Luke Jr. get in
here!''



Luke Jr. Lept through a window while shooting Luke Bavariuses
Barreta and other gun, the glass showered out and covered Ugunden
giving him many cuts and scratches. Some of the broken glass got
stuck in Ugunden's eyes which made him blind and vomit. Because
Ugunden could not see and he was covered in glass cuts he started
screaming and vomiting and running around getting vomit and urine
and blood all over the place. Luke Bavarius opened his coat up and
started throwing rats and dog guts all over Ugunden which made
Ugunden defecate and urinate and vomit and bleed even more. The
rats started eating the dog guts which made Luke Jr. and Luke
Bavarious start vomiting also. The rats tried to eat the vomit and
feces and urine but it made them sick so they vomited and exploded
covering the inside of Ugunden's shop with rat guts and blood and
feces and urine and vomit. Ugunden was still screaming and running
around and he ran out the front door of his shop. A large semi
truck was driving down the road and the driver did not see Ugunden
in time and he ran over Ugunden. Ugunden's head exploded from the
truck's tires, all the guts and vomit he had not vomited out shot
out of him like there was an explosion. The driver of the semi
truck tried to stop but it made the truck skid out of control and
the truck ran into a pet store. All the animals inside started
hooting and hollering and they all ran out and they were all on
fire. The truck was filled with gunpowder so it exploded killing
all the animals.



``Thank you for helping me dad, I am your son and I will
always love you even though you did not listen to me.'' Luke
Jr. gave his dad a hug.



``I love you too son and I will listen to you from now
on''. Luke Bavarius started to walk away, as he did Luke Jr.
Raised his weapon and pointed it at the back of Luke Bavariuses
head.



``I know you'll listen to me for the rest of your life
dad.'' Luke Jr. pulled the trigger.



The End?
 



