\chapauth{Yogi Byron}
\chapter{Horror D'oeuvres}


I am on the verge of tears by the time I arrive at Espace, as
I'm sure that I won't have a good table. However, the
maitre'd shows me my place, a cozy booth next to an aquarium,
and I feel relief wash over me in an awesome wave. I sit down. The
sound of knives scratching against bone china, however, sets my
nerves on edge. My name is Luke Bavarious. I am a private
detective. I like my work.



Complaints had been trickling in for a little over a year about
cases of food poisoning emanating from this restaurant. I look
carefully over the menu and order a lobster roll with arugula
bedding. I choose this food in particular because it is my
assignment to stop these complaints.



My suspicion is first aroused by a loud belch from the table
directly to my left. The gasses reverberate against the glass of
the aquarium and offend my nostrils. A dark and horrid man is
clutching his stomach, fork gripped tightly in his free hand. This
scene elicits a grimace of pain from his face, and, suddenly, he
shouts violently, jabbing the fork into his abdomen. A stream of
vile stomach acid and gastric juices billow forth, burning his
hands in acidic bile and causing him to vomit from behind pursed
lips onto the tablecloth in front of him. My Beretta is already
drawn as I attempt to calm the surprised crowd that is gaping at
the food-poisoned man. His wife has urinated onto the carpet and is
troubled by unwilling spasms that are shaking her body. I fire a
round into the plate of food that sits between them, while
grimacing. I snatch the ejected shell from my Beretta like
it's a flying bumblebee and place it in my mouth, clamping
down on the brass with my teeth to dull the pain of my miserable
and human, all too human, existence.



Blood is now mixing with the bile and urine into a disastrous
chemical. I fire a round with my Beretta into the man, who is
gripping the tablecloth in pain. He giggles as he is relieved of
his cruel fate, lapsing into the sweet embrace of untimely death. I
draw a bead on his poor wife, who is sitting in a pile of her own
waste like a squalid dog or cat. I fire twice. Three shells hit the
concrete. ``You!'' I yell at a waiter hiding behind the
aquarium. ``Let me speak to your manager!''



He wipes his miserable face with a cloth. ``Beggin' your
pardon, but{\ldots}I am the manager,'' he says. I motion
towards the table with my Beretta. ``Sit down.'' I say.
While he takes his seat before the lobster roll and arugula, I
catch a glimpse of myself reflected in the glass of the aquarium. A
white shirt and cummerbund are smoothed elegantly around my
midsection, and on my right side is a gleaming nametag. ``Luke
Bavarious, Head Waiter, Espace.'' Suddenly, I am sobbing. 

 



