\chapauth{Zahgaegun}
\chapter{The Pus-Stained Email from Hell}


The sweat dripped off my forehead, running down my face and forming
salty pools on the ground. Pools like the pools of blood that
always form after I kill someone. I have seen a lot of blood pools
in my lifetime for I have killed a lot of people in a lot of very
messy ways.



It's what I do. My name is Luke Bavarious; hitman, soldier,
{\em killer}.



I had been called to this sweaty place, Arabia, to kill some guys.
This was an honorable job, a soldier's mission. ``We need some guys
killed, so we called you'', they said on the phone. So here I was,
in this Godforsaken hellhole, hunched over this screen, hoping for
a morsel of communication from Home, something to feed my rotting
brain, to let me know that there was a Reason To Fight, To
Live.



Suddenly, the machine screamed out a bing-bong. New mail. It made
me smile because it reminded me of the time that I told that hooker
``You've got Male!'' while we did the sex. Now she's dead. That wiped
the smile off my face.



``I'm from the Internet'', the letter moaned onto the screen. ``We
have found your Hidden Stash of Writings from Long Ago.'' Dang, I
thought, I had hoped that no one would find that. The sweat drips
came faster now, the pools getting bigger like a child vomiting
blood{\ldots}-red cherry slurpees from the fear of riding the Viking
Ship at the county fair.



``Hurry'', it continued to moan, ``there are already many people here
pretending to be you.'' I typed fast as I could, pus-filled blisters
rising from the friction of the keyboard on my gnarled fingertips.
``I am coming'', I typed, ``Prepare the way.'' I tried to log in, but
the passwords they used were too long, too complicated for my
gnarled brain. I may only be thirteen, but my soul is almost 100
years old, due to all the killing.



Before I could get there, the sergeant bellowed my name. ``It is
time to kill'', he said while handing me a beretta and a knife.
``This is all we have left. Are you a bad enough dude to kill
everyone with just this?'' ``Yes'', said I, the cold steel of the
knife blade glinting off my eyeballs. ``Did you warn them?'', I
asked. ``Yes'', the sergeant burped. ``We flew over them and dropped
fliers warning them in whatever language they speak.'' ``Good. Then
it is fair.'', I said and walked off towards the gate of the
compound, the gate of my future and their destiny.



As he walked away, a private leaned towards the sergeant and said
``Warn them of what?''



``I warned them that The Writer is coming.'', he said. ``God have
mercy on their souls.'' 
 




