\chapauth{Zarimus}
\chapter{Little Men}


``It has happened again.'' moaned the dark clad priest, his rosary
clenched in his left hand. With his right hand he held the old
phone handset indicative of the respectable poverty of the church
office. ``Can you come right away?'' Father Dennis almost sobbed into
the phone.

Evidently what he heard comforted him and he hung up with a
relieved laugh. He turned and smiled down at the silent young boy
playing with some small figures in the corner of the room. Father
Dennis stepped forward and patted the boy on the head in a friendly
way. ``Don't worry son, the detective will find out who brutally
murdered your father and that man in the alley.''

The boy did not look up, he was still playing with the small toys,
little metal figurines of soldiers and knights and trolls he had
been carrying in a small velvet purple bag ever since he and his
mother had arrived at the church.

In a short while there was a knock at the door and Father Dennis
rose to greet the gray coated figure who introduced himself as
Detective Luke Bavarious. ``The body is in the alley behind the
church building.'' offered Father Dennis. ``You remember Nick,
Detective?'' he said, pointing at the silent boy.

``Yes I do Father Dennis.'' said Luke Bavarious, gazing with intent
at the boy. ``Has he spoken yet?'' ``Not since his father was brutally
torn apart, just like the man in the alley.'' Father Dennis faced
the grim detective squarely. ``Is it a serial killer?''

Detective Bavarious said grimly, ``We don't know yet. Let me have a
look at that body.''

In the alleyway Luke nodded to the policeman guarding the crime
scene. ``Evening Bob. Know anything yet?''

The policeman shrugged. ``Just that he died in a lot of blood. His
arms ripped off.'' Luke raised an eyebrow in surprise. ``Just like
the boy's father. Who was this guy?'' The policeman didn't know, as
it turned out. Detective Bavarious wondered if they'd ever find out
who was responsible.

Back in the church office, the boy Nicholas carefully set down a
small metal figurine that resembled a policeman. He then opened a
tiny wooden box he took from his velvet bag and gazed silently at
the two broken figurines it held. Both had their arms torn off. The
boy picked up the policeman figurine and with a swift motion, tore
off both arms.

From the alley behind the church, he could already hear the
screaming.



{\bf The End} 
 





